### 2023-01-31 paper.tex
draft - initial version

%% Manuscript for the effect of designed conversational architecture on the perception of agents
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf,screen,review, anonymous]{acmart}

\usepackage[linewidth=1pt]{mdframed}
\usepackage{lipsum}

\newcommand{\cmt}[1]{}%{\ignorespaces}

%% NOTE that a single column version may be required for 
%% submission and peer review. This can be done by changing
%% the \doucmentclass[...]{acmart} in this template to 
%% \documentclass[manuscript,screen]{acmart}
%% 
%% To ensure 100% compatibility, please check the white list of
%% approved LaTeX packages to be used with the Master Article Template at
%% https://www.acm.org/publications/taps/whitelist-of-latex-packages 
%% before creating your document. The white list page provides 
%% information on how to submit additional LaTeX packages for 
%% review and adoption.
%% Fonts used in the template cannot be substituted; margin 
%% adjustments are not allowed.
%%
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2023}
\acmYear{2023}
\acmDOI{XXXXXXX.XXXXXXX}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Conference acronym 'XX]{Make sure to enter the correct
  conference title from your rights confirmation email}{June 03--05,
  2018}{Woodstock, NY}
%
%  Uncomment \acmBooktitle if th title of the proceedings is different
%  from ``Proceedings of ...''!
%
%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
%  June 03--05, 2018, Woodstock, NY} 
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}
%TC:ignore

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
% \title[short title]{How to Make Pinocchio a Real Boy? Designing conversational architecture elements to achieve desirable anthropomorphized perceptions}
\title[Bot's Guide to Being Human]{Bot's Guide to Being Human: Investigating the Effect of Conversational Architecture Elements on the Anthropomorphized Perceptions of Conversational Agents}
% Blurring the line between human and bots

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Christina Wei}
\email{christina.wei@mail.utoronto.ca}
\affiliation{%
  \institution{University of Toronto}
  \city{Toronto}
  \country{Canada}
}

\author{Young-Ho Kim}
\email{ygho.kim@navercorp.com}
\affiliation{%
  \institution{Naver Corporation}
  \city{Seoul}
  \country{Korea}
}

\author{Anastasia Kuzminykh}
\email{anastasia.kuzminykh@utoronto.ca}
\affiliation{%
  \institution{University of Toronto}
  \city{Toronto}
  \country{Canada}
}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Wei, Kim, and Kuzminykh}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  TBD
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{conversational agents, user perception, conversational architecture, social cues}

%%\received{20 February 2007}
%%\received[revised]{12 March 2009}
%%\received[accepted]{5 June 2009}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle
%TC:endignore

\section{Introduction}

Conversational agents (CAs) are software-based systems, either voice of text-based, designed to interact with humans using natural language. Adoption for CAs such as Alexa (Amazon) or Siri (Apple) are rapidly growing in the market, with half of US internet users own one or more smart speaker devices \cite{2022comscore}. These conversational agents are designed to be ubiquitous, easily accessible through smartphones, tablets, laptops and smart devices. Because these agents leverage natural language for interaction, they solicit social responses from users, encouraging users to attribute lifelike qualities, a.k.a. anthropomorphized perceptions to CAs \cite{eyssel2012if}.

Anthropomorphism is defined as the attribution of traits that we typically associate with being distinctly human to nonhuman entities \cite{waytz2010sees}. For example, users tend to personify conversational agents like Amazon Alexa by using person pronouns instead of object pronouns in online reviews \cite{purington2017alexa}.  Research shows that anthropomorphic design is beneficial to establishing and maintaining trust between users and conversational agents \cite{seeger2021chatbots}. Also, speakers tend to align their lexical choices with conversational agents, similar to human-human conversations \cite{cowan2015does}. Anthropomorphism has been shown to ease user interactions, e.g. making agents more approachable, engaging, and trustworthy when they exhibit human characteristics \cite{qiu2009evaluating}. These processes are of particular interest for human-agent communication because they form the basis for user expectations and predispositions regarding agents' behavior, reliability of the information, etc. \cite{kuzminykh2020genie}.

One of the key factors for anthropomorphized perception is how conversational agents convey information through verbal or non-verbal cues. Studies have found that conversational agents are perceived as more socially present and emotionally intelligent if they use sentiment-adaptive response based on user's utterances, resulting in higher user satisfaction \cite{diederich2019emulating} \cite{yang2017perceived}. Also, CAs that mimic user behaviour through lexical alignment reduce users' cognitive workload, resulting in higher engagement with the interaction \cite{spillner2021talk}. Non-verbal cues such as expressive prosody contribute to higher perceived intimacy with the user, as well as higher perceived enjoyment and ease of use \cite{kim2020can}. However, conversational architecture design may lead to negative consequences, such as an agent with an extroverted personality may be seen as less trustworthy, as users are irritated by the system's overly familiar attitude \cite{andrews2012system}.

Even though there are existing research efforts investigating the effect of various conversational architecture elements on the anthropomorphized perception of agents, there is no clear view on the overall landscape on the state of research to understand what has been studied and what needs more efforts. Some reasons for this gap could be due to the lack of consistency in perception measures such as humanness or empathy. There are various questionnaires used in the studies (e.g. Godspeed Questionnaire) but their definitions for perceptions may be different. Also, there are various confounding factors like prior experience and domain of usage that makes it hard to generalize design principles for anthropomorphized perception of agents.

This paper attempts to address this gap in knowledge by investigating the following research questions: (RQ1) How does the specifics of conversational architecture design affect the anthropomorphized perception of CAs? and (RQ2) How does the specifics of conversational architecture design affect the perception of interaction with CAs? Through a comprehensive review of the existing literature, this paper presents the synthesis of a design framework developed based on X number of paper published between 2010 and 2022. The framework associated four categories of perception - interaction, ability of the agent, human attributes of the agent, and social connections with the user, with four categories of conversational architecture elements - verbal (content, style), visual (CMC), auditory (voice qualities, vocalizations), and chronemics adapted from Feine et al \cite{feine2019taxonomy}.

<One paragraph summarizing results>

<One paragraph outlining contributions to the HCI community>
* Synthesize existing framework into design framework \newline
* Point out gaps in research \newline

In the remainder of the paper, we first review the existing literature on design frameworks for conversational agents and measures of anthropomorphized perceptions. We then describe our literature review and data analysis process, following by describing the design framework synthesized based on findings of the collected literature corpus. Finally, we discuss the critical gaps in research identified through our analysis, and propose key opportunities for future research.

\section{Literature Review}

Synthesis on conversational architecture

Synthesis on measures

Connections between conversational architecture elements and measures

\section{Methods}

\subsection{Search Procedure}

We reviewed and selected relevant literature related to designed conversational architecture elements and perceptions of conversational agent following PRISMA guidelines \cite{prisma}. Searches were carried out in the ACM Digital Library between January 1 and January 15, 2023. Based on search terms used in previously published literature reviews on conversational agents \cite{clark2019state}\cite{rapp2021human} , the following keywords have been identified to search for publications related to conversational user interfaces:
\newline

\begin{mdframed}
"conversational agent" OR "natural language interface" OR "IPA" OR "intelligent personal assistant" OR "chatbot" OR "speech interface" OR "voice assistant" OR "intelligent agent" OR "human-chatbot communication" OR "virtual agent" OR "dialog* system" OR "voice user interface" OR "human computer dialog*"
\end{mdframed}

\subsection{Selection Criteria}
The initial query retrieved 2901 unique publications. The following selection criteria are applied to identify literature related to the effect of conversational architecture on perception of agents:
\begin{itemize}
  \item Peer-reviewed publications written in English
  \item Voice-based or text-based disembodied conversational agents
  \item Interaction study on the impact of designed conversational architecture elements on the perception of agents.
  \item Users must interact with conversational agent in the study. Observer studies are excluded from the corpus
  \item Measures the perceptions of the interaction or perceptions of the agent as part of the study
\end{itemize}

We screened the titles and abstracts of the papers based on the selection criteria below which resulted in 221 papers. Reviewing the full articles of these publication resulted in <X> papers for analysis. A backward/forward search was also performed to find new publications, adding <X> papers to the corpus.

<Add graphic of PRIMSA process>

\subsection{Data Analysis}

Categorization of perceptions \newline
Categorization of social cues \newline

\subsection{Dataset Characteristics}
* Year and publication venue
\newline
* Modality - voice vs. text
\newline
* Systems tested - WoZ, prototype, actual applications

\section{Framework}
%Wrote based on papers up to [60], 25 papers

\begin{figure*}[h]
  \centering
  \includegraphics[width=\textwidth]{heatmap.png}
  \caption{Heatmap of literature for perception of conversational agents for each type of conversational architecture element.}
  \Description{This graph shows the number of papers measuring the effect of conversational architecture elements on different perception measures of conversational agents. Conversational architecture elements are categorized into content (affective language, self-disclosure, humour), format (disfluency, typo, capitalization, speech rate, response delay), and style (lexical alignment, formality, emoticons, prosody). Perceptions are categorized into perception of interaction with an agent (engagement, satisfaction, accuracy), perception of social connection with an agent (intimacy, conversation tone, social presence), and perception of agent's humanness (human-likeness, trustworthiness, personality traits).}
  \label{fig:heatmap}
\end{figure*}

Figure \ref{fig:heatmap}

%%%%%
\subsection{Perception of Interaction with an Agent}
%%%%%

This section discusses user's perception of their interaction with a conversational agent. Engagement, accuracy, and satisfaction are the three variables used to evaluate how people perceive interactions with CAs. \textit{Engagement} measures user's attitude towards the task they are achieving through working with the agent, including how easy it is to use the system and its perceived usefulness, convenience and helpfulness for the user. Additionally, it includes the user's emotional responses to the interaction, such as annoyance, enjoyment, and irritation. \textit{Accuracy} measures whether the agent was perceived to be able to provide the correct answers in response to the user. \textit{Satisfaction} measures the whether the agent was able to fulfill user's expectations through the interaction encounter.

Out of the list of publications that were evaluated, there is a good coverage on the effect of conversational architecture elements on the perception of interaction with an agent. Out of the three factors, engagement is the most frequently used measure to assess interaction quality, followed by satisfaction. Perceived accuracy of the agent is rarely used within literature, with only a few papers measuring this perception.

[TODO] * Associations between conversational architecture elements and perceptions
For both text and voice modalities, lexical alignment had a positive effect on engagement by decreasing the cognitive load of users.

%%
\subsubsection{Engagement}
%%
For the elements in the language content category of conversational architecture, the use \textbf{self-disclosure} by agent had a positive effect on engagement, as the participants using the chatbot with small talk and self disclosure reported higher enjoyment after 3 weeks of daily interaction. \cite{lee2020hear}\cmt{[23]}. There are mixed results on the effect of \textbf{affective language} on engagement. One study found that CAs that uses encouraging words are rated as easier to use \cite{healey2013relating}\cmt{[39]}. However, the user of words with increased lexical emotional expressiveness did not have an effect on engagement \cite{zhu2022effects}\cmt{[26]}. The use of affective language may lead to negative impacts on engagement, as a system that uses an extroverted and overly familiar words is irritating to users. On the use of \textbf{humour}, survey result did not show a significant difference in the level of enjoyment, but qualitative feedback from participants reflected that humour made the interaction more engaging and immersive \cite{ceha2021can}\cmt{[57]}.

%%\textbf{Content}

%\textit{Affective language}
%* Use words with increased lexical emotional expressiveness by selection from NRC Valence, Arousal and Dominance (NRC-VAD) Lexicon - did not have an effect on engagement. 
%* System with extroverted personality is more irritating, did not like computer using the level of familiar with them and prefer a more reserved system. \cite{andrews2012system}\cmt{[38]}
%* Encouraging personality is rated as easier to use \cite{healey2013relating}\cmt{[39]}

%\textit{Self-Disclosure}
%* High disclosure group had higher enjoyment than the non disclosure group at the end 3 weeks (similar results %around 1 week mark).

%\textit{Humour}
%* Humour did not enhance enjoyment measurement. but qualitative feedback said that humour made the interaction more engaging and immersive

For the elements in the language style category of conversational architecture, mimicking users' utterances through \textbf{lexical alignment} yielded positive results. Multiple studies have found that being lexically aligned to users resulted in lower perceived cognitive demand and decreased perceived workload \cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}\cite{spillner2021talk}\cmt{[18]}. Interestingly, perceived lower cognitive demand did not have significant impacts on ease of use \cite{linnemann2018can}\cmt{[15]} or annoyance \cite{huiyang2022improving}\cmt{[17]}. In Spillner et al's study \cite{spillner2021talk}\cmt{[18]}, both conditions of aligning words as well as aligning words and grammatical structure to user utterances resulted in higher perceived user engagement from participants.

%
%\textbf{Style}

%\textit{Lexical Alignment}
%* Using the words already used by conversational partner resulted in lower perceived cognitive demand, but did not impact perception of habitability (ease of use). \cite{linnemann2018can}\cmt{[15]}
%* Lexical alignment (using same words) resulted in lower cognitive demand, but no impact on annoyance. \cite{huiyang2022improving}\cmt{[17]}
%* Lexical alignment - both words, and structural (grammatical transformations), movie showtimes. There is a decreased workload for substitution and transformation alignment conditions. Also, there is a significant difference in user engagement. \cite{spillner2021talk}\cmt{[18]}

%\textit{Formality}
%* No significant difference between casual and formal conversational styles for enjoyment. \cite{cox2022does}\cmt{[27]}

%\textit{Emoticons}
%* Positive but non-significant trend on helpfulness \cite{wilhelm2022keep}\cmt{[28]}
%* For discussions on mental well beings, agent using emojis is rated higher for enjoyment. However, for agent with discussing physical well being, agent using emojis is rated as lower for enjoyment. \cite{fadhil2018effect}\cmt{[52]}

For the elements in the presentation format category of conversational architecture, auditory aspects of \textbf{prosody} such as speech rate and expressive tone of voice had different impacts on engagement. In one study, users enjoyed their interaction with the CA and perceived it as easier to use, as they felt the level of agent's social behaviour is matched with their emotional states \cite{kim2020can}\cmt{[24]}. However, another study did not find any impact of emotional expressive of voice on the user engagement \cite{zhu2022effects}\cmt{[26]}. On the speech rate for CAs, a normal rate is perceived as more convenient compared to a faster rate of speech \cite{choi2020nobody}\cmt{[54]}. On the visual presentation side, the study from Westerman et al. \cite{westerman2019believe}\cmt{[9]} showed that the use of \textbf{typos} by chatbots negatively impacted the perception of working with a CA on the specific task, while the use of \textbf{capitalization} did not yield any significant impacts.

%
%\textbf{Format}

%\textit{Prosody}
%* More empathetic voice: Enjoyment is marginally significant; high empathy group felt higher ease of use. People expect a high level of agent's social behavior that is matched with their emotional states. \cite{kim2020can}\cmt{[24]}
%* No impact of emotional expressiveness on engagement \cite{zhu2022effects}\cmt{[26]}
%* convenience is higher for default rate \cite{choi2020nobody}\cmt{[54]}

%\textit{Typos}
%* Negatively impacted task attraction. \cite{westerman2019believe}\cmt{[9]}

%\textit{Capitalization}
%* Didn't impact task attraction \cite{westerman2019believe}\cmt{[9]}

%%
\subsubsection{Accuracy}
%%
There are only a few studies that measured the perception of accuracy of conversational agents for an interaction. A couple of studies reported the effect of the use of language style of \textbf{lexical alignment}. One study of a text-based CA resulted in higher perceived response accuracy \cite{huiyang2022improving}\cmt{[17]}, while the other study with voice-based CA did not find any significant differences \cite{linnemann2018can}\cmt{[15]}. Dubiel et al.'s study \cite{dubiel2020persuasive}\cmt{[60]} on \textbf{prosody} did not find any significant differences on the rating for accuracy across agents with different speech rates and pitch.

%
%\textbf{Style}

%\textit{Lexical Alignment}
%* Using the words already used by conversational partner did not result in higher response accuracy. \cite{linnemann2018can}\cmt{[15]}
%* Lexical alignment (using same words) resulted in higher perceived response accuracy. \cite{huiyang2022improving}\cmt{[17]}

%
%\textbf{Format}

%\textit{Prosody}
%* AM voice - lower speech rate and lower pitch, no significant difference on rating for accuracy. \cite{dubiel2020persuasive}\cmt{[60]}

%%
\subsubsection{Satisfaction}
%%
Several research have investigated into how the usage of \textbf{affective language} impacts the satisfaction people feel when interacting with a CA. Compared to a text-based chatbot with a static and neutral response, users reported higher service encounter satisfaction conversing with a chatbot that responded with dynamic, sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}. However, the same effect is not observed for a voice-based CA as Yang et al. did not find any difference in user satisfaction rating between the emotional-expressing agent vs. non-emotional expressing agent \cite{yang2017perceived}\cmt{[44]}. On the language style used by CAs, both \textbf{disfluency} \cite{pfeifer2009should}\cmt{[12]} and \textbf{emoticons} \cite{wilhelm2022keep}\cmt{[28]} did not have any significant effects on user satisfaction.

%\textbf{Content}

%\textit{Affective language}
%* Participants using CA with dynamic, sentiment-adaptive responses reported a higher service encounter satisfaction compared to a CA that provides static, neutral responses \cite{diederich2019emulating}\cmt{[25]}
%* Did not impact user satisfaction between the affective expression or not agent. \cite{yang2017perceived}\cmt{[44]}

%
%\textbf{Style}

%\textit{Disfluency}
%* No significant effects of satisfaction. \cite{pfeifer2009should}\cmt{[12]}

%\textit{Emoticons}
%* Positive but non-significant trend on user satisfaction \cite{wilhelm2022keep}\cmt{[28]}

Studies have found that presentation formats have significant effects on user satisfaction. In Choi et al's study \cite{choi2020nobody}\cmt{[54]} on the speech rate aspect o f\textbf{prosody} for a voice-based agent, they found that user satisfaction is higher for the default rate compared to using a faster rate. User feedback reflected that the faster rate was mechanical and harder to understand. For text-based chatbots, the addition of \textbf{response delay} increased the perception of overall user satisfaction, as the timing is similar to human-human communications and felt right \cite{gnewuch2018faster}\cmt{[19]}.

%
%\textbf{Format}

%\textit{Prosody}
%* Overall satisfaction as well as speech rate satisfaction is higher for the default rate compare to fast rate. Want everyone to understand. Hard to understand the faster rate as communicating with CA over a distance (as oppose to mobile phone. \cite{choi2020nobody}\cmt{[54]}

%\textit{Response Delay}
%* Significant difference in overall user satisfaction, the timing "felt right" and comparing response to human-human communication. \cite{gnewuch2018faster}\cmt{[19]}

%%%%%
\subsection{Perception of Agent's Ability}
%%%%%

This section discusses how user perceives the agent's ability in conditions with different conversational architecture elements. It is aiming at measuring the differences in the perception with similar system's capabilities. Out of the two variables used to evaluate this perception, \textit{Intelligence} measures whether the agent is knowledgeable, sensible, and is seem as overall intelligent. \textit{Competence} on the other hand measures the overall perception on how well the agent is handling the conversation. Out of the list of publications that were evaluated, there are only a few papers that measured the perceived ability of an agent.

[TODO] * Associations between conversational architecture elements and perceptions

%%
\subsubsection{Intelligence}
%%

On analyzing the impact of different language styles on the perception of intelligence, a couple of papers studied the effect of including \textbf{disfluencies} into agent's speech. One paper found that there is no significant impact on how knowledgeable the agent is perceived as \cite{pfeifer2009should}\cmt{[12]}. Another study showed that using fillers like "um" and "uh" decreased the agent's perceived intelligence overall \cite{jeong2019exploring}\cmt{[10]}. Upon further analysis, the authors noticed a difference between task vs. social conversations, as users perceive the intelligence to be lower in task-oriented situations, but the perception of intelligence is slightly increased in social-oriented situations. The use of \textbf{lexical alignment} did not seem to impact user's perception of an agent's intelligence, as there is no significant difference reported in the agent's domain knowledge between the aligned vs. non-aligned conditions.

%
%\textbf{Style}

%\textit{Lexical Alignment}
%* Lexical alignment - both words, and structural (grammatical transformations), movie showtimes. There is no significant difference in domain knowledge. \cite{spillner2021talk}\cmt{[18]}

%\textit{Disfluency}
%* Participants perceived the agent using fillers like "um" "uh" to be less intelligent. Especially in taks-oriented situations. In social situations, perceive intelligence is slightly increased. \cite{jeong2019exploring}\cmt{[10]}
%* No significant effects of knowledgeable. \cite{pfeifer2009should}\cmt{[12]}

On the impact of presentation format, Dubiel et al's study on \textbf{prosody} using different speech rates and pitches did not yield any significant differences on the agent rating for knowledgeable.

%
%\textbf{Format}

%\textit{Prosody}
%* AM voice - lower speech rate and lower pitch, no significant difference on rating for knowledgeable \cite{dubiel2020persuasive}\cmt{[60]}

%%
\subsubsection{Social Presence \nopunct}
%%
\hfill\\

\textbf{Content}

\textit{Affective language}
* Participants using CA with dynamic, sentiment-adaptive responses reported a higher social presence compared to a CA that provides static, neutral responses \cite{diederich2019emulating}\cmt{[25]}
* Psychological distance: Participants reported they identified with the agent more when the agent was described as being able to feel / express its feelings (patiency). \cite{lee2019s}\cmt{[55]}

\textit{Humour}
* Humourous agent was not rated as more social. \cite{ceha2021can}\cmt{[57]}

%
\textbf{Style}

%
\textbf{Format}

\textit{Prosody}
* Connectedness higher in the high empathy group. \cite{kim2020can}\cmt{[24]}

\textit{Typos}
* Negatively impacted electronic presence \cite{westerman2019believe}\cmt{[9]}

\textit{Capitalization}
* Didn't impact electronic presence \cite{westerman2019believe}\cmt{[9]}

\textit{Response Delay}
* Significant difference in perceived social presence \cite{gnewuch2018faster}\cmt{[19]}

%%
\subsubsection{Competence}
%%

There are only a couple of papers that discussed the impact of conversational architecture elements on the perception of competence. For \textbf{affective language} in the language style content category, participants rated the agent higher in competence when it has higher patiency and expressed its feelings to users. In Cox et al's study on \textbf{formality}, the authors did not find a significant difference in competence between using casual vs. formal conversational styles.

%\textbf{Content}

%\textit{Affective Language}
%* Participants rate the agent as lower in competence when it could not feel / express its feelings (patiency). \cite{lee2019s}\cmt{[55]}

%
%\textbf{Style}

%\textit{Formality}
%* No significant difference between casual and formal conversational styles for competence. \cite{cox2022does}\cmt{[27]}

%%%%%
\subsection{Perception of Social Connection with an Agent}
%%%%%

This section discusses user's perception of their social connection with a conversational agent. Social presence, conversation tone, and intimacy are the three variable used to evaluate this perception. \textit{Social presence} measures user's perceived social distance with an agent, such as social presence, connectedness, and psychological distance. \textit{Conversation tone} measures user perceptions on the way an agent is speaking to them, such as appropriateness of tone, empathetic, or emotionally expressive. \textit{Intimacy} measures the quality of relationship users have with CAs, such as intimacy, social attraction, or similarity with each other.

Out of the list of publications that were evaluated, the perception of social connection with an agent is most commonly measured for conversational architecture elements related to presentation format, like adding response delays, or changing the pitch of speech.

Out of the list of publications that were evaluated, there is a good coverage on the effect of conversational architecture elements on the perception of interaction with an agent. Out of the three factors, engagement is the most frequently used measure to assess interaction quality, followed by satisfaction. Perceived accuracy of the agent is rarely used within literature, with only a few papers measuring this perception. Out of the elements in language content, measuring the perception of social connection with an agent is commonly linked to the investigations of the use of affective language.

[TODO] * Associations between conversational architecture elements and perceptions

%%
\subsubsection{Intimacy \nopunct}
%%

%\textbf{Content}

%\textit{Self-Disclosure}
%* High disclosure group had higher level of intimacy than the non disclosure group at the end 3 weeks (similar results around 1 week mark). \cite{lee2020hear}\cmt{[23]}

%
%\textbf{Style}

%\textit{Lexical Alignment}
%* Using the words already used by conversational partner did not result in higher quality of relationship. \cite{linnemann2018can}\cmt{[15]}

%
\textbf{Format}

\textit{Prosody}
* Empathetic tone: Intimacy is significantly higher in high empathy group. Similarity is marginally significant. \cite{kim2020can}\cmt{[24]}
* Default speech rate more intimate than the fast rate, more like a human, more natural and intimate. Fast-rate CA perceived as a mechanical being. \cite{choi2020nobody}\cmt{[54]}

\textit{Typos}
* Negatively impacted social attraction. \cite{westerman2019believe}\cmt{[9]}

\textit{Capitalization}
* Didn't impact social attraction \cite{westerman2019believe}\cmt{[9]}

%%
\subsubsection{Conversation Tone \nopunct}
%%
\hfill\\

\textbf{Content}

\textit{Affective language}
* CA with dynamic, sentiment-adaptive responses is perceived as more empathetic than a CA that provides static, neutral responses \cite{diederich2019emulating}\cmt{[25]}
* Use words with increased lexical emotional expressiveness by selection from NRC Valence, Arousal and Dominance (NRC-VAD) Lexicon - increased the perception of emotional expressiveness of the agent. \cite{zhu2022effects}\cmt{[26]}
* Agent using affective expressions are seen as more empathetic \cite{yang2017perceived}\cmt{[44]}
* Empathic chatbot - ask about users feelings and responses in an empathic, supportive manner. There is a statistically significant difference in empathy rating between the advice-only chatbot and the empathic chatbot. \cite{daher2020empathic}\cmt{[58]}

%
\textbf{Style}

\textit{Formality}
* No significant difference between casual and formal conversational styles for appropriateness of tone. \cite{cox2022does}\cmt{[27]}

%
\textbf{Format}

\textit{Prosody}
* AM voice - lower speech rate and lower pitch, is rated as more involved (involved, assertive, active, sincere). There is no difference in powerful (powerful, bold, forceful) \cite{dubiel2020persuasive}\cmt{[60]}

%%%%%
\subsection{Perception of Agent's Humanness}
%%%%%

* Define category and introduce high level measures included in this perception category
* Literature coverage
* Associations between conversational architecture elements and perceptions

%%
\subsubsection{Human-likeness \nopunct}
%%
\hfill\\

\textbf{Content}

\textit{Affective language}
* CA with dynamic, sentiment-adaptive responses is perceived as more human-like than a CA that provides static, neutral responses \cite{diederich2019emulating}\cmt{[25]}
* Use words with increased lexical emotional expressiveness by selection from NRC Valence, Arousal and Dominance (NRC-VAD) Lexicon - did not have an effect on human-likeness. \cite{zhu2022effects}\cmt{[26]}

%
\textbf{Style}

\textit{Formality}
* Agents using normal style seemed more humanlike \cite{ouchi2019should}\cmt{[59]}

\textit{Disfluency}
* No statistical significance in the perceived difference for perceived humanness overall. Noticed tendency for users to evaluate agent as more human-like in the filler condition. \cite{jeong2019exploring}\cmt{[10]}
* No significant effects of naturalness. \cite{pfeifer2009should}\cmt{[12]}

%
\textbf{Format}

\textit{Prosody}
* Expressive prosody did not have an effect on human-likeness. \cite{zhu2022effects}\cmt{[26]}

\textit{Typos}
* Made the agents seem less human. \cite{westerman2019believe}\cmt{[9]}

\textit{Capitalization}
* Didn't impact humanness \cite{westerman2019believe}\cmt{[9]}

\textit{Response Delay}
* Significant difference in perceived humanness \cite{gnewuch2018faster}\cmt{[19]}

%%
\subsubsection{Trustworthiness \nopunct}
%%
\hfill\\

\textbf{Content}

\textit{Affective Language}
* System with extroverted personality is less trustworthy \cite{andrews2012system}\cmt{[38]}

\textit{Self-Disclosure}
* High disclosure group reported more trust than the non disclosure group. Trust change over time for all groups were not significant. \cite{lee2020hear}\cmt{[23]}

%
\textbf{Style}

\textit{Lexical Alignment}
* No significant effect on trustworthiness (ability, benevolence and integrity) \cite{linnemann2018can}\cmt{[15]}
* Lexical alignment (using same words) no significant impact on trustworthiness. \cite{huiyang2022improving}\cmt{[17]}
* Matched users content (pronoun use, repetition, utterance length) and acoustic variables (speech rate, pitch, loudness) did not significant impact on trustworthiness \cite{hoegen2019end}\cmt{[31]}

\textit{Disfluency}
* No significant effects of trust. \cite{pfeifer2009should}\cmt{[12]}

\textit{Emoticons}
* No significant impact on trustworthiness. \cite{wilhelm2022keep}\cmt{[28]}

%
\textbf{Format}

\textit{Prosody}
* AM voice - lower speech rate and lower pitch, no significant difference on rating for truthful. \cite{dubiel2020persuasive}\cmt{[60]}

%%
\subsubsection{Personality Traits \nopunct}
%%
\hfill\\

\textbf{Content}

\textit{Affective language}
* Use words with increased lexical emotional expressiveness by selection from NRC Valence, Arousal and Dominance (NRC-VAD) Lexicon - did not have an effect on likability. \cite{zhu2022effects}\cmt{[26]}
* Significant difference in the variances of the responses for friendliness of the agent \cite{healey2013relating}\cmt{[39]}
* Participants rate the agent as lower in warmth when it could not feel / express its feelings (patiency).  \cite{lee2019s}\cmt{[55]}

\textit{Humour}
* Humorous agent was not rated as more likeable. But it is rated as having more of a sense of humour. \cite{ceha2021can}\cmt{[57]}

%
\textbf{Style}

\textit{Lexical Alignment}
* Using the words already used by conversational partner did not result in higher likeability. \cite{linnemann2018can}\cmt{[15]}
* Lexical alignment (using same words) no significant impact on likability. \cite{huiyang2022improving}\cmt{[17]}
* Lexical alignment - both words, and structural (grammatical transformations), movie showtimes. There is no significant difference in user opinions like friendly, polite or natural. \cite{spillner2021talk}\cmt{[18]}

\textit{Formality}
* Casual conversational style perceived warmer than formal style. \cite{cox2022does}\cmt{[27]}
* Agents using normal style (vs. polite / formal style) seemed more friendly, fun and kind \cite{ouchi2019should}\cmt{[59]}

\textit{Disfluency}
* No statistical significance in the perceived difference for likability rating overall. There is significant interaction effect between fillers and context of conversation (task vs. social). Users considered fillers as entertaining and fun in social conversations, but inappropriate in task oriented situations. \cite{jeong2019exploring}\cmt{[10]}
* No significant effects of likability. \cite{pfeifer2009should}\cmt{[12]}

%
\textbf{Format}

\textit{Prosody}
*  Emotional expressiveness did not have a significant impact on likeability. \cite{zhu2022effects}\cmt{[26]}

%-------------
\section{Discussions}

\subsection{Human-human vs. Human-machine}

* Impact of lexical alignment on people's perceived annoyance and likability differed in HHI (higher) and HCI (no impact). \cite{huiyang2022improving}\cmt{[17]}.

\subsection{Perception Measures}

Construct validity - humanness, likeability, empathy, trust, engagement

Used UX score to measure the perception of agent, which has questions like:
I think the CA's response is pleasing
I think the CA's response is trustworthy
I think the CA's response is natural
I think the CA's response can shorten the social distance between the CA and me.
I think the CA's response is acceptable.
Spans across different perceptions - cannot break it down for detailed analysis. \cite{ma2022ask}\cmt{[29]}

Overall interaction measure containing: 
Would you continue interacting with the agent?
How engaging is the agent?
How focused is the agent?
How emotional is the agent?
How bored are you with the agent?
Do you trust the agent?
How likeable was the agent?
Cannot break it down for specific perceptions give it is a composite measure. \cite{hoegen2019end}\cmt{[31]}

For discussions on mental well beings, agent using emojis is rated higher for attitude (emotional connection) . However, for agent with discussing physical well being, agent using emojis is rated as lower for attitude. 
Attitude has emotional connection, coherent - coherent is an ability perception, vs. emotional connection is a social connection perception. \cite{fadhil2018effect}\cmt{[52]}

\subsection{Modality}

Did not separate - because similar 
Affective language - may be a difference? significant for text, but not as much for voice?

\subsection{Confounding Factors}

* Different perceptions of intelligence and likability for social vs. task-based interactions. \cite{jeong2019exploring}\cmt{[10]}

* Participants with positive attitudes towards computers were significantly more likely to indicate that the usage of fillers by agents was a positive aspect of the conversation, compared to participants with neutral attitudes towards computers \cite{pfeifer2009should}\cmt{[12]}

* Anonymity is a key to encouraging people to self-disclose, worried about human reactions / judgements -> may not observe the effects in the study if user identity is known. \cite{lee2020hear}\cmt{[23]}

* Perception depend on the sensitivity of information. No differences in enjoyment, warmth, competence and appropriateness of tone for income level and credit score, but CA is seen as more competent and appropriate when discussing medical history. \cite{cox2022does}\cmt{[27]} - matching to the expectation of users is important.

* Participants who believed in robotic intelligence were more likely to find the chatbot enjoyable, warm, competent and appropriate \cite{cox2022does}\cmt{[27]}

* Participants with lower levels of privacy concerns found the chatbot more enjoyable, warm, competent and appropriate \cite{cox2022does}\cmt{[27]}

* Participants with high consideration conversational style rated the agent as more trustworthy when it matcehd their conversational style, compared to when it did not. \cite{hoegen2019end}\cmt{[31]}

\subsection{Integrated effect}

* Mental model

\subsection{Study Impact}

\textbf{Interview vs experiment}
* Humour - what's said vs. study results

\textbf{Observer study vs. interaction study}
* In observer study, participants attributed higher integrity (trustworthiness), response accuracy and likeability to the agent with lexical alignment, but this effect was not observed in the interaction study. Also, interaction study had lower cognitive demand but no effect in the observer study. \cite{linnemann2018can}\cmt{[15]}
* \cite{zhu2022effects}\cmt{[26]}
* \cite{cox2022does}\cmt{[27]}

\subsection{Ethical Considerations}

Self-disclosure encourage higher trust and intimacy, to disclose sensitive information. Who have access to this data? need to be aware of privacy / data sharing practices. \cite{lee2020hear}\cmt{[23]}

\section{Limitations}

Perception measures as mentioned in discussions - may not be comparing apples to apples

\section{Conclusions}

TBD

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

\end{document}
\endinput
%%
%% End of file `paper.tex'.

### 2023-01-31 paper.tex
completed first draft of the framework writeup

@@
 %%
-\subsubsection{Social Presence \nopunct}
-%%
-\hfill\\
-
-\textbf{Content}
-
-\textit{Affective language}
-* Participants using CA with dynamic, sentiment-adaptive responses reported a higher social presence compared to a CA that provides static, neutral responses \cite{diederich2019emulating}\cmt{[25]}
-* Psychological distance: Participants reported they identified with the agent more when the agent was described as being able to feel / express its feelings (patiency). \cite{lee2019s}\cmt{[55]}
-
-\textit{Humour}
-* Humourous agent was not rated as more social. \cite{ceha2021can}\cmt{[57]}
-
-%
-\textbf{Style}
-
-%
-\textbf{Format}
-
-\textit{Prosody}
-* Connectedness higher in the high empathy group. \cite{kim2020can}\cmt{[24]}
-
-\textit{Typos}
-* Negatively impacted electronic presence \cite{westerman2019believe}\cmt{[9]}
-
-\textit{Capitalization}
-* Didn't impact electronic presence \cite{westerman2019believe}\cmt{[9]}
-
-\textit{Response Delay}
-* Significant difference in perceived social presence \cite{gnewuch2018faster}\cmt{[19]}
-
-%%
 \subsubsection{Competence}
@@
 
-Out of the list of publications that were evaluated, the perception of social connection with an agent is most commonly measured for conversational architecture elements related to presentation format, like adding response delays, or changing the pitch of speech.
-
-Out of the list of publications that were evaluated, there is a good coverage on the effect of conversational architecture elements on the perception of interaction with an agent.
-Out of the three factors, engagement is the most frequently used measure to assess interaction quality, followed by satisfaction.
-Perceived accuracy of the agent is rarely used within literature, with only a few papers measuring this perception.
-Out of the elements in language content, measuring the perception of social connection with an agent is commonly linked to the investigations of the use of affective language.
-
-[TODO] * Associations between conversational architecture elements and perceptions
+Out of the list of publications that were evaluated, there is overall consensus that the use of affective language positive affects the perception of social connection with an agent.
+Conversational architecture elements related to the format of the conversation, like adding response delays, or changing the pitch of speech are commonly investigated for perception of social connection with an agent.
+There are only a few papers exploring the effect of language styles on the perceived social connection with an agent.
 
 %%
-\subsubsection{Intimacy \nopunct}
+\subsubsection{Social Presence}
 %%
+For conversational architecture elements related to language content, studies have shown the use of \textbf{affective language} increased the perception of social presence of an agent.
+In Diederich et al's study, participants conversing with a text-based agent using dynamic, sentiment-adaptive responses reported a higher social presence compared to a CA that provides static, neutral responses \cite{diederich2019emulating}\cmt{[25]}.
+In another study, participants felt closer to the agent psychologically when the CA expressed its feelings \cite{lee2019s}\cmt{[55]}.
+On the use of \textbf{humour}, Lee et al.
+did not find any significant difference in social presence between the humourous and non-humourous agent \cite{lee2019s}\cmt{[55]}.
+
+%\textbf{Content}
+
+%\textit{Affective language}
+%* Participants using CA with dynamic, sentiment-adaptive responses reported a higher social presence compared to a CA that provides static, neutral responses \cite{diederich2019emulating}\cmt{[25]}
+%* Psychological distance: Participants reported they identified with the agent more when the agent was described as being able to feel / express its feelings (patiency). \cite{lee2019s}\cmt{[55]}
+
+%\textit{Humour}
+%* Humourous agent was not rated as more social. \cite{ceha2021can}\cmt{[57]}
+
+For text-based conversational agents, including a \textbf{response delay} increased users' perception of social presence of the agent, with participants feeling a sense of human contact and sociability with the agent \cite{kim2020can}\cmt{[24]}.
+Westerman et al.
+\cite{westerman2019believe}\cmt{[9]} studied the presence of typos and capitalized words in a text-based agent's responses.
+They found the inclusion of \textbf{typos} negatively impacted the social distance and connection with an agent, while \textbf{capitalization} did not have any significant effects.
+On the effect \textbf{prosody} on a voice-based agent, using an affective tone of voice resulted in perceived higher social connectedness with the agent \cite{kim2020can}\cmt{[24]}.
+
+%\textbf{Format}
+
+%\textit{Prosody}
+%* Connectedness higher in the high empathy group. \cite{kim2020can}\cmt{[24]}
+
+%\textit{Typos}
+%* Negatively impacted electronic presence \cite{westerman2019believe}\cmt{[9]}
+
+%\textit{Capitalization}
+%* Didn't impact electronic presence \cite{westerman2019believe}\cmt{[9]}
+
+%\textit{Response Delay}
+%* Significant difference in perceived social presence \cite{gnewuch2018faster}\cmt{[19]}
+
+%%
+\subsubsection{Conversation Tone}
+%%
+
+The use of \textbf{affective language} has a significant affect on the perception of the conversation tone by the agent.
+Multiple studies have found that agents conversing with more affective words are seen as more emotionally expressive and empathetic \cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}.
+This effect has been observed across modalities in both text-based as well as voice-based conversational agents.
+
+%\textbf{Content}
+
+%\textit{Affective language}
+%* CA with dynamic, sentiment-adaptive responses is perceived as more empathetic than a CA that provides static, neutral responses \cite{diederich2019emulating}\cmt{[25]}
+%* Use words with increased lexical emotional expressiveness by selection from NRC Valence, Arousal and Dominance (NRC-VAD) Lexicon - increased the perception of emotional expressiveness of the agent.
+\cite{zhu2022effects}\cmt{[26]}
+%* Agent using affective expressions are seen as more empathetic \cite{yang2017perceived}\cmt{[44]}
+%* Empathic chatbot - ask about users feelings and responses in an empathic, supportive manner.
+There is a statistically significant difference in empathy rating between the advice-only chatbot and the empathic chatbot.
+\cite{daher2020empathic}\cmt{[58]}
+
+On the style of language used by the agent, \textbf{formality} did not seem to impact the conversation tone of agent as Cox et al.
+\cite{cox2022does}\cmt{[27]} did not find any significant difference between casual and formal conversational styles for appropriateness of tone.
+The speech format of \textbf{prosody} seem to have an impact on the conversation tone, as a CA speaking with a lower pitch and slower speech rate is rated as more persuasive compared to other voice settings \cite{dubiel2020persuasive}\cmt{[60]}.
+However, there was no significant difference in how powerful or bold the agent's tone was perceived across various prosody settings.
+
+%\textbf{Style}
+
+%\textit{Formality}
+%* No significant difference between casual and formal conversational styles for appropriateness of tone. \cite{cox2022does}\cmt{[27]}
+
+%
+%\textbf{Format}
+
+%\textit{Prosody}
+%* AM voice - lower speech rate and lower pitch, is rated as more persuasive and involved (involved, assertive, active, sincere).
+There is no difference in powerful (powerful, bold, forceful) \cite{dubiel2020persuasive}\cmt{[60]}
+
+%%
+\subsubsection{Intimacy}
+%%
+On the use of language content, a conversational agent that included \textbf{self-disclosure} when conversing with participants resulted in higher level of intimacy over time than CAs that did not self disclose \cite{lee2020hear}\cmt{[23]}.
+On the other hand, using the style of \textbf{lexical alignment} by using the words that were already used by the participant did not result in higher quality of relationship with the agent \cite{linnemann2018can}\cmt{[15]}.
 
@@
 
-%
-\textbf{Format}
+There are several studies investigating the effect of conversational format on intimacy with a CA.
+Specifically on voice \textbf{prosody}, using an affective tone of voice increased the perceived intimacy and similarity with an agent \cite{kim2020can}\cmt{[24]}.
+Comparing voice agents with different \textbf{speech rates}, users rated the default rate as more intimate than a faster rate of speech \cite{choi2020nobody}\cmt{[54]}, noting that the default rate is more human-like and natural.
+Westerman et al's study on different text formats of conversation \cite{westerman2019believe}\cmt{[9]} showed that \textbf{typos} negatively impacted the perceived social attraction of the agent, while \textbf{capitalization} did not have any impacts.
 
-\textit{Prosody}
-* Empathetic tone: Intimacy is significantly higher in high empathy group. Similarity is marginally significant. \cite{kim2020can}\cmt{[24]}
-* Default speech rate more intimate than the fast rate, more like a human, more natural and intimate. Fast-rate CA perceived as a mechanical being. \cite{choi2020nobody}\cmt{[54]}
+%\textbf{Format}
 
-\textit{Typos}
-* Negatively impacted social attraction. \cite{westerman2019believe}\cmt{[9]}
+%\textit{Prosody}
+%* Empathetic tone: Intimacy is significantly higher in high empathy group. Similarity is marginally significant. \cite{kim2020can}\cmt{[24]}
+%* Default speech rate more intimate than the fast rate, more like a human, more natural and intimate. Fast-rate CA perceived as a mechanical being. \cite{choi2020nobody}\cmt{[54]}
 
-\textit{Capitalization}
-* Didn't impact social attraction \cite{westerman2019believe}\cmt{[9]}
+%\textit{Typos}
+%* Negatively impacted social attraction. \cite{westerman2019believe}\cmt{[9]}
 
-%%
-\subsubsection{Conversation Tone \nopunct}
-%%
-\hfill\\
-
-\textbf{Content}
-
-\textit{Affective language}
-* CA with dynamic, sentiment-adaptive responses is perceived as more empathetic than a CA that provides static, neutral responses \cite{diederich2019emulating}\cmt{[25]}
-* Use words with increased lexical emotional expressiveness by selection from NRC Valence, Arousal and Dominance (NRC-VAD) Lexicon - increased the perception of emotional expressiveness of the agent.
-\cite{zhu2022effects}\cmt{[26]}
-* Agent using affective expressions are seen as more empathetic \cite{yang2017perceived}\cmt{[44]}
-* Empathic chatbot - ask about users feelings and responses in an empathic, supportive manner.
-There is a statistically significant difference in empathy rating between the advice-only chatbot and the empathic chatbot.
-\cite{daher2020empathic}\cmt{[58]}
-
-%
-\textbf{Style}
-
-\textit{Formality}
-* No significant difference between casual and formal conversational styles for appropriateness of tone. \cite{cox2022does}\cmt{[27]}
-
-%
-\textbf{Format}
-
-\textit{Prosody}
-* AM voice - lower speech rate and lower pitch, is rated as more involved (involved, assertive, active, sincere).
-There is no difference in powerful (powerful, bold, forceful) \cite{dubiel2020persuasive}\cmt{[60]}
+%\textit{Capitalization}
+%* Didn't impact social attraction \cite{westerman2019believe}\cmt{[9]}
 
@@
 
-* Define category and introduce high level measures included in this perception category
-* Literature coverage
-* Associations between conversational architecture elements and perceptions
+This section discusses user's perception of the agent's humanness aspects.
+Human-likeness, personality traits, and trustworthiness are the three variable used to evaluate this perception.
+\textit{Human-likeness} measures the agent's similarity to humans as well assessed naturalness of interaction.
+\textit{Personality traits} measures perceptions of the agent's characteristics such as likeability, warmth, and friendliness.
+\textit{Trustworthiness} measures if users feel they can trust an agent, and whether the agent is perceived of being truthful.
+
+Out of the list of publications that were evaluated, many papers exploring the impact of language content as well as language style have measurements related to the perception of an agent's humanness.
+There seems to be fewer studies looking into the effect of conversation format on the perception of agent's humanness, as our reivew only found two studies related to voice prosody.
+Out of reviewed conversational architecture elements, one consistent finding is that the style of being lexically aligned with user's utterance did not have any impact on the perception of agent's humanness.
 
 %%
-\subsubsection{Human-likeness \nopunct}
+\subsubsection{Human-likeness}
 %%
-\hfill\\
 
-\textbf{Content}
+On the use of \textbf{affective language}, one study found that CAs with dynamic, sentiment-adaptive responses is perceived as more human than a CA that provides static, neutral responses \cite{diederich2019emulating}\cmt{[25]}.
+Another study using more emotional expressive words in conversation did not find any significant impact on the perceived human-likeness of an agent \cite{zhu2022effects}\cmt{[26]}.
 
-\textit{Affective language}
-* CA with dynamic, sentiment-adaptive responses is perceived as more human-like than a CA that provides static, neutral responses \cite{diederich2019emulating}\cmt{[25]}
-* Use words with increased lexical emotional expressiveness by selection from NRC Valence, Arousal and Dominance (NRC-VAD) Lexicon - did not have an effect on human-likeness.
+%\textbf{Content}
+
+%\textit{Affective language}
+%* CA with dynamic, sentiment-adaptive responses is perceived as more human-like than a CA that provides static, neutral responses \cite{diederich2019emulating}\cmt{[25]}
+%* Use words with increased lexical emotional expressiveness by selection from NRC Valence, Arousal and Dominance (NRC-VAD) Lexicon - did not have an effect on human-likeness.
 \cite{zhu2022effects}\cmt{[26]}
 
-%
-\textbf{Style}
+Different language styles have different impacts on user perceptions.
+On language \textbf{formality}, agents using normal style was rated as more human-like compared to formal styles of conversation \cite{ouchi2019should}\cmt{[59]}.
+\textbf{Disfluencies} did not seem to have a significant impact on the perceived humanness or naturalness of an agent \cite{jeong2019exploring}\cmt{[10]}\cite{pfeifer2009should}\cmt{[12]}.
+However, one study noticed a non-significant but positive trend in user's evaluation of the agent using fillers as being more human-like \cite{jeong2019exploring}\cmt{[10]}.
 
-\textit{Formality}
-* Agents using normal style seemed more humanlike \cite{ouchi2019should}\cmt{[59]}
+%\textbf{Style}
 
-\textit{Disfluency}
-* No statistical significance in the perceived difference for perceived humanness overall.
+%\textit{Formality}
+%* Agents using normal style seemed more humanlike \cite{ouchi2019should}\cmt{[59]}
+
+%\textit{Disfluency}
+%* No statistical significance in the perceived difference for perceived humanness overall.
 Noticed tendency for users to evaluate agent as more human-like in the filler condition.
 \cite{jeong2019exploring}\cmt{[10]}
-* No significant effects of naturalness. \cite{pfeifer2009should}\cmt{[12]}
+%* No significant effects of naturalness. \cite{pfeifer2009should}\cmt{[12]}
 
-%
-\textbf{Format}
+On the impact of different conversation formats, Zhu et al.
+did not find a significant effect of \textbf{prosody} on the perception of humanness between agent using expressive vs.
+non-expressive voices.
+For text-based CAs, the use of \textbf{typos} made the agent seem less human, while the use of \textit{capitalization} did not have any impacts on the perception of humanness \cite{westerman2019believe}\cmt{[9]}.
+Lastly, adding a \textbf{response delay} to a CA has a significant positive effect in the perceived humanness of the agent \cite{gnewuch2018faster}\cmt{[19]}.
 
-\textit{Prosody}
-* Expressive prosody did not have an effect on human-likeness. \cite{zhu2022effects}\cmt{[26]}
+%\textbf{Format}
 
-\textit{Typos}
-* Made the agents seem less human. \cite{westerman2019believe}\cmt{[9]}
+%\textit{Prosody}
+%* Expressive prosody did not have an effect on human-likeness. \cite{zhu2022effects}\cmt{[26]}
 
-\textit{Capitalization}
-* Didn't impact humanness \cite{westerman2019believe}\cmt{[9]}
+%\textit{Typos}
+%* Made the agents seem less human. \cite{westerman2019believe}\cmt{[9]}
 
-\textit{Response Delay}
-* Significant difference in perceived humanness \cite{gnewuch2018faster}\cmt{[19]}
+%\textit{Capitalization}
+%* Didn't impact humanness \cite{westerman2019believe}\cmt{[9]}
+
+%\textit{Response Delay}
+%* Significant difference in perceived humanness \cite{gnewuch2018faster}\cmt{[19]}
 
 %%
-\subsubsection{Trustworthiness \nopunct}
+\subsubsection{Trustworthiness}
 %%
-\hfill\\
 
-\textbf{Content}
+For the use of language content, agents using more \textbf{affective language} is seen as less trustworthy, as users felt it was being overly familiar \cite{andrews2012system}\cmt{[38]}.
+On the other hand, users conversing with agents that used \textbf{self-disclosure} content reported more trust towards the agent compared to the non disclosure group \cite{lee2020hear}\cmt{[23]}.
 
-\textit{Affective Language}
-* System with extroverted personality is less trustworthy \cite{andrews2012system}\cmt{[38]}
+%\textbf{Content}
 
-\textit{Self-Disclosure}
-* High disclosure group reported more trust than the non disclosure group. Trust change over time for all groups were not significant. \cite{lee2020hear}\cmt{[23]}
+%\textit{Affective Language}
+%* System with extroverted personality is less trustworthy \cite{andrews2012system}\cmt{[38]}
 
-%
-\textbf{Style}
+%\textit{Self-Disclosure}
+%* High disclosure group reported more trust than the non disclosure group. Trust change over time for all groups were not significant. \cite{lee2020hear}\cmt{[23]}
 
-\textit{Lexical Alignment}
-* No significant effect on trustworthiness (ability, benevolence and integrity) \cite{linnemann2018can}\cmt{[15]}
-* Lexical alignment (using same words) no significant impact on trustworthiness. \cite{huiyang2022improving}\cmt{[17]}
-* Matched users content (pronoun use, repetition, utterance length) and acoustic variables (speech rate, pitch, loudness) did not significant impact on trustworthiness \cite{hoegen2019end}\cmt{[31]}
+None of the studies included in this review has found any significant impact of language style, \textbf{lexical alignment} \cite{hoegen2019end}\cmt{[31]}\cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}, \textbf{disfluency} \cite{pfeifer2009should}\cmt{[12]}, and \textbf{emoticons} \cite{wilhelm2022keep}\cmt{[28]} on the perceived trustworthiness of CAs.
+Similarly for conversational format, there is not significant difference on the rating for truthfulness of the agent across different voice \textbf{prosody} settings \cite{dubiel2020persuasive}\cmt{[60]}.
 
-\textit{Disfluency}
-* No significant effects of trust. \cite{pfeifer2009should}\cmt{[12]}
+%\textbf{Style}
 
-\textit{Emoticons}
-* No significant impact on trustworthiness. \cite{wilhelm2022keep}\cmt{[28]}
+%\textit{Lexical Alignment}
+%* No significant effect on trustworthiness (ability, benevolence and integrity) \cite{linnemann2018can}\cmt{[15]}
+%* Lexical alignment (using same words) no significant impact on trustworthiness. \cite{huiyang2022improving}\cmt{[17]}
+%* Matched users content (pronoun use, repetition, utterance length) and acoustic variables (speech rate, pitch, loudness) did not significant impact on trustworthiness \cite{hoegen2019end}\cmt{[31]}
 
-%
-\textbf{Format}
+%\textit{Disfluency}
+%* No significant effects of trust. \cite{pfeifer2009should}\cmt{[12]}
 
-\textit{Prosody}
-* AM voice - lower speech rate and lower pitch, no significant difference on rating for truthful. \cite{dubiel2020persuasive}\cmt{[60]}
+%\textit{Emoticons}
+%* No significant impact on trustworthiness. \cite{wilhelm2022keep}\cmt{[28]}
+
+%\textbf{Format}
+
+%\textit{Prosody}
+%* AM voice - lower speech rate and lower pitch, no significant difference on rating for truthful. \cite{dubiel2020persuasive}\cmt{[60]}
 
@@
 %%
-\hfill\\
 
-\textbf{Content}
+There are significant difference found in the effect of language content on the perception of agent's personality traits.
+Conversational agents using emotionally expressive words are rated as more likable \cite{zhu2022effects}\cmt{[26]} and warm \cite{lee2019s}\cmt{[55]}.
+In Healey et al's study \cite{healey2013relating}\cmt{[39]}, there is a significant difference in the variances of the responses for friendliness of the agent between the agent using encouraging words compared to neutral utterances.
+As with the use of \textbf{humour}, participants rated the humorous agent as having a sense of humor, but it was not rated as more likable \cite{ceha2021can}\cmt{[57]}.
 
-\textit{Affective language}
-* Use words with increased lexical emotional expressiveness by selection from NRC Valence, Arousal and Dominance (NRC-VAD) Lexicon - did not have an effect on likability.
+%\textbf{Content}
+
+%\textit{Affective language}
+%* Use words with increased lexical emotional expressiveness by selection from NRC Valence, Arousal and Dominance (NRC-VAD) Lexicon - did not have an effect on likability.
 \cite{zhu2022effects}\cmt{[26]}
-* Significant difference in the variances of the responses for friendliness of the agent \cite{healey2013relating}\cmt{[39]}
-* Participants rate the agent as lower in warmth when it could not feel / express its feelings (patiency).  \cite{lee2019s}\cmt{[55]}
+%* Significant difference in the variances of the responses for friendliness of the agent \cite{healey2013relating}\cmt{[39]}
+%* Participants rate the agent as lower in warmth when it could not feel / express its feelings (patiency).  \cite{lee2019s}\cmt{[55]}
 
-\textit{Humour}
-* Humorous agent was not rated as more likeable. But it is rated as having more of a sense of humour. \cite{ceha2021can}\cmt{[57]}
+%\textit{Humour}
+%* Humorous agent was not rated as more likeable. But it is rated as having more of a sense of humour. \cite{ceha2021can}\cmt{[57]}
 
 %
-\textbf{Style}
 
-\textit{Lexical Alignment}
-* Using the words already used by conversational partner did not result in higher likeability. \cite{linnemann2018can}\cmt{[15]}
-* Lexical alignment (using same words) no significant impact on likability. \cite{huiyang2022improving}\cmt{[17]}
-* Lexical alignment - both words, and structural (grammatical transformations), movie showtimes.
+On the impact of language style, various studies on \textbf{lexical alignment} showed that there is no significant impact on the perception of the personality traits related to likability \cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}, friendliness \cite{spillner2021talk}\cmt{[18]}, or politeness \cite{spillner2021talk}\cmt{[18]}.
+Studies on the \textbf{formality} of language has demonstrated that casual conversational style is perceived as warmer than formal style \cite{cox2022does}\cmt{[27]}.
+Also agents using a normal style as compared to a formal style is perceived as more friendly, fun, and kind \cite{ouchi2019should}\cmt{[59]}.
+As for the use of \textbf{disfluency}, there was no statistical significance found in the perceived likability rating \cite{jeong2019exploring}\cmt{[10]}\cite{pfeifer2009should}\cmt{[12]}.
+Jeong et al.
+\cite{jeong2019exploring} found a significant interaction effect between disfluency (using fillers) and the context of the conversation (task vs.
+social), as users considered agents using fillers as entertaining and fun in social conversations, but inappropriate in task oriented situations.
+
+%\textbf{Style}
+
+%\textit{Lexical Alignment}
+%* Using the words already used by conversational partner did not result in higher likeability. \cite{linnemann2018can}\cmt{[15]}
+%* Lexical alignment (using same words) no significant impact on likability. \cite{huiyang2022improving}\cmt{[17]}
+%* Lexical alignment - both words, and structural (grammatical transformations), movie showtimes.
 There is no significant difference in user opinions like friendly, polite or natural.
@@
 
-\textit{Formality}
-* Casual conversational style perceived warmer than formal style. \cite{cox2022does}\cmt{[27]}
-* Agents using normal style (vs. polite / formal style) seemed more friendly, fun and kind \cite{ouchi2019should}\cmt{[59]}
+%\textit{Formality}
+%* Casual conversational style perceived warmer than formal style. \cite{cox2022does}\cmt{[27]}
+%* Agents using normal style (vs. polite / formal style) seemed more friendly, fun and kind \cite{ouchi2019should}\cmt{[59]}
 
-\textit{Disfluency}
-* No statistical significance in the perceived difference for likability rating overall.
+%\textit{Disfluency}
+%* No statistical significance in the perceived difference for likability rating overall.
 There is significant interaction effect between fillers and context of conversation (task vs.
@@
 \cite{jeong2019exploring}\cmt{[10]}
-* No significant effects of likability. \cite{pfeifer2009should}\cmt{[12]}
+%* No significant effects of likability. \cite{pfeifer2009should}\cmt{[12]}
 
-%
-\textbf{Format}
+In the list of reviewed papers, there was only one study measuring the perceived trustworthiness of an agent based on different conversational format of \textbf{prosody}.
+Dubiel et al.
+found that an agent using slower speech rate is perceived as more trustworthy as compared to other voice prosody settings \cite{dubiel2020persuasive}\cmt{[60]}.
 
-\textit{Prosody}
-*  Emotional expressiveness did not have a significant impact on likeability. \cite{zhu2022effects}\cmt{[26]}
+%\textbf{Format}
+
+%\textit{Prosody}
+%*  Emotional expressiveness did not have a significant impact on truthfulness. \cite{dubiel2020persuasive}\cmt{[60]}
 

### 2023-02-01 paper.tex
before adding in papers on observation studies

@@
 
+\cite{finch2020towards} Towards unified dialogue system evaluation: A comprehensive analysis of current evaluation protocols
+
 Synthesis on conversational architecture
@@
   \item Voice-based or text-based disembodied conversational agents
-  \item Interaction study on the impact of designed conversational architecture elements on the perception of agents.
-  \item Users must interact with conversational agent in the study. Observer studies are excluded from the corpus
+  \item Experiment study on the impact of designed conversational architecture elements on the perception of agents.
   \item Measures the perceptions of the interaction or perceptions of the agent as part of the study
@@
 This section discusses user's perception of their interaction with a conversational agent.
-Engagement, accuracy, and satisfaction are the three variables used to evaluate how people perceive interactions with CAs.
+\textbf{\textit{Engagement, accuracy, and satisfaction are the three variables used to evaluate how people perceive interactions with CAs}}.
 \textit{Engagement} measures user's attitude towards the task they are achieving through working with the agent, including how easy it is to use the system and its perceived usefulness, convenience and helpfulness for the user.
@@
 %%
-For the elements in the language content category of conversational architecture, the use \textbf{self-disclosure} by agent had a positive effect on engagement, as the participants using the chatbot with small talk and self disclosure reported higher enjoyment after 3 weeks of daily interaction.
-\cite{lee2020hear}\cmt{[23]}.
+For the elements in the language content category of conversational architecture, the use \textbf{self-disclosure} by agent had a positive effect on engagement, as the participants using the chatbot with small talk and self disclosure reported higher enjoyment after 3 weeks of daily interaction \cite{lee2020hear}\cmt{[23]}.
 There are mixed results on the effect of \textbf{affective language} on engagement.
@@
 %%
-\subsubsection{Personality Traits \nopunct}
+\subsubsection{Personality Traits}
 %%
@@
 
-\subsection{Human-human vs. Human-machine}
+\subsection{Inconsistencies in Perception Measures}
 
-* Impact of lexical alignment on people's perceived annoyance and likability differed in HHI (higher) and HCI (no impact). \cite{huiyang2022improving}\cmt{[17]}.
+A major roadblock in synthesizing the findings from existing academic research is the diversity and inconsistency of measurements towards the anthropomorphized perception of agents.
+It is difficult to assess whether perception measures should be compared with each other.
+Also, some measures combined anthropomorphized perceptions into a composite score, which makes it impossible to separate the perceptions into more granular details.
 
-\subsection{Perception Measures}
+Based on the literature reviewed in this paper, we noticed that similar perception concepts were \textbf{measured in different ways} through different surveys.
+For example, there are several approaches to measure the perceived \textit{human-likeness} of an agent.
+A commonly used survey is adapted from the Godspeed questionnaire \cite{bartneck2009measurement}, which measures human-likeness based on user's impression of the agent as fake / natural, machinelike / humanlike, unconscious / conscious, and artificial / lifelike (used by \cite{hoegen2019end}\cmt{[31]}, \cite{jeong2019exploring}\cmt{[10]} and \cite{ouchi2019should}\cmt{[59]}).
+Another way to measure human-likeness is adapted from Holtgraves et al.'s \cite{holtgraves2007perceiving} questionnaire, which asks users to assess the agent's perceived human-likeness, skillfulness, thoughtfulness, politeness, responsiveness and engagement (used by \cite{diederich2019emulating}\cmt{[25]} and  \cite{gnewuch2018faster}\cmt{[19]}).
+One study \cite{westerman2019believe}\cmt{[9]} used the Ascend of Man pictorial scale \cite{kteily2015ascent} as the measure of perceived human-likeness.
+It is unclear whether these different measures of perceived human-likeness are similar enough to be compared with each other.
 
-Construct validity - humanness, likeability, empathy, trust, engagement
+ In addition to different methods used to measure for the same perception, our detailed analysis revealed that the measures using the same label may have \textbf{drastically different meanings}.
+In Diedrech et al.'s study \cite{diederich2019emulating}\cmt{[25]}, \textit{empathy} measure is adapted from \cite{yan2013role} assessing whether the CA gives users individual or personal attention.
+In Daher et al.'s study \cite{daher2020empathic}\cmt{[58]}, they also measure the perception of empathy, but it is using the RoPE Scale \cite{charrier2019rope} with questions like "the robot cares about my feelings" or "the robot comforts me when I am upset." These two different measures of empathy seem to have different underlying meanings, one assessing the personalization aspect of CAs, while the other is assessing the emotional aspect of CAs.
+Another example is the measurement of \textit{trustworthiness}, with some constructs measuring the level of sensitive information user's are willing to share \cite{dinev2006privacy}, and some measuring the honesty and truthfulness of an agent \cite{lee2017enhancing}.
 
-Used UX score to measure the perception of agent, which has questions like:
-I think the CA's response is pleasing
-I think the CA's response is trustworthy
-I think the CA's response is natural
-I think the CA's response can shorten the social distance between the CA and me.
-I think the CA's response is acceptable.
-Spans across different perceptions - cannot break it down for detailed analysis. \cite{ma2022ask}\cmt{[29]}
+Lastly, there are \textbf{composite measures} of anthropomorphized perception across different categories, making it difficult to break down perceptions into granular details for analysis.
+One such example is Ma et al's study \cite{ma2022ask}\cmt{[29]} on different approaches for CAs to reply to users' uncertain queries.
+UX score is used to measure the perception of an agent, which asks whether the user thinks the CA's response is pleasing / trustworthy / natural / acceptable / shorten the distance between CA and user.
+While the study has found significant impact of the use of formal language on UX score, it is not possible to breakdown the measure into perceptions of interaction (pleasing, acceptable), social connection (shorten the distance between CA and user), and humanness (natural, trustworthy).
+Similar for Hoegen et al.'s study \cite{hoegen2019end}\cmt{[31]} on the impact of conversational style matching, it is not possible to separate the overall interaction score into different perceptions as the composite measure contains questions measuring different categories of perceptions like interaction (engaging) and humanness (trust, likable).
 
-Overall interaction measure containing: 
-Would you continue interacting with the agent?
-How engaging is the agent?
-How focused is the agent?
-How emotional is the agent?
-How bored are you with the agent?
-Do you trust the agent?
-How likeable was the agent?
-Cannot break it down for specific perceptions give it is a composite measure. \cite{hoegen2019end}\cmt{[31]}
+In recent years there has been some effort towards unifying the evaluation of conversational agents, such as the work by Finch et al.
+\cite{finch2020towards} presenting a comprehensive analysis of current evaluation protocols.
+More work is needed to categorize and consolidate perception measures to make them consistent and comparable across various studies.
 
-For discussions on mental well beings, agent using emojis is rated higher for attitude (emotional connection) .
+%For discussions on mental well beings, agent using emojis is rated higher for attitude (emotional connection) .
 However, for agent with discussing physical well being, agent using emojis is rated as lower for attitude.
-Attitude has emotional connection, coherent - coherent is an ability perception, vs. emotional connection is a social connection perception. \cite{fadhil2018effect}\cmt{[52]}
+%Attitude has emotional connection, coherent - coherent is an ability perception, vs. emotional connection is a social connection perception. \cite{fadhil2018effect}\cmt{[52]}
 
-\subsection{Modality}
+\subsection{Other Influencing Factors}
 
-Did not separate - because similar 
-Affective language - may be a difference? significant for text, but not as much for voice?
+While the discussion in the Framework section above focuses on the overall effect of conversational architecture elements on anthropomorphized perceptions,  there are other nuanced influencing factors that impact user perceptions of agents.
 
-\subsection{Confounding Factors}
+Depending on the \textbf{type of conversation} user is having with agents, it may lead to differences in perceptions for similar conversational architecture elements.
+Cox et al.
+\cite{cox2022does}\cmt{[27]} found that the perceived competence and appropriateness of tone of different language formality styles depend on the sensitivity of information discussed in the conversation.
+In this particular study, a formal language style is preferred in medical history discussions as it is matching to the expectation of users, but there is no difference in perception between formal and casual styles when discussing income level and credit scores.
+In Jeong et al's study \cite{jeong2019exploring}\cmt{[10]}, users found the agent using fillers less intelligent and likable in a task-oriented conversation, but found the same agent using fillers as slight more intelligent and likable in a social-oriented conversation.
+Another factor that could impact perceptions is the \textbf{anonymity} of conversation.
+Based on user feedback, Lee et al.
+\cite{lee2020hear}\cmt{[23]} found that the anonymity of a conversational agent is a driving factor encouraging people to self disclose without having to worried about judgements from the CA.
+The perception of the agent may be different if the user's identity is not anonymous.
 
-* Different perceptions of intelligence and likability for social vs. task-based interactions. \cite{jeong2019exploring}\cmt{[10]}
+Other than the type of conversation, \textbf{user's characteristics} can also be influencing factors on their perception of agents.
+For example, the effect of matching user's conversational style on perception of agents depend on user's own conversational style, as participants with high consideration conversational style rated the lexically aligned agent as more trustworthy \cite{hoegen2019end}\cmt{[31]}.
+In the study by Cox et al.
+\cite{cox2022does}\cmt{[27]}, participants with lower levels of privacy concerns as well as those who believe in robotic intelligence found the chatbot more enjoyable, warm, competent and appropriate.
+Similarly, participants with positive attitudes towards computers were significantly more likely to indicate that the usage of fillers by agents was a positive aspect of the conversation, compared to participants with neutral attitudes towards computers \cite{pfeifer2009should}\cmt{[12]}.
+Lastly, user's prior experience with conversational agents could impact perception of agents.
+Experienced users perceived the agent with a response delay as lower in social presence compared to the one without delay, as it is seen as inefficient to wait for the CA to respond.
+However, novice users perceived higher social presence conversing with the CAs using response delays as it is more similar to conversations with human partners \cite{gnewuch2018faster}\cmt{[19]}.
 
-* Participants with positive attitudes towards computers were significantly more likely to indicate that the usage of fillers by agents was a positive aspect of the conversation, compared to participants with neutral attitudes towards computers \cite{pfeifer2009should}\cmt{[12]}
-
-* Anonymity is a key to encouraging people to self-disclose, worried about human reactions / judgements -> may not observe the effects in the study if user identity is known.
-\cite{lee2020hear}\cmt{[23]}
-
-* Perception depend on the sensitivity of information.
-No differences in enjoyment, warmth, competence and appropriateness of tone for income level and credit score, but CA is seen as more competent and appropriate when discussing medical history.
-\cite{cox2022does}\cmt{[27]} - matching to the expectation of users is important.
-
-* Participants who believed in robotic intelligence were more likely to find the chatbot enjoyable, warm, competent and appropriate \cite{cox2022does}\cmt{[27]}
-
-* Participants with lower levels of privacy concerns found the chatbot more enjoyable, warm, competent and appropriate \cite{cox2022does}\cmt{[27]}
-
-* Participants with high consideration conversational style rated the agent as more trustworthy when it matcehd their conversational style, compared to when it did not. \cite{hoegen2019end}\cmt{[31]}
-
-\subsection{Integrated effect}
-
-* Mental model
-
-\subsection{Study Impact}
+\subsection{Study Design}
 
@@
 
+\subsection{Modality}
+
+TBD 
+Did not separate - because similar 
+Affective language - may be a difference? significant for text, but not as much for voice?
+
+\subsection{Gaps}
+
+* Combined effects - integrated mental model
+* Lack of investigations - name a few areas
+
+\subsection{Human-human vs. Human-machine}
+
+* Impact of lexical alignment on people's perceived annoyance and likability differed in HHI (higher) and HCI (no impact). \cite{huiyang2022improving}\cmt{[17]}.
+
 \subsection{Ethical Considerations}
@@
 Self-disclosure encourage higher trust and intimacy, to disclose sensitive information. Who have access to this data? need to be aware of privacy / data sharing practices. \cite{lee2020hear}\cmt{[23]}
-
-\section{Limitations}
-
-Perception measures as mentioned in discussions - may not be comparing apples to apples
 

### 2023-02-02 paper.tex
added notes for more papers (up to [64])

@@
 
-%%\textbf{Content}
-
-%\textit{Affective language}
-%* Use words with increased lexical emotional expressiveness by selection from NRC Valence, Arousal and Dominance (NRC-VAD) Lexicon - did not have an effect on engagement. 
-%* System with extroverted personality is more irritating, did not like computer using the level of familiar with them and prefer a more reserved system. \cite{andrews2012system}\cmt{[38]}
-%* Encouraging personality is rated as easier to use \cite{healey2013relating}\cmt{[39]}
-
-%\textit{Self-Disclosure}
-%* High disclosure group had higher enjoyment than the non disclosure group at the end 3 weeks (similar results %around 1 week mark).
-
-%\textit{Humour}
-%* Humour did not enhance enjoyment measurement. but qualitative feedback said that humour made the interaction more engaging and immersive
-
 For the elements in the language style category of conversational architecture, mimicking users' utterances through \textbf{lexical alignment} yielded positive results.
@@
 In Spillner et al's study \cite{spillner2021talk}\cmt{[18]}, both conditions of aligning words as well as aligning words and grammatical structure to user utterances resulted in higher perceived user engagement from participants.
-
-%
-%\textbf{Style}
-
-%\textit{Lexical Alignment}
-%* Using the words already used by conversational partner resulted in lower perceived cognitive demand, but did not impact perception of habitability (ease of use). \cite{linnemann2018can}\cmt{[15]}
-%* Lexical alignment (using same words) resulted in lower cognitive demand, but no impact on annoyance. \cite{huiyang2022improving}\cmt{[17]}
-%* Lexical alignment - both words, and structural (grammatical transformations), movie showtimes.
-There is a decreased workload for substitution and transformation alignment conditions.
-Also, there is a significant difference in user engagement.
-\cite{spillner2021talk}\cmt{[18]}
-
-%\textit{Formality}
-%* No significant difference between casual and formal conversational styles for enjoyment. \cite{cox2022does}\cmt{[27]}
-
-%\textit{Emoticons}
-%* Positive but non-significant trend on helpfulness \cite{wilhelm2022keep}\cmt{[28]}
-%* For discussions on mental well beings, agent using emojis is rated higher for enjoyment.
-However, for agent with discussing physical well being, agent using emojis is rated as lower for enjoyment.
-\cite{fadhil2018effect}\cmt{[52]}
 
@@
 
-%
-%\textbf{Format}
+Content: Humour
+* No overall significant difference between conventional method vs.
+agent using humour for enjoyment.
+Specifically, men enjoyed the agent's jokes more than women.
+\cite{miyamoto2017improving}\cmt{[46]}.
 
-%\textit{Prosody}
-%* More empathetic voice: Enjoyment is marginally significant; high empathy group felt higher ease of use.
-People expect a high level of agent's social behavior that is matched with their emotional states.
-\cite{kim2020can}\cmt{[24]}
-%* No impact of emotional expressiveness on engagement \cite{zhu2022effects}\cmt{[26]}
-%* convenience is higher for default rate \cite{choi2020nobody}\cmt{[54]}
-
-%\textit{Typos}
-%* Negatively impacted task attraction. \cite{westerman2019believe}\cmt{[9]}
-
-%\textit{Capitalization}
-%* Didn't impact task attraction \cite{westerman2019believe}\cmt{[9]}
+Style: Language Formality
+* Users spent more time with the Shakespearean chatbot version with more non-task related user inputs. Enjoyment was measured but no report \cite{elsholz2019exploring}\cmt{[61]}
 
@@
 Dubiel et al.'s study \cite{dubiel2020persuasive}\cmt{[60]} on \textbf{prosody} did not find any significant differences on the rating for accuracy across agents with different speech rates and pitch.
-
-%
-%\textbf{Style}
-
-%\textit{Lexical Alignment}
-%* Using the words already used by conversational partner did not result in higher response accuracy. \cite{linnemann2018can}\cmt{[15]}
-%* Lexical alignment (using same words) resulted in higher perceived response accuracy. \cite{huiyang2022improving}\cmt{[17]}
-
-%
-%\textbf{Format}
-
-%\textit{Prosody}
-%* AM voice - lower speech rate and lower pitch, no significant difference on rating for accuracy. \cite{dubiel2020persuasive}\cmt{[60]}
 
@@
 
-%\textbf{Content}
-
-%\textit{Affective language}
-%* Participants using CA with dynamic, sentiment-adaptive responses reported a higher service encounter satisfaction compared to a CA that provides static, neutral responses \cite{diederich2019emulating}\cmt{[25]}
-%* Did not impact user satisfaction between the affective expression or not agent. \cite{yang2017perceived}\cmt{[44]}
-
-%
-%\textbf{Style}
-
-%\textit{Disfluency}
-%* No significant effects of satisfaction. \cite{pfeifer2009should}\cmt{[12]}
-
-%\textit{Emoticons}
-%* Positive but non-significant trend on user satisfaction \cite{wilhelm2022keep}\cmt{[28]}
-
 Studies have found that presentation formats have significant effects on user satisfaction.
@@
 
-%
-%\textbf{Format}
+\textbf{Style: Language Formality}
+* Modern language had higher usability score compared to Shakespearean language \cite{elsholz2019exploring}\cmt{[61]}
+* There is no significant effect on customer satisfaction of the CA between low-status and high-status languages. \cite{habler2019effects}\cmt{[63]}
 
-%\textit{Prosody}
-%* Overall satisfaction as well as speech rate satisfaction is higher for the default rate compare to fast rate.
-Want everyone to understand.
-Hard to understand the faster rate as communicating with CA over a distance (as oppose to mobile phone.
-\cite{choi2020nobody}\cmt{[54]}
-
-%\textit{Response Delay}
-%* Significant difference in overall user satisfaction, the timing "felt right" and comparing response to human-human communication. \cite{gnewuch2018faster}\cmt{[19]}
+\textbf{Format: Prosody}
+* There is no significant effect on customer satisfaction of the CA between male-gendered and female-gendered voices. \cite{habler2019effects}\cmt{[63]}
 
@@
 
-%
-%\textbf{Style}
-
-%\textit{Lexical Alignment}
-%* Lexical alignment - both words, and structural (grammatical transformations), movie showtimes. There is no significant difference in domain knowledge. \cite{spillner2021talk}\cmt{[18]}
-
-%\textit{Disfluency}
-%* Participants perceived the agent using fillers like "um" "uh" to be less intelligent.
-Especially in taks-oriented situations.
-In social situations, perceive intelligence is slightly increased.
-\cite{jeong2019exploring}\cmt{[10]}
-%* No significant effects of knowledgeable. \cite{pfeifer2009should}\cmt{[12]}
-
 On the impact of presentation format, Dubiel et al's study on \textbf{prosody} using different speech rates and pitches did not yield any significant differences on the agent rating for knowledgeable.
-
-%
-%\textbf{Format}
-
-%\textit{Prosody}
-%* AM voice - lower speech rate and lower pitch, no significant difference on rating for knowledgeable \cite{dubiel2020persuasive}\cmt{[60]}
 
@@
 
-%\textbf{Content}
+\textbf{Style: Language Formality}
+*  Low-status language resulted in higher achieved performance ratings \cite{habler2019effects}\cmt{[63]}
 
-%\textit{Affective Language}
-%* Participants rate the agent as lower in competence when it could not feel / express its feelings (patiency). \cite{lee2019s}\cmt{[55]}
+\textbf{Format: Prosody}
+* There is no significant effect on perceived performance of the CA between male-gendered and female-gendered voices. \cite{habler2019effects}\cmt{[63]}
 
-%
-%\textbf{Style}
-
-%\textit{Formality}
-%* No significant difference between casual and formal conversational styles for competence. \cite{cox2022does}\cmt{[27]}
+\textbf{Format: Proactivity}
+* Certain proactive styles like notification strategy (conservatively proactive, letting participants know that the agent has found a solution) was evaluated as significantly higher perceived competence compared to the non-strategy.
+\cite{kraus2020effects}\cmt{[64]}
 
@@
 
-%\textbf{Content}
-
-%\textit{Affective language}
-%* Participants using CA with dynamic, sentiment-adaptive responses reported a higher social presence compared to a CA that provides static, neutral responses \cite{diederich2019emulating}\cmt{[25]}
-%* Psychological distance: Participants reported they identified with the agent more when the agent was described as being able to feel / express its feelings (patiency). \cite{lee2019s}\cmt{[55]}
-
-%\textit{Humour}
-%* Humourous agent was not rated as more social. \cite{ceha2021can}\cmt{[57]}
-
 For text-based conversational agents, including a \textbf{response delay} increased users' perception of social presence of the agent, with participants feeling a sense of human contact and sociability with the agent \cite{kim2020can}\cmt{[24]}.
@@
 
-%\textbf{Format}
+\textbf{Content: Affective Language (Voice)}
+* Model aiming to elicit position emotions from users received higher emotional connection \cite{lubis2019positive}\cmt{[43]}
 
-%\textit{Prosody}
-%* Connectedness higher in the high empathy group. \cite{kim2020can}\cmt{[24]}
+\textbf{Format: Response Delay}
+* Delayed response is associated with higher social presence \cite{gnewuch2022opposing}\cmt{[20]}
 
-%\textit{Typos}
-%* Negatively impacted electronic presence \cite{westerman2019believe}\cmt{[9]}
-
-%\textit{Capitalization}
-%* Didn't impact electronic presence \cite{westerman2019believe}\cmt{[9]}
-
-%\textit{Response Delay}
-%* Significant difference in perceived social presence \cite{gnewuch2018faster}\cmt{[19]}
+\textbf{Content: Affective language and Style: Disfluency}
+* Rated higher that agent listened openly to participants' emotions, as that agent can feel waht the user is feeling. \cite{hu2021enhancing}\cmt{[56]}
 
@@
 
-%\textbf{Content}
-
-%\textit{Affective language}
-%* CA with dynamic, sentiment-adaptive responses is perceived as more empathetic than a CA that provides static, neutral responses \cite{diederich2019emulating}\cmt{[25]}
-%* Use words with increased lexical emotional expressiveness by selection from NRC Valence, Arousal and Dominance (NRC-VAD) Lexicon - increased the perception of emotional expressiveness of the agent.
-\cite{zhu2022effects}\cmt{[26]}
-%* Agent using affective expressions are seen as more empathetic \cite{yang2017perceived}\cmt{[44]}
-%* Empathic chatbot - ask about users feelings and responses in an empathic, supportive manner.
-There is a statistically significant difference in empathy rating between the advice-only chatbot and the empathic chatbot.
-\cite{daher2020empathic}\cmt{[58]}
-
 On the style of language used by the agent, \textbf{formality} did not seem to impact the conversation tone of agent as Cox et al.
@@
 
-%\textbf{Style}
-
-%\textit{Formality}
-%* No significant difference between casual and formal conversational styles for appropriateness of tone. \cite{cox2022does}\cmt{[27]}
-
-%
-%\textbf{Format}
-
-%\textit{Prosody}
-%* AM voice - lower speech rate and lower pitch, is rated as more persuasive and involved (involved, assertive, active, sincere).
-There is no difference in powerful (powerful, bold, forceful) \cite{dubiel2020persuasive}\cmt{[60]}
+\textbf{Content: Affective language and Style: Disfluency}
+Respond with empathy to the user. \cite{hu2021enhancing}\cmt{[56]}
 
@@
 
-%\textbf{Content}
-
-%\textit{Self-Disclosure}
-%* High disclosure group had higher level of intimacy than the non disclosure group at the end 3 weeks (similar results around 1 week mark). \cite{lee2020hear}\cmt{[23]}
-
-%
-%\textbf{Style}
-
-%\textit{Lexical Alignment}
-%* Using the words already used by conversational partner did not result in higher quality of relationship. \cite{linnemann2018can}\cmt{[15]}
-
 There are several studies investigating the effect of conversational format on intimacy with a CA.
@@
 Westerman et al's study on different text formats of conversation \cite{westerman2019believe}\cmt{[9]} showed that \textbf{typos} negatively impacted the perceived social attraction of the agent, while \textbf{capitalization} did not have any impacts.
-
-%\textbf{Format}
-
-%\textit{Prosody}
-%* Empathetic tone: Intimacy is significantly higher in high empathy group. Similarity is marginally significant. \cite{kim2020can}\cmt{[24]}
-%* Default speech rate more intimate than the fast rate, more like a human, more natural and intimate. Fast-rate CA perceived as a mechanical being. \cite{choi2020nobody}\cmt{[54]}
-
-%\textit{Typos}
-%* Negatively impacted social attraction. \cite{westerman2019believe}\cmt{[9]}
-
-%\textit{Capitalization}
-%* Didn't impact social attraction \cite{westerman2019believe}\cmt{[9]}
 
@@
 
-%\textbf{Content}
-
-%\textit{Affective language}
-%* CA with dynamic, sentiment-adaptive responses is perceived as more human-like than a CA that provides static, neutral responses \cite{diederich2019emulating}\cmt{[25]}
-%* Use words with increased lexical emotional expressiveness by selection from NRC Valence, Arousal and Dominance (NRC-VAD) Lexicon - did not have an effect on human-likeness.
-\cite{zhu2022effects}\cmt{[26]}
-
 Different language styles have different impacts on user perceptions.
@@
 However, one study noticed a non-significant but positive trend in user's evaluation of the agent using fillers as being more human-like \cite{jeong2019exploring}\cmt{[10]}.
-
-%\textbf{Style}
-
-%\textit{Formality}
-%* Agents using normal style seemed more humanlike \cite{ouchi2019should}\cmt{[59]}
-
-%\textit{Disfluency}
-%* No statistical significance in the perceived difference for perceived humanness overall.
-Noticed tendency for users to evaluate agent as more human-like in the filler condition.
-\cite{jeong2019exploring}\cmt{[10]}
-%* No significant effects of naturalness. \cite{pfeifer2009should}\cmt{[12]}
 
@@
 
-%\textbf{Format}
-
-%\textit{Prosody}
-%* Expressive prosody did not have an effect on human-likeness. \cite{zhu2022effects}\cmt{[26]}
-
-%\textit{Typos}
-%* Made the agents seem less human. \cite{westerman2019believe}\cmt{[9]}
-
-%\textit{Capitalization}
-%* Didn't impact humanness \cite{westerman2019believe}\cmt{[9]}
-
-%\textit{Response Delay}
-%* Significant difference in perceived humanness \cite{gnewuch2018faster}\cmt{[19]}
+\textbf{Style: Disfluency}
+* (Voice) No significant difference in naturalness rating for About Myself text, but showed that naturalness is higher for fluent system compared to disfluent speech \cite{wester2015artificial}\cmt{[14]}.
 
@@
 
-%\textbf{Content}
-
-%\textit{Affective Language}
-%* System with extroverted personality is less trustworthy \cite{andrews2012system}\cmt{[38]}
-
-%\textit{Self-Disclosure}
-%* High disclosure group reported more trust than the non disclosure group. Trust change over time for all groups were not significant. \cite{lee2020hear}\cmt{[23]}
-
 None of the studies included in this review has found any significant impact of language style, \textbf{lexical alignment} \cite{hoegen2019end}\cmt{[31]}\cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}, \textbf{disfluency} \cite{pfeifer2009should}\cmt{[12]}, and \textbf{emoticons} \cite{wilhelm2022keep}\cmt{[28]} on the perceived trustworthiness of CAs.
@@
 
-%\textbf{Style}
+\textbf{Format: Prosody}
+* No significant difference in trust ratings across different voice prosody settings with differences in pitch. \cite{cambre2019one}\cmt{[62]}
 
-%\textit{Lexical Alignment}
-%* No significant effect on trustworthiness (ability, benevolence and integrity) \cite{linnemann2018can}\cmt{[15]}
-%* Lexical alignment (using same words) no significant impact on trustworthiness. \cite{huiyang2022improving}\cmt{[17]}
-%* Matched users content (pronoun use, repetition, utterance length) and acoustic variables (speech rate, pitch, loudness) did not significant impact on trustworthiness \cite{hoegen2019end}\cmt{[31]}
-
-%\textit{Disfluency}
-%* No significant effects of trust. \cite{pfeifer2009should}\cmt{[12]}
-
-%\textit{Emoticons}
-%* No significant impact on trustworthiness. \cite{wilhelm2022keep}\cmt{[28]}
-
-%\textbf{Format}
-
-%\textit{Prosody}
-%* AM voice - lower speech rate and lower pitch, no significant difference on rating for truthful. \cite{dubiel2020persuasive}\cmt{[60]}
+\textbf{Format: Proactivity}
+* Overall trust in the system did not differ significantly.
+The intervention style is less trusted than conservative strategies - too obstructive and imposing.
+Proactive should be subtle  \cite{kraus2020effects}\cmt{[64]}
 
@@
 
-%\textbf{Content}
-
-%\textit{Affective language}
-%* Use words with increased lexical emotional expressiveness by selection from NRC Valence, Arousal and Dominance (NRC-VAD) Lexicon - did not have an effect on likability.
-\cite{zhu2022effects}\cmt{[26]}
-%* Significant difference in the variances of the responses for friendliness of the agent \cite{healey2013relating}\cmt{[39]}
-%* Participants rate the agent as lower in warmth when it could not feel / express its feelings (patiency).  \cite{lee2019s}\cmt{[55]}
-
-%\textit{Humour}
-%* Humorous agent was not rated as more likeable. But it is rated as having more of a sense of humour. \cite{ceha2021can}\cmt{[57]}
-
-%
-
 On the impact of language style, various studies on \textbf{lexical alignment} showed that there is no significant impact on the perception of the personality traits related to likability \cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}, friendliness \cite{spillner2021talk}\cmt{[18]}, or politeness \cite{spillner2021talk}\cmt{[18]}.
@@
 
-%\textbf{Style}
-
-%\textit{Lexical Alignment}
-%* Using the words already used by conversational partner did not result in higher likeability. \cite{linnemann2018can}\cmt{[15]}
-%* Lexical alignment (using same words) no significant impact on likability. \cite{huiyang2022improving}\cmt{[17]}
-%* Lexical alignment - both words, and structural (grammatical transformations), movie showtimes.
-There is no significant difference in user opinions like friendly, polite or natural.
-\cite{spillner2021talk}\cmt{[18]}
-
-%\textit{Formality}
-%* Casual conversational style perceived warmer than formal style. \cite{cox2022does}\cmt{[27]}
-%* Agents using normal style (vs. polite / formal style) seemed more friendly, fun and kind \cite{ouchi2019should}\cmt{[59]}
-
-%\textit{Disfluency}
-%* No statistical significance in the perceived difference for likability rating overall.
-There is significant interaction effect between fillers and context of conversation (task vs.
-social).
-Users considered fillers as entertaining and fun in social conversations, but inappropriate in task oriented situations.
-\cite{jeong2019exploring}\cmt{[10]}
-%* No significant effects of likability. \cite{pfeifer2009should}\cmt{[12]}
-
 In the list of reviewed papers, there was only one study measuring the perceived trustworthiness of an agent based on different conversational format of \textbf{prosody}.
@@
 
-%\textbf{Format}
+\textbf{Content: Humour}
+* An agent that uses humourous content is assessed to be more funny \cite{khooshabeh2011does}\cmt{[37]}.
 
-%\textit{Prosody}
-%*  Emotional expressiveness did not have a significant impact on truthfulness. \cite{dubiel2020persuasive}\cmt{[60]}
+\textbf{Style: Disfluency}
+* (Voice) Both About Myself and Speed Dating ratings has shown system scored significantly differently on the Big-5 personality traits.
+Disfluency makes the voice sound more neurotic, less open, less extrovert and less conscientious \cite{wester2015artificial}\cmt{[14]}.
+
+\textbf{Format: Prosody}
+* Low voice pitch rated not as friendly as the other ones. No impact on other traits like assertive and politeness. \cite{cambre2019one}\cmt{[62]}
 
@@
 
+* Format: Response delay - Novice users perceived the agent as more socially present, but experienced users had a negative effect \cite{gnewuch2022opposing}\cmt{[20]}
+* Content: Humour - no overall significant difference between conventional method vs.
+agent using humour for enjoyment.
+Specifically, men enjoyed the agent's jokes more than women.
+\cite{miyamoto2017improving}\cmt{[46]}.
+* Format: Proactivity - significant interaction between proactive dialogue strategies and task difficulty for perceived competence and perceived reliability.
+For easier tasks, system help is not really required.
+\cite{kraus2020effects}\cmt{[64]}
+
 \subsection{Study Design}
@@
 
+\subsection{Relationship between perceptions}
+
+Response delay: social presence has a significant effect on intention to use. 
+\cite{gnewuch2022opposing}\cmt{[20]}
+
+Perceived intelligence positively associated with perceived usefulness, perceived ease of use, initial trust, and perceived anthropomorphism.
+Perceived anthropomorphism is associated with perceived enjoyment, and intention to adopt.
+Perceived usefulness and perceived enjoyment impacts intention to adopt.
+\cite{moussawi2021perceptions}\cmt{[36]}
+
+The size of the effect for language we observed is clearly higher than the size of the effect for voice. \cite{habler2019effects}\cmt{[63]}
+
 \subsection{Gaps}
 
-* Combined effects - integrated mental model
-* Lack of investigations - name a few areas
+Combined effects
+* integrated mental model \cite{knijnenburg2016inferring}\cmt{[34]}
+* Anthropomorphized chatbot (text) using affective language (emotional expressions), self-referencing, emoticons, response delays.
+Resulted in higher perceived anthropomorphism, which in result led to lower negative word of mouth and loss of trust.
+anthropomorphic design is beneficial not only to initial trust but also to the ongoing trust relationship \cite{seeger2021chatbots}\cmt{[35]}
+
+Lack of investigations - name a few areas
 
@@
 Self-disclosure encourage higher trust and intimacy, to disclose sensitive information. Who have access to this data? need to be aware of privacy / data sharing practices. \cite{lee2020hear}\cmt{[23]}
+
+Evidence for the influence of voice gender and pitch on stereotypical trait attribution.
+Active trait attribution is missing as most participants attributes to the negative side of traits for CAs.
+\cite{cambre2019one}\cmt{[62]}
 

### 2023-02-09 paper.tex
added graphics to paper; added all references from lit review

@@
 \usepackage{lipsum}
+\usepackage{multirow}
+\usepackage{graphicx}
+\usepackage{booktabs}
 
@@
 
+Design the conversational agents
+
 \section{Literature Review}
@@
 We screened the titles and abstracts of the papers based on the selection criteria below which resulted in 221 papers.
-Reviewing the full articles of these publication resulted in <X> papers for analysis.
-A backward/forward search was also performed to find new publications, adding <X> papers to the corpus.
+Reviewing the full articles of these publication resulted in 49 papers for analysis.
+An additional search for related literature was also performed to find new publications, adding 8 more papers to the corpus.
 
-<Add graphic of PRIMSA process>
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.6\columnwidth]{fig:prisma.png}
+  \caption{Literature search using PRISMA guidelines}
+  \label{fig:prisma}
+\end{figure}
+
+Figure \ref{fig:prisma}
 
@@
 
-Categorization of perceptions \newline
+\subsection{Dataset Characteristics}
+
+* Year and publication venue
+
+\begin{figure*}[h]
+  \centering
+  \includegraphics[width=\textwidth]{fig:paper.png}
+  \caption{Stacked barchart of number of papers by year and venue}
+  \label{fig:paper}
+\end{figure*}
+
+Figure \ref{fig:paper}
+
+\newline
+* Modality - voice vs. text Table \ref{tab:modality}
+
+\begin{table}[]
+\begin{tabular}{@{}ll@{}}
+\toprule
+\textbf{Modality} & \textbf{No. Papers} \\ \midrule
+Voice             & 35                  \\
+Text              & 27                  \\ \bottomrule
+\end{tabular}%
+\caption{Number of paper for voice and text modalities}
+\label{tab:modality}
+\end{table}
+
+\section{Anthropomorphized Perceptions}
+
+Here is Table \ref{tab:perceptions} for perceptions.
+
+\begin{table*}[]
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{@{}lllc@{}}
+\toprule
+ & \textbf{Measure}   & \textbf{Contains}                                  & \textbf{No. Papers} \\ \midrule
+\multirow{3}{*}{\textbf{Perception of Interaction with an Agent}}    & Usability       & accuracy, ease of use, efficiency, helpfulness & 23 \\
+ & Engagement         & enjoyment, annoyance, desirable, intention to use  & 28         \\
+ & Satisfaction       & service satisfaction, quality of interaction       & 12         \\ \midrule
+\multirow{3}{*}{\textbf{Perception of Agent's Ability}}              & Intelligence    & knowledgeable, intelligent, expertise                             & 11 \\
+ & Competence         & competent, capable                                 & 4          \\
+ & Trust              & credibility, trustworthy, truthfulness, confidence & 15         \\ \midrule
+\multirow{3}{*}{\textbf{Perception of Social Connection with Agent}} & Social Presence & connectedness, familiarity, similarity, psychological distance    & 18 \\
+ & Conversation Tone  & appropriate, expressive, empathetic, persuasive    & 13         \\
+ & Intimacy           & intimate, rapport, quality of relationship         & 7          \\ \midrule
+\multirow{2}{*}{\textbf{Perception of Agent's Humanness}}            & Human-likeness  & human-like, natural, artificial, machine-like                     & 20 \\
+ & Personality Traits & friendly, kind, warm, creepy, likeable, polite     & 27         \\ \bottomrule
+\end{tabular}%
+}
+\caption{Perception measures}
+\label{tab:perceptions}
+\end{table*}
+
+%\multirow{3}{*}{\parbox{2cm}{\textbf{Perception of Interaction with an Agent}}} & Usability & accuracy, ease of use, efficiency, helpfulness &
+
+%Usability
+%\cite{linnemann2018can}\cmt{[15]}\cite{huiyang2022improving}\cmt{[17]}\cite{spillner2021talk}\cmt{[18]}\cite{kim2020can}\cmt{[24]}\cite{wilhelm2022keep}\cmt{[28]}\cite{ma2022ask}\cmt{[29]}\cite{healey2013relating}\cmt{[39]}\cite{miehle2018exploring}\cmt{[51]}\cite{choi2020nobody}\cmt{[54]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{elsholz2019exploring}\cmt{[61]}\cite{habler2019effects}\cmt{[63]}\cite{kraus2020effects}\cmt{[64]}\cite{cuadra2021my}\cmt{[67]}\cite{roy2021users}\cmt{[71]}\cite{chan2021kinvoices}\cmt{[74]}\cite{hu2022polite}\cmt{[76]}\cite{ceha2022expressive}\cmt{[77]}\cite{haas2022keep}\cmt{[78]}\cite{jestin2022effects}\cmt{[81]}\cite{misu2011toward}\cmt{[83]}\cite{ashktorab2019resilient}\cmt{[88]}\cite{kim2019comparing}\cmt{[89]}
+
+%Engagement
+%\cite{linnemann2018can}\cmt{[15]}\cite{huiyang2022improving}\cmt{[17]}\cite{spillner2021talk}\cmt{[18]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{lee2020hear}\cmt{[23]}\cite{kim2020can}\cmt{[24]}\cite{zhu2022effects}\cmt{[26]}\cite{cox2022does}\cmt{[27]}\cite{ma2022ask}\cmt{[29]}\cite{andrews2012system}\cmt{[38]}\cite{healey2013relating}\cmt{[39]}\cite{miyamoto2017improving}\cmt{[46]}\cite{miehle2018exploring}\cmt{[51]}\cite{fadhil2018effect}\cmt{[52]}\cite{ceha2021can}\cmt{[57]}\cite{elsholz2019exploring}\cmt{[61]}\cite{cuadra2021my}\cmt{[67]}\cite{volkel2021examining}\cmt{[69]}\cite{roy2021users}\cmt{[71]}\cite{yang2021effect}\cmt{[72]}\cite{xiao2021let}\cmt{[73]}\cite{chan2021kinvoices}\cmt{[74]}\cite{volkel2022user}\cmt{[75]}\cite{ceha2022expressive}\cmt{[77]}\cite{go2021conversational}\cmt{[80]}\cite{jestin2022effects}\cmt{[81]}\cite{moilanen2022measuring}\cmt{[82]}\cite{kim2019comparing}\cmt{[89]}
+
+%Satisfaction                                                                 
+%\cite{pfeifer2009should}\cmt{[12]}\cite{gnewuch2018faster}\cmt{[19]}\cite{diederich2019emulating}\cmt{[25]}\cite{wilhelm2022keep}\cmt{[28]}\cite{ma2022ask}\cmt{[29]}\cite{hoegen2019end}\cmt{[31]}\cite{yang2017perceived}\cmt{[44]}\cite{choi2020nobody}\cmt{[54]}\cite{elsholz2019exploring}\cmt{[61]}\cite{habler2019effects}\cmt{[63]}\cite{roy2021users}\cmt{[71]}\cite{hu2022polite}\cmt{[76]}\cite{ceha2022expressive}\cmt{[77]}
+
 Categorization of social cues \newline
+* adapted from Taxonomy of social cues
+* added a middle layer
+* combined elements as we are studying disembodied agents
 
-\subsection{Dataset Characteristics}
-* Year and publication venue
-\newline
-* Modality - voice vs. text
-\newline
-* Systems tested - WoZ, prototype, actual applications
+\section{Conversation Architecture}
+
+Here is Table \ref{tab:cues} for conversation architecture elements.
+
+\begin{table*}[]
+%\resizebox{\textwidth}{!}{%
+\begin{tabular}{@{}lllc@{}}
+\toprule
+ & \textbf{Measure}      & \textbf{Contains}                                      & \multicolumn{1}{l}{\textbf{No. Papers}} \\ \midrule
+\multirow{4}{*}{\textbf{Linguistic Content}}    & Affective Language & emotional expressions, sentiment-adaptive responses & 11 \\
+ & Social Talk           & self-disclosure, social dialogue                       & 7                                       \\
+ & Humour                & humorous content, jokes                                & 5                                       \\
+ & Agent-Initiated Content & elicit user feedback, proactivity, conversation repair & 4                                       \\ \midrule
+\multirow{4}{*}{\textbf{Linguistic Style}}      & Formality          & formal vs. casual, honorific expressions                               & 9  \\
+ & Alignment             & content matching, lexical alignment, agreeableness     & 7                                       \\
+ & Elaborateness         & elaborate, concise, sentence structure                 & 6                                       \\
+ & Disfluency            & fillers, interjections, repetitions                    & 5                                       \\ \midrule
+\multirow{3}{*}{\textbf{Non-Linguistic Format}} & Prosody            & pitch, intonation, speech rate, spoken accent                          & 12 \\
+ & Text Variation        & typo, capitalization, response delay, typing indicator & 5                                       \\
+ & Emotional Cue         & emoticons, laughter                                    & 6                                       \\ \bottomrule
+\end{tabular}%
+%}
+\caption{Conversation architecture elements}
+\label{tab:cues}
+\end{table*}
 
@@
   \centering
-  \includegraphics[width=\textwidth]{heatmap.png}
+  \includegraphics[width=\textwidth]{fig:heatmap-impact.png}
   \caption{Heatmap of literature for perception of conversational agents for each type of conversational architecture element.}
@@
 Perceptions are categorized into perception of interaction with an agent (engagement, satisfaction, accuracy), perception of social connection with an agent (intimacy, conversation tone, social presence), and perception of agent's humanness (human-likeness, trustworthiness, personality traits).}
-  \label{fig:heatmap}
+  \label{fig:heatmap-impact}
 \end{figure*}
 
-Figure \ref{fig:heatmap}
+Figure \ref{fig:heatmap-impact}
 
@@
 
-Content: Humour
+\textbf{Content: Humour}
 * No overall significant difference between conventional method vs.
@@
 \cite{miyamoto2017improving}\cmt{[46]}.
+* Motivation to continue the conversation significant increased after day 2 for the humorous agent \cite{go2021conversational}\cmt{[80]}
 
-Style: Language Formality
+\textbf{Style: Language Formality}
 * Users spent more time with the Shakespearean chatbot version with more non-task related user inputs. Enjoyment was measured but no report \cite{elsholz2019exploring}\cmt{[61]}
+* commanding/formal wording was rated significantly more useful than the informal wording; while the informal wording was rated as significantly more annoying than the commanding/formal wording.
+No impact on desirability.
+\cite{jestin2022effects}\cmt{[81]}
+* High conscientiousness (formal) and high extroversion (casual) chatbot personality have higher user engagement. \cite{moilanen2022measuring}\cmt{[82]}
+* Analysis of ease of use reveals that there are no significant main effects for platform questionnaire vs. chatbot, and conversational style formal vs. casual.\cite{kim2019comparing}\cmt{[89]}
+
+\textbf{Social talk / elaborate}
+* Not significant importance between introvert and extrovert agents. But the machine-like speaking agent is rated lower. \cite{roy2021users}\cmt{[71]}
+* usefulness depended on the task \cite{haas2022keep}\cmt{[78]}
+* High extroversion chatbot personality have the higher user engagement \cite{moilanen2022measuring}\cmt{[82]}
+
+\textbf{Disfluency}
+* Using moderately repetitive utterances resulted in higher desire to continue the dialogue with the agent. \cite{yang2021effect}\cmt{[72]}
+* Interjections did not have any impacts of cognitive workload \cite{ceha2022expressive}\cmt{[77]}
+
+\textbf{Proactive}
+* Different framing has impacts on the perceived disruptiveness of the agent. \cite{xiao2021let}\cmt{[73]}
+
+\textbf{Prosody}
+* No impact on annoying, undesirable, useful \cite{jestin2022effects}\cmt{[81]}
+* Dialog-style conversation using prosodic cues is rated as less easy to understand than the reading-style \cite{misu2011toward}\cmt{[83]}
+
+\textbf{Combined}
+* (Extraverted: emoticons, self-disclosure, talkative, affective language / Introverted: formal style, less talkative) all personalities have similar usability ratings.
+Also, users have greater desire to interact with the extraverted chatbot \cite{volkel2022user}\cmt{[75]}
+* (Politeness: affective language + elaborateness of speech) no impact on usability \cite{hu2022polite}\cmt{[76]}
 
@@
 Dubiel et al.'s study \cite{dubiel2020persuasive}\cmt{[60]} on \textbf{prosody} did not find any significant differences on the rating for accuracy across agents with different speech rates and pitch.
+
+\textbf{Social talk}
+* Introverted agent is more efficient. \cite{roy2021users}\cmt{[71]}
+* Efficiency depended on the task \cite{haas2022keep}\cmt{[78]}
+
+\textbf{Language Formality}
+* commanding/formal wording was rated significantly more effective than informal wording \cite{jestin2022effects}\cmt{[81]}
+
+\textbf{Prosody}
+* No impact on effectiveness \cite{jestin2022effects}\cmt{[81]}
+
+\textbf{Repair}
+* One reason for choosing repair strategy preference is efficiency and efficacy. \cite{ashktorab2019resilient}\cmt{[88]}
 
@@
 
+\textbf{Social talk}
+* Not significant importance between introvert and extrovert agents. But the machine-like speaking agent is rated lower. \cite{roy2021users}\cmt{[71]}
+
+\textbf{Combined}
+* (Politeness: affective language + elaborateness of speech) no impact on user satisfaction \cite{hu2022polite}\cmt{[76]}
+
 %%%%%
@@
 
-[TODO] * Associations between conversational architecture elements and perceptions
+\textit{To be incorporated}
+
+\textbf{Repair}
+* perceived quality of the interaction is muhc higher in repair condition when the agent made a mistake; rating is lower if no mistake was present. \cite{cuadra2021my}\cmt{[67]}
 
@@
 
+\textbf{Prosody}
+* VA using kin's voice is rated as more intelligent. \cite{chan2021kinvoices}\cmt{[74]}
+
+\textbf{Repair}
+* One reason for choosing repair strategy preference is perceived intelligence and capability. \cite{ashktorab2019resilient}\cmt{[88]}
+
 %%
@@
 * There is no significant effect on perceived performance of the CA between male-gendered and female-gendered voices. \cite{habler2019effects}\cmt{[63]}
+* For expertise, multilingual students rated higher the non-native English-speaking virtual human. \cite{feijoo2021effects}\cmt{[70]}
 
@@
 * Rated higher that agent listened openly to participants' emotions, as that agent can feel waht the user is feeling. \cite{hu2021enhancing}\cmt{[56]}
+* social condition didn't have an impact on social presence \cite{lubold2016effects}\cmt{[86]}
+
+\textbf{Prosody}
+* VA using kin's voice is rated as more socially present and closer psychological connection with user. \cite{chan2021kinvoices}\cmt{[74]}
+* voice plus social condition has higher social presence than the social condition \cite{lubold2016effects}\cmt{[86]}
+
+\textbf{Humour}
+* Familiarity with the agent is rated higher at the end of the study (day 7) compared to non-humorous agent \cite{go2021conversational}\cmt{[80]}
+
+\textbf{Laughter}
+* Laughter had no impact on social presence of an agent \cite{niewiadomski2013laugh}\cmt{[85]}
 
@@
 
+\textbf{Disfluency}
+* Using moderately repetitive utterances resulted in higher perceived empathy. \cite{yang2021effect}\cmt{[72]}
+
+\textbf{Language Formality}
+* commanding/formal wording was rated significantly more appropriate and assertive than informal wording \cite{jestin2022effects}\cmt{[81]}
+
+\textbf{Prosody}
+* No impact on appropriate and assertive \cite{jestin2022effects}\cmt{[81]}
+* Dialog-style conversation using prosodic cues is rated as more appropriate than the reading-style \cite{misu2011toward}\cmt{[83]}
+
 %%
@@
 Westerman et al's study on different text formats of conversation \cite{westerman2019believe}\cmt{[9]} showed that \textbf{typos} negatively impacted the perceived social attraction of the agent, while \textbf{capitalization} did not have any impacts.
+
+\textbf{Disfluency}
+* Interjections did not have any impacts of quality of relationship, but it did result in higher emotional rapport. \cite{ceha2022expressive}\cmt{[77]}
+
+\textbf{Affective Language}
+* social condition didn't have an impact on social presence \cite{lubold2016effects}\cmt{[86]}
+
+\textbf{Prosody}
+* voice and social condition didn't have an impact on social presence \cite{lubold2016effects}\cmt{[86]}
 
@@
 
-%%
-\subsubsection{Trustworthiness}
-%%
+\textbf{Prosody}
+* VA using kin's voice is rated as more human-like. \cite{chan2021kinvoices}\cmt{[74]}
+* Dialog-style conversation using prosodic cues is rated as less human-like than the reading-style \cite{misu2011toward}\cmt{[83]}
 
-For the use of language content, agents using more \textbf{affective language} is seen as less trustworthy, as users felt it was being overly familiar \cite{andrews2012system}\cmt{[38]}.
-On the other hand, users conversing with agents that used \textbf{self-disclosure} content reported more trust towards the agent compared to the non disclosure group \cite{lee2020hear}\cmt{[23]}.
+\textbf{Social talk / Elaborateness}
+* Naturalness depends on the task \cite{haas2022keep}\cmt{[78]}
 
-None of the studies included in this review has found any significant impact of language style, \textbf{lexical alignment} \cite{hoegen2019end}\cmt{[31]}\cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}, \textbf{disfluency} \cite{pfeifer2009should}\cmt{[12]}, and \textbf{emoticons} \cite{wilhelm2022keep}\cmt{[28]} on the perceived trustworthiness of CAs.
-Similarly for conversational format, there is not significant difference on the rating for truthfulness of the agent across different voice \textbf{prosody} settings \cite{dubiel2020persuasive}\cmt{[60]}.
+\textbf{Language Formality}
+* No impact on artificial or humanlike perceptions \cite{jestin2022effects}\cmt{[81]}
 
-\textbf{Format: Prosody}
-* No significant difference in trust ratings across different voice prosody settings with differences in pitch. \cite{cambre2019one}\cmt{[62]}
+\textbf{Prosody}
+* Matthew voice is rated as least artificial  \cite{jestin2022effects}\cmt{[81]}
 
-\textbf{Format: Proactivity}
-* Overall trust in the system did not differ significantly.
-The intervention style is less trusted than conservative strategies - too obstructive and imposing.
-Proactive should be subtle  \cite{kraus2020effects}\cmt{[64]}
+\textbf{Laughter}
+* Laughter was not rated as natural in an agent \cite{niewiadomski2013laugh}\cmt{[85]}
+
+\textbf{Combined}
+* (Politeness: affective language + elaborateness of speech) no impact on likability, but positive politeness interactions are rated as more polite \cite{hu2022polite}\cmt{[76]}
+
+\textbf{Repair}
+* One reason for choosing repair strategy preference is naturalness. \cite{ashktorab2019resilient}\cmt{[88]}
 
@@
 
+\textit{To be incorporated}
+
 \textbf{Content: Humour}
@@
 \textbf{Format: Prosody}
-* Low voice pitch rated not as friendly as the other ones. No impact on other traits like assertive and politeness. \cite{cambre2019one}\cmt{[62]}
+* Low voice pitch rated not as friendly as the other ones. No impact on other traits like assertive and politeness. \cite{tolmeijer2021female}\cmt{[62]}
+* VA using kin's voice is rated as more likable. \cite{chan2021kinvoices}\cmt{[74]}
+* No impact on entertaining or friendly  \cite{jestin2022effects}\cmt{[81]}
+
+\textbf{Repair}
+* When VA corrected in the condition it didn't make a mistake, it is seen as anxious. Otherwise it is perceived as calm and emotionally stable. \cite{cuadra2021my}\cmt{[67]}
+* One reason for choosing repair strategy preference is politeness. \cite{ashktorab2019resilient}\cmt{[88]}
+
+\textbf{Social talk}
+* Using more social talk is positive correlated with extroversion. \cite{volkel2021manipulating}\cmt{[68]}
+* Not significant importance between introvert and extrovert agents. \cite{roy2021users}\cmt{[71]}
+* Likability depends on the task \cite{haas2022keep}\cmt{[78]}
+
+\textbf{Language Formality}
+* Informal wording was rated as strongly more entertaining and friendly than the commanding/formal wording. \cite{jestin2022effects}\cmt{[81]}
+
+\textbf{Agreeableness}
+* Being highly confrontational (less agreeable) is rated as less conscientious \cite{volkel2021manipulating}\cmt{[68]}
+* Designing for more agreeable resulted in personality rated as more agreeable \cite{volkel2021examining}\cmt{[69]}
+
+\textbf{Combined}
+* (Extraverted: emoticons, self-disclosure, talkative, affective language / Introverted: formal style, less talkative) extraverted personality rated as more extraverted \cite{volkel2022user}\cmt{[75]}
+
+%%
+\subsubsection{Trustworthiness}
+%%
+
+For the use of language content, agents using more \textbf{affective language} is seen as less trustworthy, as users felt it was being overly familiar \cite{andrews2012system}\cmt{[38]}.
+On the other hand, users conversing with agents that used \textbf{self-disclosure} content reported more trust towards the agent compared to the non disclosure group \cite{lee2020hear}\cmt{[23]}.
+
+None of the studies included in this review has found any significant impact of language style, \textbf{lexical alignment} \cite{hoegen2019end}\cmt{[31]}\cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}, \textbf{disfluency} \cite{pfeifer2009should}\cmt{[12]}, and \textbf{emoticons} \cite{wilhelm2022keep}\cmt{[28]} on the perceived trustworthiness of CAs.
+Similarly for conversational format, there is not significant difference on the rating for truthfulness of the agent across different voice \textbf{prosody} settings \cite{dubiel2020persuasive}\cmt{[60]}.
+
+\textbf{Format: Prosody}
+* No significant difference in trust ratings across different voice prosody settings with differences in pitch. \cite{tolmeijer2021female}\cmt{[62]}
+* No impact on trustworthiness  \cite{jestin2022effects}\cmt{[81]}
+
+\textbf{Format: Proactivity}
+* Overall trust in the system did not differ significantly.
+The intervention style is less trusted than conservative strategies - too obstructive and imposing.
+Proactive should be subtle  \cite{kraus2020effects}\cmt{[64]}
+
+\textbf{Language Formality}
+* No impact on trustworthiness \cite{jestin2022effects}\cmt{[81]}
 
@@
 
-\subsection{Inconsistencies in Perception Measures}
+\subsection{RQ1 - synthesis of conversation architecture elements}
+
+Sometimes a study is covering multiple conversational element cues, hard to break it out.
+For example, extroverted personality used in \cite{volkel2022user}\cmt{[75]} has emoticons, affective language, talkative, and self-disclosure.
+Need to break it down.
+
+Also, breaking down "personalities" to its core components.
+
+\subsection{RQ2 - synthesis of perceptions}
+
+\subsubsection{Inconsistencies in Perception Measures}
 
@@
 
-\subsection{Other Influencing Factors}
+\subsubsection{Relationship between perceptions}
+
+Response delay: social presence has a significant effect on intention to use. 
+\cite{gnewuch2022opposing}\cmt{[20]}
+
+Perceived intelligence positively associated with perceived usefulness, perceived ease of use, initial trust, and perceived anthropomorphism.
+Perceived anthropomorphism is associated with perceived enjoyment, and intention to adopt.
+Perceived usefulness and perceived enjoyment impacts intention to adopt.
+\cite{moussawi2021perceptions}\cmt{[36]}
+
+The size of the effect for language we observed is clearly higher than the size of the effect for voice. \cite{habler2019effects}\cmt{[63]}
+
+VA self-repair can backfire if time or accuracy is of the essence. (repair and accuracy) \cite{cuadra2021my}\cmt{[67]}
+
+\subsection{RQ3 - relationship between conversation architecture elements and perceptions}
+
+\subsubsection{Other Influencing Factors}
 
@@
 \cite{kraus2020effects}\cmt{[64]}
+* Preference for the level of social talk depended on the task, even within the same transactional context, as users preferred high level for playing a song, but low level for writing a text.
+\cite{volkel2021manipulating}\cmt{[68]}
+* Correlation between user's personality of agreeableness vs. preference for agreeable level of chatbot \cite{volkel2021examining}\cmt{[69]}
+* For expertise, multilingual students rated higher the non-native English-speaking virtual human. \cite{feijoo2021effects}\cmt{[70]}
+* Participants felt irritated when humorous statements were made when they talked about experiencing sadness \cite{go2021conversational}\cmt{[80]}
 
-\subsection{Study Design}
+%\subsubsection{Study Design}
 
-\textbf{Interview vs experiment}
-* Humour - what's said vs. study results
+%\textbf{Interview vs experiment}
+%* Humour - what's said vs. study results
 
-\textbf{Observer study vs. interaction study}
-* In observer study, participants attributed higher integrity (trustworthiness), response accuracy and likeability to the agent with lexical alignment, but this effect was not observed in the interaction study.
+%\textbf{Observer study vs. interaction study}
+%* In observer study, participants attributed higher integrity (trustworthiness), response accuracy and likeability to the agent with lexical alignment, but this effect was not observed in the interaction study.
 Also, interaction study had lower cognitive demand but no effect in the observer study.
 \cite{linnemann2018can}\cmt{[15]}
-* \cite{zhu2022effects}\cmt{[26]}
-* \cite{cox2022does}\cmt{[27]}
+%* \cite{zhu2022effects}\cmt{[26]}
+%* \cite{cox2022does}\cmt{[27]}
 
-\subsection{Modality}
+\subsubsection{Modality}
 
@@
 
-\subsection{Relationship between perceptions}
-
-Response delay: social presence has a significant effect on intention to use. 
-\cite{gnewuch2022opposing}\cmt{[20]}
-
-Perceived intelligence positively associated with perceived usefulness, perceived ease of use, initial trust, and perceived anthropomorphism.
-Perceived anthropomorphism is associated with perceived enjoyment, and intention to adopt.
-Perceived usefulness and perceived enjoyment impacts intention to adopt.
-\cite{moussawi2021perceptions}\cmt{[36]}
-
-The size of the effect for language we observed is clearly higher than the size of the effect for voice. \cite{habler2019effects}\cmt{[63]}
-
-\subsection{Gaps}
+\subsubsection{Gaps}
 
@@
 
-\subsection{Human-human vs. Human-machine}
+%\subsubsection{Human-human vs. Human-machine}
 
-* Impact of lexical alignment on people's perceived annoyance and likability differed in HHI (higher) and HCI (no impact). \cite{huiyang2022improving}\cmt{[17]}.
+%* Impact of lexical alignment on people's perceived annoyance and likability differed in HHI (higher) and HCI (no impact). \cite{huiyang2022improving}\cmt{[17]}.
 
-\subsection{Ethical Considerations}
+\subsubsection{Ethical Considerations}
 
@@
 Active trait attribution is missing as most participants attributes to the negative side of traits for CAs.
-\cite{cambre2019one}\cmt{[62]}
+\cite{tolmeijer2021female}\cmt{[62]}
+
+The social and emotional benefits of self-repair in interaction need to be balanced against the creepiness of the monitoring and modelling needed to make self-repair possible.
+\cite{cuadra2021my}\cmt{[67]}
 

### 2023-02-10 paper.tex
upload the correct paper.tex file
first draft of methods, perceptions and cues sections

@@
 % \title[short title]{How to Make Pinocchio a Real Boy? Designing conversational architecture elements to achieve desirable anthropomorphized perceptions}
-\title[Bot's Guide to Being Human]{Bot's Guide to Being Human: Investigating the Effect of Conversational Architecture Elements on the Anthropomorphized Perceptions of Conversational Agents}
+\title[Bot's Guide to Being Human]{Bot's Guide to Being Human: Investigating the Effect of Conversation Architecture Elements on the Anthropomorphized Perceptions of Conversational Agents}
 % Blurring the line between human and bots
@@
 One of the key factors for anthropomorphized perception is how conversational agents convey information through verbal or non-verbal cues.
-Studies have found that conversational agents are perceived as more socially present and emotionally intelligent if they use sentiment-adaptive response based on user's utterances, resulting in higher user satisfaction \cite{diederich2019emulating} \cite{yang2017perceived}.
+Studies have found that conversational agents are perceived as more socially present and emotionally intelligent if they use sentiment-adaptive response based on user's utterances, resulting in higher user satisfaction \cite{diederich2019emulating}\cite{yang2017perceived}.
 Also, CAs that mimic user behaviour through lexical alignment reduce users' cognitive workload, resulting in higher engagement with the interaction \cite{spillner2021talk}.
@@
 
-\section{Literature Review}
-
-\cite{finch2020towards} Towards unified dialogue system evaluation: A comprehensive analysis of current evaluation protocols
-
-Synthesis on conversational architecture
-
-Synthesis on measures
-
-Connections between conversational architecture elements and measures
+%\section{Literature Review}
+
+%\cite{finch2020towards} Towards unified dialogue system evaluation: A comprehensive analysis of current evaluation protocols
+
+%Synthesis on conversational architecture
+
+%Synthesis on measures
+
+%Connections between conversational architecture elements and measures
 
@@
 
+This section describes the research methodologies for the search procedure, selection criteria and data analysis process.
+
 \subsection{Search Procedure}
 
-We reviewed and selected relevant literature related to designed conversational architecture elements and perceptions of conversational agent following PRISMA guidelines \cite{prisma}.
+Following PRISMA guidelines \cite{prisma}, we reviewed and selected literature relevant to the relationships between the specifics of conversation architecture elements and anthropomorphized perceptions of CAs.
 Searches were carried out in the ACM Digital Library between January 1 and January 15, 2023.
-Based on search terms used in previously published literature reviews on conversational agents \cite{clark2019state}\cite{rapp2021human} , the following keywords have been identified to search for publications related to conversational user interfaces:
+During initial analysis, it didn't seem like there were common terms used to refer to either conversation architecture elements, or anthropomorphized perceptions.
+As such, search terms were kept general to literature related to conversational agents.
+Based on search terms used in previously published literature reviews \cite{clark2019state}\cite{rapp2021human} , the following keywords have been identified to search for publications related to conversational user interfaces:
 \newline
@@
   \item Peer-reviewed publications written in English
-  \item Voice-based or text-based disembodied conversational agents
-  \item Experiment study on the impact of designed conversational architecture elements on the perception of agents.
-  \item Measures the perceptions of the interaction or perceptions of the agent as part of the study
+  \item Voice-based or text-based conversational agents
+  \item Experiment study on the impact of conversation architecture elements on the anthropomorphized perceptions of agents
+  \item Impact of conversation architecture elements can be separated from other effects (e.g. embodiment)
+
 \end{itemize}
@@
 An additional search for related literature was also performed to find new publications, adding 8 more papers to the corpus.
+We identified 57 relevant articles that met our selection criteria (see Figure \ref{fig:prisma}).
 
@@
   \centering
-  \includegraphics[width=0.6\columnwidth]{fig:prisma.png}
+  \includegraphics[width=0.6\columnwidth]{fig-prisma.png}
   \caption{Literature search using PRISMA guidelines}
@@
 
-Figure \ref{fig:prisma}
-
-\subsection{Data Analysis}
-
-\subsection{Dataset Characteristics}
-
-* Year and publication venue
+\subsubsection*{Literature Corpus Characteristics}
+
+The papers reviewed (n=57) were published between May 2011 and November 2022.
+More than 75\% of the papers were published in or after 2019, with a slight trend upwards over the years (see Figure \ref{fig:paper}).
+The vast majority of the papers in our corpus were published in conference proceedings (n=50), with the remainder papers published in journals.
+Out of the papers published in conferences, the top conferences were The ACM Conference on Human Factors in Computing Systems (n=16), Conversational User Interfaces (n=7), Human-Agent Interaction (n=4), and Intelligent Virtual Agents (n=4).
+Out of the papers published in journals, some venues include the International Journal of Human-Computer Interaction (n=2) and Interacting with Computers (n=1).
+
+On the modality characteristics of the conversational agents in the corpus, there is a roughly even split between the modalities, with slightly more papers (n=30) studying voice-based CAs, and the rest (n=27) studying text-based CAs.
 
@@
   \centering
-  \includegraphics[width=\textwidth]{fig:paper.png}
+  \includegraphics[width=\textwidth]{fig-paper.png}
   \caption{Stacked barchart of number of papers by year and venue}
@@
 
-Figure \ref{fig:paper}
-
-\newline
-* Modality - voice vs. text Table \ref{tab:modality}
-
-\begin{table}[]
-\begin{tabular}{@{}ll@{}}
-\toprule
-\textbf{Modality} & \textbf{No. Papers} \\ \midrule
-Voice             & 35                  \\
-Text              & 27                  \\ \bottomrule
-\end{tabular}%
-\caption{Number of paper for voice and text modalities}
-\label{tab:modality}
-\end{table}
-
-\section{Anthropomorphized Perceptions}
-
-Here is Table \ref{tab:perceptions} for perceptions.
+\subsection{Data Analysis}
+
+\subsubsection*{Anthropomorphized Perceptions}
+The exact quotes of anthropomorphized perception measurements were extracted from each paper.
+Inductive thematic analysis was used to group these verbatim quotes into codes based on their meanings.
+For example, the code likeability of the agent contains the questionnaire item "this voice agent was likeable" used by \cite{cuadra2021my}\cmt{[67]}, Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed}'s set of questions on likeability used by \cite{linnemann2018can}\cmt{[15]}, and Subjective Assessment of Speech System Interface (SASSI) questionnaire \cite{hone2000towards}\cmt{sassi}'s set of questions on likeability used by  \cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}.
+This step resulted in 83 unique codes.
+The codes are then organized based similarity of the meanings, resulting in 11 basic themes.
+For example, the basic theme of \textit{personality traits} of the agent contains measurements such as likeability, friendliness, and warmth.
+Lastly, the 11 basic themes are categorized into 4 organizing themes: \textit{perception of interaction with agent, perception of agent's ability, perception of social connection with agent, and perception of agent's humanness} (Table \ref{tab:perceptions}).
+
+\subsubsection*{Conversation Architecture Elements}
+The conversation architecture elements used in the study were extracted from each paper.
+Some of the papers were applying multiple elements to the CA design, such as the the anthropomorphic design used in this study \cite{seeger2021chatbots}\cmt{[35]}.
+In the case where multiple elements were used, the codes broke down the conversation architecture into its core components.
+For example, the anthropomorphic design used in Seeger et al's study \cite{seeger2021chatbots}\cmt{[35]} was broken down to the elements of emotional expressions, is-typing indicator, emoticons, and response delay to capture as codes.
+58 unique codes were created as part of this process, capturing elements like sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}, lexical alignment \cite{spillner2021talk}\cmt{[18]}, and typos \cite{westerman2019believe}\cmt{[9]}.
+Codes were then organized based on similarity of the elements.
+For example, the basic theme of \textit{disfluency} contains elements of fillers \cite{jeong2019exploring}\cmt{[10]}\cite{wester2015artificial}\cmt{[14]}, interjections \cite{ceha2022expressive}\cmt{[77]}\cite{hu2021enhancing}\cmt{[56]}, and repetitions \cite{yang2021effect}\cmt{[72]}.
+Lastly, these basic themes are then categorized into organizing themes adapted from the social cues taxonomy structure by Feine et al \cite{feine2019taxonomy}.
+Based on this paper, the Verbal-Content category is mapped to our organizing theme of \textit{linguistic content}, and the Verbal-Style category is mapped to our organizing theme of \textit{linguistic style}.
+Given our analysis focuses on the text and voice aspects of a conversational agent and does not analyze the embodiment aspects of design, the visual category is not applicable for our analysis.
+Also, we collapsed the auditory and invisible categories into the organizing theme of \textit{non-linguistic format} (Table \ref{tab:cues}).
+
+\subsubsection*{Relationship Between Anthropomorphized Perceptions and Conversation Architecture Elements}
+Based on the codes developed for anthropomorphized perceptions and conversation architecture elements above, we extracted the relationships between perceptions and architecture elements from each paper, noting whether the architecture element had an impact of on the perceptions.
+Out of the 57 papers, 264 connections between anthropomorphized perceptions and conversation architecture elements were found.
+To analyze specifically the relationships between the specifics of conversation architecture that affect the anthropomorphized perceptions of CAs, 69 connections that did not result in significant relationships were discarded, resulting in 195 relationships for analysis.
+For example, the specific connection between style matching and user satisfaction was discarded because Hoegen et al.
+\cite{hoegen2019end}\cmt{[31]} did not find a significant difference between the style matching agent and the non-style matching agent for overall interaction satisfaction.
+Out of the 195 relationships, 185 were relationships between individual architecture elements and perceptions.
+These single architecture element to perception relationships are visualized as a heatmap based on literature coverage within the literature review corpus, as seen in Figure \ref{fig:heatmap-impact}.
+Perceptions impacted by the composite of multiple architecture elements in an agent will be discussed in more details in the Composite Architecture Elements section.
+
+\section{Findings}
+
+TBD
+
+\subsection{Anthropomorphized Perceptions}
 
@@
 \toprule
- & \textbf{Measure}   & \textbf{Contains}                                  & \textbf{No. Papers} \\ \midrule
-\multirow{3}{*}{\textbf{Perception of Interaction with an Agent}}    & Usability       & accuracy, ease of use, efficiency, helpfulness & 23 \\
+\textbf{Category} & \textbf{Theme}   & \textbf{Sample Codes}                                  & \textbf{No. Papers} \\ \midrule
+\multirow{3}{*}{Perception of Interaction with Agent}    & Usability       & accuracy, ease of use, efficiency, helpfulness & 23 \\
  & Engagement         & enjoyment, annoyance, desirable, intention to use  & 28         \\
  & Satisfaction       & service satisfaction, quality of interaction       & 12         \\ \midrule
-\multirow{3}{*}{\textbf{Perception of Agent's Ability}}              & Intelligence    & knowledgeable, intelligent, expertise                             & 11 \\
+\multirow{3}{*}{Perception of Agent's Ability}              & Intelligence    & knowledgeable, intelligent, expertise                             & 11 \\
  & Competence         & competent, capable                                 & 4          \\
  & Trust              & credibility, trustworthy, truthfulness, confidence & 15         \\ \midrule
-\multirow{3}{*}{\textbf{Perception of Social Connection with Agent}} & Social Presence & connectedness, familiarity, similarity, psychological distance    & 18 \\
- & Conversation Tone  & appropriate, expressive, empathetic, persuasive    & 13         \\
+\multirow{3}{*}{Perception of Social Connection with Agent}  & Conversation Tone  & appropriate, expressive, empathetic, persuasive    & 13 \\
+ & Social Presence & connectedness, familiarity, similarity, psychological distance    & 18        \\
  & Intimacy           & intimate, rapport, quality of relationship         & 7          \\ \midrule
-\multirow{2}{*}{\textbf{Perception of Agent's Humanness}}            & Human-likeness  & human-like, natural, artificial, machine-like                     & 20 \\
+\multirow{2}{*}{Perception of Agent's Humanness}            & Human-likeness  & human-like, natural, artificial, machine-like                     & 20 \\
  & Personality Traits & friendly, kind, warm, creepy, likeable, polite     & 27         \\ \bottomrule
@@
 
-%\multirow{3}{*}{\parbox{2cm}{\textbf{Perception of Interaction with an Agent}}} & Usability & accuracy, ease of use, efficiency, helpfulness &
-
-%Usability
-%\cite{linnemann2018can}\cmt{[15]}\cite{huiyang2022improving}\cmt{[17]}\cite{spillner2021talk}\cmt{[18]}\cite{kim2020can}\cmt{[24]}\cite{wilhelm2022keep}\cmt{[28]}\cite{ma2022ask}\cmt{[29]}\cite{healey2013relating}\cmt{[39]}\cite{miehle2018exploring}\cmt{[51]}\cite{choi2020nobody}\cmt{[54]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{elsholz2019exploring}\cmt{[61]}\cite{habler2019effects}\cmt{[63]}\cite{kraus2020effects}\cmt{[64]}\cite{cuadra2021my}\cmt{[67]}\cite{roy2021users}\cmt{[71]}\cite{chan2021kinvoices}\cmt{[74]}\cite{hu2022polite}\cmt{[76]}\cite{ceha2022expressive}\cmt{[77]}\cite{haas2022keep}\cmt{[78]}\cite{jestin2022effects}\cmt{[81]}\cite{misu2011toward}\cmt{[83]}\cite{ashktorab2019resilient}\cmt{[88]}\cite{kim2019comparing}\cmt{[89]}
-
-%Engagement
-%\cite{linnemann2018can}\cmt{[15]}\cite{huiyang2022improving}\cmt{[17]}\cite{spillner2021talk}\cmt{[18]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{lee2020hear}\cmt{[23]}\cite{kim2020can}\cmt{[24]}\cite{zhu2022effects}\cmt{[26]}\cite{cox2022does}\cmt{[27]}\cite{ma2022ask}\cmt{[29]}\cite{andrews2012system}\cmt{[38]}\cite{healey2013relating}\cmt{[39]}\cite{miyamoto2017improving}\cmt{[46]}\cite{miehle2018exploring}\cmt{[51]}\cite{fadhil2018effect}\cmt{[52]}\cite{ceha2021can}\cmt{[57]}\cite{elsholz2019exploring}\cmt{[61]}\cite{cuadra2021my}\cmt{[67]}\cite{volkel2021examining}\cmt{[69]}\cite{roy2021users}\cmt{[71]}\cite{yang2021effect}\cmt{[72]}\cite{xiao2021let}\cmt{[73]}\cite{chan2021kinvoices}\cmt{[74]}\cite{volkel2022user}\cmt{[75]}\cite{ceha2022expressive}\cmt{[77]}\cite{go2021conversational}\cmt{[80]}\cite{jestin2022effects}\cmt{[81]}\cite{moilanen2022measuring}\cmt{[82]}\cite{kim2019comparing}\cmt{[89]}
-
-%Satisfaction                                                                 
-%\cite{pfeifer2009should}\cmt{[12]}\cite{gnewuch2018faster}\cmt{[19]}\cite{diederich2019emulating}\cmt{[25]}\cite{wilhelm2022keep}\cmt{[28]}\cite{ma2022ask}\cmt{[29]}\cite{hoegen2019end}\cmt{[31]}\cite{yang2017perceived}\cmt{[44]}\cite{choi2020nobody}\cmt{[54]}\cite{elsholz2019exploring}\cmt{[61]}\cite{habler2019effects}\cmt{[63]}\cite{roy2021users}\cmt{[71]}\cite{hu2022polite}\cmt{[76]}\cite{ceha2022expressive}\cmt{[77]}
-
-Categorization of social cues \newline
-* adapted from Taxonomy of social cues
-* added a middle layer
-* combined elements as we are studying disembodied agents
-
-\section{Conversation Architecture}
-
-Here is Table \ref{tab:cues} for conversation architecture elements.
-
-\begin{table*}[]
+As shown in Table \ref{tab:perceptions}, there are four organizing themes defined for the anthropomorphized perceptions of conversational agents covering 11 basic themes of perception.
+The details of each theme are discussed below.
+
+\textbf{Perception of interaction with a CA} evaluates the overall interaction quality users had with the conversational agent.
+The three basic themes for this perceptions are usability, engagement and satisfaction.
+\textit{Usability} measures the utilitarian aspects of the interaction, whether it was accurate, easy to use, efficient or helpful.
+Some commonly used methods to measure usability include the response accuracy portion of the SASSI questionnaire \cite{hone2000towards}\cmt{sassi}, or the NASA Task Load Index (NASA-TLX) \cite{hart1988development}\cmt{nasa} to measure cognitive workload.
+Questions such as "the system is easy to use" or "it is easy to understand the agent" are also measures of usability.
+\textit{Engagement} on the other hand measures users' emotional reactions, whether they have enjoyed the conversation with CA, or annoyed or frustrated with the interaction.
+Some commonly used methods to measure engagement include  the annoyance portion of the SASSI questionnaire \cite{hone2000towards}\cmt{sassi}, and the Use Engagement Scale (UES) \cite{o2018practical}\cmt{ues}.
+Questions such as "I enjoyed using the system" or "I felt frustrated with the agent" are also measures of engagement.
+Lastly, \textit{Satisfaction} measures users' overall satisfaction interacting with the agent.
+Questions such as "the overall assessment of conversing with the CA was satisfactory" are used to measure this perception.
+
+\textbf{Perception of a CA's ability} evaluates the perceived capabilities of the agent.
+While there are some elements of system performance in this measure, the main aspect we are interested in is the perception differences for agents with identify system capabilities but with different architecture elements.
+Specifically, \textit{intelligence} measures the agent's expertise and knowledge, and it is commonly administered through the Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed} on the set of questions related to perceived intelligence.
+Also survey questions such as asking users about the agent's intelligence and domain knowledge are used to measure perceived intelligence.
+\textit{Competence} takes intelligence one step further by evaluating the agent's ability to put its intelligence into practice.
+To measure a CA's competence, there are usually surveys or qualitative feedback that the agent is capable and competent, and that the users have confidence in the agent's ability to get the job done.
+Lastly, \textit{trust} evaluates agent's truthfulness, credibility and benevolence.
+Some commonly used methods to evaluate trust include the Trust Propensity Scale \cite{mayer1999effect} and the Individualized Trust Scale (ITS) \cite{wheeless1977measurement}.
+Questions such as "is the agent honest" and "can I trust the agent with sensitive information" are also measures of trust.
+
+\textbf{Perception of the social connection with a CA} evaluates the emotional connections that users have with agents.
+The three basic themes of conversation tone, social presence and intimacy are included in this category.
+\textit{Conversation tone} measure the affective impression of the agent's tone, such as empathy, expressiveness, or passionate.
+Also, it measures whether the tone used by the agent is persuasive or appropriate for the conversation.
+\textit{Social presence} measures the sense of connectness and psychological distance users has with an agent.
+Some aspects in this measure include a sense of familiarity or similarity with the agent, whether users feel the agent behaves like them or have similar attitudes to them.
+The measure of \textit{Intimacy} extends social presence into the realm of the quality of relationships with an agent.
+Some commonly used measures include the set of social attraction questions from the interpersonal attraction questionnaire \cite{mccroskey1975development} and the quality of relationship inventory (QRI) \cite{pierce1997assessing}.
+These questionnaires include questions like "I think the agent could be a friend of mine", or "I feel we could establish a personal relationship with each other".
+
+\textbf{Perception of a CA's humanness} evaluates human-likeness and the anthropomorphized personality traits that users assign to agents.
+\textit{Human-likeness} measures whether the agent presented itself as natural and human-like, or artificial and machine-like.
+The Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed} set of questions related to anthropomorphism and the Ascent of Man scale \cite{kteily2015ascent} are commonly used methods to assess human-likeness.
+Survey questions with semantic scales such as "human-like / machine-like" and "artificial / natural" are also used for this perception.
+\textit{Personality traits} captures the human characteristics that are attributes to the agent, such as warm, friendly, likeable, and polite.
+This is commonly captured in the qualitative feedback from users, commenting on whether the agent is extroverted or introverted, or the human characteristics they perceive the agent such as funny or witty.
+Some studies used the measure of the Big-5 personality traits \cite{gosling2003very} to map an agent's disposition on various personality dimensions.
+
+Overall there is good coverage of perception measures based on the list of papers reviewed in our corpus.
+The most commonly measured perceptions are related to the interaction with agent, followed by the perception of agent's humanness.
+There are two basic themes that are the least measured compared to the others: competence under the perception of agent's ability, and intimacy under the perception of social connection with agent.
+This may be due to the controlled lab settings for the experiments, where participants are given the scenarios for interaction.
+This environment is not conducive to forming relationships with a conversational partner, as noted by Linnerman et al.
+in their discussions \cite{linnemann2018can}\cmt{[15]}.
+Also, the same factor could impact the assessment of agent's abilities, as the users may not feel like they have the expertise to assess an agent's competence.
+These factors could contribute to the reasons why competency and intimacy are not as frequently measured in experimental studies.
+
+% Add citations
+
+\subsection{Conversation Architecture Elements}
+
+As shown in Table \ref{tab:cues}, there are three categories defined for the conversation architecture elements covering 10 different themes.
+The details of each category and theme are discussed below.
+
+The category of \textbf{linguistic content} maps to the content category under verbal cues in Feine et al's taxonomy, which refers to elements expressed with written or spoken words that are related to the strict and literal meaning of a message (i.e.
+what is said) \cite{feine2019taxonomy}.
+The theme of \textit{affective language} captures the injection of emotional words or phrases into the agent's utterance, such as affective expressions \cite{seeger2021chatbots}\cmt{[35]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}, sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}, and encouraging words \cite{healey2013relating}\cmt{[39]}.
+\textit{Social talk} captures non-task related conversations with the user to build social connection, such as self-disclosure \cite{lee2020hear}\cmt{[23]} and social dialogue \cite{volkel2021manipulating}\cmt{[68]}\cite{lubold2016effects}\cmt{[86]}.
+The theme of \textit{humour} is similar to social talk but specific to CA's attempt to include jokes in its utterances.
+The separation of social talk and humor is based on findings from previous research, where user's attitude towards humour is different between human-human conversations vs.
+human-agent conversations \cite{clark2019makes}.
+We would like to capture the relationship between humour and agent perceptions differently from social talk.
+Lastly, the theme of \textit{agent-initiated content} captures utterances that are driven by the agent without direct prompts from the user.
+This elements in this theme include conversation repairs \cite{cuadra2021my}\cmt{[67]}\cite{ashktorab2019resilient}\cmt{[88]} and proactive content like eliciting feedback \cite{xiao2021let}\cmt{[73]}.
+
+The category of \textbf{linguistic style} maps to the style category under verbal cues in Feine et al's taxonomy, which refers to elements expressed with written or spoken words that are related to the meaningful deployment of language variation in a message (i.e.
+how something is said) \cite{feine2019taxonomy}.
+The theme of \textit{formality} describes the language style used by the conversational agent, whether it is formal vs.
+casual, such as using honorific expressions to address users \cite{ouchi2019should}\cmt{[59]}.
+\textit{Alignment} captures the degree that the agent aligns its utterances to the users, such as lexical alignment on the content and structural of the sentences \cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}, as well as agreement with the user \cite{volkel2021examining}\cmt{[69]}.
+\textit{Elaborateness} captures the sentence complexity and length of the utterances.
+For example, Roy et al.
+explored the differences in perception for variations in elaborateness such as "Cloudly, possibility of snow, high: 4, low: -10" vs "Today will be cloudy, with a high of 4 and a low of -10.
+Snow is predicted" \cite{roy2021users}\cmt{[71]}.
+Lastly, the category of \textit{disfluency} captures tye style of using non-lexical utterances like filler words ("um, uh") \cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}, or repetition of words within a sentence \cite{yang2021effect}\cmt{[72]}.
+
+Lastly, the category of \textbf{non-linguistic format} maps loosely to the elements in auditory and invisible categories in Feine et al's taxonomy \cite{feine2019taxonomy}.
+These are auditory or textual variations in the presentation of the agent's utterances.
+In the theme of \textit{prosodic cue}, it captures vocal qualities like gender of voice \cite{habler2019effects}\cmt{[63]}\cite{jestin2022effects}\cmt{[81]}, and speech rate \cite{choi2020nobody}\cmt{[54]}.
+\textit{Text variations} include different formats that text-based agents use to present information to users, like emoticons \cite{kim2019comparing}\cmt{[89]}\cite{wilhelm2022keep}\cmt{[28]}, typos \cite{westerman2019believe}\cmt{[9]}, and response delays \cite{gnewuch2022opposing}\cmt{[20]}\cite{seeger2021chatbots}\cmt{[35]}.
+
+Overall the spread of conversation architecture elements relevant to anthropomorphized perceptions are evenly distributed across linguistic content, linguistic style, and non-linguistic format.
+Looking at the different themes, there is good coverage of studies on the impact of affective language and prosodic cues on anthropomorphized perceptions.
+However, it seemed like there is a lack of studies exploring the effect of agent-initiative content on the perception of agents.
+There are various existing literature on this theme such as conversation repairs \cite{komatani2010online}\cite{reinkemeier2022repair} and agent proactively sharing content with users \cite{dubiel2019inquisitive}\cite{zargham2022understanding}, but they were not included in this systematic literature review because they did not have measures of anthropomorphized perceptions of the CA.
+This may be because conversations with CAs have historically being driven by the user, with some recent effort to understand the opportunities to be more proactive \cite{cowan2023introduction}, as existing research are focused on the functional aspects of designing an agent instead of exploring into the anthropomorphized perceptions.
+
+\begin{table*}[h]
 %\resizebox{\textwidth}{!}{%
@@
 \toprule
- & \textbf{Measure}      & \textbf{Contains}                                      & \multicolumn{1}{l}{\textbf{No. Papers}} \\ \midrule
-\multirow{4}{*}{\textbf{Linguistic Content}}    & Affective Language & emotional expressions, sentiment-adaptive responses & 11 \\
+ \textbf{Category} & \textbf{Theme}      & \textbf{Sample Codes}                                      & \multicolumn{1}{l}{\textbf{No. Papers}} \\ \midrule
+\multirow{4}{*}{Linguistic Content}    & Affective Language & emotional expressions, sentiment-adaptive responses & 11 \\
  & Social Talk           & self-disclosure, social dialogue                       & 7                                       \\
@@
  & Agent-Initiated Content & elicit user feedback, proactivity, conversation repair & 4                                       \\ \midrule
-\multirow{4}{*}{\textbf{Linguistic Style}}      & Formality          & formal vs. casual, honorific expressions                               & 9  \\
+\multirow{4}{*}{Linguistic Style}     & Formality          & formal vs. casual, honorific expressions                               & 9  \\
  & Alignment             & content matching, lexical alignment, agreeableness     & 7                                       \\
  & Elaborateness         & elaborate, concise, sentence structure                 & 6                                       \\
- & Disfluency            & fillers, interjections, repetitions                    & 5                                       \\ \midrule
-\multirow{3}{*}{\textbf{Non-Linguistic Format}} & Prosody            & pitch, intonation, speech rate, spoken accent                          & 12 \\
- & Text Variation        & typo, capitalization, response delay, typing indicator & 5                                       \\
- & Emotional Cue         & emoticons, laughter                                    & 6                                       \\ \bottomrule
+ & Disfluency            & fillers, interjections, repetitions                    & 6                                       \\ \midrule
+\multirow{2}{*}{Non-Linguistic Format}     & Prosodic Cue            & pitch, intonation, speech rate, spoken accent                          & 12 \\
+ & Text Variation        & typo, capitalization, emoticons, response delay & 9                                         \\ \bottomrule 
 \end{tabular}%
@@
 
+\subsection{Relationship Between Anthropomorphized Perceptions and Conversation Architecture Elements}
+
 \section{Framework}
@@
 
-\begin{figure*}[h]
+While the number of papers studying voice (n=27) vs.
+text (n=30) modalities is not significantly different, there are some interesting trends in the perceptions studied for CAs with different modalities.
+Overall, there are less perceptions of agent studied for text-based agents (n=101) as compared to voice-based agents (n=163).
+
+This is especially evident in the perception of social connection with agent and perception of agent's humanness.
+For the perception of social connection with a CA, there are only 19 perceptions measured for text-based agents, while there are 35 perceptions measured for voice-based agents.
+Similarly for perception of agent's humanness, there are 36 perceptions measured for text-based agents, as compared to 52 perceptions of voice-based agents.
+This highlights that there is a
+
+\begin{figure*}[]
   \centering
-  \includegraphics[width=\textwidth]{fig:heatmap-impact.png}
+  \includegraphics[width=\textwidth]{fig-heatmap-impact.png}
   \caption{Heatmap of literature for perception of conversational agents for each type of conversational architecture element.}
@@
 \section{Discussions}
+
+%Research challenges and opportunities
+
+%Ethical considerations
+
+%Limitations and future work
 

### 2023-02-12 paper.tex
first draft up to findings; updated perception table

@@
 \usepackage{booktabs}
+\usepackage{makecell}
 
@@
 
-\section{Introduction}
+\section{Introduction (Not Ready)}
 
@@
 
-\subsection{Search Procedure}
+\subsection{Data Collection}
 
@@
 
-\begin{mdframed}
-"conversational agent" OR "natural language interface" OR "IPA" OR "intelligent personal assistant" OR "chatbot" OR "speech interface" OR "voice assistant" OR "intelligent agent" OR "human-chatbot communication" OR "virtual agent" OR "dialog* system" OR "voice user interface" OR "human computer dialog*"
-\end{mdframed}
-
-\subsection{Selection Criteria}
+\textit{"conversational agent" OR "natural language interface" OR "IPA" OR "intelligent personal assistant" OR "chatbot" OR "speech interface" OR "voice assistant" OR "intelligent agent" OR "human-chatbot communication" OR "virtual agent" OR "dialog* system" OR "voice user interface" OR "human computer dialog*"}
+\newline
+
 The initial query retrieved 2901 unique publications. The following selection criteria are applied to identify literature related to the effect of conversational architecture on perception of agents:
@@
   \centering
-  \includegraphics[width=0.6\columnwidth]{fig-prisma.png}
+  \includegraphics[width=1\columnwidth]{fig-prisma.png}
   \caption{Literature search using PRISMA guidelines}
@@
 The vast majority of the papers in our corpus were published in conference proceedings (n=50), with the remainder papers published in journals.
-Out of the papers published in conferences, the top conferences were The ACM Conference on Human Factors in Computing Systems (n=16), Conversational User Interfaces (n=7), Human-Agent Interaction (n=4), and Intelligent Virtual Agents (n=4).
-Out of the papers published in journals, some venues include the International Journal of Human-Computer Interaction (n=2) and Interacting with Computers (n=1).
+Out of the papers published in conferences, the top conferences were The ACM Conference on Human Factors in Computing Systems\footnote{https://dl.acm.org/conference/chi} (n=16), Conversational User Interfaces\footnote{https://dl.acm.org/conference/cui} (n=7), Human-Agent Interaction\footnote{https://dl.acm.org/conference/hai} (n=4), and Intelligent Virtual Agents\footnote{https://dl.acm.org/conference/iva} (n=4).
+%Out of the papers published in journals, some venues include the International Journal of Human-Computer Interaction\footnote{https://www.tandfonline.com/journals/hihc20} (n=2) and Interacting with Computers\footnote{https://academic.oup.com/iwc} (n=1).
 
@@
 
-\begin{figure*}[h]
+\begin{figure}[h]
   \centering
-  \includegraphics[width=\textwidth]{fig-paper.png}
-  \caption{Stacked barchart of number of papers by year and venue}
+  \includegraphics[width=\columnwidth]{fig-paper.png}
+  \caption{Number of papers by year}
   \label{fig:paper}
-\end{figure*}
+\end{figure}
 
@@
 
-\subsubsection*{Anthropomorphized Perceptions}
-The exact quotes of anthropomorphized perception measurements were extracted from each paper.
+\subsubsection*{Anthropomorphized Perceptions} To study RQ1, the exact quotes of anthropomorphized perception measurements were extracted from each paper.
 Inductive thematic analysis was used to group these verbatim quotes into codes based on their meanings.
@@
 \subsubsection*{Conversation Architecture Elements}
-The conversation architecture elements used in the study were extracted from each paper.
+The study RQ2, the conversation architecture elements used in the study were extracted from each paper.
 Some of the papers were applying multiple elements to the CA design, such as the the anthropomorphic design used in this study \cite{seeger2021chatbots}\cmt{[35]}.
@@
 \subsubsection*{Relationship Between Anthropomorphized Perceptions and Conversation Architecture Elements}
-Based on the codes developed for anthropomorphized perceptions and conversation architecture elements above, we extracted the relationships between perceptions and architecture elements from each paper, noting whether the architecture element had an impact of on the perceptions.
+For RQ3, we extracted the relationships between perceptions and architecture elements from each paper based on the codes developed for anthropomorphized perceptions and conversation architecture elements above, noting whether the architecture element had an impact of on the perceptions.
 Out of the 57 papers, 264 connections between anthropomorphized perceptions and conversation architecture elements were found.
@@
 \subsection{Anthropomorphized Perceptions}
+
+\begin{table*}[ht]
+\renewcommand*{\arraystretch}{1.4}
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{@{}p{3.1cm} | p{2cm} | p{4cm} | p{1.5cm} | p{6cm} @{}}
+%!{\vrule width 1.2pt} 
+\Xhline{1.2pt}
+\textbf{Category} & \textbf{Theme} & \textbf{Sample Codes} & \textbf{No. Papers} & \textbf{Papers} 
+\\ \Xhline{1.2pt}
+\multirow{3}{*}{\parbox{3cm}{Perception of Interaction with Agent}}
+    & Usability & accuracy, ease of use, efficiency, helpfulness & 23 
+    & \cite{ashktorab2019resilient}\cmt{[88]}
+    \cite{ceha2022expressive}\cmt{[77]}
+    \cite{chan2021kinvoices}\cmt{[74]}
+    \cite{choi2020nobody}\cmt{[54]}
+    \cite{cuadra2021my}\cmt{[67]}
+    \cite{dubiel2020persuasive}\cmt{[60]}
+    \cite{elsholz2019exploring}\cmt{[61]}
+    \cite{haas2022keep}\cmt{[78]}
+    \cite{habler2019effects}\cmt{[63]}
+    \cite{healey2013relating}\cmt{[39]}
+    \cite{hu2022polite}\cmt{[76]}
+    \cite{huiyang2022improving}\cmt{[17]}
+    \cite{jestin2022effects}\cmt{[81]}
+    \cite{kim2019comparing}\cmt{[89]}
+    \cite{kim2020can}\cmt{[24]}
+    \cite{kraus2020effects}\cmt{[64]}
+    \cite{linnemann2018can}\cmt{[15]}
+    \cite{ma2022ask}\cmt{[29]}
+    \cite{miehle2018exploring}\cmt{[51]}
+    \cite{misu2011toward}\cmt{[83]}
+    \cite{roy2021users}\cmt{[71]}
+    \cite{spillner2021talk}\cmt{[18]}
+    \cite{wilhelm2022keep}\cmt{[28]}
+\\ \cline{2-5}
+    & Engagement & enjoyment, annoyance, desirable, intention to use  & 28
+    & \cite{andrews2012system}\cmt{[38]}
+    \cite{ceha2022expressive}\cmt{[77]}
+    \cite{ceha2021can}\cmt{[57]}
+    \cite{chan2021kinvoices}\cmt{[74]}
+    \cite{cox2022does}\cmt{[27]}
+    \cite{cuadra2021my}\cmt{[67]}
+    \cite{elsholz2019exploring}\cmt{[61]}
+    \cite{fadhil2018effect}\cmt{[52]}
+    \cite{gnewuch2022opposing}\cmt{[20]}
+    \cite{go2021conversational}\cmt{[80]}
+    \cite{healey2013relating}\cmt{[39]}
+    \cite{huiyang2022improving}\cmt{[17]}
+    \cite{jestin2022effects}\cmt{[81]}
+    \cite{kim2020can}\cmt{[24]}
+    \cite{kim2019comparing}\cmt{[89]}
+    \cite{lee2020hear}\cmt{[23]}
+    \cite{linnemann2018can}\cmt{[15]}
+    \cite{ma2022ask}\cmt{[29]}
+    \cite{miehle2018exploring}\cmt{[51]}
+    \cite{miyamoto2017improving}\cmt{[46]}
+    \cite{moilanen2022measuring}\cmt{[82]}
+    \cite{roy2021users}\cmt{[71]}
+    \cite{spillner2021talk}\cmt{[18]}
+    \cite{volkel2021examining}\cmt{[69]}
+    \cite{volkel2022user}\cmt{[75]}
+    \cite{xiao2021let}\cmt{[73]}
+    \cite{yang2021effect}\cmt{[72]}
+    \cite{zhu2022effects}\cmt{[26]}    
+\\ \cline{2-5}
+    & Satisfaction & service satisfaction, quality of interaction & 12
+    & \cite{ceha2022expressive}\cmt{[77]}
+    \cite{choi2020nobody}\cmt{[54]}
+    \cite{diederich2019emulating}\cmt{[25]}
+    \cite{elsholz2019exploring}\cmt{[61]}
+    \cite{habler2019effects}\cmt{[63]}
+    \cite{gnewuch2018faster}\cmt{[19]}
+    \cite{hoegen2019end}\cmt{[31]}
+    \cite{hu2022polite}\cmt{[76]}
+    \cite{ma2022ask}\cmt{[29]}
+    \cite{roy2021users}\cmt{[71]}
+    \cite{wilhelm2022keep}\cmt{[28]}
+    \cite{yang2017perceived}\cmt{[44]}
+\\ \Xhline{1.2pt} 
+\multirow{3}{*}{\parbox{3cm}{Perception of Agent's Ability}}
+    & Intelligence & knowledgeable, intelligent, expertise & 11
+    & \cite{ashktorab2019resilient}\cmt{[88]}
+    \cite{ceha2021can}\cmt{[57]}
+    \cite{chan2021kinvoices}\cmt{[74]}
+    \cite{cuadra2021my}\cmt{[67]}
+    \cite{dubiel2020persuasive}\cmt{[60]}
+    \cite{feijoo2021effects}\cmt{[70]}
+    \cite{hu2021enhancing}\cmt{[56]}
+    \cite{jeong2019exploring}\cmt{[10]}
+    \cite{spillner2021talk}\cmt{[18]}
+    \cite{volkel2022user}\cmt{[75]}
+    \cite{yang2017perceived}\cmt{[44]} 
+\\ \cline{2-5}
+    & Competence & competent, capable & 4 
+    & \cite{cox2022does}\cmt{[27]}
+    \cite{kraus2020effects}\cmt{[64]}
+    \cite{lee2019s}\cmt{[55]}
+    \cite{westerman2019believe}\cmt{[9]}
+\\ \cline{2-5}
+    & Trust & credibility, trustworthy, truthfulness, confidence & 15
+    & \cite{andrews2012system}\cmt{[38]}
+    \cite{chan2021kinvoices}\cmt{[74]}
+    \cite{dubiel2020persuasive}\cmt{[60]}
+    \cite{fadhil2018effect}\cmt{[52]}
+    \cite{healey2013relating}\cmt{[39]}
+    \cite{hoegen2019end}\cmt{[31]}
+    \cite{huiyang2022improving}\cmt{[17]}
+    \cite{jestin2022effects}\cmt{[81]}
+    \cite{kraus2020effects}\cmt{[64]}
+    \cite{lee2020hear}\cmt{[23]}
+    \cite{linnemann2018can}\cmt{[15]}
+    \cite{ma2022ask}\cmt{[29]}
+    \cite{seeger2021chatbots}\cmt{[35]}
+    \cite{tolmeijer2021female}\cmt{[62]}
+    \cite{wilhelm2022keep}\cmt{[28]}    
+\\ \Xhline{1.2pt} 
+\multirow{3}{*}{\parbox{3cm}{Perception of Social Connection with Agent}}
+    & Conversation Tone & appropriate, expressive, empathetic, persuasive & 13 
+    & \cite{chan2021kinvoices}\cmt{[74]}
+    \cite{cox2022does}\cmt{[27]}
+    \cite{cuadra2021my}\cmt{[67]}
+    \cite{daher2020empathic}\cmt{[58]}
+    \cite{diederich2019emulating}\cmt{[25]}
+    \cite{dubiel2020persuasive}\cmt{[60]}
+    \cite{hu2021enhancing}\cmt{[56]}
+    \cite{jestin2022effects}\cmt{[81]}
+    \cite{misu2011toward}\cmt{[83]}
+    \cite{tolmeijer2021female}\cmt{[62]}
+    \cite{yang2021effect}\cmt{[72]}
+    \cite{yang2017perceived}\cmt{[44]}
+    \cite{zhu2022effects}\cmt{[26]}           
+\\ \cline{2-5}
+    & Social Presence & connectedness, familiarity, similarity, psychological distance & 18
+    & \cite{ceha2022expressive}\cmt{[77]}
+    \cite{ceha2021can}\cmt{[57]}
+    \cite{chan2021kinvoices}\cmt{[74]}
+    \cite{choi2020nobody}\cmt{[54]}
+    \cite{cuadra2021my}\cmt{[67]}
+    \cite{diederich2019emulating}\cmt{[25]}
+    \cite{gnewuch2018faster}\cmt{[19]}
+    \cite{gnewuch2018chatbot}\cmt{[21]}
+    \cite{gnewuch2022opposing}\cmt{[20]}
+    \cite{go2021conversational}\cmt{[80]}
+    \cite{khooshabeh2011does}\cmt{[37]}
+    \cite{kim2020can}\cmt{[24]}
+    \cite{lee2019s}\cmt{[55]}
+    \cite{lubis2019positive}\cmt{[43]}
+    \cite{lubold2016effects}\cmt{[86]}
+    \cite{ma2022ask}\cmt{[29]}
+    \cite{niewiadomski2013laugh}\cmt{[85]}
+    \cite{westerman2019believe}\cmt{[9]}    
+\\ \cline{2-5}
+    & Intimacy & intimate, rapport, quality of relationship & 7 
+    & \cite{choi2020nobody}\cmt{[54]}
+    \cite{khooshabeh2011does}\cmt{[37]}
+    \cite{kim2020can}\cmt{[24]}
+    \cite{lee2020hear}\cmt{[23]}
+    \cite{linnemann2018can}\cmt{[15]}
+    \cite{lubold2016effects}\cmt{[86]}
+    \cite{westerman2019believe}\cmt{[9]}
+\\ \Xhline{1.2pt}
+\multirow{2}{*}{\parbox{3cm}{Perception of Agent's Humanness}}
+    & Human-likeness & human-like, natural, artificial, machine-like & 20
+    & \cite{ashktorab2019resilient}\cmt{[88]}
+    \cite{ceha2021can}\cmt{[57]}
+    \cite{chan2021kinvoices}\cmt{[74]}
+    \cite{choi2020nobody}\cmt{[54]}
+    \cite{cox2022does}\cmt{[27]}
+    \cite{diederich2019emulating}\cmt{[25]}
+    \cite{gnewuch2018faster}\cmt{[19]}
+    \cite{haas2022keep}\cmt{[78]}
+    \cite{hu2022polite}\cmt{[76]}
+    \cite{jeong2019exploring}\cmt{[10]}
+    \cite{jestin2022effects}\cmt{[81]}
+    \cite{lubis2019positive}\cmt{[43]}
+    \cite{ma2022ask}\cmt{[29]}
+    \cite{misu2011toward}\cmt{[83]}
+    \cite{niewiadomski2013laugh}\cmt{[85]}
+    \cite{ouchi2019should}\cmt{[59]}
+    \cite{seeger2021chatbots}\cmt{[35]}
+    \cite{wester2015artificial}\cmt{[14]}
+    \cite{westerman2019believe}\cmt{[9]}
+    \cite{zhu2022effects}\cmt{[26]}    
+\\ \cline{2-5}
+    & Personality Traits & friendly, kind, warm, creepy, likeable, polite & 27
+    & \cite{andrews2012system}\cmt{[38]}
+    \cite{ashktorab2019resilient}\cmt{[88]}
+    \cite{ceha2022expressive}\cmt{[77]}
+    \cite{ceha2021can}\cmt{[57]}
+    \cite{chan2021kinvoices}\cmt{[74]}
+    \cite{cox2022does}\cmt{[27]}
+    \cite{cuadra2021my}\cmt{[67]}
+    \cite{haas2022keep}\cmt{[78]}
+    \cite{habler2019effects}\cmt{[63]}
+    \cite{healey2013relating}\cmt{[39]}
+    \cite{hu2022polite}\cmt{[76]}
+    \cite{huiyang2022improving}\cmt{[17]}
+    \cite{jeong2019exploring}\cmt{[10]}
+    \cite{jestin2022effects}\cmt{[81]}
+    \cite{khooshabeh2011does}\cmt{[37]}
+    \cite{kim2019comparing}\cmt{[89]}
+    \cite{lee2019s}\cmt{[55]}
+    \cite{lee2020hear}\cmt{[23]}
+    \cite{linnemann2018can}\cmt{[15]}
+    \cite{miehle2018exploring}\cmt{[51]}
+    \cite{moilanen2022measuring}\cmt{[82]}
+    \cite{ouchi2019should}\cmt{[59]}
+    \cite{tolmeijer2021female}\cmt{[62]}
+    \cite{volkel2021manipulating}\cmt{[68]}
+    \cite{volkel2022user}\cmt{[75]}
+    \cite{wester2015artificial}\cmt{[14]}
+    \cite{zhu2022effects}\cmt{[26]} 
+\\ \Xhline{1.2pt}
+\end{tabular}%
+}
+\caption{Perception measures}
+\label{tab:perceptions}
+\end{table*}
+
+As shown in Table \ref{tab:perceptions}, there are four organizing themes defined for the anthropomorphized perceptions of conversational agents covering 11 basic themes of perception.
+The details of each theme are discussed below.
+
+\textbf{Perception of interaction with agent} evaluates the overall interaction quality users had with the conversational agent.
+The three basic themes for this perceptions are usability, engagement and satisfaction.
+\textit{Usability} measures the utilitarian aspects of the interaction, whether it was accurate, easy to use, efficient or helpful.
+Some commonly used methods to measure usability include the response accuracy portion of the SASSI questionnaire \cite{hone2000towards}\cmt{sassi}, or the NASA Task Load Index (NASA-TLX) \cite{hart1988development}\cmt{nasa} to measure cognitive workload.
+Questions such as "the system is easy to use" or "it is easy to understand the agent" are also measures of usability.
+\textit{Engagement} on the other hand measures users' emotional reactions, whether they have enjoyed the conversation with CA, or annoyed or frustrated with the interaction.
+Some commonly used methods to measure engagement include  the annoyance portion of the SASSI questionnaire \cite{hone2000towards}\cmt{sassi}, and the Use Engagement Scale (UES) \cite{o2018practical}\cmt{ues}.
+Questions such as "I enjoyed using the system" or "I felt frustrated with the agent" are also measures of engagement.
+Lastly, \textit{Satisfaction} measures users' overall satisfaction interacting with the agent.
+Questions such as "the overall assessment of conversing with the CA was satisfactory" are used to measure this perception.
+
+\textbf{Perception of agent's ability} evaluates the perceived capabilities of the agent.
+While there are some elements of system performance in this measure, the main aspect we are interested in is the perception differences for agents with identify system capabilities but with different architecture elements.
+Specifically, \textit{intelligence} measures the agent's expertise and knowledge, and it is commonly administered through the Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed} on the set of questions related to perceived intelligence.
+Also survey questions such as asking users about the agent's intelligence and domain knowledge are used to measure perceived intelligence.
+\textit{Competence} takes intelligence one step further by evaluating the agent's ability to put its intelligence into practice.
+To measure a CA's competence, there are usually surveys or qualitative feedback that the agent is capable and competent, and that the users have confidence in the agent's ability to get the job done.
+Lastly, \textit{trust} evaluates agent's truthfulness, credibility and benevolence.
+Some commonly used methods to evaluate trust include the Trust Propensity Scale \cite{mayer1999effect} and the Individualized Trust Scale (ITS) \cite{wheeless1977measurement}.
+Questions such as "is the agent honest" and "can I trust the agent with sensitive information" are also measures of trust.
+
+\textbf{Perception of the social connection with agent} evaluates the emotional connections that users have with agents.
+The three basic themes of conversation tone, social presence and intimacy are included in this category.
+\textit{Conversation tone} measure the affective impression of the agent's tone, such as empathy, expressiveness, or passionate.
+Also, it measures whether the tone used by the agent is persuasive or appropriate for the conversation.
+\textit{Social presence} measures the sense of connectness and psychological distance users has with an agent.
+Some aspects in this measure include a sense of familiarity or similarity with the agent, whether users feel the agent behaves like them or have similar attitudes to them.
+The measure of \textit{Intimacy} extends social presence into the realm of the quality of relationships with an agent.
+Some commonly used measures include the set of social attraction questions from the interpersonal attraction questionnaire \cite{mccroskey1975development} and the quality of relationship inventory (QRI) \cite{pierce1997assessing}.
+These questionnaires include questions like "I think the agent could be a friend of mine", or "I feel we could establish a personal relationship with each other".
+
+\textbf{Perception of agent's humanness} evaluates human-likeness and the anthropomorphized personality traits that users assign to agents.
+\textit{Human-likeness} measures whether the agent presented itself as natural and human-like, or artificial and machine-like.
+The Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed} set of questions related to anthropomorphism and the Ascent of Man scale \cite{kteily2015ascent} are commonly used methods to assess human-likeness.
+Survey questions with semantic scales such as "human-like / machine-like" and "artificial / natural" are also used for this perception.
+\textit{Personality traits} captures the human characteristics that are attributes to the agent, such as warm, friendly, likeable, and polite.
+This is commonly captured in the qualitative feedback from users, commenting on whether the agent is extroverted or introverted, or the human characteristics they perceive the agent such as funny or witty.
+Some studies used the measure of the Big-5 personality traits \cite{gosling2003very} to map an agent's disposition on various personality dimensions.
+
+Overall there is good coverage of perception measures based on the list of papers reviewed in our corpus.
+The most commonly measured perceptions are related to the interaction with agent, followed by the perception of agent's humanness.
+There are two basic themes that are the least measured compared to the others: competence under the perception of agent's ability, and intimacy under the perception of social connection with agent.
+This may be due to the controlled lab settings for the experiments, where participants are given the scenarios for interaction.
+This environment is not conducive to forming relationships with a conversational partner, as noted by Linnerman et al.
+in their discussions \cite{linnemann2018can}\cmt{[15]}.
+Also, the same factor could impact the assessment of agent's abilities, as the users may not feel like they have the expertise to assess an agent's competence.
+These factors could contribute to the reasons why competency and intimacy are not as frequently measured in experimental studies.
+
+% Add citations
+
+\subsection{Conversation Architecture Elements}
+
+As shown in Table \ref{tab:cues}, there are three categories defined for the conversation architecture elements covering 10 different themes.
+The details of each category and theme are discussed below.
+
+The category of \textbf{linguistic content} maps to the content category under verbal cues in Feine et al's taxonomy, which refers to elements expressed with written or spoken words that are related to the strict and literal meaning of a message (i.e.
+what is said) \cite{feine2019taxonomy}.
+The theme of \textit{affective language} captures the injection of emotional words or phrases into the agent's utterance, such as affective expressions \cite{seeger2021chatbots}\cmt{[35]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}, sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}, and encouraging words \cite{healey2013relating}\cmt{[39]}.
+\textit{Social talk} captures non-task related conversations with the user to build social connection, such as self-disclosure \cite{lee2020hear}\cmt{[23]} and social dialogue \cite{volkel2021manipulating}\cmt{[68]}\cite{lubold2016effects}\cmt{[86]}.
+The theme of \textit{humour} is similar to social talk but specific to CA's attempt to include jokes in its utterances.
+The separation of social talk and humor is based on findings from previous research, where user's attitude towards humour is different between human-human conversations vs.
+human-agent conversations \cite{clark2019makes}.
+We would like to capture the relationship between humour and agent perceptions differently from social talk.
+Lastly, the theme of \textit{agent-initiated content} captures utterances that are driven by the agent without direct prompts from the user.
+This elements in this theme include conversation repairs \cite{cuadra2021my}\cmt{[67]}\cite{ashktorab2019resilient}\cmt{[88]} and proactive content like eliciting feedback \cite{xiao2021let}\cmt{[73]}.
+
+The category of \textbf{linguistic style} maps to the style category under verbal cues in Feine et al's taxonomy, which refers to elements expressed with written or spoken words that are related to the meaningful deployment of language variation in a message (i.e.
+how something is said) \cite{feine2019taxonomy}.
+The theme of \textit{formality} describes the language style used by the conversational agent, whether it is formal vs.
+casual, such as using honorific expressions to address users \cite{ouchi2019should}\cmt{[59]}.
+\textit{Alignment} captures the degree that the agent aligns its utterances to the users, such as lexical alignment on the content and structural of the sentences \cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}, as well as agreement with the user \cite{volkel2021examining}\cmt{[69]}.
+\textit{Elaborateness} captures the sentence complexity and length of the utterances.
+For example, Roy et al.
+explored the differences in perception for variations in elaborateness such as "Cloudly, possibility of snow, high: 4, low: -10" vs "Today will be cloudy, with a high of 4 and a low of -10.
+Snow is predicted" \cite{roy2021users}\cmt{[71]}.
+Lastly, the category of \textit{disfluency} captures the style of using non-lexical utterances like filler words ("um, uh") \cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}, or repetition of words within a sentence \cite{yang2021effect}\cmt{[72]}.
+
+Lastly, the category of \textbf{non-linguistic format} maps loosely to the elements in auditory and invisible categories in Feine et al's taxonomy \cite{feine2019taxonomy}.
+These are auditory or textual variations in the presentation of the agent's utterances.
+In the theme of \textit{prosodic cue}, it captures vocal qualities like gender of voice \cite{habler2019effects}\cmt{[63]}\cite{jestin2022effects}\cmt{[81]}, and speech rate \cite{choi2020nobody}\cmt{[54]}.
+\textit{Text variations} include different formats that text-based agents use to present information to users, like emoticons \cite{kim2019comparing}\cmt{[89]}\cite{wilhelm2022keep}\cmt{[28]}, typos \cite{westerman2019believe}\cmt{[9]}, and response delays \cite{gnewuch2022opposing}\cmt{[20]}\cite{seeger2021chatbots}\cmt{[35]}.
+
+Overall the spread of conversation architecture elements relevant to anthropomorphized perceptions are evenly distributed across linguistic content, linguistic style, and non-linguistic format.
+Looking at the different themes, there is good coverage of studies on the impact of affective language and prosodic cues on anthropomorphized perceptions.
+However, it seemed like there is a lack of studies exploring the effect of agent-initiative content on the perception of agents.
+There are various existing literature on this theme such as conversation repairs \cite{komatani2010online}\cite{reinkemeier2022repair} and agent proactively sharing content with users \cite{dubiel2019inquisitive}\cite{zargham2022understanding}, but they were not included in this systematic literature review because they did not have measures of anthropomorphized perceptions of the CA.
+This may be because conversations with CAs have historically being driven by the user, with some recent effort to understand the opportunities to be more proactive \cite{cowan2023introduction}, as existing research are focused on the functional aspects of designing an agent instead of exploring into the anthropomorphized perceptions.
+
+Modality?
+
+\begin{table*}[h]
+%\resizebox{\textwidth}{!}{
+\begin{tabular}{@{}lllc@{}}
+\toprule
+ \textbf{Category} & \textbf{Theme}      & \textbf{Sample Codes}                                      & \textbf{No. Papers} \\ \midrule
+\multirow{4}{*}{Linguistic Content}    & Affective Language & emotional expressions, sentiment-adaptive responses & 11 \\
+ & Social Talk           & self-disclosure, social dialogue                       & 7                                       \\
+ & Humour                & humorous content, jokes                                & 5                                       \\
+ & Agent-Initiated Content & elicit user feedback, proactivity, conversation repair & 4                                       \\ \midrule
+\multirow{4}{*}{Linguistic Style}     & Formality          & formal vs. casual, honorific expressions                               & 9  \\
+ & Alignment             & content matching, lexical alignment, agreeableness     & 7                                       \\
+ & Elaborateness         & elaborate, concise, sentence structure                 & 6                                       \\
+ & Disfluency            & fillers, interjections, repetitions                    & 6                                       \\ \midrule
+\multirow{2}{*}{Non-Linguistic Format}     & Prosodic Cue            & pitch, intonation, speech rate, spoken accent                          & 12 \\
+ & Text Variation        & typo, capitalization, emoticons, response delay & 9                                         \\ \bottomrule 
+\end{tabular}%
+%}
+\caption{Conversation architecture elements}
+\label{tab:cues}
+\end{table*}
+
+\subsection{Relationship Between Anthropomorphized Perceptions and Conversation Architecture Elements}
+
+\begin{figure*}[]
+  \centering
+  \includegraphics[width=\textwidth]{fig-heatmap-impact.png}
+  \caption{Heatmap of literature for perception of conversational agents for each type of conversational architecture element}
+  \label{fig:heatmap-impact}
+\end{figure*}
+
+We extracted 265 connections between anthropomorphized perceptions and conversation architecture elements from our reviewed corpus.
+Out of these connections, 193 of them had an impacted relationship between the conversational architecture elements and anthropomorphized perceptions.
+Most of these relationships (n=183) were exploring the effect of a single conversation architecture element on perceptions of agents (e.g.
+\cite{miehle2018exploring}\cmt{[51]}\cite{westerman2019believe}\cmt{[9]}), while a few of them (n=10) used a composite of architecture elements in the study (e.g.
+\cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2021manipulating}\cmt{[68]}).
+The 183 single element relationships are visualized into a heatmap (Figure \ref{fig:heatmap-impact}) to based on the number of impacts conversational architecture elements had on the anthropomorphized perceptions.
+These relationships are discussed in details in the following sections for each perception category.
+
+%\subsubsection{Overall Characteristics}
+
+%While the number of papers studying voice (n=27) vs.
+text (n=30) modalities is not significantly different, there are some interesting trends in the perceptions studied for CAs with different modalities.
+Overall, there are less perceptions of agent studied for text-based agents (n=101) as compared to voice-based agents (n=163).
+
+%This is especially evident in the perception of social connection with agent and perception of agent's humanness.
+For the perception of social connection with a CA, there are only 19 perceptions measured for text-based agents, while there are 35 perceptions measured for voice-based agents.
+Similarly for perception of agent's humanness, there are 36 perceptions measured for text-based agents, as compared to 52 perceptions of voice-based agents.
+This highlights that there is a ..
+
+\subsubsection{Perception of Interaction with Agent}
+
+The effects of conversation architecture elements on the perception of interaction with agent is the most explored connections in the corpus (n=100).
+Out of these explored connections, the majority of them (n=69) discovered an impact between the studied architecture element and the perception.
+For the impacted relationships, the corpus had similar numbers of connections across voice-based (n=34) and text-based (n=35) CAs.
+
+Across the themes in this perception category, both \textbf{usability} and \textbf{engagement} perceptions were measured frequently in our corpus, with conversation architecture elements having effects on these measures across linguistic content, linguistic style and non-linguistic format categories.
+\textbf{Satisfaction} measures were used in some studies but it is not evaluated as often as engagement or usability.
+Several papers that measured satisfactions were conversation agents within the transaction context, especially within the customer service domain (e.g.
+\cite{diederich2019emulating}\cmt{[25]}\cite{elsholz2019exploring}\cmt{[61]}\cite{gnewuch2018faster}\cmt{[19]}).
+For the relationships across conversation architecture element categories, linguistic style has the higher number of relationships with perceptions of interaction (n=31).
+Linguistic content (n=17) and non-linguistic format (n=18) had similar number of relationships.
+
+There are a few conversation architecture elements that are notable to the perception of interaction with agent.
+First are the linguistic styles of formality and elaborateness, where they have high impacts across usability, engagement and satisfaction perceptions.
+For \textbf{formality}, various studies reported significant differences between using casual vs.
+formal styles.
+Some participants enjoyed the friendly nature of the casual style of the conversation \cite{cox2022does}\cmt{[27]}, while in another study participants reported the formal language style as boring \cite{kim2019comparing}\cmt{[89]}.
+For \textbf{elaborateness}, participants generally found the use of full sentences more useful than keyword only \cite{haas2022keep}\cmt{[78]}\cite{roy2021users}\cmt{[71]}.
+Otherwise, the impact of an agent's elaborateness on user's perception of interaction depends on the user's preference \cite{miehle2018exploring}\cmt{[51]}, as well as the topic of discussion \cite{haas2022keep}\cmt{[78]}.
+Within the linguistic content category, \textbf{social talk} and \textbf{humour} conversation architecture elements had impacts on user's perception of the interaction with an agent.
+There may be some opposing effects between different perceptions of interaction, as users enjoyed conversing with CAs using social talk more \cite{lee2020hear}\cmt{[23]}\cite{roy2021users}\cmt{[71]}, but the tradeoff is that they perceive it as less efficient \cite{roy2021users}\cmt{[71]}.
+Lastly, majority of the studies found that non-linguistic formats of a CA impacts the perception of the interaction, as \textbf{prosodic cues} such as expressiveness increased participants' engagement ratings \cite{zhu2022effects}\cmt{[26]}, and text variations such as using response delay increased user's satisfaction with the chatbot interaction \cite{gnewuch2018faster}\cmt{[19]}.
+
+\subsubsection{Perception of Agent's Ability}
+
+The effects of conversation architecture elements on the perception of agent's ability is the least explored connection in the corpus (n=35).
+Out of these explored connections, 27 relationships had an effect between the studied architecture elements and ability perceptions.
+For these impactful relationships, the corpus had similar numbers of connections across voice-based (n=15) and text-based (n=12) CAs.
+
+Across the themes in this perception category, \textbf{competence} had the smallest number of relationships in our corpus compared to intelligence and trust.
+Some studies discussed that the perception of competence is dependent various influencing factors, such as task difficulty \cite{kraus2020effects}\cmt{[64]}.
+Overall, studies on the perception of \textbf{intelligence} had impactful results, such as the use of formal language made the CA seem more knowledgeable \cite{volkel2022user}\cmt{[75]}.
+However, some evidence suggest that there are nuances to this perception, as a filler-speaking agent was perceived as less intelligent in task-oriented conditions, but was seen as slightly more intelligent in social-oriented conditions \cite{jeong2019exploring}\cmt{[10]}.
+
+For the conversation architecture categories related to the perception of agent's ability, all 10 explored connections related to \textbf{linguistic content} had impacted user's perception.
+Specifically, CAs utilizing \textbf{agent-initiative content} such as using proactive dialogue and conversation repair strategies are seen as more competent \cite{kraus2020effects}\cmt{[64]} and intelligent \cite{ashktorab2019resilient}\cmt{[88]}.
+However, the effect of being proactive on user's trust with an agent may be dependent on the proactive style of the user's own conversation patterns \cite{kraus2020effects}\cmt{[64]}.
+For CAs using \textbf{affective language}, some studies found that using more expressive words increased intelligence and competence \cite{lee2019s}\cmt{[55]}\cite{yang2017perceived}\cmt{[44]}, but it may decrease the perceived trustworthiness of an agent
+%as discussed in Healey et al's study using an agent with an encouraging personality
+\cite{healey2013relating}\cmt{[39]}.
+
+The conversation architecture categories \textbf{Linguistic style} and \textbf{non-linguistic format} had mixed results, with some elements demonstrating relationships with the perception of the agent's abilities, while some others didn't.
+Most these mixed results came from relationships with the perception of trust.
+Studies with \textbf{alignment} found differences in trust rating in the interaction studies \cite{hoegen2019end}\cmt{[31]}, while some others did not reveal any differences \cite{huiyang2022improving}\cmt{[17]}.
+Also, research method may impact the perception of trust, as an observation study and interaction study on a similar topic yielded different results on the perception of trust \cite{linnemann2018can}\cmt{[15]}.
+The use of \textbf{prosodic cues} also had varied impacts on trust, as one study found that differences in vocal cues lead to a difference in perceived truthfulness \cite{dubiel2020persuasive}\cmt{[60]}, while another study using gendered voices did not find any statistically significant differences in perceived trust \cite{jestin2022effects}\cmt{[81]}.
+
+\subsubsection{Perception of Social Connection with Agent}
+
+There are 53 explored connections between conversation architecture elements and the perception of social connection with agents, with majority of them (n=40) resulted in relationships with effects.
+Interestingly, studies explored more perceptions of social connection with agent related to voice-based CAs (n=34) compared to text-based CAs (n=19), potentially due to the assumption that voice-based agents is more suitable to cultivate human-agent relationships.
+There are some mixed results for voice-based CAs, as 10 out of the 34 connections did not find any significant results.
+Half of the neutral results come from the conversation architecture element of \textbf{prosodic cues}.
+For example, the pitch of agents' voices did not impact the perceived rapport \cite{lubold2016effects}\cmt{[86]} between agent and users or the appropriateness of tone \cite{jestin2022effects}\cmt{[81]}.
+However, there are also findings that the use of vocal cues made the agent sound more empathetic \cite{tolmeijer2021female}\cmt{[62]}, as well as increased perceived emotional connection \cite{chan2021kinvoices}\cmt{[74]}\cite{kim2020can}\cmt{[24]}.
+This shows that there are nuanced factors within prosodic cues that impact the perception of social connections that we have not captured in our relationships.
+
+Across the themes in this perception category, \textbf{social presence} (n=17) and \textbf{conversation tone} (n=18) have similar number of relationships between architecture elements and perceptions, but \textbf{intimacy} (n=5) has less number of impactful relationships.
+One reason for this is half of the explored connections did not have any effect on the perception of social connection, such as the use of capitalization \cite{westerman2019believe}\cmt{[9]}, lexical alignment \cite{linnemann2018can}\cmt{[15]}, or social dialogue \cite{lubold2016effects}\cmt{[86]}.
+For \textbf{social presence}, conversation architecture elements from \textbf{non-linguistic format} category, prosodic cue and text variation, had a number of impactful relationships in the reviewed studies.
+For example, participants conversing with the agents using kin's voices experienced significantly higher perceived co-presence where there is a closer psychological connection with the agent \cite{chan2021kinvoices}\cmt{[74]}.
+Also, text-based agents including a delay before responding to users were rated higher in social presence ratings compared to the agent that did not use any response delays \cite{gnewuch2018faster}\cmt{[19]}\cite{gnewuch2022opposing}\cmt{[20]}.
+Lastly, the use of \textbf{prosodic cues} can impact the perceived \textbf{conversation tone} of the agent as emotionally expressive \cite{zhu2022effects}\cmt{[26]} or persuasive \cite{chan2021kinvoices}\cmt{[74]}, as well as the appropriateness of the tone used by the agent \cite{jestin2022effects}\cmt{[81]}\cite{misu2011toward}\cmt{[83]}.
+
+Looking at the different categories of conversation architecture cues, the heatmap (Figure \ref{fig:heatmap-impact} shows that there are not many relationships in \textbf{linguistic style} that are related to the perceived social connection with CAs.
+There are not many explored connections in our reviewed corpus between the two, which could be an indication of the assumption that linguistic style does not impact the perception of social connections.
+While we discussed the impact of non-linguistic elements of prosodic cues and text variations earlier, the conversation architecture elements in the linguistic content category also had effects on the perception of social connections.
+Specifically, CAs using of \textbf{affective language} were perceived to be more empathetic \cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{yang2017perceived}\cmt{[44]} and emotionally expressive \cite{zhu2022effects}\cmt{[26]}, and emotional connection with the agent \cite{lee2019s}\cmt{[55]}\cite{lubis2019positive}\cmt{[43]}.
+
+%add text variation in the discussion
+
+\subsubsection{Perception of Agent's Humanness}
+
+Agent's humanness is the second most explored perception within our reviewed corpus (n=76), with majority of the connections finding impacted relationship between the studied conversation architecture elements and the perception of agent's humanness (n=56).
+While the connections were explored more for voice-based agent (n=49) as compared to text-based agents (n=27), the actual impacted relationships between the modalities were similar (voice=32, text=24).
+This is due to larger number of neutral relationships within voice modality, such as the use of affective language for a speech agent did not impact its perceived likeability \cite{hu2022polite}\cmt{[76]}.
+
+Across the themes in this perception category, both \textbf{human-likeness} and \textbf{personality traits} have relationships with almost all conversation architecture elements.
+Based on the reviewed corpus, it seems like all the conversation architecture elements extracted from literature have some impact on the perception of agent's humanness.
+However, the impacts can be both positive or negative.
+In the case of Chan et al's study \cite{chan2021kinvoices}\cmt{[74]}, participated rated the agent using kin voices as significantly more likeable compared to the generic voices, but it was perceived as eerie.
+As for the perceptions within this category, there are more relationships for perceived personality traits (n=33) vs.
+human-likeness (n=18).
+This is because many studies only have one measure for human-likeness (e.g.
+artificial or human-like), but have multiple aspects of personality to be explored.
+For example, participant rated the agent using affective language as more polite, as well as reflected that the agent seemed friendly \cite{hu2022polite}\cmt{[76]}.
+
+For the conversation architecture elements, formality in the linguistic style category and prosodic cue in the non-linguistic format category had more effects on the perception of agent's humanness in the reviewed corpus.
+For \textbf{formality}, agents using casual style is perceived as more human-like with a warm, kind and entertaining personality \cite{cox2022does}\cmt{[27]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2019comparing}\cmt{[89]}.
+The use of \textbf{prosodic cues} varying pitch, intonation and speech rate of a conversation agent generally had impacts on the perceived humanness instead of personality traits \cite{choi2020nobody}\cmt{[54]}\cite{jestin2022effects}\cmt{[81]}\cite{misu2011toward}\cmt{[83]}.
+For the architecture elements of \textbf{disfluency}, the type of impact on the perception of humanness depended on the context of the conversation.
+Studies have found that participants perceived the filler-condition agent as more likeable in the social-oriented situation, but did not find the same effect in task-oriented situations \cite{jeong2019exploring}\cmt{[10]}\cite{wester2015artificial}\cmt{[14]}.
+
+%-------------
+\section{Discussions}
+
+\subsection{Research Challenges and Opportunities}
+
+%Three major needs emerged from the trends identified by our review: 1) 2) 3).
+
+\subsubsection{Inconsistencies in Perception Measures}
+
+A major roadblock in synthesizing the findings from existing academic research is the diversity and inconsistency of measurements towards the anthropomorphized perception of agents.
+It is difficult to assess whether perception measures should be compared with each other.
+Also, some measures combined anthropomorphized perceptions into a composite score, which makes it impossible to separate the perceptions into more granular details.
+
+Based on the literature reviewed in this paper, we noticed that similar perception concepts were \textbf{measured in different ways} through different surveys.
+For example, there are several approaches to measure the perceived \textit{human-likeness} of an agent.
+A commonly used survey is adapted from the Godspeed questionnaire \cite{bartneck2009measurement}, which measures human-likeness based on user's impression of the agent as fake / natural, machinelike / humanlike, unconscious / conscious, and artificial / lifelike (used by \cite{hoegen2019end}\cmt{[31]}, \cite{jeong2019exploring}\cmt{[10]} and \cite{ouchi2019should}\cmt{[59]}).
+Another way to measure human-likeness is adapted from Holtgraves et al.'s \cite{holtgraves2007perceiving} questionnaire, which asks users to assess the agent's perceived human-likeness, skillfulness, thoughtfulness, politeness, responsiveness and engagement (used by \cite{diederich2019emulating}\cmt{[25]} and  \cite{gnewuch2018faster}\cmt{[19]}).
+One study \cite{westerman2019believe}\cmt{[9]} used the Ascend of Man pictorial scale \cite{kteily2015ascent} as the measure of perceived human-likeness.
+It is unclear whether these different measures of perceived human-likeness are similar enough to be compared with each other.
+
+ In addition to different methods used to measure for the same perception, our detailed analysis revealed that the measures using the same label may have \textbf{drastically different meanings}.
+In Diedrech et al.'s study \cite{diederich2019emulating}\cmt{[25]}, \textit{empathy} measure is adapted from \cite{yan2013role} assessing whether the CA gives users individual or personal attention.
+In Daher et al.'s study \cite{daher2020empathic}\cmt{[58]}, they also measure the perception of empathy, but it is using the RoPE Scale \cite{charrier2019rope} with questions like "the robot cares about my feelings" or "the robot comforts me when I am upset." These two different measures of empathy seem to have different underlying meanings, one assessing the personalization aspect of CAs, while the other is assessing the emotional aspect of CAs.
+Another example is the measurement of \textit{trustworthiness}, with some constructs measuring the level of sensitive information user's are willing to share \cite{dinev2006privacy}, and some measuring the honesty and truthfulness of an agent \cite{lee2017enhancing}.
+
+Lastly, there are \textbf{composite measures} of anthropomorphized perception across different categories, making it difficult to break down perceptions into granular details for analysis.
+One such example is Ma et al's study \cite{ma2022ask}\cmt{[29]} on different approaches for CAs to reply to users' uncertain queries.
+UX score is used to measure the perception of an agent, which asks whether the user thinks the CA's response is pleasing / trustworthy / natural / acceptable / shorten the distance between CA and user.
+While the study has found significant impact of the use of formal language on UX score, it is not possible to breakdown the measure into perceptions of interaction (pleasing, acceptable), social connection (shorten the distance between CA and user), and humanness (natural, trustworthy).
+Similar for Hoegen et al.'s study \cite{hoegen2019end}\cmt{[31]} on the impact of conversational style matching, it is not possible to separate the overall interaction score into different perceptions as the composite measure contains questions measuring different categories of perceptions like interaction (engaging) and humanness (trust, likable).
+
+In recent years there has been some effort towards unifying the evaluation of conversational agents, such as the work by Finch et al.
+\cite{finch2020towards} presenting a comprehensive analysis of current evaluation protocols.
+More work is needed to categorize and consolidate perception measures to make them consistent and comparable across various studies.
+
+%For discussions on mental well beings, agent using emojis is rated higher for attitude (emotional connection) .
+However, for agent with discussing physical well being, agent using emojis is rated as lower for attitude.
+%Attitude has emotional connection, coherent - coherent is an ability perception, vs. emotional connection is a social connection perception. \cite{fadhil2018effect}\cmt{[52]}
+
+\subsubsection{Other Influencing Factors}
+
+While the discussion in the Framework section above focuses on the overall effect of conversational architecture elements on anthropomorphized perceptions,  there are other nuanced influencing factors that impact user perceptions of agents.
+
+Depending on the \textbf{type of conversation} user is having with agents, it may lead to differences in perceptions for similar conversational architecture elements.
+Cox et al.
+\cite{cox2022does}\cmt{[27]} found that the perceived competence and appropriateness of tone of different language formality styles depend on the sensitivity of information discussed in the conversation.
+In this particular study, a formal language style is preferred in medical history discussions as it is matching to the expectation of users, but there is no difference in perception between formal and casual styles when discussing income level and credit scores.
+In Jeong et al's study \cite{jeong2019exploring}\cmt{[10]}, users found the agent using fillers less intelligent and likable in a task-oriented conversation, but found the same agent using fillers as slight more intelligent and likable in a social-oriented conversation.
+Another factor that could impact perceptions is the \textbf{anonymity} of conversation.
+Based on user feedback, Lee et al.
+\cite{lee2020hear}\cmt{[23]} found that the anonymity of a conversational agent is a driving factor encouraging people to self disclose without having to worried about judgements from the CA.
+The perception of the agent may be different if the user's identity is not anonymous.
+
+Other than the type of conversation, \textbf{user's characteristics} can also be influencing factors on their perception of agents.
+For example, the effect of matching user's conversational style on perception of agents depend on user's own conversational style, as participants with high consideration conversational style rated the lexically aligned agent as more trustworthy \cite{hoegen2019end}\cmt{[31]}.
+In the study by Cox et al.
+\cite{cox2022does}\cmt{[27]}, participants with lower levels of privacy concerns as well as those who believe in robotic intelligence found the chatbot more enjoyable, warm, competent and appropriate.
+Similarly, participants with positive attitudes towards computers were significantly more likely to indicate that the usage of fillers by agents was a positive aspect of the conversation, compared to participants with neutral attitudes towards computers \cite{pfeifer2009should}\cmt{[12]}.
+Lastly, user's prior experience with conversational agents could impact perception of agents.
+Experienced users perceived the agent with a response delay as lower in social presence compared to the one without delay, as it is seen as inefficient to wait for the CA to respond.
+However, novice users perceived higher social presence conversing with the CAs using response delays as it is more similar to conversations with human partners \cite{gnewuch2018faster}\cmt{[19]}.
+
+%* Format: Response delay - Novice users perceived the agent as more socially present, but experienced users had a negative effect \cite{gnewuch2022opposing}\cmt{[20]}
+%* Content: Humour - no overall significant difference between conventional method vs.
+agent using humour for enjoyment.
+Specifically, men enjoyed the agent's jokes more than women.
+\cite{miyamoto2017improving}\cmt{[46]}.
+%* Format: Proactivity - significant interaction between proactive dialogue strategies and task difficulty for perceived competence and perceived reliability.
+For easier tasks, system help is not really required.
+\cite{kraus2020effects}\cmt{[64]}
+%* Preference for the level of social talk depended on the task, even within the same transactional context, as users preferred high level for playing a song, but low level for writing a text.
+\cite{volkel2021manipulating}\cmt{[68]}
+%* Correlation between user's personality of agreeableness vs. preference for agreeable level of chatbot \cite{volkel2021examining}\cmt{[69]}
+%* For expertise, multilingual students rated higher the non-native English-speaking virtual human. \cite{feijoo2021effects}\cmt{[70]}
+%* Participants felt irritated when humorous statements were made when they talked about experiencing sadness \cite{go2021conversational}\cmt{[80]}
+
+%\subsubsection{Study Design}
+
+%\textbf{Interview vs experiment}
+%* Humour - what's said vs. study results
+
+%\textbf{Observer study vs. interaction study}
+%* In observer study, participants attributed higher integrity (trustworthiness), response accuracy and likeability to the agent with lexical alignment, but this effect was not observed in the interaction study.
+Also, interaction study had lower cognitive demand but no effect in the observer study.
+\cite{linnemann2018can}\cmt{[15]}
+%* \cite{zhu2022effects}\cmt{[26]}
+%* \cite{cox2022does}\cmt{[27]}
+
+\subsubsection{Relationship between perceptions}
+
+Response delay: social presence has a significant effect on intention to use. 
+\cite{gnewuch2022opposing}\cmt{[20]}
+
+Perceived intelligence positively associated with perceived usefulness, perceived ease of use, initial trust, and perceived anthropomorphism.
+Perceived anthropomorphism is associated with perceived enjoyment, and intention to adopt.
+Perceived usefulness and perceived enjoyment impacts intention to adopt.
+\cite{moussawi2021perceptions}\cmt{[36]}
+
+The size of the effect for language we observed is clearly higher than the size of the effect for voice. \cite{habler2019effects}\cmt{[63]}
+
+VA self-repair can backfire if time or accuracy is of the essence. (repair and accuracy) \cite{cuadra2021my}\cmt{[67]}
+
+\subsection{Ethical Considerations}
+
+Self-disclosure encourage higher trust and intimacy, to disclose sensitive information. Who have access to this data? need to be aware of privacy / data sharing practices. \cite{lee2020hear}\cmt{[23]}
+
+Evidence for the influence of voice gender and pitch on stereotypical trait attribution.
+Active trait attribution is missing as most participants attributes to the negative side of traits for CAs.
+\cite{tolmeijer2021female}\cmt{[62]}
+
+The social and emotional benefits of self-repair in interaction need to be balanced against the creepiness of the monitoring and modelling needed to make self-repair possible.
+\cite{cuadra2021my}\cmt{[67]}
+
+\subsection{Limitations and Future Work}
+
+\subsubsection{Assumptions in designed personalities of CAs}
+Sometimes a study is covering multiple conversational element cues, hard to break it out.
+For example, extroverted personality used in \cite{volkel2022user}\cmt{[75]} has emoticons, affective language, talkative, and self-disclosure.
+Need to break it down.
+
+Also, breaking down "personalities" to its core components.
+
+There are a few studies that designed conversational agents composed with multiple conversation architecture elements.
+This is especially evident in studies comparing different personalities of CAs, such as extroverted vs.
+introverted.
+In Volkel et al's study, the personality of extraversion is a combination of linguistic content like social ta
+
+\cite{moilanen2022measuring}\cmt{[82]}\cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}.
+
+%Research challenges and opportunities
+
+%Ethical considerations
+
+\subsubsection{Gaps}
+
+Combined effects
+* integrated mental model \cite{knijnenburg2016inferring}\cmt{[34]}
+* Anthropomorphized chatbot (text) using affective language (emotional expressions), self-referencing, emoticons, response delays.
+Resulted in higher perceived anthropomorphism, which in result led to lower negative word of mouth and loss of trust.
+anthropomorphic design is beneficial not only to initial trust but also to the ongoing trust relationship \cite{seeger2021chatbots}\cmt{[35]}
+
+Lack of investigations - name a few areas
+
+%\subsubsection{Human-human vs. Human-machine}
+
+%* Impact of lexical alignment on people's perceived annoyance and likability differed in HHI (higher) and HCI (no impact). \cite{huiyang2022improving}\cmt{[17]}.
+
+\section{Conclusions}
+
+TBD
+
+%%
+%% The acknowledgments section is defined using the "acks" environment
+%% (and NOT an unnumbered section). This ensures the proper
+%% identification of the section in the article metadata, and the
+%% consistent spelling of the heading.
+\begin{acks}
+To Robert, for the bagels and explaining CMYK and color spaces.
+\end{acks}
+
+%%
+%% The next two lines define the bibliography style to be used, and
+%% the bibliography file.
+\bibliographystyle{ACM-Reference-Format}
+\bibliography{references}
+
+%%
+%% If your work has an appendix, this is the place to put it.
+\appendix
+
+\onecolumn
+\section{Appendix}
 
@@
 \caption{Perception measures}
-\label{tab:perceptions}
+\label{tab:appendix-perceptions}
 \end{table*}
 
-As shown in Table \ref{tab:perceptions}, there are four organizing themes defined for the anthropomorphized perceptions of conversational agents covering 11 basic themes of perception.
-The details of each theme are discussed below.
-
-\textbf{Perception of interaction with a CA} evaluates the overall interaction quality users had with the conversational agent.
-The three basic themes for this perceptions are usability, engagement and satisfaction.
-\textit{Usability} measures the utilitarian aspects of the interaction, whether it was accurate, easy to use, efficient or helpful.
-Some commonly used methods to measure usability include the response accuracy portion of the SASSI questionnaire \cite{hone2000towards}\cmt{sassi}, or the NASA Task Load Index (NASA-TLX) \cite{hart1988development}\cmt{nasa} to measure cognitive workload.
-Questions such as "the system is easy to use" or "it is easy to understand the agent" are also measures of usability.
-\textit{Engagement} on the other hand measures users' emotional reactions, whether they have enjoyed the conversation with CA, or annoyed or frustrated with the interaction.
-Some commonly used methods to measure engagement include  the annoyance portion of the SASSI questionnaire \cite{hone2000towards}\cmt{sassi}, and the Use Engagement Scale (UES) \cite{o2018practical}\cmt{ues}.
-Questions such as "I enjoyed using the system" or "I felt frustrated with the agent" are also measures of engagement.
-Lastly, \textit{Satisfaction} measures users' overall satisfaction interacting with the agent.
-Questions such as "the overall assessment of conversing with the CA was satisfactory" are used to measure this perception.
-
-\textbf{Perception of a CA's ability} evaluates the perceived capabilities of the agent.
-While there are some elements of system performance in this measure, the main aspect we are interested in is the perception differences for agents with identify system capabilities but with different architecture elements.
-Specifically, \textit{intelligence} measures the agent's expertise and knowledge, and it is commonly administered through the Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed} on the set of questions related to perceived intelligence.
-Also survey questions such as asking users about the agent's intelligence and domain knowledge are used to measure perceived intelligence.
-\textit{Competence} takes intelligence one step further by evaluating the agent's ability to put its intelligence into practice.
-To measure a CA's competence, there are usually surveys or qualitative feedback that the agent is capable and competent, and that the users have confidence in the agent's ability to get the job done.
-Lastly, \textit{trust} evaluates agent's truthfulness, credibility and benevolence.
-Some commonly used methods to evaluate trust include the Trust Propensity Scale \cite{mayer1999effect} and the Individualized Trust Scale (ITS) \cite{wheeless1977measurement}.
-Questions such as "is the agent honest" and "can I trust the agent with sensitive information" are also measures of trust.
-
-\textbf{Perception of the social connection with a CA} evaluates the emotional connections that users have with agents.
-The three basic themes of conversation tone, social presence and intimacy are included in this category.
-\textit{Conversation tone} measure the affective impression of the agent's tone, such as empathy, expressiveness, or passionate.
-Also, it measures whether the tone used by the agent is persuasive or appropriate for the conversation.
-\textit{Social presence} measures the sense of connectness and psychological distance users has with an agent.
-Some aspects in this measure include a sense of familiarity or similarity with the agent, whether users feel the agent behaves like them or have similar attitudes to them.
-The measure of \textit{Intimacy} extends social presence into the realm of the quality of relationships with an agent.
-Some commonly used measures include the set of social attraction questions from the interpersonal attraction questionnaire \cite{mccroskey1975development} and the quality of relationship inventory (QRI) \cite{pierce1997assessing}.
-These questionnaires include questions like "I think the agent could be a friend of mine", or "I feel we could establish a personal relationship with each other".
-
-\textbf{Perception of a CA's humanness} evaluates human-likeness and the anthropomorphized personality traits that users assign to agents.
-\textit{Human-likeness} measures whether the agent presented itself as natural and human-like, or artificial and machine-like.
-The Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed} set of questions related to anthropomorphism and the Ascent of Man scale \cite{kteily2015ascent} are commonly used methods to assess human-likeness.
-Survey questions with semantic scales such as "human-like / machine-like" and "artificial / natural" are also used for this perception.
-\textit{Personality traits} captures the human characteristics that are attributes to the agent, such as warm, friendly, likeable, and polite.
-This is commonly captured in the qualitative feedback from users, commenting on whether the agent is extroverted or introverted, or the human characteristics they perceive the agent such as funny or witty.
-Some studies used the measure of the Big-5 personality traits \cite{gosling2003very} to map an agent's disposition on various personality dimensions.
-
-Overall there is good coverage of perception measures based on the list of papers reviewed in our corpus.
-The most commonly measured perceptions are related to the interaction with agent, followed by the perception of agent's humanness.
-There are two basic themes that are the least measured compared to the others: competence under the perception of agent's ability, and intimacy under the perception of social connection with agent.
-This may be due to the controlled lab settings for the experiments, where participants are given the scenarios for interaction.
-This environment is not conducive to forming relationships with a conversational partner, as noted by Linnerman et al.
-in their discussions \cite{linnemann2018can}\cmt{[15]}.
-Also, the same factor could impact the assessment of agent's abilities, as the users may not feel like they have the expertise to assess an agent's competence.
-These factors could contribute to the reasons why competency and intimacy are not as frequently measured in experimental studies.
-
-% Add citations
-
-\subsection{Conversation Architecture Elements}
-
-As shown in Table \ref{tab:cues}, there are three categories defined for the conversation architecture elements covering 10 different themes.
-The details of each category and theme are discussed below.
-
-The category of \textbf{linguistic content} maps to the content category under verbal cues in Feine et al's taxonomy, which refers to elements expressed with written or spoken words that are related to the strict and literal meaning of a message (i.e.
-what is said) \cite{feine2019taxonomy}.
-The theme of \textit{affective language} captures the injection of emotional words or phrases into the agent's utterance, such as affective expressions \cite{seeger2021chatbots}\cmt{[35]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}, sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}, and encouraging words \cite{healey2013relating}\cmt{[39]}.
-\textit{Social talk} captures non-task related conversations with the user to build social connection, such as self-disclosure \cite{lee2020hear}\cmt{[23]} and social dialogue \cite{volkel2021manipulating}\cmt{[68]}\cite{lubold2016effects}\cmt{[86]}.
-The theme of \textit{humour} is similar to social talk but specific to CA's attempt to include jokes in its utterances.
-The separation of social talk and humor is based on findings from previous research, where user's attitude towards humour is different between human-human conversations vs.
-human-agent conversations \cite{clark2019makes}.
-We would like to capture the relationship between humour and agent perceptions differently from social talk.
-Lastly, the theme of \textit{agent-initiated content} captures utterances that are driven by the agent without direct prompts from the user.
-This elements in this theme include conversation repairs \cite{cuadra2021my}\cmt{[67]}\cite{ashktorab2019resilient}\cmt{[88]} and proactive content like eliciting feedback \cite{xiao2021let}\cmt{[73]}.
-
-The category of \textbf{linguistic style} maps to the style category under verbal cues in Feine et al's taxonomy, which refers to elements expressed with written or spoken words that are related to the meaningful deployment of language variation in a message (i.e.
-how something is said) \cite{feine2019taxonomy}.
-The theme of \textit{formality} describes the language style used by the conversational agent, whether it is formal vs.
-casual, such as using honorific expressions to address users \cite{ouchi2019should}\cmt{[59]}.
-\textit{Alignment} captures the degree that the agent aligns its utterances to the users, such as lexical alignment on the content and structural of the sentences \cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}, as well as agreement with the user \cite{volkel2021examining}\cmt{[69]}.
-\textit{Elaborateness} captures the sentence complexity and length of the utterances.
-For example, Roy et al.
-explored the differences in perception for variations in elaborateness such as "Cloudly, possibility of snow, high: 4, low: -10" vs "Today will be cloudy, with a high of 4 and a low of -10.
-Snow is predicted" \cite{roy2021users}\cmt{[71]}.
-Lastly, the category of \textit{disfluency} captures tye style of using non-lexical utterances like filler words ("um, uh") \cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}, or repetition of words within a sentence \cite{yang2021effect}\cmt{[72]}.
-
-Lastly, the category of \textbf{non-linguistic format} maps loosely to the elements in auditory and invisible categories in Feine et al's taxonomy \cite{feine2019taxonomy}.
-These are auditory or textual variations in the presentation of the agent's utterances.
-In the theme of \textit{prosodic cue}, it captures vocal qualities like gender of voice \cite{habler2019effects}\cmt{[63]}\cite{jestin2022effects}\cmt{[81]}, and speech rate \cite{choi2020nobody}\cmt{[54]}.
-\textit{Text variations} include different formats that text-based agents use to present information to users, like emoticons \cite{kim2019comparing}\cmt{[89]}\cite{wilhelm2022keep}\cmt{[28]}, typos \cite{westerman2019believe}\cmt{[9]}, and response delays \cite{gnewuch2022opposing}\cmt{[20]}\cite{seeger2021chatbots}\cmt{[35]}.
-
-Overall the spread of conversation architecture elements relevant to anthropomorphized perceptions are evenly distributed across linguistic content, linguistic style, and non-linguistic format.
-Looking at the different themes, there is good coverage of studies on the impact of affective language and prosodic cues on anthropomorphized perceptions.
-However, it seemed like there is a lack of studies exploring the effect of agent-initiative content on the perception of agents.
-There are various existing literature on this theme such as conversation repairs \cite{komatani2010online}\cite{reinkemeier2022repair} and agent proactively sharing content with users \cite{dubiel2019inquisitive}\cite{zargham2022understanding}, but they were not included in this systematic literature review because they did not have measures of anthropomorphized perceptions of the CA.
-This may be because conversations with CAs have historically being driven by the user, with some recent effort to understand the opportunities to be more proactive \cite{cowan2023introduction}, as existing research are focused on the functional aspects of designing an agent instead of exploring into the anthropomorphized perceptions.
-
 \begin{table*}[h]
-%\resizebox{\textwidth}{!}{%
-\begin{tabular}{@{}lllc@{}}
+\resizebox{\textwidth}{!}{
+\begin{tabular}{@{}p{0.2\linewidth} | p{0.2\linewidth} | p{0.2\linewidth}@{}}
 \toprule
- \textbf{Category} & \textbf{Theme}      & \textbf{Sample Codes}                                      & \multicolumn{1}{l}{\textbf{No. Papers}} \\ \midrule
-\multirow{4}{*}{Linguistic Content}    & Affective Language & emotional expressions, sentiment-adaptive responses & 11 \\
- & Social Talk           & self-disclosure, social dialogue                       & 7                                       \\
- & Humour                & humorous content, jokes                                & 5                                       \\
- & Agent-Initiated Content & elicit user feedback, proactivity, conversation repair & 4                                       \\ \midrule
-\multirow{4}{*}{Linguistic Style}     & Formality          & formal vs. casual, honorific expressions                               & 9  \\
- & Alignment             & content matching, lexical alignment, agreeableness     & 7                                       \\
- & Elaborateness         & elaborate, concise, sentence structure                 & 6                                       \\
- & Disfluency            & fillers, interjections, repetitions                    & 6                                       \\ \midrule
-\multirow{2}{*}{Non-Linguistic Format}     & Prosodic Cue            & pitch, intonation, speech rate, spoken accent                          & 12 \\
- & Text Variation        & typo, capitalization, emoticons, response delay & 9                                         \\ \bottomrule 
+ \textbf{Category} & \textbf{Theme} & \textbf{Papers} \\ \midrule
+\multirow{4}{*}{Linguistic Content}    
+    & Affective Language 
+    &  
+\\
+     & Social Talk
+    &
+\\
+    & Humour
+    &
+\\
+    & Agent-Initiated Content
+    &
+\\ \midrule
+\multirow{4}{*}{Linguistic Style}
+    & Formality
+    &
+\\
+    & Alignment 
+    &
+\\
+    & Elaborateness
+    &
+\\
+    & Disfluency
+    &
+\\ \midrule
+\multirow{2}{*}{Non-Linguistic Format}
+    & Prosodic Cue
+    &
+\\
+    & Text Variation
+    &
+\\ \bottomrule 
 \end{tabular}%
-%}
+}
 \caption{Conversation architecture elements}
-\label{tab:cues}
+\label{tab:appendix-cues}
 \end{table*}
-
-\subsection{Relationship Between Anthropomorphized Perceptions and Conversation Architecture Elements}
-
-\section{Framework}
-%Wrote based on papers up to [60], 25 papers
-
-While the number of papers studying voice (n=27) vs.
-text (n=30) modalities is not significantly different, there are some interesting trends in the perceptions studied for CAs with different modalities.
-Overall, there are less perceptions of agent studied for text-based agents (n=101) as compared to voice-based agents (n=163).
-
-This is especially evident in the perception of social connection with agent and perception of agent's humanness.
-For the perception of social connection with a CA, there are only 19 perceptions measured for text-based agents, while there are 35 perceptions measured for voice-based agents.
-Similarly for perception of agent's humanness, there are 36 perceptions measured for text-based agents, as compared to 52 perceptions of voice-based agents.
-This highlights that there is a
-
-\begin{figure*}[]
-  \centering
-  \includegraphics[width=\textwidth]{fig-heatmap-impact.png}
-  \caption{Heatmap of literature for perception of conversational agents for each type of conversational architecture element.}
-  \Description{This graph shows the number of papers measuring the effect of conversational architecture elements on different perception measures of conversational agents.
-Conversational architecture elements are categorized into content (affective language, self-disclosure, humour), format (disfluency, typo, capitalization, speech rate, response delay), and style (lexical alignment, formality, emoticons, prosody).
-Perceptions are categorized into perception of interaction with an agent (engagement, satisfaction, accuracy), perception of social connection with an agent (intimacy, conversation tone, social presence), and perception of agent's humanness (human-likeness, trustworthiness, personality traits).}
-  \label{fig:heatmap-impact}
-\end{figure*}
-
-Figure \ref{fig:heatmap-impact}
-
-%%%%%
-\subsection{Perception of Interaction with an Agent}
-%%%%%
-
-This section discusses user's perception of their interaction with a conversational agent.
-\textbf{\textit{Engagement, accuracy, and satisfaction are the three variables used to evaluate how people perceive interactions with CAs}}.
-\textit{Engagement} measures user's attitude towards the task they are achieving through working with the agent, including how easy it is to use the system and its perceived usefulness, convenience and helpfulness for the user.
-Additionally, it includes the user's emotional responses to the interaction, such as annoyance, enjoyment, and irritation.
-\textit{Accuracy} measures whether the agent was perceived to be able to provide the correct answers in response to the user.
-\textit{Satisfaction} measures the whether the agent was able to fulfill user's expectations through the interaction encounter.
-
-Out of the list of publications that were evaluated, there is a good coverage on the effect of conversational architecture elements on the perception of interaction with an agent.
-Out of the three factors, engagement is the most frequently used measure to assess interaction quality, followed by satisfaction.
-Perceived accuracy of the agent is rarely used within literature, with only a few papers measuring this perception.
-
-[TODO] * Associations between conversational architecture elements and perceptions
-For both text and voice modalities, lexical alignment had a positive effect on engagement by decreasing the cognitive load of users.
-
-%%
-\subsubsection{Engagement}
-%%
-For the elements in the language content category of conversational architecture, the use \textbf{self-disclosure} by agent had a positive effect on engagement, as the participants using the chatbot with small talk and self disclosure reported higher enjoyment after 3 weeks of daily interaction \cite{lee2020hear}\cmt{[23]}.
-There are mixed results on the effect of \textbf{affective language} on engagement.
-One study found that CAs that uses encouraging words are rated as easier to use \cite{healey2013relating}\cmt{[39]}.
-However, the user of words with increased lexical emotional expressiveness did not have an effect on engagement \cite{zhu2022effects}\cmt{[26]}.
-The use of affective language may lead to negative impacts on engagement, as a system that uses an extroverted and overly familiar words is irritating to users.
-On the use of \textbf{humour}, survey result did not show a significant difference in the level of enjoyment, but qualitative feedback from participants reflected that humour made the interaction more engaging and immersive \cite{ceha2021can}\cmt{[57]}.
-
-For the elements in the language style category of conversational architecture, mimicking users' utterances through \textbf{lexical alignment} yielded positive results.
-Multiple studies have found that being lexically aligned to users resulted in lower perceived cognitive demand and decreased perceived workload \cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}\cite{spillner2021talk}\cmt{[18]}.
-Interestingly, perceived lower cognitive demand did not have significant impacts on ease of use \cite{linnemann2018can}\cmt{[15]} or annoyance \cite{huiyang2022improving}\cmt{[17]}.
-In Spillner et al's study \cite{spillner2021talk}\cmt{[18]}, both conditions of aligning words as well as aligning words and grammatical structure to user utterances resulted in higher perceived user engagement from participants.
-
-For the elements in the presentation format category of conversational architecture, auditory aspects of \textbf{prosody} such as speech rate and expressive tone of voice had different impacts on engagement.
-In one study, users enjoyed their interaction with the CA and perceived it as easier to use, as they felt the level of agent's social behaviour is matched with their emotional states \cite{kim2020can}\cmt{[24]}.
-However, another study did not find any impact of emotional expressive of voice on the user engagement \cite{zhu2022effects}\cmt{[26]}.
-On the speech rate for CAs, a normal rate is perceived as more convenient compared to a faster rate of speech \cite{choi2020nobody}\cmt{[54]}.
-On the visual presentation side, the study from Westerman et al.
-\cite{westerman2019believe}\cmt{[9]} showed that the use of \textbf{typos} by chatbots negatively impacted the perception of working with a CA on the specific task, while the use of \textbf{capitalization} did not yield any significant impacts.
-
-\textbf{Content: Humour}
-* No overall significant difference between conventional method vs.
-agent using humour for enjoyment.
-Specifically, men enjoyed the agent's jokes more than women.
-\cite{miyamoto2017improving}\cmt{[46]}.
-* Motivation to continue the conversation significant increased after day 2 for the humorous agent \cite{go2021conversational}\cmt{[80]}
-
-\textbf{Style: Language Formality}
-* Users spent more time with the Shakespearean chatbot version with more non-task related user inputs. Enjoyment was measured but no report \cite{elsholz2019exploring}\cmt{[61]}
-* commanding/formal wording was rated significantly more useful than the informal wording; while the informal wording was rated as significantly more annoying than the commanding/formal wording.
-No impact on desirability.
-\cite{jestin2022effects}\cmt{[81]}
-* High conscientiousness (formal) and high extroversion (casual) chatbot personality have higher user engagement. \cite{moilanen2022measuring}\cmt{[82]}
-* Analysis of ease of use reveals that there are no significant main effects for platform questionnaire vs. chatbot, and conversational style formal vs. casual.\cite{kim2019comparing}\cmt{[89]}
-
-\textbf{Social talk / elaborate}
-* Not significant importance between introvert and extrovert agents. But the machine-like speaking agent is rated lower. \cite{roy2021users}\cmt{[71]}
-* usefulness depended on the task \cite{haas2022keep}\cmt{[78]}
-* High extroversion chatbot personality have the higher user engagement \cite{moilanen2022measuring}\cmt{[82]}
-
-\textbf{Disfluency}
-* Using moderately repetitive utterances resulted in higher desire to continue the dialogue with the agent. \cite{yang2021effect}\cmt{[72]}
-* Interjections did not have any impacts of cognitive workload \cite{ceha2022expressive}\cmt{[77]}
-
-\textbf{Proactive}
-* Different framing has impacts on the perceived disruptiveness of the agent. \cite{xiao2021let}\cmt{[73]}
-
-\textbf{Prosody}
-* No impact on annoying, undesirable, useful \cite{jestin2022effects}\cmt{[81]}
-* Dialog-style conversation using prosodic cues is rated as less easy to understand than the reading-style \cite{misu2011toward}\cmt{[83]}
-
-\textbf{Combined}
-* (Extraverted: emoticons, self-disclosure, talkative, affective language / Introverted: formal style, less talkative) all personalities have similar usability ratings.
-Also, users have greater desire to interact with the extraverted chatbot \cite{volkel2022user}\cmt{[75]}
-* (Politeness: affective language + elaborateness of speech) no impact on usability \cite{hu2022polite}\cmt{[76]}
-
-%%
-\subsubsection{Accuracy}
-%%
-There are only a few studies that measured the perception of accuracy of conversational agents for an interaction.
-A couple of studies reported the effect of the use of language style of \textbf{lexical alignment}.
-One study of a text-based CA resulted in higher perceived response accuracy \cite{huiyang2022improving}\cmt{[17]}, while the other study with voice-based CA did not find any significant differences \cite{linnemann2018can}\cmt{[15]}.
-Dubiel et al.'s study \cite{dubiel2020persuasive}\cmt{[60]} on \textbf{prosody} did not find any significant differences on the rating for accuracy across agents with different speech rates and pitch.
-
-\textbf{Social talk}
-* Introverted agent is more efficient. \cite{roy2021users}\cmt{[71]}
-* Efficiency depended on the task \cite{haas2022keep}\cmt{[78]}
-
-\textbf{Language Formality}
-* commanding/formal wording was rated significantly more effective than informal wording \cite{jestin2022effects}\cmt{[81]}
-
-\textbf{Prosody}
-* No impact on effectiveness \cite{jestin2022effects}\cmt{[81]}
-
-\textbf{Repair}
-* One reason for choosing repair strategy preference is efficiency and efficacy. \cite{ashktorab2019resilient}\cmt{[88]}
-
-%%
-\subsubsection{Satisfaction}
-%%
-Several research have investigated into how the usage of \textbf{affective language} impacts the satisfaction people feel when interacting with a CA.
-Compared to a text-based chatbot with a static and neutral response, users reported higher service encounter satisfaction conversing with a chatbot that responded with dynamic, sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}.
-However, the same effect is not observed for a voice-based CA as Yang et al.
-did not find any difference in user satisfaction rating between the emotional-expressing agent vs.
-non-emotional expressing agent \cite{yang2017perceived}\cmt{[44]}.
-On the language style used by CAs, both \textbf{disfluency} \cite{pfeifer2009should}\cmt{[12]} and \textbf{emoticons} \cite{wilhelm2022keep}\cmt{[28]} did not have any significant effects on user satisfaction.
-
-Studies have found that presentation formats have significant effects on user satisfaction.
-In Choi et al's study \cite{choi2020nobody}\cmt{[54]} on the speech rate aspect o f\textbf{prosody} for a voice-based agent, they found that user satisfaction is higher for the default rate compared to using a faster rate.
-User feedback reflected that the faster rate was mechanical and harder to understand.
-For text-based chatbots, the addition of \textbf{response delay} increased the perception of overall user satisfaction, as the timing is similar to human-human communications and felt right \cite{gnewuch2018faster}\cmt{[19]}.
-
-\textbf{Style: Language Formality}
-* Modern language had higher usability score compared to Shakespearean language \cite{elsholz2019exploring}\cmt{[61]}
-* There is no significant effect on customer satisfaction of the CA between low-status and high-status languages. \cite{habler2019effects}\cmt{[63]}
-
-\textbf{Format: Prosody}
-* There is no significant effect on customer satisfaction of the CA between male-gendered and female-gendered voices. \cite{habler2019effects}\cmt{[63]}
-
-\textbf{Social talk}
-* Not significant importance between introvert and extrovert agents. But the machine-like speaking agent is rated lower. \cite{roy2021users}\cmt{[71]}
-
-\textbf{Combined}
-* (Politeness: affective language + elaborateness of speech) no impact on user satisfaction \cite{hu2022polite}\cmt{[76]}
-
-%%%%%
-\subsection{Perception of Agent's Ability}
-%%%%%
-
-This section discusses how user perceives the agent's ability in conditions with different conversational architecture elements.
-It is aiming at measuring the differences in the perception with similar system's capabilities.
-Out of the two variables used to evaluate this perception, \textit{Intelligence} measures whether the agent is knowledgeable, sensible, and is seem as overall intelligent.
-\textit{Competence} on the other hand measures the overall perception on how well the agent is handling the conversation.
-Out of the list of publications that were evaluated, there are only a few papers that measured the perceived ability of an agent.
-
-\textit{To be incorporated}
-
-\textbf{Repair}
-* perceived quality of the interaction is muhc higher in repair condition when the agent made a mistake; rating is lower if no mistake was present. \cite{cuadra2021my}\cmt{[67]}
-
-%%
-\subsubsection{Intelligence}
-%%
-
-On analyzing the impact of different language styles on the perception of intelligence, a couple of papers studied the effect of including \textbf{disfluencies} into agent's speech.
-One paper found that there is no significant impact on how knowledgeable the agent is perceived as \cite{pfeifer2009should}\cmt{[12]}.
-Another study showed that using fillers like "um" and "uh" decreased the agent's perceived intelligence overall \cite{jeong2019exploring}\cmt{[10]}.
-Upon further analysis, the authors noticed a difference between task vs.
-social conversations, as users perceive the intelligence to be lower in task-oriented situations, but the perception of intelligence is slightly increased in social-oriented situations.
-The use of \textbf{lexical alignment} did not seem to impact user's perception of an agent's intelligence, as there is no significant difference reported in the agent's domain knowledge between the aligned vs.
-non-aligned conditions.
-
-On the impact of presentation format, Dubiel et al's study on \textbf{prosody} using different speech rates and pitches did not yield any significant differences on the agent rating for knowledgeable.
-
-\textbf{Prosody}
-* VA using kin's voice is rated as more intelligent. \cite{chan2021kinvoices}\cmt{[74]}
-
-\textbf{Repair}
-* One reason for choosing repair strategy preference is perceived intelligence and capability. \cite{ashktorab2019resilient}\cmt{[88]}
-
-%%
-\subsubsection{Competence}
-%%
-
-There are only a couple of papers that discussed the impact of conversational architecture elements on the perception of competence.
-For \textbf{affective language} in the language style content category, participants rated the agent higher in competence when it has higher patiency and expressed its feelings to users.
-In Cox et al's study on \textbf{formality}, the authors did not find a significant difference in competence between using casual vs.
-formal conversational styles.
-
-\textbf{Style: Language Formality}
-*  Low-status language resulted in higher achieved performance ratings \cite{habler2019effects}\cmt{[63]}
-
-\textbf{Format: Prosody}
-* There is no significant effect on perceived performance of the CA between male-gendered and female-gendered voices. \cite{habler2019effects}\cmt{[63]}
-* For expertise, multilingual students rated higher the non-native English-speaking virtual human. \cite{feijoo2021effects}\cmt{[70]}
-
-\textbf{Format: Proactivity}
-* Certain proactive styles like notification strategy (conservatively proactive, letting participants know that the agent has found a solution) was evaluated as significantly higher perceived competence compared to the non-strategy.
-\cite{kraus2020effects}\cmt{[64]}
-
-%%%%%
-\subsection{Perception of Social Connection with an Agent}
-%%%%%
-
-This section discusses user's perception of their social connection with a conversational agent.
-Social presence, conversation tone, and intimacy are the three variable used to evaluate this perception.
-\textit{Social presence} measures user's perceived social distance with an agent, such as social presence, connectedness, and psychological distance.
-\textit{Conversation tone} measures user perceptions on the way an agent is speaking to them, such as appropriateness of tone, empathetic, or emotionally expressive.
-\textit{Intimacy} measures the quality of relationship users have with CAs, such as intimacy, social attraction, or similarity with each other.
-
-Out of the list of publications that were evaluated, there is overall consensus that the use of affective language positive affects the perception of social connection with an agent.
-Conversational architecture elements related to the format of the conversation, like adding response delays, or changing the pitch of speech are commonly investigated for perception of social connection with an agent.
-There are only a few papers exploring the effect of language styles on the perceived social connection with an agent.
-
-%%
-\subsubsection{Social Presence}
-%%
-For conversational architecture elements related to language content, studies have shown the use of \textbf{affective language} increased the perception of social presence of an agent.
-In Diederich et al's study, participants conversing with a text-based agent using dynamic, sentiment-adaptive responses reported a higher social presence compared to a CA that provides static, neutral responses \cite{diederich2019emulating}\cmt{[25]}.
-In another study, participants felt closer to the agent psychologically when the CA expressed its feelings \cite{lee2019s}\cmt{[55]}.
-On the use of \textbf{humour}, Lee et al.
-did not find any significant difference in social presence between the humourous and non-humourous agent \cite{lee2019s}\cmt{[55]}.
-
-For text-based conversational agents, including a \textbf{response delay} increased users' perception of social presence of the agent, with participants feeling a sense of human contact and sociability with the agent \cite{kim2020can}\cmt{[24]}.
-Westerman et al.
-\cite{westerman2019believe}\cmt{[9]} studied the presence of typos and capitalized words in a text-based agent's responses.
-They found the inclusion of \textbf{typos} negatively impacted the social distance and connection with an agent, while \textbf{capitalization} did not have any significant effects.
-On the effect \textbf{prosody} on a voice-based agent, using an affective tone of voice resulted in perceived higher social connectedness with the agent \cite{kim2020can}\cmt{[24]}.
-
-\textbf{Content: Affective Language (Voice)}
-* Model aiming to elicit position emotions from users received higher emotional connection \cite{lubis2019positive}\cmt{[43]}
-
-\textbf{Format: Response Delay}
-* Delayed response is associated with higher social presence \cite{gnewuch2022opposing}\cmt{[20]}
-
-\textbf{Content: Affective language and Style: Disfluency}
-* Rated higher that agent listened openly to participants' emotions, as that agent can feel waht the user is feeling. \cite{hu2021enhancing}\cmt{[56]}
-* social condition didn't have an impact on social presence \cite{lubold2016effects}\cmt{[86]}
-
-\textbf{Prosody}
-* VA using kin's voice is rated as more socially present and closer psychological connection with user. \cite{chan2021kinvoices}\cmt{[74]}
-* voice plus social condition has higher social presence than the social condition \cite{lubold2016effects}\cmt{[86]}
-
-\textbf{Humour}
-* Familiarity with the agent is rated higher at the end of the study (day 7) compared to non-humorous agent \cite{go2021conversational}\cmt{[80]}
-
-\textbf{Laughter}
-* Laughter had no impact on social presence of an agent \cite{niewiadomski2013laugh}\cmt{[85]}
-
-%%
-\subsubsection{Conversation Tone}
-%%
-
-The use of \textbf{affective language} has a significant affect on the perception of the conversation tone by the agent.
-Multiple studies have found that agents conversing with more affective words are seen as more emotionally expressive and empathetic \cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}.
-This effect has been observed across modalities in both text-based as well as voice-based conversational agents.
-
-On the style of language used by the agent, \textbf{formality} did not seem to impact the conversation tone of agent as Cox et al.
-\cite{cox2022does}\cmt{[27]} did not find any significant difference between casual and formal conversational styles for appropriateness of tone.
-The speech format of \textbf{prosody} seem to have an impact on the conversation tone, as a CA speaking with a lower pitch and slower speech rate is rated as more persuasive compared to other voice settings \cite{dubiel2020persuasive}\cmt{[60]}.
-However, there was no significant difference in how powerful or bold the agent's tone was perceived across various prosody settings.
-
-\textbf{Content: Affective language and Style: Disfluency}
-Respond with empathy to the user. \cite{hu2021enhancing}\cmt{[56]}
-
-\textbf{Disfluency}
-* Using moderately repetitive utterances resulted in higher perceived empathy. \cite{yang2021effect}\cmt{[72]}
-
-\textbf{Language Formality}
-* commanding/formal wording was rated significantly more appropriate and assertive than informal wording \cite{jestin2022effects}\cmt{[81]}
-
-\textbf{Prosody}
-* No impact on appropriate and assertive \cite{jestin2022effects}\cmt{[81]}
-* Dialog-style conversation using prosodic cues is rated as more appropriate than the reading-style \cite{misu2011toward}\cmt{[83]}
-
-%%
-\subsubsection{Intimacy}
-%%
-On the use of language content, a conversational agent that included \textbf{self-disclosure} when conversing with participants resulted in higher level of intimacy over time than CAs that did not self disclose \cite{lee2020hear}\cmt{[23]}.
-On the other hand, using the style of \textbf{lexical alignment} by using the words that were already used by the participant did not result in higher quality of relationship with the agent \cite{linnemann2018can}\cmt{[15]}.
-
-There are several studies investigating the effect of conversational format on intimacy with a CA.
-Specifically on voice \textbf{prosody}, using an affective tone of voice increased the perceived intimacy and similarity with an agent \cite{kim2020can}\cmt{[24]}.
-Comparing voice agents with different \textbf{speech rates}, users rated the default rate as more intimate than a faster rate of speech \cite{choi2020nobody}\cmt{[54]}, noting that the default rate is more human-like and natural.
-Westerman et al's study on different text formats of conversation \cite{westerman2019believe}\cmt{[9]} showed that \textbf{typos} negatively impacted the perceived social attraction of the agent, while \textbf{capitalization} did not have any impacts.
-
-\textbf{Disfluency}
-* Interjections did not have any impacts of quality of relationship, but it did result in higher emotional rapport. \cite{ceha2022expressive}\cmt{[77]}
-
-\textbf{Affective Language}
-* social condition didn't have an impact on social presence \cite{lubold2016effects}\cmt{[86]}
-
-\textbf{Prosody}
-* voice and social condition didn't have an impact on social presence \cite{lubold2016effects}\cmt{[86]}
-
-%%%%%
-\subsection{Perception of Agent's Humanness}
-%%%%%
-
-This section discusses user's perception of the agent's humanness aspects.
-Human-likeness, personality traits, and trustworthiness are the three variable used to evaluate this perception.
-\textit{Human-likeness} measures the agent's similarity to humans as well assessed naturalness of interaction.
-\textit{Personality traits} measures perceptions of the agent's characteristics such as likeability, warmth, and friendliness.
-\textit{Trustworthiness} measures if users feel they can trust an agent, and whether the agent is perceived of being truthful.
-
-Out of the list of publications that were evaluated, many papers exploring the impact of language content as well as language style have measurements related to the perception of an agent's humanness.
-There seems to be fewer studies looking into the effect of conversation format on the perception of agent's humanness, as our reivew only found two studies related to voice prosody.
-Out of reviewed conversational architecture elements, one consistent finding is that the style of being lexically aligned with user's utterance did not have any impact on the perception of agent's humanness.
-
-%%
-\subsubsection{Human-likeness}
-%%
-
-On the use of \textbf{affective language}, one study found that CAs with dynamic, sentiment-adaptive responses is perceived as more human than a CA that provides static, neutral responses \cite{diederich2019emulating}\cmt{[25]}.
-Another study using more emotional expressive words in conversation did not find any significant impact on the perceived human-likeness of an agent \cite{zhu2022effects}\cmt{[26]}.
-
-Different language styles have different impacts on user perceptions.
-On language \textbf{formality}, agents using normal style was rated as more human-like compared to formal styles of conversation \cite{ouchi2019should}\cmt{[59]}.
-\textbf{Disfluencies} did not seem to have a significant impact on the perceived humanness or naturalness of an agent \cite{jeong2019exploring}\cmt{[10]}\cite{pfeifer2009should}\cmt{[12]}.
-However, one study noticed a non-significant but positive trend in user's evaluation of the agent using fillers as being more human-like \cite{jeong2019exploring}\cmt{[10]}.
-
-On the impact of different conversation formats, Zhu et al.
-did not find a significant effect of \textbf{prosody} on the perception of humanness between agent using expressive vs.
-non-expressive voices.
-For text-based CAs, the use of \textbf{typos} made the agent seem less human, while the use of \textit{capitalization} did not have any impacts on the perception of humanness \cite{westerman2019believe}\cmt{[9]}.
-Lastly, adding a \textbf{response delay} to a CA has a significant positive effect in the perceived humanness of the agent \cite{gnewuch2018faster}\cmt{[19]}.
-
-\textbf{Style: Disfluency}
-* (Voice) No significant difference in naturalness rating for About Myself text, but showed that naturalness is higher for fluent system compared to disfluent speech \cite{wester2015artificial}\cmt{[14]}.
-
-\textbf{Prosody}
-* VA using kin's voice is rated as more human-like. \cite{chan2021kinvoices}\cmt{[74]}
-* Dialog-style conversation using prosodic cues is rated as less human-like than the reading-style \cite{misu2011toward}\cmt{[83]}
-
-\textbf{Social talk / Elaborateness}
-* Naturalness depends on the task \cite{haas2022keep}\cmt{[78]}
-
-\textbf{Language Formality}
-* No impact on artificial or humanlike perceptions \cite{jestin2022effects}\cmt{[81]}
-
-\textbf{Prosody}
-* Matthew voice is rated as least artificial  \cite{jestin2022effects}\cmt{[81]}
-
-\textbf{Laughter}
-* Laughter was not rated as natural in an agent \cite{niewiadomski2013laugh}\cmt{[85]}
-
-\textbf{Combined}
-* (Politeness: affective language + elaborateness of speech) no impact on likability, but positive politeness interactions are rated as more polite \cite{hu2022polite}\cmt{[76]}
-
-\textbf{Repair}
-* One reason for choosing repair strategy preference is naturalness. \cite{ashktorab2019resilient}\cmt{[88]}
-
-%%
-\subsubsection{Personality Traits}
-%%
-
-There are significant difference found in the effect of language content on the perception of agent's personality traits.
-Conversational agents using emotionally expressive words are rated as more likable \cite{zhu2022effects}\cmt{[26]} and warm \cite{lee2019s}\cmt{[55]}.
-In Healey et al's study \cite{healey2013relating}\cmt{[39]}, there is a significant difference in the variances of the responses for friendliness of the agent between the agent using encouraging words compared to neutral utterances.
-As with the use of \textbf{humour}, participants rated the humorous agent as having a sense of humor, but it was not rated as more likable \cite{ceha2021can}\cmt{[57]}.
-
-On the impact of language style, various studies on \textbf{lexical alignment} showed that there is no significant impact on the perception of the personality traits related to likability \cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}, friendliness \cite{spillner2021talk}\cmt{[18]}, or politeness \cite{spillner2021talk}\cmt{[18]}.
-Studies on the \textbf{formality} of language has demonstrated that casual conversational style is perceived as warmer than formal style \cite{cox2022does}\cmt{[27]}.
-Also agents using a normal style as compared to a formal style is perceived as more friendly, fun, and kind \cite{ouchi2019should}\cmt{[59]}.
-As for the use of \textbf{disfluency}, there was no statistical significance found in the perceived likability rating \cite{jeong2019exploring}\cmt{[10]}\cite{pfeifer2009should}\cmt{[12]}.
-Jeong et al.
-\cite{jeong2019exploring} found a significant interaction effect between disfluency (using fillers) and the context of the conversation (task vs.
-social), as users considered agents using fillers as entertaining and fun in social conversations, but inappropriate in task oriented situations.
-
-In the list of reviewed papers, there was only one study measuring the perceived trustworthiness of an agent based on different conversational format of \textbf{prosody}.
-Dubiel et al.
-found that an agent using slower speech rate is perceived as more trustworthy as compared to other voice prosody settings \cite{dubiel2020persuasive}\cmt{[60]}.
-
-\textit{To be incorporated}
-
-\textbf{Content: Humour}
-* An agent that uses humourous content is assessed to be more funny \cite{khooshabeh2011does}\cmt{[37]}.
-
-\textbf{Style: Disfluency}
-* (Voice) Both About Myself and Speed Dating ratings has shown system scored significantly differently on the Big-5 personality traits.
-Disfluency makes the voice sound more neurotic, less open, less extrovert and less conscientious \cite{wester2015artificial}\cmt{[14]}.
-
-\textbf{Format: Prosody}
-* Low voice pitch rated not as friendly as the other ones. No impact on other traits like assertive and politeness. \cite{tolmeijer2021female}\cmt{[62]}
-* VA using kin's voice is rated as more likable. \cite{chan2021kinvoices}\cmt{[74]}
-* No impact on entertaining or friendly  \cite{jestin2022effects}\cmt{[81]}
-
-\textbf{Repair}
-* When VA corrected in the condition it didn't make a mistake, it is seen as anxious. Otherwise it is perceived as calm and emotionally stable. \cite{cuadra2021my}\cmt{[67]}
-* One reason for choosing repair strategy preference is politeness. \cite{ashktorab2019resilient}\cmt{[88]}
-
-\textbf{Social talk}
-* Using more social talk is positive correlated with extroversion. \cite{volkel2021manipulating}\cmt{[68]}
-* Not significant importance between introvert and extrovert agents. \cite{roy2021users}\cmt{[71]}
-* Likability depends on the task \cite{haas2022keep}\cmt{[78]}
-
-\textbf{Language Formality}
-* Informal wording was rated as strongly more entertaining and friendly than the commanding/formal wording. \cite{jestin2022effects}\cmt{[81]}
-
-\textbf{Agreeableness}
-* Being highly confrontational (less agreeable) is rated as less conscientious \cite{volkel2021manipulating}\cmt{[68]}
-* Designing for more agreeable resulted in personality rated as more agreeable \cite{volkel2021examining}\cmt{[69]}
-
-\textbf{Combined}
-* (Extraverted: emoticons, self-disclosure, talkative, affective language / Introverted: formal style, less talkative) extraverted personality rated as more extraverted \cite{volkel2022user}\cmt{[75]}
-
-%%
-\subsubsection{Trustworthiness}
-%%
-
-For the use of language content, agents using more \textbf{affective language} is seen as less trustworthy, as users felt it was being overly familiar \cite{andrews2012system}\cmt{[38]}.
-On the other hand, users conversing with agents that used \textbf{self-disclosure} content reported more trust towards the agent compared to the non disclosure group \cite{lee2020hear}\cmt{[23]}.
-
-None of the studies included in this review has found any significant impact of language style, \textbf{lexical alignment} \cite{hoegen2019end}\cmt{[31]}\cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}, \textbf{disfluency} \cite{pfeifer2009should}\cmt{[12]}, and \textbf{emoticons} \cite{wilhelm2022keep}\cmt{[28]} on the perceived trustworthiness of CAs.
-Similarly for conversational format, there is not significant difference on the rating for truthfulness of the agent across different voice \textbf{prosody} settings \cite{dubiel2020persuasive}\cmt{[60]}.
-
-\textbf{Format: Prosody}
-* No significant difference in trust ratings across different voice prosody settings with differences in pitch. \cite{tolmeijer2021female}\cmt{[62]}
-* No impact on trustworthiness  \cite{jestin2022effects}\cmt{[81]}
-
-\textbf{Format: Proactivity}
-* Overall trust in the system did not differ significantly.
-The intervention style is less trusted than conservative strategies - too obstructive and imposing.
-Proactive should be subtle  \cite{kraus2020effects}\cmt{[64]}
-
-\textbf{Language Formality}
-* No impact on trustworthiness \cite{jestin2022effects}\cmt{[81]}
-
-%-------------
-\section{Discussions}
-
-%Research challenges and opportunities
-
-%Ethical considerations
-
-%Limitations and future work
-
-\subsection{RQ1 - synthesis of conversation architecture elements}
-
-Sometimes a study is covering multiple conversational element cues, hard to break it out.
-For example, extroverted personality used in \cite{volkel2022user}\cmt{[75]} has emoticons, affective language, talkative, and self-disclosure.
-Need to break it down.
-
-Also, breaking down "personalities" to its core components.
-
-\subsection{RQ2 - synthesis of perceptions}
-
-\subsubsection{Inconsistencies in Perception Measures}
-
-A major roadblock in synthesizing the findings from existing academic research is the diversity and inconsistency of measurements towards the anthropomorphized perception of agents.
-It is difficult to assess whether perception measures should be compared with each other.
-Also, some measures combined anthropomorphized perceptions into a composite score, which makes it impossible to separate the perceptions into more granular details.
-
-Based on the literature reviewed in this paper, we noticed that similar perception concepts were \textbf{measured in different ways} through different surveys.
-For example, there are several approaches to measure the perceived \textit{human-likeness} of an agent.
-A commonly used survey is adapted from the Godspeed questionnaire \cite{bartneck2009measurement}, which measures human-likeness based on user's impression of the agent as fake / natural, machinelike / humanlike, unconscious / conscious, and artificial / lifelike (used by \cite{hoegen2019end}\cmt{[31]}, \cite{jeong2019exploring}\cmt{[10]} and \cite{ouchi2019should}\cmt{[59]}).
-Another way to measure human-likeness is adapted from Holtgraves et al.'s \cite{holtgraves2007perceiving} questionnaire, which asks users to assess the agent's perceived human-likeness, skillfulness, thoughtfulness, politeness, responsiveness and engagement (used by \cite{diederich2019emulating}\cmt{[25]} and  \cite{gnewuch2018faster}\cmt{[19]}).
-One study \cite{westerman2019believe}\cmt{[9]} used the Ascend of Man pictorial scale \cite{kteily2015ascent} as the measure of perceived human-likeness.
-It is unclear whether these different measures of perceived human-likeness are similar enough to be compared with each other.
-
- In addition to different methods used to measure for the same perception, our detailed analysis revealed that the measures using the same label may have \textbf{drastically different meanings}.
-In Diedrech et al.'s study \cite{diederich2019emulating}\cmt{[25]}, \textit{empathy} measure is adapted from \cite{yan2013role} assessing whether the CA gives users individual or personal attention.
-In Daher et al.'s study \cite{daher2020empathic}\cmt{[58]}, they also measure the perception of empathy, but it is using the RoPE Scale \cite{charrier2019rope} with questions like "the robot cares about my feelings" or "the robot comforts me when I am upset." These two different measures of empathy seem to have different underlying meanings, one assessing the personalization aspect of CAs, while the other is assessing the emotional aspect of CAs.
-Another example is the measurement of \textit{trustworthiness}, with some constructs measuring the level of sensitive information user's are willing to share \cite{dinev2006privacy}, and some measuring the honesty and truthfulness of an agent \cite{lee2017enhancing}.
-
-Lastly, there are \textbf{composite measures} of anthropomorphized perception across different categories, making it difficult to break down perceptions into granular details for analysis.
-One such example is Ma et al's study \cite{ma2022ask}\cmt{[29]} on different approaches for CAs to reply to users' uncertain queries.
-UX score is used to measure the perception of an agent, which asks whether the user thinks the CA's response is pleasing / trustworthy / natural / acceptable / shorten the distance between CA and user.
-While the study has found significant impact of the use of formal language on UX score, it is not possible to breakdown the measure into perceptions of interaction (pleasing, acceptable), social connection (shorten the distance between CA and user), and humanness (natural, trustworthy).
-Similar for Hoegen et al.'s study \cite{hoegen2019end}\cmt{[31]} on the impact of conversational style matching, it is not possible to separate the overall interaction score into different perceptions as the composite measure contains questions measuring different categories of perceptions like interaction (engaging) and humanness (trust, likable).
-
-In recent years there has been some effort towards unifying the evaluation of conversational agents, such as the work by Finch et al.
-\cite{finch2020towards} presenting a comprehensive analysis of current evaluation protocols.
-More work is needed to categorize and consolidate perception measures to make them consistent and comparable across various studies.
-
-%For discussions on mental well beings, agent using emojis is rated higher for attitude (emotional connection) .
-However, for agent with discussing physical well being, agent using emojis is rated as lower for attitude.
-%Attitude has emotional connection, coherent - coherent is an ability perception, vs. emotional connection is a social connection perception. \cite{fadhil2018effect}\cmt{[52]}
-
-\subsubsection{Relationship between perceptions}
-
-Response delay: social presence has a significant effect on intention to use. 
-\cite{gnewuch2022opposing}\cmt{[20]}
-
-Perceived intelligence positively associated with perceived usefulness, perceived ease of use, initial trust, and perceived anthropomorphism.
-Perceived anthropomorphism is associated with perceived enjoyment, and intention to adopt.
-Perceived usefulness and perceived enjoyment impacts intention to adopt.
-\cite{moussawi2021perceptions}\cmt{[36]}
-
-The size of the effect for language we observed is clearly higher than the size of the effect for voice. \cite{habler2019effects}\cmt{[63]}
-
-VA self-repair can backfire if time or accuracy is of the essence. (repair and accuracy) \cite{cuadra2021my}\cmt{[67]}
-
-\subsection{RQ3 - relationship between conversation architecture elements and perceptions}
-
-\subsubsection{Other Influencing Factors}
-
-While the discussion in the Framework section above focuses on the overall effect of conversational architecture elements on anthropomorphized perceptions,  there are other nuanced influencing factors that impact user perceptions of agents.
-
-Depending on the \textbf{type of conversation} user is having with agents, it may lead to differences in perceptions for similar conversational architecture elements.
-Cox et al.
-\cite{cox2022does}\cmt{[27]} found that the perceived competence and appropriateness of tone of different language formality styles depend on the sensitivity of information discussed in the conversation.
-In this particular study, a formal language style is preferred in medical history discussions as it is matching to the expectation of users, but there is no difference in perception between formal and casual styles when discussing income level and credit scores.
-In Jeong et al's study \cite{jeong2019exploring}\cmt{[10]}, users found the agent using fillers less intelligent and likable in a task-oriented conversation, but found the same agent using fillers as slight more intelligent and likable in a social-oriented conversation.
-Another factor that could impact perceptions is the \textbf{anonymity} of conversation.
-Based on user feedback, Lee et al.
-\cite{lee2020hear}\cmt{[23]} found that the anonymity of a conversational agent is a driving factor encouraging people to self disclose without having to worried about judgements from the CA.
-The perception of the agent may be different if the user's identity is not anonymous.
-
-Other than the type of conversation, \textbf{user's characteristics} can also be influencing factors on their perception of agents.
-For example, the effect of matching user's conversational style on perception of agents depend on user's own conversational style, as participants with high consideration conversational style rated the lexically aligned agent as more trustworthy \cite{hoegen2019end}\cmt{[31]}.
-In the study by Cox et al.
-\cite{cox2022does}\cmt{[27]}, participants with lower levels of privacy concerns as well as those who believe in robotic intelligence found the chatbot more enjoyable, warm, competent and appropriate.
-Similarly, participants with positive attitudes towards computers were significantly more likely to indicate that the usage of fillers by agents was a positive aspect of the conversation, compared to participants with neutral attitudes towards computers \cite{pfeifer2009should}\cmt{[12]}.
-Lastly, user's prior experience with conversational agents could impact perception of agents.
-Experienced users perceived the agent with a response delay as lower in social presence compared to the one without delay, as it is seen as inefficient to wait for the CA to respond.
-However, novice users perceived higher social presence conversing with the CAs using response delays as it is more similar to conversations with human partners \cite{gnewuch2018faster}\cmt{[19]}.
-
-* Format: Response delay - Novice users perceived the agent as more socially present, but experienced users had a negative effect \cite{gnewuch2022opposing}\cmt{[20]}
-* Content: Humour - no overall significant difference between conventional method vs.
-agent using humour for enjoyment.
-Specifically, men enjoyed the agent's jokes more than women.
-\cite{miyamoto2017improving}\cmt{[46]}.
-* Format: Proactivity - significant interaction between proactive dialogue strategies and task difficulty for perceived competence and perceived reliability.
-For easier tasks, system help is not really required.
-\cite{kraus2020effects}\cmt{[64]}
-* Preference for the level of social talk depended on the task, even within the same transactional context, as users preferred high level for playing a song, but low level for writing a text.
-\cite{volkel2021manipulating}\cmt{[68]}
-* Correlation between user's personality of agreeableness vs. preference for agreeable level of chatbot \cite{volkel2021examining}\cmt{[69]}
-* For expertise, multilingual students rated higher the non-native English-speaking virtual human. \cite{feijoo2021effects}\cmt{[70]}
-* Participants felt irritated when humorous statements were made when they talked about experiencing sadness \cite{go2021conversational}\cmt{[80]}
-
-%\subsubsection{Study Design}
-
-%\textbf{Interview vs experiment}
-%* Humour - what's said vs. study results
-
-%\textbf{Observer study vs. interaction study}
-%* In observer study, participants attributed higher integrity (trustworthiness), response accuracy and likeability to the agent with lexical alignment, but this effect was not observed in the interaction study.
-Also, interaction study had lower cognitive demand but no effect in the observer study.
-\cite{linnemann2018can}\cmt{[15]}
-%* \cite{zhu2022effects}\cmt{[26]}
-%* \cite{cox2022does}\cmt{[27]}
-
-\subsubsection{Modality}
-
-TBD 
-Did not separate - because similar 
-Affective language - may be a difference? significant for text, but not as much for voice?
-
-\subsubsection{Gaps}
-
-Combined effects
-* integrated mental model \cite{knijnenburg2016inferring}\cmt{[34]}
-* Anthropomorphized chatbot (text) using affective language (emotional expressions), self-referencing, emoticons, response delays.
-Resulted in higher perceived anthropomorphism, which in result led to lower negative word of mouth and loss of trust.
-anthropomorphic design is beneficial not only to initial trust but also to the ongoing trust relationship \cite{seeger2021chatbots}\cmt{[35]}
-
-Lack of investigations - name a few areas
-
-%\subsubsection{Human-human vs. Human-machine}
-
-%* Impact of lexical alignment on people's perceived annoyance and likability differed in HHI (higher) and HCI (no impact). \cite{huiyang2022improving}\cmt{[17]}.
-
-\subsubsection{Ethical Considerations}
-
-Self-disclosure encourage higher trust and intimacy, to disclose sensitive information. Who have access to this data? need to be aware of privacy / data sharing practices. \cite{lee2020hear}\cmt{[23]}
-
-Evidence for the influence of voice gender and pitch on stereotypical trait attribution.
-Active trait attribution is missing as most participants attributes to the negative side of traits for CAs.
-\cite{tolmeijer2021female}\cmt{[62]}
-
-The social and emotional benefits of self-repair in interaction need to be balanced against the creepiness of the monitoring and modelling needed to make self-repair possible.
-\cite{cuadra2021my}\cmt{[67]}
-
-\section{Conclusions}
-
-TBD
-
-%%
-%% The acknowledgments section is defined using the "acks" environment
-%% (and NOT an unnumbered section). This ensures the proper
-%% identification of the section in the article metadata, and the
-%% consistent spelling of the heading.
-\begin{acks}
-To Robert, for the bagels and explaining CMYK and color spaces.
-\end{acks}
-
-%%
-%% The next two lines define the bibliography style to be used, and
-%% the bibliography file.
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{references}
-
-%%
-%% If your work has an appendix, this is the place to put it.
-\appendix
 
@@
 %% End of file `paper.tex'.
+
+\multirow{3}{*}{Perception of Interaction with Agent}    & Usability       \\
+ & Engagement                  \\
+ & Satisfaction                \\ \midrule
+\multirow{3}{*}{Perception of Agent's Ability}              & Intelligence     \\
+ & Competence                  \\
+ & Trust                       \\ \midrule
+\multirow{3}{*}{Perception of Social Connection with Agent}  & Conversation Tone  \\
+ & Social Presence         \\
+ & Intimacy                    \\ \midrule
+\multirow{2}{*}{Perception of Agent's Humanness}            & Human-likeness   \\
+ & Personality Traits          \\ \bottomrule

### 2023-02-13 paper.tex
first draft complete! yay

@@
 \begin{abstract}
-  TBD
+The natural language interactions of conversational agents encourage users to attribute humanlike qualities to them, but we don't yet have a systematic understanding on how to design conversation architecture to orchestrate these anthropomorphized perceptions.
+Through a comprehensive review on papers with empirical studies on the impact of conversation architecture elements on perception of agents, we collected explored connections in literature to create a consistent taxonomy for anthropomorphized perceptions, and conversation architecture elements.
+Also, we created a generalized framework of the relationship between conversation architecture and perceptions based on the number of impacts found in the reviewed studies.
+In our analysis, we found there are inconsistencies in the measurements for perceptions of agents, as well as influencing factors other than conversation architecture that could impact anthropomorphized perceptions of agents.
+Also, it is important to consider ethical aspects of designing anthropomorphized perceptions of CAs as it may have negative consequences to users.
 \end{abstract}
@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{conversational agents, user perception, conversational architecture, social cues}
+\keywords{conversational agents, user perception, conversational architecture, anthropomorphized perceptions, social cues}
 
@@
 
-\section{Introduction (Not Ready)}
+\section{Introduction}
 
@@
 One of the key factors for anthropomorphized perception is how conversational agents convey information through verbal or non-verbal cues.
-Studies have found that conversational agents are perceived as more socially present and emotionally intelligent if they use sentiment-adaptive response based on user's utterances, resulting in higher user satisfaction \cite{diederich2019emulating}\cite{yang2017perceived}.
+Studies have found that conversational agents are perceived as more socially present and emotionally intelligent if they use affect language such as sentiment-adaptive response based on user's utterances, resulting in higher user satisfaction \cite{diederich2019emulating}\cite{yang2017perceived}.
 Also, CAs that mimic user behaviour through lexical alignment reduce users' cognitive workload, resulting in higher engagement with the interaction \cite{spillner2021talk}.
-Non-verbal cues such as expressive prosody contribute to higher perceived intimacy with the user, as well as higher perceived enjoyment and ease of use \cite{kim2020can}.
-However, conversational architecture design may lead to negative consequences, such as an agent with an extroverted personality may be seen as less trustworthy, as users are irritated by the system's overly familiar attitude \cite{andrews2012system}.
+Non-linguistic cues such as expressive prosody contribute to higher perceived intimacy with the user, as well as higher perceived enjoyment and ease of use \cite{kim2020can}.
+While there is existing research on the impact of conversation architecture on anthropomorphized perceptions of agents, their findings are hard to generalize due to obstacles in consistency of taxonomy and measures.
+%However, conversational architecture design may lead to negative consequences, such as an agent with an extroverted personality may be seen as less trustworthy, as users are irritated by the system's overly familiar attitude \cite{andrews2012system}.
 
-Even though there are existing research efforts investigating the effect of various conversational architecture elements on the anthropomorphized perception of agents, there is no clear view on the overall landscape on the state of research to understand what has been studied and what needs more efforts.
-Some reasons for this gap could be due to the lack of consistency in perception measures such as humanness or empathy.
-There are various questionnaires used in the studies (e.g.
-Godspeed Questionnaire) but their definitions for perceptions may be different.
-Also, there are various confounding factors like prior experience and domain of usage that makes it hard to generalize design principles for anthropomorphized perception of agents.
+ There have been recent efforts to systematically analyze UX measurements used to evaluate conversational agents.
+In Clark et al's review for the state of speech interfaces, the authors created a list the different concepts used to measure disembodied voice-based agents such as user attitudes and task performance \cite{clark2019state}.
+Rapp et al.
+\cite{rapp2021human} analyzed literature related specifically to text-based CAs, where the themes emerged from their analysis has aspects related to the anthropomorphized perceptions, like humanness and emotional experience.
+Most recently, Zheng et al's literature review on the UX research of CAs \cite{zheng2022ux} categorized the metrics based on the type of method used, including technical measures like system error rate and perception measures like perceived social presence.
+Specifically to measures related to anthropomorphized perceptions, there is a gap of research to systematically analyze the different aspects of these perceptions, as well as a consistent taxonomy to refer to them.
+Similarly for conversation architecture elements, there is existing research to systematically analyze them, like Feine et al \cite{feine2019taxonomy}'s overall framework provides consistent categories for social cues.
+However, it is unknown which conversation architecture elements have impacts on the perceptions of agents.
+Lastly, while there are various studies investigating the effect of  conversational architecture elements on the anthropomorphized perception of agents, we did not find any systematic review and analysis to generalize the findings into a usable framework.
 
-This paper attempts to address this gap in knowledge by investigating the following research questions: (RQ1) How does the specifics of conversational architecture design affect the anthropomorphized perception of CAs?
-and (RQ2) How does the specifics of conversational architecture design affect the perception of interaction with CAs?
-Through a comprehensive review of the existing literature, this paper presents the synthesis of a design framework developed based on X number of paper published between 2010 and 2022.
-The framework associated four categories of perception - interaction, ability of the agent, human attributes of the agent, and social connections with the user, with four categories of conversational architecture elements - verbal (content, style), visual (CMC), auditory (voice qualities, vocalizations), and chronemics adapted from Feine et al \cite{feine2019taxonomy}.
+We are addressing this research gap by analyzing how to design conversation architecture in order to orchestrate anthropomorphized perceptions of conversational agents.
+First, we want to understand (RQ1) what aspects of anthropomorphized perceptions are being explored that are affected by conversation architecture.
+Conversation architecture has various aspects that affect a CA's utterances such as the use of humour, emoticons, or lexical alignment.
+This leads to our second research question: (RQ2) what are the elements of conversation architecture that are relevant to anthropomorphized perceptions?
+Lastly, we want to understand the impact of conversation architecture on perceptions of agent, which leads to our third research question: (RQ3) what are the relationships between the specifics of conversation architecture elements and the anthropomorphized perceptions of CAs?
 
-<One paragraph summarizing results>
+To answer these questions, we need to synthesize existing literature by performing a comprehensive review from 2010 to 2022 on the impact of conversation architecture elements on anthropomorphized perceptions of CAs (n=57).
+We collected perceptions that are affected by conversation architecture and grouped them into four categories and eleven themes (Table \ref{tab:perceptions}).
+Similarly, we analyzed the conversation architecture elements explored in literature and grouped them into three categories and ten themes (Table \ref{tab:cues}).
+Lastly, we coded the explored connections between conversation architecture and perceptions and demonstrated the impacted relationship into a generalized framework (Figure \ref{fig:heatmap-impact}).
+Through our analysis, we also found that there are inconsistencies on how anthropomorphized perceptions are measured across studies, as well as influencing factors other than conversation architecture that may be impacting the perceptions of agents.
 
-<One paragraph outlining contributions to the HCI community>
-* Synthesize existing framework into design framework \newline
-* Point out gaps in research \newline
+This work contributes to the HCI community by presenting an in-depth analysis on the impact of conversation architecture on anthropomorphized perceptions.
+We created a taxonomy for perceptions and conversation architecture elements to provide consistent terms that can be used in future research.
+Also, our analysis extends existing reviews on UX research of CAs \cite{clark2019state}\cite{rapp2021human}\cite{zheng2022ux} by providing a generalized framework outlining the relationships between conversation architecture and anthropomorphized perceptions.
+This framework provides the foundational knowledge to design conversation agents to solicit specific social responses from users.
 
-In the remainder of the paper, we first review the existing literature on design frameworks for conversational agents and measures of anthropomorphized perceptions.
-We then describe our literature review and data analysis process, following by describing the design framework synthesized based on findings of the collected literature corpus.
-Finally, we discuss the critical gaps in research identified through our analysis, and propose key opportunities for future research.
-
-Design the conversational agents
+In the remainder of the paper, we first outline our literature review and data analysis process, as well as the characteristics of the papers in our reviewed corpus.
+Following that, we describe in detail the taxonomy of anthropomorphized perceptions, taxonomy of conversation architecture element, as well as the framework on the relationships between perceptions and conversation architecture.
+Finally, we discuss the research challenges and opportunities as well as ethical considerations for designing conversational architecture to orchestrate anthropomorphized perceptions of conversational agents.
 
@@
 %\cite{finch2020towards} Towards unified dialogue system evaluation: A comprehensive analysis of current evaluation protocols
-
-%Synthesis on conversational architecture
-
-%Synthesis on measures
-
-%Connections between conversational architecture elements and measures
 
@@
 
-TBD
-
 \subsection{Anthropomorphized Perceptions}
@@
 \resizebox{\textwidth}{!}{%
-\begin{tabular}{@{}p{3.1cm} | p{2cm} | p{4cm} | p{1.5cm} | p{6cm} @{}}
+\begin{tabular}{@{}p{0.17\textwidth} | p{0.12\textwidth} | p{0.20\textwidth} | >{\centering}p{0.09\textwidth} | p{0.42\textwidth} @{}}
 %!{\vrule width 1.2pt} 
@@
 \\ \Xhline{1.2pt}
-\multirow{3}{*}{\parbox{3cm}{Perception of Interaction with Agent}}
+\multirow{3}{*}{\parbox{0.16\textwidth}{Perception of Interaction with Agent}}
     & Usability & accuracy, ease of use, efficiency, helpfulness & 23 
-    & \cite{ashktorab2019resilient}\cmt{[88]}
-    \cite{ceha2022expressive}\cmt{[77]}
-    \cite{chan2021kinvoices}\cmt{[74]}
-    \cite{choi2020nobody}\cmt{[54]}
-    \cite{cuadra2021my}\cmt{[67]}
-    \cite{dubiel2020persuasive}\cmt{[60]}
-    \cite{elsholz2019exploring}\cmt{[61]}
-    \cite{haas2022keep}\cmt{[78]}
-    \cite{habler2019effects}\cmt{[63]}
-    \cite{healey2013relating}\cmt{[39]}
-    \cite{hu2022polite}\cmt{[76]}
-    \cite{huiyang2022improving}\cmt{[17]}
-    \cite{jestin2022effects}\cmt{[81]}
-    \cite{kim2019comparing}\cmt{[89]}
-    \cite{kim2020can}\cmt{[24]}
-    \cite{kraus2020effects}\cmt{[64]}
-    \cite{linnemann2018can}\cmt{[15]}
-    \cite{ma2022ask}\cmt{[29]}
-    \cite{miehle2018exploring}\cmt{[51]}
-    \cite{misu2011toward}\cmt{[83]}
-    \cite{roy2021users}\cmt{[71]}
-    \cite{spillner2021talk}\cmt{[18]}
-    \cite{wilhelm2022keep}\cmt{[28]}
+    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2022expressive}\cmt{[77]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cuadra2021my}\cmt{[67]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{elsholz2019exploring}\cmt{[61]}\cite{haas2022keep}\cmt{[78]}\cite{habler2019effects}\cmt{[63]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2019comparing}\cmt{[89]}\cite{kim2020can}\cmt{[24]}
+    \cite{kraus2020effects}\cmt{[64]}\cite{linnemann2018can}\cmt{[15]}\cite{ma2022ask}\cmt{[29]}\cite{miehle2018exploring}\cmt{[51]}\cite{misu2011toward}\cmt{[83]}\cite{roy2021users}\cmt{[71]}\cite{spillner2021talk}\cmt{[18]}\cite{wilhelm2022keep}\cmt{[28]}
 \\ \cline{2-5}
     & Engagement & enjoyment, annoyance, desirable, intention to use  & 28
-    & \cite{andrews2012system}\cmt{[38]}
-    \cite{ceha2022expressive}\cmt{[77]}
-    \cite{ceha2021can}\cmt{[57]}
-    \cite{chan2021kinvoices}\cmt{[74]}
-    \cite{cox2022does}\cmt{[27]}
-    \cite{cuadra2021my}\cmt{[67]}
-    \cite{elsholz2019exploring}\cmt{[61]}
-    \cite{fadhil2018effect}\cmt{[52]}
-    \cite{gnewuch2022opposing}\cmt{[20]}
-    \cite{go2021conversational}\cmt{[80]}
-    \cite{healey2013relating}\cmt{[39]}
-    \cite{huiyang2022improving}\cmt{[17]}
-    \cite{jestin2022effects}\cmt{[81]}
-    \cite{kim2020can}\cmt{[24]}
-    \cite{kim2019comparing}\cmt{[89]}
-    \cite{lee2020hear}\cmt{[23]}
-    \cite{linnemann2018can}\cmt{[15]}
-    \cite{ma2022ask}\cmt{[29]}
-    \cite{miehle2018exploring}\cmt{[51]}
-    \cite{miyamoto2017improving}\cmt{[46]}
-    \cite{moilanen2022measuring}\cmt{[82]}
-    \cite{roy2021users}\cmt{[71]}
-    \cite{spillner2021talk}\cmt{[18]}
-    \cite{volkel2021examining}\cmt{[69]}
-    \cite{volkel2022user}\cmt{[75]}
-    \cite{xiao2021let}\cmt{[73]}
-    \cite{yang2021effect}\cmt{[72]}
-    \cite{zhu2022effects}\cmt{[26]}    
+    & \cite{andrews2012system}\cmt{[38]}\cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cox2022does}\cmt{[27]}\cite{cuadra2021my}\cmt{[67]}\cite{elsholz2019exploring}\cmt{[61]}\cite{fadhil2018effect}\cmt{[52]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{go2021conversational}\cmt{[80]}\cite{healey2013relating}\cmt{[39]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2020can}\cmt{[24]}\cite{kim2019comparing}\cmt{[89]}
+    \cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{ma2022ask}\cmt{[29]}\cite{miehle2018exploring}\cmt{[51]}\cite{miyamoto2017improving}\cmt{[46]}\cite{moilanen2022measuring}\cmt{[82]}\cite{roy2021users}\cmt{[71]}\cite{spillner2021talk}\cmt{[18]}\cite{volkel2021examining}\cmt{[69]}\cite{volkel2022user}\cmt{[75]}\cite{xiao2021let}\cmt{[73]}\cite{yang2021effect}\cmt{[72]}\cite{zhu2022effects}\cmt{[26]}
 \\ \cline{2-5}
     & Satisfaction & service satisfaction, quality of interaction & 12
-    & \cite{ceha2022expressive}\cmt{[77]}
-    \cite{choi2020nobody}\cmt{[54]}
-    \cite{diederich2019emulating}\cmt{[25]}
-    \cite{elsholz2019exploring}\cmt{[61]}
-    \cite{habler2019effects}\cmt{[63]}
-    \cite{gnewuch2018faster}\cmt{[19]}
-    \cite{hoegen2019end}\cmt{[31]}
-    \cite{hu2022polite}\cmt{[76]}
-    \cite{ma2022ask}\cmt{[29]}
-    \cite{roy2021users}\cmt{[71]}
-    \cite{wilhelm2022keep}\cmt{[28]}
-    \cite{yang2017perceived}\cmt{[44]}
+    & \cite{ceha2022expressive}\cmt{[77]}\cite{choi2020nobody}\cmt{[54]}\cite{diederich2019emulating}\cmt{[25]}\cite{elsholz2019exploring}\cmt{[61]}\cite{habler2019effects}\cmt{[63]}\cite{gnewuch2018faster}\cmt{[19]}\cite{hoegen2019end}\cmt{[31]}\cite{hu2022polite}\cmt{[76]}\cite{ma2022ask}\cmt{[29]}\cite{roy2021users}\cmt{[71]}\cite{wilhelm2022keep}\cmt{[28]}\cite{yang2017perceived}\cmt{[44]}
 \\ \Xhline{1.2pt} 
-\multirow{3}{*}{\parbox{3cm}{Perception of Agent's Ability}}
+\multirow{3}{*}{\parbox{0.16\textwidth}{Perception of Agent's Ability}}
     & Intelligence & knowledgeable, intelligent, expertise & 11
-    & \cite{ashktorab2019resilient}\cmt{[88]}
-    \cite{ceha2021can}\cmt{[57]}
-    \cite{chan2021kinvoices}\cmt{[74]}
-    \cite{cuadra2021my}\cmt{[67]}
-    \cite{dubiel2020persuasive}\cmt{[60]}
-    \cite{feijoo2021effects}\cmt{[70]}
-    \cite{hu2021enhancing}\cmt{[56]}
-    \cite{jeong2019exploring}\cmt{[10]}
-    \cite{spillner2021talk}\cmt{[18]}
-    \cite{volkel2022user}\cmt{[75]}
-    \cite{yang2017perceived}\cmt{[44]} 
+    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cuadra2021my}\cmt{[67]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{feijoo2021effects}\cmt{[70]}\cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}\cite{spillner2021talk}\cmt{[18]}\cite{volkel2022user}\cmt{[75]}\cite{yang2017perceived}\cmt{[44]}
 \\ \cline{2-5}
     & Competence & competent, capable & 4 
-    & \cite{cox2022does}\cmt{[27]}
-    \cite{kraus2020effects}\cmt{[64]}
-    \cite{lee2019s}\cmt{[55]}
-    \cite{westerman2019believe}\cmt{[9]}
+    & \cite{cox2022does}\cmt{[27]}\cite{kraus2020effects}\cmt{[64]}\cite{lee2019s}\cmt{[55]}\cite{westerman2019believe}\cmt{[9]}
 \\ \cline{2-5}
     & Trust & credibility, trustworthy, truthfulness, confidence & 15
-    & \cite{andrews2012system}\cmt{[38]}
-    \cite{chan2021kinvoices}\cmt{[74]}
-    \cite{dubiel2020persuasive}\cmt{[60]}
-    \cite{fadhil2018effect}\cmt{[52]}
-    \cite{healey2013relating}\cmt{[39]}
-    \cite{hoegen2019end}\cmt{[31]}
-    \cite{huiyang2022improving}\cmt{[17]}
-    \cite{jestin2022effects}\cmt{[81]}
-    \cite{kraus2020effects}\cmt{[64]}
-    \cite{lee2020hear}\cmt{[23]}
-    \cite{linnemann2018can}\cmt{[15]}
-    \cite{ma2022ask}\cmt{[29]}
-    \cite{seeger2021chatbots}\cmt{[35]}
-    \cite{tolmeijer2021female}\cmt{[62]}
-    \cite{wilhelm2022keep}\cmt{[28]}    
+    & \cite{andrews2012system}\cmt{[38]}\cite{chan2021kinvoices}\cmt{[74]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{fadhil2018effect}\cmt{[52]}\cite{healey2013relating}\cmt{[39]}\cite{hoegen2019end}\cmt{[31]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kraus2020effects}\cmt{[64]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{ma2022ask}\cmt{[29]}\cite{seeger2021chatbots}\cmt{[35]}\cite{tolmeijer2021female}\cmt{[62]}\cite{wilhelm2022keep}\cmt{[28]}
 \\ \Xhline{1.2pt} 
-\multirow{3}{*}{\parbox{3cm}{Perception of Social Connection with Agent}}
+\multirow{3}{*}{\parbox{0.16\textwidth}{Perception of Social Connection with Agent}}
     & Conversation Tone & appropriate, expressive, empathetic, persuasive & 13 
-    & \cite{chan2021kinvoices}\cmt{[74]}
-    \cite{cox2022does}\cmt{[27]}
-    \cite{cuadra2021my}\cmt{[67]}
-    \cite{daher2020empathic}\cmt{[58]}
-    \cite{diederich2019emulating}\cmt{[25]}
-    \cite{dubiel2020persuasive}\cmt{[60]}
-    \cite{hu2021enhancing}\cmt{[56]}
-    \cite{jestin2022effects}\cmt{[81]}
-    \cite{misu2011toward}\cmt{[83]}
-    \cite{tolmeijer2021female}\cmt{[62]}
-    \cite{yang2021effect}\cmt{[72]}
-    \cite{yang2017perceived}\cmt{[44]}
-    \cite{zhu2022effects}\cmt{[26]}           
+    & \cite{chan2021kinvoices}\cmt{[74]}\cite{cox2022does}\cmt{[27]}\cite{cuadra2021my}\cmt{[67]}\cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{hu2021enhancing}\cmt{[56]}\cite{jestin2022effects}\cmt{[81]}\cite{misu2011toward}\cmt{[83]}\cite{tolmeijer2021female}\cmt{[62]}\cite{yang2021effect}\cmt{[72]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}
 \\ \cline{2-5}
-    & Social Presence & connectedness, familiarity, similarity, psychological distance & 18
-    & \cite{ceha2022expressive}\cmt{[77]}
-    \cite{ceha2021can}\cmt{[57]}
-    \cite{chan2021kinvoices}\cmt{[74]}
-    \cite{choi2020nobody}\cmt{[54]}
-    \cite{cuadra2021my}\cmt{[67]}
-    \cite{diederich2019emulating}\cmt{[25]}
-    \cite{gnewuch2018faster}\cmt{[19]}
-    \cite{gnewuch2018chatbot}\cmt{[21]}
-    \cite{gnewuch2022opposing}\cmt{[20]}
-    \cite{go2021conversational}\cmt{[80]}
-    \cite{khooshabeh2011does}\cmt{[37]}
-    \cite{kim2020can}\cmt{[24]}
-    \cite{lee2019s}\cmt{[55]}
-    \cite{lubis2019positive}\cmt{[43]}
-    \cite{lubold2016effects}\cmt{[86]}
-    \cite{ma2022ask}\cmt{[29]}
-    \cite{niewiadomski2013laugh}\cmt{[85]}
-    \cite{westerman2019believe}\cmt{[9]}    
+    & Social Presence & connectedness, familiarity, psychological distance & 18
+    & \cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cuadra2021my}\cmt{[67]}\cite{diederich2019emulating}\cmt{[25]}\cite{gnewuch2018faster}\cmt{[19]}\cite{gnewuch2018chatbot}\cmt{[21]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{go2021conversational}\cmt{[80]}\cite{khooshabeh2011does}\cmt{[37]}\cite{kim2020can}\cmt{[24]}\cite{lee2019s}\cmt{[55]}\cite{lubis2019positive}\cmt{[43]}\cite{lubold2016effects}\cmt{[86]}
+    \cite{ma2022ask}\cmt{[29]}\cite{niewiadomski2013laugh}\cmt{[85]}\cite{westerman2019believe}\cmt{[9]}    
 \\ \cline{2-5}
     & Intimacy & intimate, rapport, quality of relationship & 7 
-    & \cite{choi2020nobody}\cmt{[54]}
-    \cite{khooshabeh2011does}\cmt{[37]}
-    \cite{kim2020can}\cmt{[24]}
-    \cite{lee2020hear}\cmt{[23]}
-    \cite{linnemann2018can}\cmt{[15]}
-    \cite{lubold2016effects}\cmt{[86]}
-    \cite{westerman2019believe}\cmt{[9]}
+    & \cite{choi2020nobody}\cmt{[54]}\cite{khooshabeh2011does}\cmt{[37]}\cite{kim2020can}\cmt{[24]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{lubold2016effects}\cmt{[86]}\cite{westerman2019believe}\cmt{[9]}
 \\ \Xhline{1.2pt}
-\multirow{2}{*}{\parbox{3cm}{Perception of Agent's Humanness}}
+\multirow{2}{*}{\parbox{0.16\textwidth}{Perception of Agent's Humanness}}
     & Human-likeness & human-like, natural, artificial, machine-like & 20
-    & \cite{ashktorab2019resilient}\cmt{[88]}
-    \cite{ceha2021can}\cmt{[57]}
-    \cite{chan2021kinvoices}\cmt{[74]}
-    \cite{choi2020nobody}\cmt{[54]}
-    \cite{cox2022does}\cmt{[27]}
-    \cite{diederich2019emulating}\cmt{[25]}
-    \cite{gnewuch2018faster}\cmt{[19]}
-    \cite{haas2022keep}\cmt{[78]}
-    \cite{hu2022polite}\cmt{[76]}
-    \cite{jeong2019exploring}\cmt{[10]}
-    \cite{jestin2022effects}\cmt{[81]}
-    \cite{lubis2019positive}\cmt{[43]}
-    \cite{ma2022ask}\cmt{[29]}
-    \cite{misu2011toward}\cmt{[83]}
-    \cite{niewiadomski2013laugh}\cmt{[85]}
-    \cite{ouchi2019should}\cmt{[59]}
-    \cite{seeger2021chatbots}\cmt{[35]}
-    \cite{wester2015artificial}\cmt{[14]}
-    \cite{westerman2019believe}\cmt{[9]}
-    \cite{zhu2022effects}\cmt{[26]}    
+    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cox2022does}\cmt{[27]}\cite{diederich2019emulating}\cmt{[25]}\cite{gnewuch2018faster}\cmt{[19]}\cite{haas2022keep}\cmt{[78]}\cite{hu2022polite}\cmt{[76]}\cite{jeong2019exploring}\cmt{[10]}\cite{jestin2022effects}\cmt{[81]}\cite{lubis2019positive}\cmt{[43]}\cite{ma2022ask}\cmt{[29]}\cite{misu2011toward}\cmt{[83]}\cite{niewiadomski2013laugh}\cmt{[85]}
+    \cite{ouchi2019should}\cmt{[59]}\cite{seeger2021chatbots}\cmt{[35]}\cite{wester2015artificial}\cmt{[14]}\cite{westerman2019believe}\cmt{[9]}\cite{zhu2022effects}\cmt{[26]}    
 \\ \cline{2-5}
     & Personality Traits & friendly, kind, warm, creepy, likeable, polite & 27
-    & \cite{andrews2012system}\cmt{[38]}
-    \cite{ashktorab2019resilient}\cmt{[88]}
-    \cite{ceha2022expressive}\cmt{[77]}
-    \cite{ceha2021can}\cmt{[57]}
-    \cite{chan2021kinvoices}\cmt{[74]}
-    \cite{cox2022does}\cmt{[27]}
-    \cite{cuadra2021my}\cmt{[67]}
-    \cite{haas2022keep}\cmt{[78]}
-    \cite{habler2019effects}\cmt{[63]}
-    \cite{healey2013relating}\cmt{[39]}
-    \cite{hu2022polite}\cmt{[76]}
-    \cite{huiyang2022improving}\cmt{[17]}
-    \cite{jeong2019exploring}\cmt{[10]}
-    \cite{jestin2022effects}\cmt{[81]}
-    \cite{khooshabeh2011does}\cmt{[37]}
-    \cite{kim2019comparing}\cmt{[89]}
-    \cite{lee2019s}\cmt{[55]}
-    \cite{lee2020hear}\cmt{[23]}
-    \cite{linnemann2018can}\cmt{[15]}
-    \cite{miehle2018exploring}\cmt{[51]}
-    \cite{moilanen2022measuring}\cmt{[82]}
-    \cite{ouchi2019should}\cmt{[59]}
-    \cite{tolmeijer2021female}\cmt{[62]}
-    \cite{volkel2021manipulating}\cmt{[68]}
-    \cite{volkel2022user}\cmt{[75]}
-    \cite{wester2015artificial}\cmt{[14]}
-    \cite{zhu2022effects}\cmt{[26]} 
+    & \cite{andrews2012system}\cmt{[38]}\cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cox2022does}\cmt{[27]}\cite{cuadra2021my}\cmt{[67]}\cite{haas2022keep}\cmt{[78]}\cite{habler2019effects}\cmt{[63]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{huiyang2022improving}\cmt{[17]}\cite{jeong2019exploring}\cmt{[10]}\cite{jestin2022effects}\cmt{[81]}\cite{khooshabeh2011does}\cmt{[37]}
+    \cite{kim2019comparing}\cmt{[89]}\cite{lee2019s}\cmt{[55]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{miehle2018exploring}\cmt{[51]}\cite{moilanen2022measuring}\cmt{[82]}\cite{ouchi2019should}\cmt{[59]}\cite{tolmeijer2021female}\cmt{[62]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}\cite{wester2015artificial}\cmt{[14]}\cite{zhu2022effects}\cmt{[26]}
 \\ \Xhline{1.2pt}
@@
 
-Modality?
-
 \begin{table*}[h]
-%\resizebox{\textwidth}{!}{
-\begin{tabular}{@{}lllc@{}}
-\toprule
- \textbf{Category} & \textbf{Theme}      & \textbf{Sample Codes}                                      & \textbf{No. Papers} \\ \midrule
-\multirow{4}{*}{Linguistic Content}    & Affective Language & emotional expressions, sentiment-adaptive responses & 11 \\
- & Social Talk           & self-disclosure, social dialogue                       & 7                                       \\
- & Humour                & humorous content, jokes                                & 5                                       \\
- & Agent-Initiated Content & elicit user feedback, proactivity, conversation repair & 4                                       \\ \midrule
-\multirow{4}{*}{Linguistic Style}     & Formality          & formal vs. casual, honorific expressions                               & 9  \\
- & Alignment             & content matching, lexical alignment, agreeableness     & 7                                       \\
- & Elaborateness         & elaborate, concise, sentence structure                 & 6                                       \\
- & Disfluency            & fillers, interjections, repetitions                    & 6                                       \\ \midrule
-\multirow{2}{*}{Non-Linguistic Format}     & Prosodic Cue            & pitch, intonation, speech rate, spoken accent                          & 12 \\
- & Text Variation        & typo, capitalization, emoticons, response delay & 9                                         \\ \bottomrule 
+\resizebox{\textwidth}{!}{
+\renewcommand*{\arraystretch}{1.4}
+\begin{tabular}{@{}p{0.17\textwidth} | p{0.14\textwidth} | p{0.25\textwidth} | >{\centering}p{0.09\textwidth} | p{0.34\textwidth} @{}}
+\Xhline{1.2pt}
+\textbf{Category} & \textbf{Theme} & \textbf{Sample Codes} & \textbf{No. Papers} & \textbf{Papers}
+\\ \Xhline{1.2pt}
+\multirow{4}{*}{Linguistic Content}    & Affective Language & emotional expressions, sentiment-adaptive responses & 11
+& \cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{lee2019s}\cmt{[55]}\cite{lubis2019positive}\cmt{[43]}\cite{moilanen2022measuring}\cmt{[82]}\cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2022user}\cmt{[75]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}
+\\ \cline{2-5}
+& Social Talk & self-disclosure, social dialogue & 7
+& \cite{andrews2012system}\cmt{[38]}\cite{lee2020hear}\cmt{[23]}\cite{lubold2016effects}\cmt{[86]}\cite{moilanen2022measuring}\cmt{[82]}\cite{roy2021users}\cmt{[71]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}
+\\ \cline{2-5}
+& Humour & humorous content, jokes & 5
+& \cite{ceha2021can}\cmt{[57]}\cite{go2021conversational}\cmt{[80]}\cite{khooshabeh2011does}\cmt{[37]}\cite{miyamoto2017improving}\cmt{[46]}\cite{volkel2021manipulating}\cmt{[68]}
+\\ \cline{2-5}
+& Agent-Initiated Content & proactive dialogue, conversation repair & 4
+& \cite{ashktorab2019resilient}\cmt{[88]}\cite{cuadra2021my}\cmt{[67]}\cite{kraus2020effects}\cmt{[64]}\cite{xiao2021let}\cmt{[73]}
+\\ \Xhline{1.2pt}
+\multirow{4}{*}{Linguistic Style} & Formality & formal vs. casual, honorific expressions & 9
+& \cite{cox2022does}\cmt{[27]}\cite{elsholz2019exploring}\cmt{[61]}\cite{habler2019effects}\cmt{[63]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2019comparing}\cmt{[89]}\cite{ma2022ask}\cmt{[29]}\cite{moilanen2022measuring}\cmt{[82]}\cite{ouchi2019should}\cmt{[59]}\cite{volkel2022user}\cmt{[75]}
+\\ \cline{2-5}
+& Alignment & content matching, lexical alignment, agreeableness & 7
+& \cite{healey2013relating}\cmt{[39]}\cite{hoegen2019end}\cmt{[31]}\cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}\cite{spillner2021talk}\cmt{[18]}\cite{volkel2021examining}\cmt{[69]}\cite{volkel2021manipulating}\cmt{[68]}
+\\ \cline{2-5}
+& Elaborateness & elaborate, concise, sentence structure & 6
+& \cite{haas2022keep}\cmt{[78]}\cite{miehle2018exploring}\cmt{[51]}\cite{moilanen2022measuring}\cmt{[82]}\cite{roy2021users}\cmt{[71]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}
+\\ \cline{2-5}
+& Disfluency & fillers, interjections, repetitions & 6
+& \cite{ceha2022expressive}\cmt{[77]}\cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}\cite{niewiadomski2013laugh}\cmt{[85]}\cite{wester2015artificial}\cmt{[14]}\cite{yang2021effect}\cmt{[72]}
+\\ \Xhline{1.2pt}
+\multirow{2}{*}{Non-Linguistic Format} & Prosodic Cue & pitch, intonation, speech rate, spoken accent & 12
+& \cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{feijoo2021effects}\cmt{[70]}\cite{habler2019effects}\cmt{[63]}\cite{hu2021enhancing}\cmt{[56]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2020can}\cmt{[24]}\cite{lubold2016effects}\cmt{[86]}\cite{misu2011toward}\cmt{[83]}\cite{tolmeijer2021female}\cmt{[62]}\cite{zhu2022effects}\cmt{[26]}
+\\ \cline{2-5}
+& Text Variation & typo, capitalization, emoticons, response delay & 9
+& \cite{fadhil2018effect}\cmt{[52]}\cite{gnewuch2018faster}\cmt{[19]}\cite{gnewuch2018chatbot}\cmt{[21]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{kim2019comparing}\cmt{[89]}\cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2022user}\cmt{[75]}\cite{westerman2019believe}\cmt{[9]}\cite{wilhelm2022keep}\cmt{[28]}
+\\ \Xhline{1.2pt}
 \end{tabular}%
-%}
+}
 \caption{Conversation architecture elements}
@@
 
- In addition to different methods used to measure for the same perception, our detailed analysis revealed that the measures using the same label may have \textbf{drastically different meanings}.
+ In addition to different methods used to measure for the same perception, our detailed analysis revealed that the measures using the same label may have \textbf{different meanings}.
 In Diedrech et al.'s study \cite{diederich2019emulating}\cmt{[25]}, \textit{empathy} measure is adapted from \cite{yan2013role} assessing whether the CA gives users individual or personal attention.
@@
 
-%For discussions on mental well beings, agent using emojis is rated higher for attitude (emotional connection) .
-However, for agent with discussing physical well being, agent using emojis is rated as lower for attitude.
-%Attitude has emotional connection, coherent - coherent is an ability perception, vs. emotional connection is a social connection perception. \cite{fadhil2018effect}\cmt{[52]}
-
-\subsubsection{Other Influencing Factors}
+\subsubsection{Nuances in Influencing Factors}
 
@@
 However, novice users perceived higher social presence conversing with the CAs using response delays as it is more similar to conversations with human partners \cite{gnewuch2018faster}\cmt{[19]}.
+
+%Designing for personalities, not individual elements
+
+%* The size of the effect for language we observed is clearly higher than the size of the effect for voice. \cite{habler2019effects}\cmt{[63]}
+
+%Combined effects
+%* integrated mental model \cite{knijnenburg2016inferring}\cmt{[34]}
+%* Anthropomorphized chatbot (text) using affective language (emotional expressions), self-referencing, emoticons, response delays.
+Resulted in higher perceived anthropomorphism, which in result led to lower negative word of mouth and loss of trust.
+anthropomorphic design is beneficial not only to initial trust but also to the ongoing trust relationship \cite{seeger2021chatbots}\cmt{[35]}
+
+%For discussions on mental well beings, agent using emojis is rated higher for attitude (emotional connection) .
+However, for agent with discussing physical well being, agent using emojis is rated as lower for attitude.
+%Attitude has emotional connection, coherent - coherent is an ability perception, vs. emotional connection is a social connection perception. \cite{fadhil2018effect}\cmt{[52]}
 
@@
 
-\subsubsection{Relationship between perceptions}
+%* that a sense of intimate connection to the CA is more important than efficient task handling in some contexts \54
+%* VA self-repair can backfire if time or accuracy is of the essence. (repair and accuracy) \cite{cuadra2021my}\cmt{[67]}
 
-Response delay: social presence has a significant effect on intention to use. 
-\cite{gnewuch2022opposing}\cmt{[20]}
-
-Perceived intelligence positively associated with perceived usefulness, perceived ease of use, initial trust, and perceived anthropomorphism.
-Perceived anthropomorphism is associated with perceived enjoyment, and intention to adopt.
-Perceived usefulness and perceived enjoyment impacts intention to adopt.
-\cite{moussawi2021perceptions}\cmt{[36]}
-
-The size of the effect for language we observed is clearly higher than the size of the effect for voice. \cite{habler2019effects}\cmt{[63]}
-
-VA self-repair can backfire if time or accuracy is of the essence. (repair and accuracy) \cite{cuadra2021my}\cmt{[67]}
-
-\subsection{Ethical Considerations}
-
-Self-disclosure encourage higher trust and intimacy, to disclose sensitive information. Who have access to this data? need to be aware of privacy / data sharing practices. \cite{lee2020hear}\cmt{[23]}
-
-Evidence for the influence of voice gender and pitch on stereotypical trait attribution.
-Active trait attribution is missing as most participants attributes to the negative side of traits for CAs.
-\cite{tolmeijer2021female}\cmt{[62]}
-
-The social and emotional benefits of self-repair in interaction need to be balanced against the creepiness of the monitoring and modelling needed to make self-repair possible.
-\cite{cuadra2021my}\cmt{[67]}
-
-\subsection{Limitations and Future Work}
-
-\subsubsection{Assumptions in designed personalities of CAs}
-Sometimes a study is covering multiple conversational element cues, hard to break it out.
+%Sometimes a study is covering multiple conversational element cues, hard to break it out.
 For example, extroverted personality used in \cite{volkel2022user}\cmt{[75]} has emoticons, affective language, talkative, and self-disclosure.
@@
 
-Also, breaking down "personalities" to its core components.
+%Also, breaking down "personalities" to its core components.
 
-There are a few studies that designed conversational agents composed with multiple conversation architecture elements.
+%There are a few studies that designed conversational agents composed with multiple conversation architecture elements.
 This is especially evident in studies comparing different personalities of CAs, such as extroverted vs.
@@
 
-\cite{moilanen2022measuring}\cmt{[82]}\cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}.
+%\cite{moilanen2022measuring}\cmt{[82]}\cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}.
 
-%Research challenges and opportunities
+\subsubsection{Consider Relationships Within Perceptions}
 
-%Ethical considerations
+There are empirical evidence that different perceptions of agent have effects on each other.
+Moussawi et al \cite{moussawi2021perceptions}\cmt{[36]} conducted a study to understand the correlations between different perceptions impacting user's intention to adopt a conversational agent.
+Specifically, they found a correlation within the category of perceived ability, where perceived intelligence is positively correlated to initial trust of the agent.
+Also, the study found that users with higher perceived intelligence of an agent are more likely to attribute higher ratings for the perception category of interaction on the perceived ease of use and enjoyment, as well as higher ratings for perceived anthropomorphism.
+Perceived anthropomorphism have a positive impact on perceived enjoyment, which lead to higher intention to adopt the CA.
+This study outlines that the perception themes we identified in this paper are not independent of each other.
 
-\subsubsection{Gaps}
+The correlations between perception measures are covered in a few of the papers in our corpus.
+In the study of using response delays, the perception of social presence had a significant effect on the intention to use \cite{gnewuch2022opposing}\cmt{[20]}.
+In another study, the CA's perceived personality trait of agreeableness has an influence on the perception of trust \cite{andrews2012system}\cmt{[38]}.
+Seeger et al's study had similar findings, where higher perceived anthropomorphism lead to lower loss of trust \cite{seeger2021chatbots}\cmt{[35]}.
+There are also effects within the same perception category, such as a speech agent that is rated higher in perceived human-likeness was associated with higher likability ratings \cite{zhu2022effects}\cmt{[26]}.
+Also, within the perception category of social connection, one study found that social distance is positively related to the perceived social attraction \cite{westerman2019believe}\cmt{[9]}.
 
-Combined effects
-* integrated mental model \cite{knijnenburg2016inferring}\cmt{[34]}
-* Anthropomorphized chatbot (text) using affective language (emotional expressions), self-referencing, emoticons, response delays.
-Resulted in higher perceived anthropomorphism, which in result led to lower negative word of mouth and loss of trust.
-anthropomorphic design is beneficial not only to initial trust but also to the ongoing trust relationship \cite{seeger2021chatbots}\cmt{[35]}
+These correlations between perceptions demonstrate that designing for specific anthropomorphized perceptions of conversational agents is more nuanced than the sum of the impacts from individual perceptions.
+Perceptions have influences on each other, either within the same category or across different categories.
+However, there is not enough studied connections in existing literature to make a meaningful systematic analysis of the relationship within perceptions.
+More research is needed in this area to study these relationships, to understand whether there are systematic trends in the influences of perceptions, and whether there is a sequence of perceptions to achieve the desired overall anthropomorphized perception of agents.
 
-Lack of investigations - name a few areas
+\subsection{Ethical Considerations}
 
-%\subsubsection{Human-human vs. Human-machine}
+While the use of conversation architecture elements can be used to design anthropomorphized perceptions, it is important to address the potential ethical implications that could negative impact users.
+There are three items discussed in this section: societal stereotypes, influencing user's actions and privacy concerns.
 
-%* Impact of lexical alignment on people's perceived annoyance and likability differed in HHI (higher) and HCI (no impact). \cite{huiyang2022improving}\cmt{[17]}.
+For prosodic cues, there are various studies in our corpus exploring the effect of different pitches on different perceptions of agents.
+Even in studies not explicitly studying the effect of gendered voices in an agent, possible stereotypes may still exist in the study.
+Studies exploring the impact of gendered voices found that lower pitches usually associated with men are considered to be more desirable, authoritative but less friendly \cite{tolmeijer2021female}\cmt{[62]}\cite{jestin2022effects}\cmt{[81]}.
+For Dubiel et al's study \cite{dubiel2020persuasive}\cmt{[60]}, the prosody setting with the lower mean pitch was selected as the more persuasive voice through a user study.
+These results may be due to the unconscious bias to select a male sounding voice as more persuasive over female sounding voices that are usually using higher pitches.
+While some guidelines recommend designing agents to be androgynous to avoid gender stereotypes \cite{ruane2019conversational}, there are limitations in creating gender-ambiguous voices.
+Currently there is no defined aspects on what is perceived as a gender-neutral voice  \cite{jestin2022effects}\cmt{[81]}, and there is a lack of voice generators available to generate voices that are seen as androgynous \cite{tolmeijer2021female}\cmt{[62]}.
+
+Conversation architecture elements can be used to design perceptions of agents to make the CA more persuasive.
+This opens up the ethical issue of influencing user's attitudes and behaviours through these persuasion techniques.
+In a study by Chan et al \cite{chan2021kinvoices}\cmt{[74]}, they found that CAs using kin's voices are perceived as more credible and likeable, with a higher perceived social presence with the agent.
+These perceptions contributes to the agent being more engaging and persuasive, therefore people are more likely to comply with its requests.
+Andrew et al \cite{andrews2012system}\cmt{[38]} found that tailoring the personality of the CA to users will positively impact an agent's persuasiveness.
+These persuasion techniques can be beneficial to help users achieve their goals, but can also be used for harmful actions, such as when trying to get someone to believe false information for their own gain.
+
+Another key area of concern is privacy.
+Given the natural language format of conversational agents, users may be disclosing more sensitive and personal information than needed for the interaction.
+In relationship to conversation architecture, some elements like self-disclosure and using persuasive voices resulting in higher trust, leading participants to disclose sensitive information with the agent \cite{lee2020hear}\cmt{[23]}\cite{dubiel2020persuasive}\cmt{[60]}.
+This can expose users to attacks, such as CAs using voice impersonation to ask for personal information for malicious intents \cite{chan2021kinvoices}\cmt{[74]}.
+Designing for anthropomorphized perceptions of agents requires careful consideration of privacy issues including the sensitivity of the data, who has access to it, and how to protect against nefarious users.
+
+\subsection{Limitations and Future Work}
+
+Our systematic literature review was limited to papers published in the ACM Digital Library between 2010 and 2022.
+We may have missed literature published outside this time period, as well as in other libraries.
+Also, most of the studies in our corpus are based on lab experiments with short interactions.
+The generalizability of these findings need to be verified through longer term engagements with conversational agents deployed in real world situations.
+Lastly, research without empirical studies on the perception of agents are excluded based on our selection criteria.
+We may have missed some influential findings in these papers.
+To better understand the relationships between conversation architecture elements and anthropomorphized perceptions, we plan to conduct future reviews in literature and user studies to understand their real-world impacts.
 
@@
 
-TBD
+In this paper, we discussed the results of a systematic review of existing literature published in the ACM Digital Library on the impact of conversation architecture elements on anthropomorphized perceptions of CAs.
+Through our synthesis of our corpus of 57 papers, we have created a consistent taxonomy for perceptions of agents, as well as conversation architecture elements.
+Also, we have mapped the relationships between perceptions and conversation architecture to a generalized framework based on the impacts discussed in our reviewed corpus.
+Through our analysis, we have found that perception measures are being used inconsistently across studies, as well as other influencing factors on the perception of agents.
+We recommend future research to consider creating consistent measures that can explore different aspects of perceptions, as well as more explorations into the patterns behind other influencing factors that have impacts on anthropomorphized perceptions.
+While our research contribute to design conversation architecture to orchestrate specific anthropomorphized perceptions, we urge everyone to incorporate ethical perspectives into their design considerations.
 
@@
 \begin{acks}
-To Robert, for the bagels and explaining CMYK and color spaces.
+TBD
 \end{acks}
@@
 
-\onecolumn
-\section{Appendix}
-
-\begin{table*}[]
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{@{}lllc@{}}
-\toprule
-\textbf{Category} & \textbf{Theme}   & \textbf{Sample Codes}                                  & \textbf{No. Papers}   \\ \midrule
-\multirow{3}{*}{Perception of Interaction with Agent}    & Usability       & accuracy, ease of use, efficiency, helpfulness & 23 \\
- & Engagement         & enjoyment, annoyance, desirable, intention to use  & 28         \\
- & Satisfaction       & service satisfaction, quality of interaction       & 12         \\ \midrule
-\multirow{3}{*}{Perception of Agent's Ability}              & Intelligence    & knowledgeable, intelligent, expertise                             & 11 \\
- & Competence         & competent, capable                                 & 4          \\
- & Trust              & credibility, trustworthy, truthfulness, confidence & 15         \\ \midrule
-\multirow{3}{*}{Perception of Social Connection with Agent}  & Conversation Tone  & appropriate, expressive, empathetic, persuasive    & 13 \\
- & Social Presence & connectedness, familiarity, similarity, psychological distance    & 18        \\
- & Intimacy           & intimate, rapport, quality of relationship         & 7          \\ \midrule
-\multirow{2}{*}{Perception of Agent's Humanness}            & Human-likeness  & human-like, natural, artificial, machine-like                     & 20 \\
- & Personality Traits & friendly, kind, warm, creepy, likeable, polite     & 27         \\ \bottomrule
-\end{tabular}%
-}
-\caption{Perception measures}
-\label{tab:appendix-perceptions}
-\end{table*}
-
-\begin{table*}[h]
-\resizebox{\textwidth}{!}{
-\begin{tabular}{@{}p{0.2\linewidth} | p{0.2\linewidth} | p{0.2\linewidth}@{}}
-\toprule
- \textbf{Category} & \textbf{Theme} & \textbf{Papers} \\ \midrule
-\multirow{4}{*}{Linguistic Content}    
-    & Affective Language 
-    &  
-\\
-     & Social Talk
-    &
-\\
-    & Humour
-    &
-\\
-    & Agent-Initiated Content
-    &
-\\ \midrule
-\multirow{4}{*}{Linguistic Style}
-    & Formality
-    &
-\\
-    & Alignment 
-    &
-\\
-    & Elaborateness
-    &
-\\
-    & Disfluency
-    &
-\\ \midrule
-\multirow{2}{*}{Non-Linguistic Format}
-    & Prosodic Cue
-    &
-\\
-    & Text Variation
-    &
-\\ \bottomrule 
-\end{tabular}%
-}
-\caption{Conversation architecture elements}
-\label{tab:appendix-cues}
-\end{table*}
-
 \end{document}
@@
 %% End of file `paper.tex'.
-
-\multirow{3}{*}{Perception of Interaction with Agent}    & Usability       \\
- & Engagement                  \\
- & Satisfaction                \\ \midrule
-\multirow{3}{*}{Perception of Agent's Ability}              & Intelligence     \\
- & Competence                  \\
- & Trust                       \\ \midrule
-\multirow{3}{*}{Perception of Social Connection with Agent}  & Conversation Tone  \\
- & Social Presence         \\
- & Intimacy                    \\ \midrule
-\multirow{2}{*}{Perception of Agent's Humanness}            & Human-likeness   \\
- & Personality Traits          \\ \bottomrule

### 2023-02-14 paper.tex
title & abstract updates, update figures, added coverage heatmap

@@
 % \title[short title]{How to Make Pinocchio a Real Boy? Designing conversational architecture elements to achieve desirable anthropomorphized perceptions}
-\title[Bot's Guide to Being Human]{Bot's Guide to Being Human: Investigating the Effect of Conversation Architecture Elements on the Anthropomorphized Perceptions of Conversational Agents}
-% Blurring the line between human and bots
+\title[The Bot with the Eloquent Speech]{The Bot with the Eloquent Speech: Exploring the Relationship between Perceptions of Conversational Agents and Their Conversation Architecture}
 
@@
 \begin{abstract}
-The natural language interactions of conversational agents encourage users to attribute humanlike qualities to them, but we don't yet have a systematic understanding on how to design conversation architecture to orchestrate these anthropomorphized perceptions.
-Through a comprehensive review on papers with empirical studies on the impact of conversation architecture elements on perception of agents, we collected explored connections in literature to create a consistent taxonomy for anthropomorphized perceptions, and conversation architecture elements.
-Also, we created a generalized framework of the relationship between conversation architecture and perceptions based on the number of impacts found in the reviewed studies.
-In our analysis, we found there are inconsistencies in the measurements for perceptions of agents, as well as influencing factors other than conversation architecture that could impact anthropomorphized perceptions of agents.
-Also, it is important to consider ethical aspects of designing anthropomorphized perceptions of CAs as it may have negative consequences to users.
+Previous research has demonstrated a relationship between the structure of conversational agents' natural language interaction and how these agents are perceived by their users.
+However, the systematic connections between the perception of agents and elements of conversation architecture are not well understood.
+Furthermore, there is no clear definition of the aspects of perception that are affected and the elements of conversation architecture.
+In this paper, we present a synthesized framework demonstrating the connections between perceptions of agents and conversation architecture elements, using a taxonomy of eleven perceptions grouped into four categories, and ten elements grouped into three categories.
+We highlight the need for further research for the perception of agent's ability and perception of social connection with agent's, especially as it relates to the linguistic style of conversational agents.
+Also, there is the need to be consistent in the assessment of agents' perceptions, and address ethical concerns in design.
 \end{abstract}
@@
 %TC:endignore
+
+%%%% TODO %%%%
+% Add headmap of explored relationships - side by side with the connections - show numbers - DONE
+% Put the heatmap of impact earlier in the paper - DONE
+% Put the tables together - DONE
+% show what is explored vs. the connections that had impacts. - DONE
+% User perception of agent instead of anthropomorphized perceptions
+% Refer to the explored connection in writing, and connections with impacts
+% Update to use perception aspects and categories (instead of themes and organizing themes)
+% Update introduction
+% Include focus areas for future reasearch
+% Reviewed recording up to 17:31
+% Question about single column vs. double column format - ask Jaisie
 
@@
 
+\begin{figure*}[]
+  \centering
+  \includegraphics[width=\textwidth]{fig-heatmap-impact.png}
+  \caption{Heatmap of literature for perception of conversational agents for each type of conversational architecture element}
+  \label{fig:heatmap-impact}
+\end{figure*}
+
 \subsection{Anthropomorphized Perceptions}
-
-\begin{table*}[ht]
-\renewcommand*{\arraystretch}{1.4}
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{@{}p{0.17\textwidth} | p{0.12\textwidth} | p{0.20\textwidth} | >{\centering}p{0.09\textwidth} | p{0.42\textwidth} @{}}
-%!{\vrule width 1.2pt} 
-\Xhline{1.2pt}
-\textbf{Category} & \textbf{Theme} & \textbf{Sample Codes} & \textbf{No. Papers} & \textbf{Papers} 
-\\ \Xhline{1.2pt}
-\multirow{3}{*}{\parbox{0.16\textwidth}{Perception of Interaction with Agent}}
-    & Usability & accuracy, ease of use, efficiency, helpfulness & 23 
-    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2022expressive}\cmt{[77]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cuadra2021my}\cmt{[67]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{elsholz2019exploring}\cmt{[61]}\cite{haas2022keep}\cmt{[78]}\cite{habler2019effects}\cmt{[63]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2019comparing}\cmt{[89]}\cite{kim2020can}\cmt{[24]}
-    \cite{kraus2020effects}\cmt{[64]}\cite{linnemann2018can}\cmt{[15]}\cite{ma2022ask}\cmt{[29]}\cite{miehle2018exploring}\cmt{[51]}\cite{misu2011toward}\cmt{[83]}\cite{roy2021users}\cmt{[71]}\cite{spillner2021talk}\cmt{[18]}\cite{wilhelm2022keep}\cmt{[28]}
-\\ \cline{2-5}
-    & Engagement & enjoyment, annoyance, desirable, intention to use  & 28
-    & \cite{andrews2012system}\cmt{[38]}\cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cox2022does}\cmt{[27]}\cite{cuadra2021my}\cmt{[67]}\cite{elsholz2019exploring}\cmt{[61]}\cite{fadhil2018effect}\cmt{[52]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{go2021conversational}\cmt{[80]}\cite{healey2013relating}\cmt{[39]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2020can}\cmt{[24]}\cite{kim2019comparing}\cmt{[89]}
-    \cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{ma2022ask}\cmt{[29]}\cite{miehle2018exploring}\cmt{[51]}\cite{miyamoto2017improving}\cmt{[46]}\cite{moilanen2022measuring}\cmt{[82]}\cite{roy2021users}\cmt{[71]}\cite{spillner2021talk}\cmt{[18]}\cite{volkel2021examining}\cmt{[69]}\cite{volkel2022user}\cmt{[75]}\cite{xiao2021let}\cmt{[73]}\cite{yang2021effect}\cmt{[72]}\cite{zhu2022effects}\cmt{[26]}
-\\ \cline{2-5}
-    & Satisfaction & service satisfaction, quality of interaction & 12
-    & \cite{ceha2022expressive}\cmt{[77]}\cite{choi2020nobody}\cmt{[54]}\cite{diederich2019emulating}\cmt{[25]}\cite{elsholz2019exploring}\cmt{[61]}\cite{habler2019effects}\cmt{[63]}\cite{gnewuch2018faster}\cmt{[19]}\cite{hoegen2019end}\cmt{[31]}\cite{hu2022polite}\cmt{[76]}\cite{ma2022ask}\cmt{[29]}\cite{roy2021users}\cmt{[71]}\cite{wilhelm2022keep}\cmt{[28]}\cite{yang2017perceived}\cmt{[44]}
-\\ \Xhline{1.2pt} 
-\multirow{3}{*}{\parbox{0.16\textwidth}{Perception of Agent's Ability}}
-    & Intelligence & knowledgeable, intelligent, expertise & 11
-    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cuadra2021my}\cmt{[67]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{feijoo2021effects}\cmt{[70]}\cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}\cite{spillner2021talk}\cmt{[18]}\cite{volkel2022user}\cmt{[75]}\cite{yang2017perceived}\cmt{[44]}
-\\ \cline{2-5}
-    & Competence & competent, capable & 4 
-    & \cite{cox2022does}\cmt{[27]}\cite{kraus2020effects}\cmt{[64]}\cite{lee2019s}\cmt{[55]}\cite{westerman2019believe}\cmt{[9]}
-\\ \cline{2-5}
-    & Trust & credibility, trustworthy, truthfulness, confidence & 15
-    & \cite{andrews2012system}\cmt{[38]}\cite{chan2021kinvoices}\cmt{[74]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{fadhil2018effect}\cmt{[52]}\cite{healey2013relating}\cmt{[39]}\cite{hoegen2019end}\cmt{[31]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kraus2020effects}\cmt{[64]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{ma2022ask}\cmt{[29]}\cite{seeger2021chatbots}\cmt{[35]}\cite{tolmeijer2021female}\cmt{[62]}\cite{wilhelm2022keep}\cmt{[28]}
-\\ \Xhline{1.2pt} 
-\multirow{3}{*}{\parbox{0.16\textwidth}{Perception of Social Connection with Agent}}
-    & Conversation Tone & appropriate, expressive, empathetic, persuasive & 13 
-    & \cite{chan2021kinvoices}\cmt{[74]}\cite{cox2022does}\cmt{[27]}\cite{cuadra2021my}\cmt{[67]}\cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{hu2021enhancing}\cmt{[56]}\cite{jestin2022effects}\cmt{[81]}\cite{misu2011toward}\cmt{[83]}\cite{tolmeijer2021female}\cmt{[62]}\cite{yang2021effect}\cmt{[72]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}
-\\ \cline{2-5}
-    & Social Presence & connectedness, familiarity, psychological distance & 18
-    & \cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cuadra2021my}\cmt{[67]}\cite{diederich2019emulating}\cmt{[25]}\cite{gnewuch2018faster}\cmt{[19]}\cite{gnewuch2018chatbot}\cmt{[21]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{go2021conversational}\cmt{[80]}\cite{khooshabeh2011does}\cmt{[37]}\cite{kim2020can}\cmt{[24]}\cite{lee2019s}\cmt{[55]}\cite{lubis2019positive}\cmt{[43]}\cite{lubold2016effects}\cmt{[86]}
-    \cite{ma2022ask}\cmt{[29]}\cite{niewiadomski2013laugh}\cmt{[85]}\cite{westerman2019believe}\cmt{[9]}    
-\\ \cline{2-5}
-    & Intimacy & intimate, rapport, quality of relationship & 7 
-    & \cite{choi2020nobody}\cmt{[54]}\cite{khooshabeh2011does}\cmt{[37]}\cite{kim2020can}\cmt{[24]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{lubold2016effects}\cmt{[86]}\cite{westerman2019believe}\cmt{[9]}
-\\ \Xhline{1.2pt}
-\multirow{2}{*}{\parbox{0.16\textwidth}{Perception of Agent's Humanness}}
-    & Human-likeness & human-like, natural, artificial, machine-like & 20
-    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cox2022does}\cmt{[27]}\cite{diederich2019emulating}\cmt{[25]}\cite{gnewuch2018faster}\cmt{[19]}\cite{haas2022keep}\cmt{[78]}\cite{hu2022polite}\cmt{[76]}\cite{jeong2019exploring}\cmt{[10]}\cite{jestin2022effects}\cmt{[81]}\cite{lubis2019positive}\cmt{[43]}\cite{ma2022ask}\cmt{[29]}\cite{misu2011toward}\cmt{[83]}\cite{niewiadomski2013laugh}\cmt{[85]}
-    \cite{ouchi2019should}\cmt{[59]}\cite{seeger2021chatbots}\cmt{[35]}\cite{wester2015artificial}\cmt{[14]}\cite{westerman2019believe}\cmt{[9]}\cite{zhu2022effects}\cmt{[26]}    
-\\ \cline{2-5}
-    & Personality Traits & friendly, kind, warm, creepy, likeable, polite & 27
-    & \cite{andrews2012system}\cmt{[38]}\cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cox2022does}\cmt{[27]}\cite{cuadra2021my}\cmt{[67]}\cite{haas2022keep}\cmt{[78]}\cite{habler2019effects}\cmt{[63]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{huiyang2022improving}\cmt{[17]}\cite{jeong2019exploring}\cmt{[10]}\cite{jestin2022effects}\cmt{[81]}\cite{khooshabeh2011does}\cmt{[37]}
-    \cite{kim2019comparing}\cmt{[89]}\cite{lee2019s}\cmt{[55]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{miehle2018exploring}\cmt{[51]}\cite{moilanen2022measuring}\cmt{[82]}\cite{ouchi2019should}\cmt{[59]}\cite{tolmeijer2021female}\cmt{[62]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}\cite{wester2015artificial}\cmt{[14]}\cite{zhu2022effects}\cmt{[26]}
-\\ \Xhline{1.2pt}
-\end{tabular}%
-}
-\caption{Perception measures}
-\label{tab:perceptions}
-\end{table*}
 
@@
 
+\begin{table*}[ht]
+\renewcommand*{\arraystretch}{1.4}
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{@{}p{0.17\textwidth} | p{0.12\textwidth} | p{0.20\textwidth} | >{\centering}p{0.09\textwidth} | p{0.42\textwidth} @{}}
+%!{\vrule width 1.2pt} 
+\Xhline{1.2pt}
+\multicolumn{2}{l|}{\textbf{Perception Aspects}} & \textbf{Examples} & \textbf{No. Papers} & \textbf{Papers} 
+\\ \Xhline{1.2pt}
+\multirow{3}{*}{\parbox{0.16\textwidth}{Perception of Interaction with Agent}}
+    & Usability & accuracy, ease of use, efficiency, helpfulness & 23 
+    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2022expressive}\cmt{[77]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cuadra2021my}\cmt{[67]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{elsholz2019exploring}\cmt{[61]}\cite{haas2022keep}\cmt{[78]}\cite{habler2019effects}\cmt{[63]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2019comparing}\cmt{[89]}\cite{kim2020can}\cmt{[24]}
+    \cite{kraus2020effects}\cmt{[64]}\cite{linnemann2018can}\cmt{[15]}\cite{ma2022ask}\cmt{[29]}\cite{miehle2018exploring}\cmt{[51]}\cite{misu2011toward}\cmt{[83]}\cite{roy2021users}\cmt{[71]}\cite{spillner2021talk}\cmt{[18]}\cite{wilhelm2022keep}\cmt{[28]}
+\\ \cline{2-5}
+    & Engagement & enjoyment, annoyance, desirable, intention to use  & 28
+    & \cite{andrews2012system}\cmt{[38]}\cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cox2022does}\cmt{[27]}\cite{cuadra2021my}\cmt{[67]}\cite{elsholz2019exploring}\cmt{[61]}\cite{fadhil2018effect}\cmt{[52]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{go2021conversational}\cmt{[80]}\cite{healey2013relating}\cmt{[39]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2020can}\cmt{[24]}\cite{kim2019comparing}\cmt{[89]}
+    \cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{ma2022ask}\cmt{[29]}\cite{miehle2018exploring}\cmt{[51]}\cite{miyamoto2017improving}\cmt{[46]}\cite{moilanen2022measuring}\cmt{[82]}\cite{roy2021users}\cmt{[71]}\cite{spillner2021talk}\cmt{[18]}\cite{volkel2021examining}\cmt{[69]}\cite{volkel2022user}\cmt{[75]}\cite{xiao2021let}\cmt{[73]}\cite{yang2021effect}\cmt{[72]}\cite{zhu2022effects}\cmt{[26]}
+\\ \cline{2-5}
+    & Satisfaction & service satisfaction, quality of interaction & 12
+    & \cite{ceha2022expressive}\cmt{[77]}\cite{choi2020nobody}\cmt{[54]}\cite{diederich2019emulating}\cmt{[25]}\cite{elsholz2019exploring}\cmt{[61]}\cite{habler2019effects}\cmt{[63]}\cite{gnewuch2018faster}\cmt{[19]}\cite{hoegen2019end}\cmt{[31]}\cite{hu2022polite}\cmt{[76]}\cite{ma2022ask}\cmt{[29]}\cite{roy2021users}\cmt{[71]}\cite{wilhelm2022keep}\cmt{[28]}\cite{yang2017perceived}\cmt{[44]}
+\\ \Xhline{1.2pt} 
+\multirow{3}{*}{\parbox{0.16\textwidth}{Perception of Agent's Ability}}
+    & Intelligence & knowledgeable, intelligent, expertise & 11
+    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cuadra2021my}\cmt{[67]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{feijoo2021effects}\cmt{[70]}\cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}\cite{spillner2021talk}\cmt{[18]}\cite{volkel2022user}\cmt{[75]}\cite{yang2017perceived}\cmt{[44]}
+\\ \cline{2-5}
+    & Competence & competent, capable & 4 
+    & \cite{cox2022does}\cmt{[27]}\cite{kraus2020effects}\cmt{[64]}\cite{lee2019s}\cmt{[55]}\cite{westerman2019believe}\cmt{[9]}
+\\ \cline{2-5}
+    & Trust & credibility, trustworthy, truthfulness, confidence & 15
+    & \cite{andrews2012system}\cmt{[38]}\cite{chan2021kinvoices}\cmt{[74]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{fadhil2018effect}\cmt{[52]}\cite{healey2013relating}\cmt{[39]}\cite{hoegen2019end}\cmt{[31]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kraus2020effects}\cmt{[64]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{ma2022ask}\cmt{[29]}\cite{seeger2021chatbots}\cmt{[35]}\cite{tolmeijer2021female}\cmt{[62]}\cite{wilhelm2022keep}\cmt{[28]}
+\\ \Xhline{1.2pt} 
+\multirow{3}{*}{\parbox{0.16\textwidth}{Perception of Social Connection with Agent}}
+    & Conversation Tone & appropriate, expressive, empathetic, persuasive & 13 
+    & \cite{chan2021kinvoices}\cmt{[74]}\cite{cox2022does}\cmt{[27]}\cite{cuadra2021my}\cmt{[67]}\cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{hu2021enhancing}\cmt{[56]}\cite{jestin2022effects}\cmt{[81]}\cite{misu2011toward}\cmt{[83]}\cite{tolmeijer2021female}\cmt{[62]}\cite{yang2021effect}\cmt{[72]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}
+\\ \cline{2-5}
+    & Social Presence & connectedness, familiarity, psychological distance & 18
+    & \cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cuadra2021my}\cmt{[67]}\cite{diederich2019emulating}\cmt{[25]}\cite{gnewuch2018faster}\cmt{[19]}\cite{gnewuch2018chatbot}\cmt{[21]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{go2021conversational}\cmt{[80]}\cite{khooshabeh2011does}\cmt{[37]}\cite{kim2020can}\cmt{[24]}\cite{lee2019s}\cmt{[55]}\cite{lubis2019positive}\cmt{[43]}\cite{lubold2016effects}\cmt{[86]}
+    \cite{ma2022ask}\cmt{[29]}\cite{niewiadomski2013laugh}\cmt{[85]}\cite{westerman2019believe}\cmt{[9]}    
+\\ \cline{2-5}
+    & Intimacy & intimate, rapport, quality of relationship & 7 
+    & \cite{choi2020nobody}\cmt{[54]}\cite{khooshabeh2011does}\cmt{[37]}\cite{kim2020can}\cmt{[24]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{lubold2016effects}\cmt{[86]}\cite{westerman2019believe}\cmt{[9]}
+\\ \Xhline{1.2pt}
+\multirow{2}{*}{\parbox{0.16\textwidth}{Perception of Agent's Humanness}}
+    & Human-likeness & human-like, natural, artificial, machine-like & 20
+    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cox2022does}\cmt{[27]}\cite{diederich2019emulating}\cmt{[25]}\cite{gnewuch2018faster}\cmt{[19]}\cite{haas2022keep}\cmt{[78]}\cite{hu2022polite}\cmt{[76]}\cite{jeong2019exploring}\cmt{[10]}\cite{jestin2022effects}\cmt{[81]}\cite{lubis2019positive}\cmt{[43]}\cite{ma2022ask}\cmt{[29]}\cite{misu2011toward}\cmt{[83]}\cite{niewiadomski2013laugh}\cmt{[85]}
+    \cite{ouchi2019should}\cmt{[59]}\cite{seeger2021chatbots}\cmt{[35]}\cite{wester2015artificial}\cmt{[14]}\cite{westerman2019believe}\cmt{[9]}\cite{zhu2022effects}\cmt{[26]}    
+\\ \cline{2-5}
+    & Personality Traits & friendly, kind, warm, creepy, likeable, polite & 27
+    & \cite{andrews2012system}\cmt{[38]}\cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cox2022does}\cmt{[27]}\cite{cuadra2021my}\cmt{[67]}\cite{haas2022keep}\cmt{[78]}\cite{habler2019effects}\cmt{[63]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{huiyang2022improving}\cmt{[17]}\cite{jeong2019exploring}\cmt{[10]}\cite{jestin2022effects}\cmt{[81]}\cite{khooshabeh2011does}\cmt{[37]}
+    \cite{kim2019comparing}\cmt{[89]}\cite{lee2019s}\cmt{[55]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{miehle2018exploring}\cmt{[51]}\cite{moilanen2022measuring}\cmt{[82]}\cite{ouchi2019should}\cmt{[59]}\cite{tolmeijer2021female}\cmt{[62]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}\cite{wester2015artificial}\cmt{[14]}\cite{zhu2022effects}\cmt{[26]}
+\\ \Xhline{1.2pt}
+\end{tabular}%
+}
+\caption{Perception measures}
+\label{tab:perceptions}
+\end{table*}
+
 \subsection{Conversation Architecture Elements}
@@
 \Xhline{1.2pt}
-\textbf{Category} & \textbf{Theme} & \textbf{Sample Codes} & \textbf{No. Papers} & \textbf{Papers}
+\textbf{Element Category} & \textbf{Element} & \textbf{Examples} & \textbf{No. Papers} & \textbf{Papers}
 \\ \Xhline{1.2pt}
@@
 
-\subsection{Relationship Between Anthropomorphized Perceptions and Conversation Architecture Elements}
-
-\begin{figure*}[]
-  \centering
-  \includegraphics[width=\textwidth]{fig-heatmap-impact.png}
-  \caption{Heatmap of literature for perception of conversational agents for each type of conversational architecture element}
-  \label{fig:heatmap-impact}
-\end{figure*}
+\subsection{Relationship Between Perceptions of Agents and Conversation Architecture}
 
@@
 Lastly, majority of the studies found that non-linguistic formats of a CA impacts the perception of the interaction, as \textbf{prosodic cues} such as expressiveness increased participants' engagement ratings \cite{zhu2022effects}\cmt{[26]}, and text variations such as using response delay increased user's satisfaction with the chatbot interaction \cite{gnewuch2018faster}\cmt{[19]}.
+
+\begin{figure*}[]
+  \centering
+  \includegraphics[width=\textwidth]{fig-heatmap-coverage.png}
+  \caption{Heatmap of literature for perception of conversational agents for each type of conversational architecture element}
+  \label{fig:heatmap-coverage}
+\end{figure*}
 

### 2023-02-14 paper.tex
second pass up to 3.1

@@
 We highlight the need for further research for the perception of agent's ability and perception of social connection with agent's, especially as it relates to the linguistic style of conversational agents.
-Also, there is the need to be consistent in the assessment of agents' perceptions, and address ethical concerns in design.
+Also, there is the need to be consistent in the assessment of agents' perceptions, and consider ethical concerns in design.
 \end{abstract}
@@
 
-Conversational agents (CAs) are software-based systems, either voice of text-based, designed to interact with humans using natural language.
-Adoption for CAs such as Alexa (Amazon) or Siri (Apple) are rapidly growing in the market, with half of US internet users own one or more smart speaker devices \cite{2022comscore}.
+Conversational agents (CAs) are designed to interact with humans using natural language through voice or text modalities.
+Adoption for CAs such as Alexa (Amazon) or Siri (Apple) are rapidly growing in the market, with half of Internet users in United States own one or more smart speaker devices \cite{2022comscore}.
 These conversational agents are designed to be ubiquitous, easily accessible through smartphones, tablets, laptops and smart devices.
-Because these agents leverage natural language for interaction, they solicit social responses from users, encouraging users to attribute lifelike qualities, a.k.a.
-anthropomorphized perceptions to CAs \cite{eyssel2012if}.
+Since these agents interact with users using natural language, there are nuances in their communications affected by conversation architecture, which is what they say and how they say it.
+%they solicit social responses from users, encouraging users to attribute lifelike qualities, a.k.a. anthropomorphized perceptions to CAs \cite{eyssel2012if}.
 
-Anthropomorphism is defined as the attribution of traits that we typically associate with being distinctly human to nonhuman entities \cite{waytz2010sees}.
+%Anthropomorphism is defined as the attribution of traits that we typically associate with being distinctly human to nonhuman entities \cite{waytz2010sees}.
 For example, users tend to personify conversational agents like Amazon Alexa by using person pronouns instead of object pronouns in online reviews \cite{purington2017alexa}.
@@
 
-One of the key factors for anthropomorphized perception is how conversational agents convey information through verbal or non-verbal cues.
+Previous research has show that there is a connection between conversation architecture and the perception of agents.
 Studies have found that conversational agents are perceived as more socially present and emotionally intelligent if they use affect language such as sentiment-adaptive response based on user's utterances, resulting in higher user satisfaction \cite{diederich2019emulating}\cite{yang2017perceived}.
-Also, CAs that mimic user behaviour through lexical alignment reduce users' cognitive workload, resulting in higher engagement with the interaction \cite{spillner2021talk}.
+Also, CAs that mimic user's utterances through lexical alignment reduce users' cognitive workload, resulting in higher engagement with the interaction \cite{spillner2021talk}.
 Non-linguistic cues such as expressive prosody contribute to higher perceived intimacy with the user, as well as higher perceived enjoyment and ease of use \cite{kim2020can}.
-While there is existing research on the impact of conversation architecture on anthropomorphized perceptions of agents, their findings are hard to generalize due to obstacles in consistency of taxonomy and measures.
+Although research on how conversation architecture affects agents' perceptions already exists, there is a lack of understanding on the coverage of relationships explored in literature, as well as synthesizing these findings into a generalized framework.
+One of the possible issues is the lack of clear and consistent definition on the aspects of user's perceptions of agent and conversation architectural elements.
 %However, conversational architecture design may lead to negative consequences, such as an agent with an extroverted personality may be seen as less trustworthy, as users are irritated by the system's overly familiar attitude \cite{andrews2012system}.
 
- There have been recent efforts to systematically analyze UX measurements used to evaluate conversational agents.
-In Clark et al's review for the state of speech interfaces, the authors created a list the different concepts used to measure disembodied voice-based agents such as user attitudes and task performance \cite{clark2019state}.
-Rapp et al.
-\cite{rapp2021human} analyzed literature related specifically to text-based CAs, where the themes emerged from their analysis has aspects related to the anthropomorphized perceptions, like humanness and emotional experience.
+Related to the perception aspects of agents, there have been recent efforts to systematically analyze user experience criteria used to evaluate conversational agents.
+Some review papers have created a list of dimensions used to assess conversational agents, which include the perceptions of agents (e.g.
+empathy, humanness) alongside other assessments (e.g.
+physiological data) \cite{clark2019state}\cite{finch2020towards}.
+%In Clark et al's review for the state of speech interfaces, the authors created a list the different concepts used to assess disembodied voice-based agents such as user attitudes and task performance \cite{clark2019state}.
+Other papers categorized CA assessments into themes.
+For example, Rapp et al.
+\cite{rapp2021human} generated themes related to how users' experience with chatbots such as experiencing the chatbot including assessments on expectation, perception, satisfaction etc.
 Most recently, Zheng et al's literature review on the UX research of CAs \cite{zheng2022ux} categorized the metrics based on the type of method used, including technical measures like system error rate and perception measures like perceived social presence.
-Specifically to measures related to anthropomorphized perceptions, there is a gap of research to systematically analyze the different aspects of these perceptions, as well as a consistent taxonomy to refer to them.
-Similarly for conversation architecture elements, there is existing research to systematically analyze them, like Feine et al \cite{feine2019taxonomy}'s overall framework provides consistent categories for social cues.
+However, existing studies use different terminologies and categories across aspects of perception.
+As an illustration, it is unclear if the theme of experiencing the chatbot from Rapp et al.
+\cite{rapp2021human} contains similar aspects to the perception towards CA in Zheng et al \cite{zheng2022ux}'s analysis.
+
+For conversation architecture elements, Feine et al \cite{feine2019taxonomy} created a foundational knowledge by providing a taxonomy of social cues, which is defined as "a cue of a CA that triggers a social reaction of the user towards the CA." Elements of conversation architecture are captured in the taxonomy, alongside other social cues such as the embodied agents' appearance and movements.
+Clark et al \cite{clark2019state} had also captured conversation architecture elements under the research topic of system speech production, with similar categorizations across content, style, and other topics.
+While these papers captured conversation architecture elements as part of their broader scope of research, there exist the need for standardized definitions specifically for conversation architecture that reflects its unique characteristics.
+
+%there is existing research to systematically analyze them, like Feine et al \cite{feine2019taxonomy}'s overall framework provides consistent categories for social cues.
 However, it is unknown which conversation architecture elements have impacts on the perceptions of agents.
@@
 
-We are addressing this research gap by analyzing how to design conversation architecture in order to orchestrate anthropomorphized perceptions of conversational agents.
-First, we want to understand (RQ1) what aspects of anthropomorphized perceptions are being explored that are affected by conversation architecture.
-Conversation architecture has various aspects that affect a CA's utterances such as the use of humour, emoticons, or lexical alignment.
-This leads to our second research question: (RQ2) what are the elements of conversation architecture that are relevant to anthropomorphized perceptions?
-Lastly, we want to understand the impact of conversation architecture on perceptions of agent, which leads to our third research question: (RQ3) what are the relationships between the specifics of conversation architecture elements and the anthropomorphized perceptions of CAs?
+In this paper, we are addressing these research gaps by analyzing how to design conversation architecture in order to orchestrate the perceptions of conversational agents.
+First, we want to understand \textbf{(RQ1) what perception aspects of agents are being explored in relation to the effects of conversation architecture elements}.
+Various elements of conversation architecture can be used in a CA's utterances such as humour, emoticons, or lexical alignment.
+This leads to our second research question: \textbf{(RQ2) what elements of conversation architecture are relevant to the perceptions of agents?} Lastly, we want to understand the impact of conversation architecture on perceptions of agent, which leads to our third research question: \textbf{(RQ3) what are the relationships between the specifics of conversation architecture elements and the perceptions of CAs?}
 
-To answer these questions, we need to synthesize existing literature by performing a comprehensive review from 2010 to 2022 on the impact of conversation architecture elements on anthropomorphized perceptions of CAs (n=57).
-We collected perceptions that are affected by conversation architecture and grouped them into four categories and eleven themes (Table \ref{tab:perceptions}).
-Similarly, we analyzed the conversation architecture elements explored in literature and grouped them into three categories and ten themes (Table \ref{tab:cues}).
-Lastly, we coded the explored connections between conversation architecture and perceptions and demonstrated the impacted relationship into a generalized framework (Figure \ref{fig:heatmap-impact}).
-Through our analysis, we also found that there are inconsistencies on how anthropomorphized perceptions are measured across studies, as well as influencing factors other than conversation architecture that may be impacting the perceptions of agents.
+To answer these questions, we performed a comprehensive review of existing literature from 2010 to 2022 and synthesized findings on the impact of conversation architecture elements on the perceptions of CAs based on relevant papers (n=57).
+We collected perceptions of agents that are affected by conversation architecture,  grouped the aspects into four categories and eleven sub-categories (Table \ref{tab:perceptions}).
+We also analyzed conversation architecture related to perception of agents and grouped them into three categories and ten elements (Table \ref{tab:cues}).
+Lastly, we coded the explored connections between conversation architecture and perceptions and demonstrated the relationship into a synthesized framework (Figure \ref{fig:heatmap-impact}).
+Through our analysis, we also found that there are inconsistencies in the assessment of perceptions across studies, as well as influencing factors other than conversation architecture that impact the perceptions of agents.
 
-This work contributes to the HCI community by presenting an in-depth analysis on the impact of conversation architecture on anthropomorphized perceptions.
-We created a taxonomy for perceptions and conversation architecture elements to provide consistent terms that can be used in future research.
-Also, our analysis extends existing reviews on UX research of CAs \cite{clark2019state}\cite{rapp2021human}\cite{zheng2022ux} by providing a generalized framework outlining the relationships between conversation architecture and anthropomorphized perceptions.
-This framework provides the foundational knowledge to design conversation agents to solicit specific social responses from users.
+This work contributes to the HCI community by presenting an in-depth analysis on the affect of conversation architecture on perceptions of conversational agents.
+We created a taxonomy for perception aspects and conversation architecture elements, providing clear and consistent terms that can be used in future research.
+Also, our analysis extends existing reviews on UX research of CAs \cite{clark2019state}\cite{rapp2021human}\cite{zheng2022ux} by providing a synthesized framework outlining the relationships between conversation architecture and perceptions of agents.
+With the help of this framework, we are taking the first step to understand how to design conversational agents to solicit specific social reactions from users.
 
-In the remainder of the paper, we first outline our literature review and data analysis process, as well as the characteristics of the papers in our reviewed corpus.
-Following that, we describe in detail the taxonomy of anthropomorphized perceptions, taxonomy of conversation architecture element, as well as the framework on the relationships between perceptions and conversation architecture.
-Finally, we discuss the research challenges and opportunities as well as ethical considerations for designing conversational architecture to orchestrate anthropomorphized perceptions of conversational agents.
+In the remainder of the paper, we first outline our data collection and data analysis process, as well as the characteristics of the papers in our reviewed corpus.
+Following that, we describe in detail the taxonomy for the perception of agents, the taxonomy for conversation architecture element, as well as the framework on the relationships between perceptions of agents and conversation architecture.
+Finally, we discuss research challenges and opportunities as well as ethical considerations for designing conversational architecture to orchestrate perceptions of conversational agents.
 
@@
 
-This section describes the research methodologies for the search procedure, selection criteria and data analysis process.
+This section describes the research methodologies used for data collection and data analysis. Additionally, it presents the characteristics of the papers in our reviewed corpus.
 
@@
 
-Following PRISMA guidelines \cite{prisma}, we reviewed and selected literature relevant to the relationships between the specifics of conversation architecture elements and anthropomorphized perceptions of CAs.
+Following PRISMA guidelines \cite{prisma}, we reviewed and selected literature exploring the relationship between the specifics of conversation architecture elements and perceptions of CAs.
 Searches were carried out in the ACM Digital Library between January 1 and January 15, 2023.
-During initial analysis, it didn't seem like there were common terms used to refer to either conversation architecture elements, or anthropomorphized perceptions.
-As such, search terms were kept general to literature related to conversational agents.
-Based on search terms used in previously published literature reviews \cite{clark2019state}\cite{rapp2021human} , the following keywords have been identified to search for publications related to conversational user interfaces:
+Through our analysis, we didn't find any common terms used to refer to either conversation architecture elements, or aspects of perceptions.
+As such, we kept our search term to capture articles related to conversational agents.
+Based on search terms used in previously published literature reviews \cite{clark2019state}\cite{rapp2021human}, the following keywords are used to search for publications related to conversational user interfaces:
 \newline
@@
 
-The initial query retrieved 2901 unique publications. The following selection criteria are applied to identify literature related to the effect of conversational architecture on perception of agents:
+The following selection criteria are applied to identify literature related to the effect of conversational architecture on the perception of agents:
 \begin{itemize}
-  \item Peer-reviewed publications written in English
-  \item Voice-based or text-based conversational agents
-  \item Experiment study on the impact of conversation architecture elements on the anthropomorphized perceptions of agents
-  \item Impact of conversation architecture elements can be separated from other effects (e.g. embodiment)
+  \item The paper was published between 2010 and 2022.
+  \item The paper is peer-reviewed and written in English.
+  \item The paper contains the use of voice-based or text-based conversational agents.
+  \item The paper contains studies on the impact of conversation architecture elements on the perceptions of agents.
+  \item The paper contains impact of conversation architecture elements can be separated from other effects (e.g. embodiment).
 
@@
 
-We screened the titles and abstracts of the papers based on the selection criteria below which resulted in 221 papers.
-Reviewing the full articles of these publication resulted in 49 papers for analysis.
-An additional search for related literature was also performed to find new publications, adding 8 more papers to the corpus.
-We identified 57 relevant articles that met our selection criteria (see Figure \ref{fig:prisma}).
+The initial query retrieved 2901 unique publications.
+We screened the titles and abstracts of the papers based on the selection criteria above, resulting in 221 papers.
+The fully body of these papers are then reviewed, selecting papers that met the criteria.
+A search for additional literature was also performed to supplement the corpus, adding 8 more papers to the selection.
+In total, we identified 57 relevant articles for analysis (see Figure \ref{fig:prisma}).
 
@@
 
-On the modality characteristics of the conversational agents in the corpus, there is a roughly even split between the modalities, with slightly more papers (n=30) studying voice-based CAs, and the rest (n=27) studying text-based CAs.
+On the modality characteristics of the conversational agents in the corpus, there is a roughly even split between the modalities, with slightly more papers exploring voice-based CAs (n=30) compared to text-based CAs (n=27).
 
@@
 
-\subsubsection*{Anthropomorphized Perceptions} To study RQ1, the exact quotes of anthropomorphized perception measurements were extracted from each paper.
-Inductive thematic analysis was used to group these verbatim quotes into codes based on their meanings.
-For example, the code likeability of the agent contains the questionnaire item "this voice agent was likeable" used by \cite{cuadra2021my}\cmt{[67]}, Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed}'s set of questions on likeability used by \cite{linnemann2018can}\cmt{[15]}, and Subjective Assessment of Speech System Interface (SASSI) questionnaire \cite{hone2000towards}\cmt{sassi}'s set of questions on likeability used by  \cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}.
+\subsubsection*{Perceptions of Agents} To understand the perceptions of agents related to conversation architecture (RQ1), assessments for the perceptions of agents were extracted from each paper.
+We used inductive thematic analysis to group these assessments into codes based on their meanings.
+For example, the code likeability of the agent contains assessments such as the questionnaire item "this voice agent was likeable" used by \cite{cuadra2021my}\cmt{[67]}, Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed}'s set of questions on likeability used by \cite{linnemann2018can}\cmt{[15]}, and Subjective Assessment of Speech System Interface (SASSI) questionnaire \cite{hone2000towards}\cmt{sassi}'s set of questions on likeability used by \cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}.
 This step resulted in 83 unique codes.
-The codes are then organized based similarity of the meanings, resulting in 11 basic themes.
-For example, the basic theme of \textit{personality traits} of the agent contains measurements such as likeability, friendliness, and warmth.
-Lastly, the 11 basic themes are categorized into 4 organizing themes: \textit{perception of interaction with agent, perception of agent's ability, perception of social connection with agent, and perception of agent's humanness} (Table \ref{tab:perceptions}).
+These codes are then organized based similarity of the meanings, resulting in 11 aspects of perceptions.
+For example, the aspect of \textit{personality traits} of the agent contains measurements such as likeability, friendliness, and warmth.
+Lastly, the 11 aspects are grouped into 4 categories: \textit{perception of interaction with agent, perception of agent's ability, perception of social connection with agent, and perception of agent's humanness} (Table \ref{tab:perceptions}).
 
 \subsubsection*{Conversation Architecture Elements}
-The study RQ2, the conversation architecture elements used in the study were extracted from each paper.
-Some of the papers were applying multiple elements to the CA design, such as the the anthropomorphic design used in this study \cite{seeger2021chatbots}\cmt{[35]}.
-In the case where multiple elements were used, the codes broke down the conversation architecture into its core components.
-For example, the anthropomorphic design used in Seeger et al's study \cite{seeger2021chatbots}\cmt{[35]} was broken down to the elements of emotional expressions, is-typing indicator, emoticons, and response delay to capture as codes.
-58 unique codes were created as part of this process, capturing elements like sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}, lexical alignment \cite{spillner2021talk}\cmt{[18]}, and typos \cite{westerman2019believe}\cmt{[9]}.
-Codes were then organized based on similarity of the elements.
-For example, the basic theme of \textit{disfluency} contains elements of fillers \cite{jeong2019exploring}\cmt{[10]}\cite{wester2015artificial}\cmt{[14]}, interjections \cite{ceha2022expressive}\cmt{[77]}\cite{hu2021enhancing}\cmt{[56]}, and repetitions \cite{yang2021effect}\cmt{[72]}.
-Lastly, these basic themes are then categorized into organizing themes adapted from the social cues taxonomy structure by Feine et al \cite{feine2019taxonomy}.
-Based on this paper, the Verbal-Content category is mapped to our organizing theme of \textit{linguistic content}, and the Verbal-Style category is mapped to our organizing theme of \textit{linguistic style}.
-Given our analysis focuses on the text and voice aspects of a conversational agent and does not analyze the embodiment aspects of design, the visual category is not applicable for our analysis.
-Also, we collapsed the auditory and invisible categories into the organizing theme of \textit{non-linguistic format} (Table \ref{tab:cues}).
+As to the elements of conversation architecture that are relevant to the perception of agents (RQ2), we extracted the conversation architecture used in each paper as codes.
+Some of the papers used multiple features in their CA design, such as the the anthropomorphic agent used in Seeger et al's study \cite{seeger2021chatbots}\cmt{[35]}.
+In these composite situations, we broke them down into their individual features.
+For example, the anthropomorphic agent \cite{seeger2021chatbots}\cmt{[35]} was separated into emotional expressions, is-typing indicator, emoticons, and response delay and captured as codes.
+58 unique codes were created as part of this process, capturing features like sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}, lexical alignment \cite{spillner2021talk}\cmt{[18]}, and typos \cite{westerman2019believe}\cmt{[9]}.
+We then organized these codes into elements based on similarity.
+For example, the element of \textit{disfluency} contains fillers \cite{jeong2019exploring}\cmt{[10]}\cite{wester2015artificial}\cmt{[14]}, interjections \cite{ceha2022expressive}\cmt{[77]}\cite{hu2021enhancing}\cmt{[56]}, and repetitions \cite{yang2021effect}\cmt{[72]}.
+Lastly, these elements are grouped into categories adapted from the social cues taxonomy structure by Feine et al \cite{feine2019taxonomy}.
+Based on this paper, the Verbal-Content category is mapped to our category of \textit{linguistic content}, and the Verbal-Style category is mapped to our category of \textit{linguistic style}.
+Given our analysis focuses on the conversational aspects of a CA, the social cues' categories related to embodiment aspects were not used.
+Also, we collapsed the auditory and invisible categories into our category of \textit{non-linguistic format} (Table \ref{tab:cues}).
 
-\subsubsection*{Relationship Between Anthropomorphized Perceptions and Conversation Architecture Elements}
-For RQ3, we extracted the relationships between perceptions and architecture elements from each paper based on the codes developed for anthropomorphized perceptions and conversation architecture elements above, noting whether the architecture element had an impact of on the perceptions.
-Out of the 57 papers, 264 connections between anthropomorphized perceptions and conversation architecture elements were found.
-To analyze specifically the relationships between the specifics of conversation architecture that affect the anthropomorphized perceptions of CAs, 69 connections that did not result in significant relationships were discarded, resulting in 195 relationships for analysis.
-For example, the specific connection between style matching and user satisfaction was discarded because Hoegen et al.
+\subsubsection*{Relationship Between Perceptions of Agents and Conversation Architecture}
+To study the relationship between conversation architecture and conversation architecture, we extracted the connections explored in each paper, using the perception aspects and conversation architecture elements developed in the previous data analysis steps.
+Each connection's effect was also recorded based on whether an impact was found in the study and the nature of that impact.
+Out of our review corpus, 265 explored connections between perceptions of agents and conversation architecture were found.
+To analyze specifically the relationships between the specifics of conversation architecture that affect the perceptions of CAs, 72 connections that did not result in significant relationships were discarded, resulting in 193 relationships for analysis.
+For example, the connection between the matching style of a CA and user satisfaction was discarded because Hoegen et al.
 \cite{hoegen2019end}\cmt{[31]} did not find a significant difference between the style matching agent and the non-style matching agent for overall interaction satisfaction.
-Out of the 195 relationships, 185 were relationships between individual architecture elements and perceptions.
-These single architecture element to perception relationships are visualized as a heatmap based on literature coverage within the literature review corpus, as seen in Figure \ref{fig:heatmap-impact}.
-Perceptions impacted by the composite of multiple architecture elements in an agent will be discussed in more details in the Composite Architecture Elements section.
+Out of the 193 relationships, 10 were relationships using agents using multiple architecture elements.
+They were not included in the framework as it is not possible attribute the perceptions of agents to its underlying elements.
+Overall, 183 relationships between individual architecture elements and perceptions of agents are incorporated into our synthesized framework, visualized as a heatmap to demonstrate their relationships with each other (Figure \ref{fig:heatmap-impact}).
+
+%183 were relationships between individual architecture elements and perceptions. These single architecture element are included in our synthesized frame, 
+%CAs using multiple conversation architecture elements were discarded because perceptions are measured at the aggregate level, we cannot attribute the perceptions of agents down to its underlying elements.
+%Perceptions impacted by the composite of multiple architecture elements in an agent will be discussed in more details in the Composite Architecture Elements section.
 
@@
 
-As shown in Table \ref{tab:perceptions}, there are four organizing themes defined for the anthropomorphized perceptions of conversational agents covering 11 basic themes of perception.
-The details of each theme are discussed below.
+As shown in Table \ref{tab:perceptions}, there are four categories defined for the perceptions of conversational agents covering 11 aspects of perception.
+The details of each aspect are discussed below.
 
-\textbf{Perception of interaction with agent} evaluates the overall interaction quality users had with the conversational agent.
-The three basic themes for this perceptions are usability, engagement and satisfaction.
-\textit{Usability} measures the utilitarian aspects of the interaction, whether it was accurate, easy to use, efficient or helpful.
+\textbf{Perception of interaction with agent} assesses the overall interaction quality users had with the conversational agent.
+The three aspects for this perceptions are usability, engagement and satisfaction.
+\textit{Usability} captures the utilitarian aspects of the interaction, whether it was accurate, easy to use, efficient or helpful.
 Some commonly used methods to measure usability include the response accuracy portion of the SASSI questionnaire \cite{hone2000towards}\cmt{sassi}, or the NASA Task Load Index (NASA-TLX) \cite{hart1988development}\cmt{nasa} to measure cognitive workload.
-Questions such as "the system is easy to use" or "it is easy to understand the agent" are also measures of usability.
-\textit{Engagement} on the other hand measures users' emotional reactions, whether they have enjoyed the conversation with CA, or annoyed or frustrated with the interaction.
+Questions such as "the system is easy to use" or "it is easy to understand the agent" are also used to evaluate usability.
+\textit{Engagement} on the other hand captures users' emotional reactions to the CA, whether they have enjoyed the conversation, or annoyed or frustrated with the interaction.
 Some commonly used methods to measure engagement include the annoyance portion of the SASSI questionnaire \cite{hone2000towards}\cmt{sassi}, and the Use Engagement Scale (UES) \cite{o2018practical}\cmt{ues}.
-Questions such as "I enjoyed using the system" or "I felt frustrated with the agent" are also measures of engagement.
-Lastly, \textit{Satisfaction} measures users' overall satisfaction interacting with the agent.
-Questions such as "the overall assessment of conversing with the CA was satisfactory" are used to measure this perception.
+Questions such as "I enjoyed using the system" or "I felt frustrated with the agent" are also used to evaluate engagement.
+Lastly, \textit{Satisfaction} captures users' overall satisfaction interacting with the agent.
+Questions such as "the overall assessment of conversing with the CA was satisfactory" are used to evaluate this perception.
 
-\textbf{Perception of agent's ability} evaluates the perceived capabilities of the agent.
-While there are some elements of system performance in this measure, the main aspect we are interested in is the perception differences for agents with identify system capabilities but with different architecture elements.
-Specifically, \textit{intelligence} measures the agent's expertise and knowledge, and it is commonly administered through the Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed} on the set of questions related to perceived intelligence.
-Also survey questions such as asking users about the agent's intelligence and domain knowledge are used to measure perceived intelligence.
-\textit{Competence} takes intelligence one step further by evaluating the agent's ability to put its intelligence into practice.
-To measure a CA's competence, there are usually surveys or qualitative feedback that the agent is capable and competent, and that the users have confidence in the agent's ability to get the job done.
-Lastly, \textit{trust} evaluates agent's truthfulness, credibility and benevolence.
+\textbf{Perception of agent's ability} assesses the perceived capabilities of the agent.
+While there are some elements of system performance in this category, we are mainly concerned with how agents with varied architecture elements but equivalent system capabilities are perceived differently.
+Specifically, \textit{intelligence} captures the agent's expertise and knowledge, and it is commonly administered through the Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed} using the set of questions related to perceived intelligence.
+Also survey questions such as asking users about the agent's intelligence and domain knowledge are used to evaluate perceived intelligence.
+\textit{Competence} takes intelligence one step further by examining the agent's ability to put its intelligence into practice.
+Surveys or qualitative feedback are usually used to assess if the agent is capable and competent, and whether users have confidence in the agent's ability to get the job done.
+Lastly, \textit{trust} captures agent's truthfulness, credibility and benevolence.
 Some commonly used methods to evaluate trust include the Trust Propensity Scale \cite{mayer1999effect} and the Individualized Trust Scale (ITS) \cite{wheeless1977measurement}.
-Questions such as "is the agent honest" and "can I trust the agent with sensitive information" are also measures of trust.
+Questions such as "is the agent honest" and "can I trust the agent with sensitive information" are also used to evaluate trust.
 
-\textbf{Perception of the social connection with agent} evaluates the emotional connections that users have with agents.
-The three basic themes of conversation tone, social presence and intimacy are included in this category.
-\textit{Conversation tone} measure the affective impression of the agent's tone, such as empathy, expressiveness, or passionate.
-Also, it measures whether the tone used by the agent is persuasive or appropriate for the conversation.
-\textit{Social presence} measures the sense of connectness and psychological distance users has with an agent.
-Some aspects in this measure include a sense of familiarity or similarity with the agent, whether users feel the agent behaves like them or have similar attitudes to them.
-The measure of \textit{Intimacy} extends social presence into the realm of the quality of relationships with an agent.
-Some commonly used measures include the set of social attraction questions from the interpersonal attraction questionnaire \cite{mccroskey1975development} and the quality of relationship inventory (QRI) \cite{pierce1997assessing}.
+\textbf{Perception of the social connection with agent} assesses the emotional connections that users have with agents.
+This category includes perception aspects of conversation tone, social presence and intimacy.
+\textit{Conversation tone} captures the affective impression of the agent's tone, such as empathy and expressiveness.
+Also, this aspect includes whether the tone used by the agent is persuasive or appropriate for the conversation.
+\textit{Social presence} captures the sense of connectness and psychological distance users have with an agent.
+Some aspects in this category include the sense of familiarity or similarity with the agent, and whether users feel the agent behaves like them or have similar attitudes to them.
+The category of \textit{Intimacy} extends social presence into the realm of the quality of relationships with an agent.
+Some commonly used methods to assess intimacy include the set of social attraction questions from the interpersonal attraction questionnaire \cite{mccroskey1975development} and the quality of relationship inventory (QRI) \cite{pierce1997assessing}.
 These questionnaires include questions like "I think the agent could be a friend of mine", or "I feel we could establish a personal relationship with each other".
 
-\textbf{Perception of agent's humanness} evaluates human-likeness and the anthropomorphized personality traits that users assign to agents.
-\textit{Human-likeness} measures whether the agent presented itself as natural and human-like, or artificial and machine-like.
-The Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed} set of questions related to anthropomorphism and the Ascent of Man scale \cite{kteily2015ascent} are commonly used methods to assess human-likeness.
-Survey questions with semantic scales such as "human-like / machine-like" and "artificial / natural" are also used for this perception.
+\textbf{Perception of agent's humanness} assesses the specifics of anthropomorphized perceptions of conversational agents.
+\textit{Human-likeness} captures whether the agent presented itself as natural and human-like, or artificial and machine-like.
+The Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed} set of questions related to anthropomorphism and the Ascent of Man scale \cite{kteily2015ascent} are commonly used methods to evaluate human-likeness.
+Survey questions with semantic scales such as "human-like / machine-like" and "artificial / natural" are also commonly used for this aspect of perception.
 \textit{Personality traits} captures the human characteristics that are attributes to the agent, such as warm, friendly, likeable, and polite.
-This is commonly captured in the qualitative feedback from users, commenting on whether the agent is extroverted or introverted, or the human characteristics they perceive the agent such as funny or witty.
-Some studies used the measure of the Big-5 personality traits \cite{gosling2003very} to map an agent's disposition on various personality dimensions.
+This is commonly collected as qualitative feedback from users, commenting on whether the agent is extroverted or introverted, or the human characteristics they perceive the agent such as funny or witty.
+Sometimes the Big-5 personality traits questionnaire \cite{gosling2003very} is used to map an agent's disposition on various personality dimensions.
 
-Overall there is good coverage of perception measures based on the list of papers reviewed in our corpus.
-The most commonly measured perceptions are related to the interaction with agent, followed by the perception of agent's humanness.
-There are two basic themes that are the least measured compared to the others: competence under the perception of agent's ability, and intimacy under the perception of social connection with agent.
+Overall there is a good coverage of different aspects of perception based on the list of papers reviewed in our corpus.
+The most commonly explored aspect categories is the perception the interaction with agent, followed by the perception of agent's humanness.
+There are two aspects that are the least explored compared to the others relationships: competence within the perception of agent's ability, and intimacy within the perception of social connection with agent.
 This may be due to the controlled lab settings for the experiments, where participants are given the scenarios for interaction.
-This environment is not conducive to forming relationships with a conversational partner, as noted by Linnerman et al.
+This type of environment is not conducive to forming relationships with a conversational partner, as noted by Linnerman et al.
 in their discussions \cite{linnemann2018can}\cmt{[15]}.
-Also, the same factor could impact the assessment of agent's abilities, as the users may not feel like they have the expertise to assess an agent's competence.
-These factors could contribute to the reasons why competency and intimacy are not as frequently measured in experimental studies.
-
-% Add citations
+The same factor could impact the assessment of agent's competence, as the users may not feel like they have the expertise to assess their perceptions.
+%These factors could contribute to the reasons why competency and intimacy are not as frequently measured in experimental studies.
 
@@
 \end{table*}
+
+%CW - second pass up to here
 
@@
 We may have missed some influential findings in these papers.
-To better understand the relationships between conversation architecture elements and anthropomorphized perceptions, we plan to conduct future reviews in literature and user studies to understand their real-world impacts.
+To better understand the relationships between conversation architecture elements and the perceptions of agents, we plan to conduct future reviews in literature and user studies to understand their real-world impacts.
+
+<TODO> Add more about perception of abilities, perception of social connections, especially for linguistic cues.
 

### 2023-02-15 paper.tex
AK edit of title & abstract

@@
 % \title[short title]{How to Make Pinocchio a Real Boy? Designing conversational architecture elements to achieve desirable anthropomorphized perceptions}
-\title[The Bot with the Eloquent Speech]{The Bot with the Eloquent Speech: Exploring the Relationship between Perceptions of Conversational Agents and Their Conversation Architecture}
+\title{The Bot on Speaking Terms: The Effects of Conversation Architecture on Perceptions of Conversational Agents}
 
@@
 %% of authors' names for this purpose.
-\renewcommand{\shortauthors}{Wei, Kim, and Kuzminykh}
+\renewcommand{\shortauthors}{Anon}
 
@@
 \begin{abstract}
-Previous research has demonstrated a relationship between the structure of conversational agents' natural language interaction and how these agents are perceived by their users.
-However, the systematic connections between the perception of agents and elements of conversation architecture are not well understood.
-Furthermore, there is no clear definition of the aspects of perception that are affected and the elements of conversation architecture.
+%Conversational agents employ natural language to interact with human users. While it is broadly accepted that the specifics of speech interactions affect the perception of communicating parties, 
+%Previous research has demonstrated a relationship between the structure of conversational agents' natural language interaction and how these agents are perceived by their users. However, 
+%there is a lack of systematic understanding of the connections between the perception of agents and elements of conversation architecture. % are not well understood. 
+%Furthermore, there is no clear definition of the aspects of perception that are affected and the elements of conversation architecture.
 In this paper, we present a synthesized framework demonstrating the connections between perceptions of agents and conversation architecture elements, using a taxonomy of eleven perceptions grouped into four categories, and ten elements grouped into three categories.
@@
 Also, there is the need to be consistent in the assessment of agents' perceptions, and consider ethical concerns in design.
+Conversational agents are deliberately designed to interact by simulating natural conversation, and the effectiveness of these interactions is shown to be affected by users' perceptions of an agent.
+While research on human-human and human-agent communication suggests the association between speech specifics and perceptions of communicating parties, there is a lack of systematic understanding of how an agent’s conversation architecture affects users' perceptions.
+To address this gap, we present a framework that outlines the relationships between elements of agents’ conversation architecture grouped around dialog strategy, content affectiveness, content style and speech format, and agent characteristics grouped around perceptions of interactions with an agent, agent's ability, sociability, and humanness.
+Synthesized based on literature review (n=57), the framework demonstrates both the identified relationships and the areas lacking empirical evidence.
+We discuss the implications of the framework for the conversation design and highlight the inconsistency issues with the domain terminology and measurements.
 \end{abstract}
@@
 
-Conversational agents (CAs) are designed to interact with humans using natural language through voice or text modalities.
-Adoption for CAs such as Alexa (Amazon) or Siri (Apple) are rapidly growing in the market, with half of Internet users in United States own one or more smart speaker devices \cite{2022comscore}.
+Conversational agents (CAs), such as Amazon Alexa or Siri, are designed to interact with humans using natural language through voice or text modalities.
+%Adoption of CAs such as Amazon Alexa or Siri (Apple) is rapidly growing in the market, with half of Internet users in United States owning one or more smart speaker devices \cite{2022comscore}.
 These conversational agents are designed to be ubiquitous, easily accessible through smartphones, tablets, laptops and smart devices.
@@
 %they solicit social responses from users, encouraging users to attribute lifelike qualities, a.k.a. anthropomorphized perceptions to CAs \cite{eyssel2012if}.
-
 %Anthropomorphism is defined as the attribution of traits that we typically associate with being distinctly human to nonhuman entities \cite{waytz2010sees}.
@@
 \cite{kuzminykh2020genie}.
-
-Previous research has show that there is a connection between conversation architecture and the perception of agents.
+Previous research has shown that there is a connection between conversation architecture and the perception of agents.
 Studies have found that conversational agents are perceived as more socially present and emotionally intelligent if they use affect language such as sentiment-adaptive response based on user's utterances, resulting in higher user satisfaction \cite{diederich2019emulating}\cite{yang2017perceived}.
@@
 
-For conversation architecture elements, Feine et al \cite{feine2019taxonomy} created a foundational knowledge by providing a taxonomy of social cues, which is defined as "a cue of a CA that triggers a social reaction of the user towards the CA." Elements of conversation architecture are captured in the taxonomy, alongside other social cues such as the embodied agents' appearance and movements.
+For conversation architecture elements, Feine et al \cite{feine2019taxonomy} created foundational knowledge by providing a taxonomy of social cues, which is defined as "a cue of a CA that triggers a social reaction of the user towards the CA." Elements of conversation architecture are captured in the taxonomy, alongside other social cues such as the embodied agents' appearance and movements.
 Clark et al \cite{clark2019state} had also captured conversation architecture elements under the research topic of system speech production, with similar categorizations across content, style, and other topics.
@@
 
-As shown in Table \ref{tab:cues}, there are three categories defined for the conversation architecture elements covering 10 different themes.
-The details of each category and theme are discussed below.
+As shown in Table \ref{tab:cues}, there are three categories defined for conversation architecture elements across ten different elements. The details of each category and element are discussed below.
 

### 2023-02-15 paper.tex
updated perception and architecture taxonomy based on AK feedback

@@
 %% of authors' names for this purpose.
-\renewcommand{\shortauthors}{Anon}
+\renewcommand{\shortauthors}{Wei, Kim, Kuzminykh} %It will be automatically anonymized through the document class property anonymous
 
@@
 \\ \Xhline{1.2pt}
-\multirow{3}{*}{\parbox{0.16\textwidth}{Perception of Interaction with Agent}}
-    & Usability & accuracy, ease of use, efficiency, helpfulness & 23 
+\multirow{3}{*}{\parbox{0.17\textwidth}{Perception of \newline Interaction with Agent}}
+    & Usability & accuracy, ease of use, \newline efficiency, helpfulness & 23 
     & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2022expressive}\cmt{[77]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cuadra2021my}\cmt{[67]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{elsholz2019exploring}\cmt{[61]}\cite{haas2022keep}\cmt{[78]}\cite{habler2019effects}\cmt{[63]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2019comparing}\cmt{[89]}\cite{kim2020can}\cmt{[24]}
@@
 \\ \cline{2-5}
-    & Engagement & enjoyment, annoyance, desirable, intention to use  & 28
+    & Engagement & enjoyment, annoyance, \newline desirable, intention to use  & 28
     & \cite{andrews2012system}\cmt{[38]}\cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cox2022does}\cmt{[27]}\cite{cuadra2021my}\cmt{[67]}\cite{elsholz2019exploring}\cmt{[61]}\cite{fadhil2018effect}\cmt{[52]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{go2021conversational}\cmt{[80]}\cite{healey2013relating}\cmt{[39]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2020can}\cmt{[24]}\cite{kim2019comparing}\cmt{[89]}
@@
 \\ \cline{2-5}
-    & Competence & competent, capable & 4 
-    & \cite{cox2022does}\cmt{[27]}\cite{kraus2020effects}\cmt{[64]}\cite{lee2019s}\cmt{[55]}\cite{westerman2019believe}\cmt{[9]}
+    & Competence & competent, appropriate & 6 
+    & \cite{cox2022does}\cmt{[27]}\cite{kraus2020effects}\cmt{[64]}\cite{jestin2022effects}\cmt{[81]}\cite{lee2019s}\cmt{[55]}\cite{misu2011toward}\cmt{[83]}\cite{westerman2019believe}\cmt{[9]}
 \\ \cline{2-5}
@@
 \\ \Xhline{1.2pt} 
-\multirow{3}{*}{\parbox{0.16\textwidth}{Perception of Social Connection with Agent}}
-    & Conversation Tone & appropriate, expressive, empathetic, persuasive & 13 
-    & \cite{chan2021kinvoices}\cmt{[74]}\cite{cox2022does}\cmt{[27]}\cite{cuadra2021my}\cmt{[67]}\cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{hu2021enhancing}\cmt{[56]}\cite{jestin2022effects}\cmt{[81]}\cite{misu2011toward}\cmt{[83]}\cite{tolmeijer2021female}\cmt{[62]}\cite{yang2021effect}\cmt{[72]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}
+\multirow{3}{*}{\parbox{0.16\textwidth}{Perception of \newline Sociability with Agent}}
+    & Conversation Tone & friendly, warm, empathetic, persuasive & 20 
+    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cox2022does}\cmt{[27]}\cite{cuadra2021my}\cmt{[67]}\cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{healey2013relating}\cmt{[39]}\cite{hu2021enhancing}\cmt{[56]}\cite{hu2022polite}\cmt{[76]}\cite{jestin2022effects}\cmt{[81]}\cite{khooshabeh2011does}\cmt{[37]}\cite{kim2019comparing}\cmt{[89]}\cite{lee2019s}\cmt{[55]}\cite{miehle2018exploring}\cmt{[51]}
+    \cite{moilanen2022measuring}\cmt{[82]}\cite{tolmeijer2021female}\cmt{[62]}\cite{yang2021effect}\cmt{[72]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}
 \\ \cline{2-5}
@@
 \multirow{2}{*}{\parbox{0.16\textwidth}{Perception of Agent's Humanness}}
-    & Human-likeness & human-like, natural, artificial, machine-like & 20
+    & Human-likeness & human-like, natural, \newline artificial, machine-like & 20
     & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cox2022does}\cmt{[27]}\cite{diederich2019emulating}\cmt{[25]}\cite{gnewuch2018faster}\cmt{[19]}\cite{haas2022keep}\cmt{[78]}\cite{hu2022polite}\cmt{[76]}\cite{jeong2019exploring}\cmt{[10]}\cite{jestin2022effects}\cmt{[81]}\cite{lubis2019positive}\cmt{[43]}\cite{ma2022ask}\cmt{[29]}\cite{misu2011toward}\cmt{[83]}\cite{niewiadomski2013laugh}\cmt{[85]}
@@
 \\ \cline{2-5}
-    & Personality Traits & friendly, kind, warm, creepy, likeable, polite & 27
-    & \cite{andrews2012system}\cmt{[38]}\cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cox2022does}\cmt{[27]}\cite{cuadra2021my}\cmt{[67]}\cite{haas2022keep}\cmt{[78]}\cite{habler2019effects}\cmt{[63]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{huiyang2022improving}\cmt{[17]}\cite{jeong2019exploring}\cmt{[10]}\cite{jestin2022effects}\cmt{[81]}\cite{khooshabeh2011does}\cmt{[37]}
-    \cite{kim2019comparing}\cmt{[89]}\cite{lee2019s}\cmt{[55]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{miehle2018exploring}\cmt{[51]}\cite{moilanen2022measuring}\cmt{[82]}\cite{ouchi2019should}\cmt{[59]}\cite{tolmeijer2021female}\cmt{[62]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}\cite{wester2015artificial}\cmt{[14]}\cite{zhu2022effects}\cmt{[26]}
+    & Personality Traits & likeable, kind, witty, funny, creepy & 20
+    & \cite{andrews2012system}\cmt{[38]}\cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cuadra2021my}\cmt{[67]}\cite{haas2022keep}\cmt{[78]}\cite{habler2019effects}\cmt{[63]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{huiyang2022improving}\cmt{[17]}\cite{jeong2019exploring}\cmt{[10]}\cite{kim2019comparing}\cmt{[89]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{miehle2018exploring}\cmt{[51]}
+    \cite{ouchi2019should}\cmt{[59]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}\cite{wester2015artificial}\cmt{[14]}\cite{zhu2022effects}\cmt{[26]} 
 \\ \Xhline{1.2pt}
@@
 \Xhline{1.2pt}
-\textbf{Element Category} & \textbf{Element} & \textbf{Examples} & \textbf{No. Papers} & \textbf{Papers}
+\multicolumn{2}{l|}{\textbf{Conversation Architecture Elements}} & \textbf{Examples} & \textbf{No. Papers} & \textbf{Papers}
 \\ \Xhline{1.2pt}
-\multirow{4}{*}{Linguistic Content}    & Affective Language & emotional expressions, sentiment-adaptive responses & 11
+\multirow{3}{*}{Dialog Strategy} & Social Dialog & social talk, self-disclosure  & 7
+& \cite{andrews2012system}\cmt{[38]}\cite{lee2020hear}\cmt{[23]}\cite{lubold2016effects}\cmt{[86]}\cite{moilanen2022measuring}\cmt{[82]}\cite{roy2021users}\cmt{[71]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}
+\\ \cline{2-5}
+
+& Initiative & proactive dialogue, conversation \newline repair & 4
+& \cite{ashktorab2019resilient}\cmt{[88]}\cite{cuadra2021my}\cmt{[67]}\cite{kraus2020effects}\cmt{[64]}\cite{xiao2021let}\cmt{[73]}
+\\ \cline{2-5}
+
+& Response Delay & response delay, typing indicator & 4
+& \cite{gnewuch2018faster}\cmt{[19]}\cite{gnewuch2018chatbot}\cmt{[21]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{seeger2021chatbots}\cmt{[35]}
+\\ \Xhline{1.2pt}
+
+\multirow{2}{*}{Content Affectiveness} & Affective Language & emotional expressions, sentiment-adaptive responses & 11
 & \cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{lee2019s}\cmt{[55]}\cite{lubis2019positive}\cmt{[43]}\cite{moilanen2022measuring}\cmt{[82]}\cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2022user}\cmt{[75]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}
 \\ \cline{2-5}
-& Social Talk & self-disclosure, social dialogue & 7
-& \cite{andrews2012system}\cmt{[38]}\cite{lee2020hear}\cmt{[23]}\cite{lubold2016effects}\cmt{[86]}\cite{moilanen2022measuring}\cmt{[82]}\cite{roy2021users}\cmt{[71]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}
-\\ \cline{2-5}
+
 & Humour & humorous content, jokes & 5
 & \cite{ceha2021can}\cmt{[57]}\cite{go2021conversational}\cmt{[80]}\cite{khooshabeh2011does}\cmt{[37]}\cite{miyamoto2017improving}\cmt{[46]}\cite{volkel2021manipulating}\cmt{[68]}
-\\ \cline{2-5}
-& Agent-Initiated Content & proactive dialogue, conversation repair & 4
-& \cite{ashktorab2019resilient}\cmt{[88]}\cite{cuadra2021my}\cmt{[67]}\cite{kraus2020effects}\cmt{[64]}\cite{xiao2021let}\cmt{[73]}
 \\ \Xhline{1.2pt}
-\multirow{4}{*}{Linguistic Style} & Formality & formal vs. casual, honorific expressions & 9
+
+\multirow{3}{*}{Content Style} & Formality & formal vs. casual, honorific \newline expressions & 9
 & \cite{cox2022does}\cmt{[27]}\cite{elsholz2019exploring}\cmt{[61]}\cite{habler2019effects}\cmt{[63]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2019comparing}\cmt{[89]}\cite{ma2022ask}\cmt{[29]}\cite{moilanen2022measuring}\cmt{[82]}\cite{ouchi2019should}\cmt{[59]}\cite{volkel2022user}\cmt{[75]}
 \\ \cline{2-5}
-& Alignment & content matching, lexical alignment, agreeableness & 7
+
+& Alignment & content matching, lexical \newline alignment, agreeableness & 7
 & \cite{healey2013relating}\cmt{[39]}\cite{hoegen2019end}\cmt{[31]}\cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}\cite{spillner2021talk}\cmt{[18]}\cite{volkel2021examining}\cmt{[69]}\cite{volkel2021manipulating}\cmt{[68]}
 \\ \cline{2-5}
-& Elaborateness & elaborate, concise, sentence structure & 6
+
+& Elaborateness & elaborate, concise, sentence \newline structure & 6
 & \cite{haas2022keep}\cmt{[78]}\cite{miehle2018exploring}\cmt{[51]}\cite{moilanen2022measuring}\cmt{[82]}\cite{roy2021users}\cmt{[71]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}
-\\ \cline{2-5}
-& Disfluency & fillers, interjections, repetitions & 6
-& \cite{ceha2022expressive}\cmt{[77]}\cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}\cite{niewiadomski2013laugh}\cmt{[85]}\cite{wester2015artificial}\cmt{[14]}\cite{yang2021effect}\cmt{[72]}
 \\ \Xhline{1.2pt}
-\multirow{2}{*}{Non-Linguistic Format} & Prosodic Cue & pitch, intonation, speech rate, spoken accent & 12
+
+\multirow{3}{*}{Speech Format} & Prosody & pitch, intonation, speech rate, \newline spoken accent & 12
 & \cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{feijoo2021effects}\cmt{[70]}\cite{habler2019effects}\cmt{[63]}\cite{hu2021enhancing}\cmt{[56]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2020can}\cmt{[24]}\cite{lubold2016effects}\cmt{[86]}\cite{misu2011toward}\cmt{[83]}\cite{tolmeijer2021female}\cmt{[62]}\cite{zhu2022effects}\cmt{[26]}
 \\ \cline{2-5}
-& Text Variation & typo, capitalization, emoticons, response delay & 9
-& \cite{fadhil2018effect}\cmt{[52]}\cite{gnewuch2018faster}\cmt{[19]}\cite{gnewuch2018chatbot}\cmt{[21]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{kim2019comparing}\cmt{[89]}\cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2022user}\cmt{[75]}\cite{westerman2019believe}\cmt{[9]}\cite{wilhelm2022keep}\cmt{[28]}
+
+& Disfluency & fillers, interjections, repetitions, \newline typos & 7
+& \cite{ceha2022expressive}\cmt{[77]}\cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}\cite{niewiadomski2013laugh}\cmt{[85]}\cite{wester2015artificial}\cmt{[14]}\cite{westerman2019believe}\cmt{[9]}\cite{yang2021effect}\cmt{[72]}
+\\ \cline{2-5}
+
+& Text Formatting & capitalization, emoticons & 6
+& \cite{fadhil2018effect}\cmt{[52]}\cite{kim2019comparing}\cmt{[89]}\cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2022user}\cmt{[75]}\cite{westerman2019believe}\cmt{[9]}\cite{wilhelm2022keep}\cmt{[28]}
 \\ \Xhline{1.2pt}

### 2023-02-16 paper.tex
second pass up to 3.3.2

@@
 Also, there is the need to be consistent in the assessment of agents' perceptions, and consider ethical concerns in design.
-Conversational agents are deliberately designed to interact by simulating natural conversation, and the effectiveness of these interactions is shown to be affected by users' perceptions of an agent.
+%[AK Edit] Conversational agents are deliberately designed to interact by simulating natural conversation, and the effectiveness of these interactions is shown to be affected by users' perceptions of an agent.
 While research on human-human and human-agent communication suggests the association between speech specifics and perceptions of communicating parties, there is a lack of systematic understanding of how an agent’s conversation architecture affects users' perceptions.
@@
 We discuss the implications of the framework for the conversation design and highlight the inconsistency issues with the domain terminology and measurements.
+Conversational agents mimic natural conversation to interact with users.
+Since the effectiveness of interactions strongly depends on users’ perception of agents, it is crucial to design agents’ behaviors to provide the intended user perceptions.
+Research on human-agent and human-human communication suggests that speech specifics are associated with perceptions of communicating parties, but there is a lack of systematic understanding of how speech specifics of agents affect users' perceptions.
+To address this gap, we present a framework outlining the relationships between elements of agents’ conversation architecture (dialog strategy, content affectiveness, content style and speech format) and aspects of users’ perception (interaction, ability, sociability and humanness).
+Synthesized based on literature reviewed from the domains of HCI, NLP and linguistics (n=57), this framework demonstrates both the identified relationships and the areas lacking empirical evidence.
+We discuss the implications of the framework for conversation design and highlight the inconsistencies with terminology and measurements.
 \end{abstract}
@@
 %%
-\begin{CCSXML}
-<ccs2012>
- <concept>
-  <concept_id>10010520.10010553.10010562</concept_id>
-  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
-  <concept_significance>500</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010575.10010755</concept_id>
-  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-  <concept_significance>300</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010553.10010554</concept_id>
-  <concept_desc>Computer systems organization~Robotics</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>10003033.10003083.10003095</concept_id>
-  <concept_desc>Networks~Network reliability</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
-</ccs2012>
-\end{CCSXML}
+%\begin{CCSXML}
+%<ccs2012>
+% <concept>
+%  <concept_id>10010520.10010553.10010562</concept_id>
+%  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
+%  <concept_significance>500</concept_significance>
+% </concept>
+% <concept>
+%  <concept_id>10010520.10010575.10010755</concept_id>
+%  <concept_desc>Computer systems organization~Redundancy</concept_desc>
+%  <concept_significance>300</concept_significance>
+% </concept>
+% <concept>
+%  <concept_id>10010520.10010553.10010554</concept_id>
+%  <concept_desc>Computer systems organization~Robotics</concept_desc>
+%  <concept_significance>100</concept_significance>
+% </concept>
+% <concept>
+%  <concept_id>10003033.10003083.10003095</concept_id>
+%  <concept_desc>Networks~Network reliability</concept_desc>
+%  <concept_significance>100</concept_significance>
+% </concept>
+%</ccs2012>
+%\end{CCSXML}
 
-\ccsdesc[500]{Computer systems organization~Embedded systems}
-\ccsdesc[300]{Computer systems organization~Redundancy}
-\ccsdesc{Computer systems organization~Robotics}
-\ccsdesc[100]{Networks~Network reliability}
+%\ccsdesc[500]{Computer systems organization~Embedded systems}
+%\ccsdesc[300]{Computer systems organization~Redundancy}
+%\ccsdesc{Computer systems organization~Robotics}
+%\ccsdesc[100]{Networks~Network reliability}
+
+\ccsdesc{TBD}
 
@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{conversational agents, user perception, conversational architecture, anthropomorphized perceptions, social cues}
+\keywords{conversational agents, user perception, conversational architecture, anthropomorphized perceptions}
 
@@
 %TC:endignore
-
-%%%% TODO %%%%
-% Add headmap of explored relationships - side by side with the connections - show numbers - DONE
-% Put the heatmap of impact earlier in the paper - DONE
-% Put the tables together - DONE
-% show what is explored vs. the connections that had impacts. - DONE
-% User perception of agent instead of anthropomorphized perceptions
-% Refer to the explored connection in writing, and connections with impacts
-% Update to use perception aspects and categories (instead of themes and organizing themes)
-% Update introduction
-% Include focus areas for future reasearch
-% Reviewed recording up to 17:31
-% Question about single column vs. double column format - ask Jaisie
 
@@
 We used inductive thematic analysis to group these assessments into codes based on their meanings.
-For example, the code likeability of the agent contains assessments such as the questionnaire item "this voice agent was likeable" used by \cite{cuadra2021my}\cmt{[67]}, Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed}'s set of questions on likeability used by \cite{linnemann2018can}\cmt{[15]}, and Subjective Assessment of Speech System Interface (SASSI) questionnaire \cite{hone2000towards}\cmt{sassi}'s set of questions on likeability used by \cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}.
+For example, the code likeability of the agent contains the questionnaire item "this voice agent was likeable" used by \cite{cuadra2021my}\cmt{[67]}, Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed}'s set of questions on likeability used by \cite{linnemann2018can}\cmt{[15]}, and Subjective Assessment of Speech System Interface (SASSI) questionnaire \cite{hone2000towards}\cmt{sassi}'s set of questions on likeability used by \cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}.
 This step resulted in 83 unique codes.
 These codes are then organized based similarity of the meanings, resulting in 11 aspects of perceptions.
-For example, the aspect of \textit{personality traits} of the agent contains measurements such as likeability, friendliness, and warmth.
-Lastly, the 11 aspects are grouped into 4 categories: \textit{perception of interaction with agent, perception of agent's ability, perception of social connection with agent, and perception of agent's humanness} (Table \ref{tab:perceptions}).
+For example, the aspect of personality traits of the agent contains measurements such as likeability, funniness, and kindness.
+Lastly, the 11 aspects are grouped into 4 categories: perception of interaction with agent, perception of agent's ability, perception of sociability with agent, and perception of agent's humanness (Table \ref{tab:perceptions}).
 
 \subsubsection*{Conversation Architecture Elements}
-As to the elements of conversation architecture that are relevant to the perception of agents (RQ2), we extracted the conversation architecture used in each paper as codes.
+As to the elements of conversation architecture that are relevant to the perception of agents (RQ2), we extracted the specifics of conversation architecture used in each paper.
 Some of the papers used multiple features in their CA design, such as the the anthropomorphic agent used in Seeger et al's study \cite{seeger2021chatbots}\cmt{[35]}.
@@
 58 unique codes were created as part of this process, capturing features like sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}, lexical alignment \cite{spillner2021talk}\cmt{[18]}, and typos \cite{westerman2019believe}\cmt{[9]}.
-We then organized these codes into elements based on similarity.
-For example, the element of \textit{disfluency} contains fillers \cite{jeong2019exploring}\cmt{[10]}\cite{wester2015artificial}\cmt{[14]}, interjections \cite{ceha2022expressive}\cmt{[77]}\cite{hu2021enhancing}\cmt{[56]}, and repetitions \cite{yang2021effect}\cmt{[72]}.
-Lastly, these elements are grouped into categories adapted from the social cues taxonomy structure by Feine et al \cite{feine2019taxonomy}.
-Based on this paper, the Verbal-Content category is mapped to our category of \textit{linguistic content}, and the Verbal-Style category is mapped to our category of \textit{linguistic style}.
-Given our analysis focuses on the conversational aspects of a CA, the social cues' categories related to embodiment aspects were not used.
-Also, we collapsed the auditory and invisible categories into our category of \textit{non-linguistic format} (Table \ref{tab:cues}).
+We then organized these codes into elements based on similarity, resulting in 12 elements of conversation architecture.
+For example, the element of disfluency contains fillers \cite{jeong2019exploring}\cmt{[10]}\cite{wester2015artificial}\cmt{[14]}, interjections \cite{ceha2022expressive}\cmt{[77]}\cite{hu2021enhancing}\cmt{[56]}, repetitions \cite{yang2021effect}\cmt{[72]} and typos \cite{westerman2019believe}\cmt{[9]}.
+These elements are grouped into 4 categories: dialog strategy, content affectiveness, content style, and speech format (Table \ref{tab:cues}).
 
 \subsubsection*{Relationship Between Perceptions of Agents and Conversation Architecture}
-To study the relationship between conversation architecture and conversation architecture, we extracted the connections explored in each paper, using the perception aspects and conversation architecture elements developed in the previous data analysis steps.
-Each connection's effect was also recorded based on whether an impact was found in the study and the nature of that impact.
-Out of our review corpus, 265 explored connections between perceptions of agents and conversation architecture were found.
-To analyze specifically the relationships between the specifics of conversation architecture that affect the perceptions of CAs, 72 connections that did not result in significant relationships were discarded, resulting in 193 relationships for analysis.
-For example, the connection between the matching style of a CA and user satisfaction was discarded because Hoegen et al.
+To study the effect of conversation architecture on users' perceptions (RQ3), we extracted the connections explored in each paper, using the perception aspects and conversation architecture elements developed in the previous data analysis steps.
+Each connection's effect was also recorded based on whether an association was found in the study and the nature of that association.
+Out of our review corpus, 265 connections between perceptions of agents and conversation architecture were explored in literature.
+To analyze the specifics of conversation architecture that affect the perceptions of CAs, 72 connections that did not result in observed relationships were discarded, resulting in 193 relationships for analysis.
+For example, the connection between the matching style of a CA and user satisfaction was removed because Hoegen et al.
 \cite{hoegen2019end}\cmt{[31]} did not find a significant difference between the style matching agent and the non-style matching agent for overall interaction satisfaction.
-Out of the 193 relationships, 10 were relationships using agents using multiple architecture elements.
-They were not included in the framework as it is not possible attribute the perceptions of agents to its underlying elements.
+Out of the 193 relationships, 10 were relationships based on agents using multiple architecture elements (e.g.
+\cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2021manipulating}\cmt{[68]}).
+They were not included in the final framework as we could not attribute the perceptions of agents to the underlying core elements.
 Overall, 183 relationships between individual architecture elements and perceptions of agents are incorporated into our synthesized framework, visualized as a heatmap to demonstrate their relationships with each other (Figure \ref{fig:heatmap-impact}).
-
-%183 were relationships between individual architecture elements and perceptions. These single architecture element are included in our synthesized frame, 
-%CAs using multiple conversation architecture elements were discarded because perceptions are measured at the aggregate level, we cannot attribute the perceptions of agents down to its underlying elements.
-%Perceptions impacted by the composite of multiple architecture elements in an agent will be discussed in more details in the Composite Architecture Elements section.
 
@@
 
-\subsection{Anthropomorphized Perceptions}
+\subsection{Perceptions of Agents}
 
-As shown in Table \ref{tab:perceptions}, there are four categories defined for the perceptions of conversational agents covering 11 aspects of perception.
-The details of each aspect are discussed below.
+As shown in Table \ref{tab:perceptions}, there are four categories defined for the perceptions of conversational agents covering 11 different aspects of perception.
+The details of each category and aspect are discussed below.
 
@@
 The three aspects for this perceptions are usability, engagement and satisfaction.
-\textit{Usability} captures the utilitarian aspects of the interaction, whether it was accurate, easy to use, efficient or helpful.
-Some commonly used methods to measure usability include the response accuracy portion of the SASSI questionnaire \cite{hone2000towards}\cmt{sassi}, or the NASA Task Load Index (NASA-TLX) \cite{hart1988development}\cmt{nasa} to measure cognitive workload.
+\textit{Usability} captures the utilitarian component of the interaction, whether it was accurate, easy to use, efficient or helpful.
+Some commonly used methods to evaluate usability include the response accuracy portion of the SASSI questionnaire \cite{hone2000towards}\cmt{sassi}, or the NASA Task Load Index (NASA-TLX) \cite{hart1988development}\cmt{nasa} for cognitive workload.
 Questions such as "the system is easy to use" or "it is easy to understand the agent" are also used to evaluate usability.
 \textit{Engagement} on the other hand captures users' emotional reactions to the CA, whether they have enjoyed the conversation, or annoyed or frustrated with the interaction.
-Some commonly used methods to measure engagement include the annoyance portion of the SASSI questionnaire \cite{hone2000towards}\cmt{sassi}, and the Use Engagement Scale (UES) \cite{o2018practical}\cmt{ues}.
+Some commonly used methods to evaluate engagement include the annoyance portion of the SASSI questionnaire \cite{hone2000towards}\cmt{sassi}, and the Use Engagement Scale (UES) \cite{o2018practical}\cmt{ues}.
 Questions such as "I enjoyed using the system" or "I felt frustrated with the agent" are also used to evaluate engagement.
@@
 \textbf{Perception of agent's ability} assesses the perceived capabilities of the agent.
-While there are some elements of system performance in this category, we are mainly concerned with how agents with varied architecture elements but equivalent system capabilities are perceived differently.
+Unlike system capabilities that affect agent's performance, the perceived ability category captures perceptions of agents with equivalent system capabilities but varied conversation architecture elements.
 Specifically, \textit{intelligence} captures the agent's expertise and knowledge, and it is commonly administered through the Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed} using the set of questions related to perceived intelligence.
@@
 Surveys or qualitative feedback are usually used to assess if the agent is capable and competent, and whether users have confidence in the agent's ability to get the job done.
-Lastly, \textit{trust} captures agent's truthfulness, credibility and benevolence.
+Lastly, \textit{credibility} captures agent's truthfulness, benevolence, and user's confidence in CAs.
 Some commonly used methods to evaluate trust include the Trust Propensity Scale \cite{mayer1999effect} and the Individualized Trust Scale (ITS) \cite{wheeless1977measurement}.
@@
 
-\textbf{Perception of the social connection with agent} assesses the emotional connections that users have with agents.
+\textbf{Perception of the sociability with agent} assesses the emotional connections that users have with agents.
 This category includes perception aspects of conversation tone, social presence and intimacy.
 \textit{Conversation tone} captures the affective impression of the agent's tone, such as empathy and expressiveness.
-Also, this aspect includes whether the tone used by the agent is persuasive or appropriate for the conversation.
+Also, this aspect includes whether the tone used by the agent was perceived as friendly, polite or warm.
 \textit{Social presence} captures the sense of connectness and psychological distance users have with an agent.
@@
 Survey questions with semantic scales such as "human-like / machine-like" and "artificial / natural" are also commonly used for this aspect of perception.
-\textit{Personality traits} captures the human characteristics that are attributes to the agent, such as warm, friendly, likeable, and polite.
-This is commonly collected as qualitative feedback from users, commenting on whether the agent is extroverted or introverted, or the human characteristics they perceive the agent such as funny or witty.
+\textit{Personality traits} captures the human characteristics that are attributes to the agent.
+This is commonly collected as qualitative feedback from users, commenting on whether the agent is extroverted or introverted, or the perceived personality such as likeable, funny or witty.
 Sometimes the Big-5 personality traits questionnaire \cite{gosling2003very} is used to map an agent's disposition on various personality dimensions.
@@
 
-%CW - second pass up to here
-
-\subsection{Conversation Architecture Elements}
-
-As shown in Table \ref{tab:cues}, there are three categories defined for conversation architecture elements across ten different elements. The details of each category and element are discussed below.
-
-The category of \textbf{linguistic content} maps to the content category under verbal cues in Feine et al's taxonomy, which refers to elements expressed with written or spoken words that are related to the strict and literal meaning of a message (i.e.
-what is said) \cite{feine2019taxonomy}.
-The theme of \textit{affective language} captures the injection of emotional words or phrases into the agent's utterance, such as affective expressions \cite{seeger2021chatbots}\cmt{[35]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}, sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}, and encouraging words \cite{healey2013relating}\cmt{[39]}.
-\textit{Social talk} captures non-task related conversations with the user to build social connection, such as self-disclosure \cite{lee2020hear}\cmt{[23]} and social dialogue \cite{volkel2021manipulating}\cmt{[68]}\cite{lubold2016effects}\cmt{[86]}.
-The theme of \textit{humour} is similar to social talk but specific to CA's attempt to include jokes in its utterances.
-The separation of social talk and humor is based on findings from previous research, where user's attitude towards humour is different between human-human conversations vs.
-human-agent conversations \cite{clark2019makes}.
-We would like to capture the relationship between humour and agent perceptions differently from social talk.
-Lastly, the theme of \textit{agent-initiated content} captures utterances that are driven by the agent without direct prompts from the user.
-This elements in this theme include conversation repairs \cite{cuadra2021my}\cmt{[67]}\cite{ashktorab2019resilient}\cmt{[88]} and proactive content like eliciting feedback \cite{xiao2021let}\cmt{[73]}.
-
-The category of \textbf{linguistic style} maps to the style category under verbal cues in Feine et al's taxonomy, which refers to elements expressed with written or spoken words that are related to the meaningful deployment of language variation in a message (i.e.
-how something is said) \cite{feine2019taxonomy}.
-The theme of \textit{formality} describes the language style used by the conversational agent, whether it is formal vs.
-casual, such as using honorific expressions to address users \cite{ouchi2019should}\cmt{[59]}.
-\textit{Alignment} captures the degree that the agent aligns its utterances to the users, such as lexical alignment on the content and structural of the sentences \cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}, as well as agreement with the user \cite{volkel2021examining}\cmt{[69]}.
-\textit{Elaborateness} captures the sentence complexity and length of the utterances.
-For example, Roy et al.
-explored the differences in perception for variations in elaborateness such as "Cloudly, possibility of snow, high: 4, low: -10" vs "Today will be cloudy, with a high of 4 and a low of -10.
-Snow is predicted" \cite{roy2021users}\cmt{[71]}.
-Lastly, the category of \textit{disfluency} captures the style of using non-lexical utterances like filler words ("um, uh") \cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}, or repetition of words within a sentence \cite{yang2021effect}\cmt{[72]}.
-
-Lastly, the category of \textbf{non-linguistic format} maps loosely to the elements in auditory and invisible categories in Feine et al's taxonomy \cite{feine2019taxonomy}.
-These are auditory or textual variations in the presentation of the agent's utterances.
-In the theme of \textit{prosodic cue}, it captures vocal qualities like gender of voice \cite{habler2019effects}\cmt{[63]}\cite{jestin2022effects}\cmt{[81]}, and speech rate \cite{choi2020nobody}\cmt{[54]}.
-\textit{Text variations} include different formats that text-based agents use to present information to users, like emoticons \cite{kim2019comparing}\cmt{[89]}\cite{wilhelm2022keep}\cmt{[28]}, typos \cite{westerman2019believe}\cmt{[9]}, and response delays \cite{gnewuch2022opposing}\cmt{[20]}\cite{seeger2021chatbots}\cmt{[35]}.
-
-Overall the spread of conversation architecture elements relevant to anthropomorphized perceptions are evenly distributed across linguistic content, linguistic style, and non-linguistic format.
-Looking at the different themes, there is good coverage of studies on the impact of affective language and prosodic cues on anthropomorphized perceptions.
-However, it seemed like there is a lack of studies exploring the effect of agent-initiative content on the perception of agents.
-There are various existing literature on this theme such as conversation repairs \cite{komatani2010online}\cite{reinkemeier2022repair} and agent proactively sharing content with users \cite{dubiel2019inquisitive}\cite{zargham2022understanding}, but they were not included in this systematic literature review because they did not have measures of anthropomorphized perceptions of the CA.
-This may be because conversations with CAs have historically being driven by the user, with some recent effort to understand the opportunities to be more proactive \cite{cowan2023introduction}, as existing research are focused on the functional aspects of designing an agent instead of exploring into the anthropomorphized perceptions.
-
 \begin{table*}[h]
@@
 
-& Humour & humorous content, jokes & 5
-& \cite{ceha2021can}\cmt{[57]}\cite{go2021conversational}\cmt{[80]}\cite{khooshabeh2011does}\cmt{[37]}\cite{miyamoto2017improving}\cmt{[46]}\cite{volkel2021manipulating}\cmt{[68]}
+& Humour & humorous content, jokes & 6
+& \cite{ceha2021can}\cmt{[57]}\cite{go2021conversational}\cmt{[80]}\cite{khooshabeh2011does}\cmt{[37]}\cite{miyamoto2017improving}\cmt{[46]}\cite{niewiadomski2013laugh}\cmt{[85]}\cite{volkel2021manipulating}\cmt{[68]}
 \\ \Xhline{1.2pt}
@@
 
-& Disfluency & fillers, interjections, repetitions, \newline typos & 7
-& \cite{ceha2022expressive}\cmt{[77]}\cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}\cite{niewiadomski2013laugh}\cmt{[85]}\cite{wester2015artificial}\cmt{[14]}\cite{westerman2019believe}\cmt{[9]}\cite{yang2021effect}\cmt{[72]}
+& Disfluency & fillers, interjections, repetitions, \newline typos & 6
+& \cite{ceha2022expressive}\cmt{[77]}\cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}\cite{wester2015artificial}\cmt{[14]}\cite{westerman2019believe}\cmt{[9]}\cite{yang2021effect}\cmt{[72]}
 \\ \cline{2-5}
@@
 
+\subsection{Conversation Architecture Elements}
+
+As shown in Table \ref{tab:cues}, there are four categories defined for conversation architecture across 12 different elements. The details of each category and element are discussed below.
+
+The category of \textbf{dialog strategy} refers to the approach used by a conversational agent to engage in a dialogue with a user, which includes the use of social dialogs, agent-initiated content, and adding delays to responses.
+Specifically, the element of \textit{social dialogue} captures non-task related conversations with the user to build social connection, such as self-disclosure \cite{lee2020hear}\cmt{[23]} and small talk like chitchats \cite{lubold2016effects}\cmt{[86]}\cite{volkel2021manipulating}\cmt{[68]}.
+The element of \textit{initiative} captures utterances that are initiated by the agent without direct prompts from the user.
+For example, the agent is taking the initiative to proactively repair the conversation with a user \cite{ashktorab2019resilient}\cmt{[88]}\cite{cuadra2021my}\cmt{[67]}, or actively elicit feedback from users \cite{xiao2021let}\cmt{[73]}.
+Lastly, \textit{response delay} refers to the tactic of deliberatively delaying for a certain period of time before an agent responds to users \cite{gnewuch2018faster}\cmt{[19]}\cite{gnewuch2022opposing}\cmt{[20]}.
+It is mainly used in text-based CAs alongside visual displays of typing indicators \cite{gnewuch2018chatbot}\cmt{[21]}.
+
+\textbf{Content affectiveness} refers to the conversational agent's use of language to convey emotions or to elicit emotions from users.
+The architecture element of \textit{affective language} captures the injection of emotional words or phrases into the agent's utterance, such as affective expressions \cite{seeger2021chatbots}\cmt{[35]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}, sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}, and encouraging words \cite{healey2013relating}\cmt{[39]}.
+The other element in this category, \textit{humour}, captures an agent's attempt to include jokes in its dialog.
+Several studies in our reviewed corpus have explored the effect of humour on various perceptions of agents (e.g.
+\cite{ceha2021can}\cmt{[57]}\cite{khooshabeh2011does}\cmt{[37]}).
+
+The category of \textbf{content style} refers to the variations of language used in a message aside from the content meaning of the message (i.e.
+how something is said).
+The element of \textit{formality} describes the linguistic style used by the conversational agent, whether it is formal vs.
+casual, such as using honorific expressions to address users \cite{ouchi2019should}\cmt{[59]}.
+\textit{Alignment} captures the degree that the agent aligns its utterances to the users, such as lexical alignment on the content and structural of the sentences \cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}, as well as referring and agreeing with users' utterances \cite{volkel2021examining}\cmt{[69]}.
+Lastly, the element of \textit{elaborateness} captures the sentence complexity and length of agents' utterances.
+For example, Roy et al.
+explored the differences in perception for variations in elaborateness such as "Cloudly, possibility of snow, high: 4, low: -10" vs "Today will be cloudy, with a high of 4 and a low of -10.
+Snow is predicted" \cite{roy2021users}\cmt{[71]}.
+
+Lastly, the category of \textbf{speech format} captures the non-verbal component of a conversational agent's utterances for both text and voice modalities. \textit{Disfluency} captures 
+the use of non-lexical utterances like filler words ("um, uh") \cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}, or repetition of words within a sentence \cite{yang2021effect}\cmt{[72]}.
+It also includes the format of using typos \cite{westerman2019believe}\cmt{[9]} for text-based agents.
+For voice-based agents specifically, the element of \textit{prosody} encompasses vocal qualities like pitch \cite{habler2019effects}\cmt{[63]}\cite{jestin2022effects}\cmt{[81]}, speech rate \cite{choi2020nobody}\cmt{[54]}, and spoken accent \cite{feijoo2021effects}\cmt{[70]}.
+For text-based CAs, the \textit{text formatting} element includes different formats agents uses to present information to users, such as using capitalization \cite{westerman2019believe}\cmt{[9]} or emoticons \cite{kim2019comparing}\cmt{[89]}\cite{wilhelm2022keep}\cmt{[28]}.
+
+Overall there are similar number of conversation architecture elements explored across the four categories of dialog strategy, content affectiveness, content style, and speech format.
+As for explorations related to different modalities of agents, there is a noticeable difference in the category of speech format, where architecture elements related to voice-based agents (n=15) are explored more than text-based agents (n=7).
+Looking across the 12 different elements, there is good coverage of studies on the impact of affective language and prosody cues on the perceptions of agents.
+However, there are less studies exploring the effect of agent initiated content and response delay on the perception of agents.
+Specifically for the element of initiative under dialog strategy category, there is literature on conversation repairs \cite{komatani2010online}\cite{reinkemeier2022repair} and agent proactively sharing content with users \cite{dubiel2019inquisitive}\cite{zargham2022understanding}, but many of them did not not include assessments of perceptions of the CA.
+This may be due to the fact that the usage of agent-initiated content is relatively new, as CA interactions have historically been driven by users.
+As such, current research is focused on the functional aspects of agents initiating contents instead of exploring the perceptions of agents.
+As for response delay, there are indications that this element is under-explored in literature.
+Only 4 studies in our reviewed corpus used an agent with response delay, and the majority of these publications were written by the same authors.
+
 \subsection{Relationship Between Perceptions of Agents and Conversation Architecture}
 
-We extracted 265 connections between anthropomorphized perceptions and conversation architecture elements from our reviewed corpus.
-Out of these connections, 193 of them had an impacted relationship between the conversational architecture elements and anthropomorphized perceptions.
-Most of these relationships (n=183) were exploring the effect of a single conversation architecture element on perceptions of agents (e.g.
-\cite{miehle2018exploring}\cmt{[51]}\cite{westerman2019believe}\cmt{[9]}), while a few of them (n=10) used a composite of architecture elements in the study (e.g.
-\cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2021manipulating}\cmt{[68]}).
-The 183 single element relationships are visualized into a heatmap (Figure \ref{fig:heatmap-impact}) to based on the number of impacts conversational architecture elements had on the anthropomorphized perceptions.
-These relationships are discussed in details in the following sections for each perception category.
+There are 183 identified relationships between perceptions of agents and conversation architecture out of the 265 explored connections that are included in our synthesized framework (Figure \ref{fig:heatmap-impact}).
+To compare the number of identified relationships vs.
+the explored connections in literature, Figure \ref{fig:heatmap-coverage} shows a side-by-side comparison between the two.
+The detailed analysis on the differences between explored and identified relationships are discussed in the subsections below.
 
-%\subsubsection{Overall Characteristics}
-
-%While the number of papers studying voice (n=27) vs.
-text (n=30) modalities is not significantly different, there are some interesting trends in the perceptions studied for CAs with different modalities.
-Overall, there are less perceptions of agent studied for text-based agents (n=101) as compared to voice-based agents (n=163).
-
-%This is especially evident in the perception of social connection with agent and perception of agent's humanness.
-For the perception of social connection with a CA, there are only 19 perceptions measured for text-based agents, while there are 35 perceptions measured for voice-based agents.
-Similarly for perception of agent's humanness, there are 36 perceptions measured for text-based agents, as compared to 52 perceptions of voice-based agents.
-This highlights that there is a ..
-
-\subsubsection{Perception of Interaction with Agent}
-
-The effects of conversation architecture elements on the perception of interaction with agent is the most explored connections in the corpus (n=100).
-Out of these explored connections, the majority of them (n=69) discovered an impact between the studied architecture element and the perception.
-For the impacted relationships, the corpus had similar numbers of connections across voice-based (n=34) and text-based (n=35) CAs.
-
-Across the themes in this perception category, both \textbf{usability} and \textbf{engagement} perceptions were measured frequently in our corpus, with conversation architecture elements having effects on these measures across linguistic content, linguistic style and non-linguistic format categories.
-\textbf{Satisfaction} measures were used in some studies but it is not evaluated as often as engagement or usability.
-Several papers that measured satisfactions were conversation agents within the transaction context, especially within the customer service domain (e.g.
-\cite{diederich2019emulating}\cmt{[25]}\cite{elsholz2019exploring}\cmt{[61]}\cite{gnewuch2018faster}\cmt{[19]}).
-For the relationships across conversation architecture element categories, linguistic style has the higher number of relationships with perceptions of interaction (n=31).
-Linguistic content (n=17) and non-linguistic format (n=18) had similar number of relationships.
-
-There are a few conversation architecture elements that are notable to the perception of interaction with agent.
-First are the linguistic styles of formality and elaborateness, where they have high impacts across usability, engagement and satisfaction perceptions.
-For \textbf{formality}, various studies reported significant differences between using casual vs.
-formal styles.
-Some participants enjoyed the friendly nature of the casual style of the conversation \cite{cox2022does}\cmt{[27]}, while in another study participants reported the formal language style as boring \cite{kim2019comparing}\cmt{[89]}.
-For \textbf{elaborateness}, participants generally found the use of full sentences more useful than keyword only \cite{haas2022keep}\cmt{[78]}\cite{roy2021users}\cmt{[71]}.
-Otherwise, the impact of an agent's elaborateness on user's perception of interaction depends on the user's preference \cite{miehle2018exploring}\cmt{[51]}, as well as the topic of discussion \cite{haas2022keep}\cmt{[78]}.
-Within the linguistic content category, \textbf{social talk} and \textbf{humour} conversation architecture elements had impacts on user's perception of the interaction with an agent.
-There may be some opposing effects between different perceptions of interaction, as users enjoyed conversing with CAs using social talk more \cite{lee2020hear}\cmt{[23]}\cite{roy2021users}\cmt{[71]}, but the tradeoff is that they perceive it as less efficient \cite{roy2021users}\cmt{[71]}.
-Lastly, majority of the studies found that non-linguistic formats of a CA impacts the perception of the interaction, as \textbf{prosodic cues} such as expressiveness increased participants' engagement ratings \cite{zhu2022effects}\cmt{[26]}, and text variations such as using response delay increased user's satisfaction with the chatbot interaction \cite{gnewuch2018faster}\cmt{[19]}.
+While the number of papers studying CAs with voice (n=27) vs.
+text (n=30) modalities is not significantly different, there are some interesting patterns we found with regards to the modalities of the identified relationships between perceptions of agents and conversation architecture.
+Overall, we confirmed the pattern found earlier that there are more conversation architecture elements explored related to voice vs.
+text in the speech format category.
+Because there are smaller number of text-based CAs using speech format elements, we also observed significantly less number of relationships between text-based CA across all perceptions of agents.
+other interesting findings related to modality are discussed later in this paper.
 
@@
 
+\subsubsection{Perception of Interaction with Agent}
+
+The effects of conversation architecture elements on the perception of interaction with agent is the most explored connections in the corpus (n=97).
+Out of these explored connections, the majority of them (n=66) discovered a relationship between aspects of perception related to the perception of interaction with agent related to the studied architecture element.
+Looking at the difference between modalities, we noticed more voice-based agents (n=25) resulted in null relationships compared to text-based agents (n=6).
+The conversation architecture element of \textit{alignment} contributed the most to the null results for voice-based agents, with 9 out of 11 explored connections did not find any relationships related the perception of interaction with agents.
+
+Across the aspects for the perception of interaction, both \textit{usability} and \textit{engagement} were assessed frequently in the reviewed literature, with conversation architecture having effects on these perception aspects across all architecture element categories.
+The aspect of \textit{satisfaction} was used in some studies to evaluate perception but it is not used as often as engagement or usability.
+Several papers that assessed user satisfactions were conversation agents within the transaction context, especially within the customer service domain (e.g.
+\cite{diederich2019emulating}\cmt{[25]}\cite{elsholz2019exploring}\cmt{[61]}\cite{gnewuch2018faster}\cmt{[19]}).
+
+The category of conversation architecture elements with the most identified relationships to perceptions of interaction is \textit{content style}.
+Specifically for the element of \textit{elaborateness}, users found the use of full sentences more useful than keyword only \cite{haas2022keep}\cmt{[78]}\cite{roy2021users}\cmt{[71]}.
+Otherwise, the effect of an agent's elaborateness on user's perception of interaction depends on the user's preference \cite{miehle2018exploring}\cmt{[51]}, as well as the topic of discussion \cite{haas2022keep}\cmt{[78]}.
+As for \textit{formality}, various studies reported significant differences in perceptions of interaction between using casual vs.
+formal styles.
+Some users experienced higher engagement with agent interacting with the casual style of the conversation \cite{cox2022does}\cmt{[27]}, while in another study users reported the formal language style as less engaging as it is boring \cite{kim2019comparing}\cmt{[89]}.
+
+The speech format of an agent also resulted in a high number of identified relationships with the perception of interaction with CAs, with majority of the explored connections resulted in effects between the perception aspects and architecture elements.
+The element with the most identified relationships is \textit{prosody}.
+For example, studies found that a CA's expressiveness in vocal cues increased participants' engagement ratings \cite{zhu2022effects}\cmt{[26]}, and different pitches of voice affect users' perception of engagement and usability \cite{chan2021kinvoices}\cmt{[74]}\cite{habler2019effects}\cmt{[63]}.
+
+Dialog strategy and content affectiveness categories of conversation architecture did not have as many identified relationships with perceptions of interaction.
+It is worth noting the effect of using the \textit{initiative} element, as CAs that use self-initiated content are perceived as more efficient and higher quality of interaction (e.g.
+\cite{cuadra2021my}\cmt{[67]}).
+Also, some studies have discovered conflicting effects between different perception aspects of interaction for CAs using \textit{social dialog}, as users enjoyed the conversation using social talk \cite{lee2020hear}\cmt{[23]}\cite{roy2021users}\cmt{[71]}, but perceived the CA as less efficient \cite{roy2021users}\cmt{[71]}.
+
 \subsubsection{Perception of Agent's Ability}
 
-The effects of conversation architecture elements on the perception of agent's ability is the least explored connection in the corpus (n=35).
-Out of these explored connections, 27 relationships had an effect between the studied architecture elements and ability perceptions.
-For these impactful relationships, the corpus had similar numbers of connections across voice-based (n=15) and text-based (n=12) CAs.
+The effects of conversation architecture elements on the perception of agent's ability is the least explored connection in the corpus (n=39).
+Out of these explored connections, the majority of them (n=30) found relationships between the studied architecture element and the perceptions of agent's ability.
+There are no notable differences between the text and voice modalities of CAs for either explored connections or the identified relationships.
 
-Across the themes in this perception category, \textbf{competence} had the smallest number of relationships in our corpus compared to intelligence and trust.
-Some studies discussed that the perception of competence is dependent various influencing factors, such as task difficulty \cite{kraus2020effects}\cmt{[64]}.
-Overall, studies on the perception of \textbf{intelligence} had impactful results, such as the use of formal language made the CA seem more knowledgeable \cite{volkel2022user}\cmt{[75]}.
-However, some evidence suggest that there are nuances to this perception, as a filler-speaking agent was perceived as less intelligent in task-oriented conditions, but was seen as slightly more intelligent in social-oriented conditions \cite{jeong2019exploring}\cmt{[10]}.
+Aspects within the perception of agent's ability had similar number of identified relationships across intelligence, competence and credibility.
+Our review revealed that the perceived ability of a CA is also dependent on other influencing factors in addition to conversation architecture elements.
+Volkel et al.
+\cite{kraus2020effects}\cmt{[64]} found that the perception of competence of a proactive CA is dependent on task difficulty \cite{kraus2020effects}\cmt{[64]}.
+Also, the perception of intelligence for an agent using fillers depended on the context of the conversation, as the filler-speaking agent was perceived as less intelligent in task-oriented conditions, but was seen as slightly more intelligent in social-oriented conditions \cite{jeong2019exploring}\cmt{[10]}.
 
-For the conversation architecture categories related to the perception of agent's ability, all 10 explored connections related to \textbf{linguistic content} had impacted user's perception.
-Specifically, CAs utilizing \textbf{agent-initiative content} such as using proactive dialogue and conversation repair strategies are seen as more competent \cite{kraus2020effects}\cmt{[64]} and intelligent \cite{ashktorab2019resilient}\cmt{[88]}.
-However, the effect of being proactive on user's trust with an agent may be dependent on the proactive style of the user's own conversation patterns \cite{kraus2020effects}\cmt{[64]}.
-For CAs using \textbf{affective language}, some studies found that using more expressive words increased intelligence and competence \cite{lee2019s}\cmt{[55]}\cite{yang2017perceived}\cmt{[44]}, but it may decrease the perceived trustworthiness of an agent
-%as discussed in Healey et al's study using an agent with an encouraging personality
-\cite{healey2013relating}\cmt{[39]}.
+Out of the explored conversation architecture elements, \textit{prosody} had relationships identified with aspects across the perception category of agent's ability.
+For example, Chan et al.
+\cite{chan2021kinvoices}\cmt{[74]} found that agents using kin's voices are rated as more intelligent and credible than generic voices.
+Also, the style of speech used by an agent affects the perception of appropriateness of tone, which is an aspect of the perceived competence of an agent \cite{misu2011toward}\cmt{[83]}.
+Different content styles of \textit{formality} also impacts the perceived competence of an agent \cite{cox2022does}\cmt{[27]}\cite{jestin2022effects}\cmt{[81]}.
+Specifically related to perceived credibility of an agent, being \textit{lexically aligned} with the user resulted improved the rating of trustworthiness of an agent \cite{hoegen2019end}\cmt{[31]}\cite{linnemann2018can}\cmt{[15]}.
+There were mixed results on the use of emoticons within the \textit{text formatting} element.
+One study found the chatbot using emoticons as less trustworthy \cite{wilhelm2022keep}\cmt{[28]}, while another study found that users assigned higher scores for confidence to the agent using emojis \cite{fadhil2018effect}\cmt{[52]}.
 
-The conversation architecture categories \textbf{Linguistic style} and \textbf{non-linguistic format} had mixed results, with some elements demonstrating relationships with the perception of the agent's abilities, while some others didn't.
-Most these mixed results came from relationships with the perception of trust.
-Studies with \textbf{alignment} found differences in trust rating in the interaction studies \cite{hoegen2019end}\cmt{[31]}, while some others did not reveal any differences \cite{huiyang2022improving}\cmt{[17]}.
-Also, research method may impact the perception of trust, as an observation study and interaction study on a similar topic yielded different results on the perception of trust \cite{linnemann2018can}\cmt{[15]}.
-The use of \textbf{prosodic cues} also had varied impacts on trust, as one study found that differences in vocal cues lead to a difference in perceived truthfulness \cite{dubiel2020persuasive}\cmt{[60]}, while another study using gendered voices did not find any statistically significant differences in perceived trust \cite{jestin2022effects}\cmt{[81]}.
+There are several conversation architecture elements with little to no explorations to the perception of agent's ability.
+Specifically, both categories of dialog strategy and content affectiveness are minimally explored in our reviewed corpus, with no explored connections with \textit{response delay} and only one or two connections explored for \textit{social dialog} and \textit{humour}.
+While the content style category had coverage in some aspects of perceived abilities, it is worth noting that \textit{elaborateness} did not have any explored connections with perceived ability of agents.
+Further research in these areas is needed to fill these gaps.
 
-\subsubsection{Perception of Social Connection with Agent}
+%% CW - second pass up to here Feb 15
+
+\subsubsection{Perception of Sociability with Agent}
 
@@
 This shows that there are nuanced factors within prosodic cues that impact the perception of social connections that we have not captured in our relationships.
+
+%For humour: Clark et al.
+\cite{clark2019makes} found that humour is an important conversational characteristic for human-human interactions, but viewed as a novelty feature for human-agent conversations.
 
@@
 
+%include different age considerations - cite Jaisie's paper
+
 While the use of conversation architecture elements can be used to design anthropomorphized perceptions, it is important to address the potential ethical implications that could negative impact users.

### 2023-02-17 paper.tex
second pass completed! yay!

@@
 \begin{abstract}
-%Conversational agents employ natural language to interact with human users. While it is broadly accepted that the specifics of speech interactions affect the perception of communicating parties, 
-%Previous research has demonstrated a relationship between the structure of conversational agents' natural language interaction and how these agents are perceived by their users. However, 
-%there is a lack of systematic understanding of the connections between the perception of agents and elements of conversation architecture. % are not well understood. 
-%Furthermore, there is no clear definition of the aspects of perception that are affected and the elements of conversation architecture.
-In this paper, we present a synthesized framework demonstrating the connections between perceptions of agents and conversation architecture elements, using a taxonomy of eleven perceptions grouped into four categories, and ten elements grouped into three categories.
-We highlight the need for further research for the perception of agent's ability and perception of social connection with agent's, especially as it relates to the linguistic style of conversational agents.
-Also, there is the need to be consistent in the assessment of agents' perceptions, and consider ethical concerns in design.
-%[AK Edit] Conversational agents are deliberately designed to interact by simulating natural conversation, and the effectiveness of these interactions is shown to be affected by users' perceptions of an agent.
-While research on human-human and human-agent communication suggests the association between speech specifics and perceptions of communicating parties, there is a lack of systematic understanding of how an agent’s conversation architecture affects users' perceptions.
-To address this gap, we present a framework that outlines the relationships between elements of agents’ conversation architecture grouped around dialog strategy, content affectiveness, content style and speech format, and agent characteristics grouped around perceptions of interactions with an agent, agent's ability, sociability, and humanness.
-Synthesized based on literature review (n=57), the framework demonstrates both the identified relationships and the areas lacking empirical evidence.
-We discuss the implications of the framework for the conversation design and highlight the inconsistency issues with the domain terminology and measurements.
 Conversational agents mimic natural conversation to interact with users.
@@
 \cite{hoegen2019end}\cmt{[31]} did not find a significant difference between the style matching agent and the non-style matching agent for overall interaction satisfaction.
-Out of the 193 relationships, 10 were relationships based on agents using multiple architecture elements (e.g.
+Out of the 193 relationships, 10 were relationships based on agents modifying multiple architecture elements (e.g.
 \cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2021manipulating}\cmt{[68]}).
@@
 
-Across the aspects for the perception of interaction, both \textit{usability} and \textit{engagement} were assessed frequently in the reviewed literature, with conversation architecture having effects on these perception aspects across all architecture element categories.
-The aspect of \textit{satisfaction} was used in some studies to evaluate perception but it is not used as often as engagement or usability.
+Across the aspects for the perception of interaction, both usability and engagement were assessed frequently in the reviewed literature, with conversation architecture having effects on these perception aspects across all architecture element categories.
+The aspect of satisfaction was used in some studies to evaluate perception but it is not used as often as engagement or usability.
 Several papers that assessed user satisfactions were conversation agents within the transaction context, especially within the customer service domain (e.g.
@@
 
-The category of conversation architecture elements with the most identified relationships to perceptions of interaction is \textit{content style}.
+The category of conversation architecture elements with the most identified relationships to perceptions of interaction is content style.
 Specifically for the element of \textit{elaborateness}, users found the use of full sentences more useful than keyword only \cite{haas2022keep}\cmt{[78]}\cite{roy2021users}\cmt{[71]}.
@@
 While the content style category had coverage in some aspects of perceived abilities, it is worth noting that \textit{elaborateness} did not have any explored connections with perceived ability of agents.
-Further research in these areas is needed to fill these gaps.
-
-%% CW - second pass up to here Feb 15
+Further research in these areas is needed to fill these gaps in understanding.
 
@@
 
-There are 53 explored connections between conversation architecture elements and the perception of social connection with agents, with majority of them (n=40) resulted in relationships with effects.
-Interestingly, studies explored more perceptions of social connection with agent related to voice-based CAs (n=34) compared to text-based CAs (n=19), potentially due to the assumption that voice-based agents is more suitable to cultivate human-agent relationships.
-There are some mixed results for voice-based CAs, as 10 out of the 34 connections did not find any significant results.
-Half of the neutral results come from the conversation architecture element of \textbf{prosodic cues}.
-For example, the pitch of agents' voices did not impact the perceived rapport \cite{lubold2016effects}\cmt{[86]} between agent and users or the appropriateness of tone \cite{jestin2022effects}\cmt{[81]}.
-However, there are also findings that the use of vocal cues made the agent sound more empathetic \cite{tolmeijer2021female}\cmt{[62]}, as well as increased perceived emotional connection \cite{chan2021kinvoices}\cmt{[74]}\cite{kim2020can}\cmt{[24]}.
-This shows that there are nuanced factors within prosodic cues that impact the perception of social connections that we have not captured in our relationships.
+The perception of agent's humanness is the second most explored category within our reviewed corpus (n=64), with majority of the connections identified relationship between the studied conversation architecture elements and the anthropomorphized perceptions of agent (n=49).
+Interestingly, studies explored more perceptions of sociability with agent related to voice-based CAs (n=40) compared to text-based CAs (n=24), potentially due to the assumption that interactions with text-based agents are perceived as less personal and more formal \cite{kocielnik2018designing}.
+There are some mixed results for voice-based CAs, as 12 out of the 28 connections did not find any significant results.
+Drilling down to the specific elements, we noticed that the use of \textit{alignment} in voice-based agents did not effect the perception of sociability with agent \cite{healey2013relating}\cmt{[39]}\cite{linnemann2018can}\cmt{[15]}.
+We didn't have data on text-based agents' perceived social connections with users to compare with voice-based agents, as the studies using alignment and text modality in our corpus did not assess this aspect category of perception.
 
-%For humour: Clark et al.
+Across the aspects in this perception category, conversation tone had the most number of identified relationship (n=27) with the perceived social connection with CAs, followed by the aspect of social presence (n=17).
+There are only 5 relationships found that are linked to the perception aspect of intimacy.
+One reason for this is half of the explored connections did not have any effect on the perception of sociability with agent, such as the use of capitalization \cite{westerman2019believe}\cmt{[9]}, lexical alignment \cite{linnemann2018can}\cmt{[15]}, or social talk \cite{lubold2016effects}\cmt{[86]}.
+For the perception aspect of social presence, we noticed a gap in the exploration of conversation architecture elements of formality, alignment, and elaborateness in the content style category, as there are no papers explored at this intersection.
+
+Looking at the different categories of conversation architecture elements, the heatmap (Figure \ref{fig:heatmap-impact} shows that there are not many relationships in content style category that are related to the perceived sociability with CAs in general, with most of the discovered effects concentrated at the intersection of \textit{formality} and conversation tone.
+Studies have found that CAs using casual style of conversation are perceived as warm, empathetic and friendly \cite{jestin2022effects}\cmt{[81]}\cite{kim2019comparing}\cmt{[89]}, while CAs using formal style of conversation are perceived as polite but lacks empathy \cite{cox2022does}\cmt{[27]}.
+The rest of the architecture elements and perception aspects of sociability are minimally explored in literature, which indicates the need for more research in this area.
+
+There are a few specific conversation architecture elements that had more identified relationships with perceptions of sociability with agent.
+Specifically, CAs using of \textit{affective language} were perceived to be more empathetic \cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{yang2017perceived}\cmt{[44]} and emotionally expressive \cite{zhu2022effects}\cmt{[26]}, as well as being more emotional connected with their users \cite{lee2019s}\cmt{[55]}\cite{lubis2019positive}\cmt{[43]}.
+Also, different variations of a voice-based CA's \textit{prosody} have effects on the perceived sociability with agent, such as an agent using expressive prosody is assessed as more intimate and more similar with the user \cite{kim2020can}\cmt{[24]}.
+Lastly, the conversation architecture element of \textit{humour} has identified relationships across the social connection category of perception.
+Clark et al.
 \cite{clark2019makes} found that humour is an important conversational characteristic for human-human interactions, but viewed as a novelty feature for human-agent conversations.
-
-Across the themes in this perception category, \textbf{social presence} (n=17) and \textbf{conversation tone} (n=18) have similar number of relationships between architecture elements and perceptions, but \textbf{intimacy} (n=5) has less number of impactful relationships.
-One reason for this is half of the explored connections did not have any effect on the perception of social connection, such as the use of capitalization \cite{westerman2019believe}\cmt{[9]}, lexical alignment \cite{linnemann2018can}\cmt{[15]}, or social dialogue \cite{lubold2016effects}\cmt{[86]}.
-For \textbf{social presence}, conversation architecture elements from \textbf{non-linguistic format} category, prosodic cue and text variation, had a number of impactful relationships in the reviewed studies.
-For example, participants conversing with the agents using kin's voices experienced significantly higher perceived co-presence where there is a closer psychological connection with the agent \cite{chan2021kinvoices}\cmt{[74]}.
-Also, text-based agents including a delay before responding to users were rated higher in social presence ratings compared to the agent that did not use any response delays \cite{gnewuch2018faster}\cmt{[19]}\cite{gnewuch2022opposing}\cmt{[20]}.
-Lastly, the use of \textbf{prosodic cues} can impact the perceived \textbf{conversation tone} of the agent as emotionally expressive \cite{zhu2022effects}\cmt{[26]} or persuasive \cite{chan2021kinvoices}\cmt{[74]}, as well as the appropriateness of the tone used by the agent \cite{jestin2022effects}\cmt{[81]}\cite{misu2011toward}\cmt{[83]}.
-
-Looking at the different categories of conversation architecture cues, the heatmap (Figure \ref{fig:heatmap-impact} shows that there are not many relationships in \textbf{linguistic style} that are related to the perceived social connection with CAs.
-There are not many explored connections in our reviewed corpus between the two, which could be an indication of the assumption that linguistic style does not impact the perception of social connections.
-While we discussed the impact of non-linguistic elements of prosodic cues and text variations earlier, the conversation architecture elements in the linguistic content category also had effects on the perception of social connections.
-Specifically, CAs using of \textbf{affective language} were perceived to be more empathetic \cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{yang2017perceived}\cmt{[44]} and emotionally expressive \cite{zhu2022effects}\cmt{[26]}, and emotional connection with the agent \cite{lee2019s}\cmt{[55]}\cite{lubis2019positive}\cmt{[43]}.
-
-%add text variation in the discussion
+However, in our review we found that humor has effects on human-agent relationships, as humorous agents are rated as more friendly, intimate, and similar by users compared to non-humorous agents \cite{go2021conversational}\cmt{[80]}\cite{khooshabeh2011does}\cmt{[37]}.
 
@@
 
-Agent's humanness is the second most explored perception within our reviewed corpus (n=76), with majority of the connections finding impacted relationship between the studied conversation architecture elements and the perception of agent's humanness (n=56).
-While the connections were explored more for voice-based agent (n=49) as compared to text-based agents (n=27), the actual impacted relationships between the modalities were similar (voice=32, text=24).
-This is due to larger number of neutral relationships within voice modality, such as the use of affective language for a speech agent did not impact its perceived likeability \cite{hu2022polite}\cmt{[76]}.
+There are 55 explored connections between conversation architecture elements and the perception of sociability with agents, with majority of them (n=38) finding identified relationships in literature.
+There are significantly more explorations for voice-based agents (n=39) as compared to text-based agents (n=16).
+Previous studies have found that modality may have an effect on the perception of humanness, as voice-based agents are perceived as more human-like as compared to text-based agents \cite{cho2019effects}.
+Out of the 39 explored connections for voice-based agents, 14 of them did not result in any relationships.
+This is especially evident in the architecture element of \textit{affective language} for voice-based agents, as most of the connections resulted in null relationships.
+For example, when comparing the ratings of human-likeness or likeability for a speech agent employing expressive words to the one not using any, Zhu et al \cite{zhu2022effects}\cmt{[26]} were unable to detect any statistically significant differences in both of the observation study and interaction study.
 
-Across the themes in this perception category, both \textbf{human-likeness} and \textbf{personality traits} have relationships with almost all conversation architecture elements.
-Based on the reviewed corpus, it seems like all the conversation architecture elements extracted from literature have some impact on the perception of agent's humanness.
-However, the impacts can be both positive or negative.
+Across the aspects in this perception category, both human-likeness and personality traits have relationships with almost all the conversation architecture elements.
+Specifically for the use of \textit{prosody} elements, our review found some opposing effects on the perception of the agent's humanness.
 In the case of Chan et al's study \cite{chan2021kinvoices}\cmt{[74]}, participated rated the agent using kin voices as significantly more likeable compared to the generic voices, but it was perceived as eerie.
-As for the perceptions within this category, there are more relationships for perceived personality traits (n=33) vs.
-human-likeness (n=18).
-This is because many studies only have one measure for human-likeness (e.g.
-artificial or human-like), but have multiple aspects of personality to be explored.
-For example, participant rated the agent using affective language as more polite, as well as reflected that the agent seemed friendly \cite{hu2022polite}\cmt{[76]}.
+This may be a warning indicator to watch out for the uncanny valley effect \cite{mori2012uncanny} and advise CA designers to carefully select conversation architecture elements to elicit anthropomorphized perceptions.
 
-For the conversation architecture elements, formality in the linguistic style category and prosodic cue in the non-linguistic format category had more effects on the perception of agent's humanness in the reviewed corpus.
-For \textbf{formality}, agents using casual style is perceived as more human-like with a warm, kind and entertaining personality \cite{cox2022does}\cmt{[27]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2019comparing}\cmt{[89]}.
-The use of \textbf{prosodic cues} varying pitch, intonation and speech rate of a conversation agent generally had impacts on the perceived humanness instead of personality traits \cite{choi2020nobody}\cmt{[54]}\cite{jestin2022effects}\cmt{[81]}\cite{misu2011toward}\cmt{[83]}.
-For the architecture elements of \textbf{disfluency}, the type of impact on the perception of humanness depended on the context of the conversation.
+There are a few notable conversation architecture elements related to the perceived humanness of conversational agents.
+The use of \textit{prosody} such as varying pitch, intonation and speech rate has more identified relationships with the perceived personality traits of an agent as compared to the perceived human-likeness, especially on the aspect of likeability \cite{choi2020nobody}\cmt{[54]}\cite{jestin2022effects}\cmt{[81]}\cite{misu2011toward}\cmt{[83]}.
+For the architecture elements of \textit{disfluency}, the type of impact on the perception of humanness depended on the context of the conversation.
 Studies have found that participants perceived the filler-condition agent as more likeable in the social-oriented situation, but did not find the same effect in task-oriented situations \cite{jeong2019exploring}\cmt{[10]}\cite{wester2015artificial}\cmt{[14]}.
+The use of \textit{alignment} in an agent had a number of identified relationships with the perception of personality traits, with some studies finding CAs that are lexically aligned with a user are more likeable \cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}.
 
@@
 
-\subsubsection{Inconsistencies in Perception Measures}
+\subsubsection{The Need for Consistent Evaluation Protocols for Perceptions of Agents}
 
-A major roadblock in synthesizing the findings from existing academic research is the diversity and inconsistency of measurements towards the anthropomorphized perception of agents.
-It is difficult to assess whether perception measures should be compared with each other.
-Also, some measures combined anthropomorphized perceptions into a composite score, which makes it impossible to separate the perceptions into more granular details.
+We found a diversity of approaches used to assess perceptions of agents in our reviewed corpus.
+While we made our best efforts to group perceptions used in literature based on similarity with each other, the inconsistent and composite nature of these perception assessments makes it challenging to synthesize them into a framework that contains homogeneous components in each perception aspect that can be compared with each other.
 
-Based on the literature reviewed in this paper, we noticed that similar perception concepts were \textbf{measured in different ways} through different surveys.
-For example, there are several approaches to measure the perceived \textit{human-likeness} of an agent.
-A commonly used survey is adapted from the Godspeed questionnaire \cite{bartneck2009measurement}, which measures human-likeness based on user's impression of the agent as fake / natural, machinelike / humanlike, unconscious / conscious, and artificial / lifelike (used by \cite{hoegen2019end}\cmt{[31]}, \cite{jeong2019exploring}\cmt{[10]} and \cite{ouchi2019should}\cmt{[59]}).
-Another way to measure human-likeness is adapted from Holtgraves et al.'s \cite{holtgraves2007perceiving} questionnaire, which asks users to assess the agent's perceived human-likeness, skillfulness, thoughtfulness, politeness, responsiveness and engagement (used by \cite{diederich2019emulating}\cmt{[25]} and  \cite{gnewuch2018faster}\cmt{[19]}).
-One study \cite{westerman2019believe}\cmt{[9]} used the Ascend of Man pictorial scale \cite{kteily2015ascent} as the measure of perceived human-likeness.
-It is unclear whether these different measures of perceived human-likeness are similar enough to be compared with each other.
+Based on the literature reviewed in this paper, it is unclear whether perception aspects using similar labels are being evaluated \textit{consistently} through different approaches.
+For example, we found several methods used to assess the perceived human-likeness of an agent.
+A commonly used survey is adapted from the Godspeed questionnaire \cite{bartneck2009measurement}, which evaluates human-likeness based on users' impression of the agent as fake / natural, machinelike / humanlike, unconscious / conscious, and artificial / lifelike (used by \cite{hoegen2019end}\cmt{[31]}, \cite{jeong2019exploring}\cmt{[10]} and \cite{ouchi2019should}\cmt{[59]}).
+Another method used to evaluate human-likeness is adapted from Holtgraves et al.'s \cite{holtgraves2007perceiving} questionnaire, which asks users questions related to the agent's perceived human-likeness, skillfulness, thoughtfulness, politeness, responsiveness and engagement (used by \cite{diederich2019emulating}\cmt{[25]} and  \cite{gnewuch2018faster}\cmt{[19]}).
+One study \cite{westerman2019believe}\cmt{[9]} used the Ascend of Man scale \cite{kteily2015ascent} with pictures showing the evolution from ape to man, asking users to choose a depiction that best represents the agent's perceived human-likeness.
+It is unclear whether these different methods are capturing assessments of similar perception aspects that can be compared with each other.
+Another example is the evaluation of the perception of agent's empathy.
+In Diedrech et al.'s study \cite{diederich2019emulating}\cmt{[25]}, empathy is assessed by asking users whether the CA is giving users individual or personal attention.
+In another study that also studies the perception of empathy \cite{daher2020empathic}\cmt{[58]}, the RoPE Scale \cite{charrier2019rope} is used with questions like "the robot cares about my feelings" or "the robot comforts me when I am upset." These two different evaluations of empathy seem to have different underlying meanings, one assessing the personalization aspect of CAs, while the other is assessing the emotional aspect of CAs.
 
- In addition to different methods used to measure for the same perception, our detailed analysis revealed that the measures using the same label may have \textbf{different meanings}.
-In Diedrech et al.'s study \cite{diederich2019emulating}\cmt{[25]}, \textit{empathy} measure is adapted from \cite{yan2013role} assessing whether the CA gives users individual or personal attention.
-In Daher et al.'s study \cite{daher2020empathic}\cmt{[58]}, they also measure the perception of empathy, but it is using the RoPE Scale \cite{charrier2019rope} with questions like "the robot cares about my feelings" or "the robot comforts me when I am upset." These two different measures of empathy seem to have different underlying meanings, one assessing the personalization aspect of CAs, while the other is assessing the emotional aspect of CAs.
-Another example is the measurement of \textit{trustworthiness}, with some constructs measuring the level of sensitive information user's are willing to share \cite{dinev2006privacy}, and some measuring the honesty and truthfulness of an agent \cite{lee2017enhancing}.
+In addition the problem of consistency in evaluating perceptions, there is the issue of  \textit{composite measures} being used in the assessment of users' perceptions.
+These composite measures collapse multiple aspects of perception into one measurement, making it impossible to break down perceptions into more granular aspects for analysis.
+One such example is Ma et al's study \cite{ma2022ask}\cmt{[29]} on the different approaches for CAs to reply to users' uncertain queries.
+A single UX score is used to evaluate the users' perceptions, which composes of questions on whether the user thinks the CA's response is pleasing / trustworthy / natural / acceptable / shorten the distance between CA and user.
+The UX score encompasses multiple aspects across several perception categories.
+While this study has found significant effect for the use of formal language on the user rated UX score, it is not possible to understand how the details of formality is related to the perception categories of interaction (pleasing, acceptable), sociability (shorten the distance between CA and user), and humanness (natural, trustworthy).
+The humanness questionnaire from Holtgraves et al \cite{holtgraves2007perceiving} has a similar problem, evaluating across perception categories of interaction (responsiveness, engagement), ability (skillfulness), sociability (politeness), and humanness (human-likeness, thoughtfulness).
 
-Lastly, there are \textbf{composite measures} of anthropomorphized perception across different categories, making it difficult to break down perceptions into granular details for analysis.
-One such example is Ma et al's study \cite{ma2022ask}\cmt{[29]} on different approaches for CAs to reply to users' uncertain queries.
-UX score is used to measure the perception of an agent, which asks whether the user thinks the CA's response is pleasing / trustworthy / natural / acceptable / shorten the distance between CA and user.
-While the study has found significant impact of the use of formal language on UX score, it is not possible to breakdown the measure into perceptions of interaction (pleasing, acceptable), social connection (shorten the distance between CA and user), and humanness (natural, trustworthy).
-Similar for Hoegen et al.'s study \cite{hoegen2019end}\cmt{[31]} on the impact of conversational style matching, it is not possible to separate the overall interaction score into different perceptions as the composite measure contains questions measuring different categories of perceptions like interaction (engaging) and humanness (trust, likable).
+There has been some effort recently towards unifying the evaluation of conversational agents, such as the work by Finch et al.
+\cite{finch2020towards} presenting a comprehensive analysis of current evaluation protocols.
+More research is needed in this area to standardize the assessment of perceptions to make them consistent, granular, and comparable across literature.
 
-In recent years there has been some effort towards unifying the evaluation of conversational agents, such as the work by Finch et al.
-\cite{finch2020towards} presenting a comprehensive analysis of current evaluation protocols.
-More work is needed to categorize and consolidate perception measures to make them consistent and comparable across various studies.
+\subsubsection{Investigate the Relationship Across Perception Aspects of Agents}
 
-\subsubsection{Nuances in Influencing Factors}
+There is evidence in literature that perception aspects of agents have effects on each other.
+For instance, Moussawi et al.
+\cite{moussawi2021perceptions}\cmt{[36]} conducted a study to understand the correlations between different perceptions related to users' intention to adopt a conversational agent.
+Specifically, they found a correlation within the category of perceived ability, where an agent's perceived intelligence is positively correlated to the perceived initial trust of the agent.
+This study also found that users with higher perceived intelligence of an agent are more likely to attribute higher ratings for perceived human-likeness, as well as for the usability and engagement aspects in the perception category of interaction.
+Lastly, the authors found that perceived humanness have a positive impact on perceived enjoyment, which lead to higher intention to adopt the CA.
+This study outlines that the perception aspects identified in this paper are not independent of each other.
 
-While the discussion in the Framework section above focuses on the overall effect of conversational architecture elements on anthropomorphized perceptions,  there are other nuanced influencing factors that impact user perceptions of agents.
-
-Depending on the \textbf{type of conversation} user is having with agents, it may lead to differences in perceptions for similar conversational architecture elements.
-Cox et al.
-\cite{cox2022does}\cmt{[27]} found that the perceived competence and appropriateness of tone of different language formality styles depend on the sensitivity of information discussed in the conversation.
-In this particular study, a formal language style is preferred in medical history discussions as it is matching to the expectation of users, but there is no difference in perception between formal and casual styles when discussing income level and credit scores.
-In Jeong et al's study \cite{jeong2019exploring}\cmt{[10]}, users found the agent using fillers less intelligent and likable in a task-oriented conversation, but found the same agent using fillers as slight more intelligent and likable in a social-oriented conversation.
-Another factor that could impact perceptions is the \textbf{anonymity} of conversation.
-Based on user feedback, Lee et al.
-\cite{lee2020hear}\cmt{[23]} found that the anonymity of a conversational agent is a driving factor encouraging people to self disclose without having to worried about judgements from the CA.
-The perception of the agent may be different if the user's identity is not anonymous.
-
-Other than the type of conversation, \textbf{user's characteristics} can also be influencing factors on their perception of agents.
-For example, the effect of matching user's conversational style on perception of agents depend on user's own conversational style, as participants with high consideration conversational style rated the lexically aligned agent as more trustworthy \cite{hoegen2019end}\cmt{[31]}.
-In the study by Cox et al.
-\cite{cox2022does}\cmt{[27]}, participants with lower levels of privacy concerns as well as those who believe in robotic intelligence found the chatbot more enjoyable, warm, competent and appropriate.
-Similarly, participants with positive attitudes towards computers were significantly more likely to indicate that the usage of fillers by agents was a positive aspect of the conversation, compared to participants with neutral attitudes towards computers \cite{pfeifer2009should}\cmt{[12]}.
-Lastly, user's prior experience with conversational agents could impact perception of agents.
-Experienced users perceived the agent with a response delay as lower in social presence compared to the one without delay, as it is seen as inefficient to wait for the CA to respond.
-However, novice users perceived higher social presence conversing with the CAs using response delays as it is more similar to conversations with human partners \cite{gnewuch2018faster}\cmt{[19]}.
-
-%Designing for personalities, not individual elements
-
-%* The size of the effect for language we observed is clearly higher than the size of the effect for voice. \cite{habler2019effects}\cmt{[63]}
-
-%Combined effects
-%* integrated mental model \cite{knijnenburg2016inferring}\cmt{[34]}
-%* Anthropomorphized chatbot (text) using affective language (emotional expressions), self-referencing, emoticons, response delays.
-Resulted in higher perceived anthropomorphism, which in result led to lower negative word of mouth and loss of trust.
-anthropomorphic design is beneficial not only to initial trust but also to the ongoing trust relationship \cite{seeger2021chatbots}\cmt{[35]}
-
-%For discussions on mental well beings, agent using emojis is rated higher for attitude (emotional connection) .
-However, for agent with discussing physical well being, agent using emojis is rated as lower for attitude.
-%Attitude has emotional connection, coherent - coherent is an ability perception, vs. emotional connection is a social connection perception. \cite{fadhil2018effect}\cmt{[52]}
-
-%* Format: Response delay - Novice users perceived the agent as more socially present, but experienced users had a negative effect \cite{gnewuch2022opposing}\cmt{[20]}
-%* Content: Humour - no overall significant difference between conventional method vs.
-agent using humour for enjoyment.
-Specifically, men enjoyed the agent's jokes more than women.
-\cite{miyamoto2017improving}\cmt{[46]}.
-%* Format: Proactivity - significant interaction between proactive dialogue strategies and task difficulty for perceived competence and perceived reliability.
-For easier tasks, system help is not really required.
-\cite{kraus2020effects}\cmt{[64]}
-%* Preference for the level of social talk depended on the task, even within the same transactional context, as users preferred high level for playing a song, but low level for writing a text.
-\cite{volkel2021manipulating}\cmt{[68]}
-%* Correlation between user's personality of agreeableness vs. preference for agreeable level of chatbot \cite{volkel2021examining}\cmt{[69]}
-%* For expertise, multilingual students rated higher the non-native English-speaking virtual human. \cite{feijoo2021effects}\cmt{[70]}
-%* Participants felt irritated when humorous statements were made when they talked about experiencing sadness \cite{go2021conversational}\cmt{[80]}
-
-%\subsubsection{Study Design}
-
-%\textbf{Interview vs experiment}
-%* Humour - what's said vs. study results
-
-%\textbf{Observer study vs. interaction study}
-%* In observer study, participants attributed higher integrity (trustworthiness), response accuracy and likeability to the agent with lexical alignment, but this effect was not observed in the interaction study.
-Also, interaction study had lower cognitive demand but no effect in the observer study.
-\cite{linnemann2018can}\cmt{[15]}
-%* \cite{zhu2022effects}\cmt{[26]}
-%* \cite{cox2022does}\cmt{[27]}
-
-%* that a sense of intimate connection to the CA is more important than efficient task handling in some contexts \54
-%* VA self-repair can backfire if time or accuracy is of the essence. (repair and accuracy) \cite{cuadra2021my}\cmt{[67]}
-
-%Sometimes a study is covering multiple conversational element cues, hard to break it out.
-For example, extroverted personality used in \cite{volkel2022user}\cmt{[75]} has emoticons, affective language, talkative, and self-disclosure.
-Need to break it down.
-
-%Also, breaking down "personalities" to its core components.
-
-%There are a few studies that designed conversational agents composed with multiple conversation architecture elements.
-This is especially evident in studies comparing different personalities of CAs, such as extroverted vs.
-introverted.
-In Volkel et al's study, the personality of extraversion is a combination of linguistic content like social ta
-
-%\cite{moilanen2022measuring}\cmt{[82]}\cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}.
-
-\subsubsection{Consider Relationships Within Perceptions}
-
-There are empirical evidence that different perceptions of agent have effects on each other.
-Moussawi et al \cite{moussawi2021perceptions}\cmt{[36]} conducted a study to understand the correlations between different perceptions impacting user's intention to adopt a conversational agent.
-Specifically, they found a correlation within the category of perceived ability, where perceived intelligence is positively correlated to initial trust of the agent.
-Also, the study found that users with higher perceived intelligence of an agent are more likely to attribute higher ratings for the perception category of interaction on the perceived ease of use and enjoyment, as well as higher ratings for perceived anthropomorphism.
-Perceived anthropomorphism have a positive impact on perceived enjoyment, which lead to higher intention to adopt the CA.
-This study outlines that the perception themes we identified in this paper are not independent of each other.
-
-The correlations between perception measures are covered in a few of the papers in our corpus.
-In the study of using response delays, the perception of social presence had a significant effect on the intention to use \cite{gnewuch2022opposing}\cmt{[20]}.
-In another study, the CA's perceived personality trait of agreeableness has an influence on the perception of trust \cite{andrews2012system}\cmt{[38]}.
-Seeger et al's study had similar findings, where higher perceived anthropomorphism lead to lower loss of trust \cite{seeger2021chatbots}\cmt{[35]}.
-There are also effects within the same perception category, such as a speech agent that is rated higher in perceived human-likeness was associated with higher likability ratings \cite{zhu2022effects}\cmt{[26]}.
+Correlations between perception aspects are discussed in a few of the papers we reviewed.
+One of the studies showed that the CA's perceived personality trait of agreeableness has an influence on the users' perception of credibility \cite{andrews2012system}\cmt{[38]}.
+Seeger et al's study found a similar correlation, where higher perceived anthropomorphism led to lower loss of trust \cite{seeger2021chatbots}\cmt{[35]}.
+There are also correlations between aspects found within the same perception category, such as a speech agent that is rated higher in perceived human-likeness was associated with higher likability ratings \cite{zhu2022effects}\cmt{[26]}.
 Also, within the perception category of social connection, one study found that social distance is positively related to the perceived social attraction \cite{westerman2019believe}\cmt{[9]}.
 
-These correlations between perceptions demonstrate that designing for specific anthropomorphized perceptions of conversational agents is more nuanced than the sum of the impacts from individual perceptions.
-Perceptions have influences on each other, either within the same category or across different categories.
-However, there is not enough studied connections in existing literature to make a meaningful systematic analysis of the relationship within perceptions.
-More research is needed in this area to study these relationships, to understand whether there are systematic trends in the influences of perceptions, and whether there is a sequence of perceptions to achieve the desired overall anthropomorphized perception of agents.
+These correlations demonstrate that some perception aspects have effects on each other, either within the same category or across different categories.
+While there are limited research into this area, further investigations are needed to understand the relationships between various perception aspects.
+
+\subsubsection{Research Directions for the Effects of Conversation Architecture on Users' Perceptions}
+
+Our synthesized framework (Figure \ref{fig:heatmap-impact}) serves as a foundational understanding on the effect of conversation architecture on the perception of agents.
+It showcases the density of explored relationships between them, as well as highlighting areas that are under-explored.
+In order to continue building our knowledge, it is important to investigate further into the effect of contextual factors as well as multiple conversation architecture elements on users' perceptions.
+
+There are a few \textit{under-explored areas} in our synthesized framework.
+The perception category of agent's ability has the least number of explored connections with conversation architecture compared to other perception categories.
+Specifically, more studies are needed to understand the effects of social dialog, response delay, humour and elaborateness on users' perceptions of agents' ability.
+For the perception category of sociability with agent, there is a general lack of explored connections with the conversation architecture category of content style, especially for alignment and elaborateness elements.
+Lastly, more studies on the effect of dialog strategy for conversation architecture elements of initiative and response delay on the perceptions of agent are needed.
+
+Some studies have discussed how differences in \textit{contextual factors} resulted in variations in the perceptions of agents while using similar conversation architecture elements.
+One of the factors is users' experience with CAs, as Gnewuch et al.
+\cite{gnewuch2018faster}\cmt{[19]} found that experienced users perceived the agent with a response delay as lower in social presence because it is seen as inefficient to wait for the CA to respond, but novice users perceived higher social presence conversing with the CAs using response delays because it is more similar to conversations with human partners \cite{gnewuch2018faster}\cmt{[19]}.
+User characteristics is another factor, as the perceived trustworthiness of a style matching agent depended on users' own conversational style \cite{hoegen2019end}\cmt{[31]}.
+Some other contextual factors that resulted in differences in perceptions of agent include the purpose of conversation (e.g.
+transactional vs.
+social) \cite{jeong2019exploring}\cmt{[10]}, anonymity of the conversation \cite{lee2020hear}\cmt{[23]}, and the sensitivity of information discussed in the interaction \cite{cox2022does}\cmt{[27]}.
+A comprehensive review to identify these contextual factors as well as to understand their effects on the perceptions of agents across various conversation architecture elements would be useful to tailor CA design for specific situations.
+
+As we gain a better understanding about the effects of a single conversation architecture element on the perceptions of agents, we can extend the research to using \textit{multiple conversation architecture elements} in an agent.
+Several papers in our reviewed corpus incorporated composite elements in an agent, such as the design of an anthropomorphized chatbot using elements such as affective language, emoticons, response delays to assess users' perceptions compared to a non-anthropomorphized chatbot \cite{seeger2021chatbots}\cmt{[35]}.
+In addition to explore the combined effects of conversation architecture elements on users' perceptions, it would also be interesting to understand the relative importance of each element on perceptions.
+Some studies analyzed the effect of modifying conversation architecture elements individually, as well as their combined effect on user's perceptions (e.g.
+\cite{habler2019effects}\cmt{[63]}\cite{lubold2016effects}\cmt{[86]}\cite{zhu2022effects}\cmt{[26]}).
+Specifically, Habler et al.
+\cite{habler2019effects}\cmt{[63]} found that the effect for social dialog is higher than the effect for prosody on the perception of agents.
 
@@
 
-%include different age considerations - cite Jaisie's paper
+The designers of conversational agents need to consider ethical implications and potential negative impacts for users.
+This section discusses three main areas of concerns related to the effect of conversation architecture on the perceptions of agents: gender stereotypes, influencing user's actions and privacy concerns.
 
-While the use of conversation architecture elements can be used to design anthropomorphized perceptions, it is important to address the potential ethical implications that could negative impact users.
-There are three items discussed in this section: societal stereotypes, influencing user's actions and privacy concerns.
+For the element of prosody, various studies in our corpus explored the effect of different pitches on the perceptions of agents.
+Even in studies that are not explicitly analyzing the effect of different gendered voices in an agent, possible stereotypes may still exist in the study.
+Based on our reviewed corpus, studies found that lower pitches commonly associated with men are considered to be more desirable, authoritative but less friendly \cite{tolmeijer2021female}\cmt{[62]}\cite{jestin2022effects}\cmt{[81]}.
+For Dubiel et al's study \cite{dubiel2020persuasive}\cmt{[60]}, the agent with lower mean pitch was selected as the more persuasive voice.
+These results may be demonstrating users' unconscious bias to select a male sounding voice as more persuasive and authoritative over female sounding voices that are commonly associated with higher pitches.
+While some guidelines recommend designing agents to be androgynous to avoid gender stereotypes \cite{ruane2019conversational}, there are limitations in creating gender-ambiguous voices.
+Currently there is no defined guidelines on what is perceived as a gender-neutral voice \cite{jestin2022effects}\cmt{[81]}.
+There is also a lack of voice generators available to generate voices that are perceived as androgynous \cite{tolmeijer2021female}\cmt{[62]}.
 
-For prosodic cues, there are various studies in our corpus exploring the effect of different pitches on different perceptions of agents.
-Even in studies not explicitly studying the effect of gendered voices in an agent, possible stereotypes may still exist in the study.
-Studies exploring the impact of gendered voices found that lower pitches usually associated with men are considered to be more desirable, authoritative but less friendly \cite{tolmeijer2021female}\cmt{[62]}\cite{jestin2022effects}\cmt{[81]}.
-For Dubiel et al's study \cite{dubiel2020persuasive}\cmt{[60]}, the prosody setting with the lower mean pitch was selected as the more persuasive voice through a user study.
-These results may be due to the unconscious bias to select a male sounding voice as more persuasive over female sounding voices that are usually using higher pitches.
-While some guidelines recommend designing agents to be androgynous to avoid gender stereotypes \cite{ruane2019conversational}, there are limitations in creating gender-ambiguous voices.
-Currently there is no defined aspects on what is perceived as a gender-neutral voice  \cite{jestin2022effects}\cmt{[81]}, and there is a lack of voice generators available to generate voices that are seen as androgynous \cite{tolmeijer2021female}\cmt{[62]}.
-
-Conversation architecture elements can be used to design perceptions of agents to make the CA more persuasive.
-This opens up the ethical issue of influencing user's attitudes and behaviours through these persuasion techniques.
+Studies have demonstrated that conversation architecture elements can be used to design perceptions of agents to make CAs more persuasive.
+This opens up the ethical issue of influencing users' attitudes and behaviours through these persuasion techniques.
 In a study by Chan et al \cite{chan2021kinvoices}\cmt{[74]}, they found that CAs using kin's voices are perceived as more credible and likeable, with a higher perceived social presence with the agent.
@@
 Andrew et al \cite{andrews2012system}\cmt{[38]} found that tailoring the personality of the CA to users will positively impact an agent's persuasiveness.
-These persuasion techniques can be beneficial to help users achieve their goals, but can also be used for harmful actions, such as when trying to get someone to believe false information for their own gain.
+These persuasion techniques can be beneficial to help users achieve their goals, but can also be used for harmful actions, such as trying to get users to believe in false information.
 
@@
 Given the natural language format of conversational agents, users may be disclosing more sensitive and personal information than needed for the interaction.
-In relationship to conversation architecture, some elements like self-disclosure and using persuasive voices resulting in higher trust, leading participants to disclose sensitive information with the agent \cite{lee2020hear}\cmt{[23]}\cite{dubiel2020persuasive}\cmt{[60]}.
+In relationship to conversation architecture, using elements like self-disclosure and persuasive voice prosody settings could result in users perceiving higher trust with the agent, leading them to disclose more sensitive information  \cite{lee2020hear}\cmt{[23]}\cite{dubiel2020persuasive}\cmt{[60]}.
 This can expose users to attacks, such as CAs using voice impersonation to ask for personal information for malicious intents \cite{chan2021kinvoices}\cmt{[74]}.
-Designing for anthropomorphized perceptions of agents requires careful consideration of privacy issues including the sensitivity of the data, who has access to it, and how to protect against nefarious users.
+Designing for perceptions of agents requires careful consideration of privacy issues including the sensitivity of the data, who has access to it, and how to protect against nefarious users.
 
-\subsection{Limitations and Future Work}
+\subsection{Limitations}
 
@@
 We may have missed literature published outside this time period, as well as in other libraries.
-Also, most of the studies in our corpus are based on lab experiments with short interactions.
+Also, most of the studies in our corpus are based on lab experiments using short interactions with users.
 The generalizability of these findings need to be verified through longer term engagements with conversational agents deployed in real world situations.
@@
 We may have missed some influential findings in these papers.
-To better understand the relationships between conversation architecture elements and the perceptions of agents, we plan to conduct future reviews in literature and user studies to understand their real-world impacts.
-
-<TODO> Add more about perception of abilities, perception of social connections, especially for linguistic cues.
+%To better understand the relationships between conversation architecture elements and the perceptions of agents, we plan to conduct future reviews in literature and user studies to understand their real-world impacts.
 
@@
 
-In this paper, we discussed the results of a systematic review of existing literature published in the ACM Digital Library on the impact of conversation architecture elements on anthropomorphized perceptions of CAs.
-Through our synthesis of our corpus of 57 papers, we have created a consistent taxonomy for perceptions of agents, as well as conversation architecture elements.
-Also, we have mapped the relationships between perceptions and conversation architecture to a generalized framework based on the impacts discussed in our reviewed corpus.
-Through our analysis, we have found that perception measures are being used inconsistently across studies, as well as other influencing factors on the perception of agents.
-We recommend future research to consider creating consistent measures that can explore different aspects of perceptions, as well as more explorations into the patterns behind other influencing factors that have impacts on anthropomorphized perceptions.
-While our research contribute to design conversation architecture to orchestrate specific anthropomorphized perceptions, we urge everyone to incorporate ethical perspectives into their design considerations.
+In this paper, we discussed the results of a systematic review of existing literature published in the ACM Digital Library on the effect of conversation architecture elements on the perceptions of CAs.
+Through our synthesis of 57 papers in our corpus, we present a framework outlining the relationships between elements of agents’ conversation architecture (dialog strategy, content affectiveness, content style and speech format) and aspects of users’ perception (interaction, ability, sociability and humanness).
+During our analysis, we found the need for consistent protocols in evaluating perceptions of agents, as measurements are inconsistent across studies.
+Further research is needed to investigate the under-explored areas in the framework, the relationship across perception aspects, the influence of contextual factors, and the effect of composite conversation architecture elements on users' perceptions.
+While our research contribute to the design conversation architecture to orchestrate specific perceptions of agent, we urge designers to incorporate ethical perspectives into their design considerations.
 

### 2023-02-18 paper.tex
reworked introduction based on AK comments

@@
 
-Conversational agents (CAs), such as Amazon Alexa or Siri, are designed to interact with humans using natural language through voice or text modalities.
-%Adoption of CAs such as Amazon Alexa or Siri (Apple) is rapidly growing in the market, with half of Internet users in United States owning one or more smart speaker devices \cite{2022comscore}.
-These conversational agents are designed to be ubiquitous, easily accessible through smartphones, tablets, laptops and smart devices.
-Since these agents interact with users using natural language, there are nuances in their communications affected by conversation architecture, which is what they say and how they say it.
-%they solicit social responses from users, encouraging users to attribute lifelike qualities, a.k.a. anthropomorphized perceptions to CAs \cite{eyssel2012if}.
+Conversational agents (CAs), such as Amazon Alexa or Google Assistant, are designed to interact with humans using natural language through voice or text modalities.
+Since these agents interact with users using natural language, conversation architecture — which refers to what a CA says and how it says it — affects how these agents interact with users.
+The effectiveness of these interactions with CAs are strongly dependent on users' perceptions of agents \cite{knijnenburg2016inferring}\cite{seeger2021chatbots}.
+According to previous research, there is a correlation between CAs' conversation architecture and users' perception of these agents.
+
+While there are various studies on how different conversation architecture elements affects agents' perceptions, there is a paucity of knowledge on the overall coverage and effects of these relationships explored in literature.
+For conversation architecture elements, The use of affective language is commonly explored, with studies finding that conversational agents are perceived as more socially present and emotionally intelligent if they use sentiment-adaptive response based on user's utterances \cite{diederich2019emulating}\cite{yang2017perceived}.
+Another commonly explored element is the use of prosody in voice-based agents, such as the use of express prosody contributing to higher perceived enjoyment and intimacy with the agent \cite{kim2020can}.
+However, there is a lack of research to synthesize these findings into an overall framework.
+One of the possible issues is the lack of clear and consistent definitions on the aspects of user's perceptions of agent and conversation architectural elements.
+
+Currently there is no systematic understanding on the elements of conversation architecture that are relevant to perceptions of agents.
+Some papers have started to examine the speech specifics that are being explored in literature, such as Clark et al.
+\cite{clark2019state} capturing different elements of system speech production for voice-based agents and categorizing them based on content, style, and other topics.
+There are also some investigations of conversation architecture elements within the broader field of studying cues that trigger a social reaction of the user towards the CA.
+Feine et al's \cite{feine2019taxonomy} paper laid the foundation to create a consistent taxonomy for these social cues.
+However, there is no comprehensive research specifically for conversation architecture elements that are relevant to user perceptions.
+
+Related to user perceptions, there is also no systematic understanding on the perceptions of agents affected by speech variations.
+Some research discussed the perceptions of agents as part of the broader scope of user experiences of CAs.
+These publications have gathered UX dimensions used to evaluate conversational agents, which include the perceptions of agents (e.g.
+empathy, humanness) alongside other assessments (e.g.
+physiological data) \cite{clark2019state}\cite{finch2020towards}.
+Some even categorized the metrics based on the type of method used, including technical measures like system error rate and perception measures like perceived social presence \cite{zheng2022ux}.
+However, these studies are assessing the general field of UX measurements and not specifically on the perceptions of agents, and do not analyze the effects of conversation architecture on these perceptions.
+
+These research gaps discussed above: the paucity of knowledge on synthesizing the effect of speech specifics on perceptions of CAs as well as the lack of systematic understanding on the elements of conversation architecture and perceptions of agents motivated us to the goal of how to design conversation architecture in order to orchestrate perceptions of conversational agents.
+First, we want to understand \textbf{(RQ1) what perception aspects of agents are being explored in relation to the effects of conversation architecture elements}.
+While there are various architecture elements of conversation architecture used in a CA's utterances, we don't have a holistic understanding of them.
+This leads to our second research question: \textbf{(RQ2) what elements of conversation architecture are relevant to the perceptions of agents?} Lastly, we want to understand the effect of conversation architecture on perceptions of agent, specifically: \textbf{(RQ3) what are the relationships between conversation architecture elements and the perceptions of CAs?}
+
+To answer these questions, we performed a comprehensive review on existing literature from 2010 to 2022 and synthesized the effect of conversation architecture elements on the perceptions of CAs based on 57 relevant papers (Figure \ref{fig:heatmap-impact}).
+We also grouped the perceptions of agents affected by conversation architecture into four categories and eleven aspects (Table \ref{tab:perceptions}), and grouped the speech variations related to perceptions of agents into four categories and eleven elements (Table \ref{tab:cues}).
+%Lastly, we coded the explored connections between conversation architecture and perceptions and synthesized their relationships into a framework.
+Through our analysis, we also found that there are inconsistencies in the assessment of perceptions across studies, as well as influencing factors other than conversation architecture that impact the perceptions of agents.
+This work contributes to the HCI community by presenting a framework that demonstrates the effect of conversation architecture on perceptions of conversational agents, as well as taxonomies for perception aspects and conversation architecture elements providing clear and consistent terms that can be used in future research.
+Together, these contributions move us one step closer to designing CAs that effectively interact with users.
+%Also, our analysis extends existing reviews on UX research of CAs \cite{clark2019state}\cite{rapp2021human}\cite{zheng2022ux} by providing a synthesized framework outlining the relationships between conversation architecture and perceptions of agents.
+With the help of this framework, we are taking the first step to understand how to design conversational agents to solicit specific social reactions from users.
+
+In the remainder of the paper, we first outline related background work, our literature review process, as well as the characteristics of the papers in our reviewed corpus.
+Following that, we describe in detail the taxonomy for the perception of agents, the taxonomy for conversation architecture element, as well as the framework on the relationships between perceptions of agents and conversation architecture.
+Finally, we discuss research challenges and opportunities as well as ethical considerations for designing conversational architecture to orchestrate perceptions of conversational agents.
+
+\section{Literature Review}
+
+* human-human vs. human-AI
+
+* anthropomorphism
 %Anthropomorphism is defined as the attribution of traits that we typically associate with being distinctly human to nonhuman entities \cite{waytz2010sees}.
@@
 \cite{kuzminykh2020genie}.
-Previous research has shown that there is a connection between conversation architecture and the perception of agents.
-Studies have found that conversational agents are perceived as more socially present and emotionally intelligent if they use affect language such as sentiment-adaptive response based on user's utterances, resulting in higher user satisfaction \cite{diederich2019emulating}\cite{yang2017perceived}.
-Also, CAs that mimic user's utterances through lexical alignment reduce users' cognitive workload, resulting in higher engagement with the interaction \cite{spillner2021talk}.
-Non-linguistic cues such as expressive prosody contribute to higher perceived intimacy with the user, as well as higher perceived enjoyment and ease of use \cite{kim2020can}.
-Although research on how conversation architecture affects agents' perceptions already exists, there is a lack of understanding on the coverage of relationships explored in literature, as well as synthesizing these findings into a generalized framework.
-One of the possible issues is the lack of clear and consistent definition on the aspects of user's perceptions of agent and conversation architectural elements.
-%However, conversational architecture design may lead to negative consequences, such as an agent with an extroverted personality may be seen as less trustworthy, as users are irritated by the system's overly familiar attitude \cite{andrews2012system}.
 
-Related to the perception aspects of agents, there have been recent efforts to systematically analyze user experience criteria used to evaluate conversational agents.
-Some review papers have created a list of dimensions used to assess conversational agents, which include the perceptions of agents (e.g.
-empathy, humanness) alongside other assessments (e.g.
-physiological data) \cite{clark2019state}\cite{finch2020towards}.
-%In Clark et al's review for the state of speech interfaces, the authors created a list the different concepts used to assess disembodied voice-based agents such as user attitudes and task performance \cite{clark2019state}.
-Other papers categorized CA assessments into themes.
+* how to synthesize
+
+* user experience evaluations of conversational agents
+%Other papers categorized CA assessments into themes.
 For example, Rapp et al.
@@
 \cite{rapp2021human} contains similar aspects to the perception towards CA in Zheng et al \cite{zheng2022ux}'s analysis.
-
-For conversation architecture elements, Feine et al \cite{feine2019taxonomy} created foundational knowledge by providing a taxonomy of social cues, which is defined as "a cue of a CA that triggers a social reaction of the user towards the CA." Elements of conversation architecture are captured in the taxonomy, alongside other social cues such as the embodied agents' appearance and movements.
-Clark et al \cite{clark2019state} had also captured conversation architecture elements under the research topic of system speech production, with similar categorizations across content, style, and other topics.
-While these papers captured conversation architecture elements as part of their broader scope of research, there exist the need for standardized definitions specifically for conversation architecture that reflects its unique characteristics.
-
-%there is existing research to systematically analyze them, like Feine et al \cite{feine2019taxonomy}'s overall framework provides consistent categories for social cues.
-However, it is unknown which conversation architecture elements have impacts on the perceptions of agents.
-Lastly, while there are various studies investigating the effect of  conversational architecture elements on the anthropomorphized perception of agents, we did not find any systematic review and analysis to generalize the findings into a usable framework.
-
-In this paper, we are addressing these research gaps by analyzing how to design conversation architecture in order to orchestrate the perceptions of conversational agents.
-First, we want to understand \textbf{(RQ1) what perception aspects of agents are being explored in relation to the effects of conversation architecture elements}.
-Various elements of conversation architecture can be used in a CA's utterances such as humour, emoticons, or lexical alignment.
-This leads to our second research question: \textbf{(RQ2) what elements of conversation architecture are relevant to the perceptions of agents?} Lastly, we want to understand the impact of conversation architecture on perceptions of agent, which leads to our third research question: \textbf{(RQ3) what are the relationships between the specifics of conversation architecture elements and the perceptions of CAs?}
-
-To answer these questions, we performed a comprehensive review of existing literature from 2010 to 2022 and synthesized findings on the impact of conversation architecture elements on the perceptions of CAs based on relevant papers (n=57).
-We collected perceptions of agents that are affected by conversation architecture,  grouped the aspects into four categories and eleven sub-categories (Table \ref{tab:perceptions}).
-We also analyzed conversation architecture related to perception of agents and grouped them into three categories and ten elements (Table \ref{tab:cues}).
-Lastly, we coded the explored connections between conversation architecture and perceptions and demonstrated the relationship into a synthesized framework (Figure \ref{fig:heatmap-impact}).
-Through our analysis, we also found that there are inconsistencies in the assessment of perceptions across studies, as well as influencing factors other than conversation architecture that impact the perceptions of agents.
-
-This work contributes to the HCI community by presenting an in-depth analysis on the affect of conversation architecture on perceptions of conversational agents.
-We created a taxonomy for perception aspects and conversation architecture elements, providing clear and consistent terms that can be used in future research.
-Also, our analysis extends existing reviews on UX research of CAs \cite{clark2019state}\cite{rapp2021human}\cite{zheng2022ux} by providing a synthesized framework outlining the relationships between conversation architecture and perceptions of agents.
-With the help of this framework, we are taking the first step to understand how to design conversational agents to solicit specific social reactions from users.
-
-In the remainder of the paper, we first outline our data collection and data analysis process, as well as the characteristics of the papers in our reviewed corpus.
-Following that, we describe in detail the taxonomy for the perception of agents, the taxonomy for conversation architecture element, as well as the framework on the relationships between perceptions of agents and conversation architecture.
-Finally, we discuss research challenges and opportunities as well as ethical considerations for designing conversational architecture to orchestrate perceptions of conversational agents.
-
-%\section{Literature Review}
-
 %\cite{finch2020towards} Towards unified dialogue system evaluation: A comprehensive analysis of current evaluation protocols
@@
 Through our analysis, we didn't find any common terms used to refer to either conversation architecture elements, or aspects of perceptions.
-As such, we kept our search term to capture articles related to conversational agents.
+As such, we generalized our search term to capture articles related to conversational agents.
 Based on search terms used in previously published literature reviews \cite{clark2019state}\cite{rapp2021human}, the following keywords are used to search for publications related to conversational user interfaces:
@@
 }
-\caption{Perception measures}
+\caption{Perception aspects}
 \label{tab:perceptions}

### 2023-02-19 paper.tex
added Related Work section

@@
 
-\section{Literature Review}
+\section{Related Work}
 
-* human-human vs. human-AI
+Communication with conversational agents is similar to communicating with humans as they both use natural languages for the interaction.
+While it is tempting to leverage components from human-human conversation in designing interactions with conversational agents, studies have demonstrated that there are differences between human-human communications and human-agent communications.
+Currently people consider CAs as a user-controlled tool rather than a social companion, with focuses on the utilitarian aspects of the conversation \cite{clark2019makes}\cmt{[1]}.
+When conversing with conversational agents, users tend to use shorter messages with limited vocabulary, adapting to the style of the agent \cite{hill2015real}.
+Also, some studies found that small talk and humour are considered unnecessary or even inauthentic in conversations with CAs, while these elements are important in scaffolding communications with human partners \cite{clark2019makes}\cmt{[1]}\cite{doyle2019mapping}\cmt{[2]}.
+There are also machine-like traits that users preferred in a CA, such as the ability to interact through multimodal media, and a machine's perceived ability to be objective and non-judgemental \cite{doyle2019mapping}\cmt{[2]}\cite{kim2022understanding}\cmt{[3]}.
+Given human-agent communications are different from human-human communications, it is important to look specifically at the design of user experiences for conversational agents.
 
-* anthropomorphism
+There have been numerous studies on the user experiences for conversational agents, and some attempts to synthesize findings across literature.
+Several papers have mapped out the current state of research for conversational agents for specific agent types (e.g.
+text-based, voice-based, polyadic) highlighting major trends, topics, methods and evaluating metrics \cite{clark2019state}\cmt{[33]}\cite{rapp2021human}\cmt{[5]}\cite{zheng2022ux}.
+Other papers looked at specific dimensions of user experiences or domains of usage, such as Van Pinxteren et al.
+\cite{van2020human} examining the effects of agents' human-like communicative behaviours on their relationships with users, and Kocaballi et al.
+\cite{kocaballi2022design} exploring the challenges and opportunities of CAs in healthcare.
+There are also publications aimed to unify concepts used in the research for CA user experiences, for instance Feine et al.
+\cite{feine2019taxonomy} creating a taxonomy of social cues, and Finch et al.
+\cite{finch2020towards} analyzing evaluation protocols for dialogue systems.
+To the best of our knowledge, there is currently no synthesis on the speech specifics of CAs, the perceptions of agents, or the relationship between them.
+
+Conversation architecture has been demonstrated to play an important role in users' perceptions of agents \cite{knijnenburg2016inferring}\cite{moussawi2021perceptions}\cite{seeger2021chatbots}\cmt{[35]}.
+Yet, little is known about the overall landscape on the how the specifics of speech variations affect these perceptions.
+Given the paucity of research in this area, this paper aims to synthesize the identified relationships between conversation architecture elements and users' perceptions of agents.
+
+%Other papers categorized CA assessments into themes.
+For example, Rapp et al.
+\cite{rapp2021human} generated themes related to how users' experience with chatbots such as experiencing the chatbot including assessments on expectation, perception, satisfaction etc.
+Most recently, Zheng et al's literature review on the UX research of CAs \cite{zheng2022ux} categorized the metrics based on the type of method used, including technical measures like system error rate and perception measures like perceived social presence.
+However, existing studies use different terminologies and categories across aspects of perception.
+As an illustration, it is unclear if the theme of experiencing the chatbot from Rapp et al.
+\cite{rapp2021human} contains similar aspects to the perception towards CA in Zheng et al \cite{zheng2022ux}'s analysis.
+%\cite{finch2020towards} Towards unified dialogue system evaluation: A comprehensive analysis of current evaluation protocols
+
 %Anthropomorphism is defined as the attribution of traits that we typically associate with being distinctly human to nonhuman entities \cite{waytz2010sees}.
@@
 \cite{kuzminykh2020genie}.
-
-* how to synthesize
-
-* user experience evaluations of conversational agents
-%Other papers categorized CA assessments into themes.
-For example, Rapp et al.
-\cite{rapp2021human} generated themes related to how users' experience with chatbots such as experiencing the chatbot including assessments on expectation, perception, satisfaction etc.
-Most recently, Zheng et al's literature review on the UX research of CAs \cite{zheng2022ux} categorized the metrics based on the type of method used, including technical measures like system error rate and perception measures like perceived social presence.
-However, existing studies use different terminologies and categories across aspects of perception.
-As an illustration, it is unclear if the theme of experiencing the chatbot from Rapp et al.
-\cite{rapp2021human} contains similar aspects to the perception towards CA in Zheng et al \cite{zheng2022ux}'s analysis.
-%\cite{finch2020towards} Towards unified dialogue system evaluation: A comprehensive analysis of current evaluation protocols
 

### 2023-02-21 archive/old.tex
restructured manuscript

%%%%%
\subsection{Perception of Interaction with an Agent}
%%%%%

This section discusses user's perception of their interaction with a conversational agent. \textbf{\textit{Engagement, accuracy, and satisfaction are the three variables used to evaluate how people perceive interactions with CAs}}. \textit{Engagement} measures user's attitude towards the task they are achieving through working with the agent, including how easy it is to use the system and its perceived usefulness, convenience and helpfulness for the user. Additionally, it includes the user's emotional responses to the interaction, such as annoyance, enjoyment, and irritation. \textit{Accuracy} measures whether the agent was perceived to be able to provide the correct answers in response to the user. \textit{Satisfaction} measures the whether the agent was able to fulfill user's expectations through the interaction encounter.

Out of the list of publications that were evaluated, there is a good coverage on the effect of conversational architecture elements on the perception of interaction with an agent. Out of the three factors, engagement is the most frequently used measure to assess interaction quality, followed by satisfaction. Perceived accuracy of the agent is rarely used within literature, with only a few papers measuring this perception.

[TODO] * Associations between conversational architecture elements and perceptions
For both text and voice modalities, lexical alignment had a positive effect on engagement by decreasing the cognitive load of users.

%%
\subsubsection{Engagement}
%%
For the elements in the language content category of conversational architecture, the use \textbf{self-disclosure} by agent had a positive effect on engagement, as the participants using the chatbot with small talk and self disclosure reported higher enjoyment after 3 weeks of daily interaction \cite{lee2020hear}\cmt{[23]}. There are mixed results on the effect of \textbf{affective language} on engagement. One study found that CAs that uses encouraging words are rated as easier to use \cite{healey2013relating}\cmt{[39]}. However, the user of words with increased lexical emotional expressiveness did not have an effect on engagement \cite{zhu2022effects}\cmt{[26]}. The use of affective language may lead to negative impacts on engagement, as a system that uses an extroverted and overly familiar words is irritating to users. On the use of \textbf{humour}, survey result did not show a significant difference in the level of enjoyment, but qualitative feedback from participants reflected that humour made the interaction more engaging and immersive \cite{ceha2021can}\cmt{[57]}.

For the elements in the language style category of conversational architecture, mimicking users' utterances through \textbf{lexical alignment} yielded positive results. Multiple studies have found that being lexically aligned to users resulted in lower perceived cognitive demand and decreased perceived workload \cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}\cite{spillner2021talk}\cmt{[18]}. Interestingly, perceived lower cognitive demand did not have significant impacts on ease of use \cite{linnemann2018can}\cmt{[15]} or annoyance \cite{huiyang2022improving}\cmt{[17]}. In Spillner et al's study \cite{spillner2021talk}\cmt{[18]}, both conditions of aligning words as well as aligning words and grammatical structure to user utterances resulted in higher perceived user engagement from participants.

For the elements in the presentation format category of conversational architecture, auditory aspects of \textbf{prosody} such as speech rate and expressive tone of voice had different impacts on engagement. In one study, users enjoyed their interaction with the CA and perceived it as easier to use, as they felt the level of agent's social behaviour is matched with their emotional states \cite{kim2020can}\cmt{[24]}. However, another study did not find any impact of emotional expressive of voice on the user engagement \cite{zhu2022effects}\cmt{[26]}. On the speech rate for CAs, a normal rate is perceived as more convenient compared to a faster rate of speech \cite{choi2020nobody}\cmt{[54]}. On the visual presentation side, the study from Westerman et al. \cite{westerman2019believe}\cmt{[9]} showed that the use of \textbf{typos} by chatbots negatively impacted the perception of working with a CA on the specific task, while the use of \textbf{capitalization} did not yield any significant impacts.

\textbf{Content: Humour}
* No overall significant difference between conventional method vs. agent using humour for enjoyment. Specifically, men enjoyed the agent's jokes more than women.  \cite{miyamoto2017improving}\cmt{[46]}.
* Motivation to continue the conversation significant increased after day 2 for the humorous agent \cite{go2021conversational}\cmt{[80]}

\textbf{Style: Language Formality}
* Users spent more time with the Shakespearean chatbot version with more non-task related user inputs. Enjoyment was measured but no report \cite{elsholz2019exploring}\cmt{[61]}
* commanding/formal wording was rated significantly more useful than the informal wording; while the informal wording was rated as significantly more annoying than the commanding/formal wording. No impact on desirability. \cite{jestin2022effects}\cmt{[81]}
* High conscientiousness (formal) and high extroversion (casual) chatbot personality have higher user engagement. \cite{moilanen2022measuring}\cmt{[82]}
* Analysis of ease of use reveals that there are no significant main effects for platform questionnaire vs. chatbot, and conversational style formal vs. casual.\cite{kim2019comparing}\cmt{[89]}

\textbf{Social talk / elaborate}
* Not significant importance between introvert and extrovert agents. But the machine-like speaking agent is rated lower. \cite{roy2021users}\cmt{[71]}
* usefulness depended on the task \cite{haas2022keep}\cmt{[78]}
* High extroversion chatbot personality have the higher user engagement \cite{moilanen2022measuring}\cmt{[82]}

\textbf{Disfluency}
* Using moderately repetitive utterances resulted in higher desire to continue the dialogue with the agent. \cite{yang2021effect}\cmt{[72]}
* Interjections did not have any impacts of cognitive workload \cite{ceha2022expressive}\cmt{[77]}

\textbf{Proactive}
* Different framing has impacts on the perceived disruptiveness of the agent. \cite{xiao2021let}\cmt{[73]}

\textbf{Prosody}
* No impact on annoying, undesirable, useful \cite{jestin2022effects}\cmt{[81]}
* Dialog-style conversation using prosodic cues is rated as less easy to understand than the reading-style \cite{misu2011toward}\cmt{[83]}

\textbf{Combined}
* (Extraverted: emoticons, self-disclosure, talkative, affective language / Introverted: formal style, less talkative) all personalities have similar usability ratings. Also, users have greater desire to interact with the extraverted chatbot \cite{volkel2022user}\cmt{[75]}
* (Politeness: affective language + elaborateness of speech) no impact on usability \cite{hu2022polite}\cmt{[76]}

%%
\subsubsection{Accuracy}
%%
There are only a few studies that measured the perception of accuracy of conversational agents for an interaction. A couple of studies reported the effect of the use of language style of \textbf{lexical alignment}. One study of a text-based CA resulted in higher perceived response accuracy \cite{huiyang2022improving}\cmt{[17]}, while the other study with voice-based CA did not find any significant differences \cite{linnemann2018can}\cmt{[15]}. Dubiel et al.'s study \cite{dubiel2020persuasive}\cmt{[60]} on \textbf{prosody} did not find any significant differences on the rating for accuracy across agents with different speech rates and pitch.

\textbf{Social talk}
* Introverted agent is more efficient. \cite{roy2021users}\cmt{[71]}
* Efficiency depended on the task \cite{haas2022keep}\cmt{[78]}

\textbf{Language Formality}
* commanding/formal wording was rated significantly more effective than informal wording \cite{jestin2022effects}\cmt{[81]}

\textbf{Prosody}
* No impact on effectiveness \cite{jestin2022effects}\cmt{[81]}

\textbf{Repair}
* One reason for choosing repair strategy preference is efficiency and efficacy. \cite{ashktorab2019resilient}\cmt{[88]}

%%
\subsubsection{Satisfaction}
%%
Several research have investigated into how the usage of \textbf{affective language} impacts the satisfaction people feel when interacting with a CA. Compared to a text-based chatbot with a static and neutral response, users reported higher service encounter satisfaction conversing with a chatbot that responded with dynamic, sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}. However, the same effect is not observed for a voice-based CA as Yang et al. did not find any difference in user satisfaction rating between the emotional-expressing agent vs. non-emotional expressing agent \cite{yang2017perceived}\cmt{[44]}. On the language style used by CAs, both \textbf{disfluency} \cite{pfeifer2009should}\cmt{[12]} and \textbf{emoticons} \cite{wilhelm2022keep}\cmt{[28]} did not have any significant effects on user satisfaction.

Studies have found that presentation formats have significant effects on user satisfaction. In Choi et al's study \cite{choi2020nobody}\cmt{[54]} on the speech rate aspect o f\textbf{prosody} for a voice-based agent, they found that user satisfaction is higher for the default rate compared to using a faster rate. User feedback reflected that the faster rate was mechanical and harder to understand. For text-based chatbots, the addition of \textbf{response delay} increased the perception of overall user satisfaction, as the timing is similar to human-human communications and felt right \cite{gnewuch2018faster}\cmt{[19]}.

\textbf{Style: Language Formality}
* Modern language had higher usability score compared to Shakespearean language \cite{elsholz2019exploring}\cmt{[61]}
* There is no significant effect on customer satisfaction of the CA between low-status and high-status languages. \cite{habler2019effects}\cmt{[63]}

\textbf{Format: Prosody}
* There is no significant effect on customer satisfaction of the CA between male-gendered and female-gendered voices. \cite{habler2019effects}\cmt{[63]}

\textbf{Social talk}
* Not significant importance between introvert and extrovert agents. But the machine-like speaking agent is rated lower. \cite{roy2021users}\cmt{[71]}

\textbf{Combined}
* (Politeness: affective language + elaborateness of speech) no impact on user satisfaction \cite{hu2022polite}\cmt{[76]}

%%%%%
\subsection{Perception of Agent's Ability}
%%%%%

This section discusses how user perceives the agent's ability in conditions with different conversational architecture elements. It is aiming at measuring the differences in the perception with similar system's capabilities. Out of the two variables used to evaluate this perception, \textit{Intelligence} measures whether the agent is knowledgeable, sensible, and is seem as overall intelligent. \textit{Competence} on the other hand measures the overall perception on how well the agent is handling the conversation. Out of the list of publications that were evaluated, there are only a few papers that measured the perceived ability of an agent.

\textit{To be incorporated}

\textbf{Repair}
* perceived quality of the interaction is muhc higher in repair condition when the agent made a mistake; rating is lower if no mistake was present. \cite{cuadra2021my}\cmt{[67]}

%%
\subsubsection{Intelligence}
%%

On analyzing the impact of different language styles on the perception of intelligence, a couple of papers studied the effect of including \textbf{disfluencies} into agent's speech. One paper found that there is no significant impact on how knowledgeable the agent is perceived as \cite{pfeifer2009should}\cmt{[12]}. Another study showed that using fillers like "um" and "uh" decreased the agent's perceived intelligence overall \cite{jeong2019exploring}\cmt{[10]}. Upon further analysis, the authors noticed a difference between task vs. social conversations, as users perceive the intelligence to be lower in task-oriented situations, but the perception of intelligence is slightly increased in social-oriented situations. The use of \textbf{lexical alignment} did not seem to impact user's perception of an agent's intelligence, as there is no significant difference reported in the agent's domain knowledge between the aligned vs. non-aligned conditions.

On the impact of presentation format, Dubiel et al's study on \textbf{prosody} using different speech rates and pitches did not yield any significant differences on the agent rating for knowledgeable.

\textbf{Prosody}
* VA using kin's voice is rated as more intelligent. \cite{chan2021kinvoices}\cmt{[74]}

\textbf{Repair}
* One reason for choosing repair strategy preference is perceived intelligence and capability. \cite{ashktorab2019resilient}\cmt{[88]}

%%
\subsubsection{Competence}
%%

There are only a couple of papers that discussed the impact of conversational architecture elements on the perception of competence. For \textbf{affective language} in the language style content category, participants rated the agent higher in competence when it has higher patiency and expressed its feelings to users. In Cox et al's study on \textbf{formality}, the authors did not find a significant difference in competence between using casual vs. formal conversational styles.

\textbf{Style: Language Formality}
*  Low-status language resulted in higher achieved performance ratings \cite{habler2019effects}\cmt{[63]}

\textbf{Format: Prosody}
* There is no significant effect on perceived performance of the CA between male-gendered and female-gendered voices. \cite{habler2019effects}\cmt{[63]}
* For expertise, multilingual students rated higher the non-native English-speaking virtual human. \cite{feijoo2021effects}\cmt{[70]}

\textbf{Format: Proactivity}
* Certain proactive styles like notification strategy (conservatively proactive, letting participants know that the agent has found a solution) was evaluated as significantly higher perceived competence compared to the non-strategy. \cite{kraus2020effects}\cmt{[64]}

%%%%%
\subsection{Perception of Social Connection with an Agent}
%%%%%

This section discusses user's perception of their social connection with a conversational agent. Social presence, conversation tone, and intimacy are the three variable used to evaluate this perception. \textit{Social presence} measures user's perceived social distance with an agent, such as social presence, connectedness, and psychological distance. \textit{Conversation tone} measures user perceptions on the way an agent is speaking to them, such as appropriateness of tone, empathetic, or emotionally expressive. \textit{Intimacy} measures the quality of relationship users have with CAs, such as intimacy, social attraction, or similarity with each other.

Out of the list of publications that were evaluated, there is overall consensus that the use of affective language positive affects the perception of social connection with an agent. Conversational architecture elements related to the format of the conversation, like adding response delays, or changing the pitch of speech are commonly investigated for perception of social connection with an agent. There are only a few papers exploring the effect of language styles on the perceived social connection with an agent.

%%
\subsubsection{Social Presence}
%%
For conversational architecture elements related to language content, studies have shown the use of \textbf{affective language} increased the perception of social presence of an agent. In Diederich et al's study, participants conversing with a text-based agent using dynamic, sentiment-adaptive responses reported a higher social presence compared to a CA that provides static, neutral responses \cite{diederich2019emulating}\cmt{[25]}. In another study, participants felt closer to the agent psychologically when the CA expressed its feelings \cite{lee2019s}\cmt{[55]}. On the use of \textbf{humour}, Lee et al. did not find any significant difference in social presence between the humourous and non-humourous agent \cite{lee2019s}\cmt{[55]}.

For text-based conversational agents, including a \textbf{response delay} increased users' perception of social presence of the agent, with participants feeling a sense of human contact and sociability with the agent \cite{kim2020can}\cmt{[24]}. Westerman et al. \cite{westerman2019believe}\cmt{[9]} studied the presence of typos and capitalized words in a text-based agent's responses. They found the inclusion of \textbf{typos} negatively impacted the social distance and connection with an agent, while \textbf{capitalization} did not have any significant effects. On the effect \textbf{prosody} on a voice-based agent, using an affective tone of voice resulted in perceived higher social connectedness with the agent \cite{kim2020can}\cmt{[24]}.

\textbf{Content: Affective Language (Voice)}
* Model aiming to elicit position emotions from users received higher emotional connection \cite{lubis2019positive}\cmt{[43]}

\textbf{Format: Response Delay}
* Delayed response is associated with higher social presence \cite{gnewuch2022opposing}\cmt{[20]}

\textbf{Content: Affective language and Style: Disfluency}
* Rated higher that agent listened openly to participants' emotions, as that agent can feel waht the user is feeling. \cite{hu2021enhancing}\cmt{[56]}
* social condition didn't have an impact on social presence \cite{lubold2016effects}\cmt{[86]}

\textbf{Prosody}
* VA using kin's voice is rated as more socially present and closer psychological connection with user. \cite{chan2021kinvoices}\cmt{[74]}
* voice plus social condition has higher social presence than the social condition \cite{lubold2016effects}\cmt{[86]}

\textbf{Humour}
* Familiarity with the agent is rated higher at the end of the study (day 7) compared to non-humorous agent \cite{go2021conversational}\cmt{[80]}

\textbf{Laughter}
* Laughter had no impact on social presence of an agent \cite{niewiadomski2013laugh}\cmt{[85]}

%%
\subsubsection{Conversation Tone}
%%

The use of \textbf{affective language} has a significant affect on the perception of the conversation tone by the agent. Multiple studies have found that agents conversing with more affective words are seen as more emotionally expressive and empathetic \cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}. This effect has been observed across modalities in both text-based as well as voice-based conversational agents.

On the style of language used by the agent, \textbf{formality} did not seem to impact the conversation tone of agent as Cox et al. \cite{cox2022does}\cmt{[27]} did not find any significant difference between casual and formal conversational styles for appropriateness of tone. The speech format of \textbf{prosody} seem to have an impact on the conversation tone, as a CA speaking with a lower pitch and slower speech rate is rated as more persuasive compared to other voice settings \cite{dubiel2020persuasive}\cmt{[60]}. However, there was no significant difference in how powerful or bold the agent's tone was perceived across various prosody settings.

\textbf{Content: Affective language and Style: Disfluency}
Respond with empathy to the user. \cite{hu2021enhancing}\cmt{[56]}

\textbf{Disfluency}
* Using moderately repetitive utterances resulted in higher perceived empathy. \cite{yang2021effect}\cmt{[72]}

\textbf{Language Formality}
* commanding/formal wording was rated significantly more appropriate and assertive than informal wording \cite{jestin2022effects}\cmt{[81]}

\textbf{Prosody}
* No impact on appropriate and assertive \cite{jestin2022effects}\cmt{[81]}
* Dialog-style conversation using prosodic cues is rated as more appropriate than the reading-style \cite{misu2011toward}\cmt{[83]}

%%
\subsubsection{Intimacy}
%%
On the use of language content, a conversational agent that included \textbf{self-disclosure} when conversing with participants resulted in higher level of intimacy over time than CAs that did not self disclose \cite{lee2020hear}\cmt{[23]}. On the other hand, using the style of \textbf{lexical alignment} by using the words that were already used by the participant did not result in higher quality of relationship with the agent \cite{linnemann2018can}\cmt{[15]}.

There are several studies investigating the effect of conversational format on intimacy with a CA. Specifically on voice \textbf{prosody}, using an affective tone of voice increased the perceived intimacy and similarity with an agent \cite{kim2020can}\cmt{[24]}. Comparing voice agents with different \textbf{speech rates}, users rated the default rate as more intimate than a faster rate of speech \cite{choi2020nobody}\cmt{[54]}, noting that the default rate is more human-like and natural. Westerman et al's study on different text formats of conversation \cite{westerman2019believe}\cmt{[9]} showed that \textbf{typos} negatively impacted the perceived social attraction of the agent, while \textbf{capitalization} did not have any impacts.

\textbf{Disfluency}
* Interjections did not have any impacts of quality of relationship, but it did result in higher emotional rapport. \cite{ceha2022expressive}\cmt{[77]}

\textbf{Affective Language}
* social condition didn't have an impact on social presence \cite{lubold2016effects}\cmt{[86]}

\textbf{Prosody}
* voice and social condition didn't have an impact on social presence \cite{lubold2016effects}\cmt{[86]}

%%%%%
\subsection{Perception of Agent's Humanness}
%%%%%

This section discusses user's perception of the agent's humanness aspects. Human-likeness, personality traits, and trustworthiness are the three variable used to evaluate this perception. \textit{Human-likeness} measures the agent's similarity to humans as well assessed naturalness of interaction. \textit{Personality traits} measures perceptions of the agent's characteristics such as likeability, warmth, and friendliness. \textit{Trustworthiness} measures if users feel they can trust an agent, and whether the agent is perceived of being truthful.

Out of the list of publications that were evaluated, many papers exploring the impact of language content as well as language style have measurements related to the perception of an agent's humanness. There seems to be fewer studies looking into the effect of conversation format on the perception of agent's humanness, as our reivew only found two studies related to voice prosody. Out of reviewed conversational architecture elements, one consistent finding is that the style of being lexically aligned with user's utterance did not have any impact on the perception of agent's humanness.

%%
\subsubsection{Human-likeness}
%%

On the use of \textbf{affective language}, one study found that CAs with dynamic, sentiment-adaptive responses is perceived as more human than a CA that provides static, neutral responses \cite{diederich2019emulating}\cmt{[25]}. Another study using more emotional expressive words in conversation did not find any significant impact on the perceived human-likeness of an agent \cite{zhu2022effects}\cmt{[26]}.

Different language styles have different impacts on user perceptions. On language \textbf{formality}, agents using normal style was rated as more human-like compared to formal styles of conversation \cite{ouchi2019should}\cmt{[59]}. \textbf{Disfluencies} did not seem to have a significant impact on the perceived humanness or naturalness of an agent \cite{jeong2019exploring}\cmt{[10]}\cite{pfeifer2009should}\cmt{[12]}. However, one study noticed a non-significant but positive trend in user's evaluation of the agent using fillers as being more human-like \cite{jeong2019exploring}\cmt{[10]}.

On the impact of different conversation formats, Zhu et al. did not find a significant effect of \textbf{prosody} on the perception of humanness between agent using expressive vs. non-expressive voices. For text-based CAs, the use of \textbf{typos} made the agent seem less human, while the use of \textit{capitalization} did not have any impacts on the perception of humanness \cite{westerman2019believe}\cmt{[9]}. Lastly, adding a \textbf{response delay} to a CA has a significant positive effect in the perceived humanness of the agent \cite{gnewuch2018faster}\cmt{[19]}.

\textbf{Style: Disfluency}
* (Voice) No significant difference in naturalness rating for About Myself text, but showed that naturalness is higher for fluent system compared to disfluent speech \cite{wester2015artificial}\cmt{[14]}.

\textbf{Prosody}
* VA using kin's voice is rated as more human-like. \cite{chan2021kinvoices}\cmt{[74]}
* Dialog-style conversation using prosodic cues is rated as less human-like than the reading-style \cite{misu2011toward}\cmt{[83]}

\textbf{Social talk / Elaborateness}
* Naturalness depends on the task \cite{haas2022keep}\cmt{[78]}

\textbf{Language Formality}
* No impact on artificial or humanlike perceptions \cite{jestin2022effects}\cmt{[81]}

\textbf{Prosody}
* Matthew voice is rated as least artificial  \cite{jestin2022effects}\cmt{[81]}

\textbf{Laughter}
* Laughter was not rated as natural in an agent \cite{niewiadomski2013laugh}\cmt{[85]}

\textbf{Combined}
* (Politeness: affective language + elaborateness of speech) no impact on likability, but positive politeness interactions are rated as more polite \cite{hu2022polite}\cmt{[76]}

\textbf{Repair}
* One reason for choosing repair strategy preference is naturalness. \cite{ashktorab2019resilient}\cmt{[88]}

%%
\subsubsection{Personality Traits}
%%

There are significant difference found in the effect of language content on the perception of agent's personality traits. Conversational agents using emotionally expressive words are rated as more likable \cite{zhu2022effects}\cmt{[26]} and warm \cite{lee2019s}\cmt{[55]}. In Healey et al's study \cite{healey2013relating}\cmt{[39]}, there is a significant difference in the variances of the responses for friendliness of the agent between the agent using encouraging words compared to neutral utterances. As with the use of \textbf{humour}, participants rated the humorous agent as having a sense of humor, but it was not rated as more likable \cite{ceha2021can}\cmt{[57]}.

On the impact of language style, various studies on \textbf{lexical alignment} showed that there is no significant impact on the perception of the personality traits related to likability \cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}, friendliness \cite{spillner2021talk}\cmt{[18]}, or politeness \cite{spillner2021talk}\cmt{[18]}. Studies on the \textbf{formality} of language has demonstrated that casual conversational style is perceived as warmer than formal style \cite{cox2022does}\cmt{[27]}. Also agents using a normal style as compared to a formal style is perceived as more friendly, fun, and kind \cite{ouchi2019should}\cmt{[59]}. As for the use of \textbf{disfluency}, there was no statistical significance found in the perceived likability rating \cite{jeong2019exploring}\cmt{[10]}\cite{pfeifer2009should}\cmt{[12]}. Jeong et al. \cite{jeong2019exploring} found a significant interaction effect between disfluency (using fillers) and the context of the conversation (task vs. social), as users considered agents using fillers as entertaining and fun in social conversations, but inappropriate in task oriented situations.

In the list of reviewed papers, there was only one study measuring the perceived trustworthiness of an agent based on different conversational format of \textbf{prosody}. Dubiel et al. found that an agent using slower speech rate is perceived as more trustworthy as compared to other voice prosody settings \cite{dubiel2020persuasive}\cmt{[60]}.

\textit{To be incorporated}

\textbf{Content: Humour}
* An agent that uses humourous content is assessed to be more funny \cite{khooshabeh2011does}\cmt{[37]}.

\textbf{Style: Disfluency}
* (Voice) Both About Myself and Speed Dating ratings has shown system scored significantly differently on the Big-5 personality traits. Disfluency makes the voice sound more neurotic, less open, less extrovert and less conscientious \cite{wester2015artificial}\cmt{[14]}.

\textbf{Format: Prosody}
* Low voice pitch rated not as friendly as the other ones. No impact on other traits like assertive and politeness. \cite{tolmeijer2021female}\cmt{[62]}
* VA using kin's voice is rated as more likable. \cite{chan2021kinvoices}\cmt{[74]}
* No impact on entertaining or friendly  \cite{jestin2022effects}\cmt{[81]}

\textbf{Repair}
* When VA corrected in the condition it didn't make a mistake, it is seen as anxious. Otherwise it is perceived as calm and emotionally stable. \cite{cuadra2021my}\cmt{[67]}
* One reason for choosing repair strategy preference is politeness. \cite{ashktorab2019resilient}\cmt{[88]}

\textbf{Social talk}
* Using more social talk is positive correlated with extroversion. \cite{volkel2021manipulating}\cmt{[68]}
* Not significant importance between introvert and extrovert agents. \cite{roy2021users}\cmt{[71]}
* Likability depends on the task \cite{haas2022keep}\cmt{[78]}

\textbf{Language Formality}
* Informal wording was rated as strongly more entertaining and friendly than the commanding/formal wording. \cite{jestin2022effects}\cmt{[81]}

\textbf{Agreeableness}
* Being highly confrontational (less agreeable) is rated as less conscientious \cite{volkel2021manipulating}\cmt{[68]}
* Designing for more agreeable resulted in personality rated as more agreeable \cite{volkel2021examining}\cmt{[69]}

\textbf{Combined}
* (Extraverted: emoticons, self-disclosure, talkative, affective language / Introverted: formal style, less talkative) extraverted personality rated as more extraverted \cite{volkel2022user}\cmt{[75]}

%%
\subsubsection{Trustworthiness}
%%

For the use of language content, agents using more \textbf{affective language} is seen as less trustworthy, as users felt it was being overly familiar \cite{andrews2012system}\cmt{[38]}. On the other hand, users conversing with agents that used \textbf{self-disclosure} content reported more trust towards the agent compared to the non disclosure group \cite{lee2020hear}\cmt{[23]}.

None of the studies included in this review has found any significant impact of language style, \textbf{lexical alignment} \cite{hoegen2019end}\cmt{[31]}\cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}, \textbf{disfluency} \cite{pfeifer2009should}\cmt{[12]}, and \textbf{emoticons} \cite{wilhelm2022keep}\cmt{[28]} on the perceived trustworthiness of CAs. Similarly for conversational format, there is not significant difference on the rating for truthfulness of the agent across different voice \textbf{prosody} settings \cite{dubiel2020persuasive}\cmt{[60]}.

\textbf{Format: Prosody}
* No significant difference in trust ratings across different voice prosody settings with differences in pitch. \cite{tolmeijer2021female}\cmt{[62]}
* No impact on trustworthiness  \cite{jestin2022effects}\cmt{[81]}

\textbf{Format: Proactivity}
* Overall trust in the system did not differ significantly. The intervention style is less trusted than conservative strategies - too obstructive and imposing. Proactive should be subtle  \cite{kraus2020effects}\cmt{[64]}

\textbf{Language Formality}
* No impact on trustworthiness \cite{jestin2022effects}\cmt{[81]}

### 2023-02-21 figures/fig-heatmap_coverage.tex
restructured manuscript

--- 2023-02-18 paper.tex
@@
-%% Manuscript for the effect of designed conversational architecture on the perception of agents
-%%
-%% The first command in your LaTeX source must be the \documentclass command.
-\documentclass[sigconf,screen,review, anonymous]{acmart}
-
-\usepackage[linewidth=1pt]{mdframed}
-\usepackage{lipsum}
-\usepackage{multirow}
-\usepackage{graphicx}
-\usepackage{booktabs}
-\usepackage{makecell}
-
-\newcommand{\cmt}[1]{}%{\ignorespaces}
-
-%% NOTE that a single column version may be required for 
-%% submission and peer review. This can be done by changing
-%% the \doucmentclass[...]{acmart} in this template to 
-%% \documentclass[manuscript,screen]{acmart}
-%% 
-%% To ensure 100% compatibility, please check the white list of
-%% approved LaTeX packages to be used with the Master Article Template at
-%% https://www.acm.org/publications/taps/whitelist-of-latex-packages 
-%% before creating your document. The white list page provides 
-%% information on how to submit additional LaTeX packages for 
-%% review and adoption.
-%% Fonts used in the template cannot be substituted; margin 
-%% adjustments are not allowed.
-%%
-%%
-%% \BibTeX command to typeset BibTeX logo in the docs
-\AtBeginDocument{%
-  \providecommand\BibTeX{{%
-    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
-
-%% Rights management information.  This information is sent to you
-%% when you complete the rights form.  These commands have SAMPLE
-%% values in them; it is your responsibility as an author to replace
-%% the commands and values with those provided to you when you
-%% complete the rights form.
-\setcopyright{acmcopyright}
-\copyrightyear{2023}
-\acmYear{2023}
-\acmDOI{XXXXXXX.XXXXXXX}
-
-%% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[Conference acronym 'XX]{Make sure to enter the correct
-  conference title from your rights confirmation email}{June 03--05,
-  2018}{Woodstock, NY}
-%
-%  Uncomment \acmBooktitle if th title of the proceedings is different
-%  from ``Proceedings of ...''!
-%
-%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
-%  June 03--05, 2018, Woodstock, NY} 
-\acmPrice{15.00}
-\acmISBN{978-1-4503-XXXX-X/18/06}
-
-%%
-%% Submission ID.
-%% Use this when submitting an article to a sponsored event. You'll
-%% receive a unique submission ID from the organizers
-%% of the event, and this ID should be used as the parameter to this command.
-%%\acmSubmissionID{123-A56-BU3}
-
-%%
-%% end of the preamble, start of the body of the document source.
-\begin{document}
-%TC:ignore
-
-%%
-%% The "title" command has an optional parameter,
-%% allowing the author to define a "short title" to be used in page headers.
-% \title[short title]{How to Make Pinocchio a Real Boy? Designing conversational architecture elements to achieve desirable anthropomorphized perceptions}
-\title{The Bot on Speaking Terms: The Effects of Conversation Architecture on Perceptions of Conversational Agents}
-
-%%
-%% The "author" command and its associated commands are used to define
-%% the authors and their affiliations.
-%% Of note is the shared affiliation of the first two authors, and the
-%% "authornote" and "authornotemark" commands
-%% used to denote shared contribution to the research.
-\author{Christina Wei}
-\email{christina.wei@mail.utoronto.ca}
-\affiliation{%
-  \institution{University of Toronto}
-  \city{Toronto}
-  \country{Canada}
-}
-
-\author{Young-Ho Kim}
-\email{ygho.kim@navercorp.com}
-\affiliation{%
-  \institution{Naver Corporation}
-  \city{Seoul}
-  \country{Korea}
-}
-
-\author{Anastasia Kuzminykh}
-\email{anastasia.kuzminykh@utoronto.ca}
-\affiliation{%
-  \institution{University of Toronto}
-  \city{Toronto}
-  \country{Canada}
-}
-
-%%
-%% By default, the full list of authors will be used in the page
-%% headers. Often, this list is too long, and will overlap
-%% other information printed in the page headers. This command allows
-%% the author to define a more concise list
-%% of authors' names for this purpose.
-\renewcommand{\shortauthors}{Wei, Kim, Kuzminykh} %It will be automatically anonymized through the document class property anonymous
-
-%%
-%% The abstract is a short summary of the work to be presented in the
-%% article.
-\begin{abstract}
-Conversational agents mimic natural conversation to interact with users.
-Since the effectiveness of interactions strongly depends on users’ perception of agents, it is crucial to design agents’ behaviors to provide the intended user perceptions.
-Research on human-agent and human-human communication suggests that speech specifics are associated with perceptions of communicating parties, but there is a lack of systematic understanding of how speech specifics of agents affect users' perceptions.
-To address this gap, we present a framework outlining the relationships between elements of agents’ conversation architecture (dialog strategy, content affectiveness, content style and speech format) and aspects of users’ perception (interaction, ability, sociability and humanness).
-Synthesized based on literature reviewed from the domains of HCI, NLP and linguistics (n=57), this framework demonstrates both the identified relationships and the areas lacking empirical evidence.
-We discuss the implications of the framework for conversation design and highlight the inconsistencies with terminology and measurements.
-\end{abstract}
-
-%%
-%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
-%% Please copy and paste the code instead of the example below.
-%%
-%\begin{CCSXML}
-%<ccs2012>
-% <concept>
-%  <concept_id>10010520.10010553.10010562</concept_id>
-%  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
-%  <concept_significance>500</concept_significance>
-% </concept>
-% <concept>
-%  <concept_id>10010520.10010575.10010755</concept_id>
-%  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-%  <concept_significance>300</concept_significance>
-% </concept>
-% <concept>
-%  <concept_id>10010520.10010553.10010554</concept_id>
-%  <concept_desc>Computer systems organization~Robotics</concept_desc>
-%  <concept_significance>100</concept_significance>
-% </concept>
-% <concept>
-%  <concept_id>10003033.10003083.10003095</concept_id>
-%  <concept_desc>Networks~Network reliability</concept_desc>
-%  <concept_significance>100</concept_significance>
-% </concept>
-%</ccs2012>
-%\end{CCSXML}
-
-%\ccsdesc[500]{Computer systems organization~Embedded systems}
-%\ccsdesc[300]{Computer systems organization~Redundancy}
-%\ccsdesc{Computer systems organization~Robotics}
-%\ccsdesc[100]{Networks~Network reliability}
-
-\ccsdesc{TBD}
-
-%%
-%% Keywords. The author(s) should pick words that accurately describe
-%% the work being presented. Separate the keywords with commas.
-\keywords{conversational agents, user perception, conversational architecture, anthropomorphized perceptions}
-
-%%\received{20 February 2007}
-%%\received[revised]{12 March 2009}
-%%\received[accepted]{5 June 2009}
-
-%%
-%% This command processes the author and affiliation and title
-%% information and builds the first part of the formatted document.
-\maketitle
-%TC:endignore
-
-\section{Introduction}
-
-Conversational agents (CAs), such as Amazon Alexa or Google Assistant, are designed to interact with humans using natural language through voice or text modalities.
-Since these agents interact with users using natural language, conversation architecture — which refers to what a CA says and how it says it — affects how these agents interact with users.
-The effectiveness of these interactions with CAs are strongly dependent on users' perceptions of agents \cite{knijnenburg2016inferring}\cite{seeger2021chatbots}.
-According to previous research, there is a correlation between CAs' conversation architecture and users' perception of these agents.
-
-While there are various studies on how different conversation architecture elements affects agents' perceptions, there is a paucity of knowledge on the overall coverage and effects of these relationships explored in literature.
-For conversation architecture elements, The use of affective language is commonly explored, with studies finding that conversational agents are perceived as more socially present and emotionally intelligent if they use sentiment-adaptive response based on user's utterances \cite{diederich2019emulating}\cite{yang2017perceived}.
-Another commonly explored element is the use of prosody in voice-based agents, such as the use of express prosody contributing to higher perceived enjoyment and intimacy with the agent \cite{kim2020can}.
-However, there is a lack of research to synthesize these findings into an overall framework.
-One of the possible issues is the lack of clear and consistent definitions on the aspects of user's perceptions of agent and conversation architectural elements.
-
-Currently there is no systematic understanding on the elements of conversation architecture that are relevant to perceptions of agents.
-Some papers have started to examine the speech specifics that are being explored in literature, such as Clark et al.
-\cite{clark2019state} capturing different elements of system speech production for voice-based agents and categorizing them based on content, style, and other topics.
-There are also some investigations of conversation architecture elements within the broader field of studying cues that trigger a social reaction of the user towards the CA.
-Feine et al's \cite{feine2019taxonomy} paper laid the foundation to create a consistent taxonomy for these social cues.
-However, there is no comprehensive research specifically for conversation architecture elements that are relevant to user perceptions.
-
-Related to user perceptions, there is also no systematic understanding on the perceptions of agents affected by speech variations.
-Some research discussed the perceptions of agents as part of the broader scope of user experiences of CAs.
-These publications have gathered UX dimensions used to evaluate conversational agents, which include the perceptions of agents (e.g.
-empathy, humanness) alongside other assessments (e.g.
-physiological data) \cite{clark2019state}\cite{finch2020towards}.
-Some even categorized the metrics based on the type of method used, including technical measures like system error rate and perception measures like perceived social presence \cite{zheng2022ux}.
-However, these studies are assessing the general field of UX measurements and not specifically on the perceptions of agents, and do not analyze the effects of conversation architecture on these perceptions.
-
-These research gaps discussed above: the paucity of knowledge on synthesizing the effect of speech specifics on perceptions of CAs as well as the lack of systematic understanding on the elements of conversation architecture and perceptions of agents motivated us to the goal of how to design conversation architecture in order to orchestrate perceptions of conversational agents.
-First, we want to understand \textbf{(RQ1) what perception aspects of agents are being explored in relation to the effects of conversation architecture elements}.
-While there are various architecture elements of conversation architecture used in a CA's utterances, we don't have a holistic understanding of them.
-This leads to our second research question: \textbf{(RQ2) what elements of conversation architecture are relevant to the perceptions of agents?} Lastly, we want to understand the effect of conversation architecture on perceptions of agent, specifically: \textbf{(RQ3) what are the relationships between conversation architecture elements and the perceptions of CAs?}
-
-To answer these questions, we performed a comprehensive review on existing literature from 2010 to 2022 and synthesized the effect of conversation architecture elements on the perceptions of CAs based on 57 relevant papers (Figure \ref{fig:heatmap-impact}).
-We also grouped the perceptions of agents affected by conversation architecture into four categories and eleven aspects (Table \ref{tab:perceptions}), and grouped the speech variations related to perceptions of agents into four categories and eleven elements (Table \ref{tab:cues}).
-%Lastly, we coded the explored connections between conversation architecture and perceptions and synthesized their relationships into a framework.
-Through our analysis, we also found that there are inconsistencies in the assessment of perceptions across studies, as well as influencing factors other than conversation architecture that impact the perceptions of agents.
-This work contributes to the HCI community by presenting a framework that demonstrates the effect of conversation architecture on perceptions of conversational agents, as well as taxonomies for perception aspects and conversation architecture elements providing clear and consistent terms that can be used in future research.
-Together, these contributions move us one step closer to designing CAs that effectively interact with users.
-%Also, our analysis extends existing reviews on UX research of CAs \cite{clark2019state}\cite{rapp2021human}\cite{zheng2022ux} by providing a synthesized framework outlining the relationships between conversation architecture and perceptions of agents.
-With the help of this framework, we are taking the first step to understand how to design conversational agents to solicit specific social reactions from users.
-
-In the remainder of the paper, we first outline related background work, our literature review process, as well as the characteristics of the papers in our reviewed corpus.
-Following that, we describe in detail the taxonomy for the perception of agents, the taxonomy for conversation architecture element, as well as the framework on the relationships between perceptions of agents and conversation architecture.
-Finally, we discuss research challenges and opportunities as well as ethical considerations for designing conversational architecture to orchestrate perceptions of conversational agents.
-
-\section{Literature Review}
-
-* human-human vs. human-AI
-
-* anthropomorphism
-%Anthropomorphism is defined as the attribution of traits that we typically associate with being distinctly human to nonhuman entities \cite{waytz2010sees}.
-For example, users tend to personify conversational agents like Amazon Alexa by using person pronouns instead of object pronouns in online reviews \cite{purington2017alexa}.
-Research shows that anthropomorphic design is beneficial to establishing and maintaining trust between users and conversational agents \cite{seeger2021chatbots}.
-Also, speakers tend to align their lexical choices with conversational agents, similar to human-human conversations \cite{cowan2015does}.
-Anthropomorphism has been shown to ease user interactions, e.g.
-making agents more approachable, engaging, and trustworthy when they exhibit human characteristics \cite{qiu2009evaluating}.
-These processes are of particular interest for human-agent communication because they form the basis for user expectations and predispositions regarding agents' behavior, reliability of the information, etc.
-\cite{kuzminykh2020genie}.
-
-* how to synthesize
-
-* user experience evaluations of conversational agents
-%Other papers categorized CA assessments into themes.
-For example, Rapp et al.
-\cite{rapp2021human} generated themes related to how users' experience with chatbots such as experiencing the chatbot including assessments on expectation, perception, satisfaction etc.
-Most recently, Zheng et al's literature review on the UX research of CAs \cite{zheng2022ux} categorized the metrics based on the type of method used, including technical measures like system error rate and perception measures like perceived social presence.
-However, existing studies use different terminologies and categories across aspects of perception.
-As an illustration, it is unclear if the theme of experiencing the chatbot from Rapp et al.
-\cite{rapp2021human} contains similar aspects to the perception towards CA in Zheng et al \cite{zheng2022ux}'s analysis.
-%\cite{finch2020towards} Towards unified dialogue system evaluation: A comprehensive analysis of current evaluation protocols
-
-\section{Methods}
-
-This section describes the research methodologies used for data collection and data analysis. Additionally, it presents the characteristics of the papers in our reviewed corpus.
-
-\subsection{Data Collection}
-
-Following PRISMA guidelines \cite{prisma}, we reviewed and selected literature exploring the relationship between the specifics of conversation architecture elements and perceptions of CAs.
-Searches were carried out in the ACM Digital Library between January 1 and January 15, 2023.
-Through our analysis, we didn't find any common terms used to refer to either conversation architecture elements, or aspects of perceptions.
-As such, we generalized our search term to capture articles related to conversational agents.
-Based on search terms used in previously published literature reviews \cite{clark2019state}\cite{rapp2021human}, the following keywords are used to search for publications related to conversational user interfaces:
-\newline
-
-\textit{"conversational agent" OR "natural language interface" OR "IPA" OR "intelligent personal assistant" OR "chatbot" OR "speech interface" OR "voice assistant" OR "intelligent agent" OR "human-chatbot communication" OR "virtual agent" OR "dialog* system" OR "voice user interface" OR "human computer dialog*"}
-\newline
-
-The following selection criteria are applied to identify literature related to the effect of conversational architecture on the perception of agents:
-\begin{itemize}
-  \item The paper was published between 2010 and 2022.
-  \item The paper is peer-reviewed and written in English.
-  \item The paper contains the use of voice-based or text-based conversational agents.
-  \item The paper contains studies on the impact of conversation architecture elements on the perceptions of agents.
-  \item The paper contains impact of conversation architecture elements can be separated from other effects (e.g. embodiment).
-
-\end{itemize}
-
-The initial query retrieved 2901 unique publications.
-We screened the titles and abstracts of the papers based on the selection criteria above, resulting in 221 papers.
-The fully body of these papers are then reviewed, selecting papers that met the criteria.
-A search for additional literature was also performed to supplement the corpus, adding 8 more papers to the selection.
-In total, we identified 57 relevant articles for analysis (see Figure \ref{fig:prisma}).
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=1\columnwidth]{fig-prisma.png}
-  \caption{Literature search using PRISMA guidelines}
-  \label{fig:prisma}
-\end{figure}
-
-\subsubsection*{Literature Corpus Characteristics}
-
-The papers reviewed (n=57) were published between May 2011 and November 2022.
-More than 75\% of the papers were published in or after 2019, with a slight trend upwards over the years (see Figure \ref{fig:paper}).
-The vast majority of the papers in our corpus were published in conference proceedings (n=50), with the remainder papers published in journals.
-Out of the papers published in conferences, the top conferences were The ACM Conference on Human Factors in Computing Systems\footnote{https://dl.acm.org/conference/chi} (n=16), Conversational User Interfaces\footnote{https://dl.acm.org/conference/cui} (n=7), Human-Agent Interaction\footnote{https://dl.acm.org/conference/hai} (n=4), and Intelligent Virtual Agents\footnote{https://dl.acm.org/conference/iva} (n=4).
-%Out of the papers published in journals, some venues include the International Journal of Human-Computer Interaction\footnote{https://www.tandfonline.com/journals/hihc20} (n=2) and Interacting with Computers\footnote{https://academic.oup.com/iwc} (n=1).
-
-On the modality characteristics of the conversational agents in the corpus, there is a roughly even split between the modalities, with slightly more papers exploring voice-based CAs (n=30) compared to text-based CAs (n=27).
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=\columnwidth]{fig-paper.png}
-  \caption{Number of papers by year}
-  \label{fig:paper}
-\end{figure}
-
-\subsection{Data Analysis}
-
-\subsubsection*{Perceptions of Agents} To understand the perceptions of agents related to conversation architecture (RQ1), assessments for the perceptions of agents were extracted from each paper.
-We used inductive thematic analysis to group these assessments into codes based on their meanings.
-For example, the code likeability of the agent contains the questionnaire item "this voice agent was likeable" used by \cite{cuadra2021my}\cmt{[67]}, Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed}'s set of questions on likeability used by \cite{linnemann2018can}\cmt{[15]}, and Subjective Assessment of Speech System Interface (SASSI) questionnaire \cite{hone2000towards}\cmt{sassi}'s set of questions on likeability used by \cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}.
-This step resulted in 83 unique codes.
-These codes are then organized based similarity of the meanings, resulting in 11 aspects of perceptions.
-For example, the aspect of personality traits of the agent contains measurements such as likeability, funniness, and kindness.
-Lastly, the 11 aspects are grouped into 4 categories: perception of interaction with agent, perception of agent's ability, perception of sociability with agent, and perception of agent's humanness (Table \ref{tab:perceptions}).
-
-\subsubsection*{Conversation Architecture Elements}
-As to the elements of conversation architecture that are relevant to the perception of agents (RQ2), we extracted the specifics of conversation architecture used in each paper.
-Some of the papers used multiple features in their CA design, such as the the anthropomorphic agent used in Seeger et al's study \cite{seeger2021chatbots}\cmt{[35]}.
-In these composite situations, we broke them down into their individual features.
-For example, the anthropomorphic agent \cite{seeger2021chatbots}\cmt{[35]} was separated into emotional expressions, is-typing indicator, emoticons, and response delay and captured as codes.
-58 unique codes were created as part of this process, capturing features like sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}, lexical alignment \cite{spillner2021talk}\cmt{[18]}, and typos \cite{westerman2019believe}\cmt{[9]}.
-We then organized these codes into elements based on similarity, resulting in 12 elements of conversation architecture.
-For example, the element of disfluency contains fillers \cite{jeong2019exploring}\cmt{[10]}\cite{wester2015artificial}\cmt{[14]}, interjections \cite{ceha2022expressive}\cmt{[77]}\cite{hu2021enhancing}\cmt{[56]}, repetitions \cite{yang2021effect}\cmt{[72]} and typos \cite{westerman2019believe}\cmt{[9]}.
-These elements are grouped into 4 categories: dialog strategy, content affectiveness, content style, and speech format (Table \ref{tab:cues}).
-
-\subsubsection*{Relationship Between Perceptions of Agents and Conversation Architecture}
-To study the effect of conversation architecture on users' perceptions (RQ3), we extracted the connections explored in each paper, using the perception aspects and conversation architecture elements developed in the previous data analysis steps.
-Each connection's effect was also recorded based on whether an association was found in the study and the nature of that association.
-Out of our review corpus, 265 connections between perceptions of agents and conversation architecture were explored in literature.
-To analyze the specifics of conversation architecture that affect the perceptions of CAs, 72 connections that did not result in observed relationships were discarded, resulting in 193 relationships for analysis.
-For example, the connection between the matching style of a CA and user satisfaction was removed because Hoegen et al.
-\cite{hoegen2019end}\cmt{[31]} did not find a significant difference between the style matching agent and the non-style matching agent for overall interaction satisfaction.
-Out of the 193 relationships, 10 were relationships based on agents modifying multiple architecture elements (e.g.
-\cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2021manipulating}\cmt{[68]}).
-They were not included in the final framework as we could not attribute the perceptions of agents to the underlying core elements.
-Overall, 183 relationships between individual architecture elements and perceptions of agents are incorporated into our synthesized framework, visualized as a heatmap to demonstrate their relationships with each other (Figure \ref{fig:heatmap-impact}).
-
-\section{Findings}
+%% Side by side comparison between coverage and identified relationships
 
@@
   \centering
-  \includegraphics[width=\textwidth]{fig-heatmap-impact.png}
+  \includegraphics[width=\textwidth]{figures/fig-heatmap_coverage.pdf}
   \caption{Heatmap of literature for perception of conversational agents for each type of conversational architecture element}
-  \label{fig:heatmap-impact}
+  \label{fig:heatmap_coverage}
 \end{figure*}
-
-\subsection{Perceptions of Agents}
-
-As shown in Table \ref{tab:perceptions}, there are four categories defined for the perceptions of conversational agents covering 11 different aspects of perception.
-The details of each category and aspect are discussed below.
-
-\textbf{Perception of interaction with agent} assesses the overall interaction quality users had with the conversational agent.
-The three aspects for this perceptions are usability, engagement and satisfaction.
-\textit{Usability} captures the utilitarian component of the interaction, whether it was accurate, easy to use, efficient or helpful.
-Some commonly used methods to evaluate usability include the response accuracy portion of the SASSI questionnaire \cite{hone2000towards}\cmt{sassi}, or the NASA Task Load Index (NASA-TLX) \cite{hart1988development}\cmt{nasa} for cognitive workload.
-Questions such as "the system is easy to use" or "it is easy to understand the agent" are also used to evaluate usability.
-\textit{Engagement} on the other hand captures users' emotional reactions to the CA, whether they have enjoyed the conversation, or annoyed or frustrated with the interaction.
-Some commonly used methods to evaluate engagement include the annoyance portion of the SASSI questionnaire \cite{hone2000towards}\cmt{sassi}, and the Use Engagement Scale (UES) \cite{o2018practical}\cmt{ues}.
-Questions such as "I enjoyed using the system" or "I felt frustrated with the agent" are also used to evaluate engagement.
-Lastly, \textit{Satisfaction} captures users' overall satisfaction interacting with the agent.
-Questions such as "the overall assessment of conversing with the CA was satisfactory" are used to evaluate this perception.
-
-\textbf{Perception of agent's ability} assesses the perceived capabilities of the agent.
-Unlike system capabilities that affect agent's performance, the perceived ability category captures perceptions of agents with equivalent system capabilities but varied conversation architecture elements.
-Specifically, \textit{intelligence} captures the agent's expertise and knowledge, and it is commonly administered through the Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed} using the set of questions related to perceived intelligence.
-Also survey questions such as asking users about the agent's intelligence and domain knowledge are used to evaluate perceived intelligence.
-\textit{Competence} takes intelligence one step further by examining the agent's ability to put its intelligence into practice.
-Surveys or qualitative feedback are usually used to assess if the agent is capable and competent, and whether users have confidence in the agent's ability to get the job done.
-Lastly, \textit{credibility} captures agent's truthfulness, benevolence, and user's confidence in CAs.
-Some commonly used methods to evaluate trust include the Trust Propensity Scale \cite{mayer1999effect} and the Individualized Trust Scale (ITS) \cite{wheeless1977measurement}.
-Questions such as "is the agent honest" and "can I trust the agent with sensitive information" are also used to evaluate trust.
-
-\textbf{Perception of the sociability with agent} assesses the emotional connections that users have with agents.
-This category includes perception aspects of conversation tone, social presence and intimacy.
-\textit{Conversation tone} captures the affective impression of the agent's tone, such as empathy and expressiveness.
-Also, this aspect includes whether the tone used by the agent was perceived as friendly, polite or warm.
-\textit{Social presence} captures the sense of connectness and psychological distance users have with an agent.
-Some aspects in this category include the sense of familiarity or similarity with the agent, and whether users feel the agent behaves like them or have similar attitudes to them.
-The category of \textit{Intimacy} extends social presence into the realm of the quality of relationships with an agent.
-Some commonly used methods to assess intimacy include the set of social attraction questions from the interpersonal attraction questionnaire \cite{mccroskey1975development} and the quality of relationship inventory (QRI) \cite{pierce1997assessing}.
-These questionnaires include questions like "I think the agent could be a friend of mine", or "I feel we could establish a personal relationship with each other".
-
-\textbf{Perception of agent's humanness} assesses the specifics of anthropomorphized perceptions of conversational agents.
-\textit{Human-likeness} captures whether the agent presented itself as natural and human-like, or artificial and machine-like.
-The Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed} set of questions related to anthropomorphism and the Ascent of Man scale \cite{kteily2015ascent} are commonly used methods to evaluate human-likeness.
-Survey questions with semantic scales such as "human-like / machine-like" and "artificial / natural" are also commonly used for this aspect of perception.
-\textit{Personality traits} captures the human characteristics that are attributes to the agent.
-This is commonly collected as qualitative feedback from users, commenting on whether the agent is extroverted or introverted, or the perceived personality such as likeable, funny or witty.
-Sometimes the Big-5 personality traits questionnaire \cite{gosling2003very} is used to map an agent's disposition on various personality dimensions.
-
-Overall there is a good coverage of different aspects of perception based on the list of papers reviewed in our corpus.
-The most commonly explored aspect categories is the perception the interaction with agent, followed by the perception of agent's humanness.
-There are two aspects that are the least explored compared to the others relationships: competence within the perception of agent's ability, and intimacy within the perception of social connection with agent.
-This may be due to the controlled lab settings for the experiments, where participants are given the scenarios for interaction.
-This type of environment is not conducive to forming relationships with a conversational partner, as noted by Linnerman et al.
-in their discussions \cite{linnemann2018can}\cmt{[15]}.
-The same factor could impact the assessment of agent's competence, as the users may not feel like they have the expertise to assess their perceptions.
-%These factors could contribute to the reasons why competency and intimacy are not as frequently measured in experimental studies.
-
-\begin{table*}[ht]
-\renewcommand*{\arraystretch}{1.4}
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{@{}p{0.17\textwidth} | p{0.12\textwidth} | p{0.20\textwidth} | >{\centering}p{0.09\textwidth} | p{0.42\textwidth} @{}}
-%!{\vrule width 1.2pt} 
-\Xhline{1.2pt}
-\multicolumn{2}{l|}{\textbf{Perception Aspects}} & \textbf{Examples} & \textbf{No. Papers} & \textbf{Papers} 
-\\ \Xhline{1.2pt}
-\multirow{3}{*}{\parbox{0.17\textwidth}{Perception of \newline Interaction with Agent}}
-    & Usability & accuracy, ease of use, \newline efficiency, helpfulness & 23 
-    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2022expressive}\cmt{[77]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cuadra2021my}\cmt{[67]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{elsholz2019exploring}\cmt{[61]}\cite{haas2022keep}\cmt{[78]}\cite{habler2019effects}\cmt{[63]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2019comparing}\cmt{[89]}\cite{kim2020can}\cmt{[24]}
-    \cite{kraus2020effects}\cmt{[64]}\cite{linnemann2018can}\cmt{[15]}\cite{ma2022ask}\cmt{[29]}\cite{miehle2018exploring}\cmt{[51]}\cite{misu2011toward}\cmt{[83]}\cite{roy2021users}\cmt{[71]}\cite{spillner2021talk}\cmt{[18]}\cite{wilhelm2022keep}\cmt{[28]}
-\\ \cline{2-5}
-    & Engagement & enjoyment, annoyance, \newline desirable, intention to use  & 28
-    & \cite{andrews2012system}\cmt{[38]}\cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cox2022does}\cmt{[27]}\cite{cuadra2021my}\cmt{[67]}\cite{elsholz2019exploring}\cmt{[61]}\cite{fadhil2018effect}\cmt{[52]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{go2021conversational}\cmt{[80]}\cite{healey2013relating}\cmt{[39]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2020can}\cmt{[24]}\cite{kim2019comparing}\cmt{[89]}
-    \cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{ma2022ask}\cmt{[29]}\cite{miehle2018exploring}\cmt{[51]}\cite{miyamoto2017improving}\cmt{[46]}\cite{moilanen2022measuring}\cmt{[82]}\cite{roy2021users}\cmt{[71]}\cite{spillner2021talk}\cmt{[18]}\cite{volkel2021examining}\cmt{[69]}\cite{volkel2022user}\cmt{[75]}\cite{xiao2021let}\cmt{[73]}\cite{yang2021effect}\cmt{[72]}\cite{zhu2022effects}\cmt{[26]}
-\\ \cline{2-5}
-    & Satisfaction & service satisfaction, quality of interaction & 12
-    & \cite{ceha2022expressive}\cmt{[77]}\cite{choi2020nobody}\cmt{[54]}\cite{diederich2019emulating}\cmt{[25]}\cite{elsholz2019exploring}\cmt{[61]}\cite{habler2019effects}\cmt{[63]}\cite{gnewuch2018faster}\cmt{[19]}\cite{hoegen2019end}\cmt{[31]}\cite{hu2022polite}\cmt{[76]}\cite{ma2022ask}\cmt{[29]}\cite{roy2021users}\cmt{[71]}\cite{wilhelm2022keep}\cmt{[28]}\cite{yang2017perceived}\cmt{[44]}
-\\ \Xhline{1.2pt} 
-\multirow{3}{*}{\parbox{0.16\textwidth}{Perception of Agent's Ability}}
-    & Intelligence & knowledgeable, intelligent, expertise & 11
-    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cuadra2021my}\cmt{[67]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{feijoo2021effects}\cmt{[70]}\cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}\cite{spillner2021talk}\cmt{[18]}\cite{volkel2022user}\cmt{[75]}\cite{yang2017perceived}\cmt{[44]}
-\\ \cline{2-5}
-    & Competence & competent, appropriate & 6 
-    & \cite{cox2022does}\cmt{[27]}\cite{kraus2020effects}\cmt{[64]}\cite{jestin2022effects}\cmt{[81]}\cite{lee2019s}\cmt{[55]}\cite{misu2011toward}\cmt{[83]}\cite{westerman2019believe}\cmt{[9]}
-\\ \cline{2-5}
-    & Trust & credibility, trustworthy, truthfulness, confidence & 15
-    & \cite{andrews2012system}\cmt{[38]}\cite{chan2021kinvoices}\cmt{[74]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{fadhil2018effect}\cmt{[52]}\cite{healey2013relating}\cmt{[39]}\cite{hoegen2019end}\cmt{[31]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kraus2020effects}\cmt{[64]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{ma2022ask}\cmt{[29]}\cite{seeger2021chatbots}\cmt{[35]}\cite{tolmeijer2021female}\cmt{[62]}\cite{wilhelm2022keep}\cmt{[28]}
-\\ \Xhline{1.2pt} 
-\multirow{3}{*}{\parbox{0.16\textwidth}{Perception of \newline Sociability with Agent}}
-    & Conversation Tone & friendly, warm, empathetic, persuasive & 20 
-    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cox2022does}\cmt{[27]}\cite{cuadra2021my}\cmt{[67]}\cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{healey2013relating}\cmt{[39]}\cite{hu2021enhancing}\cmt{[56]}\cite{hu2022polite}\cmt{[76]}\cite{jestin2022effects}\cmt{[81]}\cite{khooshabeh2011does}\cmt{[37]}\cite{kim2019comparing}\cmt{[89]}\cite{lee2019s}\cmt{[55]}\cite{miehle2018exploring}\cmt{[51]}
-    \cite{moilanen2022measuring}\cmt{[82]}\cite{tolmeijer2021female}\cmt{[62]}\cite{yang2021effect}\cmt{[72]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}
-\\ \cline{2-5}
-    & Social Presence & connectedness, familiarity, psychological distance & 18
-    & \cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cuadra2021my}\cmt{[67]}\cite{diederich2019emulating}\cmt{[25]}\cite{gnewuch2018faster}\cmt{[19]}\cite{gnewuch2018chatbot}\cmt{[21]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{go2021conversational}\cmt{[80]}\cite{khooshabeh2011does}\cmt{[37]}\cite{kim2020can}\cmt{[24]}\cite{lee2019s}\cmt{[55]}\cite{lubis2019positive}\cmt{[43]}\cite{lubold2016effects}\cmt{[86]}
-    \cite{ma2022ask}\cmt{[29]}\cite{niewiadomski2013laugh}\cmt{[85]}\cite{westerman2019believe}\cmt{[9]}    
-\\ \cline{2-5}
-    & Intimacy & intimate, rapport, quality of relationship & 7 
-    & \cite{choi2020nobody}\cmt{[54]}\cite{khooshabeh2011does}\cmt{[37]}\cite{kim2020can}\cmt{[24]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{lubold2016effects}\cmt{[86]}\cite{westerman2019believe}\cmt{[9]}
-\\ \Xhline{1.2pt}
-\multirow{2}{*}{\parbox{0.16\textwidth}{Perception of Agent's Humanness}}
-    & Human-likeness & human-like, natural, \newline artificial, machine-like & 20
-    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cox2022does}\cmt{[27]}\cite{diederich2019emulating}\cmt{[25]}\cite{gnewuch2018faster}\cmt{[19]}\cite{haas2022keep}\cmt{[78]}\cite{hu2022polite}\cmt{[76]}\cite{jeong2019exploring}\cmt{[10]}\cite{jestin2022effects}\cmt{[81]}\cite{lubis2019positive}\cmt{[43]}\cite{ma2022ask}\cmt{[29]}\cite{misu2011toward}\cmt{[83]}\cite{niewiadomski2013laugh}\cmt{[85]}
-    \cite{ouchi2019should}\cmt{[59]}\cite{seeger2021chatbots}\cmt{[35]}\cite{wester2015artificial}\cmt{[14]}\cite{westerman2019believe}\cmt{[9]}\cite{zhu2022effects}\cmt{[26]}    
-\\ \cline{2-5}
-    & Personality Traits & likeable, kind, witty, funny, creepy & 20
-    & \cite{andrews2012system}\cmt{[38]}\cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cuadra2021my}\cmt{[67]}\cite{haas2022keep}\cmt{[78]}\cite{habler2019effects}\cmt{[63]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{huiyang2022improving}\cmt{[17]}\cite{jeong2019exploring}\cmt{[10]}\cite{kim2019comparing}\cmt{[89]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{miehle2018exploring}\cmt{[51]}
-    \cite{ouchi2019should}\cmt{[59]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}\cite{wester2015artificial}\cmt{[14]}\cite{zhu2022effects}\cmt{[26]} 
-\\ \Xhline{1.2pt}
-\end{tabular}%
-}
-\caption{Perception aspects}
-\label{tab:perceptions}
-\end{table*}
-
-\begin{table*}[h]
-\resizebox{\textwidth}{!}{
-\renewcommand*{\arraystretch}{1.4}
-\begin{tabular}{@{}p{0.17\textwidth} | p{0.14\textwidth} | p{0.25\textwidth} | >{\centering}p{0.09\textwidth} | p{0.34\textwidth} @{}}
-\Xhline{1.2pt}
-\multicolumn{2}{l|}{\textbf{Conversation Architecture Elements}} & \textbf{Examples} & \textbf{No. Papers} & \textbf{Papers}
-\\ \Xhline{1.2pt}
-\multirow{3}{*}{Dialog Strategy} & Social Dialog & social talk, self-disclosure  & 7
-& \cite{andrews2012system}\cmt{[38]}\cite{lee2020hear}\cmt{[23]}\cite{lubold2016effects}\cmt{[86]}\cite{moilanen2022measuring}\cmt{[82]}\cite{roy2021users}\cmt{[71]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}
-\\ \cline{2-5}
-
-& Initiative & proactive dialogue, conversation \newline repair & 4
-& \cite{ashktorab2019resilient}\cmt{[88]}\cite{cuadra2021my}\cmt{[67]}\cite{kraus2020effects}\cmt{[64]}\cite{xiao2021let}\cmt{[73]}
-\\ \cline{2-5}
-
-& Response Delay & response delay, typing indicator & 4
-& \cite{gnewuch2018faster}\cmt{[19]}\cite{gnewuch2018chatbot}\cmt{[21]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{seeger2021chatbots}\cmt{[35]}
-\\ \Xhline{1.2pt}
-
-\multirow{2}{*}{Content Affectiveness} & Affective Language & emotional expressions, sentiment-adaptive responses & 11
-& \cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{lee2019s}\cmt{[55]}\cite{lubis2019positive}\cmt{[43]}\cite{moilanen2022measuring}\cmt{[82]}\cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2022user}\cmt{[75]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}
-\\ \cline{2-5}
-
-& Humour & humorous content, jokes & 6
-& \cite{ceha2021can}\cmt{[57]}\cite{go2021conversational}\cmt{[80]}\cite{khooshabeh2011does}\cmt{[37]}\cite{miyamoto2017improving}\cmt{[46]}\cite{niewiadomski2013laugh}\cmt{[85]}\cite{volkel2021manipulating}\cmt{[68]}
-\\ \Xhline{1.2pt}
-
-\multirow{3}{*}{Content Style} & Formality & formal vs. casual, honorific \newline expressions & 9
-& \cite{cox2022does}\cmt{[27]}\cite{elsholz2019exploring}\cmt{[61]}\cite{habler2019effects}\cmt{[63]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2019comparing}\cmt{[89]}\cite{ma2022ask}\cmt{[29]}\cite{moilanen2022measuring}\cmt{[82]}\cite{ouchi2019should}\cmt{[59]}\cite{volkel2022user}\cmt{[75]}
-\\ \cline{2-5}
-
-& Alignment & content matching, lexical \newline alignment, agreeableness & 7
-& \cite{healey2013relating}\cmt{[39]}\cite{hoegen2019end}\cmt{[31]}\cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}\cite{spillner2021talk}\cmt{[18]}\cite{volkel2021examining}\cmt{[69]}\cite{volkel2021manipulating}\cmt{[68]}
-\\ \cline{2-5}
-
-& Elaborateness & elaborate, concise, sentence \newline structure & 6
-& \cite{haas2022keep}\cmt{[78]}\cite{miehle2018exploring}\cmt{[51]}\cite{moilanen2022measuring}\cmt{[82]}\cite{roy2021users}\cmt{[71]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}
-\\ \Xhline{1.2pt}
-
-\multirow{3}{*}{Speech Format} & Prosody & pitch, intonation, speech rate, \newline spoken accent & 12
-& \cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{feijoo2021effects}\cmt{[70]}\cite{habler2019effects}\cmt{[63]}\cite{hu2021enhancing}\cmt{[56]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2020can}\cmt{[24]}\cite{lubold2016effects}\cmt{[86]}\cite{misu2011toward}\cmt{[83]}\cite{tolmeijer2021female}\cmt{[62]}\cite{zhu2022effects}\cmt{[26]}
-\\ \cline{2-5}
-
-& Disfluency & fillers, interjections, repetitions, \newline typos & 6
-& \cite{ceha2022expressive}\cmt{[77]}\cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}\cite{wester2015artificial}\cmt{[14]}\cite{westerman2019believe}\cmt{[9]}\cite{yang2021effect}\cmt{[72]}
-\\ \cline{2-5}
-
-& Text Formatting & capitalization, emoticons & 6
-& \cite{fadhil2018effect}\cmt{[52]}\cite{kim2019comparing}\cmt{[89]}\cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2022user}\cmt{[75]}\cite{westerman2019believe}\cmt{[9]}\cite{wilhelm2022keep}\cmt{[28]}
-\\ \Xhline{1.2pt}
-\end{tabular}%
-}
-\caption{Conversation architecture elements}
-\label{tab:cues}
-\end{table*}
-
-\subsection{Conversation Architecture Elements}
-
-As shown in Table \ref{tab:cues}, there are four categories defined for conversation architecture across 12 different elements. The details of each category and element are discussed below.
-
-The category of \textbf{dialog strategy} refers to the approach used by a conversational agent to engage in a dialogue with a user, which includes the use of social dialogs, agent-initiated content, and adding delays to responses.
-Specifically, the element of \textit{social dialogue} captures non-task related conversations with the user to build social connection, such as self-disclosure \cite{lee2020hear}\cmt{[23]} and small talk like chitchats \cite{lubold2016effects}\cmt{[86]}\cite{volkel2021manipulating}\cmt{[68]}.
-The element of \textit{initiative} captures utterances that are initiated by the agent without direct prompts from the user.
-For example, the agent is taking the initiative to proactively repair the conversation with a user \cite{ashktorab2019resilient}\cmt{[88]}\cite{cuadra2021my}\cmt{[67]}, or actively elicit feedback from users \cite{xiao2021let}\cmt{[73]}.
-Lastly, \textit{response delay} refers to the tactic of deliberatively delaying for a certain period of time before an agent responds to users \cite{gnewuch2018faster}\cmt{[19]}\cite{gnewuch2022opposing}\cmt{[20]}.
-It is mainly used in text-based CAs alongside visual displays of typing indicators \cite{gnewuch2018chatbot}\cmt{[21]}.
-
-\textbf{Content affectiveness} refers to the conversational agent's use of language to convey emotions or to elicit emotions from users.
-The architecture element of \textit{affective language} captures the injection of emotional words or phrases into the agent's utterance, such as affective expressions \cite{seeger2021chatbots}\cmt{[35]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}, sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}, and encouraging words \cite{healey2013relating}\cmt{[39]}.
-The other element in this category, \textit{humour}, captures an agent's attempt to include jokes in its dialog.
-Several studies in our reviewed corpus have explored the effect of humour on various perceptions of agents (e.g.
-\cite{ceha2021can}\cmt{[57]}\cite{khooshabeh2011does}\cmt{[37]}).
-
-The category of \textbf{content style} refers to the variations of language used in a message aside from the content meaning of the message (i.e.
-how something is said).
-The element of \textit{formality} describes the linguistic style used by the conversational agent, whether it is formal vs.
-casual, such as using honorific expressions to address users \cite{ouchi2019should}\cmt{[59]}.
-\textit{Alignment} captures the degree that the agent aligns its utterances to the users, such as lexical alignment on the content and structural of the sentences \cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}, as well as referring and agreeing with users' utterances \cite{volkel2021examining}\cmt{[69]}.
-Lastly, the element of \textit{elaborateness} captures the sentence complexity and length of agents' utterances.
-For example, Roy et al.
-explored the differences in perception for variations in elaborateness such as "Cloudly, possibility of snow, high: 4, low: -10" vs "Today will be cloudy, with a high of 4 and a low of -10.
-Snow is predicted" \cite{roy2021users}\cmt{[71]}.
-
-Lastly, the category of \textbf{speech format} captures the non-verbal component of a conversational agent's utterances for both text and voice modalities. \textit{Disfluency} captures 
-the use of non-lexical utterances like filler words ("um, uh") \cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}, or repetition of words within a sentence \cite{yang2021effect}\cmt{[72]}.
-It also includes the format of using typos \cite{westerman2019believe}\cmt{[9]} for text-based agents.
-For voice-based agents specifically, the element of \textit{prosody} encompasses vocal qualities like pitch \cite{habler2019effects}\cmt{[63]}\cite{jestin2022effects}\cmt{[81]}, speech rate \cite{choi2020nobody}\cmt{[54]}, and spoken accent \cite{feijoo2021effects}\cmt{[70]}.
-For text-based CAs, the \textit{text formatting} element includes different formats agents uses to present information to users, such as using capitalization \cite{westerman2019believe}\cmt{[9]} or emoticons \cite{kim2019comparing}\cmt{[89]}\cite{wilhelm2022keep}\cmt{[28]}.
-
-Overall there are similar number of conversation architecture elements explored across the four categories of dialog strategy, content affectiveness, content style, and speech format.
-As for explorations related to different modalities of agents, there is a noticeable difference in the category of speech format, where architecture elements related to voice-based agents (n=15) are explored more than text-based agents (n=7).
-Looking across the 12 different elements, there is good coverage of studies on the impact of affective language and prosody cues on the perceptions of agents.
-However, there are less studies exploring the effect of agent initiated content and response delay on the perception of agents.
-Specifically for the element of initiative under dialog strategy category, there is literature on conversation repairs \cite{komatani2010online}\cite{reinkemeier2022repair} and agent proactively sharing content with users \cite{dubiel2019inquisitive}\cite{zargham2022understanding}, but many of them did not not include assessments of perceptions of the CA.
-This may be due to the fact that the usage of agent-initiated content is relatively new, as CA interactions have historically been driven by users.
-As such, current research is focused on the functional aspects of agents initiating contents instead of exploring the perceptions of agents.
-As for response delay, there are indications that this element is under-explored in literature.
-Only 4 studies in our reviewed corpus used an agent with response delay, and the majority of these publications were written by the same authors.
-
-\subsection{Relationship Between Perceptions of Agents and Conversation Architecture}
-
-There are 183 identified relationships between perceptions of agents and conversation architecture out of the 265 explored connections that are included in our synthesized framework (Figure \ref{fig:heatmap-impact}).
-To compare the number of identified relationships vs.
-the explored connections in literature, Figure \ref{fig:heatmap-coverage} shows a side-by-side comparison between the two.
-The detailed analysis on the differences between explored and identified relationships are discussed in the subsections below.
-
-While the number of papers studying CAs with voice (n=27) vs.
-text (n=30) modalities is not significantly different, there are some interesting patterns we found with regards to the modalities of the identified relationships between perceptions of agents and conversation architecture.
-Overall, we confirmed the pattern found earlier that there are more conversation architecture elements explored related to voice vs.
-text in the speech format category.
-Because there are smaller number of text-based CAs using speech format elements, we also observed significantly less number of relationships between text-based CA across all perceptions of agents.
-other interesting findings related to modality are discussed later in this paper.
-
-\begin{figure*}[]
-  \centering
-  \includegraphics[width=\textwidth]{fig-heatmap-coverage.png}
-  \caption{Heatmap of literature for perception of conversational agents for each type of conversational architecture element}
-  \label{fig:heatmap-coverage}
-\end{figure*}
-
-\subsubsection{Perception of Interaction with Agent}
-
-The effects of conversation architecture elements on the perception of interaction with agent is the most explored connections in the corpus (n=97).
-Out of these explored connections, the majority of them (n=66) discovered a relationship between aspects of perception related to the perception of interaction with agent related to the studied architecture element.
-Looking at the difference between modalities, we noticed more voice-based agents (n=25) resulted in null relationships compared to text-based agents (n=6).
-The conversation architecture element of \textit{alignment} contributed the most to the null results for voice-based agents, with 9 out of 11 explored connections did not find any relationships related the perception of interaction with agents.
-
-Across the aspects for the perception of interaction, both usability and engagement were assessed frequently in the reviewed literature, with conversation architecture having effects on these perception aspects across all architecture element categories.
-The aspect of satisfaction was used in some studies to evaluate perception but it is not used as often as engagement or usability.
-Several papers that assessed user satisfactions were conversation agents within the transaction context, especially within the customer service domain (e.g.
-\cite{diederich2019emulating}\cmt{[25]}\cite{elsholz2019exploring}\cmt{[61]}\cite{gnewuch2018faster}\cmt{[19]}).
-
-The category of conversation architecture elements with the most identified relationships to perceptions of interaction is content style.
-Specifically for the element of \textit{elaborateness}, users found the use of full sentences more useful than keyword only \cite{haas2022keep}\cmt{[78]}\cite{roy2021users}\cmt{[71]}.
-Otherwise, the effect of an agent's elaborateness on user's perception of interaction depends on the user's preference \cite{miehle2018exploring}\cmt{[51]}, as well as the topic of discussion \cite{haas2022keep}\cmt{[78]}.
-As for \textit{formality}, various studies reported significant differences in perceptions of interaction between using casual vs.
-formal styles.
-Some users experienced higher engagement with agent interacting with the casual style of the conversation \cite{cox2022does}\cmt{[27]}, while in another study users reported the formal language style as less engaging as it is boring \cite{kim2019comparing}\cmt{[89]}.
-
-The speech format of an agent also resulted in a high number of identified relationships with the perception of interaction with CAs, with majority of the explored connections resulted in effects between the perception aspects and architecture elements.
-The element with the most identified relationships is \textit{prosody}.
-For example, studies found that a CA's expressiveness in vocal cues increased participants' engagement ratings \cite{zhu2022effects}\cmt{[26]}, and different pitches of voice affect users' perception of engagement and usability \cite{chan2021kinvoices}\cmt{[74]}\cite{habler2019effects}\cmt{[63]}.
-
-Dialog strategy and content affectiveness categories of conversation architecture did not have as many identified relationships with perceptions of interaction.
-It is worth noting the effect of using the \textit{initiative} element, as CAs that use self-initiated content are perceived as more efficient and higher quality of interaction (e.g.
-\cite{cuadra2021my}\cmt{[67]}).
-Also, some studies have discovered conflicting effects between different perception aspects of interaction for CAs using \textit{social dialog}, as users enjoyed the conversation using social talk \cite{lee2020hear}\cmt{[23]}\cite{roy2021users}\cmt{[71]}, but perceived the CA as less efficient \cite{roy2021users}\cmt{[71]}.
-
-\subsubsection{Perception of Agent's Ability}
-
-The effects of conversation architecture elements on the perception of agent's ability is the least explored connection in the corpus (n=39).
-Out of these explored connections, the majority of them (n=30) found relationships between the studied architecture element and the perceptions of agent's ability.
-There are no notable differences between the text and voice modalities of CAs for either explored connections or the identified relationships.
-
-Aspects within the perception of agent's ability had similar number of identified relationships across intelligence, competence and credibility.
-Our review revealed that the perceived ability of a CA is also dependent on other influencing factors in addition to conversation architecture elements.
-Volkel et al.
-\cite{kraus2020effects}\cmt{[64]} found that the perception of competence of a proactive CA is dependent on task difficulty \cite{kraus2020effects}\cmt{[64]}.
-Also, the perception of intelligence for an agent using fillers depended on the context of the conversation, as the filler-speaking agent was perceived as less intelligent in task-oriented conditions, but was seen as slightly more intelligent in social-oriented conditions \cite{jeong2019exploring}\cmt{[10]}.
-
-Out of the explored conversation architecture elements, \textit{prosody} had relationships identified with aspects across the perception category of agent's ability.
-For example, Chan et al.
-\cite{chan2021kinvoices}\cmt{[74]} found that agents using kin's voices are rated as more intelligent and credible than generic voices.
-Also, the style of speech used by an agent affects the perception of appropriateness of tone, which is an aspect of the perceived competence of an agent \cite{misu2011toward}\cmt{[83]}.
-Different content styles of \textit{formality} also impacts the perceived competence of an agent \cite{cox2022does}\cmt{[27]}\cite{jestin2022effects}\cmt{[81]}.
-Specifically related to perceived credibility of an agent, being \textit{lexically aligned} with the user resulted improved the rating of trustworthiness of an agent \cite{hoegen2019end}\cmt{[31]}\cite{linnemann2018can}\cmt{[15]}.
-There were mixed results on the use of emoticons within the \textit{text formatting} element.
-One study found the chatbot using emoticons as less trustworthy \cite{wilhelm2022keep}\cmt{[28]}, while another study found that users assigned higher scores for confidence to the agent using emojis \cite{fadhil2018effect}\cmt{[52]}.
-
-There are several conversation architecture elements with little to no explorations to the perception of agent's ability.
-Specifically, both categories of dialog strategy and content affectiveness are minimally explored in our reviewed corpus, with no explored connections with \textit{response delay} and only one or two connections explored for \textit{social dialog} and \textit{humour}.
-While the content style category had coverage in some aspects of perceived abilities, it is worth noting that \textit{elaborateness} did not have any explored connections with perceived ability of agents.
-Further research in these areas is needed to fill these gaps in understanding.
-
-\subsubsection{Perception of Sociability with Agent}
-
-The perception of agent's humanness is the second most explored category within our reviewed corpus (n=64), with majority of the connections identified relationship between the studied conversation architecture elements and the anthropomorphized perceptions of agent (n=49).
-Interestingly, studies explored more perceptions of sociability with agent related to voice-based CAs (n=40) compared to text-based CAs (n=24), potentially due to the assumption that interactions with text-based agents are perceived as less personal and more formal \cite{kocielnik2018designing}.
-There are some mixed results for voice-based CAs, as 12 out of the 28 connections did not find any significant results.
-Drilling down to the specific elements, we noticed that the use of \textit{alignment} in voice-based agents did not effect the perception of sociability with agent \cite{healey2013relating}\cmt{[39]}\cite{linnemann2018can}\cmt{[15]}.
-We didn't have data on text-based agents' perceived social connections with users to compare with voice-based agents, as the studies using alignment and text modality in our corpus did not assess this aspect category of perception.
-
-Across the aspects in this perception category, conversation tone had the most number of identified relationship (n=27) with the perceived social connection with CAs, followed by the aspect of social presence (n=17).
-There are only 5 relationships found that are linked to the perception aspect of intimacy.
-One reason for this is half of the explored connections did not have any effect on the perception of sociability with agent, such as the use of capitalization \cite{westerman2019believe}\cmt{[9]}, lexical alignment \cite{linnemann2018can}\cmt{[15]}, or social talk \cite{lubold2016effects}\cmt{[86]}.
-For the perception aspect of social presence, we noticed a gap in the exploration of conversation architecture elements of formality, alignment, and elaborateness in the content style category, as there are no papers explored at this intersection.
-
-Looking at the different categories of conversation architecture elements, the heatmap (Figure \ref{fig:heatmap-impact} shows that there are not many relationships in content style category that are related to the perceived sociability with CAs in general, with most of the discovered effects concentrated at the intersection of \textit{formality} and conversation tone.
-Studies have found that CAs using casual style of conversation are perceived as warm, empathetic and friendly \cite{jestin2022effects}\cmt{[81]}\cite{kim2019comparing}\cmt{[89]}, while CAs using formal style of conversation are perceived as polite but lacks empathy \cite{cox2022does}\cmt{[27]}.
-The rest of the architecture elements and perception aspects of sociability are minimally explored in literature, which indicates the need for more research in this area.
-
-There are a few specific conversation architecture elements that had more identified relationships with perceptions of sociability with agent.
-Specifically, CAs using of \textit{affective language} were perceived to be more empathetic \cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{yang2017perceived}\cmt{[44]} and emotionally expressive \cite{zhu2022effects}\cmt{[26]}, as well as being more emotional connected with their users \cite{lee2019s}\cmt{[55]}\cite{lubis2019positive}\cmt{[43]}.
-Also, different variations of a voice-based CA's \textit{prosody} have effects on the perceived sociability with agent, such as an agent using expressive prosody is assessed as more intimate and more similar with the user \cite{kim2020can}\cmt{[24]}.
-Lastly, the conversation architecture element of \textit{humour} has identified relationships across the social connection category of perception.
-Clark et al.
-\cite{clark2019makes} found that humour is an important conversational characteristic for human-human interactions, but viewed as a novelty feature for human-agent conversations.
-However, in our review we found that humor has effects on human-agent relationships, as humorous agents are rated as more friendly, intimate, and similar by users compared to non-humorous agents \cite{go2021conversational}\cmt{[80]}\cite{khooshabeh2011does}\cmt{[37]}.
-
-\subsubsection{Perception of Agent's Humanness}
-
-There are 55 explored connections between conversation architecture elements and the perception of sociability with agents, with majority of them (n=38) finding identified relationships in literature.
-There are significantly more explorations for voice-based agents (n=39) as compared to text-based agents (n=16).
-Previous studies have found that modality may have an effect on the perception of humanness, as voice-based agents are perceived as more human-like as compared to text-based agents \cite{cho2019effects}.
-Out of the 39 explored connections for voice-based agents, 14 of them did not result in any relationships.
-This is especially evident in the architecture element of \textit{affective language} for voice-based agents, as most of the connections resulted in null relationships.
-For example, when comparing the ratings of human-likeness or likeability for a speech agent employing expressive words to the one not using any, Zhu et al \cite{zhu2022effects}\cmt{[26]} were unable to detect any statistically significant differences in both of the observation study and interaction study.
-
-Across the aspects in this perception category, both human-likeness and personality traits have relationships with almost all the conversation architecture elements.
-Specifically for the use of \textit{prosody} elements, our review found some opposing effects on the perception of the agent's humanness.
-In the case of Chan et al's study \cite{chan2021kinvoices}\cmt{[74]}, participated rated the agent using kin voices as significantly more likeable compared to the generic voices, but it was perceived as eerie.
-This may be a warning indicator to watch out for the uncanny valley effect \cite{mori2012uncanny} and advise CA designers to carefully select conversation architecture elements to elicit anthropomorphized perceptions.
-
-There are a few notable conversation architecture elements related to the perceived humanness of conversational agents.
-The use of \textit{prosody} such as varying pitch, intonation and speech rate has more identified relationships with the perceived personality traits of an agent as compared to the perceived human-likeness, especially on the aspect of likeability \cite{choi2020nobody}\cmt{[54]}\cite{jestin2022effects}\cmt{[81]}\cite{misu2011toward}\cmt{[83]}.
-For the architecture elements of \textit{disfluency}, the type of impact on the perception of humanness depended on the context of the conversation.
-Studies have found that participants perceived the filler-condition agent as more likeable in the social-oriented situation, but did not find the same effect in task-oriented situations \cite{jeong2019exploring}\cmt{[10]}\cite{wester2015artificial}\cmt{[14]}.
-The use of \textit{alignment} in an agent had a number of identified relationships with the perception of personality traits, with some studies finding CAs that are lexically aligned with a user are more likeable \cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}.
-
-%-------------
-\section{Discussions}
-
-\subsection{Research Challenges and Opportunities}
-
-%Three major needs emerged from the trends identified by our review: 1) 2) 3).
-
-\subsubsection{The Need for Consistent Evaluation Protocols for Perceptions of Agents}
-
-We found a diversity of approaches used to assess perceptions of agents in our reviewed corpus.
-While we made our best efforts to group perceptions used in literature based on similarity with each other, the inconsistent and composite nature of these perception assessments makes it challenging to synthesize them into a framework that contains homogeneous components in each perception aspect that can be compared with each other.
-
-Based on the literature reviewed in this paper, it is unclear whether perception aspects using similar labels are being evaluated \textit{consistently} through different approaches.
-For example, we found several methods used to assess the perceived human-likeness of an agent.
-A commonly used survey is adapted from the Godspeed questionnaire \cite{bartneck2009measurement}, which evaluates human-likeness based on users' impression of the agent as fake / natural, machinelike / humanlike, unconscious / conscious, and artificial / lifelike (used by \cite{hoegen2019end}\cmt{[31]}, \cite{jeong2019exploring}\cmt{[10]} and \cite{ouchi2019should}\cmt{[59]}).
-Another method used to evaluate human-likeness is adapted from Holtgraves et al.'s \cite{holtgraves2007perceiving} questionnaire, which asks users questions related to the agent's perceived human-likeness, skillfulness, thoughtfulness, politeness, responsiveness and engagement (used by \cite{diederich2019emulating}\cmt{[25]} and  \cite{gnewuch2018faster}\cmt{[19]}).
-One study \cite{westerman2019believe}\cmt{[9]} used the Ascend of Man scale \cite{kteily2015ascent} with pictures showing the evolution from ape to man, asking users to choose a depiction that best represents the agent's perceived human-likeness.
-It is unclear whether these different methods are capturing assessments of similar perception aspects that can be compared with each other.
-Another example is the evaluation of the perception of agent's empathy.
-In Diedrech et al.'s study \cite{diederich2019emulating}\cmt{[25]}, empathy is assessed by asking users whether the CA is giving users individual or personal attention.
-In another study that also studies the perception of empathy \cite{daher2020empathic}\cmt{[58]}, the RoPE Scale \cite{charrier2019rope} is used with questions like "the robot cares about my feelings" or "the robot comforts me when I am upset." These two different evaluations of empathy seem to have different underlying meanings, one assessing the personalization aspect of CAs, while the other is assessing the emotional aspect of CAs.
-
-In addition the problem of consistency in evaluating perceptions, there is the issue of  \textit{composite measures} being used in the assessment of users' perceptions.
-These composite measures collapse multiple aspects of perception into one measurement, making it impossible to break down perceptions into more granular aspects for analysis.
-One such example is Ma et al's study \cite{ma2022ask}\cmt{[29]} on the different approaches for CAs to reply to users' uncertain queries.
-A single UX score is used to evaluate the users' perceptions, which composes of questions on whether the user thinks the CA's response is pleasing / trustworthy / natural / acceptable / shorten the distance between CA and user.
-The UX score encompasses multiple aspects across several perception categories.
-While this study has found significant effect for the use of formal language on the user rated UX score, it is not possible to understand how the details of formality is related to the perception categories of interaction (pleasing, acceptable), sociability (shorten the distance between CA and user), and humanness (natural, trustworthy).
-The humanness questionnaire from Holtgraves et al \cite{holtgraves2007perceiving} has a similar problem, evaluating across perception categories of interaction (responsiveness, engagement), ability (skillfulness), sociability (politeness), and humanness (human-likeness, thoughtfulness).
-
-There has been some effort recently towards unifying the evaluation of conversational agents, such as the work by Finch et al.
-\cite{finch2020towards} presenting a comprehensive analysis of current evaluation protocols.
-More research is needed in this area to standardize the assessment of perceptions to make them consistent, granular, and comparable across literature.
-
-\subsubsection{Investigate the Relationship Across Perception Aspects of Agents}
-
-There is evidence in literature that perception aspects of agents have effects on each other.
-For instance, Moussawi et al.
-\cite{moussawi2021perceptions}\cmt{[36]} conducted a study to understand the correlations between different perceptions related to users' intention to adopt a conversational agent.
-Specifically, they found a correlation within the category of perceived ability, where an agent's perceived intelligence is positively correlated to the perceived initial trust of the agent.
-This study also found that users with higher perceived intelligence of an agent are more likely to attribute higher ratings for perceived human-likeness, as well as for the usability and engagement aspects in the perception category of interaction.
-Lastly, the authors found that perceived humanness have a positive impact on perceived enjoyment, which lead to higher intention to adopt the CA.
-This study outlines that the perception aspects identified in this paper are not independent of each other.
-
-Correlations between perception aspects are discussed in a few of the papers we reviewed.
-One of the studies showed that the CA's perceived personality trait of agreeableness has an influence on the users' perception of credibility \cite{andrews2012system}\cmt{[38]}.
-Seeger et al's study found a similar correlation, where higher perceived anthropomorphism led to lower loss of trust \cite{seeger2021chatbots}\cmt{[35]}.
-There are also correlations between aspects found within the same perception category, such as a speech agent that is rated higher in perceived human-likeness was associated with higher likability ratings \cite{zhu2022effects}\cmt{[26]}.
-Also, within the perception category of social connection, one study found that social distance is positively related to the perceived social attraction \cite{westerman2019believe}\cmt{[9]}.
-
-These correlations demonstrate that some perception aspects have effects on each other, either within the same category or across different categories.
-While there are limited research into this area, further investigations are needed to understand the relationships between various perception aspects.
-
-\subsubsection{Research Directions for the Effects of Conversation Architecture on Users' Perceptions}
-
-Our synthesized framework (Figure \ref{fig:heatmap-impact}) serves as a foundational understanding on the effect of conversation architecture on the perception of agents.
-It showcases the density of explored relationships between them, as well as highlighting areas that are under-explored.
-In order to continue building our knowledge, it is important to investigate further into the effect of contextual factors as well as multiple conversation architecture elements on users' perceptions.
-
-There are a few \textit{under-explored areas} in our synthesized framework.
-The perception category of agent's ability has the least number of explored connections with conversation architecture compared to other perception categories.
-Specifically, more studies are needed to understand the effects of social dialog, response delay, humour and elaborateness on users' perceptions of agents' ability.
-For the perception category of sociability with agent, there is a general lack of explored connections with the conversation architecture category of content style, especially for alignment and elaborateness elements.
-Lastly, more studies on the effect of dialog strategy for conversation architecture elements of initiative and response delay on the perceptions of agent are needed.
-
-Some studies have discussed how differences in \textit{contextual factors} resulted in variations in the perceptions of agents while using similar conversation architecture elements.
-One of the factors is users' experience with CAs, as Gnewuch et al.
-\cite{gnewuch2018faster}\cmt{[19]} found that experienced users perceived the agent with a response delay as lower in social presence because it is seen as inefficient to wait for the CA to respond, but novice users perceived higher social presence conversing with the CAs using response delays because it is more similar to conversations with human partners \cite{gnewuch2018faster}\cmt{[19]}.
-User characteristics is another factor, as the perceived trustworthiness of a style matching agent depended on users' own conversational style \cite{hoegen2019end}\cmt{[31]}.
-Some other contextual factors that resulted in differences in perceptions of agent include the purpose of conversation (e.g.
-transactional vs.
-social) \cite{jeong2019exploring}\cmt{[10]}, anonymity of the conversation \cite{lee2020hear}\cmt{[23]}, and the sensitivity of information discussed in the interaction \cite{cox2022does}\cmt{[27]}.
-A comprehensive review to identify these contextual factors as well as to understand their effects on the perceptions of agents across various conversation architecture elements would be useful to tailor CA design for specific situations.
-
-As we gain a better understanding about the effects of a single conversation architecture element on the perceptions of agents, we can extend the research to using \textit{multiple conversation architecture elements} in an agent.
-Several papers in our reviewed corpus incorporated composite elements in an agent, such as the design of an anthropomorphized chatbot using elements such as affective language, emoticons, response delays to assess users' perceptions compared to a non-anthropomorphized chatbot \cite{seeger2021chatbots}\cmt{[35]}.
-In addition to explore the combined effects of conversation architecture elements on users' perceptions, it would also be interesting to understand the relative importance of each element on perceptions.
-Some studies analyzed the effect of modifying conversation architecture elements individually, as well as their combined effect on user's perceptions (e.g.
-\cite{habler2019effects}\cmt{[63]}\cite{lubold2016effects}\cmt{[86]}\cite{zhu2022effects}\cmt{[26]}).
-Specifically, Habler et al.
-\cite{habler2019effects}\cmt{[63]} found that the effect for social dialog is higher than the effect for prosody on the perception of agents.
-
-\subsection{Ethical Considerations}
-
-The designers of conversational agents need to consider ethical implications and potential negative impacts for users.
-This section discusses three main areas of concerns related to the effect of conversation architecture on the perceptions of agents: gender stereotypes, influencing user's actions and privacy concerns.
-
-For the element of prosody, various studies in our corpus explored the effect of different pitches on the perceptions of agents.
-Even in studies that are not explicitly analyzing the effect of different gendered voices in an agent, possible stereotypes may still exist in the study.
-Based on our reviewed corpus, studies found that lower pitches commonly associated with men are considered to be more desirable, authoritative but less friendly \cite{tolmeijer2021female}\cmt{[62]}\cite{jestin2022effects}\cmt{[81]}.
-For Dubiel et al's study \cite{dubiel2020persuasive}\cmt{[60]}, the agent with lower mean pitch was selected as the more persuasive voice.
-These results may be demonstrating users' unconscious bias to select a male sounding voice as more persuasive and authoritative over female sounding voices that are commonly associated with higher pitches.
-While some guidelines recommend designing agents to be androgynous to avoid gender stereotypes \cite{ruane2019conversational}, there are limitations in creating gender-ambiguous voices.
-Currently there is no defined guidelines on what is perceived as a gender-neutral voice \cite{jestin2022effects}\cmt{[81]}.
-There is also a lack of voice generators available to generate voices that are perceived as androgynous \cite{tolmeijer2021female}\cmt{[62]}.
-
-Studies have demonstrated that conversation architecture elements can be used to design perceptions of agents to make CAs more persuasive.
-This opens up the ethical issue of influencing users' attitudes and behaviours through these persuasion techniques.
-In a study by Chan et al \cite{chan2021kinvoices}\cmt{[74]}, they found that CAs using kin's voices are perceived as more credible and likeable, with a higher perceived social presence with the agent.
-These perceptions contributes to the agent being more engaging and persuasive, therefore people are more likely to comply with its requests.
-Andrew et al \cite{andrews2012system}\cmt{[38]} found that tailoring the personality of the CA to users will positively impact an agent's persuasiveness.
-These persuasion techniques can be beneficial to help users achieve their goals, but can also be used for harmful actions, such as trying to get users to believe in false information.
-
-Another key area of concern is privacy.
-Given the natural language format of conversational agents, users may be disclosing more sensitive and personal information than needed for the interaction.
-In relationship to conversation architecture, using elements like self-disclosure and persuasive voice prosody settings could result in users perceiving higher trust with the agent, leading them to disclose more sensitive information  \cite{lee2020hear}\cmt{[23]}\cite{dubiel2020persuasive}\cmt{[60]}.
-This can expose users to attacks, such as CAs using voice impersonation to ask for personal information for malicious intents \cite{chan2021kinvoices}\cmt{[74]}.
-Designing for perceptions of agents requires careful consideration of privacy issues including the sensitivity of the data, who has access to it, and how to protect against nefarious users.
-
-\subsection{Limitations}
-
-Our systematic literature review was limited to papers published in the ACM Digital Library between 2010 and 2022.
-We may have missed literature published outside this time period, as well as in other libraries.
-Also, most of the studies in our corpus are based on lab experiments using short interactions with users.
-The generalizability of these findings need to be verified through longer term engagements with conversational agents deployed in real world situations.
-Lastly, research without empirical studies on the perception of agents are excluded based on our selection criteria.
-We may have missed some influential findings in these papers.
-%To better understand the relationships between conversation architecture elements and the perceptions of agents, we plan to conduct future reviews in literature and user studies to understand their real-world impacts.
-
-\section{Conclusions}
-
-In this paper, we discussed the results of a systematic review of existing literature published in the ACM Digital Library on the effect of conversation architecture elements on the perceptions of CAs.
-Through our synthesis of 57 papers in our corpus, we present a framework outlining the relationships between elements of agents’ conversation architecture (dialog strategy, content affectiveness, content style and speech format) and aspects of users’ perception (interaction, ability, sociability and humanness).
-During our analysis, we found the need for consistent protocols in evaluating perceptions of agents, as measurements are inconsistent across studies.
-Further research is needed to investigate the under-explored areas in the framework, the relationship across perception aspects, the influence of contextual factors, and the effect of composite conversation architecture elements on users' perceptions.
-While our research contribute to the design conversation architecture to orchestrate specific perceptions of agent, we urge designers to incorporate ethical perspectives into their design considerations.
-
-%%
-%% The acknowledgments section is defined using the "acks" environment
-%% (and NOT an unnumbered section). This ensures the proper
-%% identification of the section in the article metadata, and the
-%% consistent spelling of the heading.
-\begin{acks}
-TBD
-\end{acks}
-
-%%
-%% The next two lines define the bibliography style to be used, and
-%% the bibliography file.
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{references}
-
-%%
-%% If your work has an appendix, this is the place to put it.
-\appendix
-
-\end{document}
-\endinput
-%%
-%% End of file `paper.tex'.

### 2023-02-21 figures/fig-prisma.tex
restructured manuscript

--- 2023-02-18 paper.tex
@@
-%% Manuscript for the effect of designed conversational architecture on the perception of agents
-%%
-%% The first command in your LaTeX source must be the \documentclass command.
-\documentclass[sigconf,screen,review, anonymous]{acmart}
-
-\usepackage[linewidth=1pt]{mdframed}
-\usepackage{lipsum}
-\usepackage{multirow}
-\usepackage{graphicx}
-\usepackage{booktabs}
-\usepackage{makecell}
-
-\newcommand{\cmt}[1]{}%{\ignorespaces}
-
-%% NOTE that a single column version may be required for 
-%% submission and peer review. This can be done by changing
-%% the \doucmentclass[...]{acmart} in this template to 
-%% \documentclass[manuscript,screen]{acmart}
-%% 
-%% To ensure 100% compatibility, please check the white list of
-%% approved LaTeX packages to be used with the Master Article Template at
-%% https://www.acm.org/publications/taps/whitelist-of-latex-packages 
-%% before creating your document. The white list page provides 
-%% information on how to submit additional LaTeX packages for 
-%% review and adoption.
-%% Fonts used in the template cannot be substituted; margin 
-%% adjustments are not allowed.
-%%
-%%
-%% \BibTeX command to typeset BibTeX logo in the docs
-\AtBeginDocument{%
-  \providecommand\BibTeX{{%
-    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
-
-%% Rights management information.  This information is sent to you
-%% when you complete the rights form.  These commands have SAMPLE
-%% values in them; it is your responsibility as an author to replace
-%% the commands and values with those provided to you when you
-%% complete the rights form.
-\setcopyright{acmcopyright}
-\copyrightyear{2023}
-\acmYear{2023}
-\acmDOI{XXXXXXX.XXXXXXX}
-
-%% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[Conference acronym 'XX]{Make sure to enter the correct
-  conference title from your rights confirmation email}{June 03--05,
-  2018}{Woodstock, NY}
-%
-%  Uncomment \acmBooktitle if th title of the proceedings is different
-%  from ``Proceedings of ...''!
-%
-%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
-%  June 03--05, 2018, Woodstock, NY} 
-\acmPrice{15.00}
-\acmISBN{978-1-4503-XXXX-X/18/06}
-
-%%
-%% Submission ID.
-%% Use this when submitting an article to a sponsored event. You'll
-%% receive a unique submission ID from the organizers
-%% of the event, and this ID should be used as the parameter to this command.
-%%\acmSubmissionID{123-A56-BU3}
-
-%%
-%% end of the preamble, start of the body of the document source.
-\begin{document}
-%TC:ignore
-
-%%
-%% The "title" command has an optional parameter,
-%% allowing the author to define a "short title" to be used in page headers.
-% \title[short title]{How to Make Pinocchio a Real Boy? Designing conversational architecture elements to achieve desirable anthropomorphized perceptions}
-\title{The Bot on Speaking Terms: The Effects of Conversation Architecture on Perceptions of Conversational Agents}
-
-%%
-%% The "author" command and its associated commands are used to define
-%% the authors and their affiliations.
-%% Of note is the shared affiliation of the first two authors, and the
-%% "authornote" and "authornotemark" commands
-%% used to denote shared contribution to the research.
-\author{Christina Wei}
-\email{christina.wei@mail.utoronto.ca}
-\affiliation{%
-  \institution{University of Toronto}
-  \city{Toronto}
-  \country{Canada}
-}
-
-\author{Young-Ho Kim}
-\email{ygho.kim@navercorp.com}
-\affiliation{%
-  \institution{Naver Corporation}
-  \city{Seoul}
-  \country{Korea}
-}
-
-\author{Anastasia Kuzminykh}
-\email{anastasia.kuzminykh@utoronto.ca}
-\affiliation{%
-  \institution{University of Toronto}
-  \city{Toronto}
-  \country{Canada}
-}
-
-%%
-%% By default, the full list of authors will be used in the page
-%% headers. Often, this list is too long, and will overlap
-%% other information printed in the page headers. This command allows
-%% the author to define a more concise list
-%% of authors' names for this purpose.
-\renewcommand{\shortauthors}{Wei, Kim, Kuzminykh} %It will be automatically anonymized through the document class property anonymous
-
-%%
-%% The abstract is a short summary of the work to be presented in the
-%% article.
-\begin{abstract}
-Conversational agents mimic natural conversation to interact with users.
-Since the effectiveness of interactions strongly depends on users’ perception of agents, it is crucial to design agents’ behaviors to provide the intended user perceptions.
-Research on human-agent and human-human communication suggests that speech specifics are associated with perceptions of communicating parties, but there is a lack of systematic understanding of how speech specifics of agents affect users' perceptions.
-To address this gap, we present a framework outlining the relationships between elements of agents’ conversation architecture (dialog strategy, content affectiveness, content style and speech format) and aspects of users’ perception (interaction, ability, sociability and humanness).
-Synthesized based on literature reviewed from the domains of HCI, NLP and linguistics (n=57), this framework demonstrates both the identified relationships and the areas lacking empirical evidence.
-We discuss the implications of the framework for conversation design and highlight the inconsistencies with terminology and measurements.
-\end{abstract}
-
-%%
-%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
-%% Please copy and paste the code instead of the example below.
-%%
-%\begin{CCSXML}
-%<ccs2012>
-% <concept>
-%  <concept_id>10010520.10010553.10010562</concept_id>
-%  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
-%  <concept_significance>500</concept_significance>
-% </concept>
-% <concept>
-%  <concept_id>10010520.10010575.10010755</concept_id>
-%  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-%  <concept_significance>300</concept_significance>
-% </concept>
-% <concept>
-%  <concept_id>10010520.10010553.10010554</concept_id>
-%  <concept_desc>Computer systems organization~Robotics</concept_desc>
-%  <concept_significance>100</concept_significance>
-% </concept>
-% <concept>
-%  <concept_id>10003033.10003083.10003095</concept_id>
-%  <concept_desc>Networks~Network reliability</concept_desc>
-%  <concept_significance>100</concept_significance>
-% </concept>
-%</ccs2012>
-%\end{CCSXML}
-
-%\ccsdesc[500]{Computer systems organization~Embedded systems}
-%\ccsdesc[300]{Computer systems organization~Redundancy}
-%\ccsdesc{Computer systems organization~Robotics}
-%\ccsdesc[100]{Networks~Network reliability}
-
-\ccsdesc{TBD}
-
-%%
-%% Keywords. The author(s) should pick words that accurately describe
-%% the work being presented. Separate the keywords with commas.
-\keywords{conversational agents, user perception, conversational architecture, anthropomorphized perceptions}
-
-%%\received{20 February 2007}
-%%\received[revised]{12 March 2009}
-%%\received[accepted]{5 June 2009}
-
-%%
-%% This command processes the author and affiliation and title
-%% information and builds the first part of the formatted document.
-\maketitle
-%TC:endignore
-
-\section{Introduction}
-
-Conversational agents (CAs), such as Amazon Alexa or Google Assistant, are designed to interact with humans using natural language through voice or text modalities.
-Since these agents interact with users using natural language, conversation architecture — which refers to what a CA says and how it says it — affects how these agents interact with users.
-The effectiveness of these interactions with CAs are strongly dependent on users' perceptions of agents \cite{knijnenburg2016inferring}\cite{seeger2021chatbots}.
-According to previous research, there is a correlation between CAs' conversation architecture and users' perception of these agents.
-
-While there are various studies on how different conversation architecture elements affects agents' perceptions, there is a paucity of knowledge on the overall coverage and effects of these relationships explored in literature.
-For conversation architecture elements, The use of affective language is commonly explored, with studies finding that conversational agents are perceived as more socially present and emotionally intelligent if they use sentiment-adaptive response based on user's utterances \cite{diederich2019emulating}\cite{yang2017perceived}.
-Another commonly explored element is the use of prosody in voice-based agents, such as the use of express prosody contributing to higher perceived enjoyment and intimacy with the agent \cite{kim2020can}.
-However, there is a lack of research to synthesize these findings into an overall framework.
-One of the possible issues is the lack of clear and consistent definitions on the aspects of user's perceptions of agent and conversation architectural elements.
-
-Currently there is no systematic understanding on the elements of conversation architecture that are relevant to perceptions of agents.
-Some papers have started to examine the speech specifics that are being explored in literature, such as Clark et al.
-\cite{clark2019state} capturing different elements of system speech production for voice-based agents and categorizing them based on content, style, and other topics.
-There are also some investigations of conversation architecture elements within the broader field of studying cues that trigger a social reaction of the user towards the CA.
-Feine et al's \cite{feine2019taxonomy} paper laid the foundation to create a consistent taxonomy for these social cues.
-However, there is no comprehensive research specifically for conversation architecture elements that are relevant to user perceptions.
-
-Related to user perceptions, there is also no systematic understanding on the perceptions of agents affected by speech variations.
-Some research discussed the perceptions of agents as part of the broader scope of user experiences of CAs.
-These publications have gathered UX dimensions used to evaluate conversational agents, which include the perceptions of agents (e.g.
-empathy, humanness) alongside other assessments (e.g.
-physiological data) \cite{clark2019state}\cite{finch2020towards}.
-Some even categorized the metrics based on the type of method used, including technical measures like system error rate and perception measures like perceived social presence \cite{zheng2022ux}.
-However, these studies are assessing the general field of UX measurements and not specifically on the perceptions of agents, and do not analyze the effects of conversation architecture on these perceptions.
-
-These research gaps discussed above: the paucity of knowledge on synthesizing the effect of speech specifics on perceptions of CAs as well as the lack of systematic understanding on the elements of conversation architecture and perceptions of agents motivated us to the goal of how to design conversation architecture in order to orchestrate perceptions of conversational agents.
-First, we want to understand \textbf{(RQ1) what perception aspects of agents are being explored in relation to the effects of conversation architecture elements}.
-While there are various architecture elements of conversation architecture used in a CA's utterances, we don't have a holistic understanding of them.
-This leads to our second research question: \textbf{(RQ2) what elements of conversation architecture are relevant to the perceptions of agents?} Lastly, we want to understand the effect of conversation architecture on perceptions of agent, specifically: \textbf{(RQ3) what are the relationships between conversation architecture elements and the perceptions of CAs?}
-
-To answer these questions, we performed a comprehensive review on existing literature from 2010 to 2022 and synthesized the effect of conversation architecture elements on the perceptions of CAs based on 57 relevant papers (Figure \ref{fig:heatmap-impact}).
-We also grouped the perceptions of agents affected by conversation architecture into four categories and eleven aspects (Table \ref{tab:perceptions}), and grouped the speech variations related to perceptions of agents into four categories and eleven elements (Table \ref{tab:cues}).
-%Lastly, we coded the explored connections between conversation architecture and perceptions and synthesized their relationships into a framework.
-Through our analysis, we also found that there are inconsistencies in the assessment of perceptions across studies, as well as influencing factors other than conversation architecture that impact the perceptions of agents.
-This work contributes to the HCI community by presenting a framework that demonstrates the effect of conversation architecture on perceptions of conversational agents, as well as taxonomies for perception aspects and conversation architecture elements providing clear and consistent terms that can be used in future research.
-Together, these contributions move us one step closer to designing CAs that effectively interact with users.
-%Also, our analysis extends existing reviews on UX research of CAs \cite{clark2019state}\cite{rapp2021human}\cite{zheng2022ux} by providing a synthesized framework outlining the relationships between conversation architecture and perceptions of agents.
-With the help of this framework, we are taking the first step to understand how to design conversational agents to solicit specific social reactions from users.
-
-In the remainder of the paper, we first outline related background work, our literature review process, as well as the characteristics of the papers in our reviewed corpus.
-Following that, we describe in detail the taxonomy for the perception of agents, the taxonomy for conversation architecture element, as well as the framework on the relationships between perceptions of agents and conversation architecture.
-Finally, we discuss research challenges and opportunities as well as ethical considerations for designing conversational architecture to orchestrate perceptions of conversational agents.
-
-\section{Literature Review}
-
-* human-human vs. human-AI
-
-* anthropomorphism
-%Anthropomorphism is defined as the attribution of traits that we typically associate with being distinctly human to nonhuman entities \cite{waytz2010sees}.
-For example, users tend to personify conversational agents like Amazon Alexa by using person pronouns instead of object pronouns in online reviews \cite{purington2017alexa}.
-Research shows that anthropomorphic design is beneficial to establishing and maintaining trust between users and conversational agents \cite{seeger2021chatbots}.
-Also, speakers tend to align their lexical choices with conversational agents, similar to human-human conversations \cite{cowan2015does}.
-Anthropomorphism has been shown to ease user interactions, e.g.
-making agents more approachable, engaging, and trustworthy when they exhibit human characteristics \cite{qiu2009evaluating}.
-These processes are of particular interest for human-agent communication because they form the basis for user expectations and predispositions regarding agents' behavior, reliability of the information, etc.
-\cite{kuzminykh2020genie}.
-
-* how to synthesize
-
-* user experience evaluations of conversational agents
-%Other papers categorized CA assessments into themes.
-For example, Rapp et al.
-\cite{rapp2021human} generated themes related to how users' experience with chatbots such as experiencing the chatbot including assessments on expectation, perception, satisfaction etc.
-Most recently, Zheng et al's literature review on the UX research of CAs \cite{zheng2022ux} categorized the metrics based on the type of method used, including technical measures like system error rate and perception measures like perceived social presence.
-However, existing studies use different terminologies and categories across aspects of perception.
-As an illustration, it is unclear if the theme of experiencing the chatbot from Rapp et al.
-\cite{rapp2021human} contains similar aspects to the perception towards CA in Zheng et al \cite{zheng2022ux}'s analysis.
-%\cite{finch2020towards} Towards unified dialogue system evaluation: A comprehensive analysis of current evaluation protocols
-
-\section{Methods}
-
-This section describes the research methodologies used for data collection and data analysis. Additionally, it presents the characteristics of the papers in our reviewed corpus.
-
-\subsection{Data Collection}
-
-Following PRISMA guidelines \cite{prisma}, we reviewed and selected literature exploring the relationship between the specifics of conversation architecture elements and perceptions of CAs.
-Searches were carried out in the ACM Digital Library between January 1 and January 15, 2023.
-Through our analysis, we didn't find any common terms used to refer to either conversation architecture elements, or aspects of perceptions.
-As such, we generalized our search term to capture articles related to conversational agents.
-Based on search terms used in previously published literature reviews \cite{clark2019state}\cite{rapp2021human}, the following keywords are used to search for publications related to conversational user interfaces:
-\newline
-
-\textit{"conversational agent" OR "natural language interface" OR "IPA" OR "intelligent personal assistant" OR "chatbot" OR "speech interface" OR "voice assistant" OR "intelligent agent" OR "human-chatbot communication" OR "virtual agent" OR "dialog* system" OR "voice user interface" OR "human computer dialog*"}
-\newline
-
-The following selection criteria are applied to identify literature related to the effect of conversational architecture on the perception of agents:
-\begin{itemize}
-  \item The paper was published between 2010 and 2022.
-  \item The paper is peer-reviewed and written in English.
-  \item The paper contains the use of voice-based or text-based conversational agents.
-  \item The paper contains studies on the impact of conversation architecture elements on the perceptions of agents.
-  \item The paper contains impact of conversation architecture elements can be separated from other effects (e.g. embodiment).
-
-\end{itemize}
-
-The initial query retrieved 2901 unique publications.
-We screened the titles and abstracts of the papers based on the selection criteria above, resulting in 221 papers.
-The fully body of these papers are then reviewed, selecting papers that met the criteria.
-A search for additional literature was also performed to supplement the corpus, adding 8 more papers to the selection.
-In total, we identified 57 relevant articles for analysis (see Figure \ref{fig:prisma}).
+%% PRISMA Process Visualization %%
 
@@
   \centering
-  \includegraphics[width=1\columnwidth]{fig-prisma.png}
+  \includegraphics[width=1\columnwidth]{figures/fig-prisma.pdf}
   \caption{Literature search using PRISMA guidelines}
@@
 \end{figure}
-
-\subsubsection*{Literature Corpus Characteristics}
-
-The papers reviewed (n=57) were published between May 2011 and November 2022.
-More than 75\% of the papers were published in or after 2019, with a slight trend upwards over the years (see Figure \ref{fig:paper}).
-The vast majority of the papers in our corpus were published in conference proceedings (n=50), with the remainder papers published in journals.
-Out of the papers published in conferences, the top conferences were The ACM Conference on Human Factors in Computing Systems\footnote{https://dl.acm.org/conference/chi} (n=16), Conversational User Interfaces\footnote{https://dl.acm.org/conference/cui} (n=7), Human-Agent Interaction\footnote{https://dl.acm.org/conference/hai} (n=4), and Intelligent Virtual Agents\footnote{https://dl.acm.org/conference/iva} (n=4).
-%Out of the papers published in journals, some venues include the International Journal of Human-Computer Interaction\footnote{https://www.tandfonline.com/journals/hihc20} (n=2) and Interacting with Computers\footnote{https://academic.oup.com/iwc} (n=1).
-
-On the modality characteristics of the conversational agents in the corpus, there is a roughly even split between the modalities, with slightly more papers exploring voice-based CAs (n=30) compared to text-based CAs (n=27).
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=\columnwidth]{fig-paper.png}
-  \caption{Number of papers by year}
-  \label{fig:paper}
-\end{figure}
-
-\subsection{Data Analysis}
-
-\subsubsection*{Perceptions of Agents} To understand the perceptions of agents related to conversation architecture (RQ1), assessments for the perceptions of agents were extracted from each paper.
-We used inductive thematic analysis to group these assessments into codes based on their meanings.
-For example, the code likeability of the agent contains the questionnaire item "this voice agent was likeable" used by \cite{cuadra2021my}\cmt{[67]}, Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed}'s set of questions on likeability used by \cite{linnemann2018can}\cmt{[15]}, and Subjective Assessment of Speech System Interface (SASSI) questionnaire \cite{hone2000towards}\cmt{sassi}'s set of questions on likeability used by \cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}.
-This step resulted in 83 unique codes.
-These codes are then organized based similarity of the meanings, resulting in 11 aspects of perceptions.
-For example, the aspect of personality traits of the agent contains measurements such as likeability, funniness, and kindness.
-Lastly, the 11 aspects are grouped into 4 categories: perception of interaction with agent, perception of agent's ability, perception of sociability with agent, and perception of agent's humanness (Table \ref{tab:perceptions}).
-
-\subsubsection*{Conversation Architecture Elements}
-As to the elements of conversation architecture that are relevant to the perception of agents (RQ2), we extracted the specifics of conversation architecture used in each paper.
-Some of the papers used multiple features in their CA design, such as the the anthropomorphic agent used in Seeger et al's study \cite{seeger2021chatbots}\cmt{[35]}.
-In these composite situations, we broke them down into their individual features.
-For example, the anthropomorphic agent \cite{seeger2021chatbots}\cmt{[35]} was separated into emotional expressions, is-typing indicator, emoticons, and response delay and captured as codes.
-58 unique codes were created as part of this process, capturing features like sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}, lexical alignment \cite{spillner2021talk}\cmt{[18]}, and typos \cite{westerman2019believe}\cmt{[9]}.
-We then organized these codes into elements based on similarity, resulting in 12 elements of conversation architecture.
-For example, the element of disfluency contains fillers \cite{jeong2019exploring}\cmt{[10]}\cite{wester2015artificial}\cmt{[14]}, interjections \cite{ceha2022expressive}\cmt{[77]}\cite{hu2021enhancing}\cmt{[56]}, repetitions \cite{yang2021effect}\cmt{[72]} and typos \cite{westerman2019believe}\cmt{[9]}.
-These elements are grouped into 4 categories: dialog strategy, content affectiveness, content style, and speech format (Table \ref{tab:cues}).
-
-\subsubsection*{Relationship Between Perceptions of Agents and Conversation Architecture}
-To study the effect of conversation architecture on users' perceptions (RQ3), we extracted the connections explored in each paper, using the perception aspects and conversation architecture elements developed in the previous data analysis steps.
-Each connection's effect was also recorded based on whether an association was found in the study and the nature of that association.
-Out of our review corpus, 265 connections between perceptions of agents and conversation architecture were explored in literature.
-To analyze the specifics of conversation architecture that affect the perceptions of CAs, 72 connections that did not result in observed relationships were discarded, resulting in 193 relationships for analysis.
-For example, the connection between the matching style of a CA and user satisfaction was removed because Hoegen et al.
-\cite{hoegen2019end}\cmt{[31]} did not find a significant difference between the style matching agent and the non-style matching agent for overall interaction satisfaction.
-Out of the 193 relationships, 10 were relationships based on agents modifying multiple architecture elements (e.g.
-\cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2021manipulating}\cmt{[68]}).
-They were not included in the final framework as we could not attribute the perceptions of agents to the underlying core elements.
-Overall, 183 relationships between individual architecture elements and perceptions of agents are incorporated into our synthesized framework, visualized as a heatmap to demonstrate their relationships with each other (Figure \ref{fig:heatmap-impact}).
-
-\section{Findings}
-
-\begin{figure*}[]
-  \centering
-  \includegraphics[width=\textwidth]{fig-heatmap-impact.png}
-  \caption{Heatmap of literature for perception of conversational agents for each type of conversational architecture element}
-  \label{fig:heatmap-impact}
-\end{figure*}
-
-\subsection{Perceptions of Agents}
-
-As shown in Table \ref{tab:perceptions}, there are four categories defined for the perceptions of conversational agents covering 11 different aspects of perception.
-The details of each category and aspect are discussed below.
-
-\textbf{Perception of interaction with agent} assesses the overall interaction quality users had with the conversational agent.
-The three aspects for this perceptions are usability, engagement and satisfaction.
-\textit{Usability} captures the utilitarian component of the interaction, whether it was accurate, easy to use, efficient or helpful.
-Some commonly used methods to evaluate usability include the response accuracy portion of the SASSI questionnaire \cite{hone2000towards}\cmt{sassi}, or the NASA Task Load Index (NASA-TLX) \cite{hart1988development}\cmt{nasa} for cognitive workload.
-Questions such as "the system is easy to use" or "it is easy to understand the agent" are also used to evaluate usability.
-\textit{Engagement} on the other hand captures users' emotional reactions to the CA, whether they have enjoyed the conversation, or annoyed or frustrated with the interaction.
-Some commonly used methods to evaluate engagement include the annoyance portion of the SASSI questionnaire \cite{hone2000towards}\cmt{sassi}, and the Use Engagement Scale (UES) \cite{o2018practical}\cmt{ues}.
-Questions such as "I enjoyed using the system" or "I felt frustrated with the agent" are also used to evaluate engagement.
-Lastly, \textit{Satisfaction} captures users' overall satisfaction interacting with the agent.
-Questions such as "the overall assessment of conversing with the CA was satisfactory" are used to evaluate this perception.
-
-\textbf{Perception of agent's ability} assesses the perceived capabilities of the agent.
-Unlike system capabilities that affect agent's performance, the perceived ability category captures perceptions of agents with equivalent system capabilities but varied conversation architecture elements.
-Specifically, \textit{intelligence} captures the agent's expertise and knowledge, and it is commonly administered through the Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed} using the set of questions related to perceived intelligence.
-Also survey questions such as asking users about the agent's intelligence and domain knowledge are used to evaluate perceived intelligence.
-\textit{Competence} takes intelligence one step further by examining the agent's ability to put its intelligence into practice.
-Surveys or qualitative feedback are usually used to assess if the agent is capable and competent, and whether users have confidence in the agent's ability to get the job done.
-Lastly, \textit{credibility} captures agent's truthfulness, benevolence, and user's confidence in CAs.
-Some commonly used methods to evaluate trust include the Trust Propensity Scale \cite{mayer1999effect} and the Individualized Trust Scale (ITS) \cite{wheeless1977measurement}.
-Questions such as "is the agent honest" and "can I trust the agent with sensitive information" are also used to evaluate trust.
-
-\textbf{Perception of the sociability with agent} assesses the emotional connections that users have with agents.
-This category includes perception aspects of conversation tone, social presence and intimacy.
-\textit{Conversation tone} captures the affective impression of the agent's tone, such as empathy and expressiveness.
-Also, this aspect includes whether the tone used by the agent was perceived as friendly, polite or warm.
-\textit{Social presence} captures the sense of connectness and psychological distance users have with an agent.
-Some aspects in this category include the sense of familiarity or similarity with the agent, and whether users feel the agent behaves like them or have similar attitudes to them.
-The category of \textit{Intimacy} extends social presence into the realm of the quality of relationships with an agent.
-Some commonly used methods to assess intimacy include the set of social attraction questions from the interpersonal attraction questionnaire \cite{mccroskey1975development} and the quality of relationship inventory (QRI) \cite{pierce1997assessing}.
-These questionnaires include questions like "I think the agent could be a friend of mine", or "I feel we could establish a personal relationship with each other".
-
-\textbf{Perception of agent's humanness} assesses the specifics of anthropomorphized perceptions of conversational agents.
-\textit{Human-likeness} captures whether the agent presented itself as natural and human-like, or artificial and machine-like.
-The Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed} set of questions related to anthropomorphism and the Ascent of Man scale \cite{kteily2015ascent} are commonly used methods to evaluate human-likeness.
-Survey questions with semantic scales such as "human-like / machine-like" and "artificial / natural" are also commonly used for this aspect of perception.
-\textit{Personality traits} captures the human characteristics that are attributes to the agent.
-This is commonly collected as qualitative feedback from users, commenting on whether the agent is extroverted or introverted, or the perceived personality such as likeable, funny or witty.
-Sometimes the Big-5 personality traits questionnaire \cite{gosling2003very} is used to map an agent's disposition on various personality dimensions.
-
-Overall there is a good coverage of different aspects of perception based on the list of papers reviewed in our corpus.
-The most commonly explored aspect categories is the perception the interaction with agent, followed by the perception of agent's humanness.
-There are two aspects that are the least explored compared to the others relationships: competence within the perception of agent's ability, and intimacy within the perception of social connection with agent.
-This may be due to the controlled lab settings for the experiments, where participants are given the scenarios for interaction.
-This type of environment is not conducive to forming relationships with a conversational partner, as noted by Linnerman et al.
-in their discussions \cite{linnemann2018can}\cmt{[15]}.
-The same factor could impact the assessment of agent's competence, as the users may not feel like they have the expertise to assess their perceptions.
-%These factors could contribute to the reasons why competency and intimacy are not as frequently measured in experimental studies.
-
-\begin{table*}[ht]
-\renewcommand*{\arraystretch}{1.4}
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{@{}p{0.17\textwidth} | p{0.12\textwidth} | p{0.20\textwidth} | >{\centering}p{0.09\textwidth} | p{0.42\textwidth} @{}}
-%!{\vrule width 1.2pt} 
-\Xhline{1.2pt}
-\multicolumn{2}{l|}{\textbf{Perception Aspects}} & \textbf{Examples} & \textbf{No. Papers} & \textbf{Papers} 
-\\ \Xhline{1.2pt}
-\multirow{3}{*}{\parbox{0.17\textwidth}{Perception of \newline Interaction with Agent}}
-    & Usability & accuracy, ease of use, \newline efficiency, helpfulness & 23 
-    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2022expressive}\cmt{[77]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cuadra2021my}\cmt{[67]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{elsholz2019exploring}\cmt{[61]}\cite{haas2022keep}\cmt{[78]}\cite{habler2019effects}\cmt{[63]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2019comparing}\cmt{[89]}\cite{kim2020can}\cmt{[24]}
-    \cite{kraus2020effects}\cmt{[64]}\cite{linnemann2018can}\cmt{[15]}\cite{ma2022ask}\cmt{[29]}\cite{miehle2018exploring}\cmt{[51]}\cite{misu2011toward}\cmt{[83]}\cite{roy2021users}\cmt{[71]}\cite{spillner2021talk}\cmt{[18]}\cite{wilhelm2022keep}\cmt{[28]}
-\\ \cline{2-5}
-    & Engagement & enjoyment, annoyance, \newline desirable, intention to use  & 28
-    & \cite{andrews2012system}\cmt{[38]}\cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cox2022does}\cmt{[27]}\cite{cuadra2021my}\cmt{[67]}\cite{elsholz2019exploring}\cmt{[61]}\cite{fadhil2018effect}\cmt{[52]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{go2021conversational}\cmt{[80]}\cite{healey2013relating}\cmt{[39]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2020can}\cmt{[24]}\cite{kim2019comparing}\cmt{[89]}
-    \cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{ma2022ask}\cmt{[29]}\cite{miehle2018exploring}\cmt{[51]}\cite{miyamoto2017improving}\cmt{[46]}\cite{moilanen2022measuring}\cmt{[82]}\cite{roy2021users}\cmt{[71]}\cite{spillner2021talk}\cmt{[18]}\cite{volkel2021examining}\cmt{[69]}\cite{volkel2022user}\cmt{[75]}\cite{xiao2021let}\cmt{[73]}\cite{yang2021effect}\cmt{[72]}\cite{zhu2022effects}\cmt{[26]}
-\\ \cline{2-5}
-    & Satisfaction & service satisfaction, quality of interaction & 12
-    & \cite{ceha2022expressive}\cmt{[77]}\cite{choi2020nobody}\cmt{[54]}\cite{diederich2019emulating}\cmt{[25]}\cite{elsholz2019exploring}\cmt{[61]}\cite{habler2019effects}\cmt{[63]}\cite{gnewuch2018faster}\cmt{[19]}\cite{hoegen2019end}\cmt{[31]}\cite{hu2022polite}\cmt{[76]}\cite{ma2022ask}\cmt{[29]}\cite{roy2021users}\cmt{[71]}\cite{wilhelm2022keep}\cmt{[28]}\cite{yang2017perceived}\cmt{[44]}
-\\ \Xhline{1.2pt} 
-\multirow{3}{*}{\parbox{0.16\textwidth}{Perception of Agent's Ability}}
-    & Intelligence & knowledgeable, intelligent, expertise & 11
-    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cuadra2021my}\cmt{[67]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{feijoo2021effects}\cmt{[70]}\cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}\cite{spillner2021talk}\cmt{[18]}\cite{volkel2022user}\cmt{[75]}\cite{yang2017perceived}\cmt{[44]}
-\\ \cline{2-5}
-    & Competence & competent, appropriate & 6 
-    & \cite{cox2022does}\cmt{[27]}\cite{kraus2020effects}\cmt{[64]}\cite{jestin2022effects}\cmt{[81]}\cite{lee2019s}\cmt{[55]}\cite{misu2011toward}\cmt{[83]}\cite{westerman2019believe}\cmt{[9]}
-\\ \cline{2-5}
-    & Trust & credibility, trustworthy, truthfulness, confidence & 15
-    & \cite{andrews2012system}\cmt{[38]}\cite{chan2021kinvoices}\cmt{[74]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{fadhil2018effect}\cmt{[52]}\cite{healey2013relating}\cmt{[39]}\cite{hoegen2019end}\cmt{[31]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kraus2020effects}\cmt{[64]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{ma2022ask}\cmt{[29]}\cite{seeger2021chatbots}\cmt{[35]}\cite{tolmeijer2021female}\cmt{[62]}\cite{wilhelm2022keep}\cmt{[28]}
-\\ \Xhline{1.2pt} 
-\multirow{3}{*}{\parbox{0.16\textwidth}{Perception of \newline Sociability with Agent}}
-    & Conversation Tone & friendly, warm, empathetic, persuasive & 20 
-    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cox2022does}\cmt{[27]}\cite{cuadra2021my}\cmt{[67]}\cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{healey2013relating}\cmt{[39]}\cite{hu2021enhancing}\cmt{[56]}\cite{hu2022polite}\cmt{[76]}\cite{jestin2022effects}\cmt{[81]}\cite{khooshabeh2011does}\cmt{[37]}\cite{kim2019comparing}\cmt{[89]}\cite{lee2019s}\cmt{[55]}\cite{miehle2018exploring}\cmt{[51]}
-    \cite{moilanen2022measuring}\cmt{[82]}\cite{tolmeijer2021female}\cmt{[62]}\cite{yang2021effect}\cmt{[72]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}
-\\ \cline{2-5}
-    & Social Presence & connectedness, familiarity, psychological distance & 18
-    & \cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cuadra2021my}\cmt{[67]}\cite{diederich2019emulating}\cmt{[25]}\cite{gnewuch2018faster}\cmt{[19]}\cite{gnewuch2018chatbot}\cmt{[21]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{go2021conversational}\cmt{[80]}\cite{khooshabeh2011does}\cmt{[37]}\cite{kim2020can}\cmt{[24]}\cite{lee2019s}\cmt{[55]}\cite{lubis2019positive}\cmt{[43]}\cite{lubold2016effects}\cmt{[86]}
-    \cite{ma2022ask}\cmt{[29]}\cite{niewiadomski2013laugh}\cmt{[85]}\cite{westerman2019believe}\cmt{[9]}    
-\\ \cline{2-5}
-    & Intimacy & intimate, rapport, quality of relationship & 7 
-    & \cite{choi2020nobody}\cmt{[54]}\cite{khooshabeh2011does}\cmt{[37]}\cite{kim2020can}\cmt{[24]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{lubold2016effects}\cmt{[86]}\cite{westerman2019believe}\cmt{[9]}
-\\ \Xhline{1.2pt}
-\multirow{2}{*}{\parbox{0.16\textwidth}{Perception of Agent's Humanness}}
-    & Human-likeness & human-like, natural, \newline artificial, machine-like & 20
-    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cox2022does}\cmt{[27]}\cite{diederich2019emulating}\cmt{[25]}\cite{gnewuch2018faster}\cmt{[19]}\cite{haas2022keep}\cmt{[78]}\cite{hu2022polite}\cmt{[76]}\cite{jeong2019exploring}\cmt{[10]}\cite{jestin2022effects}\cmt{[81]}\cite{lubis2019positive}\cmt{[43]}\cite{ma2022ask}\cmt{[29]}\cite{misu2011toward}\cmt{[83]}\cite{niewiadomski2013laugh}\cmt{[85]}
-    \cite{ouchi2019should}\cmt{[59]}\cite{seeger2021chatbots}\cmt{[35]}\cite{wester2015artificial}\cmt{[14]}\cite{westerman2019believe}\cmt{[9]}\cite{zhu2022effects}\cmt{[26]}    
-\\ \cline{2-5}
-    & Personality Traits & likeable, kind, witty, funny, creepy & 20
-    & \cite{andrews2012system}\cmt{[38]}\cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cuadra2021my}\cmt{[67]}\cite{haas2022keep}\cmt{[78]}\cite{habler2019effects}\cmt{[63]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{huiyang2022improving}\cmt{[17]}\cite{jeong2019exploring}\cmt{[10]}\cite{kim2019comparing}\cmt{[89]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{miehle2018exploring}\cmt{[51]}
-    \cite{ouchi2019should}\cmt{[59]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}\cite{wester2015artificial}\cmt{[14]}\cite{zhu2022effects}\cmt{[26]} 
-\\ \Xhline{1.2pt}
-\end{tabular}%
-}
-\caption{Perception aspects}
-\label{tab:perceptions}
-\end{table*}
-
-\begin{table*}[h]
-\resizebox{\textwidth}{!}{
-\renewcommand*{\arraystretch}{1.4}
-\begin{tabular}{@{}p{0.17\textwidth} | p{0.14\textwidth} | p{0.25\textwidth} | >{\centering}p{0.09\textwidth} | p{0.34\textwidth} @{}}
-\Xhline{1.2pt}
-\multicolumn{2}{l|}{\textbf{Conversation Architecture Elements}} & \textbf{Examples} & \textbf{No. Papers} & \textbf{Papers}
-\\ \Xhline{1.2pt}
-\multirow{3}{*}{Dialog Strategy} & Social Dialog & social talk, self-disclosure  & 7
-& \cite{andrews2012system}\cmt{[38]}\cite{lee2020hear}\cmt{[23]}\cite{lubold2016effects}\cmt{[86]}\cite{moilanen2022measuring}\cmt{[82]}\cite{roy2021users}\cmt{[71]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}
-\\ \cline{2-5}
-
-& Initiative & proactive dialogue, conversation \newline repair & 4
-& \cite{ashktorab2019resilient}\cmt{[88]}\cite{cuadra2021my}\cmt{[67]}\cite{kraus2020effects}\cmt{[64]}\cite{xiao2021let}\cmt{[73]}
-\\ \cline{2-5}
-
-& Response Delay & response delay, typing indicator & 4
-& \cite{gnewuch2018faster}\cmt{[19]}\cite{gnewuch2018chatbot}\cmt{[21]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{seeger2021chatbots}\cmt{[35]}
-\\ \Xhline{1.2pt}
-
-\multirow{2}{*}{Content Affectiveness} & Affective Language & emotional expressions, sentiment-adaptive responses & 11
-& \cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{lee2019s}\cmt{[55]}\cite{lubis2019positive}\cmt{[43]}\cite{moilanen2022measuring}\cmt{[82]}\cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2022user}\cmt{[75]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}
-\\ \cline{2-5}
-
-& Humour & humorous content, jokes & 6
-& \cite{ceha2021can}\cmt{[57]}\cite{go2021conversational}\cmt{[80]}\cite{khooshabeh2011does}\cmt{[37]}\cite{miyamoto2017improving}\cmt{[46]}\cite{niewiadomski2013laugh}\cmt{[85]}\cite{volkel2021manipulating}\cmt{[68]}
-\\ \Xhline{1.2pt}
-
-\multirow{3}{*}{Content Style} & Formality & formal vs. casual, honorific \newline expressions & 9
-& \cite{cox2022does}\cmt{[27]}\cite{elsholz2019exploring}\cmt{[61]}\cite{habler2019effects}\cmt{[63]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2019comparing}\cmt{[89]}\cite{ma2022ask}\cmt{[29]}\cite{moilanen2022measuring}\cmt{[82]}\cite{ouchi2019should}\cmt{[59]}\cite{volkel2022user}\cmt{[75]}
-\\ \cline{2-5}
-
-& Alignment & content matching, lexical \newline alignment, agreeableness & 7
-& \cite{healey2013relating}\cmt{[39]}\cite{hoegen2019end}\cmt{[31]}\cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}\cite{spillner2021talk}\cmt{[18]}\cite{volkel2021examining}\cmt{[69]}\cite{volkel2021manipulating}\cmt{[68]}
-\\ \cline{2-5}
-
-& Elaborateness & elaborate, concise, sentence \newline structure & 6
-& \cite{haas2022keep}\cmt{[78]}\cite{miehle2018exploring}\cmt{[51]}\cite{moilanen2022measuring}\cmt{[82]}\cite{roy2021users}\cmt{[71]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}
-\\ \Xhline{1.2pt}
-
-\multirow{3}{*}{Speech Format} & Prosody & pitch, intonation, speech rate, \newline spoken accent & 12
-& \cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{feijoo2021effects}\cmt{[70]}\cite{habler2019effects}\cmt{[63]}\cite{hu2021enhancing}\cmt{[56]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2020can}\cmt{[24]}\cite{lubold2016effects}\cmt{[86]}\cite{misu2011toward}\cmt{[83]}\cite{tolmeijer2021female}\cmt{[62]}\cite{zhu2022effects}\cmt{[26]}
-\\ \cline{2-5}
-
-& Disfluency & fillers, interjections, repetitions, \newline typos & 6
-& \cite{ceha2022expressive}\cmt{[77]}\cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}\cite{wester2015artificial}\cmt{[14]}\cite{westerman2019believe}\cmt{[9]}\cite{yang2021effect}\cmt{[72]}
-\\ \cline{2-5}
-
-& Text Formatting & capitalization, emoticons & 6
-& \cite{fadhil2018effect}\cmt{[52]}\cite{kim2019comparing}\cmt{[89]}\cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2022user}\cmt{[75]}\cite{westerman2019believe}\cmt{[9]}\cite{wilhelm2022keep}\cmt{[28]}
-\\ \Xhline{1.2pt}
-\end{tabular}%
-}
-\caption{Conversation architecture elements}
-\label{tab:cues}
-\end{table*}
-
-\subsection{Conversation Architecture Elements}
-
-As shown in Table \ref{tab:cues}, there are four categories defined for conversation architecture across 12 different elements. The details of each category and element are discussed below.
-
-The category of \textbf{dialog strategy} refers to the approach used by a conversational agent to engage in a dialogue with a user, which includes the use of social dialogs, agent-initiated content, and adding delays to responses.
-Specifically, the element of \textit{social dialogue} captures non-task related conversations with the user to build social connection, such as self-disclosure \cite{lee2020hear}\cmt{[23]} and small talk like chitchats \cite{lubold2016effects}\cmt{[86]}\cite{volkel2021manipulating}\cmt{[68]}.
-The element of \textit{initiative} captures utterances that are initiated by the agent without direct prompts from the user.
-For example, the agent is taking the initiative to proactively repair the conversation with a user \cite{ashktorab2019resilient}\cmt{[88]}\cite{cuadra2021my}\cmt{[67]}, or actively elicit feedback from users \cite{xiao2021let}\cmt{[73]}.
-Lastly, \textit{response delay} refers to the tactic of deliberatively delaying for a certain period of time before an agent responds to users \cite{gnewuch2018faster}\cmt{[19]}\cite{gnewuch2022opposing}\cmt{[20]}.
-It is mainly used in text-based CAs alongside visual displays of typing indicators \cite{gnewuch2018chatbot}\cmt{[21]}.
-
-\textbf{Content affectiveness} refers to the conversational agent's use of language to convey emotions or to elicit emotions from users.
-The architecture element of \textit{affective language} captures the injection of emotional words or phrases into the agent's utterance, such as affective expressions \cite{seeger2021chatbots}\cmt{[35]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}, sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}, and encouraging words \cite{healey2013relating}\cmt{[39]}.
-The other element in this category, \textit{humour}, captures an agent's attempt to include jokes in its dialog.
-Several studies in our reviewed corpus have explored the effect of humour on various perceptions of agents (e.g.
-\cite{ceha2021can}\cmt{[57]}\cite{khooshabeh2011does}\cmt{[37]}).
-
-The category of \textbf{content style} refers to the variations of language used in a message aside from the content meaning of the message (i.e.
-how something is said).
-The element of \textit{formality} describes the linguistic style used by the conversational agent, whether it is formal vs.
-casual, such as using honorific expressions to address users \cite{ouchi2019should}\cmt{[59]}.
-\textit{Alignment} captures the degree that the agent aligns its utterances to the users, such as lexical alignment on the content and structural of the sentences \cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}, as well as referring and agreeing with users' utterances \cite{volkel2021examining}\cmt{[69]}.
-Lastly, the element of \textit{elaborateness} captures the sentence complexity and length of agents' utterances.
-For example, Roy et al.
-explored the differences in perception for variations in elaborateness such as "Cloudly, possibility of snow, high: 4, low: -10" vs "Today will be cloudy, with a high of 4 and a low of -10.
-Snow is predicted" \cite{roy2021users}\cmt{[71]}.
-
-Lastly, the category of \textbf{speech format} captures the non-verbal component of a conversational agent's utterances for both text and voice modalities. \textit{Disfluency} captures 
-the use of non-lexical utterances like filler words ("um, uh") \cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}, or repetition of words within a sentence \cite{yang2021effect}\cmt{[72]}.
-It also includes the format of using typos \cite{westerman2019believe}\cmt{[9]} for text-based agents.
-For voice-based agents specifically, the element of \textit{prosody} encompasses vocal qualities like pitch \cite{habler2019effects}\cmt{[63]}\cite{jestin2022effects}\cmt{[81]}, speech rate \cite{choi2020nobody}\cmt{[54]}, and spoken accent \cite{feijoo2021effects}\cmt{[70]}.
-For text-based CAs, the \textit{text formatting} element includes different formats agents uses to present information to users, such as using capitalization \cite{westerman2019believe}\cmt{[9]} or emoticons \cite{kim2019comparing}\cmt{[89]}\cite{wilhelm2022keep}\cmt{[28]}.
-
-Overall there are similar number of conversation architecture elements explored across the four categories of dialog strategy, content affectiveness, content style, and speech format.
-As for explorations related to different modalities of agents, there is a noticeable difference in the category of speech format, where architecture elements related to voice-based agents (n=15) are explored more than text-based agents (n=7).
-Looking across the 12 different elements, there is good coverage of studies on the impact of affective language and prosody cues on the perceptions of agents.
-However, there are less studies exploring the effect of agent initiated content and response delay on the perception of agents.
-Specifically for the element of initiative under dialog strategy category, there is literature on conversation repairs \cite{komatani2010online}\cite{reinkemeier2022repair} and agent proactively sharing content with users \cite{dubiel2019inquisitive}\cite{zargham2022understanding}, but many of them did not not include assessments of perceptions of the CA.
-This may be due to the fact that the usage of agent-initiated content is relatively new, as CA interactions have historically been driven by users.
-As such, current research is focused on the functional aspects of agents initiating contents instead of exploring the perceptions of agents.
-As for response delay, there are indications that this element is under-explored in literature.
-Only 4 studies in our reviewed corpus used an agent with response delay, and the majority of these publications were written by the same authors.
-
-\subsection{Relationship Between Perceptions of Agents and Conversation Architecture}
-
-There are 183 identified relationships between perceptions of agents and conversation architecture out of the 265 explored connections that are included in our synthesized framework (Figure \ref{fig:heatmap-impact}).
-To compare the number of identified relationships vs.
-the explored connections in literature, Figure \ref{fig:heatmap-coverage} shows a side-by-side comparison between the two.
-The detailed analysis on the differences between explored and identified relationships are discussed in the subsections below.
-
-While the number of papers studying CAs with voice (n=27) vs.
-text (n=30) modalities is not significantly different, there are some interesting patterns we found with regards to the modalities of the identified relationships between perceptions of agents and conversation architecture.
-Overall, we confirmed the pattern found earlier that there are more conversation architecture elements explored related to voice vs.
-text in the speech format category.
-Because there are smaller number of text-based CAs using speech format elements, we also observed significantly less number of relationships between text-based CA across all perceptions of agents.
-other interesting findings related to modality are discussed later in this paper.
-
-\begin{figure*}[]
-  \centering
-  \includegraphics[width=\textwidth]{fig-heatmap-coverage.png}
-  \caption{Heatmap of literature for perception of conversational agents for each type of conversational architecture element}
-  \label{fig:heatmap-coverage}
-\end{figure*}
-
-\subsubsection{Perception of Interaction with Agent}
-
-The effects of conversation architecture elements on the perception of interaction with agent is the most explored connections in the corpus (n=97).
-Out of these explored connections, the majority of them (n=66) discovered a relationship between aspects of perception related to the perception of interaction with agent related to the studied architecture element.
-Looking at the difference between modalities, we noticed more voice-based agents (n=25) resulted in null relationships compared to text-based agents (n=6).
-The conversation architecture element of \textit{alignment} contributed the most to the null results for voice-based agents, with 9 out of 11 explored connections did not find any relationships related the perception of interaction with agents.
-
-Across the aspects for the perception of interaction, both usability and engagement were assessed frequently in the reviewed literature, with conversation architecture having effects on these perception aspects across all architecture element categories.
-The aspect of satisfaction was used in some studies to evaluate perception but it is not used as often as engagement or usability.
-Several papers that assessed user satisfactions were conversation agents within the transaction context, especially within the customer service domain (e.g.
-\cite{diederich2019emulating}\cmt{[25]}\cite{elsholz2019exploring}\cmt{[61]}\cite{gnewuch2018faster}\cmt{[19]}).
-
-The category of conversation architecture elements with the most identified relationships to perceptions of interaction is content style.
-Specifically for the element of \textit{elaborateness}, users found the use of full sentences more useful than keyword only \cite{haas2022keep}\cmt{[78]}\cite{roy2021users}\cmt{[71]}.
-Otherwise, the effect of an agent's elaborateness on user's perception of interaction depends on the user's preference \cite{miehle2018exploring}\cmt{[51]}, as well as the topic of discussion \cite{haas2022keep}\cmt{[78]}.
-As for \textit{formality}, various studies reported significant differences in perceptions of interaction between using casual vs.
-formal styles.
-Some users experienced higher engagement with agent interacting with the casual style of the conversation \cite{cox2022does}\cmt{[27]}, while in another study users reported the formal language style as less engaging as it is boring \cite{kim2019comparing}\cmt{[89]}.
-
-The speech format of an agent also resulted in a high number of identified relationships with the perception of interaction with CAs, with majority of the explored connections resulted in effects between the perception aspects and architecture elements.
-The element with the most identified relationships is \textit{prosody}.
-For example, studies found that a CA's expressiveness in vocal cues increased participants' engagement ratings \cite{zhu2022effects}\cmt{[26]}, and different pitches of voice affect users' perception of engagement and usability \cite{chan2021kinvoices}\cmt{[74]}\cite{habler2019effects}\cmt{[63]}.
-
-Dialog strategy and content affectiveness categories of conversation architecture did not have as many identified relationships with perceptions of interaction.
-It is worth noting the effect of using the \textit{initiative} element, as CAs that use self-initiated content are perceived as more efficient and higher quality of interaction (e.g.
-\cite{cuadra2021my}\cmt{[67]}).
-Also, some studies have discovered conflicting effects between different perception aspects of interaction for CAs using \textit{social dialog}, as users enjoyed the conversation using social talk \cite{lee2020hear}\cmt{[23]}\cite{roy2021users}\cmt{[71]}, but perceived the CA as less efficient \cite{roy2021users}\cmt{[71]}.
-
-\subsubsection{Perception of Agent's Ability}
-
-The effects of conversation architecture elements on the perception of agent's ability is the least explored connection in the corpus (n=39).
-Out of these explored connections, the majority of them (n=30) found relationships between the studied architecture element and the perceptions of agent's ability.
-There are no notable differences between the text and voice modalities of CAs for either explored connections or the identified relationships.
-
-Aspects within the perception of agent's ability had similar number of identified relationships across intelligence, competence and credibility.
-Our review revealed that the perceived ability of a CA is also dependent on other influencing factors in addition to conversation architecture elements.
-Volkel et al.
-\cite{kraus2020effects}\cmt{[64]} found that the perception of competence of a proactive CA is dependent on task difficulty \cite{kraus2020effects}\cmt{[64]}.
-Also, the perception of intelligence for an agent using fillers depended on the context of the conversation, as the filler-speaking agent was perceived as less intelligent in task-oriented conditions, but was seen as slightly more intelligent in social-oriented conditions \cite{jeong2019exploring}\cmt{[10]}.
-
-Out of the explored conversation architecture elements, \textit{prosody} had relationships identified with aspects across the perception category of agent's ability.
-For example, Chan et al.
-\cite{chan2021kinvoices}\cmt{[74]} found that agents using kin's voices are rated as more intelligent and credible than generic voices.
-Also, the style of speech used by an agent affects the perception of appropriateness of tone, which is an aspect of the perceived competence of an agent \cite{misu2011toward}\cmt{[83]}.
-Different content styles of \textit{formality} also impacts the perceived competence of an agent \cite{cox2022does}\cmt{[27]}\cite{jestin2022effects}\cmt{[81]}.
-Specifically related to perceived credibility of an agent, being \textit{lexically aligned} with the user resulted improved the rating of trustworthiness of an agent \cite{hoegen2019end}\cmt{[31]}\cite{linnemann2018can}\cmt{[15]}.
-There were mixed results on the use of emoticons within the \textit{text formatting} element.
-One study found the chatbot using emoticons as less trustworthy \cite{wilhelm2022keep}\cmt{[28]}, while another study found that users assigned higher scores for confidence to the agent using emojis \cite{fadhil2018effect}\cmt{[52]}.
-
-There are several conversation architecture elements with little to no explorations to the perception of agent's ability.
-Specifically, both categories of dialog strategy and content affectiveness are minimally explored in our reviewed corpus, with no explored connections with \textit{response delay} and only one or two connections explored for \textit{social dialog} and \textit{humour}.
-While the content style category had coverage in some aspects of perceived abilities, it is worth noting that \textit{elaborateness} did not have any explored connections with perceived ability of agents.
-Further research in these areas is needed to fill these gaps in understanding.
-
-\subsubsection{Perception of Sociability with Agent}
-
-The perception of agent's humanness is the second most explored category within our reviewed corpus (n=64), with majority of the connections identified relationship between the studied conversation architecture elements and the anthropomorphized perceptions of agent (n=49).
-Interestingly, studies explored more perceptions of sociability with agent related to voice-based CAs (n=40) compared to text-based CAs (n=24), potentially due to the assumption that interactions with text-based agents are perceived as less personal and more formal \cite{kocielnik2018designing}.
-There are some mixed results for voice-based CAs, as 12 out of the 28 connections did not find any significant results.
-Drilling down to the specific elements, we noticed that the use of \textit{alignment} in voice-based agents did not effect the perception of sociability with agent \cite{healey2013relating}\cmt{[39]}\cite{linnemann2018can}\cmt{[15]}.
-We didn't have data on text-based agents' perceived social connections with users to compare with voice-based agents, as the studies using alignment and text modality in our corpus did not assess this aspect category of perception.
-
-Across the aspects in this perception category, conversation tone had the most number of identified relationship (n=27) with the perceived social connection with CAs, followed by the aspect of social presence (n=17).
-There are only 5 relationships found that are linked to the perception aspect of intimacy.
-One reason for this is half of the explored connections did not have any effect on the perception of sociability with agent, such as the use of capitalization \cite{westerman2019believe}\cmt{[9]}, lexical alignment \cite{linnemann2018can}\cmt{[15]}, or social talk \cite{lubold2016effects}\cmt{[86]}.
-For the perception aspect of social presence, we noticed a gap in the exploration of conversation architecture elements of formality, alignment, and elaborateness in the content style category, as there are no papers explored at this intersection.
-
-Looking at the different categories of conversation architecture elements, the heatmap (Figure \ref{fig:heatmap-impact} shows that there are not many relationships in content style category that are related to the perceived sociability with CAs in general, with most of the discovered effects concentrated at the intersection of \textit{formality} and conversation tone.
-Studies have found that CAs using casual style of conversation are perceived as warm, empathetic and friendly \cite{jestin2022effects}\cmt{[81]}\cite{kim2019comparing}\cmt{[89]}, while CAs using formal style of conversation are perceived as polite but lacks empathy \cite{cox2022does}\cmt{[27]}.
-The rest of the architecture elements and perception aspects of sociability are minimally explored in literature, which indicates the need for more research in this area.
-
-There are a few specific conversation architecture elements that had more identified relationships with perceptions of sociability with agent.
-Specifically, CAs using of \textit{affective language} were perceived to be more empathetic \cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{yang2017perceived}\cmt{[44]} and emotionally expressive \cite{zhu2022effects}\cmt{[26]}, as well as being more emotional connected with their users \cite{lee2019s}\cmt{[55]}\cite{lubis2019positive}\cmt{[43]}.
-Also, different variations of a voice-based CA's \textit{prosody} have effects on the perceived sociability with agent, such as an agent using expressive prosody is assessed as more intimate and more similar with the user \cite{kim2020can}\cmt{[24]}.
-Lastly, the conversation architecture element of \textit{humour} has identified relationships across the social connection category of perception.
-Clark et al.
-\cite{clark2019makes} found that humour is an important conversational characteristic for human-human interactions, but viewed as a novelty feature for human-agent conversations.
-However, in our review we found that humor has effects on human-agent relationships, as humorous agents are rated as more friendly, intimate, and similar by users compared to non-humorous agents \cite{go2021conversational}\cmt{[80]}\cite{khooshabeh2011does}\cmt{[37]}.
-
-\subsubsection{Perception of Agent's Humanness}
-
-There are 55 explored connections between conversation architecture elements and the perception of sociability with agents, with majority of them (n=38) finding identified relationships in literature.
-There are significantly more explorations for voice-based agents (n=39) as compared to text-based agents (n=16).
-Previous studies have found that modality may have an effect on the perception of humanness, as voice-based agents are perceived as more human-like as compared to text-based agents \cite{cho2019effects}.
-Out of the 39 explored connections for voice-based agents, 14 of them did not result in any relationships.
-This is especially evident in the architecture element of \textit{affective language} for voice-based agents, as most of the connections resulted in null relationships.
-For example, when comparing the ratings of human-likeness or likeability for a speech agent employing expressive words to the one not using any, Zhu et al \cite{zhu2022effects}\cmt{[26]} were unable to detect any statistically significant differences in both of the observation study and interaction study.
-
-Across the aspects in this perception category, both human-likeness and personality traits have relationships with almost all the conversation architecture elements.
-Specifically for the use of \textit{prosody} elements, our review found some opposing effects on the perception of the agent's humanness.
-In the case of Chan et al's study \cite{chan2021kinvoices}\cmt{[74]}, participated rated the agent using kin voices as significantly more likeable compared to the generic voices, but it was perceived as eerie.
-This may be a warning indicator to watch out for the uncanny valley effect \cite{mori2012uncanny} and advise CA designers to carefully select conversation architecture elements to elicit anthropomorphized perceptions.
-
-There are a few notable conversation architecture elements related to the perceived humanness of conversational agents.
-The use of \textit{prosody} such as varying pitch, intonation and speech rate has more identified relationships with the perceived personality traits of an agent as compared to the perceived human-likeness, especially on the aspect of likeability \cite{choi2020nobody}\cmt{[54]}\cite{jestin2022effects}\cmt{[81]}\cite{misu2011toward}\cmt{[83]}.
-For the architecture elements of \textit{disfluency}, the type of impact on the perception of humanness depended on the context of the conversation.
-Studies have found that participants perceived the filler-condition agent as more likeable in the social-oriented situation, but did not find the same effect in task-oriented situations \cite{jeong2019exploring}\cmt{[10]}\cite{wester2015artificial}\cmt{[14]}.
-The use of \textit{alignment} in an agent had a number of identified relationships with the perception of personality traits, with some studies finding CAs that are lexically aligned with a user are more likeable \cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}.
-
-%-------------
-\section{Discussions}
-
-\subsection{Research Challenges and Opportunities}
-
-%Three major needs emerged from the trends identified by our review: 1) 2) 3).
-
-\subsubsection{The Need for Consistent Evaluation Protocols for Perceptions of Agents}
-
-We found a diversity of approaches used to assess perceptions of agents in our reviewed corpus.
-While we made our best efforts to group perceptions used in literature based on similarity with each other, the inconsistent and composite nature of these perception assessments makes it challenging to synthesize them into a framework that contains homogeneous components in each perception aspect that can be compared with each other.
-
-Based on the literature reviewed in this paper, it is unclear whether perception aspects using similar labels are being evaluated \textit{consistently} through different approaches.
-For example, we found several methods used to assess the perceived human-likeness of an agent.
-A commonly used survey is adapted from the Godspeed questionnaire \cite{bartneck2009measurement}, which evaluates human-likeness based on users' impression of the agent as fake / natural, machinelike / humanlike, unconscious / conscious, and artificial / lifelike (used by \cite{hoegen2019end}\cmt{[31]}, \cite{jeong2019exploring}\cmt{[10]} and \cite{ouchi2019should}\cmt{[59]}).
-Another method used to evaluate human-likeness is adapted from Holtgraves et al.'s \cite{holtgraves2007perceiving} questionnaire, which asks users questions related to the agent's perceived human-likeness, skillfulness, thoughtfulness, politeness, responsiveness and engagement (used by \cite{diederich2019emulating}\cmt{[25]} and  \cite{gnewuch2018faster}\cmt{[19]}).
-One study \cite{westerman2019believe}\cmt{[9]} used the Ascend of Man scale \cite{kteily2015ascent} with pictures showing the evolution from ape to man, asking users to choose a depiction that best represents the agent's perceived human-likeness.
-It is unclear whether these different methods are capturing assessments of similar perception aspects that can be compared with each other.
-Another example is the evaluation of the perception of agent's empathy.
-In Diedrech et al.'s study \cite{diederich2019emulating}\cmt{[25]}, empathy is assessed by asking users whether the CA is giving users individual or personal attention.
-In another study that also studies the perception of empathy \cite{daher2020empathic}\cmt{[58]}, the RoPE Scale \cite{charrier2019rope} is used with questions like "the robot cares about my feelings" or "the robot comforts me when I am upset." These two different evaluations of empathy seem to have different underlying meanings, one assessing the personalization aspect of CAs, while the other is assessing the emotional aspect of CAs.
-
-In addition the problem of consistency in evaluating perceptions, there is the issue of  \textit{composite measures} being used in the assessment of users' perceptions.
-These composite measures collapse multiple aspects of perception into one measurement, making it impossible to break down perceptions into more granular aspects for analysis.
-One such example is Ma et al's study \cite{ma2022ask}\cmt{[29]} on the different approaches for CAs to reply to users' uncertain queries.
-A single UX score is used to evaluate the users' perceptions, which composes of questions on whether the user thinks the CA's response is pleasing / trustworthy / natural / acceptable / shorten the distance between CA and user.
-The UX score encompasses multiple aspects across several perception categories.
-While this study has found significant effect for the use of formal language on the user rated UX score, it is not possible to understand how the details of formality is related to the perception categories of interaction (pleasing, acceptable), sociability (shorten the distance between CA and user), and humanness (natural, trustworthy).
-The humanness questionnaire from Holtgraves et al \cite{holtgraves2007perceiving} has a similar problem, evaluating across perception categories of interaction (responsiveness, engagement), ability (skillfulness), sociability (politeness), and humanness (human-likeness, thoughtfulness).
-
-There has been some effort recently towards unifying the evaluation of conversational agents, such as the work by Finch et al.
-\cite{finch2020towards} presenting a comprehensive analysis of current evaluation protocols.
-More research is needed in this area to standardize the assessment of perceptions to make them consistent, granular, and comparable across literature.
-
-\subsubsection{Investigate the Relationship Across Perception Aspects of Agents}
-
-There is evidence in literature that perception aspects of agents have effects on each other.
-For instance, Moussawi et al.
-\cite{moussawi2021perceptions}\cmt{[36]} conducted a study to understand the correlations between different perceptions related to users' intention to adopt a conversational agent.
-Specifically, they found a correlation within the category of perceived ability, where an agent's perceived intelligence is positively correlated to the perceived initial trust of the agent.
-This study also found that users with higher perceived intelligence of an agent are more likely to attribute higher ratings for perceived human-likeness, as well as for the usability and engagement aspects in the perception category of interaction.
-Lastly, the authors found that perceived humanness have a positive impact on perceived enjoyment, which lead to higher intention to adopt the CA.
-This study outlines that the perception aspects identified in this paper are not independent of each other.
-
-Correlations between perception aspects are discussed in a few of the papers we reviewed.
-One of the studies showed that the CA's perceived personality trait of agreeableness has an influence on the users' perception of credibility \cite{andrews2012system}\cmt{[38]}.
-Seeger et al's study found a similar correlation, where higher perceived anthropomorphism led to lower loss of trust \cite{seeger2021chatbots}\cmt{[35]}.
-There are also correlations between aspects found within the same perception category, such as a speech agent that is rated higher in perceived human-likeness was associated with higher likability ratings \cite{zhu2022effects}\cmt{[26]}.
-Also, within the perception category of social connection, one study found that social distance is positively related to the perceived social attraction \cite{westerman2019believe}\cmt{[9]}.
-
-These correlations demonstrate that some perception aspects have effects on each other, either within the same category or across different categories.
-While there are limited research into this area, further investigations are needed to understand the relationships between various perception aspects.
-
-\subsubsection{Research Directions for the Effects of Conversation Architecture on Users' Perceptions}
-
-Our synthesized framework (Figure \ref{fig:heatmap-impact}) serves as a foundational understanding on the effect of conversation architecture on the perception of agents.
-It showcases the density of explored relationships between them, as well as highlighting areas that are under-explored.
-In order to continue building our knowledge, it is important to investigate further into the effect of contextual factors as well as multiple conversation architecture elements on users' perceptions.
-
-There are a few \textit{under-explored areas} in our synthesized framework.
-The perception category of agent's ability has the least number of explored connections with conversation architecture compared to other perception categories.
-Specifically, more studies are needed to understand the effects of social dialog, response delay, humour and elaborateness on users' perceptions of agents' ability.
-For the perception category of sociability with agent, there is a general lack of explored connections with the conversation architecture category of content style, especially for alignment and elaborateness elements.
-Lastly, more studies on the effect of dialog strategy for conversation architecture elements of initiative and response delay on the perceptions of agent are needed.
-
-Some studies have discussed how differences in \textit{contextual factors} resulted in variations in the perceptions of agents while using similar conversation architecture elements.
-One of the factors is users' experience with CAs, as Gnewuch et al.
-\cite{gnewuch2018faster}\cmt{[19]} found that experienced users perceived the agent with a response delay as lower in social presence because it is seen as inefficient to wait for the CA to respond, but novice users perceived higher social presence conversing with the CAs using response delays because it is more similar to conversations with human partners \cite{gnewuch2018faster}\cmt{[19]}.
-User characteristics is another factor, as the perceived trustworthiness of a style matching agent depended on users' own conversational style \cite{hoegen2019end}\cmt{[31]}.
-Some other contextual factors that resulted in differences in perceptions of agent include the purpose of conversation (e.g.
-transactional vs.
-social) \cite{jeong2019exploring}\cmt{[10]}, anonymity of the conversation \cite{lee2020hear}\cmt{[23]}, and the sensitivity of information discussed in the interaction \cite{cox2022does}\cmt{[27]}.
-A comprehensive review to identify these contextual factors as well as to understand their effects on the perceptions of agents across various conversation architecture elements would be useful to tailor CA design for specific situations.
-
-As we gain a better understanding about the effects of a single conversation architecture element on the perceptions of agents, we can extend the research to using \textit{multiple conversation architecture elements} in an agent.
-Several papers in our reviewed corpus incorporated composite elements in an agent, such as the design of an anthropomorphized chatbot using elements such as affective language, emoticons, response delays to assess users' perceptions compared to a non-anthropomorphized chatbot \cite{seeger2021chatbots}\cmt{[35]}.
-In addition to explore the combined effects of conversation architecture elements on users' perceptions, it would also be interesting to understand the relative importance of each element on perceptions.
-Some studies analyzed the effect of modifying conversation architecture elements individually, as well as their combined effect on user's perceptions (e.g.
-\cite{habler2019effects}\cmt{[63]}\cite{lubold2016effects}\cmt{[86]}\cite{zhu2022effects}\cmt{[26]}).
-Specifically, Habler et al.
-\cite{habler2019effects}\cmt{[63]} found that the effect for social dialog is higher than the effect for prosody on the perception of agents.
-
-\subsection{Ethical Considerations}
-
-The designers of conversational agents need to consider ethical implications and potential negative impacts for users.
-This section discusses three main areas of concerns related to the effect of conversation architecture on the perceptions of agents: gender stereotypes, influencing user's actions and privacy concerns.
-
-For the element of prosody, various studies in our corpus explored the effect of different pitches on the perceptions of agents.
-Even in studies that are not explicitly analyzing the effect of different gendered voices in an agent, possible stereotypes may still exist in the study.
-Based on our reviewed corpus, studies found that lower pitches commonly associated with men are considered to be more desirable, authoritative but less friendly \cite{tolmeijer2021female}\cmt{[62]}\cite{jestin2022effects}\cmt{[81]}.
-For Dubiel et al's study \cite{dubiel2020persuasive}\cmt{[60]}, the agent with lower mean pitch was selected as the more persuasive voice.
-These results may be demonstrating users' unconscious bias to select a male sounding voice as more persuasive and authoritative over female sounding voices that are commonly associated with higher pitches.
-While some guidelines recommend designing agents to be androgynous to avoid gender stereotypes \cite{ruane2019conversational}, there are limitations in creating gender-ambiguous voices.
-Currently there is no defined guidelines on what is perceived as a gender-neutral voice \cite{jestin2022effects}\cmt{[81]}.
-There is also a lack of voice generators available to generate voices that are perceived as androgynous \cite{tolmeijer2021female}\cmt{[62]}.
-
-Studies have demonstrated that conversation architecture elements can be used to design perceptions of agents to make CAs more persuasive.
-This opens up the ethical issue of influencing users' attitudes and behaviours through these persuasion techniques.
-In a study by Chan et al \cite{chan2021kinvoices}\cmt{[74]}, they found that CAs using kin's voices are perceived as more credible and likeable, with a higher perceived social presence with the agent.
-These perceptions contributes to the agent being more engaging and persuasive, therefore people are more likely to comply with its requests.
-Andrew et al \cite{andrews2012system}\cmt{[38]} found that tailoring the personality of the CA to users will positively impact an agent's persuasiveness.
-These persuasion techniques can be beneficial to help users achieve their goals, but can also be used for harmful actions, such as trying to get users to believe in false information.
-
-Another key area of concern is privacy.
-Given the natural language format of conversational agents, users may be disclosing more sensitive and personal information than needed for the interaction.
-In relationship to conversation architecture, using elements like self-disclosure and persuasive voice prosody settings could result in users perceiving higher trust with the agent, leading them to disclose more sensitive information  \cite{lee2020hear}\cmt{[23]}\cite{dubiel2020persuasive}\cmt{[60]}.
-This can expose users to attacks, such as CAs using voice impersonation to ask for personal information for malicious intents \cite{chan2021kinvoices}\cmt{[74]}.
-Designing for perceptions of agents requires careful consideration of privacy issues including the sensitivity of the data, who has access to it, and how to protect against nefarious users.
-
-\subsection{Limitations}
-
-Our systematic literature review was limited to papers published in the ACM Digital Library between 2010 and 2022.
-We may have missed literature published outside this time period, as well as in other libraries.
-Also, most of the studies in our corpus are based on lab experiments using short interactions with users.
-The generalizability of these findings need to be verified through longer term engagements with conversational agents deployed in real world situations.
-Lastly, research without empirical studies on the perception of agents are excluded based on our selection criteria.
-We may have missed some influential findings in these papers.
-%To better understand the relationships between conversation architecture elements and the perceptions of agents, we plan to conduct future reviews in literature and user studies to understand their real-world impacts.
-
-\section{Conclusions}
-
-In this paper, we discussed the results of a systematic review of existing literature published in the ACM Digital Library on the effect of conversation architecture elements on the perceptions of CAs.
-Through our synthesis of 57 papers in our corpus, we present a framework outlining the relationships between elements of agents’ conversation architecture (dialog strategy, content affectiveness, content style and speech format) and aspects of users’ perception (interaction, ability, sociability and humanness).
-During our analysis, we found the need for consistent protocols in evaluating perceptions of agents, as measurements are inconsistent across studies.
-Further research is needed to investigate the under-explored areas in the framework, the relationship across perception aspects, the influence of contextual factors, and the effect of composite conversation architecture elements on users' perceptions.
-While our research contribute to the design conversation architecture to orchestrate specific perceptions of agent, we urge designers to incorporate ethical perspectives into their design considerations.
-
-%%
-%% The acknowledgments section is defined using the "acks" environment
-%% (and NOT an unnumbered section). This ensures the proper
-%% identification of the section in the article metadata, and the
-%% consistent spelling of the heading.
-\begin{acks}
-TBD
-\end{acks}
-
-%%
-%% The next two lines define the bibliography style to be used, and
-%% the bibliography file.
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{references}
-
-%%
-%% If your work has an appendix, this is the place to put it.
-\appendix
-
-\end{document}
-\endinput
-%%
-%% End of file `paper.tex'.

### 2023-02-21 paper.tex
restructured manuscript

--- 2023-02-18 paper.tex
@@
 %% The first command in your LaTeX source must be the \documentclass command.
-\documentclass[sigconf,screen,review, anonymous]{acmart}
+\documentclass[sigconf,screen,review, anonymous]{config/acmart}
 
@@
 \author{Young-Ho Kim}
-\email{ygho.kim@navercorp.com}
+\email{yghokim@younghokim.net}
 \affiliation{%
-  \institution{Naver Corporation}
-  \city{Seoul}
-  \country{Korea}
+  \institution{NAVER AI Lab}
+  \country{Republic of Korea}
 }
@@
 
-\section{Introduction}
-
-Conversational agents (CAs), such as Amazon Alexa or Google Assistant, are designed to interact with humans using natural language through voice or text modalities.
-Since these agents interact with users using natural language, conversation architecture — which refers to what a CA says and how it says it — affects how these agents interact with users.
-The effectiveness of these interactions with CAs are strongly dependent on users' perceptions of agents \cite{knijnenburg2016inferring}\cite{seeger2021chatbots}.
-According to previous research, there is a correlation between CAs' conversation architecture and users' perception of these agents.
-
-While there are various studies on how different conversation architecture elements affects agents' perceptions, there is a paucity of knowledge on the overall coverage and effects of these relationships explored in literature.
-For conversation architecture elements, The use of affective language is commonly explored, with studies finding that conversational agents are perceived as more socially present and emotionally intelligent if they use sentiment-adaptive response based on user's utterances \cite{diederich2019emulating}\cite{yang2017perceived}.
-Another commonly explored element is the use of prosody in voice-based agents, such as the use of express prosody contributing to higher perceived enjoyment and intimacy with the agent \cite{kim2020can}.
-However, there is a lack of research to synthesize these findings into an overall framework.
-One of the possible issues is the lack of clear and consistent definitions on the aspects of user's perceptions of agent and conversation architectural elements.
-
-Currently there is no systematic understanding on the elements of conversation architecture that are relevant to perceptions of agents.
-Some papers have started to examine the speech specifics that are being explored in literature, such as Clark et al.
-\cite{clark2019state} capturing different elements of system speech production for voice-based agents and categorizing them based on content, style, and other topics.
-There are also some investigations of conversation architecture elements within the broader field of studying cues that trigger a social reaction of the user towards the CA.
-Feine et al's \cite{feine2019taxonomy} paper laid the foundation to create a consistent taxonomy for these social cues.
-However, there is no comprehensive research specifically for conversation architecture elements that are relevant to user perceptions.
-
-Related to user perceptions, there is also no systematic understanding on the perceptions of agents affected by speech variations.
-Some research discussed the perceptions of agents as part of the broader scope of user experiences of CAs.
-These publications have gathered UX dimensions used to evaluate conversational agents, which include the perceptions of agents (e.g.
-empathy, humanness) alongside other assessments (e.g.
-physiological data) \cite{clark2019state}\cite{finch2020towards}.
-Some even categorized the metrics based on the type of method used, including technical measures like system error rate and perception measures like perceived social presence \cite{zheng2022ux}.
-However, these studies are assessing the general field of UX measurements and not specifically on the perceptions of agents, and do not analyze the effects of conversation architecture on these perceptions.
-
-These research gaps discussed above: the paucity of knowledge on synthesizing the effect of speech specifics on perceptions of CAs as well as the lack of systematic understanding on the elements of conversation architecture and perceptions of agents motivated us to the goal of how to design conversation architecture in order to orchestrate perceptions of conversational agents.
-First, we want to understand \textbf{(RQ1) what perception aspects of agents are being explored in relation to the effects of conversation architecture elements}.
-While there are various architecture elements of conversation architecture used in a CA's utterances, we don't have a holistic understanding of them.
-This leads to our second research question: \textbf{(RQ2) what elements of conversation architecture are relevant to the perceptions of agents?} Lastly, we want to understand the effect of conversation architecture on perceptions of agent, specifically: \textbf{(RQ3) what are the relationships between conversation architecture elements and the perceptions of CAs?}
-
-To answer these questions, we performed a comprehensive review on existing literature from 2010 to 2022 and synthesized the effect of conversation architecture elements on the perceptions of CAs based on 57 relevant papers (Figure \ref{fig:heatmap-impact}).
-We also grouped the perceptions of agents affected by conversation architecture into four categories and eleven aspects (Table \ref{tab:perceptions}), and grouped the speech variations related to perceptions of agents into four categories and eleven elements (Table \ref{tab:cues}).
-%Lastly, we coded the explored connections between conversation architecture and perceptions and synthesized their relationships into a framework.
-Through our analysis, we also found that there are inconsistencies in the assessment of perceptions across studies, as well as influencing factors other than conversation architecture that impact the perceptions of agents.
-This work contributes to the HCI community by presenting a framework that demonstrates the effect of conversation architecture on perceptions of conversational agents, as well as taxonomies for perception aspects and conversation architecture elements providing clear and consistent terms that can be used in future research.
-Together, these contributions move us one step closer to designing CAs that effectively interact with users.
-%Also, our analysis extends existing reviews on UX research of CAs \cite{clark2019state}\cite{rapp2021human}\cite{zheng2022ux} by providing a synthesized framework outlining the relationships between conversation architecture and perceptions of agents.
-With the help of this framework, we are taking the first step to understand how to design conversational agents to solicit specific social reactions from users.
-
-In the remainder of the paper, we first outline related background work, our literature review process, as well as the characteristics of the papers in our reviewed corpus.
-Following that, we describe in detail the taxonomy for the perception of agents, the taxonomy for conversation architecture element, as well as the framework on the relationships between perceptions of agents and conversation architecture.
-Finally, we discuss research challenges and opportunities as well as ethical considerations for designing conversational architecture to orchestrate perceptions of conversational agents.
-
-\section{Literature Review}
-
-* human-human vs. human-AI
-
-* anthropomorphism
-%Anthropomorphism is defined as the attribution of traits that we typically associate with being distinctly human to nonhuman entities \cite{waytz2010sees}.
-For example, users tend to personify conversational agents like Amazon Alexa by using person pronouns instead of object pronouns in online reviews \cite{purington2017alexa}.
-Research shows that anthropomorphic design is beneficial to establishing and maintaining trust between users and conversational agents \cite{seeger2021chatbots}.
-Also, speakers tend to align their lexical choices with conversational agents, similar to human-human conversations \cite{cowan2015does}.
-Anthropomorphism has been shown to ease user interactions, e.g.
-making agents more approachable, engaging, and trustworthy when they exhibit human characteristics \cite{qiu2009evaluating}.
-These processes are of particular interest for human-agent communication because they form the basis for user expectations and predispositions regarding agents' behavior, reliability of the information, etc.
-\cite{kuzminykh2020genie}.
-
-* how to synthesize
-
-* user experience evaluations of conversational agents
-%Other papers categorized CA assessments into themes.
-For example, Rapp et al.
-\cite{rapp2021human} generated themes related to how users' experience with chatbots such as experiencing the chatbot including assessments on expectation, perception, satisfaction etc.
-Most recently, Zheng et al's literature review on the UX research of CAs \cite{zheng2022ux} categorized the metrics based on the type of method used, including technical measures like system error rate and perception measures like perceived social presence.
-However, existing studies use different terminologies and categories across aspects of perception.
-As an illustration, it is unclear if the theme of experiencing the chatbot from Rapp et al.
-\cite{rapp2021human} contains similar aspects to the perception towards CA in Zheng et al \cite{zheng2022ux}'s analysis.
-%\cite{finch2020towards} Towards unified dialogue system evaluation: A comprehensive analysis of current evaluation protocols
-
-\section{Methods}
-
-This section describes the research methodologies used for data collection and data analysis. Additionally, it presents the characteristics of the papers in our reviewed corpus.
-
-\subsection{Data Collection}
-
-Following PRISMA guidelines \cite{prisma}, we reviewed and selected literature exploring the relationship between the specifics of conversation architecture elements and perceptions of CAs.
-Searches were carried out in the ACM Digital Library between January 1 and January 15, 2023.
-Through our analysis, we didn't find any common terms used to refer to either conversation architecture elements, or aspects of perceptions.
-As such, we generalized our search term to capture articles related to conversational agents.
-Based on search terms used in previously published literature reviews \cite{clark2019state}\cite{rapp2021human}, the following keywords are used to search for publications related to conversational user interfaces:
-\newline
-
-\textit{"conversational agent" OR "natural language interface" OR "IPA" OR "intelligent personal assistant" OR "chatbot" OR "speech interface" OR "voice assistant" OR "intelligent agent" OR "human-chatbot communication" OR "virtual agent" OR "dialog* system" OR "voice user interface" OR "human computer dialog*"}
-\newline
-
-The following selection criteria are applied to identify literature related to the effect of conversational architecture on the perception of agents:
-\begin{itemize}
-  \item The paper was published between 2010 and 2022.
-  \item The paper is peer-reviewed and written in English.
-  \item The paper contains the use of voice-based or text-based conversational agents.
-  \item The paper contains studies on the impact of conversation architecture elements on the perceptions of agents.
-  \item The paper contains impact of conversation architecture elements can be separated from other effects (e.g. embodiment).
-
-\end{itemize}
-
-The initial query retrieved 2901 unique publications.
-We screened the titles and abstracts of the papers based on the selection criteria above, resulting in 221 papers.
-The fully body of these papers are then reviewed, selecting papers that met the criteria.
-A search for additional literature was also performed to supplement the corpus, adding 8 more papers to the selection.
-In total, we identified 57 relevant articles for analysis (see Figure \ref{fig:prisma}).
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=1\columnwidth]{fig-prisma.png}
-  \caption{Literature search using PRISMA guidelines}
-  \label{fig:prisma}
-\end{figure}
-
-\subsubsection*{Literature Corpus Characteristics}
-
-The papers reviewed (n=57) were published between May 2011 and November 2022.
-More than 75\% of the papers were published in or after 2019, with a slight trend upwards over the years (see Figure \ref{fig:paper}).
-The vast majority of the papers in our corpus were published in conference proceedings (n=50), with the remainder papers published in journals.
-Out of the papers published in conferences, the top conferences were The ACM Conference on Human Factors in Computing Systems\footnote{https://dl.acm.org/conference/chi} (n=16), Conversational User Interfaces\footnote{https://dl.acm.org/conference/cui} (n=7), Human-Agent Interaction\footnote{https://dl.acm.org/conference/hai} (n=4), and Intelligent Virtual Agents\footnote{https://dl.acm.org/conference/iva} (n=4).
-%Out of the papers published in journals, some venues include the International Journal of Human-Computer Interaction\footnote{https://www.tandfonline.com/journals/hihc20} (n=2) and Interacting with Computers\footnote{https://academic.oup.com/iwc} (n=1).
-
-On the modality characteristics of the conversational agents in the corpus, there is a roughly even split between the modalities, with slightly more papers exploring voice-based CAs (n=30) compared to text-based CAs (n=27).
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=\columnwidth]{fig-paper.png}
-  \caption{Number of papers by year}
-  \label{fig:paper}
-\end{figure}
-
-\subsection{Data Analysis}
-
-\subsubsection*{Perceptions of Agents} To understand the perceptions of agents related to conversation architecture (RQ1), assessments for the perceptions of agents were extracted from each paper.
-We used inductive thematic analysis to group these assessments into codes based on their meanings.
-For example, the code likeability of the agent contains the questionnaire item "this voice agent was likeable" used by \cite{cuadra2021my}\cmt{[67]}, Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed}'s set of questions on likeability used by \cite{linnemann2018can}\cmt{[15]}, and Subjective Assessment of Speech System Interface (SASSI) questionnaire \cite{hone2000towards}\cmt{sassi}'s set of questions on likeability used by \cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}.
-This step resulted in 83 unique codes.
-These codes are then organized based similarity of the meanings, resulting in 11 aspects of perceptions.
-For example, the aspect of personality traits of the agent contains measurements such as likeability, funniness, and kindness.
-Lastly, the 11 aspects are grouped into 4 categories: perception of interaction with agent, perception of agent's ability, perception of sociability with agent, and perception of agent's humanness (Table \ref{tab:perceptions}).
-
-\subsubsection*{Conversation Architecture Elements}
-As to the elements of conversation architecture that are relevant to the perception of agents (RQ2), we extracted the specifics of conversation architecture used in each paper.
-Some of the papers used multiple features in their CA design, such as the the anthropomorphic agent used in Seeger et al's study \cite{seeger2021chatbots}\cmt{[35]}.
-In these composite situations, we broke them down into their individual features.
-For example, the anthropomorphic agent \cite{seeger2021chatbots}\cmt{[35]} was separated into emotional expressions, is-typing indicator, emoticons, and response delay and captured as codes.
-58 unique codes were created as part of this process, capturing features like sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}, lexical alignment \cite{spillner2021talk}\cmt{[18]}, and typos \cite{westerman2019believe}\cmt{[9]}.
-We then organized these codes into elements based on similarity, resulting in 12 elements of conversation architecture.
-For example, the element of disfluency contains fillers \cite{jeong2019exploring}\cmt{[10]}\cite{wester2015artificial}\cmt{[14]}, interjections \cite{ceha2022expressive}\cmt{[77]}\cite{hu2021enhancing}\cmt{[56]}, repetitions \cite{yang2021effect}\cmt{[72]} and typos \cite{westerman2019believe}\cmt{[9]}.
-These elements are grouped into 4 categories: dialog strategy, content affectiveness, content style, and speech format (Table \ref{tab:cues}).
-
-\subsubsection*{Relationship Between Perceptions of Agents and Conversation Architecture}
-To study the effect of conversation architecture on users' perceptions (RQ3), we extracted the connections explored in each paper, using the perception aspects and conversation architecture elements developed in the previous data analysis steps.
-Each connection's effect was also recorded based on whether an association was found in the study and the nature of that association.
-Out of our review corpus, 265 connections between perceptions of agents and conversation architecture were explored in literature.
-To analyze the specifics of conversation architecture that affect the perceptions of CAs, 72 connections that did not result in observed relationships were discarded, resulting in 193 relationships for analysis.
-For example, the connection between the matching style of a CA and user satisfaction was removed because Hoegen et al.
-\cite{hoegen2019end}\cmt{[31]} did not find a significant difference between the style matching agent and the non-style matching agent for overall interaction satisfaction.
-Out of the 193 relationships, 10 were relationships based on agents modifying multiple architecture elements (e.g.
-\cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2021manipulating}\cmt{[68]}).
-They were not included in the final framework as we could not attribute the perceptions of agents to the underlying core elements.
-Overall, 183 relationships between individual architecture elements and perceptions of agents are incorporated into our synthesized framework, visualized as a heatmap to demonstrate their relationships with each other (Figure \ref{fig:heatmap-impact}).
-
-\section{Findings}
-
-\begin{figure*}[]
-  \centering
-  \includegraphics[width=\textwidth]{fig-heatmap-impact.png}
-  \caption{Heatmap of literature for perception of conversational agents for each type of conversational architecture element}
-  \label{fig:heatmap-impact}
-\end{figure*}
-
-\subsection{Perceptions of Agents}
-
-As shown in Table \ref{tab:perceptions}, there are four categories defined for the perceptions of conversational agents covering 11 different aspects of perception.
-The details of each category and aspect are discussed below.
-
-\textbf{Perception of interaction with agent} assesses the overall interaction quality users had with the conversational agent.
-The three aspects for this perceptions are usability, engagement and satisfaction.
-\textit{Usability} captures the utilitarian component of the interaction, whether it was accurate, easy to use, efficient or helpful.
-Some commonly used methods to evaluate usability include the response accuracy portion of the SASSI questionnaire \cite{hone2000towards}\cmt{sassi}, or the NASA Task Load Index (NASA-TLX) \cite{hart1988development}\cmt{nasa} for cognitive workload.
-Questions such as "the system is easy to use" or "it is easy to understand the agent" are also used to evaluate usability.
-\textit{Engagement} on the other hand captures users' emotional reactions to the CA, whether they have enjoyed the conversation, or annoyed or frustrated with the interaction.
-Some commonly used methods to evaluate engagement include the annoyance portion of the SASSI questionnaire \cite{hone2000towards}\cmt{sassi}, and the Use Engagement Scale (UES) \cite{o2018practical}\cmt{ues}.
-Questions such as "I enjoyed using the system" or "I felt frustrated with the agent" are also used to evaluate engagement.
-Lastly, \textit{Satisfaction} captures users' overall satisfaction interacting with the agent.
-Questions such as "the overall assessment of conversing with the CA was satisfactory" are used to evaluate this perception.
-
-\textbf{Perception of agent's ability} assesses the perceived capabilities of the agent.
-Unlike system capabilities that affect agent's performance, the perceived ability category captures perceptions of agents with equivalent system capabilities but varied conversation architecture elements.
-Specifically, \textit{intelligence} captures the agent's expertise and knowledge, and it is commonly administered through the Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed} using the set of questions related to perceived intelligence.
-Also survey questions such as asking users about the agent's intelligence and domain knowledge are used to evaluate perceived intelligence.
-\textit{Competence} takes intelligence one step further by examining the agent's ability to put its intelligence into practice.
-Surveys or qualitative feedback are usually used to assess if the agent is capable and competent, and whether users have confidence in the agent's ability to get the job done.
-Lastly, \textit{credibility} captures agent's truthfulness, benevolence, and user's confidence in CAs.
-Some commonly used methods to evaluate trust include the Trust Propensity Scale \cite{mayer1999effect} and the Individualized Trust Scale (ITS) \cite{wheeless1977measurement}.
-Questions such as "is the agent honest" and "can I trust the agent with sensitive information" are also used to evaluate trust.
-
-\textbf{Perception of the sociability with agent} assesses the emotional connections that users have with agents.
-This category includes perception aspects of conversation tone, social presence and intimacy.
-\textit{Conversation tone} captures the affective impression of the agent's tone, such as empathy and expressiveness.
-Also, this aspect includes whether the tone used by the agent was perceived as friendly, polite or warm.
-\textit{Social presence} captures the sense of connectness and psychological distance users have with an agent.
-Some aspects in this category include the sense of familiarity or similarity with the agent, and whether users feel the agent behaves like them or have similar attitudes to them.
-The category of \textit{Intimacy} extends social presence into the realm of the quality of relationships with an agent.
-Some commonly used methods to assess intimacy include the set of social attraction questions from the interpersonal attraction questionnaire \cite{mccroskey1975development} and the quality of relationship inventory (QRI) \cite{pierce1997assessing}.
-These questionnaires include questions like "I think the agent could be a friend of mine", or "I feel we could establish a personal relationship with each other".
-
-\textbf{Perception of agent's humanness} assesses the specifics of anthropomorphized perceptions of conversational agents.
-\textit{Human-likeness} captures whether the agent presented itself as natural and human-like, or artificial and machine-like.
-The Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed} set of questions related to anthropomorphism and the Ascent of Man scale \cite{kteily2015ascent} are commonly used methods to evaluate human-likeness.
-Survey questions with semantic scales such as "human-like / machine-like" and "artificial / natural" are also commonly used for this aspect of perception.
-\textit{Personality traits} captures the human characteristics that are attributes to the agent.
-This is commonly collected as qualitative feedback from users, commenting on whether the agent is extroverted or introverted, or the perceived personality such as likeable, funny or witty.
-Sometimes the Big-5 personality traits questionnaire \cite{gosling2003very} is used to map an agent's disposition on various personality dimensions.
-
-Overall there is a good coverage of different aspects of perception based on the list of papers reviewed in our corpus.
-The most commonly explored aspect categories is the perception the interaction with agent, followed by the perception of agent's humanness.
-There are two aspects that are the least explored compared to the others relationships: competence within the perception of agent's ability, and intimacy within the perception of social connection with agent.
-This may be due to the controlled lab settings for the experiments, where participants are given the scenarios for interaction.
-This type of environment is not conducive to forming relationships with a conversational partner, as noted by Linnerman et al.
-in their discussions \cite{linnemann2018can}\cmt{[15]}.
-The same factor could impact the assessment of agent's competence, as the users may not feel like they have the expertise to assess their perceptions.
-%These factors could contribute to the reasons why competency and intimacy are not as frequently measured in experimental studies.
-
-\begin{table*}[ht]
-\renewcommand*{\arraystretch}{1.4}
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{@{}p{0.17\textwidth} | p{0.12\textwidth} | p{0.20\textwidth} | >{\centering}p{0.09\textwidth} | p{0.42\textwidth} @{}}
-%!{\vrule width 1.2pt} 
-\Xhline{1.2pt}
-\multicolumn{2}{l|}{\textbf{Perception Aspects}} & \textbf{Examples} & \textbf{No. Papers} & \textbf{Papers} 
-\\ \Xhline{1.2pt}
-\multirow{3}{*}{\parbox{0.17\textwidth}{Perception of \newline Interaction with Agent}}
-    & Usability & accuracy, ease of use, \newline efficiency, helpfulness & 23 
-    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2022expressive}\cmt{[77]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cuadra2021my}\cmt{[67]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{elsholz2019exploring}\cmt{[61]}\cite{haas2022keep}\cmt{[78]}\cite{habler2019effects}\cmt{[63]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2019comparing}\cmt{[89]}\cite{kim2020can}\cmt{[24]}
-    \cite{kraus2020effects}\cmt{[64]}\cite{linnemann2018can}\cmt{[15]}\cite{ma2022ask}\cmt{[29]}\cite{miehle2018exploring}\cmt{[51]}\cite{misu2011toward}\cmt{[83]}\cite{roy2021users}\cmt{[71]}\cite{spillner2021talk}\cmt{[18]}\cite{wilhelm2022keep}\cmt{[28]}
-\\ \cline{2-5}
-    & Engagement & enjoyment, annoyance, \newline desirable, intention to use  & 28
-    & \cite{andrews2012system}\cmt{[38]}\cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cox2022does}\cmt{[27]}\cite{cuadra2021my}\cmt{[67]}\cite{elsholz2019exploring}\cmt{[61]}\cite{fadhil2018effect}\cmt{[52]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{go2021conversational}\cmt{[80]}\cite{healey2013relating}\cmt{[39]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2020can}\cmt{[24]}\cite{kim2019comparing}\cmt{[89]}
-    \cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{ma2022ask}\cmt{[29]}\cite{miehle2018exploring}\cmt{[51]}\cite{miyamoto2017improving}\cmt{[46]}\cite{moilanen2022measuring}\cmt{[82]}\cite{roy2021users}\cmt{[71]}\cite{spillner2021talk}\cmt{[18]}\cite{volkel2021examining}\cmt{[69]}\cite{volkel2022user}\cmt{[75]}\cite{xiao2021let}\cmt{[73]}\cite{yang2021effect}\cmt{[72]}\cite{zhu2022effects}\cmt{[26]}
-\\ \cline{2-5}
-    & Satisfaction & service satisfaction, quality of interaction & 12
-    & \cite{ceha2022expressive}\cmt{[77]}\cite{choi2020nobody}\cmt{[54]}\cite{diederich2019emulating}\cmt{[25]}\cite{elsholz2019exploring}\cmt{[61]}\cite{habler2019effects}\cmt{[63]}\cite{gnewuch2018faster}\cmt{[19]}\cite{hoegen2019end}\cmt{[31]}\cite{hu2022polite}\cmt{[76]}\cite{ma2022ask}\cmt{[29]}\cite{roy2021users}\cmt{[71]}\cite{wilhelm2022keep}\cmt{[28]}\cite{yang2017perceived}\cmt{[44]}
-\\ \Xhline{1.2pt} 
-\multirow{3}{*}{\parbox{0.16\textwidth}{Perception of Agent's Ability}}
-    & Intelligence & knowledgeable, intelligent, expertise & 11
-    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cuadra2021my}\cmt{[67]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{feijoo2021effects}\cmt{[70]}\cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}\cite{spillner2021talk}\cmt{[18]}\cite{volkel2022user}\cmt{[75]}\cite{yang2017perceived}\cmt{[44]}
-\\ \cline{2-5}
-    & Competence & competent, appropriate & 6 
-    & \cite{cox2022does}\cmt{[27]}\cite{kraus2020effects}\cmt{[64]}\cite{jestin2022effects}\cmt{[81]}\cite{lee2019s}\cmt{[55]}\cite{misu2011toward}\cmt{[83]}\cite{westerman2019believe}\cmt{[9]}
-\\ \cline{2-5}
-    & Trust & credibility, trustworthy, truthfulness, confidence & 15
-    & \cite{andrews2012system}\cmt{[38]}\cite{chan2021kinvoices}\cmt{[74]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{fadhil2018effect}\cmt{[52]}\cite{healey2013relating}\cmt{[39]}\cite{hoegen2019end}\cmt{[31]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kraus2020effects}\cmt{[64]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{ma2022ask}\cmt{[29]}\cite{seeger2021chatbots}\cmt{[35]}\cite{tolmeijer2021female}\cmt{[62]}\cite{wilhelm2022keep}\cmt{[28]}
-\\ \Xhline{1.2pt} 
-\multirow{3}{*}{\parbox{0.16\textwidth}{Perception of \newline Sociability with Agent}}
-    & Conversation Tone & friendly, warm, empathetic, persuasive & 20 
-    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cox2022does}\cmt{[27]}\cite{cuadra2021my}\cmt{[67]}\cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{healey2013relating}\cmt{[39]}\cite{hu2021enhancing}\cmt{[56]}\cite{hu2022polite}\cmt{[76]}\cite{jestin2022effects}\cmt{[81]}\cite{khooshabeh2011does}\cmt{[37]}\cite{kim2019comparing}\cmt{[89]}\cite{lee2019s}\cmt{[55]}\cite{miehle2018exploring}\cmt{[51]}
-    \cite{moilanen2022measuring}\cmt{[82]}\cite{tolmeijer2021female}\cmt{[62]}\cite{yang2021effect}\cmt{[72]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}
-\\ \cline{2-5}
-    & Social Presence & connectedness, familiarity, psychological distance & 18
-    & \cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cuadra2021my}\cmt{[67]}\cite{diederich2019emulating}\cmt{[25]}\cite{gnewuch2018faster}\cmt{[19]}\cite{gnewuch2018chatbot}\cmt{[21]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{go2021conversational}\cmt{[80]}\cite{khooshabeh2011does}\cmt{[37]}\cite{kim2020can}\cmt{[24]}\cite{lee2019s}\cmt{[55]}\cite{lubis2019positive}\cmt{[43]}\cite{lubold2016effects}\cmt{[86]}
-    \cite{ma2022ask}\cmt{[29]}\cite{niewiadomski2013laugh}\cmt{[85]}\cite{westerman2019believe}\cmt{[9]}    
-\\ \cline{2-5}
-    & Intimacy & intimate, rapport, quality of relationship & 7 
-    & \cite{choi2020nobody}\cmt{[54]}\cite{khooshabeh2011does}\cmt{[37]}\cite{kim2020can}\cmt{[24]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{lubold2016effects}\cmt{[86]}\cite{westerman2019believe}\cmt{[9]}
-\\ \Xhline{1.2pt}
-\multirow{2}{*}{\parbox{0.16\textwidth}{Perception of Agent's Humanness}}
-    & Human-likeness & human-like, natural, \newline artificial, machine-like & 20
-    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cox2022does}\cmt{[27]}\cite{diederich2019emulating}\cmt{[25]}\cite{gnewuch2018faster}\cmt{[19]}\cite{haas2022keep}\cmt{[78]}\cite{hu2022polite}\cmt{[76]}\cite{jeong2019exploring}\cmt{[10]}\cite{jestin2022effects}\cmt{[81]}\cite{lubis2019positive}\cmt{[43]}\cite{ma2022ask}\cmt{[29]}\cite{misu2011toward}\cmt{[83]}\cite{niewiadomski2013laugh}\cmt{[85]}
-    \cite{ouchi2019should}\cmt{[59]}\cite{seeger2021chatbots}\cmt{[35]}\cite{wester2015artificial}\cmt{[14]}\cite{westerman2019believe}\cmt{[9]}\cite{zhu2022effects}\cmt{[26]}    
-\\ \cline{2-5}
-    & Personality Traits & likeable, kind, witty, funny, creepy & 20
-    & \cite{andrews2012system}\cmt{[38]}\cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cuadra2021my}\cmt{[67]}\cite{haas2022keep}\cmt{[78]}\cite{habler2019effects}\cmt{[63]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{huiyang2022improving}\cmt{[17]}\cite{jeong2019exploring}\cmt{[10]}\cite{kim2019comparing}\cmt{[89]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{miehle2018exploring}\cmt{[51]}
-    \cite{ouchi2019should}\cmt{[59]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}\cite{wester2015artificial}\cmt{[14]}\cite{zhu2022effects}\cmt{[26]} 
-\\ \Xhline{1.2pt}
-\end{tabular}%
-}
-\caption{Perception aspects}
-\label{tab:perceptions}
-\end{table*}
-
-\begin{table*}[h]
-\resizebox{\textwidth}{!}{
-\renewcommand*{\arraystretch}{1.4}
-\begin{tabular}{@{}p{0.17\textwidth} | p{0.14\textwidth} | p{0.25\textwidth} | >{\centering}p{0.09\textwidth} | p{0.34\textwidth} @{}}
-\Xhline{1.2pt}
-\multicolumn{2}{l|}{\textbf{Conversation Architecture Elements}} & \textbf{Examples} & \textbf{No. Papers} & \textbf{Papers}
-\\ \Xhline{1.2pt}
-\multirow{3}{*}{Dialog Strategy} & Social Dialog & social talk, self-disclosure  & 7
-& \cite{andrews2012system}\cmt{[38]}\cite{lee2020hear}\cmt{[23]}\cite{lubold2016effects}\cmt{[86]}\cite{moilanen2022measuring}\cmt{[82]}\cite{roy2021users}\cmt{[71]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}
-\\ \cline{2-5}
-
-& Initiative & proactive dialogue, conversation \newline repair & 4
-& \cite{ashktorab2019resilient}\cmt{[88]}\cite{cuadra2021my}\cmt{[67]}\cite{kraus2020effects}\cmt{[64]}\cite{xiao2021let}\cmt{[73]}
-\\ \cline{2-5}
-
-& Response Delay & response delay, typing indicator & 4
-& \cite{gnewuch2018faster}\cmt{[19]}\cite{gnewuch2018chatbot}\cmt{[21]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{seeger2021chatbots}\cmt{[35]}
-\\ \Xhline{1.2pt}
-
-\multirow{2}{*}{Content Affectiveness} & Affective Language & emotional expressions, sentiment-adaptive responses & 11
-& \cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{lee2019s}\cmt{[55]}\cite{lubis2019positive}\cmt{[43]}\cite{moilanen2022measuring}\cmt{[82]}\cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2022user}\cmt{[75]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}
-\\ \cline{2-5}
-
-& Humour & humorous content, jokes & 6
-& \cite{ceha2021can}\cmt{[57]}\cite{go2021conversational}\cmt{[80]}\cite{khooshabeh2011does}\cmt{[37]}\cite{miyamoto2017improving}\cmt{[46]}\cite{niewiadomski2013laugh}\cmt{[85]}\cite{volkel2021manipulating}\cmt{[68]}
-\\ \Xhline{1.2pt}
-
-\multirow{3}{*}{Content Style} & Formality & formal vs. casual, honorific \newline expressions & 9
-& \cite{cox2022does}\cmt{[27]}\cite{elsholz2019exploring}\cmt{[61]}\cite{habler2019effects}\cmt{[63]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2019comparing}\cmt{[89]}\cite{ma2022ask}\cmt{[29]}\cite{moilanen2022measuring}\cmt{[82]}\cite{ouchi2019should}\cmt{[59]}\cite{volkel2022user}\cmt{[75]}
-\\ \cline{2-5}
-
-& Alignment & content matching, lexical \newline alignment, agreeableness & 7
-& \cite{healey2013relating}\cmt{[39]}\cite{hoegen2019end}\cmt{[31]}\cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}\cite{spillner2021talk}\cmt{[18]}\cite{volkel2021examining}\cmt{[69]}\cite{volkel2021manipulating}\cmt{[68]}
-\\ \cline{2-5}
-
-& Elaborateness & elaborate, concise, sentence \newline structure & 6
-& \cite{haas2022keep}\cmt{[78]}\cite{miehle2018exploring}\cmt{[51]}\cite{moilanen2022measuring}\cmt{[82]}\cite{roy2021users}\cmt{[71]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}
-\\ \Xhline{1.2pt}
-
-\multirow{3}{*}{Speech Format} & Prosody & pitch, intonation, speech rate, \newline spoken accent & 12
-& \cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{feijoo2021effects}\cmt{[70]}\cite{habler2019effects}\cmt{[63]}\cite{hu2021enhancing}\cmt{[56]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2020can}\cmt{[24]}\cite{lubold2016effects}\cmt{[86]}\cite{misu2011toward}\cmt{[83]}\cite{tolmeijer2021female}\cmt{[62]}\cite{zhu2022effects}\cmt{[26]}
-\\ \cline{2-5}
-
-& Disfluency & fillers, interjections, repetitions, \newline typos & 6
-& \cite{ceha2022expressive}\cmt{[77]}\cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}\cite{wester2015artificial}\cmt{[14]}\cite{westerman2019believe}\cmt{[9]}\cite{yang2021effect}\cmt{[72]}
-\\ \cline{2-5}
-
-& Text Formatting & capitalization, emoticons & 6
-& \cite{fadhil2018effect}\cmt{[52]}\cite{kim2019comparing}\cmt{[89]}\cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2022user}\cmt{[75]}\cite{westerman2019believe}\cmt{[9]}\cite{wilhelm2022keep}\cmt{[28]}
-\\ \Xhline{1.2pt}
-\end{tabular}%
-}
-\caption{Conversation architecture elements}
-\label{tab:cues}
-\end{table*}
-
-\subsection{Conversation Architecture Elements}
-
-As shown in Table \ref{tab:cues}, there are four categories defined for conversation architecture across 12 different elements. The details of each category and element are discussed below.
-
-The category of \textbf{dialog strategy} refers to the approach used by a conversational agent to engage in a dialogue with a user, which includes the use of social dialogs, agent-initiated content, and adding delays to responses.
-Specifically, the element of \textit{social dialogue} captures non-task related conversations with the user to build social connection, such as self-disclosure \cite{lee2020hear}\cmt{[23]} and small talk like chitchats \cite{lubold2016effects}\cmt{[86]}\cite{volkel2021manipulating}\cmt{[68]}.
-The element of \textit{initiative} captures utterances that are initiated by the agent without direct prompts from the user.
-For example, the agent is taking the initiative to proactively repair the conversation with a user \cite{ashktorab2019resilient}\cmt{[88]}\cite{cuadra2021my}\cmt{[67]}, or actively elicit feedback from users \cite{xiao2021let}\cmt{[73]}.
-Lastly, \textit{response delay} refers to the tactic of deliberatively delaying for a certain period of time before an agent responds to users \cite{gnewuch2018faster}\cmt{[19]}\cite{gnewuch2022opposing}\cmt{[20]}.
-It is mainly used in text-based CAs alongside visual displays of typing indicators \cite{gnewuch2018chatbot}\cmt{[21]}.
-
-\textbf{Content affectiveness} refers to the conversational agent's use of language to convey emotions or to elicit emotions from users.
-The architecture element of \textit{affective language} captures the injection of emotional words or phrases into the agent's utterance, such as affective expressions \cite{seeger2021chatbots}\cmt{[35]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}, sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}, and encouraging words \cite{healey2013relating}\cmt{[39]}.
-The other element in this category, \textit{humour}, captures an agent's attempt to include jokes in its dialog.
-Several studies in our reviewed corpus have explored the effect of humour on various perceptions of agents (e.g.
-\cite{ceha2021can}\cmt{[57]}\cite{khooshabeh2011does}\cmt{[37]}).
-
-The category of \textbf{content style} refers to the variations of language used in a message aside from the content meaning of the message (i.e.
-how something is said).
-The element of \textit{formality} describes the linguistic style used by the conversational agent, whether it is formal vs.
-casual, such as using honorific expressions to address users \cite{ouchi2019should}\cmt{[59]}.
-\textit{Alignment} captures the degree that the agent aligns its utterances to the users, such as lexical alignment on the content and structural of the sentences \cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}, as well as referring and agreeing with users' utterances \cite{volkel2021examining}\cmt{[69]}.
-Lastly, the element of \textit{elaborateness} captures the sentence complexity and length of agents' utterances.
-For example, Roy et al.
-explored the differences in perception for variations in elaborateness such as "Cloudly, possibility of snow, high: 4, low: -10" vs "Today will be cloudy, with a high of 4 and a low of -10.
-Snow is predicted" \cite{roy2021users}\cmt{[71]}.
-
-Lastly, the category of \textbf{speech format} captures the non-verbal component of a conversational agent's utterances for both text and voice modalities. \textit{Disfluency} captures 
-the use of non-lexical utterances like filler words ("um, uh") \cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}, or repetition of words within a sentence \cite{yang2021effect}\cmt{[72]}.
-It also includes the format of using typos \cite{westerman2019believe}\cmt{[9]} for text-based agents.
-For voice-based agents specifically, the element of \textit{prosody} encompasses vocal qualities like pitch \cite{habler2019effects}\cmt{[63]}\cite{jestin2022effects}\cmt{[81]}, speech rate \cite{choi2020nobody}\cmt{[54]}, and spoken accent \cite{feijoo2021effects}\cmt{[70]}.
-For text-based CAs, the \textit{text formatting} element includes different formats agents uses to present information to users, such as using capitalization \cite{westerman2019believe}\cmt{[9]} or emoticons \cite{kim2019comparing}\cmt{[89]}\cite{wilhelm2022keep}\cmt{[28]}.
-
-Overall there are similar number of conversation architecture elements explored across the four categories of dialog strategy, content affectiveness, content style, and speech format.
-As for explorations related to different modalities of agents, there is a noticeable difference in the category of speech format, where architecture elements related to voice-based agents (n=15) are explored more than text-based agents (n=7).
-Looking across the 12 different elements, there is good coverage of studies on the impact of affective language and prosody cues on the perceptions of agents.
-However, there are less studies exploring the effect of agent initiated content and response delay on the perception of agents.
-Specifically for the element of initiative under dialog strategy category, there is literature on conversation repairs \cite{komatani2010online}\cite{reinkemeier2022repair} and agent proactively sharing content with users \cite{dubiel2019inquisitive}\cite{zargham2022understanding}, but many of them did not not include assessments of perceptions of the CA.
-This may be due to the fact that the usage of agent-initiated content is relatively new, as CA interactions have historically been driven by users.
-As such, current research is focused on the functional aspects of agents initiating contents instead of exploring the perceptions of agents.
-As for response delay, there are indications that this element is under-explored in literature.
-Only 4 studies in our reviewed corpus used an agent with response delay, and the majority of these publications were written by the same authors.
-
-\subsection{Relationship Between Perceptions of Agents and Conversation Architecture}
-
-There are 183 identified relationships between perceptions of agents and conversation architecture out of the 265 explored connections that are included in our synthesized framework (Figure \ref{fig:heatmap-impact}).
-To compare the number of identified relationships vs.
-the explored connections in literature, Figure \ref{fig:heatmap-coverage} shows a side-by-side comparison between the two.
-The detailed analysis on the differences between explored and identified relationships are discussed in the subsections below.
-
-While the number of papers studying CAs with voice (n=27) vs.
-text (n=30) modalities is not significantly different, there are some interesting patterns we found with regards to the modalities of the identified relationships between perceptions of agents and conversation architecture.
-Overall, we confirmed the pattern found earlier that there are more conversation architecture elements explored related to voice vs.
-text in the speech format category.
-Because there are smaller number of text-based CAs using speech format elements, we also observed significantly less number of relationships between text-based CA across all perceptions of agents.
-other interesting findings related to modality are discussed later in this paper.
-
-\begin{figure*}[]
-  \centering
-  \includegraphics[width=\textwidth]{fig-heatmap-coverage.png}
-  \caption{Heatmap of literature for perception of conversational agents for each type of conversational architecture element}
-  \label{fig:heatmap-coverage}
-\end{figure*}
-
-\subsubsection{Perception of Interaction with Agent}
-
-The effects of conversation architecture elements on the perception of interaction with agent is the most explored connections in the corpus (n=97).
-Out of these explored connections, the majority of them (n=66) discovered a relationship between aspects of perception related to the perception of interaction with agent related to the studied architecture element.
-Looking at the difference between modalities, we noticed more voice-based agents (n=25) resulted in null relationships compared to text-based agents (n=6).
-The conversation architecture element of \textit{alignment} contributed the most to the null results for voice-based agents, with 9 out of 11 explored connections did not find any relationships related the perception of interaction with agents.
-
-Across the aspects for the perception of interaction, both usability and engagement were assessed frequently in the reviewed literature, with conversation architecture having effects on these perception aspects across all architecture element categories.
-The aspect of satisfaction was used in some studies to evaluate perception but it is not used as often as engagement or usability.
-Several papers that assessed user satisfactions were conversation agents within the transaction context, especially within the customer service domain (e.g.
-\cite{diederich2019emulating}\cmt{[25]}\cite{elsholz2019exploring}\cmt{[61]}\cite{gnewuch2018faster}\cmt{[19]}).
-
-The category of conversation architecture elements with the most identified relationships to perceptions of interaction is content style.
-Specifically for the element of \textit{elaborateness}, users found the use of full sentences more useful than keyword only \cite{haas2022keep}\cmt{[78]}\cite{roy2021users}\cmt{[71]}.
-Otherwise, the effect of an agent's elaborateness on user's perception of interaction depends on the user's preference \cite{miehle2018exploring}\cmt{[51]}, as well as the topic of discussion \cite{haas2022keep}\cmt{[78]}.
-As for \textit{formality}, various studies reported significant differences in perceptions of interaction between using casual vs.
-formal styles.
-Some users experienced higher engagement with agent interacting with the casual style of the conversation \cite{cox2022does}\cmt{[27]}, while in another study users reported the formal language style as less engaging as it is boring \cite{kim2019comparing}\cmt{[89]}.
-
-The speech format of an agent also resulted in a high number of identified relationships with the perception of interaction with CAs, with majority of the explored connections resulted in effects between the perception aspects and architecture elements.
-The element with the most identified relationships is \textit{prosody}.
-For example, studies found that a CA's expressiveness in vocal cues increased participants' engagement ratings \cite{zhu2022effects}\cmt{[26]}, and different pitches of voice affect users' perception of engagement and usability \cite{chan2021kinvoices}\cmt{[74]}\cite{habler2019effects}\cmt{[63]}.
-
-Dialog strategy and content affectiveness categories of conversation architecture did not have as many identified relationships with perceptions of interaction.
-It is worth noting the effect of using the \textit{initiative} element, as CAs that use self-initiated content are perceived as more efficient and higher quality of interaction (e.g.
-\cite{cuadra2021my}\cmt{[67]}).
-Also, some studies have discovered conflicting effects between different perception aspects of interaction for CAs using \textit{social dialog}, as users enjoyed the conversation using social talk \cite{lee2020hear}\cmt{[23]}\cite{roy2021users}\cmt{[71]}, but perceived the CA as less efficient \cite{roy2021users}\cmt{[71]}.
-
-\subsubsection{Perception of Agent's Ability}
-
-The effects of conversation architecture elements on the perception of agent's ability is the least explored connection in the corpus (n=39).
-Out of these explored connections, the majority of them (n=30) found relationships between the studied architecture element and the perceptions of agent's ability.
-There are no notable differences between the text and voice modalities of CAs for either explored connections or the identified relationships.
-
-Aspects within the perception of agent's ability had similar number of identified relationships across intelligence, competence and credibility.
-Our review revealed that the perceived ability of a CA is also dependent on other influencing factors in addition to conversation architecture elements.
-Volkel et al.
-\cite{kraus2020effects}\cmt{[64]} found that the perception of competence of a proactive CA is dependent on task difficulty \cite{kraus2020effects}\cmt{[64]}.
-Also, the perception of intelligence for an agent using fillers depended on the context of the conversation, as the filler-speaking agent was perceived as less intelligent in task-oriented conditions, but was seen as slightly more intelligent in social-oriented conditions \cite{jeong2019exploring}\cmt{[10]}.
-
-Out of the explored conversation architecture elements, \textit{prosody} had relationships identified with aspects across the perception category of agent's ability.
-For example, Chan et al.
-\cite{chan2021kinvoices}\cmt{[74]} found that agents using kin's voices are rated as more intelligent and credible than generic voices.
-Also, the style of speech used by an agent affects the perception of appropriateness of tone, which is an aspect of the perceived competence of an agent \cite{misu2011toward}\cmt{[83]}.
-Different content styles of \textit{formality} also impacts the perceived competence of an agent \cite{cox2022does}\cmt{[27]}\cite{jestin2022effects}\cmt{[81]}.
-Specifically related to perceived credibility of an agent, being \textit{lexically aligned} with the user resulted improved the rating of trustworthiness of an agent \cite{hoegen2019end}\cmt{[31]}\cite{linnemann2018can}\cmt{[15]}.
-There were mixed results on the use of emoticons within the \textit{text formatting} element.
-One study found the chatbot using emoticons as less trustworthy \cite{wilhelm2022keep}\cmt{[28]}, while another study found that users assigned higher scores for confidence to the agent using emojis \cite{fadhil2018effect}\cmt{[52]}.
-
-There are several conversation architecture elements with little to no explorations to the perception of agent's ability.
-Specifically, both categories of dialog strategy and content affectiveness are minimally explored in our reviewed corpus, with no explored connections with \textit{response delay} and only one or two connections explored for \textit{social dialog} and \textit{humour}.
-While the content style category had coverage in some aspects of perceived abilities, it is worth noting that \textit{elaborateness} did not have any explored connections with perceived ability of agents.
-Further research in these areas is needed to fill these gaps in understanding.
-
-\subsubsection{Perception of Sociability with Agent}
-
-The perception of agent's humanness is the second most explored category within our reviewed corpus (n=64), with majority of the connections identified relationship between the studied conversation architecture elements and the anthropomorphized perceptions of agent (n=49).
-Interestingly, studies explored more perceptions of sociability with agent related to voice-based CAs (n=40) compared to text-based CAs (n=24), potentially due to the assumption that interactions with text-based agents are perceived as less personal and more formal \cite{kocielnik2018designing}.
-There are some mixed results for voice-based CAs, as 12 out of the 28 connections did not find any significant results.
-Drilling down to the specific elements, we noticed that the use of \textit{alignment} in voice-based agents did not effect the perception of sociability with agent \cite{healey2013relating}\cmt{[39]}\cite{linnemann2018can}\cmt{[15]}.
-We didn't have data on text-based agents' perceived social connections with users to compare with voice-based agents, as the studies using alignment and text modality in our corpus did not assess this aspect category of perception.
-
-Across the aspects in this perception category, conversation tone had the most number of identified relationship (n=27) with the perceived social connection with CAs, followed by the aspect of social presence (n=17).
-There are only 5 relationships found that are linked to the perception aspect of intimacy.
-One reason for this is half of the explored connections did not have any effect on the perception of sociability with agent, such as the use of capitalization \cite{westerman2019believe}\cmt{[9]}, lexical alignment \cite{linnemann2018can}\cmt{[15]}, or social talk \cite{lubold2016effects}\cmt{[86]}.
-For the perception aspect of social presence, we noticed a gap in the exploration of conversation architecture elements of formality, alignment, and elaborateness in the content style category, as there are no papers explored at this intersection.
-
-Looking at the different categories of conversation architecture elements, the heatmap (Figure \ref{fig:heatmap-impact} shows that there are not many relationships in content style category that are related to the perceived sociability with CAs in general, with most of the discovered effects concentrated at the intersection of \textit{formality} and conversation tone.
-Studies have found that CAs using casual style of conversation are perceived as warm, empathetic and friendly \cite{jestin2022effects}\cmt{[81]}\cite{kim2019comparing}\cmt{[89]}, while CAs using formal style of conversation are perceived as polite but lacks empathy \cite{cox2022does}\cmt{[27]}.
-The rest of the architecture elements and perception aspects of sociability are minimally explored in literature, which indicates the need for more research in this area.
-
-There are a few specific conversation architecture elements that had more identified relationships with perceptions of sociability with agent.
-Specifically, CAs using of \textit{affective language} were perceived to be more empathetic \cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{yang2017perceived}\cmt{[44]} and emotionally expressive \cite{zhu2022effects}\cmt{[26]}, as well as being more emotional connected with their users \cite{lee2019s}\cmt{[55]}\cite{lubis2019positive}\cmt{[43]}.
-Also, different variations of a voice-based CA's \textit{prosody} have effects on the perceived sociability with agent, such as an agent using expressive prosody is assessed as more intimate and more similar with the user \cite{kim2020can}\cmt{[24]}.
-Lastly, the conversation architecture element of \textit{humour} has identified relationships across the social connection category of perception.
-Clark et al.
-\cite{clark2019makes} found that humour is an important conversational characteristic for human-human interactions, but viewed as a novelty feature for human-agent conversations.
-However, in our review we found that humor has effects on human-agent relationships, as humorous agents are rated as more friendly, intimate, and similar by users compared to non-humorous agents \cite{go2021conversational}\cmt{[80]}\cite{khooshabeh2011does}\cmt{[37]}.
-
-\subsubsection{Perception of Agent's Humanness}
-
-There are 55 explored connections between conversation architecture elements and the perception of sociability with agents, with majority of them (n=38) finding identified relationships in literature.
-There are significantly more explorations for voice-based agents (n=39) as compared to text-based agents (n=16).
-Previous studies have found that modality may have an effect on the perception of humanness, as voice-based agents are perceived as more human-like as compared to text-based agents \cite{cho2019effects}.
-Out of the 39 explored connections for voice-based agents, 14 of them did not result in any relationships.
-This is especially evident in the architecture element of \textit{affective language} for voice-based agents, as most of the connections resulted in null relationships.
-For example, when comparing the ratings of human-likeness or likeability for a speech agent employing expressive words to the one not using any, Zhu et al \cite{zhu2022effects}\cmt{[26]} were unable to detect any statistically significant differences in both of the observation study and interaction study.
-
-Across the aspects in this perception category, both human-likeness and personality traits have relationships with almost all the conversation architecture elements.
-Specifically for the use of \textit{prosody} elements, our review found some opposing effects on the perception of the agent's humanness.
-In the case of Chan et al's study \cite{chan2021kinvoices}\cmt{[74]}, participated rated the agent using kin voices as significantly more likeable compared to the generic voices, but it was perceived as eerie.
-This may be a warning indicator to watch out for the uncanny valley effect \cite{mori2012uncanny} and advise CA designers to carefully select conversation architecture elements to elicit anthropomorphized perceptions.
-
-There are a few notable conversation architecture elements related to the perceived humanness of conversational agents.
-The use of \textit{prosody} such as varying pitch, intonation and speech rate has more identified relationships with the perceived personality traits of an agent as compared to the perceived human-likeness, especially on the aspect of likeability \cite{choi2020nobody}\cmt{[54]}\cite{jestin2022effects}\cmt{[81]}\cite{misu2011toward}\cmt{[83]}.
-For the architecture elements of \textit{disfluency}, the type of impact on the perception of humanness depended on the context of the conversation.
-Studies have found that participants perceived the filler-condition agent as more likeable in the social-oriented situation, but did not find the same effect in task-oriented situations \cite{jeong2019exploring}\cmt{[10]}\cite{wester2015artificial}\cmt{[14]}.
-The use of \textit{alignment} in an agent had a number of identified relationships with the perception of personality traits, with some studies finding CAs that are lexically aligned with a user are more likeable \cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}.
-
-%-------------
-\section{Discussions}
-
-\subsection{Research Challenges and Opportunities}
-
-%Three major needs emerged from the trends identified by our review: 1) 2) 3).
-
-\subsubsection{The Need for Consistent Evaluation Protocols for Perceptions of Agents}
-
-We found a diversity of approaches used to assess perceptions of agents in our reviewed corpus.
-While we made our best efforts to group perceptions used in literature based on similarity with each other, the inconsistent and composite nature of these perception assessments makes it challenging to synthesize them into a framework that contains homogeneous components in each perception aspect that can be compared with each other.
-
-Based on the literature reviewed in this paper, it is unclear whether perception aspects using similar labels are being evaluated \textit{consistently} through different approaches.
-For example, we found several methods used to assess the perceived human-likeness of an agent.
-A commonly used survey is adapted from the Godspeed questionnaire \cite{bartneck2009measurement}, which evaluates human-likeness based on users' impression of the agent as fake / natural, machinelike / humanlike, unconscious / conscious, and artificial / lifelike (used by \cite{hoegen2019end}\cmt{[31]}, \cite{jeong2019exploring}\cmt{[10]} and \cite{ouchi2019should}\cmt{[59]}).
-Another method used to evaluate human-likeness is adapted from Holtgraves et al.'s \cite{holtgraves2007perceiving} questionnaire, which asks users questions related to the agent's perceived human-likeness, skillfulness, thoughtfulness, politeness, responsiveness and engagement (used by \cite{diederich2019emulating}\cmt{[25]} and  \cite{gnewuch2018faster}\cmt{[19]}).
-One study \cite{westerman2019believe}\cmt{[9]} used the Ascend of Man scale \cite{kteily2015ascent} with pictures showing the evolution from ape to man, asking users to choose a depiction that best represents the agent's perceived human-likeness.
-It is unclear whether these different methods are capturing assessments of similar perception aspects that can be compared with each other.
-Another example is the evaluation of the perception of agent's empathy.
-In Diedrech et al.'s study \cite{diederich2019emulating}\cmt{[25]}, empathy is assessed by asking users whether the CA is giving users individual or personal attention.
-In another study that also studies the perception of empathy \cite{daher2020empathic}\cmt{[58]}, the RoPE Scale \cite{charrier2019rope} is used with questions like "the robot cares about my feelings" or "the robot comforts me when I am upset." These two different evaluations of empathy seem to have different underlying meanings, one assessing the personalization aspect of CAs, while the other is assessing the emotional aspect of CAs.
-
-In addition the problem of consistency in evaluating perceptions, there is the issue of  \textit{composite measures} being used in the assessment of users' perceptions.
-These composite measures collapse multiple aspects of perception into one measurement, making it impossible to break down perceptions into more granular aspects for analysis.
-One such example is Ma et al's study \cite{ma2022ask}\cmt{[29]} on the different approaches for CAs to reply to users' uncertain queries.
-A single UX score is used to evaluate the users' perceptions, which composes of questions on whether the user thinks the CA's response is pleasing / trustworthy / natural / acceptable / shorten the distance between CA and user.
-The UX score encompasses multiple aspects across several perception categories.
-While this study has found significant effect for the use of formal language on the user rated UX score, it is not possible to understand how the details of formality is related to the perception categories of interaction (pleasing, acceptable), sociability (shorten the distance between CA and user), and humanness (natural, trustworthy).
-The humanness questionnaire from Holtgraves et al \cite{holtgraves2007perceiving} has a similar problem, evaluating across perception categories of interaction (responsiveness, engagement), ability (skillfulness), sociability (politeness), and humanness (human-likeness, thoughtfulness).
-
-There has been some effort recently towards unifying the evaluation of conversational agents, such as the work by Finch et al.
-\cite{finch2020towards} presenting a comprehensive analysis of current evaluation protocols.
-More research is needed in this area to standardize the assessment of perceptions to make them consistent, granular, and comparable across literature.
-
-\subsubsection{Investigate the Relationship Across Perception Aspects of Agents}
-
-There is evidence in literature that perception aspects of agents have effects on each other.
-For instance, Moussawi et al.
-\cite{moussawi2021perceptions}\cmt{[36]} conducted a study to understand the correlations between different perceptions related to users' intention to adopt a conversational agent.
-Specifically, they found a correlation within the category of perceived ability, where an agent's perceived intelligence is positively correlated to the perceived initial trust of the agent.
-This study also found that users with higher perceived intelligence of an agent are more likely to attribute higher ratings for perceived human-likeness, as well as for the usability and engagement aspects in the perception category of interaction.
-Lastly, the authors found that perceived humanness have a positive impact on perceived enjoyment, which lead to higher intention to adopt the CA.
-This study outlines that the perception aspects identified in this paper are not independent of each other.
-
-Correlations between perception aspects are discussed in a few of the papers we reviewed.
-One of the studies showed that the CA's perceived personality trait of agreeableness has an influence on the users' perception of credibility \cite{andrews2012system}\cmt{[38]}.
-Seeger et al's study found a similar correlation, where higher perceived anthropomorphism led to lower loss of trust \cite{seeger2021chatbots}\cmt{[35]}.
-There are also correlations between aspects found within the same perception category, such as a speech agent that is rated higher in perceived human-likeness was associated with higher likability ratings \cite{zhu2022effects}\cmt{[26]}.
-Also, within the perception category of social connection, one study found that social distance is positively related to the perceived social attraction \cite{westerman2019believe}\cmt{[9]}.
-
-These correlations demonstrate that some perception aspects have effects on each other, either within the same category or across different categories.
-While there are limited research into this area, further investigations are needed to understand the relationships between various perception aspects.
-
-\subsubsection{Research Directions for the Effects of Conversation Architecture on Users' Perceptions}
-
-Our synthesized framework (Figure \ref{fig:heatmap-impact}) serves as a foundational understanding on the effect of conversation architecture on the perception of agents.
-It showcases the density of explored relationships between them, as well as highlighting areas that are under-explored.
-In order to continue building our knowledge, it is important to investigate further into the effect of contextual factors as well as multiple conversation architecture elements on users' perceptions.
-
-There are a few \textit{under-explored areas} in our synthesized framework.
-The perception category of agent's ability has the least number of explored connections with conversation architecture compared to other perception categories.
-Specifically, more studies are needed to understand the effects of social dialog, response delay, humour and elaborateness on users' perceptions of agents' ability.
-For the perception category of sociability with agent, there is a general lack of explored connections with the conversation architecture category of content style, especially for alignment and elaborateness elements.
-Lastly, more studies on the effect of dialog strategy for conversation architecture elements of initiative and response delay on the perceptions of agent are needed.
-
-Some studies have discussed how differences in \textit{contextual factors} resulted in variations in the perceptions of agents while using similar conversation architecture elements.
-One of the factors is users' experience with CAs, as Gnewuch et al.
-\cite{gnewuch2018faster}\cmt{[19]} found that experienced users perceived the agent with a response delay as lower in social presence because it is seen as inefficient to wait for the CA to respond, but novice users perceived higher social presence conversing with the CAs using response delays because it is more similar to conversations with human partners \cite{gnewuch2018faster}\cmt{[19]}.
-User characteristics is another factor, as the perceived trustworthiness of a style matching agent depended on users' own conversational style \cite{hoegen2019end}\cmt{[31]}.
-Some other contextual factors that resulted in differences in perceptions of agent include the purpose of conversation (e.g.
-transactional vs.
-social) \cite{jeong2019exploring}\cmt{[10]}, anonymity of the conversation \cite{lee2020hear}\cmt{[23]}, and the sensitivity of information discussed in the interaction \cite{cox2022does}\cmt{[27]}.
-A comprehensive review to identify these contextual factors as well as to understand their effects on the perceptions of agents across various conversation architecture elements would be useful to tailor CA design for specific situations.
-
-As we gain a better understanding about the effects of a single conversation architecture element on the perceptions of agents, we can extend the research to using \textit{multiple conversation architecture elements} in an agent.
-Several papers in our reviewed corpus incorporated composite elements in an agent, such as the design of an anthropomorphized chatbot using elements such as affective language, emoticons, response delays to assess users' perceptions compared to a non-anthropomorphized chatbot \cite{seeger2021chatbots}\cmt{[35]}.
-In addition to explore the combined effects of conversation architecture elements on users' perceptions, it would also be interesting to understand the relative importance of each element on perceptions.
-Some studies analyzed the effect of modifying conversation architecture elements individually, as well as their combined effect on user's perceptions (e.g.
-\cite{habler2019effects}\cmt{[63]}\cite{lubold2016effects}\cmt{[86]}\cite{zhu2022effects}\cmt{[26]}).
-Specifically, Habler et al.
-\cite{habler2019effects}\cmt{[63]} found that the effect for social dialog is higher than the effect for prosody on the perception of agents.
-
-\subsection{Ethical Considerations}
-
-The designers of conversational agents need to consider ethical implications and potential negative impacts for users.
-This section discusses three main areas of concerns related to the effect of conversation architecture on the perceptions of agents: gender stereotypes, influencing user's actions and privacy concerns.
-
-For the element of prosody, various studies in our corpus explored the effect of different pitches on the perceptions of agents.
-Even in studies that are not explicitly analyzing the effect of different gendered voices in an agent, possible stereotypes may still exist in the study.
-Based on our reviewed corpus, studies found that lower pitches commonly associated with men are considered to be more desirable, authoritative but less friendly \cite{tolmeijer2021female}\cmt{[62]}\cite{jestin2022effects}\cmt{[81]}.
-For Dubiel et al's study \cite{dubiel2020persuasive}\cmt{[60]}, the agent with lower mean pitch was selected as the more persuasive voice.
-These results may be demonstrating users' unconscious bias to select a male sounding voice as more persuasive and authoritative over female sounding voices that are commonly associated with higher pitches.
-While some guidelines recommend designing agents to be androgynous to avoid gender stereotypes \cite{ruane2019conversational}, there are limitations in creating gender-ambiguous voices.
-Currently there is no defined guidelines on what is perceived as a gender-neutral voice \cite{jestin2022effects}\cmt{[81]}.
-There is also a lack of voice generators available to generate voices that are perceived as androgynous \cite{tolmeijer2021female}\cmt{[62]}.
-
-Studies have demonstrated that conversation architecture elements can be used to design perceptions of agents to make CAs more persuasive.
-This opens up the ethical issue of influencing users' attitudes and behaviours through these persuasion techniques.
-In a study by Chan et al \cite{chan2021kinvoices}\cmt{[74]}, they found that CAs using kin's voices are perceived as more credible and likeable, with a higher perceived social presence with the agent.
-These perceptions contributes to the agent being more engaging and persuasive, therefore people are more likely to comply with its requests.
-Andrew et al \cite{andrews2012system}\cmt{[38]} found that tailoring the personality of the CA to users will positively impact an agent's persuasiveness.
-These persuasion techniques can be beneficial to help users achieve their goals, but can also be used for harmful actions, such as trying to get users to believe in false information.
-
-Another key area of concern is privacy.
-Given the natural language format of conversational agents, users may be disclosing more sensitive and personal information than needed for the interaction.
-In relationship to conversation architecture, using elements like self-disclosure and persuasive voice prosody settings could result in users perceiving higher trust with the agent, leading them to disclose more sensitive information  \cite{lee2020hear}\cmt{[23]}\cite{dubiel2020persuasive}\cmt{[60]}.
-This can expose users to attacks, such as CAs using voice impersonation to ask for personal information for malicious intents \cite{chan2021kinvoices}\cmt{[74]}.
-Designing for perceptions of agents requires careful consideration of privacy issues including the sensitivity of the data, who has access to it, and how to protect against nefarious users.
-
-\subsection{Limitations}
-
-Our systematic literature review was limited to papers published in the ACM Digital Library between 2010 and 2022.
-We may have missed literature published outside this time period, as well as in other libraries.
-Also, most of the studies in our corpus are based on lab experiments using short interactions with users.
-The generalizability of these findings need to be verified through longer term engagements with conversational agents deployed in real world situations.
-Lastly, research without empirical studies on the perception of agents are excluded based on our selection criteria.
-We may have missed some influential findings in these papers.
-%To better understand the relationships between conversation architecture elements and the perceptions of agents, we plan to conduct future reviews in literature and user studies to understand their real-world impacts.
-
-\section{Conclusions}
-
-In this paper, we discussed the results of a systematic review of existing literature published in the ACM Digital Library on the effect of conversation architecture elements on the perceptions of CAs.
-Through our synthesis of 57 papers in our corpus, we present a framework outlining the relationships between elements of agents’ conversation architecture (dialog strategy, content affectiveness, content style and speech format) and aspects of users’ perception (interaction, ability, sociability and humanness).
-During our analysis, we found the need for consistent protocols in evaluating perceptions of agents, as measurements are inconsistent across studies.
-Further research is needed to investigate the under-explored areas in the framework, the relationship across perception aspects, the influence of contextual factors, and the effect of composite conversation architecture elements on users' perceptions.
-While our research contribute to the design conversation architecture to orchestrate specific perceptions of agent, we urge designers to incorporate ethical perspectives into their design considerations.
+\input{sections/1-introduction}
+\input{sections/2-related_work}
+\input{sections/3-method}
+\input{sections/4-findings}
+\input{sections/5-discussion}
+\input{sections/6-conclusion}
 
@@
 %% the bibliography file.
-\bibliographystyle{ACM-Reference-Format}
+\bibliographystyle{config/ACM-Reference-Format}
 \bibliography{references}

### 2023-02-21 sections/1-introduction.tex
restructured manuscript

%% INTRODUCTION SECTION %%

\section{Introduction}

Conversational agents (CAs), such as Amazon Alexa or Google Assistant, are designed to interact with humans using natural language through voice or text modalities. Since these agents interact with users using natural language, conversation architecture — which refers to what a CA says and how it says it — affects how these agents interact with users. The effectiveness of these interactions with CAs are strongly dependent on users' perceptions of agents \cite{knijnenburg2016inferring}\cite{seeger2021chatbots}. According to previous research, there is a correlation between CAs' conversation architecture and users' perception of these agents.

While there are various studies on how different conversation architecture elements affects agents' perceptions, there is a paucity of knowledge on the overall coverage and effects of these relationships explored in literature. For conversation architecture elements, The use of affective language is commonly explored, with studies finding that conversational agents are perceived as more socially present and emotionally intelligent if they use sentiment-adaptive response based on user's utterances \cite{diederich2019emulating}\cite{yang2017perceived}. Another commonly explored element is the use of prosody in voice-based agents, such as the use of express prosody contributing to higher perceived enjoyment and intimacy with the agent \cite{kim2020can}. However, there is a lack of research to synthesize these findings into an overall framework. One of the possible issues is the lack of clear and consistent definitions on the aspects of user's perceptions of agent and conversation architectural elements.

Currently there is no systematic understanding on the elements of conversation architecture that are relevant to perceptions of agents. Some papers have started to examine the speech specifics that are being explored in literature, such as Clark et al. \cite{clark2019state} capturing different elements of system speech production for voice-based agents and categorizing them based on content, style, and other topics. There are also some investigations of conversation architecture elements within the broader field of studying cues that trigger a social reaction of the user towards the CA. Feine et al's \cite{feine2019taxonomy} paper laid the foundation to create a consistent taxonomy for these social cues. However, there is no comprehensive research specifically for conversation architecture elements that are relevant to user perceptions.

Related to user perceptions, there is also no systematic understanding on the perceptions of agents affected by speech variations. Some research discussed the perceptions of agents as part of the broader scope of user experiences of CAs. These publications have gathered UX dimensions used to evaluate conversational agents, which include the perceptions of agents (e.g. empathy, humanness) alongside other assessments (e.g. physiological data) \cite{clark2019state}\cite{finch2020towards}. Some even categorized the metrics based on the type of method used, including technical measures like system error rate and perception measures like perceived social presence \cite{zheng2022ux}. However, these studies are assessing the general field of UX measurements and not specifically on the perceptions of agents, and do not analyze the effects of conversation architecture on these perceptions.

These research gaps discussed above: the paucity of knowledge on synthesizing the effect of speech specifics on perceptions of CAs as well as the lack of systematic understanding on the elements of conversation architecture and perceptions of agents motivated us to the goal of how to design conversation architecture in order to orchestrate perceptions of conversational agents. First, we want to understand \textbf{(RQ1) what perception aspects of agents are being explored in relation to the effects of conversation architecture elements}. While there are various architecture elements of conversation architecture used in a CA's utterances, we don't have a holistic understanding of them. This leads to our second research question: \textbf{(RQ2) what elements of conversation architecture are relevant to the perceptions of agents?} Lastly, we want to understand the effect of conversation architecture on perceptions of agent, specifically: \textbf{(RQ3) what are the relationships between conversation architecture elements and the perceptions of CAs?}

To answer these questions, we performed a comprehensive review on existing literature from 2010 to 2022 and synthesized the effect of conversation architecture elements on the perceptions of CAs based on 57 relevant papers (Figure \ref{fig:heatmap-impact}). We also grouped the perceptions of agents affected by conversation architecture into four categories and eleven aspects (Table \ref{tab:perceptions}), and grouped the speech variations related to perceptions of agents into four categories and eleven elements (Table \ref{tab:cues}). %Lastly, we coded the explored connections between conversation architecture and perceptions and synthesized their relationships into a framework. Through our analysis, we also found that there are inconsistencies in the assessment of perceptions across studies, as well as influencing factors other than conversation architecture that impact the perceptions of agents. 
This work contributes to the HCI community by presenting a framework that demonstrates the effect of conversation architecture on perceptions of conversational agents, as well as taxonomies for perception aspects and conversation architecture elements providing clear and consistent terms that can be used in future research. Together, these contributions move us one step closer to designing CAs that effectively interact with users. 
%Also, our analysis extends existing reviews on UX research of CAs \cite{clark2019state}\cite{rapp2021human}\cite{zheng2022ux} by providing a synthesized framework outlining the relationships between conversation architecture and perceptions of agents. With the help of this framework, we are taking the first step to understand how to design conversational agents to solicit specific social reactions from users.

In the remainder of the paper, we first outline related background work, our literature review process, as well as the characteristics of the papers in our reviewed corpus. Following that, we describe in detail the taxonomy for the perception of agents, the taxonomy for conversation architecture element, as well as the framework on the relationships between perceptions of agents and conversation architecture. Finally, we discuss research challenges and opportunities as well as ethical considerations for designing conversational architecture to orchestrate perceptions of conversational agents.

### 2023-02-21 sections/2-related_work.tex
restructured manuscript

%% RELATED WORK SECTION %%

\section{Related Work}

Communication with conversational agents is similar to communicating with humans as they both use natural languages for the interaction. While it is tempting to leverage components from human-human conversation in designing interactions with conversational agents, studies have demonstrated that there are differences between human-human communications and human-agent communications. Currently people consider CAs as a user-controlled tool rather than a social companion, with focuses on the utilitarian aspects of the conversation \cite{clark2019makes}\cmt{[1]}. When conversing with conversational agents, users tend to use shorter messages with limited vocabulary, adapting to the style of the agent \cite{hill2015real}. Also, some studies found that small talk and humour are considered unnecessary or even inauthentic in conversations with CAs, while these elements are important in scaffolding communications with human partners \cite{clark2019makes}\cmt{[1]}\cite{doyle2019mapping}\cmt{[2]}. There are also machine-like traits that users preferred in a CA, such as the ability to interact through multimodal media, and a machine's perceived ability to be objective and non-judgemental \cite{doyle2019mapping}\cmt{[2]}\cite{kim2022understanding}\cmt{[3]}. Given human-agent communications are different from human-human communications, it is important to look specifically at the design of user experiences for conversational agents.

There have been numerous studies on the user experiences for conversational agents, and some attempts to synthesize findings across literature. Several papers have mapped out the current state of research for conversational agents for specific agent types (e.g. text-based, voice-based, polyadic) highlighting major trends, topics, methods and evaluating metrics \cite{clark2019state}\cmt{[33]}\cite{rapp2021human}\cmt{[5]}\cite{zheng2022ux}. Other papers looked at specific dimensions of user experiences or domains of usage, such as Van Pinxteren et al. \cite{van2020human} examining the effects of agents' human-like communicative behaviours on their relationships with users, and Kocaballi et al. \cite{kocaballi2022design} exploring the challenges and opportunities of CAs in healthcare. There are also publications aimed to unify concepts used in the research for CA user experiences, for instance Feine et al. \cite{feine2019taxonomy} creating a taxonomy of social cues, and Finch et al. \cite{finch2020towards} analyzing evaluation protocols for dialogue systems. To the best of our knowledge, there is currently no synthesis on the speech specifics of CAs, the perceptions of agents, or the relationship between them.

Conversation architecture has been demonstrated to play an important role in users' perceptions of agents \cite{knijnenburg2016inferring}\cite{moussawi2021perceptions}\cite{seeger2021chatbots}\cmt{[35]}. Yet, little is known about the overall landscape on the how the specifics of speech variations affect these perceptions. Given the paucity of research in this area, this paper aims to synthesize the identified relationships between conversation architecture elements and users' perceptions of agents.

%Other papers categorized CA assessments into themes. For example, Rapp et al. \cite{rapp2021human} generated themes related to how users' experience with chatbots such as experiencing the chatbot including assessments on expectation, perception, satisfaction etc.  Most recently, Zheng et al's literature review on the UX research of CAs \cite{zheng2022ux} categorized the metrics based on the type of method used, including technical measures like system error rate and perception measures like perceived social presence. However, existing studies use different terminologies and categories across aspects of perception. As an illustration, it is unclear if the theme of experiencing the chatbot from Rapp et al. \cite{rapp2021human} contains similar aspects to the perception towards CA in Zheng et al \cite{zheng2022ux}'s analysis.
%\cite{finch2020towards} Towards unified dialogue system evaluation: A comprehensive analysis of current evaluation protocols

%Anthropomorphism is defined as the attribution of traits that we typically associate with being distinctly human to nonhuman entities \cite{waytz2010sees}. For example, users tend to personify conversational agents like Amazon Alexa by using person pronouns instead of object pronouns in online reviews \cite{purington2017alexa}.  Research shows that anthropomorphic design is beneficial to establishing and maintaining trust between users and conversational agents \cite{seeger2021chatbots}. Also, speakers tend to align their lexical choices with conversational agents, similar to human-human conversations \cite{cowan2015does}. Anthropomorphism has been shown to ease user interactions, e.g. making agents more approachable, engaging, and trustworthy when they exhibit human characteristics \cite{qiu2009evaluating}. These processes are of particular interest for human-agent communication because they form the basis for user expectations and predispositions regarding agents' behavior, reliability of the information, etc. \cite{kuzminykh2020genie}.

### 2023-02-21 sections/3-method.tex
restructured manuscript

%% METHOD SECTION %%

\section{Method}

This section describes the research methodologies used for data collection and data analysis. Additionally, it presents the characteristics of the papers in our reviewed corpus.

\subsection{Data Collection}

Following PRISMA guidelines \cite{prisma}, we reviewed and selected literature exploring the relationship between the specifics of conversation architecture elements and perceptions of CAs. Searches were carried out in the ACM Digital Library between January 1 and January 15, 2023. Through our analysis, we didn't find any common terms used to refer to either conversation architecture elements, or aspects of perceptions. As such, we generalized our search term to capture articles related to conversational agents. Based on search terms used in previously published literature reviews \cite{clark2019state}\cite{rapp2021human}, the following keywords are used to search for publications related to conversational user interfaces:
\newline

\textit{"conversational agent" OR "natural language interface" OR "IPA" OR "intelligent personal assistant" OR "chatbot" OR "speech interface" OR "voice assistant" OR "intelligent agent" OR "human-chatbot communication" OR "virtual agent" OR "dialog* system" OR "voice user interface" OR "human computer dialog*"}
\newline

The following selection criteria are applied to identify literature related to the effect of conversational architecture on the perception of agents:
\begin{itemize}
  \item The paper was published between 2010 and 2022.
  \item The paper is peer-reviewed and written in English.
  \item The paper contains the use of voice-based or text-based conversational agents.
  \item The paper contains studies on the impact of conversation architecture elements on the perceptions of agents.
  \item The paper contains impact of conversation architecture elements can be separated from other effects (e.g. embodiment).

\end{itemize}

The initial query retrieved 2901 unique publications. We screened the titles and abstracts of the papers based on the selection criteria above, resulting in 221 papers. The fully body of these papers are then reviewed, selecting papers that met the criteria. A search for additional literature was also performed to supplement the corpus, adding 8 more papers to the selection. In total, we identified 57 relevant articles for analysis (see Figure \ref{fig:prisma}).

\input{figures/fig-prisma}

\subsubsection*{Literature Corpus Characteristics}

The papers reviewed (n=57) were published between May 2011 and November 2022. More than 75\% of the papers were published in or after 2019, with a slight trend upwards over the years (see Figure \ref{fig:paper}). The vast majority of the papers in our corpus were published in conference proceedings (n=50), with the remainder papers published in journals. Out of the papers published in conferences, the top conferences were The ACM Conference on Human Factors in Computing Systems\footnote{https://dl.acm.org/conference/chi} (n=16), Conversational User Interfaces\footnote{https://dl.acm.org/conference/cui} (n=7), Human-Agent Interaction\footnote{https://dl.acm.org/conference/hai} (n=4), and Intelligent Virtual Agents\footnote{https://dl.acm.org/conference/iva} (n=4). 
%Out of the papers published in journals, some venues include the International Journal of Human-Computer Interaction\footnote{https://www.tandfonline.com/journals/hihc20} (n=2) and Interacting with Computers\footnote{https://academic.oup.com/iwc} (n=1).

On the modality characteristics of the conversational agents in the corpus, there is a roughly even split between the modalities, with slightly more papers exploring voice-based CAs (n=30) compared to text-based CAs (n=27).

\input{figures/fig-paper}

\subsection{Data Analysis}

\subsubsection*{Perceptions of Agents} To understand the perceptions of agents related to conversation architecture (RQ1), assessments for the perceptions of agents were extracted from each paper. We used inductive thematic analysis to group these assessments into codes based on their meanings. For example, the code likeability of the agent contains the questionnaire item "this voice agent was likeable" used by \cite{cuadra2021my}\cmt{[67]}, Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed}'s set of questions on likeability used by \cite{linnemann2018can}\cmt{[15]}, and Subjective Assessment of Speech System Interface (SASSI) questionnaire \cite{hone2000towards}\cmt{sassi}'s set of questions on likeability used by \cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}. This step resulted in 83 unique codes. These codes are then organized based similarity of the meanings, resulting in 11 aspects of perceptions. For example, the aspect of personality traits of the agent contains measurements such as likeability, funniness, and kindness. Lastly, the 11 aspects are grouped into 4 categories: perception of interaction with agent, perception of agent's ability, perception of sociability with agent, and perception of agent's humanness (Table \ref{tbl:perceptions}).

\subsubsection*{Conversation Architecture Elements}
As to the elements of conversation architecture that are relevant to the perception of agents (RQ2), we extracted the specifics of conversation architecture used in each paper. Some of the papers used multiple features in their CA design, such as the the anthropomorphic agent used in Seeger et al's study \cite{seeger2021chatbots}\cmt{[35]}. In these composite situations, we broke them down into their individual features. For example, the anthropomorphic agent \cite{seeger2021chatbots}\cmt{[35]} was separated into emotional expressions, is-typing indicator, emoticons, and response delay and captured as codes. 58 unique codes were created as part of this process, capturing features like sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}, lexical alignment \cite{spillner2021talk}\cmt{[18]}, and typos \cite{westerman2019believe}\cmt{[9]}. We then organized these codes into elements based on similarity, resulting in 12 elements of conversation architecture. For example, the element of disfluency contains fillers \cite{jeong2019exploring}\cmt{[10]}\cite{wester2015artificial}\cmt{[14]}, interjections \cite{ceha2022expressive}\cmt{[77]}\cite{hu2021enhancing}\cmt{[56]}, repetitions \cite{yang2021effect}\cmt{[72]} and typos \cite{westerman2019believe}\cmt{[9]}. These elements are grouped into 4 categories: dialog strategy, content affectiveness, content style, and speech format (Table \ref{tbl:conversation_architecture}).

\subsubsection*{Relationship Between Perceptions of Agents and Conversation Architecture}

\input{figures/fig-heatmap_identified}

To study the effect of conversation architecture on users' perceptions (RQ3), we extracted the connections explored in each paper, using the perception aspects and conversation architecture elements developed in the previous data analysis steps. Each connection's effect was also recorded based on whether an association was found in the study and the nature of that association. Out of our review corpus, 265 connections between perceptions of agents and conversation architecture were explored in literature. To analyze the specifics of conversation architecture that affect the perceptions of CAs, 72 connections that did not result in observed relationships were discarded, resulting in 193 relationships for analysis. For example, the connection between the matching style of a CA and user satisfaction was removed because Hoegen et al. \cite{hoegen2019end}\cmt{[31]} did not find a significant difference between the style matching agent and the non-style matching agent for overall interaction satisfaction. Out of the 193 relationships, 10 were relationships based on agents modifying multiple architecture elements (e.g. \cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2021manipulating}\cmt{[68]}). They were not included in the final framework as we could not attribute the perceptions of agents to the underlying core elements. Overall, 183 relationships between individual architecture elements and perceptions of agents are incorporated into our synthesized framework, visualized as a heatmap to demonstrate their relationships with each other (Figure \ref{fig:heatmap_identified}).

### 2023-02-21 sections/4-findings.tex
restructured manuscript

%% FINDINGS %%

\section{Findings}

\subsection{Perceptions of Agents}

As shown in Table \ref{tbl:perceptions}, there are four categories defined for the perceptions of conversational agents covering 11 different aspects of perception. The details of each category and aspect are discussed below.

\textbf{Perception of interaction with agent} assesses the overall interaction quality users had with the conversational agent. The three aspects for this perceptions are usability, engagement and satisfaction. \textit{Usability} captures the utilitarian component of the interaction, whether it was accurate, easy to use, efficient or helpful. Some commonly used methods to evaluate usability include the response accuracy portion of the SASSI questionnaire \cite{hone2000towards}\cmt{sassi}, or the NASA Task Load Index (NASA-TLX) \cite{hart1988development}\cmt{nasa} for cognitive workload. Questions such as "the system is easy to use" or "it is easy to understand the agent" are also used to evaluate usability. \textit{Engagement} on the other hand captures users' emotional reactions to the CA, whether they have enjoyed the conversation, or annoyed or frustrated with the interaction. Some commonly used methods to evaluate engagement include the annoyance portion of the SASSI questionnaire \cite{hone2000towards}\cmt{sassi}, and the Use Engagement Scale (UES) \cite{o2018practical}\cmt{ues}. Questions such as "I enjoyed using the system" or "I felt frustrated with the agent" are also used to evaluate engagement. Lastly, \textit{Satisfaction} captures users' overall satisfaction interacting with the agent. Questions such as "the overall assessment of conversing with the CA was satisfactory" are used to evaluate this perception.

\textbf{Perception of agent's ability} assesses the perceived capabilities of the agent. Unlike system capabilities that affect agent's performance, the perceived ability category captures perceptions of agents with equivalent system capabilities but varied conversation architecture elements. Specifically, \textit{intelligence} captures the agent's expertise and knowledge, and it is commonly administered through the Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed} using the set of questions related to perceived intelligence. Also survey questions such as asking users about the agent's intelligence and domain knowledge are used to evaluate perceived intelligence. \textit{Competence} takes intelligence one step further by examining the agent's ability to put its intelligence into practice. Surveys or qualitative feedback are usually used to assess if the agent is capable and competent, and whether users have confidence in the agent's ability to get the job done. Lastly, \textit{credibility} captures agent's truthfulness, benevolence, and user's confidence in CAs. Some commonly used methods to evaluate trust include the Trust Propensity Scale \cite{mayer1999effect} and the Individualized Trust Scale (ITS) \cite{wheeless1977measurement}. Questions such as "is the agent honest" and "can I trust the agent with sensitive information" are also used to evaluate trust.

\textbf{Perception of the sociability with agent} assesses the emotional connections that users have with agents. This category includes perception aspects of conversation tone, social presence and intimacy. \textit{Conversation tone} captures the affective impression of the agent's tone, such as empathy and expressiveness. Also, this aspect includes whether the tone used by the agent was perceived as friendly, polite or warm. \textit{Social presence} captures the sense of connectness and psychological distance users have with an agent. Some aspects in this category include the sense of familiarity or similarity with the agent, and whether users feel the agent behaves like them or have similar attitudes to them. The category of \textit{Intimacy} extends social presence into the realm of the quality of relationships with an agent. Some commonly used methods to assess intimacy include the set of social attraction questions from the interpersonal attraction questionnaire \cite{mccroskey1975development} and the quality of relationship inventory (QRI) \cite{pierce1997assessing}. These questionnaires include questions like "I think the agent could be a friend of mine", or "I feel we could establish a personal relationship with each other".

\textbf{Perception of agent's humanness} assesses the specifics of anthropomorphized perceptions of conversational agents. \textit{Human-likeness} captures whether the agent presented itself as natural and human-like, or artificial and machine-like. The Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed} set of questions related to anthropomorphism and the Ascent of Man scale \cite{kteily2015ascent} are commonly used methods to evaluate human-likeness. Survey questions with semantic scales such as "human-like / machine-like" and "artificial / natural" are also commonly used for this aspect of perception. \textit{Personality traits} captures the human characteristics that are attributes to the agent. This is commonly collected as qualitative feedback from users, commenting on whether the agent is extroverted or introverted, or the perceived personality such as likeable, funny or witty. Sometimes the Big-5 personality traits questionnaire \cite{gosling2003very} is used to map an agent's disposition on various personality dimensions.

Overall there is a good coverage of different aspects of perception based on the list of papers reviewed in our corpus. The most commonly explored aspect categories is the perception the interaction with agent, followed by the perception of agent's humanness. There are two aspects that are the least explored compared to the others relationships: competence within the perception of agent's ability, and intimacy within the perception of social connection with agent. This may be due to the controlled lab settings for the experiments, where participants are given the scenarios for interaction. This type of environment is not conducive to forming relationships with a conversational partner, as noted by Linnerman et al. in their discussions \cite{linnemann2018can}\cmt{[15]}. The same factor could impact the assessment of agent's competence, as the users may not feel like they have the expertise to assess their perceptions. 
%These factors could contribute to the reasons why competency and intimacy are not as frequently measured in experimental studies.

\input{tables/tbl-perceptions}
\input{tables/tbl-conversation_architecture}

\subsection{Conversation Architecture Elements}

As shown in Table \ref{tbl:conversation_architecture}, there are four categories defined for conversation architecture across 12 different elements. The details of each category and element are discussed below.

The category of \textbf{dialog strategy} refers to the approach used by a conversational agent to engage in a dialogue with a user, which includes the use of social dialogs, agent-initiated content, and adding delays to responses. Specifically, the element of \textit{social dialogue} captures non-task related conversations with the user to build social connection, such as self-disclosure \cite{lee2020hear}\cmt{[23]} and small talk like chitchats \cite{lubold2016effects}\cmt{[86]}\cite{volkel2021manipulating}\cmt{[68]}. The element of \textit{initiative} captures utterances that are initiated by the agent without direct prompts from the user. For example, the agent is taking the initiative to proactively repair the conversation with a user \cite{ashktorab2019resilient}\cmt{[88]}\cite{cuadra2021my}\cmt{[67]}, or actively elicit feedback from users \cite{xiao2021let}\cmt{[73]}. Lastly, \textit{response delay} refers to the tactic of deliberatively delaying for a certain period of time before an agent responds to users \cite{gnewuch2018faster}\cmt{[19]}\cite{gnewuch2022opposing}\cmt{[20]}. It is mainly used in text-based CAs alongside visual displays of typing indicators \cite{gnewuch2018chatbot}\cmt{[21]}.

\textbf{Content affectiveness} refers to the conversational agent's use of language to convey emotions or to elicit emotions from users. The architecture element of \textit{affective language} captures the injection of emotional words or phrases into the agent's utterance, such as affective expressions \cite{seeger2021chatbots}\cmt{[35]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}, sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}, and encouraging words \cite{healey2013relating}\cmt{[39]}. The other element in this category, \textit{humour}, captures an agent's attempt to include jokes in its dialog. Several studies in our reviewed corpus have explored the effect of humour on various perceptions of agents (e.g. \cite{ceha2021can}\cmt{[57]}\cite{khooshabeh2011does}\cmt{[37]}).

The category of \textbf{content style} refers to the variations of language used in a message aside from the content meaning of the message (i.e. how something is said). The element of \textit{formality} describes the linguistic style used by the conversational agent, whether it is formal vs. casual, such as using honorific expressions to address users \cite{ouchi2019should}\cmt{[59]}. \textit{Alignment} captures the degree that the agent aligns its utterances to the users, such as lexical alignment on the content and structural of the sentences \cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}, as well as referring and agreeing with users' utterances \cite{volkel2021examining}\cmt{[69]}. Lastly, the element of \textit{elaborateness} captures the sentence complexity and length of agents' utterances. For example, Roy et al. explored the differences in perception for variations in elaborateness such as "Cloudly, possibility of snow, high: 4, low: -10" vs "Today will be cloudy, with a high of 4 and a low of -10. Snow is predicted" \cite{roy2021users}\cmt{[71]}.

Lastly, the category of \textbf{speech format} captures the non-verbal component of a conversational agent's utterances for both text and voice modalities. \textit{Disfluency} captures 
the use of non-lexical utterances like filler words ("um, uh") \cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}, or repetition of words within a sentence \cite{yang2021effect}\cmt{[72]}. It also includes the format of using typos \cite{westerman2019believe}\cmt{[9]} for text-based agents. For voice-based agents specifically, the element of \textit{prosody} encompasses vocal qualities like pitch \cite{habler2019effects}\cmt{[63]}\cite{jestin2022effects}\cmt{[81]}, speech rate \cite{choi2020nobody}\cmt{[54]}, and spoken accent \cite{feijoo2021effects}\cmt{[70]}. For text-based CAs, the \textit{text formatting} element includes different formats agents uses to present information to users, such as using capitalization \cite{westerman2019believe}\cmt{[9]} or emoticons \cite{kim2019comparing}\cmt{[89]}\cite{wilhelm2022keep}\cmt{[28]}.

Overall there are similar number of conversation architecture elements explored across the four categories of dialog strategy, content affectiveness, content style, and speech format. As for explorations related to different modalities of agents, there is a noticeable difference in the category of speech format, where architecture elements related to voice-based agents (n=15) are explored more than text-based agents (n=7). Looking across the 12 different elements, there is good coverage of studies on the impact of affective language and prosody cues on the perceptions of agents. However, there are less studies exploring the effect of agent initiated content and response delay on the perception of agents. Specifically for the element of initiative under dialog strategy category, there is literature on conversation repairs \cite{komatani2010online}\cite{reinkemeier2022repair} and agent proactively sharing content with users \cite{dubiel2019inquisitive}\cite{zargham2022understanding}, but many of them did not not include assessments of perceptions of the CA. This may be due to the fact that the usage of agent-initiated content is relatively new, as CA interactions have historically been driven by users. As such, current research is focused on the functional aspects of agents initiating contents instead of exploring the perceptions of agents. As for response delay, there are indications that this element is under-explored in literature. Only 4 studies in our reviewed corpus used an agent with response delay, and the majority of these publications were written by the same authors.

\subsection{Relationship Between Perceptions of Agents and Conversation Architecture}

There are 183 identified relationships between perceptions of agents and conversation architecture out of the 265 explored connections that are included in our synthesized framework (Figure \ref{fig:heatmap_identified}). To compare the number of identified relationships vs. the explored connections in literature, Figure \ref{fig:heatmap_coverage} shows a side-by-side comparison between the two. The detailed analysis on the differences between explored and identified relationships are discussed in the subsections below.

While the number of papers studying CAs with voice (n=27) vs. text (n=30) modalities is not significantly different, there are some interesting patterns we found with regards to the modalities of the identified relationships between perceptions of agents and conversation architecture. Overall, we confirmed the pattern found earlier that there are more conversation architecture elements explored related to voice vs. text in the speech format category. Because there are smaller number of text-based CAs using speech format elements, we also observed significantly less number of relationships between text-based CA across all perceptions of agents. other interesting findings related to modality are discussed later in this paper.

\input{figures/fig-heatmap_coverage}

\subsubsection{Perception of Interaction with Agent}

The effects of conversation architecture elements on the perception of interaction with agent is the most explored connections in the corpus (n=97). Out of these explored connections, the majority of them (n=66) discovered a relationship between aspects of perception related to the perception of interaction with agent related to the studied architecture element. Looking at the difference between modalities, we noticed more voice-based agents (n=25) resulted in null relationships compared to text-based agents (n=6). The conversation architecture element of \textit{alignment} contributed the most to the null results for voice-based agents, with 9 out of 11 explored connections did not find any relationships related the perception of interaction with agents.

Across the aspects for the perception of interaction, both usability and engagement were assessed frequently in the reviewed literature, with conversation architecture having effects on these perception aspects across all architecture element categories. The aspect of satisfaction was used in some studies to evaluate perception but it is not used as often as engagement or usability. Several papers that assessed user satisfactions were conversation agents within the transaction context, especially within the customer service domain (e.g. \cite{diederich2019emulating}\cmt{[25]}\cite{elsholz2019exploring}\cmt{[61]}\cite{gnewuch2018faster}\cmt{[19]}).

The category of conversation architecture elements with the most identified relationships to perceptions of interaction is content style. Specifically for the element of \textit{elaborateness}, users found the use of full sentences more useful than keyword only \cite{haas2022keep}\cmt{[78]}\cite{roy2021users}\cmt{[71]}. Otherwise, the effect of an agent's elaborateness on user's perception of interaction depends on the user's preference \cite{miehle2018exploring}\cmt{[51]}, as well as the topic of discussion \cite{haas2022keep}\cmt{[78]}. As for \textit{formality}, various studies reported significant differences in perceptions of interaction between using casual vs. formal styles. Some users experienced higher engagement with agent interacting with the casual style of the conversation \cite{cox2022does}\cmt{[27]}, while in another study users reported the formal language style as less engaging as it is boring \cite{kim2019comparing}\cmt{[89]}.

The speech format of an agent also resulted in a high number of identified relationships with the perception of interaction with CAs, with majority of the explored connections resulted in effects between the perception aspects and architecture elements. The element with the most identified relationships is \textit{prosody}. For example, studies found that a CA's expressiveness in vocal cues increased participants' engagement ratings \cite{zhu2022effects}\cmt{[26]}, and different pitches of voice affect users' perception of engagement and usability \cite{chan2021kinvoices}\cmt{[74]}\cite{habler2019effects}\cmt{[63]}.

Dialog strategy and content affectiveness categories of conversation architecture did not have as many identified relationships with perceptions of interaction. It is worth noting the effect of using the \textit{initiative} element, as CAs that use self-initiated content are perceived as more efficient and higher quality of interaction (e.g. \cite{cuadra2021my}\cmt{[67]}). Also, some studies have discovered conflicting effects between different perception aspects of interaction for CAs using \textit{social dialog}, as users enjoyed the conversation using social talk \cite{lee2020hear}\cmt{[23]}\cite{roy2021users}\cmt{[71]}, but perceived the CA as less efficient \cite{roy2021users}\cmt{[71]}.

\subsubsection{Perception of Agent's Ability}

The effects of conversation architecture elements on the perception of agent's ability is the least explored connection in the corpus (n=39). Out of these explored connections, the majority of them (n=30) found relationships between the studied architecture element and the perceptions of agent's ability. There are no notable differences between the text and voice modalities of CAs for either explored connections or the identified relationships.

Aspects within the perception of agent's ability had similar number of identified relationships across intelligence, competence and credibility. Our review revealed that the perceived ability of a CA is also dependent on other influencing factors in addition to conversation architecture elements. Volkel et al. \cite{kraus2020effects}\cmt{[64]} found that the perception of competence of a proactive CA is dependent on task difficulty \cite{kraus2020effects}\cmt{[64]}. Also, the perception of intelligence for an agent using fillers depended on the context of the conversation, as the filler-speaking agent was perceived as less intelligent in task-oriented conditions, but was seen as slightly more intelligent in social-oriented conditions \cite{jeong2019exploring}\cmt{[10]}.

Out of the explored conversation architecture elements, \textit{prosody} had relationships identified with aspects across the perception category of agent's ability. For example, Chan et al. \cite{chan2021kinvoices}\cmt{[74]} found that agents using kin's voices are rated as more intelligent and credible than generic voices. Also, the style of speech used by an agent affects the perception of appropriateness of tone, which is an aspect of the perceived competence of an agent \cite{misu2011toward}\cmt{[83]}. Different content styles of \textit{formality} also impacts the perceived competence of an agent \cite{cox2022does}\cmt{[27]}\cite{jestin2022effects}\cmt{[81]}. Specifically related to perceived credibility of an agent, being \textit{lexically aligned} with the user resulted improved the rating of trustworthiness of an agent \cite{hoegen2019end}\cmt{[31]}\cite{linnemann2018can}\cmt{[15]}. There were mixed results on the use of emoticons within the \textit{text formatting} element. One study found the chatbot using emoticons as less trustworthy \cite{wilhelm2022keep}\cmt{[28]}, while another study found that users assigned higher scores for confidence to the agent using emojis \cite{fadhil2018effect}\cmt{[52]}.

There are several conversation architecture elements with little to no explorations to the perception of agent's ability. Specifically, both categories of dialog strategy and content affectiveness are minimally explored in our reviewed corpus, with no explored connections with \textit{response delay} and only one or two connections explored for \textit{social dialog} and \textit{humour}. While the content style category had coverage in some aspects of perceived abilities, it is worth noting that \textit{elaborateness} did not have any explored connections with perceived ability of agents. Further research in these areas is needed to fill these gaps in understanding.

\subsubsection{Perception of Sociability with Agent}

The perception of agent's humanness is the second most explored category within our reviewed corpus (n=64), with majority of the connections identified relationship between the studied conversation architecture elements and the anthropomorphized perceptions of agent (n=49). Interestingly, studies explored more perceptions of sociability with agent related to voice-based CAs (n=40) compared to text-based CAs (n=24), potentially due to the assumption that interactions with text-based agents are perceived as less personal and more formal \cite{kocielnik2018designing}. There are some mixed results for voice-based CAs, as 12 out of the 28 connections did not find any significant results. Drilling down to the specific elements, we noticed that the use of \textit{alignment} in voice-based agents did not effect the perception of sociability with agent \cite{healey2013relating}\cmt{[39]}\cite{linnemann2018can}\cmt{[15]}. We didn't have data on text-based agents' perceived social connections with users to compare with voice-based agents, as the studies using alignment and text modality in our corpus did not assess this aspect category of perception.

Across the aspects in this perception category, conversation tone had the most number of identified relationship (n=27) with the perceived social connection with CAs, followed by the aspect of social presence (n=17). There are only 5 relationships found that are linked to the perception aspect of intimacy. One reason for this is half of the explored connections did not have any effect on the perception of sociability with agent, such as the use of capitalization \cite{westerman2019believe}\cmt{[9]}, lexical alignment \cite{linnemann2018can}\cmt{[15]}, or social talk \cite{lubold2016effects}\cmt{[86]}. For the perception aspect of social presence, we noticed a gap in the exploration of conversation architecture elements of formality, alignment, and elaborateness in the content style category, as there are no papers explored at this intersection.

Looking at the different categories of conversation architecture elements, the heatmap (Figure \ref{fig:heatmap-impact} shows that there are not many relationships in content style category that are related to the perceived sociability with CAs in general, with most of the discovered effects concentrated at the intersection of \textit{formality} and conversation tone. Studies have found that CAs using casual style of conversation are perceived as warm, empathetic and friendly \cite{jestin2022effects}\cmt{[81]}\cite{kim2019comparing}\cmt{[89]}, while CAs using formal style of conversation are perceived as polite but lacks empathy \cite{cox2022does}\cmt{[27]}. The rest of the architecture elements and perception aspects of sociability are minimally explored in literature, which indicates the need for more research in this area.

There are a few specific conversation architecture elements that had more identified relationships with perceptions of sociability with agent. Specifically, CAs using of \textit{affective language} were perceived to be more empathetic \cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{yang2017perceived}\cmt{[44]} and emotionally expressive \cite{zhu2022effects}\cmt{[26]}, as well as being more emotional connected with their users \cite{lee2019s}\cmt{[55]}\cite{lubis2019positive}\cmt{[43]}. Also, different variations of a voice-based CA's \textit{prosody} have effects on the perceived sociability with agent, such as an agent using expressive prosody is assessed as more intimate and more similar with the user \cite{kim2020can}\cmt{[24]}. Lastly, the conversation architecture element of \textit{humour} has identified relationships across the social connection category of perception. Clark et al. \cite{clark2019makes} found that humour is an important conversational characteristic for human-human interactions, but viewed as a novelty feature for human-agent conversations. However, in our review we found that humor has effects on human-agent relationships, as humorous agents are rated as more friendly, intimate, and similar by users compared to non-humorous agents \cite{go2021conversational}\cmt{[80]}\cite{khooshabeh2011does}\cmt{[37]}.

\subsubsection{Perception of Agent's Humanness}

There are 55 explored connections between conversation architecture elements and the perception of sociability with agents, with majority of them (n=38) finding identified relationships in literature. There are significantly more explorations for voice-based agents (n=39) as compared to text-based agents (n=16). Previous studies have found that modality may have an effect on the perception of humanness, as voice-based agents are perceived as more human-like as compared to text-based agents \cite{cho2019effects}. Out of the 39 explored connections for voice-based agents, 14 of them did not result in any relationships. This is especially evident in the architecture element of \textit{affective language} for voice-based agents, as most of the connections resulted in null relationships. For example, when comparing the ratings of human-likeness or likeability for a speech agent employing expressive words to the one not using any, Zhu et al \cite{zhu2022effects}\cmt{[26]} were unable to detect any statistically significant differences in both of the observation study and interaction study.

Across the aspects in this perception category, both human-likeness and personality traits have relationships with almost all the conversation architecture elements. Specifically for the use of \textit{prosody} elements, our review found some opposing effects on the perception of the agent's humanness. In the case of Chan et al's study \cite{chan2021kinvoices}\cmt{[74]}, participated rated the agent using kin voices as significantly more likeable compared to the generic voices, but it was perceived as eerie. This may be a warning indicator to watch out for the uncanny valley effect \cite{mori2012uncanny} and advise CA designers to carefully select conversation architecture elements to elicit anthropomorphized perceptions.

There are a few notable conversation architecture elements related to the perceived humanness of conversational agents. The use of \textit{prosody} such as varying pitch, intonation and speech rate has more identified relationships with the perceived personality traits of an agent as compared to the perceived human-likeness, especially on the aspect of likeability \cite{choi2020nobody}\cmt{[54]}\cite{jestin2022effects}\cmt{[81]}\cite{misu2011toward}\cmt{[83]}. For the architecture elements of \textit{disfluency}, the type of impact on the perception of humanness depended on the context of the conversation. Studies have found that participants perceived the filler-condition agent as more likeable in the social-oriented situation, but did not find the same effect in task-oriented situations \cite{jeong2019exploring}\cmt{[10]}\cite{wester2015artificial}\cmt{[14]}. The use of \textit{alignment} in an agent had a number of identified relationships with the perception of personality traits, with some studies finding CAs that are lexically aligned with a user are more likeable \cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}.

### 2023-02-21 sections/5-discussion.tex
restructured manuscript

%% DISCUSSION SECTION %%

\section{Discussion}

\subsection{Research Challenges and Opportunities}

%Three major needs emerged from the trends identified by our review: 1) 2) 3).

\subsubsection{The Need for Consistent Evaluation Protocols for Perceptions of Agents}

We found a diversity of approaches used to assess perceptions of agents in our reviewed corpus. While we made our best efforts to group perceptions used in literature based on similarity with each other, the inconsistent and composite nature of these perception assessments makes it challenging to synthesize them into a framework that contains homogeneous components in each perception aspect that can be compared with each other.

Based on the literature reviewed in this paper, it is unclear whether perception aspects using similar labels are being evaluated \textit{consistently} through different approaches. For example, we found several methods used to assess the perceived human-likeness of an agent. A commonly used survey is adapted from the Godspeed questionnaire \cite{bartneck2009measurement}, which evaluates human-likeness based on users' impression of the agent as fake / natural, machinelike / humanlike, unconscious / conscious, and artificial / lifelike (used by \cite{hoegen2019end}\cmt{[31]}, \cite{jeong2019exploring}\cmt{[10]} and \cite{ouchi2019should}\cmt{[59]}). Another method used to evaluate human-likeness is adapted from Holtgraves et al.'s \cite{holtgraves2007perceiving} questionnaire, which asks users questions related to the agent's perceived human-likeness, skillfulness, thoughtfulness, politeness, responsiveness and engagement (used by \cite{diederich2019emulating}\cmt{[25]} and  \cite{gnewuch2018faster}\cmt{[19]}). One study \cite{westerman2019believe}\cmt{[9]} used the Ascend of Man scale \cite{kteily2015ascent} with pictures showing the evolution from ape to man, asking users to choose a depiction that best represents the agent's perceived human-likeness. It is unclear whether these different methods are capturing assessments of similar perception aspects that can be compared with each other. Another example is the evaluation of the perception of agent's empathy. In Diedrech et al.'s study \cite{diederich2019emulating}\cmt{[25]}, empathy is assessed by asking users whether the CA is giving users individual or personal attention. In another study that also studies the perception of empathy \cite{daher2020empathic}\cmt{[58]}, the RoPE Scale \cite{charrier2019rope} is used with questions like "the robot cares about my feelings" or "the robot comforts me when I am upset." These two different evaluations of empathy seem to have different underlying meanings, one assessing the personalization aspect of CAs, while the other is assessing the emotional aspect of CAs.

In addition the problem of consistency in evaluating perceptions, there is the issue of  \textit{composite measures} being used in the assessment of users' perceptions. These composite measures collapse multiple aspects of perception into one measurement, making it impossible to break down perceptions into more granular aspects for analysis. One such example is Ma et al's study \cite{ma2022ask}\cmt{[29]} on the different approaches for CAs to reply to users' uncertain queries. A single UX score is used to evaluate the users' perceptions, which composes of questions on whether the user thinks the CA's response is pleasing / trustworthy / natural / acceptable / shorten the distance between CA and user. The UX score encompasses multiple aspects across several perception categories. While this study has found significant effect for the use of formal language on the user rated UX score, it is not possible to understand how the details of formality is related to the perception categories of interaction (pleasing, acceptable), sociability (shorten the distance between CA and user), and humanness (natural, trustworthy). The humanness questionnaire from Holtgraves et al \cite{holtgraves2007perceiving} has a similar problem, evaluating across perception categories of interaction (responsiveness, engagement), ability (skillfulness), sociability (politeness), and humanness (human-likeness, thoughtfulness).

There has been some effort recently towards unifying the evaluation of conversational agents, such as the work by Finch et al. \cite{finch2020towards} presenting a comprehensive analysis of current evaluation protocols. More research is needed in this area to standardize the assessment of perceptions to make them consistent, granular, and comparable across literature.

\subsubsection{Investigate the Relationship Across Perception Aspects of Agents}

There is evidence in literature that perception aspects of agents have effects on each other. For instance, Moussawi et al. \cite{moussawi2021perceptions}\cmt{[36]} conducted a study to understand the correlations between different perceptions related to users' intention to adopt a conversational agent. Specifically, they found a correlation within the category of perceived ability, where an agent's perceived intelligence is positively correlated to the perceived initial trust of the agent. This study also found that users with higher perceived intelligence of an agent are more likely to attribute higher ratings for perceived human-likeness, as well as for the usability and engagement aspects in the perception category of interaction. Lastly, the authors found that perceived humanness have a positive impact on perceived enjoyment, which lead to higher intention to adopt the CA. This study outlines that the perception aspects identified in this paper are not independent of each other.

Correlations between perception aspects are discussed in a few of the papers we reviewed. One of the studies showed that the CA's perceived personality trait of agreeableness has an influence on the users' perception of credibility \cite{andrews2012system}\cmt{[38]}. Seeger et al's study found a similar correlation, where higher perceived anthropomorphism led to lower loss of trust \cite{seeger2021chatbots}\cmt{[35]}. There are also correlations between aspects found within the same perception category, such as a speech agent that is rated higher in perceived human-likeness was associated with higher likability ratings \cite{zhu2022effects}\cmt{[26]}. Also, within the perception category of social connection, one study found that social distance is positively related to the perceived social attraction \cite{westerman2019believe}\cmt{[9]}.

These correlations demonstrate that some perception aspects have effects on each other, either within the same category or across different categories. While there are limited research into this area, further investigations are needed to understand the relationships between various perception aspects.

\subsubsection{Research Directions for the Effects of Conversation Architecture on Users' Perceptions}

Our synthesized framework (Figure \ref{fig:heatmap-impact}) serves as a foundational understanding on the effect of conversation architecture on the perception of agents. It showcases the density of explored relationships between them, as well as highlighting areas that are under-explored. In order to continue building our knowledge, it is important to investigate further into the effect of contextual factors as well as multiple conversation architecture elements on users' perceptions.

There are a few \textit{under-explored areas} in our synthesized framework. The perception category of agent's ability has the least number of explored connections with conversation architecture compared to other perception categories. Specifically, more studies are needed to understand the effects of social dialog, response delay, humour and elaborateness on users' perceptions of agents' ability. For the perception category of sociability with agent, there is a general lack of explored connections with the conversation architecture category of content style, especially for alignment and elaborateness elements. Lastly, more studies on the effect of dialog strategy for conversation architecture elements of initiative and response delay on the perceptions of agent are needed.

Some studies have discussed how differences in \textit{contextual factors} resulted in variations in the perceptions of agents while using similar conversation architecture elements. One of the factors is users' experience with CAs, as Gnewuch et al. \cite{gnewuch2018faster}\cmt{[19]} found that experienced users perceived the agent with a response delay as lower in social presence because it is seen as inefficient to wait for the CA to respond, but novice users perceived higher social presence conversing with the CAs using response delays because it is more similar to conversations with human partners \cite{gnewuch2018faster}\cmt{[19]}. User characteristics is another factor, as the perceived trustworthiness of a style matching agent depended on users' own conversational style \cite{hoegen2019end}\cmt{[31]}. Some other contextual factors that resulted in differences in perceptions of agent include the purpose of conversation (e.g. transactional vs. social) \cite{jeong2019exploring}\cmt{[10]}, anonymity of the conversation \cite{lee2020hear}\cmt{[23]}, and the sensitivity of information discussed in the interaction \cite{cox2022does}\cmt{[27]}. A comprehensive review to identify these contextual factors as well as to understand their effects on the perceptions of agents across various conversation architecture elements would be useful to tailor CA design for specific situations.

As we gain a better understanding about the effects of a single conversation architecture element on the perceptions of agents, we can extend the research to using \textit{multiple conversation architecture elements} in an agent. Several papers in our reviewed corpus incorporated composite elements in an agent, such as the design of an anthropomorphized chatbot using elements such as affective language, emoticons, response delays to assess users' perceptions compared to a non-anthropomorphized chatbot \cite{seeger2021chatbots}\cmt{[35]}. In addition to explore the combined effects of conversation architecture elements on users' perceptions, it would also be interesting to understand the relative importance of each element on perceptions. Some studies analyzed the effect of modifying conversation architecture elements individually, as well as their combined effect on user's perceptions (e.g. \cite{habler2019effects}\cmt{[63]}\cite{lubold2016effects}\cmt{[86]}\cite{zhu2022effects}\cmt{[26]}). Specifically, Habler et al. \cite{habler2019effects}\cmt{[63]} found that the effect for social dialog is higher than the effect for prosody on the perception of agents.

\subsection{Ethical Considerations}

The designers of conversational agents need to consider ethical implications and potential negative impacts for users. This section discusses three main areas of concerns related to the effect of conversation architecture on the perceptions of agents: gender stereotypes, influencing user's actions and privacy concerns.

For the element of prosody, various studies in our corpus explored the effect of different pitches on the perceptions of agents. Even in studies that are not explicitly analyzing the effect of different gendered voices in an agent, possible stereotypes may still exist in the study. Based on our reviewed corpus, studies found that lower pitches commonly associated with men are considered to be more desirable, authoritative but less friendly \cite{tolmeijer2021female}\cmt{[62]}\cite{jestin2022effects}\cmt{[81]}. For Dubiel et al's study \cite{dubiel2020persuasive}\cmt{[60]}, the agent with lower mean pitch was selected as the more persuasive voice. These results may be demonstrating users' unconscious bias to select a male sounding voice as more persuasive and authoritative over female sounding voices that are commonly associated with higher pitches. While some guidelines recommend designing agents to be androgynous to avoid gender stereotypes \cite{ruane2019conversational}, there are limitations in creating gender-ambiguous voices. Currently there is no defined guidelines on what is perceived as a gender-neutral voice \cite{jestin2022effects}\cmt{[81]}. There is also a lack of voice generators available to generate voices that are perceived as androgynous \cite{tolmeijer2021female}\cmt{[62]}.

Studies have demonstrated that conversation architecture elements can be used to design perceptions of agents to make CAs more persuasive. This opens up the ethical issue of influencing users' attitudes and behaviours through these persuasion techniques. In a study by Chan et al \cite{chan2021kinvoices}\cmt{[74]}, they found that CAs using kin's voices are perceived as more credible and likeable, with a higher perceived social presence with the agent. These perceptions contributes to the agent being more engaging and persuasive, therefore people are more likely to comply with its requests. Andrew et al \cite{andrews2012system}\cmt{[38]} found that tailoring the personality of the CA to users will positively impact an agent's persuasiveness. These persuasion techniques can be beneficial to help users achieve their goals, but can also be used for harmful actions, such as trying to get users to believe in false information.

Another key area of concern is privacy. Given the natural language format of conversational agents, users may be disclosing more sensitive and personal information than needed for the interaction. In relationship to conversation architecture, using elements like self-disclosure and persuasive voice prosody settings could result in users perceiving higher trust with the agent, leading them to disclose more sensitive information  \cite{lee2020hear}\cmt{[23]}\cite{dubiel2020persuasive}\cmt{[60]}. This can expose users to attacks, such as CAs using voice impersonation to ask for personal information for malicious intents \cite{chan2021kinvoices}\cmt{[74]}. Designing for perceptions of agents requires careful consideration of privacy issues including the sensitivity of the data, who has access to it, and how to protect against nefarious users.

\subsection{Limitations}

Our systematic literature review was limited to papers published in the ACM Digital Library between 2010 and 2022. We may have missed literature published outside this time period, as well as in other libraries. Also, most of the studies in our corpus are based on lab experiments using short interactions with users. The generalizability of these findings need to be verified through longer term engagements with conversational agents deployed in real world situations. Lastly, research without empirical studies on the perception of agents are excluded based on our selection criteria. We may have missed some influential findings in these papers. %To better understand the relationships between conversation architecture elements and the perceptions of agents, we plan to conduct future reviews in literature and user studies to understand their real-world impacts.

### 2023-02-21 sections/6-conclusion.tex
restructured manuscript

%% CONCLUSION SECTION %%

\section{Conclusion}

In this paper, we discussed the results of a systematic review of existing literature published in the ACM Digital Library on the effect of conversation architecture elements on the perceptions of CAs. Through our synthesis of 57 papers in our corpus, we present a framework outlining the relationships between elements of agents’ conversation architecture (dialog strategy, content affectiveness, content style and speech format) and aspects of users’ perception (interaction, ability, sociability and humanness). During our analysis, we found the need for consistent protocols in evaluating perceptions of agents, as measurements are inconsistent across studies. Further research is needed to investigate the under-explored areas in the framework, the relationship across perception aspects, the influence of contextual factors, and the effect of composite conversation architecture elements on users' perceptions. While our research contribute to the design conversation architecture to orchestrate specific perceptions of agent, we urge designers to incorporate ethical perspectives into their design considerations.

### 2023-02-21 tables/tbl-conversation_architecture.tex
restructured manuscript

%% CONVERSATION ARCHITECTURE ELEMENTS TABLE %%

\begin{table*}[h]
\resizebox{\textwidth}{!}{
\renewcommand*{\arraystretch}{1.4}
\begin{tabular}{@{}p{0.17\textwidth} | p{0.14\textwidth} | p{0.25\textwidth} | >{\centering}p{0.09\textwidth} | p{0.34\textwidth} @{}}
\Xhline{1.2pt}
\multicolumn{2}{l|}{\textbf{Conversation Architecture Elements}} & \textbf{Examples} & \textbf{No. Papers} & \textbf{Papers}
\\ \Xhline{1.2pt}
\multirow{3}{*}{Dialog Strategy} & Social Dialog & social talk, self-disclosure  & 7
& \cite{andrews2012system}\cmt{[38]}\cite{lee2020hear}\cmt{[23]}\cite{lubold2016effects}\cmt{[86]}\cite{moilanen2022measuring}\cmt{[82]}\cite{roy2021users}\cmt{[71]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}
\\ \cline{2-5}

& Initiative & proactive dialogue, conversation \newline repair & 4
& \cite{ashktorab2019resilient}\cmt{[88]}\cite{cuadra2021my}\cmt{[67]}\cite{kraus2020effects}\cmt{[64]}\cite{xiao2021let}\cmt{[73]}
\\ \cline{2-5}

& Response Delay & response delay, typing indicator & 4
& \cite{gnewuch2018faster}\cmt{[19]}\cite{gnewuch2018chatbot}\cmt{[21]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{seeger2021chatbots}\cmt{[35]}
\\ \Xhline{1.2pt}

\multirow{2}{*}{Content Affectiveness} & Affective Language & emotional expressions, sentiment-adaptive responses & 11
& \cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{lee2019s}\cmt{[55]}\cite{lubis2019positive}\cmt{[43]}\cite{moilanen2022measuring}\cmt{[82]}\cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2022user}\cmt{[75]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}
\\ \cline{2-5}

& Humour & humorous content, jokes & 6
& \cite{ceha2021can}\cmt{[57]}\cite{go2021conversational}\cmt{[80]}\cite{khooshabeh2011does}\cmt{[37]}\cite{miyamoto2017improving}\cmt{[46]}\cite{niewiadomski2013laugh}\cmt{[85]}\cite{volkel2021manipulating}\cmt{[68]}
\\ \Xhline{1.2pt}

\multirow{3}{*}{Content Style} & Formality & formal vs. casual, honorific \newline expressions & 9
& \cite{cox2022does}\cmt{[27]}\cite{elsholz2019exploring}\cmt{[61]}\cite{habler2019effects}\cmt{[63]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2019comparing}\cmt{[89]}\cite{ma2022ask}\cmt{[29]}\cite{moilanen2022measuring}\cmt{[82]}\cite{ouchi2019should}\cmt{[59]}\cite{volkel2022user}\cmt{[75]}
\\ \cline{2-5}

& Alignment & content matching, lexical \newline alignment, agreeableness & 7
& \cite{healey2013relating}\cmt{[39]}\cite{hoegen2019end}\cmt{[31]}\cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}\cite{spillner2021talk}\cmt{[18]}\cite{volkel2021examining}\cmt{[69]}\cite{volkel2021manipulating}\cmt{[68]}
\\ \cline{2-5}

& Elaborateness & elaborate, concise, sentence \newline structure & 6
& \cite{haas2022keep}\cmt{[78]}\cite{miehle2018exploring}\cmt{[51]}\cite{moilanen2022measuring}\cmt{[82]}\cite{roy2021users}\cmt{[71]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}
\\ \Xhline{1.2pt}

\multirow{3}{*}{Speech Format} & Prosody & pitch, intonation, speech rate, \newline spoken accent & 12
& \cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{feijoo2021effects}\cmt{[70]}\cite{habler2019effects}\cmt{[63]}\cite{hu2021enhancing}\cmt{[56]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2020can}\cmt{[24]}\cite{lubold2016effects}\cmt{[86]}\cite{misu2011toward}\cmt{[83]}\cite{tolmeijer2021female}\cmt{[62]}\cite{zhu2022effects}\cmt{[26]}
\\ \cline{2-5}

& Disfluency & fillers, interjections, repetitions, \newline typos & 6
& \cite{ceha2022expressive}\cmt{[77]}\cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}\cite{wester2015artificial}\cmt{[14]}\cite{westerman2019believe}\cmt{[9]}\cite{yang2021effect}\cmt{[72]}
\\ \cline{2-5}

& Text Formatting & capitalization, emoticons & 6
& \cite{fadhil2018effect}\cmt{[52]}\cite{kim2019comparing}\cmt{[89]}\cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2022user}\cmt{[75]}\cite{westerman2019believe}\cmt{[9]}\cite{wilhelm2022keep}\cmt{[28]}
\\ \Xhline{1.2pt}
\end{tabular}%
}
\caption{Conversation architecture elements}
\label{tbl:conversation_architecture}
\end{table*}

### 2023-02-21 tables/tbl-perceptions.tex
restructured manuscript

%% PERCEPTION ASPECTS TABLE %%

\begin{table*}[ht]
\renewcommand*{\arraystretch}{1.4}
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}p{0.17\textwidth} | p{0.12\textwidth} | p{0.20\textwidth} | >{\centering}p{0.09\textwidth} | p{0.42\textwidth} @{}}
%!{\vrule width 1.2pt} 
\Xhline{1.2pt}
\multicolumn{2}{l|}{\textbf{Perception Aspects}} & \textbf{Examples} & \textbf{No. Papers} & \textbf{Papers} 
\\ \Xhline{1.2pt}
\multirow{3}{*}{\parbox{0.17\textwidth}{Perception of \newline Interaction with Agent}}
    & Usability & accuracy, ease of use, \newline efficiency, helpfulness & 23 
    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2022expressive}\cmt{[77]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cuadra2021my}\cmt{[67]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{elsholz2019exploring}\cmt{[61]}\cite{haas2022keep}\cmt{[78]}\cite{habler2019effects}\cmt{[63]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2019comparing}\cmt{[89]}\cite{kim2020can}\cmt{[24]}
    \cite{kraus2020effects}\cmt{[64]}\cite{linnemann2018can}\cmt{[15]}\cite{ma2022ask}\cmt{[29]}\cite{miehle2018exploring}\cmt{[51]}\cite{misu2011toward}\cmt{[83]}\cite{roy2021users}\cmt{[71]}\cite{spillner2021talk}\cmt{[18]}\cite{wilhelm2022keep}\cmt{[28]}
\\ \cline{2-5}
    & Engagement & enjoyment, annoyance, \newline desirable, intention to use  & 28
    & \cite{andrews2012system}\cmt{[38]}\cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cox2022does}\cmt{[27]}\cite{cuadra2021my}\cmt{[67]}\cite{elsholz2019exploring}\cmt{[61]}\cite{fadhil2018effect}\cmt{[52]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{go2021conversational}\cmt{[80]}\cite{healey2013relating}\cmt{[39]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2020can}\cmt{[24]}\cite{kim2019comparing}\cmt{[89]}
    \cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{ma2022ask}\cmt{[29]}\cite{miehle2018exploring}\cmt{[51]}\cite{miyamoto2017improving}\cmt{[46]}\cite{moilanen2022measuring}\cmt{[82]}\cite{roy2021users}\cmt{[71]}\cite{spillner2021talk}\cmt{[18]}\cite{volkel2021examining}\cmt{[69]}\cite{volkel2022user}\cmt{[75]}\cite{xiao2021let}\cmt{[73]}\cite{yang2021effect}\cmt{[72]}\cite{zhu2022effects}\cmt{[26]}    
\\ \cline{2-5}
    & Satisfaction & service satisfaction, quality of interaction & 12
    & \cite{ceha2022expressive}\cmt{[77]}\cite{choi2020nobody}\cmt{[54]}\cite{diederich2019emulating}\cmt{[25]}\cite{elsholz2019exploring}\cmt{[61]}\cite{habler2019effects}\cmt{[63]}\cite{gnewuch2018faster}\cmt{[19]}\cite{hoegen2019end}\cmt{[31]}\cite{hu2022polite}\cmt{[76]}\cite{ma2022ask}\cmt{[29]}\cite{roy2021users}\cmt{[71]}\cite{wilhelm2022keep}\cmt{[28]}\cite{yang2017perceived}\cmt{[44]}
\\ \Xhline{1.2pt} 
\multirow{3}{*}{\parbox{0.16\textwidth}{Perception of Agent's Ability}}
    & Intelligence & knowledgeable, intelligent, expertise & 11
    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cuadra2021my}\cmt{[67]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{feijoo2021effects}\cmt{[70]}\cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}\cite{spillner2021talk}\cmt{[18]}\cite{volkel2022user}\cmt{[75]}\cite{yang2017perceived}\cmt{[44]} 
\\ \cline{2-5}
    & Competence & competent, appropriate & 6 
    & \cite{cox2022does}\cmt{[27]}\cite{kraus2020effects}\cmt{[64]}\cite{jestin2022effects}\cmt{[81]}\cite{lee2019s}\cmt{[55]}\cite{misu2011toward}\cmt{[83]}\cite{westerman2019believe}\cmt{[9]}
\\ \cline{2-5}
    & Trust & credibility, trustworthy, truthfulness, confidence & 15
    & \cite{andrews2012system}\cmt{[38]}\cite{chan2021kinvoices}\cmt{[74]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{fadhil2018effect}\cmt{[52]}\cite{healey2013relating}\cmt{[39]}\cite{hoegen2019end}\cmt{[31]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kraus2020effects}\cmt{[64]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{ma2022ask}\cmt{[29]}\cite{seeger2021chatbots}\cmt{[35]}\cite{tolmeijer2021female}\cmt{[62]}\cite{wilhelm2022keep}\cmt{[28]}    
\\ \Xhline{1.2pt} 
\multirow{3}{*}{\parbox{0.16\textwidth}{Perception of \newline Sociability with Agent}}
    & Conversation Tone & friendly, warm, empathetic, persuasive & 20 
    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cox2022does}\cmt{[27]}\cite{cuadra2021my}\cmt{[67]}\cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{healey2013relating}\cmt{[39]}\cite{hu2021enhancing}\cmt{[56]}\cite{hu2022polite}\cmt{[76]}\cite{jestin2022effects}\cmt{[81]}\cite{khooshabeh2011does}\cmt{[37]}\cite{kim2019comparing}\cmt{[89]}\cite{lee2019s}\cmt{[55]}\cite{miehle2018exploring}\cmt{[51]}
    \cite{moilanen2022measuring}\cmt{[82]}\cite{tolmeijer2021female}\cmt{[62]}\cite{yang2021effect}\cmt{[72]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}
\\ \cline{2-5}
    & Social Presence & connectedness, familiarity, psychological distance & 18
    & \cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cuadra2021my}\cmt{[67]}\cite{diederich2019emulating}\cmt{[25]}\cite{gnewuch2018faster}\cmt{[19]}\cite{gnewuch2018chatbot}\cmt{[21]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{go2021conversational}\cmt{[80]}\cite{khooshabeh2011does}\cmt{[37]}\cite{kim2020can}\cmt{[24]}\cite{lee2019s}\cmt{[55]}\cite{lubis2019positive}\cmt{[43]}\cite{lubold2016effects}\cmt{[86]}
    \cite{ma2022ask}\cmt{[29]}\cite{niewiadomski2013laugh}\cmt{[85]}\cite{westerman2019believe}\cmt{[9]}    
\\ \cline{2-5}
    & Intimacy & intimate, rapport, quality of relationship & 7 
    & \cite{choi2020nobody}\cmt{[54]}\cite{khooshabeh2011does}\cmt{[37]}\cite{kim2020can}\cmt{[24]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{lubold2016effects}\cmt{[86]}\cite{westerman2019believe}\cmt{[9]}
\\ \Xhline{1.2pt}
\multirow{2}{*}{\parbox{0.16\textwidth}{Perception of Agent's Humanness}}
    & Human-likeness & human-like, natural, \newline artificial, machine-like & 20
    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cox2022does}\cmt{[27]}\cite{diederich2019emulating}\cmt{[25]}\cite{gnewuch2018faster}\cmt{[19]}\cite{haas2022keep}\cmt{[78]}\cite{hu2022polite}\cmt{[76]}\cite{jeong2019exploring}\cmt{[10]}\cite{jestin2022effects}\cmt{[81]}\cite{lubis2019positive}\cmt{[43]}\cite{ma2022ask}\cmt{[29]}\cite{misu2011toward}\cmt{[83]}\cite{niewiadomski2013laugh}\cmt{[85]}
    \cite{ouchi2019should}\cmt{[59]}\cite{seeger2021chatbots}\cmt{[35]}\cite{wester2015artificial}\cmt{[14]}\cite{westerman2019believe}\cmt{[9]}\cite{zhu2022effects}\cmt{[26]}    
\\ \cline{2-5}
    & Personality Traits & likeable, kind, witty, funny, creepy & 20
    & \cite{andrews2012system}\cmt{[38]}\cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cuadra2021my}\cmt{[67]}\cite{haas2022keep}\cmt{[78]}\cite{habler2019effects}\cmt{[63]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{huiyang2022improving}\cmt{[17]}\cite{jeong2019exploring}\cmt{[10]}\cite{kim2019comparing}\cmt{[89]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{miehle2018exploring}\cmt{[51]}
    \cite{ouchi2019should}\cmt{[59]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}\cite{wester2015artificial}\cmt{[14]}\cite{zhu2022effects}\cmt{[26]} 
\\ \Xhline{1.2pt}
\end{tabular}%
}
\caption{Perception aspects}
\label{tbl:perceptions}
\end{table*}

### 2023-02-22 sections/1-introduction.tex
Young-Ho edit and fix citations/references

@@
 Conversational agents (CAs), such as Amazon Alexa or Google Assistant, are designed to interact with humans using natural language through voice or text modalities.
-Since these agents interact with users using natural language, conversation architecture — which refers to what a CA says and how it says it — affects how these agents interact with users.
-The effectiveness of these interactions with CAs are strongly dependent on users' perceptions of agents \cite{knijnenburg2016inferring}\cite{seeger2021chatbots}.
+Since these agents communicate in natural language, \textit{conversation architecture}---what and how a CA says---affects users' perceptions of agents and, in turn, the effectiveness of their interactions~\cite{knijnenburg2016inferring, seeger2021chatbots}.
 According to previous research, there is a correlation between CAs' conversation architecture and users' perception of these agents.
 
-While there are various studies on how different conversation architecture elements affects agents' perceptions, there is a paucity of knowledge on the overall coverage and effects of these relationships explored in literature.
-For conversation architecture elements, The use of affective language is commonly explored, with studies finding that conversational agents are perceived as more socially present and emotionally intelligent if they use sentiment-adaptive response based on user's utterances \cite{diederich2019emulating}\cite{yang2017perceived}.
+While various studies investigated how different conversation architecture elements affect agents' perceptions, there is a paucity of knowledge on the overall coverage and effects of these relationships explored in literature.
+For conversation architecture elements, the use of affective language is commonly explored, with studies finding that conversational agents are perceived as more socially present and emotionally intelligent if they use sentiment-adaptive response based on user's utterances~\cite{diederich2019emulating, yang2017perceived}.
 Another commonly explored element is the use of prosody in voice-based agents, such as the use of express prosody contributing to higher perceived enjoyment and intimacy with the agent \cite{kim2020can}.
 However, there is a lack of research to synthesize these findings into an overall framework.
-One of the possible issues is the lack of clear and consistent definitions on the aspects of user's perceptions of agent and conversation architectural elements.
+One of the possible issues is the lack of clear and consistent definitions of the aspects of users' perceptions of agent and conversation architectural elements.
 
-Currently there is no systematic understanding on the elements of conversation architecture that are relevant to perceptions of agents.
-Some papers have started to examine the speech specifics that are being explored in literature, such as Clark et al.
-\cite{clark2019state} capturing different elements of system speech production for voice-based agents and categorizing them based on content, style, and other topics.
+Currently, there is no systematic understanding on the elements of conversation architecture that are relevant to the perceptions of agents.
+Some papers have started to examine the speech specifics explored in literature, such as \citet{clark2019state} capturing different elements of system speech production for voice-based agents and categorizing them based on content, style, and other topics.
 There are also some investigations of conversation architecture elements within the broader field of studying cues that trigger a social reaction of the user towards the CA.
@@
 empathy, humanness) alongside other assessments (e.g.
-physiological data) \cite{clark2019state}\cite{finch2020towards}.
+physiological data) \cite{clark2019state, finch2020towards}.
 Some even categorized the metrics based on the type of method used, including technical measures like system error rate and perception measures like perceived social presence \cite{zheng2022ux}.
@@
 
-To answer these questions, we performed a comprehensive review on existing literature from 2010 to 2022 and synthesized the effect of conversation architecture elements on the perceptions of CAs based on 57 relevant papers (Figure \ref{fig:heatmap-impact}).
-We also grouped the perceptions of agents affected by conversation architecture into four categories and eleven aspects (Table \ref{tab:perceptions}), and grouped the speech variations related to perceptions of agents into four categories and eleven elements (Table \ref{tab:cues}).
+To answer these questions, we performed a comprehensive review on existing literature from 2010 to 2022 and synthesized the effect of conversation architecture elements on the perceptions of CAs based on 57 relevant papers (\autoref{fig:heatmap_identified}).
+We also grouped the perceptions of agents affected by conversation architecture into four categories and eleven aspects (\autoref{tbl:perceptions}), and grouped the speech variations related to perceptions of agents into four categories and eleven elements (\autoref{tbl:conversation_architecture}).
 %Lastly, we coded the explored connections between conversation architecture and perceptions and synthesized their relationships into a framework.

### 2023-02-22 sections/2-related_work.tex
Young-Ho edit and fix citations/references

@@
 When conversing with conversational agents, users tend to use shorter messages with limited vocabulary, adapting to the style of the agent \cite{hill2015real}.
-Also, some studies found that small talk and humour are considered unnecessary or even inauthentic in conversations with CAs, while these elements are important in scaffolding communications with human partners \cite{clark2019makes}\cmt{[1]}\cite{doyle2019mapping}\cmt{[2]}.
-There are also machine-like traits that users preferred in a CA, such as the ability to interact through multimodal media, and a machine's perceived ability to be objective and non-judgemental \cite{doyle2019mapping}\cmt{[2]}\cite{kim2022understanding}\cmt{[3]}.
+Also, some studies found that small talk and humour are considered unnecessary or even inauthentic in conversations with CAs, while these elements are important in scaffolding communications with human partners \cite{clark2019makes, doyle2019mapping}\cmt{[1],[2]}.
+There are also machine-like traits that users preferred in a CA, such as the ability to interact through multimodal media, and a machine's perceived ability to be objective and non-judgemental \cite{doyle2019mapping, kim2022understanding}\cmt{[2],[3]}.
 Given human-agent communications are different from human-human communications, it is important to look specifically at the design of user experiences for conversational agents.
@@
 Several papers have mapped out the current state of research for conversational agents for specific agent types (e.g.
-text-based, voice-based, polyadic) highlighting major trends, topics, methods and evaluating metrics \cite{clark2019state}\cmt{[33]}\cite{rapp2021human}\cmt{[5]}\cite{zheng2022ux}.
+text-based, voice-based, polyadic) highlighting major trends, topics, methods and evaluating metrics \cite{clark2019state, rapp2021human, zheng2022ux}\cmt{[33][5]}.
 Other papers looked at specific dimensions of user experiences or domains of usage, such as Van Pinxteren et al.
@@
 
-Conversation architecture has been demonstrated to play an important role in users' perceptions of agents \cite{knijnenburg2016inferring}\cite{moussawi2021perceptions}\cite{seeger2021chatbots}\cmt{[35]}.
+Conversation architecture has been demonstrated to play an important role in users' perceptions of agents \cite{knijnenburg2016inferring, moussawi2021perceptions, seeger2021chatbots}\cmt{[35]}.
 Yet, little is known about the overall landscape on the how the specifics of speech variations affect these perceptions.

### 2023-02-22 sections/3-method.tex
Young-Ho edit and fix citations/references

@@
 As such, we generalized our search term to capture articles related to conversational agents.
-Based on search terms used in previously published literature reviews \cite{clark2019state}\cite{rapp2021human}, the following keywords are used to search for publications related to conversational user interfaces:
+Based on search terms used in previously published literature reviews \cite{clark2019state, rapp2021human}, the following keywords are used to search for publications related to conversational user interfaces:
 \newline
@@
 We used inductive thematic analysis to group these assessments into codes based on their meanings.
-For example, the code likeability of the agent contains the questionnaire item "this voice agent was likeable" used by \cite{cuadra2021my}\cmt{[67]}, Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed}'s set of questions on likeability used by \cite{linnemann2018can}\cmt{[15]}, and Subjective Assessment of Speech System Interface (SASSI) questionnaire \cite{hone2000towards}\cmt{sassi}'s set of questions on likeability used by \cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}.
+For example, the code likeability of the agent contains the questionnaire item "this voice agent was likeable" used by \cite{cuadra2021my}\cmt{[67]}, Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed}'s set of questions on likeability used by \cite{linnemann2018can}\cmt{[15]}, and Subjective Assessment of Speech System Interface (SASSI) questionnaire \cite{hone2000towards}\cmt{sassi}'s set of questions on likeability used by \cite{chan2021kinvoices, choi2020nobody}\cmt{[74][54]}.
 This step resulted in 83 unique codes.
@@
 For example, the aspect of personality traits of the agent contains measurements such as likeability, funniness, and kindness.
-Lastly, the 11 aspects are grouped into 4 categories: perception of interaction with agent, perception of agent's ability, perception of sociability with agent, and perception of agent's humanness (Table \ref{tbl:perceptions}).
+Lastly, the 11 aspects are grouped into 4 categories: perception of interaction with agent, perception of agent's ability, perception of sociability with agent, and perception of agent's humanness (\autoref{tbl:perceptions}).
 
@@
 We then organized these codes into elements based on similarity, resulting in 12 elements of conversation architecture.
-For example, the element of disfluency contains fillers \cite{jeong2019exploring}\cmt{[10]}\cite{wester2015artificial}\cmt{[14]}, interjections \cite{ceha2022expressive}\cmt{[77]}\cite{hu2021enhancing}\cmt{[56]}, repetitions \cite{yang2021effect}\cmt{[72]} and typos \cite{westerman2019believe}\cmt{[9]}.
-These elements are grouped into 4 categories: dialog strategy, content affectiveness, content style, and speech format (Table \ref{tbl:conversation_architecture}).
+For example, the element of disfluency contains fillers \cite{jeong2019exploring, wester2015artificial}\cmt{[10][14]}, interjections \cite{ceha2022expressive, hu2021enhancing}\cmt{[77][56]}, repetitions \cite{yang2021effect}\cmt{[72]} and typos \cite{westerman2019believe}\cmt{[9]}.
+These elements are grouped into 4 categories: dialog strategy, content affectiveness, content style, and speech format (\autoref{tbl:conversation_architecture}).
 
@@
 Out of the 193 relationships, 10 were relationships based on agents modifying multiple architecture elements (e.g.
-\cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2021manipulating}\cmt{[68]}).
+\cite{seeger2021chatbots, volkel2021manipulating}\cmt{[35][68]}).
 They were not included in the final framework as we could not attribute the perceptions of agents to the underlying core elements.
-Overall, 183 relationships between individual architecture elements and perceptions of agents are incorporated into our synthesized framework, visualized as a heatmap to demonstrate their relationships with each other (Figure \ref{fig:heatmap_identified}).
+Overall, 183 relationships between individual architecture elements and perceptions of agents are incorporated into our synthesized framework, visualized as a heatmap to demonstrate their relationships with each other (\autoref{fig:heatmap_identified}).

### 2023-02-22 sections/4-findings.tex
Young-Ho edit and fix citations/references

@@
 The category of \textbf{dialog strategy} refers to the approach used by a conversational agent to engage in a dialogue with a user, which includes the use of social dialogs, agent-initiated content, and adding delays to responses.
-Specifically, the element of \textit{social dialogue} captures non-task related conversations with the user to build social connection, such as self-disclosure \cite{lee2020hear}\cmt{[23]} and small talk like chitchats \cite{lubold2016effects}\cmt{[86]}\cite{volkel2021manipulating}\cmt{[68]}.
+Specifically, the element of \textit{social dialogue} captures non-task related conversations with the user to build social connection, such as self-disclosure \cite{lee2020hear}\cmt{[23]} and small talk like chitchats \cite{lubold2016effects, volkel2021manipulating}\cmt{[86][68]}.
 The element of \textit{initiative} captures utterances that are initiated by the agent without direct prompts from the user.
-For example, the agent is taking the initiative to proactively repair the conversation with a user \cite{ashktorab2019resilient}\cmt{[88]}\cite{cuadra2021my}\cmt{[67]}, or actively elicit feedback from users \cite{xiao2021let}\cmt{[73]}.
-Lastly, \textit{response delay} refers to the tactic of deliberatively delaying for a certain period of time before an agent responds to users \cite{gnewuch2018faster}\cmt{[19]}\cite{gnewuch2022opposing}\cmt{[20]}.
+For example, the agent is taking the initiative to proactively repair the conversation with a user \cite{ashktorab2019resilient, cuadra2021my}\cmt{[88][67]}, or actively elicit feedback from users \cite{xiao2021let}\cmt{[73]}.
+Lastly, \textit{response delay} refers to the tactic of deliberately delaying for a certain period of time before an agent responds to users \cite{gnewuch2018faster, gnewuch2022opposing}\cmt{[19][20]}.
 It is mainly used in text-based CAs alongside visual displays of typing indicators \cite{gnewuch2018chatbot}\cmt{[21]}.
@@
 \textbf{Content affectiveness} refers to the conversational agent's use of language to convey emotions or to elicit emotions from users.
-The architecture element of \textit{affective language} captures the injection of emotional words or phrases into the agent's utterance, such as affective expressions \cite{seeger2021chatbots}\cmt{[35]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}, sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}, and encouraging words \cite{healey2013relating}\cmt{[39]}.
+The architecture element of \textit{affective language} captures the injection of emotional words or phrases into the agent's utterance, such as affective expressions \cite{seeger2021chatbots, yang2017perceived, zhu2022effects}\cmt{[35][44][26]}, sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}, and encouraging words \cite{healey2013relating}\cmt{[39]}.
 The other element in this category, \textit{humour}, captures an agent's attempt to include jokes in its dialog.
 Several studies in our reviewed corpus have explored the effect of humour on various perceptions of agents (e.g.
-\cite{ceha2021can}\cmt{[57]}\cite{khooshabeh2011does}\cmt{[37]}).
+\cite{ceha2021can, khooshabeh2011does}\cmt{[57][37]}).
 
@@
 casual, such as using honorific expressions to address users \cite{ouchi2019should}\cmt{[59]}.
-\textit{Alignment} captures the degree that the agent aligns its utterances to the users, such as lexical alignment on the content and structural of the sentences \cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}, as well as referring and agreeing with users' utterances \cite{volkel2021examining}\cmt{[69]}.
+\textit{Alignment} captures the degree that the agent aligns its utterances to the users, such as lexical alignment on the content and structural of the sentences \cite{huiyang2022improving, linnemann2018can}\cmt{[17][15]}, as well as referring and agreeing with users' utterances \cite{volkel2021examining}\cmt{[69]}.
 Lastly, the element of \textit{elaborateness} captures the sentence complexity and length of agents' utterances.
@@
 Lastly, the category of \textbf{speech format} captures the non-verbal component of a conversational agent's utterances for both text and voice modalities. \textit{Disfluency} captures 
-the use of non-lexical utterances like filler words ("um, uh") \cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}, or repetition of words within a sentence \cite{yang2021effect}\cmt{[72]}.
+the use of non-lexical utterances like filler words ("um, uh") \cite{hu2021enhancing, jeong2019exploring}\cmt{[56][10]}, or repetition of words within a sentence \cite{yang2021effect}\cmt{[72]}.
 It also includes the format of using typos \cite{westerman2019believe}\cmt{[9]} for text-based agents.
-For voice-based agents specifically, the element of \textit{prosody} encompasses vocal qualities like pitch \cite{habler2019effects}\cmt{[63]}\cite{jestin2022effects}\cmt{[81]}, speech rate \cite{choi2020nobody}\cmt{[54]}, and spoken accent \cite{feijoo2021effects}\cmt{[70]}.
-For text-based CAs, the \textit{text formatting} element includes different formats agents uses to present information to users, such as using capitalization \cite{westerman2019believe}\cmt{[9]} or emoticons \cite{kim2019comparing}\cmt{[89]}\cite{wilhelm2022keep}\cmt{[28]}.
+For voice-based agents specifically, the element of \textit{prosody} encompasses vocal qualities like pitch \cite{habler2019effects, jestin2022effects}\cmt{[63][81]}, speech rate \cite{choi2020nobody}\cmt{[54]}, and spoken accent \cite{feijoo2021effects}\cmt{[70]}.
+For text-based CAs, the \textit{text formatting} element includes different formats agents uses to present information to users, such as using capitalization \cite{westerman2019believe}\cmt{[9]} or emoticons \cite{kim2019comparing, wilhelm2022keep}\cmt{[89][28]}.
 
@@
 However, there are less studies exploring the effect of agent initiated content and response delay on the perception of agents.
-Specifically for the element of initiative under dialog strategy category, there is literature on conversation repairs \cite{komatani2010online}\cite{reinkemeier2022repair} and agent proactively sharing content with users \cite{dubiel2019inquisitive}\cite{zargham2022understanding}, but many of them did not not include assessments of perceptions of the CA.
+Specifically for the element of initiative under dialog strategy category, there is literature on conversation repairs \cite{komatani2010online, reinkemeier2022repair} and agent proactively sharing content with users \cite{dubiel2019inquisitive, zargham2022understanding}, but many of them did not not include assessments of perceptions of the CA.
 This may be due to the fact that the usage of agent-initiated content is relatively new, as CA interactions have historically been driven by users.
@@
 
-There are 183 identified relationships between perceptions of agents and conversation architecture out of the 265 explored connections that are included in our synthesized framework (Figure \ref{fig:heatmap_identified}).
+There are 183 identified relationships between perceptions of agents and conversation architecture out of the 265 explored connections that are included in our synthesized framework (\autoref{fig:heatmap_identified}).
 To compare the number of identified relationships vs.
-the explored connections in literature, Figure \ref{fig:heatmap_coverage} shows a side-by-side comparison between the two.
+the explored connections in literature, \autoref{fig:heatmap_coverage} shows a side-by-side comparison between the two.
 The detailed analysis on the differences between explored and identified relationships are discussed in the subsections below.
@@
 Several papers that assessed user satisfactions were conversation agents within the transaction context, especially within the customer service domain (e.g.
-\cite{diederich2019emulating}\cmt{[25]}\cite{elsholz2019exploring}\cmt{[61]}\cite{gnewuch2018faster}\cmt{[19]}).
+\cite{diederich2019emulating, elsholz2019exploring, gnewuch2018faster}\cmt{[25][61][19]}).
 
 The category of conversation architecture elements with the most identified relationships to perceptions of interaction is content style.
-Specifically for the element of \textit{elaborateness}, users found the use of full sentences more useful than keyword only \cite{haas2022keep}\cmt{[78]}\cite{roy2021users}\cmt{[71]}.
+Specifically for the element of \textit{elaborateness}, users found the use of full sentences more useful than keyword only \cite{haas2022keep, roy2021users}\cmt{[78][71]}.
 Otherwise, the effect of an agent's elaborateness on user's perception of interaction depends on the user's preference \cite{miehle2018exploring}\cmt{[51]}, as well as the topic of discussion \cite{haas2022keep}\cmt{[78]}.
@@
 The element with the most identified relationships is \textit{prosody}.
-For example, studies found that a CA's expressiveness in vocal cues increased participants' engagement ratings \cite{zhu2022effects}\cmt{[26]}, and different pitches of voice affect users' perception of engagement and usability \cite{chan2021kinvoices}\cmt{[74]}\cite{habler2019effects}\cmt{[63]}.
+For example, studies found that a CA's expressiveness in vocal cues increased participants' engagement ratings \cite{zhu2022effects}\cmt{[26]}, and different pitches of voice affect users' perception of engagement and usability \cite{chan2021kinvoices, habler2019effects}\cmt{[74][63]}.
 
@@
 \cite{cuadra2021my}\cmt{[67]}).
-Also, some studies have discovered conflicting effects between different perception aspects of interaction for CAs using \textit{social dialog}, as users enjoyed the conversation using social talk \cite{lee2020hear}\cmt{[23]}\cite{roy2021users}\cmt{[71]}, but perceived the CA as less efficient \cite{roy2021users}\cmt{[71]}.
+Also, some studies have discovered conflicting effects between different perception aspects of interaction for CAs using \textit{social dialog}, as users enjoyed the conversation using social talk \cite{lee2020hear, roy2021users}\cmt{[23][71]}, but perceived the CA as less efficient \cite{roy2021users}\cmt{[71]}.
 
@@
 Also, the style of speech used by an agent affects the perception of appropriateness of tone, which is an aspect of the perceived competence of an agent \cite{misu2011toward}\cmt{[83]}.
-Different content styles of \textit{formality} also impacts the perceived competence of an agent \cite{cox2022does}\cmt{[27]}\cite{jestin2022effects}\cmt{[81]}.
-Specifically related to perceived credibility of an agent, being \textit{lexically aligned} with the user resulted improved the rating of trustworthiness of an agent \cite{hoegen2019end}\cmt{[31]}\cite{linnemann2018can}\cmt{[15]}.
+Different content styles of \textit{formality} also impacts the perceived competence of an agent \cite{cox2022does, jestin2022effects}\cmt{[27][81]}.
+Specifically related to perceived credibility of an agent, being \textit{lexically aligned} with the user resulted improved the rating of trustworthiness of an agent \cite{hoegen2019end, linnemann2018can}\cmt{[31][15]}.
 There were mixed results on the use of emoticons within the \textit{text formatting} element.
@@
 There are some mixed results for voice-based CAs, as 12 out of the 28 connections did not find any significant results.
-Drilling down to the specific elements, we noticed that the use of \textit{alignment} in voice-based agents did not effect the perception of sociability with agent \cite{healey2013relating}\cmt{[39]}\cite{linnemann2018can}\cmt{[15]}.
+Drilling down to the specific elements, we noticed that the use of \textit{alignment} in voice-based agents did not effect the perception of sociability with agent \cite{healey2013relating, linnemann2018can}\cmt{[39][15]}.
 We didn't have data on text-based agents' perceived social connections with users to compare with voice-based agents, as the studies using alignment and text modality in our corpus did not assess this aspect category of perception.
@@
 
-Looking at the different categories of conversation architecture elements, the heatmap (Figure \ref{fig:heatmap-impact} shows that there are not many relationships in content style category that are related to the perceived sociability with CAs in general, with most of the discovered effects concentrated at the intersection of \textit{formality} and conversation tone.
-Studies have found that CAs using casual style of conversation are perceived as warm, empathetic and friendly \cite{jestin2022effects}\cmt{[81]}\cite{kim2019comparing}\cmt{[89]}, while CAs using formal style of conversation are perceived as polite but lacks empathy \cite{cox2022does}\cmt{[27]}.
+Looking at the different categories of conversation architecture elements, the heatmap (\autoref{fig:heatmap_identified}) shows that there are not many relationships in content style category that are related to the perceived sociability with CAs in general, with most of the discovered effects concentrated at the intersection of \textit{formality} and conversation tone.
+Studies have found that CAs using casual style of conversation are perceived as warm, empathetic and friendly \cite{jestin2022effects, kim2019comparing}\cmt{[81][89]}, while CAs using formal style of conversation are perceived as polite but lacks empathy \cite{cox2022does}\cmt{[27]}.
 The rest of the architecture elements and perception aspects of sociability are minimally explored in literature, which indicates the need for more research in this area.
@@
 There are a few specific conversation architecture elements that had more identified relationships with perceptions of sociability with agent.
-Specifically, CAs using of \textit{affective language} were perceived to be more empathetic \cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{yang2017perceived}\cmt{[44]} and emotionally expressive \cite{zhu2022effects}\cmt{[26]}, as well as being more emotional connected with their users \cite{lee2019s}\cmt{[55]}\cite{lubis2019positive}\cmt{[43]}.
+Specifically, CAs using of \textit{affective language} were perceived to be more empathetic \cite{daher2020empathic, diederich2019emulating, yang2017perceived}\cmt{[58][25][44]} and emotionally expressive \cite{zhu2022effects}\cmt{[26]}, as well as being more emotional connected with their users \cite{lee2019s, lubis2019positive}\cmt{[55][43]}.
 Also, different variations of a voice-based CA's \textit{prosody} have effects on the perceived sociability with agent, such as an agent using expressive prosody is assessed as more intimate and more similar with the user \cite{kim2020can}\cmt{[24]}.
@@
 \cite{clark2019makes} found that humour is an important conversational characteristic for human-human interactions, but viewed as a novelty feature for human-agent conversations.
-However, in our review we found that humor has effects on human-agent relationships, as humorous agents are rated as more friendly, intimate, and similar by users compared to non-humorous agents \cite{go2021conversational}\cmt{[80]}\cite{khooshabeh2011does}\cmt{[37]}.
+However, in our review we found that humor has effects on human-agent relationships, as humorous agents are rated as more friendly, intimate, and similar by users compared to non-humorous agents \cite{go2021conversational, khooshabeh2011does}\cmt{[80][37]}.
 
@@
 There are a few notable conversation architecture elements related to the perceived humanness of conversational agents.
-The use of \textit{prosody} such as varying pitch, intonation and speech rate has more identified relationships with the perceived personality traits of an agent as compared to the perceived human-likeness, especially on the aspect of likeability \cite{choi2020nobody}\cmt{[54]}\cite{jestin2022effects}\cmt{[81]}\cite{misu2011toward}\cmt{[83]}.
+The use of \textit{prosody} such as varying pitch, intonation and speech rate has more identified relationships with the perceived personality traits of an agent as compared to the perceived human-likeness, especially on the aspect of likeability \cite{choi2020nobody, jestin2022effects, misu2011toward}\cmt{[54][81][83]}.
 For the architecture elements of \textit{disfluency}, the type of impact on the perception of humanness depended on the context of the conversation.
-Studies have found that participants perceived the filler-condition agent as more likeable in the social-oriented situation, but did not find the same effect in task-oriented situations \cite{jeong2019exploring}\cmt{[10]}\cite{wester2015artificial}\cmt{[14]}.
-The use of \textit{alignment} in an agent had a number of identified relationships with the perception of personality traits, with some studies finding CAs that are lexically aligned with a user are more likeable \cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}.
+Studies have found that participants perceived the filler-condition agent as more likeable in the social-oriented situation, but did not find the same effect in task-oriented situations \cite{jeong2019exploring, wester2015artificial}\cmt{[10][14]}.
+The use of \textit{alignment} in an agent had a number of identified relationships with the perception of personality traits, with some studies finding CAs that are lexically aligned with a user are more likeable \cite{huiyang2022improving, linnemann2018can}\cmt{[17][15]}.

### 2023-02-22 sections/5-discussion.tex
Young-Ho edit and fix citations/references

@@
 Some studies analyzed the effect of modifying conversation architecture elements individually, as well as their combined effect on user's perceptions (e.g.
-\cite{habler2019effects}\cmt{[63]}\cite{lubold2016effects}\cmt{[86]}\cite{zhu2022effects}\cmt{[26]}).
+\cite{habler2019effects, lubold2016effects, zhu2022effects}\cmt{[63][86][26]}).
 Specifically, Habler et al.
@@
 Even in studies that are not explicitly analyzing the effect of different gendered voices in an agent, possible stereotypes may still exist in the study.
-Based on our reviewed corpus, studies found that lower pitches commonly associated with men are considered to be more desirable, authoritative but less friendly \cite{tolmeijer2021female}\cmt{[62]}\cite{jestin2022effects}\cmt{[81]}.
+Based on our reviewed corpus, studies found that lower pitches commonly associated with men are considered to be more desirable, authoritative but less friendly \cite{jestin2022effects, tolmeijer2021female}\cmt{[81][62]}.
 For Dubiel et al's study \cite{dubiel2020persuasive}\cmt{[60]}, the agent with lower mean pitch was selected as the more persuasive voice.
@@
 Given the natural language format of conversational agents, users may be disclosing more sensitive and personal information than needed for the interaction.
-In relationship to conversation architecture, using elements like self-disclosure and persuasive voice prosody settings could result in users perceiving higher trust with the agent, leading them to disclose more sensitive information  \cite{lee2020hear}\cmt{[23]}\cite{dubiel2020persuasive}\cmt{[60]}.
+In relationship to conversation architecture, using elements like self-disclosure and persuasive voice prosody settings could result in users perceiving higher trust with the agent, leading them to disclose more sensitive information  \cite{dubiel2020persuasive, lee2020hear}\cmt{[60][23]}.
 This can expose users to attacks, such as CAs using voice impersonation to ask for personal information for malicious intents \cite{chan2021kinvoices}\cmt{[74]}.

### 2023-02-23 figures/fig-heatmap_coverage.tex
update introduction & related work; descriptions for figures

@@
   \includegraphics[width=\textwidth]{figures/fig-heatmap_coverage.pdf}
-  \caption{Heatmap of literature for perception of conversational agents for each type of conversational architecture element}
+  \caption{Comparison between identified relationships and explored connections in literature}
+  \Description{This figure shows a side by side comparison between the 183 identified relationships and the 265 explored connections in literature for conversation architecture elements and perceptions of agents.
+The visuals are shown as two heatmaps, with darker shades depicting higher number of relationships.
+The numbers within each cell at the interaction of a specific conversation architecture element and perception aspect outlines the number of relationships found in the reviewed corpus.}
   \label{fig:heatmap_coverage}

### 2023-02-23 figures/fig-heatmap_identified.tex
restructured manuscript
update introduction & related work; descriptions for figures

--- 2023-02-21 figures/fig-heatmap_coverage.tex
@@
-%% Side by side comparison between coverage and identified relationships
+%% Heatmap of the identified relationships between perceptions & conversation architecture
 
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/fig-heatmap_coverage.pdf}
-  \caption{Heatmap of literature for perception of conversational agents for each type of conversational architecture element}
-  \label{fig:heatmap_coverage}
+  \includegraphics[width=\textwidth]{figures/fig-heatmap_identified.pdf}
+  \caption{Synthesized framework on the identified relationship between perception of agents and conversation architecture elements}
+  \Description{This figure shows a heatmap the 183 identified relationships between conversation architecture elements and perceptions of agents.
+Each speech element is listed down the rows of the heatmap, grouped by the four categories dialog strategy, content affectiveness, content style, and speech format.
+Each perception aspect is listed across the columns of the table, grouped by the four categories perception of interaction with agent, perception of agent's ability, perception of sociability with agent, and perception of agent's humanness.
+Each cell has a different shade of colour, with the darker shades depicting higher number of relationships, and the lighter shades depicting smaller number of relationships.}
+  \label{fig:heatmap_identified}
 \end{figure*}

### 2023-02-23 figures/fig-prisma.tex
update introduction & related work; descriptions for figures

@@
   \includegraphics[width=1\columnwidth]{figures/fig-prisma.pdf}
-  \caption{Literature search using PRISMA guidelines}
+  \caption{Literature search process}
+  \Description{This figure shows the literature search process, starting with automated databases search yielding 2901 publications.
+Screening the titles and abstracts of the papers based selection criteria resulted in 221 papers.
+Next, full article reviews filtered the list down to 49 papers.
+An additional search identified 8 more papers, for a total of 57 papers included in our reviewed corpus.}
   \label{fig:prisma}

### 2023-02-23 sections/1-introduction.tex
update introduction & related work; descriptions for figures

@@
 Conversational agents (CAs), such as Amazon Alexa or Google Assistant, are designed to interact with humans using natural language through voice or text modalities.
-Since these agents communicate in natural language, \textit{conversation architecture}---what and how a CA says---affects users' perceptions of agents and, in turn, the effectiveness of their interactions~\cite{knijnenburg2016inferring, seeger2021chatbots}.
+Since these agents communicate in natural language, \textit{conversation architecture}---what and how a CA says---affects users' perceptions of agents and, in turn, the effectiveness of their interactions in achieving users' goals \cite{knijnenburg2016inferring, seeger2021chatbots}.
 According to previous research, there is a correlation between CAs' conversation architecture and users' perception of these agents.
 
-While various studies investigated how different conversation architecture elements affect agents' perceptions, there is a paucity of knowledge on the overall coverage and effects of these relationships explored in literature.
+While various studies investigated how different speech elements affect agents' perceptions, there is a paucity of knowledge on the overall coverage and effects of these relationships explored in literature.
+One reason for this disparity is the lack of clear and consistent definitions of the aspects of users' perceptions of agent and conversation architectural elements.
+Some papers have discussed the speech specifics of agents as part of  a broader analysis on the state of research \cite{clark2019state} or social cues \cite{feine2019taxonomy}, but there is no comprehensive research specifically for conversation architecture elements that are relevant to user perceptions.
+Similarly for user perceptions, while there some research exploring the perceptions of agents as part of understanding the user experiences \cite{clark2019state, finch2020towards} or social cues \cite{feine2019taxonomy} of CAs, there is no exhaustive research specifically for perceptions of agents that are affected by conversation architecture elements.
+
+%While various studies investigated how different conversation architecture elements affect agents' perceptions, there is a paucity of knowledge on the overall coverage and effects of these relationships explored in literature.
 For conversation architecture elements, the use of affective language is commonly explored, with studies finding that conversational agents are perceived as more socially present and emotionally intelligent if they use sentiment-adaptive response based on user's utterances~\cite{diederich2019emulating, yang2017perceived}.
@@
 
-Currently, there is no systematic understanding on the elements of conversation architecture that are relevant to the perceptions of agents.
+%Currently, there is no systematic understanding on the elements of conversation architecture that are relevant to the perceptions of agents.
 Some papers have started to examine the speech specifics explored in literature, such as \citet{clark2019state} capturing different elements of system speech production for voice-based agents and categorizing them based on content, style, and other topics.
@@
 
-Related to user perceptions, there is also no systematic understanding on the perceptions of agents affected by speech variations.
+%Related to user perceptions, there is also no systematic understanding on the perceptions of agents affected by speech variations.
 Some research discussed the perceptions of agents as part of the broader scope of user experiences of CAs.
@@
 
-These research gaps discussed above: the paucity of knowledge on synthesizing the effect of speech specifics on perceptions of CAs as well as the lack of systematic understanding on the elements of conversation architecture and perceptions of agents motivated us to the goal of how to design conversation architecture in order to orchestrate perceptions of conversational agents.
+These research gaps related to the paucity of knowledge on synthesizing the effect of speech specifics on perceptions of CAs as well as the lack of systematic understanding on the elements of conversation architecture and perceptions of agents motivated us to the goal of how to design conversation architecture in order to orchestrate perceptions of conversational agents.
 First, we want to understand \textbf{(RQ1) what perception aspects of agents are being explored in relation to the effects of conversation architecture elements}.
@@
 We also grouped the perceptions of agents affected by conversation architecture into four categories and eleven aspects (\autoref{tbl:perceptions}), and grouped the speech variations related to perceptions of agents into four categories and eleven elements (\autoref{tbl:conversation_architecture}).
+We found that perceptions of interaction with CAs (usability, engagement, satisfaction) have the most number of explored and identified relationships with speech variations, while the perceptions of CAs' ability (intelligence, competence, credibility) have the least number of explored and identified relationships.
+Also, the conversation architecture elements of response delay and agent initiated dialog related perceptions of CAs are under-explored in literature.
 %Lastly, we coded the explored connections between conversation architecture and perceptions and synthesized their relationships into a framework.

### 2023-02-23 sections/2-related_work.tex
update introduction & related work; descriptions for figures

@@
 
-There have been numerous studies on the user experiences for conversational agents, and some attempts to synthesize findings across literature.
-Several papers have mapped out the current state of research for conversational agents for specific agent types (e.g.
+There are a number of studies investigating factors affecting user experiences for conversational agents, such as the relationship between conversation architecture elements and agents' perceptions.
+For instance, the use of affective language is commonly explored, with studies finding that conversational agents are perceived as more socially present and emotionally intelligent if they use sentiment-adaptive response based on user's utterances \cite{diederich2019emulating, yang2017perceived}.
+Another commonly explored element is the use of prosody in voice-based agents, such as the use of express prosody contributing to higher perceived enjoyment and intimacy with the agent \cite{kim2020can}.
+However, there is a paucity of research to synthesize these findings on user experiences with agents across literature.
+
+In recent years, several papers have synthesized the current state of research for conversational agents for specific agent types (e.g.
 text-based, voice-based, polyadic) highlighting major trends, topics, methods and evaluating metrics \cite{clark2019state, rapp2021human, zheng2022ux}\cmt{[33][5]}.
-Other papers looked at specific dimensions of user experiences or domains of usage, such as Van Pinxteren et al.
-\cite{van2020human} examining the effects of agents' human-like communicative behaviours on their relationships with users, and Kocaballi et al.
-\cite{kocaballi2022design} exploring the challenges and opportunities of CAs in healthcare.
-There are also publications aimed to unify concepts used in the research for CA user experiences, for instance Feine et al.
-\cite{feine2019taxonomy} creating a taxonomy of social cues, and Finch et al.
-\cite{finch2020towards} analyzing evaluation protocols for dialogue systems.
+Other papers looked at specific dimensions of user experiences or domains of usage, such as \citet{van2020human} examining the effects of agents' human-like communicative behaviours on their relationships with users, and \citet{kocaballi2022design} exploring the challenges and opportunities of CAs in healthcare.
+There are also publications aimed to unify concepts used in the research for CA user experiences, for instance \citet{feine2019taxonomy} creating a taxonomy of social cues, and \citet{finch2020towards} analyzing evaluation protocols for dialogue systems.
 To the best of our knowledge, there is currently no synthesis on the speech specifics of CAs, the perceptions of agents, or the relationship between them.
@@
 Given the paucity of research in this area, this paper aims to synthesize the identified relationships between conversation architecture elements and users' perceptions of agents.
+
+%Currently, there is no systematic understanding on the elements of conversation architecture that are relevant to the perceptions of agents.
+Some papers have started to examine the speech specifics explored in literature, such as \citet{clark2019state} capturing different elements of system speech production for voice-based agents and categorizing them based on content, style, and other topics.
+There are also some investigations of conversation architecture elements within the broader field of studying cues that trigger a social reaction of the user towards the CA.
+Feine et al's \cite{feine2019taxonomy} paper laid the foundation to create a consistent taxonomy for these social cues.
+However, there is no comprehensive research specifically for conversation architecture elements that are relevant to user perceptions.
+
+%Related to user perceptions, there is also no systematic understanding on the perceptions of agents affected by speech variations.
+Some research discussed the perceptions of agents as part of the broader scope of user experiences of CAs.
+These publications have gathered UX dimensions used to evaluate conversational agents, which include the perceptions of agents (e.g.
+empathy, humanness) alongside other assessments (e.g.
+physiological data) \cite{clark2019state, finch2020towards}.
+Some even categorized the metrics based on the type of method used, including technical measures like system error rate and perception measures like perceived social presence \cite{zheng2022ux}.
+However, these studies are assessing the general field of UX measurements and not specifically on the perceptions of agents, and do not analyze the effects of conversation architecture on these perceptions.
 

### 2023-02-23 sections/3-method.tex
update introduction & related work; descriptions for figures

@@
 We screened the titles and abstracts of the papers based on the selection criteria above, resulting in 221 papers.
-The fully body of these papers are then reviewed, selecting papers that met the criteria.
+The fully body of these papers are then reviewed, selecting 49 papers that met the criteria.
 A search for additional literature was also performed to supplement the corpus, adding 8 more papers to the selection.
-In total, we identified 57 relevant articles for analysis (see Figure \ref{fig:prisma}).
+In total, we identified 57 relevant articles for analysis (see \autoref{fig:prisma}).
 
@@
 The papers reviewed (n=57) were published between May 2011 and November 2022.
-More than 75\% of the papers were published in or after 2019, with a slight trend upwards over the years (see Figure \ref{fig:paper}).
+More than 75\% of the papers were published in or after 2019, with a slight trend upwards over the years (see \autoref{fig:paper}).
 The vast majority of the papers in our corpus were published in conference proceedings (n=50), with the remainder papers published in journals.

### 2023-02-23 sections/4-findings.tex
update introduction & related work; descriptions for figures

@@
 
-As shown in Table \ref{tbl:perceptions}, there are four categories defined for the perceptions of conversational agents covering 11 different aspects of perception.
+As shown in \autoref{tbl:perceptions}, there are four categories defined for the perceptions of conversational agents covering 11 different aspects of perception.
 The details of each category and aspect are discussed below.
@@
 
-As shown in Table \ref{tbl:conversation_architecture}, there are four categories defined for conversation architecture across 12 different elements.
+As shown in \autoref{tbl:conversation_architecture}, there are four categories defined for conversation architecture across 12 different elements.
 The details of each category and element are discussed below.

### 2023-02-23 sections/5-discussion.tex
update introduction & related work; descriptions for figures

@@
 
-Our synthesized framework (Figure \ref{fig:heatmap-impact}) serves as a foundational understanding on the effect of conversation architecture on the perception of agents.
+Our synthesized framework (\autoref{fig:heatmap_identified}) lays the foundation in understanding the effect of conversation architecture on the perception of agents.
 It showcases the density of explored relationships between them, as well as highlighting areas that are under-explored.

### 2023-02-23 tables/tbl-conversation_architecture.tex
update introduction & related work; descriptions for figures

@@
 \caption{Conversation architecture elements}
+\Description{This table categorizes conversation architecture elements into four categories,  provide some examples for the element, and show the number of papers as well as references to the papers in our reviewed corpus.
+The first category is dialog strategy, which contains the elements of social dialog, initiative and response delay.
+The second category is content affectiveness, which contains the elements of affective language and humour.
+The third category is content style, which contains the elements of formality, alignment and elaborateness.
+The fourth category is speech format, which contains the elements of prosody, disfluency, and text formatting.}
 \label{tbl:conversation_architecture}

### 2023-02-23 tables/tbl-perceptions.tex
update introduction & related work; descriptions for figures

@@
 \\ \cline{2-5}
-    & Trust & credibility, trustworthy, truthfulness, confidence & 15
+    & Credibility & trustworthy, truthfulness, confidence & 15
     & \cite{andrews2012system}\cmt{[38]}\cite{chan2021kinvoices}\cmt{[74]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{fadhil2018effect}\cmt{[52]}\cite{healey2013relating}\cmt{[39]}\cite{hoegen2019end}\cmt{[31]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kraus2020effects}\cmt{[64]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{ma2022ask}\cmt{[29]}\cite{seeger2021chatbots}\cmt{[35]}\cite{tolmeijer2021female}\cmt{[62]}\cite{wilhelm2022keep}\cmt{[28]}
@@
 \caption{Perception aspects}
+\Description{This table categorizes perceptions of agents into four categories, provide some examples for the perception aspect, and show the number of papers as well as references to the papers in our reviewed corpus.
+The first category is perception of interaction with agent, which contains the aspects of usability, engagement, and satisfaction.
+The second category is perception of agent's ability, which contains the aspects of intelligence, competence, and credibility.
+The third category is perception of sociability with agent, which contains the aspects of conversation tone, social presence, and intimacy.
+The fourth category is perception of agent's humanness, which contains aspects of human-likeness and personality traits.}
 \label{tbl:perceptions}

### 2023-02-26 sections/1-introduction.tex
Young-Ho edits

@@
 
-While various studies investigated how different speech elements affect agents' perceptions, there is a paucity of knowledge on the overall coverage and effects of these relationships explored in literature.
+While various studies investigated how different speech elements affect agents' perceptions~(e.g.,~\cite{clark2019state, feine2019taxonomy, finch2020towards}), there is a paucity of knowledge on the overall coverage and effects of these relationships explored in literature.
 One reason for this disparity is the lack of clear and consistent definitions of the aspects of users' perceptions of agent and conversation architectural elements.
@@
 
-These research gaps related to the paucity of knowledge on synthesizing the effect of speech specifics on perceptions of CAs as well as the lack of systematic understanding on the elements of conversation architecture and perceptions of agents motivated us to the goal of how to design conversation architecture in order to orchestrate perceptions of conversational agents.
+%These research gaps related to the paucity of knowledge on synthesizing the effect of speech specifics on perceptions of CAs as well as the lack of systematic understanding on the elements of conversation architecture and perceptions of agents
+To address these research gaps, we aim to understand how to design conversation architecture in order to orchestrate perceptions of conversational agents.
 First, we want to understand \textbf{(RQ1) what perception aspects of agents are being explored in relation to the effects of conversation architecture elements}.

### 2023-02-26 sections/4-findings.tex
Young-Ho edits

@@
 Some commonly used methods to evaluate usability include the response accuracy portion of the SASSI questionnaire \cite{hone2000towards}\cmt{sassi}, or the NASA Task Load Index (NASA-TLX) \cite{hart1988development}\cmt{nasa} for cognitive workload.
-Questions such as "the system is easy to use" or "it is easy to understand the agent" are also used to evaluate usability.
+Questions such as ``\textit{the system is easy to use}'' or ``\textit{it is easy to understand the agent}'' are also used to evaluate usability.
 \textit{Engagement} on the other hand captures users' emotional reactions to the CA, whether they have enjoyed the conversation, or annoyed or frustrated with the interaction.
 Some commonly used methods to evaluate engagement include the annoyance portion of the SASSI questionnaire \cite{hone2000towards}\cmt{sassi}, and the Use Engagement Scale (UES) \cite{o2018practical}\cmt{ues}.
-Questions such as "I enjoyed using the system" or "I felt frustrated with the agent" are also used to evaluate engagement.
+Questions such as ``\textit{I enjoyed using the system}'' or ``\textit{I felt frustrated with the agent}'' are also used to evaluate engagement.
 Lastly, \textit{Satisfaction} captures users' overall satisfaction interacting with the agent.
-Questions such as "the overall assessment of conversing with the CA was satisfactory" are used to evaluate this perception.
+Questions such as ``\textit{the overall assessment of conversing with the CA was satisfactory}'' are used to evaluate this perception.
 
@@
 Some commonly used methods to evaluate trust include the Trust Propensity Scale \cite{mayer1999effect} and the Individualized Trust Scale (ITS) \cite{wheeless1977measurement}.
-Questions such as "is the agent honest" and "can I trust the agent with sensitive information" are also used to evaluate trust.
+Questions such as ``\textit{is the agent honest}'' and ``\textit{can I trust the agent with sensitive information}'' are also used to evaluate trust.
 
@@
 Also, this aspect includes whether the tone used by the agent was perceived as friendly, polite or warm.
-\textit{Social presence} captures the sense of connectness and psychological distance users have with an agent.
+\textit{Social presence} captures the sense of connectedness and psychological distance users have with an agent.
 Some aspects in this category include the sense of familiarity or similarity with the agent, and whether users feel the agent behaves like them or have similar attitudes to them.
@@
 Some commonly used methods to assess intimacy include the set of social attraction questions from the interpersonal attraction questionnaire \cite{mccroskey1975development} and the quality of relationship inventory (QRI) \cite{pierce1997assessing}.
-These questionnaires include questions like "I think the agent could be a friend of mine", or "I feel we could establish a personal relationship with each other".
+These questionnaires include questions like ``\textit{I think the agent could be a friend of mine}'', or ``\textit{I feel we could establish a personal relationship with each other}''.
 
@@
 The Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed} set of questions related to anthropomorphism and the Ascent of Man scale \cite{kteily2015ascent} are commonly used methods to evaluate human-likeness.
-Survey questions with semantic scales such as "human-like / machine-like" and "artificial / natural" are also commonly used for this aspect of perception.
+Survey questions with semantic scales such as ``\textit{human-like / machine-like}'' and ``\textit{artificial / natural}'' are also commonly used for this aspect of perception.
 \textit{Personality traits} captures the human characteristics that are attributes to the agent.
@@
 For example, Roy et al.
-explored the differences in perception for variations in elaborateness such as "Cloudly, possibility of snow, high: 4, low: -10" vs "Today will be cloudy, with a high of 4 and a low of -10.
-Snow is predicted" \cite{roy2021users}\cmt{[71]}.
+explored the differences in perception for variations in elaborateness such as ``\textit{Cloudly, possibility of snow, high: 4, low: -10}'' vs ``\textit{Today will be cloudy, with a high of 4 and a low of -10.
+Snow is predicted}'' \cite{roy2021users}\cmt{[71]}.
 
 Lastly, the category of \textbf{speech format} captures the non-verbal component of a conversational agent's utterances for both text and voice modalities. \textit{Disfluency} captures 
-the use of non-lexical utterances like filler words ("um, uh") \cite{hu2021enhancing, jeong2019exploring}\cmt{[56][10]}, or repetition of words within a sentence \cite{yang2021effect}\cmt{[72]}.
+the use of non-lexical utterances like filler words (``\textit{um, uh}'') \cite{hu2021enhancing, jeong2019exploring}\cmt{[56][10]}, or repetition of words within a sentence \cite{yang2021effect}\cmt{[72]}.
 It also includes the format of using typos \cite{westerman2019believe}\cmt{[9]} for text-based agents.

### 2023-02-27 figures/fig-heatmap_coverage.tex
Anastasia edit

--- 2023-02-21 figures/fig-heatmap_coverage.tex
@@
   \includegraphics[width=\textwidth]{figures/fig-heatmap_coverage.pdf}
-  \caption{Heatmap of literature for perception of conversational agents for each type of conversational architecture element}
+  \caption{Number of past work that identified relationships between conversation architecture and the perception of agents (on the left) and number of past work that explored possible connections (on the right).}
+  \Description{This figure shows a side-by-side comparison between the 183 identified relationships within the 265 explored connections in literature for conversation architecture elements and perceptions of agents.
+The visuals are shown as two heatmaps, with darker shades depicting a higher number of relationships.
+The numbers within each cell at the interaction of a specific conversation architecture element and perception aspect outlines the number of relationships found in the reviewed corpus.}
   \label{fig:heatmap_coverage}

### 2023-02-27 paper.tex
Anastasia edit

@@
 %%
-%\begin{CCSXML}
-%<ccs2012>
-% <concept>
-%  <concept_id>10010520.10010553.10010562</concept_id>
-%  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
-%  <concept_significance>500</concept_significance>
-% </concept>
-% <concept>
-%  <concept_id>10010520.10010575.10010755</concept_id>
-%  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-%  <concept_significance>300</concept_significance>
-% </concept>
-% <concept>
-%  <concept_id>10010520.10010553.10010554</concept_id>
-%  <concept_desc>Computer systems organization~Robotics</concept_desc>
-%  <concept_significance>100</concept_significance>
-% </concept>
-% <concept>
-%  <concept_id>10003033.10003083.10003095</concept_id>
-%  <concept_desc>Networks~Network reliability</concept_desc>
-%  <concept_significance>100</concept_significance>
-% </concept>
-%</ccs2012>
-%\end{CCSXML}
+\begin{CCSXML}
+<ccs2012>
+   <concept>
+       <concept_id>10003120.10003121.10003126</concept_id>
+       <concept_desc>Human-centered computing~HCI theory, concepts and models</concept_desc>
+       <concept_significance>500</concept_significance>
+       </concept>
+   <concept>
+       <concept_id>10003120.10003121.10003122</concept_id>
+       <concept_desc>Human-centered computing~HCI design and evaluation methods</concept_desc>
+       <concept_significance>500</concept_significance>
+       </concept>
+   <concept>
+       <concept_id>10003120.10003121.10003124.10010870</concept_id>
+       <concept_desc>Human-centered computing~Natural language interfaces</concept_desc>
+       <concept_significance>500</concept_significance>
+       </concept>
+ </ccs2012>
+\end{CCSXML}
 
-%\ccsdesc[500]{Computer systems organization~Embedded systems}
-%\ccsdesc[300]{Computer systems organization~Redundancy}
-%\ccsdesc{Computer systems organization~Robotics}
-%\ccsdesc[100]{Networks~Network reliability}
-
-\ccsdesc{TBD}
+\ccsdesc[500]{Human-centered computing~HCI theory, concepts and models}
+\ccsdesc[500]{Human-centered computing~HCI design and evaluation methods}
+\ccsdesc[500]{Human-centered computing~Natural language interfaces}
 
@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{conversational agents, user perception, conversational architecture, anthropomorphized perceptions}
+\keywords{conversational agents, user perception, conversation architecture, anthropomorphized perceptions}
 

### 2023-02-27 sections/1-introduction.tex
Anastasia edit

--- 2023-02-22 sections/1-introduction.tex
@@
 Conversational agents (CAs), such as Amazon Alexa or Google Assistant, are designed to interact with humans using natural language through voice or text modalities.
-Since these agents communicate in natural language, \textit{conversation architecture}---what and how a CA says---affects users' perceptions of agents and, in turn, the effectiveness of their interactions~\cite{knijnenburg2016inferring, seeger2021chatbots}.
-According to previous research, there is a correlation between CAs' conversation architecture and users' perception of these agents.
+Since these agents communicate in natural language, \textit{conversation architecture}---what and how a CA says---affects users' perceptions of agents and, in turn, the effectiveness of their interactions with users \cite{knijnenburg2016inferring, seeger2021chatbots}, i.e.
+supporting users in achieving users' goals.
+For instance, previous research suggests that there is a relationship between CAs' conversation architecture and how users perceive these agents %.
+%While various studies investigated how some elements of conversation architecture affect users' perceptions of agents~
+(e.g.,~\cite{clark2019state, feine2019taxonomy, finch2020towards}).
+However, there is currently a lack of systematic understanding of these relationships, i.e.
+what elements of conversation architecture are impactful for users' perceptions and how.
+Specifically, while various studies investigated how some elements of conversation architecture affect some aspects of users' perceptions or discussed the speech specifics of agents as part of a broader analysis of the state of research \cite{clark2019state,feine2019taxonomy}, there is no comprehensive analysis of %research specifically for
+conversation architecture elements that are relevant to user perceptions.
+Yet, this systematic understanding is essential for guiding the design of conversation architecture, which would allow us to both predict and develop users' appropriate perceptions of agents.
 
-While various studies investigated how different conversation architecture elements affect agents' perceptions, there is a paucity of knowledge on the overall coverage and effects of these relationships explored in literature.
-For conversation architecture elements, the use of affective language is commonly explored, with studies finding that conversational agents are perceived as more socially present and emotionally intelligent if they use sentiment-adaptive response based on user's utterances~\cite{diederich2019emulating, yang2017perceived}.
-Another commonly explored element is the use of prosody in voice-based agents, such as the use of express prosody contributing to higher perceived enjoyment and intimacy with the agent \cite{kim2020can}.
-However, there is a lack of research to synthesize these findings into an overall framework.
-One of the possible issues is the lack of clear and consistent definitions of the aspects of users' perceptions of agent and conversation architectural elements.
+%there is a lack of systematic understanding of these relationships.
+%paucity of knowledge on the overall coverage and effects of these relationships explored in literature. 
+%One reason for this disparity is, arguably, the lack of clear and consistent definitions of both the aspects of users' perceptions of agent and conversation architectural elements.
+Although some authors discuss the speech specifics of agents as part of a broader analysis on the state of research \cite{clark2019state,feine2019taxonomy}, there is no comprehensive analysis of %research specifically for
+%conversation architecture elements that are relevant to user perceptions.
+Similarly for user perceptions, while there is some research exploring the perceptions of agents as part of understanding the user experiences \cite{clark2019state, finch2020towards} or social cues \cite{feine2019taxonomy} of CAs, there is no exhaustive research specifically for perceptions of agents that are affected by conversation architecture elements.
 
-Currently, there is no systematic understanding on the elements of conversation architecture that are relevant to the perceptions of agents.
-Some papers have started to examine the speech specifics explored in literature, such as \citet{clark2019state} capturing different elements of system speech production for voice-based agents and categorizing them based on content, style, and other topics.
-There are also some investigations of conversation architecture elements within the broader field of studying cues that trigger a social reaction of the user towards the CA.
-Feine et al's \cite{feine2019taxonomy} paper laid the foundation to create a consistent taxonomy for these social cues.
-However, there is no comprehensive research specifically for conversation architecture elements that are relevant to user perceptions.
+%These research gaps related to the paucity of knowledge on synthesizing the effect of speech specifics on perceptions of CAs as well as the lack of systematic understanding on the elements of conversation architecture and perceptions of agents
+To address this gap, in this paper, we
+%we aim to understand how to design conversation architecture in order to orchestrate perceptions of conversational agents.
+%First, we 
+explore the following research questions: \textbf{(RQ1) what aspects of users' perceptions of agents have been explored in relation to the effects of conversation architecture elements}, \textbf{(RQ2) what elements of conversation architecture are relevant to users' perceptions of agents?}, and \textbf{(RQ3) what is known of the specifics of these relationships between conversation architecture elements and the perceptions of CAs?}
+%While there are various elements of conversation architecture used in a CA's utterances, we don't have a systematic understanding of them.
+This leads to our second research question: \textbf{(RQ2) what elements of conversation architecture are relevant to users' perceptions of agents?} Lastly, we want to understand the effect of conversation architecture on perceptions of agent, specifically: \textbf{(RQ3) what are the relationships between conversation architecture elements and the perceptions of CAs?}
+To answer these questions, we performed a comprehensive review of the existing literature published from 2010 to 2022 and synthesized the effect of conversation architecture elements on the perceptions of CAs based on the final dataset of 57 relevant papers (\autoref{fig:heatmap_identified}).
+Based on this review, we grouped the perceptions of agents that were shown to be affected by conversation architecture into four categories and eleven aspects (\autoref{tbl:perceptions}) and grouped the speech variations related to perceptions of agents into four categories and eleven elements (\autoref{tbl:conversation_architecture}).
+We found that perceptions of interaction with CAs (usability, engagement, satisfaction) have been most explored in relation to speech variations, while the perceptions of CAs' ability (intelligence, competence, credibility) have been explored the least.
+%the least number of explored and identified relationships. 
+Our results also show that the conversation architecture elements of response delay and agent-initiated dialog-related perceptions of CAs are under-explored in literature. 
+Thus, this work contributes to the CUI community by presenting a framework that synthesizes the findings on the effect of conversation architecture on perceptions of conversational agents and identifies and clusters perception aspects and conversation architecture elements.
+%, providing clear and consistent terms that can be used in future research.
+Together, these contributions move us one step closer to designing CAs that effectively interact with users.
 
-Related to user perceptions, there is also no systematic understanding on the perceptions of agents affected by speech variations.
-Some research discussed the perceptions of agents as part of the broader scope of user experiences of CAs.
-These publications have gathered UX dimensions used to evaluate conversational agents, which include the perceptions of agents (e.g.
-empathy, humanness) alongside other assessments (e.g.
-physiological data) \cite{clark2019state, finch2020towards}.
-Some even categorized the metrics based on the type of method used, including technical measures like system error rate and perception measures like perceived social presence \cite{zheng2022ux}.
-However, these studies are assessing the general field of UX measurements and not specifically on the perceptions of agents, and do not analyze the effects of conversation architecture on these perceptions.
-
-These research gaps discussed above: the paucity of knowledge on synthesizing the effect of speech specifics on perceptions of CAs as well as the lack of systematic understanding on the elements of conversation architecture and perceptions of agents motivated us to the goal of how to design conversation architecture in order to orchestrate perceptions of conversational agents.
-First, we want to understand \textbf{(RQ1) what perception aspects of agents are being explored in relation to the effects of conversation architecture elements}.
-While there are various architecture elements of conversation architecture used in a CA's utterances, we don't have a holistic understanding of them.
-This leads to our second research question: \textbf{(RQ2) what elements of conversation architecture are relevant to the perceptions of agents?} Lastly, we want to understand the effect of conversation architecture on perceptions of agent, specifically: \textbf{(RQ3) what are the relationships between conversation architecture elements and the perceptions of CAs?}
-
-To answer these questions, we performed a comprehensive review on existing literature from 2010 to 2022 and synthesized the effect of conversation architecture elements on the perceptions of CAs based on 57 relevant papers (\autoref{fig:heatmap_identified}).
-We also grouped the perceptions of agents affected by conversation architecture into four categories and eleven aspects (\autoref{tbl:perceptions}), and grouped the speech variations related to perceptions of agents into four categories and eleven elements (\autoref{tbl:conversation_architecture}).
-%Lastly, we coded the explored connections between conversation architecture and perceptions and synthesized their relationships into a framework.
-Through our analysis, we also found that there are inconsistencies in the assessment of perceptions across studies, as well as influencing factors other than conversation architecture that impact the perceptions of agents.
-This work contributes to the HCI community by presenting a framework that demonstrates the effect of conversation architecture on perceptions of conversational agents, as well as taxonomies for perception aspects and conversation architecture elements providing clear and consistent terms that can be used in future research.
-Together, these contributions move us one step closer to designing CAs that effectively interact with users.
-%Also, our analysis extends existing reviews on UX research of CAs \cite{clark2019state}\cite{rapp2021human}\cite{zheng2022ux} by providing a synthesized framework outlining the relationships between conversation architecture and perceptions of agents.
-With the help of this framework, we are taking the first step to understand how to design conversational agents to solicit specific social reactions from users.
-
-In the remainder of the paper, we first outline related background work, our literature review process, as well as the characteristics of the papers in our reviewed corpus.
-Following that, we describe in detail the taxonomy for the perception of agents, the taxonomy for conversation architecture element, as well as the framework on the relationships between perceptions of agents and conversation architecture.
-Finally, we discuss research challenges and opportunities as well as ethical considerations for designing conversational architecture to orchestrate perceptions of conversational agents.
+In the remainder of the paper, we first outline related background work, then describe the literature review process and the framework synthesis method, %, the characteristics of the papers in our reviewed corpus.
+Following that, we
+followed by a detailed description of the taxonomies of the aspects of the perception of agents and conversation architecture elements, as well as the synthesized framework for their relationships.
+We conclude by discussing the implications of this work, including
+the associated research challenges and opportunities, as well as ethical considerations for designing the conversational architecture to affect users' perceptions of conversational agents.

### 2023-02-27 sections/2-related_work.tex
Anastasia edit

--- 2023-02-22 sections/2-related_work.tex
@@
 \section{Related Work}
-
-Communication with conversational agents is similar to communicating with humans as they both use natural languages for the interaction.
-While it is tempting to leverage components from human-human conversation in designing interactions with conversational agents, studies have demonstrated that there are differences between human-human communications and human-agent communications.
-Currently people consider CAs as a user-controlled tool rather than a social companion, with focuses on the utilitarian aspects of the conversation \cite{clark2019makes}\cmt{[1]}.
-When conversing with conversational agents, users tend to use shorter messages with limited vocabulary, adapting to the style of the agent \cite{hill2015real}.
+%Communication with conversational agents 
+Similar to human-human communication, human communication with conversational agents relies on natural languages for interaction.
+However, while it is tempting to leverage components from human-human conversation in designing interactions with conversational agents, studies have demonstrated that there are differences between human-human communications and human-agent communications \cite{clark2019makes, hill2015real}.
+Currently, CAs are considered as a user-controlled tool rather than a social companion, with a focus on the utilitarian aspects of the conversation \cite{clark2019makes}\cmt{[1]}.
+When conversing with agents, users tend to use shorter messages with limited vocabulary, adapting to the style of the agent \cite{hill2015real}.
 Also, some studies found that small talk and humour are considered unnecessary or even inauthentic in conversations with CAs, while these elements are important in scaffolding communications with human partners \cite{clark2019makes, doyle2019mapping}\cmt{[1],[2]}.
@@
 
-There have been numerous studies on the user experiences for conversational agents, and some attempts to synthesize findings across literature.
-Several papers have mapped out the current state of research for conversational agents for specific agent types (e.g.
+There are a number of studies investigating factors affecting user experiences for conversational agents, which includes exploring the relationship between conversation architecture elements and agents' perceptions.
+For instance, the use of affective language is commonly explored, with studies finding that conversational agents are perceived as more socially present and emotionally intelligent if they use sentiment-adaptive responses based on user's utterances \cite{diederich2019emulating, yang2017perceived}.
+Another commonly explored element is the use of prosody in voice-based agents, such as the use of express prosody contributing to higher perceived enjoyment and intimacy with the agent \cite{kim2020can}.
+However, there is a paucity of research to synthesize these findings on user experiences with agents across literature.
+
+In recent years, several papers have synthesized the current state of research for conversational agents for specific agent types (e.g.
 text-based, voice-based, polyadic) highlighting major trends, topics, methods and evaluating metrics \cite{clark2019state, rapp2021human, zheng2022ux}\cmt{[33][5]}.
-Other papers looked at specific dimensions of user experiences or domains of usage, such as Van Pinxteren et al.
-\cite{van2020human} examining the effects of agents' human-like communicative behaviours on their relationships with users, and Kocaballi et al.
-\cite{kocaballi2022design} exploring the challenges and opportunities of CAs in healthcare.
-There are also publications aimed to unify concepts used in the research for CA user experiences, for instance Feine et al.
-\cite{feine2019taxonomy} creating a taxonomy of social cues, and Finch et al.
-\cite{finch2020towards} analyzing evaluation protocols for dialogue systems.
+Other papers looked at specific dimensions of user experiences or domains of usage, such as \citet{van2020human} examining the effects of agents' human-like communicative behaviours on their relationships with users, and \citet{kocaballi2022design} exploring the challenges and opportunities of CAs in healthcare.
+There are also publications aimed to unify concepts used in the research for CA user experiences, for instance \citet{feine2019taxonomy} creating a taxonomy of social cues, and \citet{finch2020towards} analyzing evaluation protocols for dialogue systems.
 To the best of our knowledge, there is currently no synthesis on the speech specifics of CAs, the perceptions of agents, or the relationship between them.
@@
 Given the paucity of research in this area, this paper aims to synthesize the identified relationships between conversation architecture elements and users' perceptions of agents.
-
-%Other papers categorized CA assessments into themes.
-For example, Rapp et al.
-\cite{rapp2021human} generated themes related to how users' experience with chatbots such as experiencing the chatbot including assessments on expectation, perception, satisfaction etc.
-Most recently, Zheng et al's literature review on the UX research of CAs \cite{zheng2022ux} categorized the metrics based on the type of method used, including technical measures like system error rate and perception measures like perceived social presence.
-However, existing studies use different terminologies and categories across aspects of perception.
-As an illustration, it is unclear if the theme of experiencing the chatbot from Rapp et al.
-\cite{rapp2021human} contains similar aspects to the perception towards CA in Zheng et al \cite{zheng2022ux}'s analysis.
-%\cite{finch2020towards} Towards unified dialogue system evaluation: A comprehensive analysis of current evaluation protocols
-
-%Anthropomorphism is defined as the attribution of traits that we typically associate with being distinctly human to nonhuman entities \cite{waytz2010sees}.
-For example, users tend to personify conversational agents like Amazon Alexa by using person pronouns instead of object pronouns in online reviews \cite{purington2017alexa}.
-Research shows that anthropomorphic design is beneficial to establishing and maintaining trust between users and conversational agents \cite{seeger2021chatbots}.
-Also, speakers tend to align their lexical choices with conversational agents, similar to human-human conversations \cite{cowan2015does}.
-Anthropomorphism has been shown to ease user interactions, e.g.
-making agents more approachable, engaging, and trustworthy when they exhibit human characteristics \cite{qiu2009evaluating}.
-These processes are of particular interest for human-agent communication because they form the basis for user expectations and predispositions regarding agents' behavior, reliability of the information, etc.
-\cite{kuzminykh2020genie}.

### 2023-02-27 sections/3-method.tex
Anastasia edit

@@
 
-This section describes the research methodologies used for data collection and data analysis. Additionally, it presents the characteristics of the papers in our reviewed corpus.
+%This section describes the research methodologies used for data collection and data analysis. Additionally, it presents the characteristics of the papers in our reviewed corpus.
 
 \subsection{Data Collection}
-
-Following PRISMA guidelines \cite{prisma}, we reviewed and selected literature exploring the relationship between the specifics of conversation architecture elements and perceptions of CAs.
+To perform a literature analysis of past findings on the relationship between the specifics of conversation architecture and perceptions of CAs, we identified, reviewed, and selected relevant literature using PRISMA guidelines \cite{prisma}.
+%, we reviewed and selected literature exploring the relationship between the specifics of conversation architecture elements and perceptions of CAs.
 Searches were carried out in the ACM Digital Library between January 1 and January 15, 2023.
-Through our analysis, we didn't find any common terms used to refer to either conversation architecture elements, or aspects of perceptions.
+Through our analysis, we didn't find any common terms used to refer to either conversation architecture elements or aspects of perceptions.
 As such, we generalized our search term to capture articles related to conversational agents.
@@
 We screened the titles and abstracts of the papers based on the selection criteria above, resulting in 221 papers.
-The fully body of these papers are then reviewed, selecting 49 papers that met the criteria.
-A search for additional literature was also performed to supplement the corpus, adding 8 more papers to the selection.
+The fully body of these papers were then reviewed, selecting 49 papers that met the criteria.
+A search for additional literature based on citation tracing was also performed to supplement the corpus, adding 8 more papers to the selection.
 In total, we identified 57 relevant articles for analysis (see \autoref{fig:prisma}).
@@
 The papers reviewed (n=57) were published between May 2011 and November 2022.
-More than 75\% of the papers were published in or after 2019, with a slight trend upwards over the years (see \autoref{fig:paper}).
+The majority of the papers were published in or after 2019, with a slight trend upwards over the years (see \autoref{fig:paper}).
 The vast majority of the papers in our corpus were published in conference proceedings (n=50), with the remainder papers published in journals.
@@
 This step resulted in 83 unique codes.
-These codes are then organized based similarity of the meanings, resulting in 11 aspects of perceptions.
+These codes are then organized based on similarity of the meanings, resulting in 11 aspects of perceptions.
 For example, the aspect of personality traits of the agent contains measurements such as likeability, funniness, and kindness.

### 2023-02-27 sections/4-findings.tex
Anastasia edit

@@
 
-As shown in \autoref{tbl:perceptions}, there are four categories defined for the perceptions of conversational agents covering 11 different aspects of perception.
+As shown in \autoref{tbl:perceptions}, we defined four categories for the perceptions of conversational agents covering 11 different aspects of perception.
 The details of each category and aspect are discussed below.
@@
 \textit{Social presence} captures the sense of connectedness and psychological distance users have with an agent.
-Some aspects in this category include the sense of familiarity or similarity with the agent, and whether users feel the agent behaves like them or have similar attitudes to them.
+Some aspects in this category include the sense of familiarity or similarity with the agent, and whether users feel the agent behaves like them or has similar attitudes to them.
 The category of \textit{Intimacy} extends social presence into the realm of the quality of relationships with an agent.
@@
 Overall there is a good coverage of different aspects of perception based on the list of papers reviewed in our corpus.
-The most commonly explored aspect categories is the perception the interaction with agent, followed by the perception of agent's humanness.
+The perception of interaction with agent is the most commonly explored category, followed by the perception of agent's humanness.
 There are two aspects that are the least explored compared to the others relationships: competence within the perception of agent's ability, and intimacy within the perception of social connection with agent.
@@
 The same factor could impact the assessment of agent's competence, as the users may not feel like they have the expertise to assess their perceptions.
-%These factors could contribute to the reasons why competency and intimacy are not as frequently measured in experimental studies.
 
@@
 
-As shown in \autoref{tbl:conversation_architecture}, there are four categories defined for conversation architecture across 12 different elements.
+As shown in \autoref{tbl:conversation_architecture}, we defined four categories for conversation architecture across 12 different elements.
 The details of each category and element are discussed below.

### 2023-02-27 sections/5-discussion.tex
Anastasia edit

@@
 One such example is Ma et al's study \cite{ma2022ask}\cmt{[29]} on the different approaches for CAs to reply to users' uncertain queries.
-A single UX score is used to evaluate the users' perceptions, which composes of questions on whether the user thinks the CA's response is pleasing / trustworthy / natural / acceptable / shorten the distance between CA and user.
+A single UX score is used to evaluate the users' perceptions, which composes of questions on whether the user thinks the CA's response is pleasing / trustworthy / natural / acceptable / shorten the distance between CA and the user.
 The UX score encompasses multiple aspects across several perception categories.
-While this study has found significant effect for the use of formal language on the user rated UX score, it is not possible to understand how the details of formality is related to the perception categories of interaction (pleasing, acceptable), sociability (shorten the distance between CA and user), and humanness (natural, trustworthy).
+While this study has found significant effect for the use of formal language on the user-rated UX score, it is not possible to understand how the details of formality is related to the perception categories of interaction (pleasing, acceptable), sociability (shorten the distance between CA and user), and humanness (natural, trustworthy).
 The humanness questionnaire from Holtgraves et al \cite{holtgraves2007perceiving} has a similar problem, evaluating across perception categories of interaction (responsiveness, engagement), ability (skillfulness), sociability (politeness), and humanness (human-likeness, thoughtfulness).
@@
 There are also correlations between aspects found within the same perception category, such as a speech agent that is rated higher in perceived human-likeness was associated with higher likability ratings \cite{zhu2022effects}\cmt{[26]}.
-Also, within the perception category of social connection, one study found that social distance is positively related to the perceived social attraction \cite{westerman2019believe}\cmt{[9]}.
+Also, within the perception category of social connection, one study found that social distance is positively related to perceived social attraction \cite{westerman2019believe}\cmt{[9]}.
 
@@
 Specifically, more studies are needed to understand the effects of social dialog, response delay, humour and elaborateness on users' perceptions of agents' ability.
-For the perception category of sociability with agent, there is a general lack of explored connections with the conversation architecture category of content style, especially for alignment and elaborateness elements.
-Lastly, more studies on the effect of dialog strategy for conversation architecture elements of initiative and response delay on the perceptions of agent are needed.
+For the perception category of sociability with agents, there is a general lack of explored connections with the conversation architecture category of content style, especially for alignment and elaborateness elements.
+Lastly, more studies on the effect of dialog strategy for conversation architecture elements of initiative and response delay on the perceptions of agents are needed.
 
@@
 \cite{gnewuch2018faster}\cmt{[19]} found that experienced users perceived the agent with a response delay as lower in social presence because it is seen as inefficient to wait for the CA to respond, but novice users perceived higher social presence conversing with the CAs using response delays because it is more similar to conversations with human partners \cite{gnewuch2018faster}\cmt{[19]}.
-User characteristics is another factor, as the perceived trustworthiness of a style matching agent depended on users' own conversational style \cite{hoegen2019end}\cmt{[31]}.
-Some other contextual factors that resulted in differences in perceptions of agent include the purpose of conversation (e.g.
+User characteristics is another factor, as the perceived trustworthiness of a style-matching agent depended on users' own conversational style \cite{hoegen2019end}\cmt{[31]}.
+Some other contextual factors that resulted in differences in perceptions of an agent include the purpose of conversation (e.g.
 transactional vs.
@@
 
-As we gain a better understanding about the effects of a single conversation architecture element on the perceptions of agents, we can extend the research to using \textit{multiple conversation architecture elements} in an agent.
-Several papers in our reviewed corpus incorporated composite elements in an agent, such as the design of an anthropomorphized chatbot using elements such as affective language, emoticons, response delays to assess users' perceptions compared to a non-anthropomorphized chatbot \cite{seeger2021chatbots}\cmt{[35]}.
-In addition to explore the combined effects of conversation architecture elements on users' perceptions, it would also be interesting to understand the relative importance of each element on perceptions.
+As we gain a better understanding of the effects of a single conversation architecture element on the perceptions of agents, we can extend the research to using \textit{multiple conversation architecture elements} in an agent.
+Several papers in our reviewed corpus incorporated composite elements in an agent, such as the design of an anthropomorphized chatbot using elements such as affective language, emoticons, and response delays to assess users' perceptions compared to a non-anthropomorphized chatbot \cite{seeger2021chatbots}\cmt{[35]}.
+In addition to exploring the combined effects of conversation architecture elements on users' perceptions, it would also be interesting to understand the relative importance of each element on perceptions.
 Some studies analyzed the effect of modifying conversation architecture elements individually, as well as their combined effect on user's perceptions (e.g.
@@
 Specifically, Habler et al.
-\cite{habler2019effects}\cmt{[63]} found that the effect for social dialog is higher than the effect for prosody on the perception of agents.
+\cite{habler2019effects}\cmt{[63]} found that the effect of social dialog is higher than the effect of prosody on the perception of agents.
 
@@
 The designers of conversational agents need to consider ethical implications and potential negative impacts for users.
-This section discusses three main areas of concerns related to the effect of conversation architecture on the perceptions of agents: gender stereotypes, influencing user's actions and privacy concerns.
+This section discusses three main areas of concern related to the effect of conversation architecture on the perceptions of agents: gender stereotypes, influencing users' actions, and privacy concerns.
 
@@
 Even in studies that are not explicitly analyzing the effect of different gendered voices in an agent, possible stereotypes may still exist in the study.
-Based on our reviewed corpus, studies found that lower pitches commonly associated with men are considered to be more desirable, authoritative but less friendly \cite{jestin2022effects, tolmeijer2021female}\cmt{[81][62]}.
-For Dubiel et al's study \cite{dubiel2020persuasive}\cmt{[60]}, the agent with lower mean pitch was selected as the more persuasive voice.
-These results may be demonstrating users' unconscious bias to select a male sounding voice as more persuasive and authoritative over female sounding voices that are commonly associated with higher pitches.
+Based on our reviewed corpus, studies found that lower pitches commonly associated with men are considered to be more desirable and authoritative but less friendly \cite{jestin2022effects, tolmeijer2021female}\cmt{[81][62]}.
+For Dubiel et al's study \cite{dubiel2020persuasive}\cmt{[60]}, the agent with a lower mean pitch was selected as the more persuasive voice.
+These results may be demonstrating users' unconscious bias to select a male-sounding voice as more persuasive and authoritative over female-sounding voices that are commonly associated with higher pitches.
 While some guidelines recommend designing agents to be androgynous to avoid gender stereotypes \cite{ruane2019conversational}, there are limitations in creating gender-ambiguous voices.
-Currently there is no defined guidelines on what is perceived as a gender-neutral voice \cite{jestin2022effects}\cmt{[81]}.
+Currently, there are no defined guidelines on what is perceived as a gender-neutral voice \cite{jestin2022effects}\cmt{[81]}.
 There is also a lack of voice generators available to generate voices that are perceived as androgynous \cite{tolmeijer2021female}\cmt{[62]}.
@@
 This opens up the ethical issue of influencing users' attitudes and behaviours through these persuasion techniques.
-In a study by Chan et al \cite{chan2021kinvoices}\cmt{[74]}, they found that CAs using kin's voices are perceived as more credible and likeable, with a higher perceived social presence with the agent.
-These perceptions contributes to the agent being more engaging and persuasive, therefore people are more likely to comply with its requests.
+In a study by Chan et al \cite{chan2021kinvoices}\cmt{[74]}, they found that CAs using kin's voices are perceived as more credible and likable, with a higher perceived social presence with the agent.
+These perceptions contribute to the agent being more engaging and persuasive, therefore people are more likely to comply with its requests.
 Andrew et al \cite{andrews2012system}\cmt{[38]} found that tailoring the personality of the CA to users will positively impact an agent's persuasiveness.
@@
 Also, most of the studies in our corpus are based on lab experiments using short interactions with users.
-The generalizability of these findings need to be verified through longer term engagements with conversational agents deployed in real world situations.
-Lastly, research without empirical studies on the perception of agents are excluded based on our selection criteria.
+The generalizability of these findings needs to be verified through longer-term engagements with conversational agents deployed in real-world situations.
+Lastly, research without empirical studies on the perception of agents is excluded based on our selection criteria.
 We may have missed some influential findings in these papers.

### 2023-02-27 figures/fig-heatmap_identified.tex
submitted version to CUI 2023

@@
 
-\begin{figure*}[]
+\begin{figure*}[t]
   \centering
-  \includegraphics[width=\textwidth]{figures/fig-heatmap_identified.pdf}
-  \caption{Synthesized framework on the identified relationship between perception of agents and conversation architecture elements}
+  \includegraphics[width=0.9\textwidth]{figures/fig-heatmap_identified.pdf}
+  \caption{Synthesized framework on the identified relationship between perception of agents and conversation architecture elements.
+The heatmap visualizes the number of relationships identified from the literature.
+Note that a single paper may describe more than one relationship.}
   \Description{This figure shows a heatmap the 183 identified relationships between conversation architecture elements and perceptions of agents.

### 2023-02-27 sections/1-introduction.tex
submitted version to CUI 2023

@@
 Since these agents communicate in natural language, \textit{conversation architecture}---what and how a CA says---affects users' perceptions of agents and, in turn, the effectiveness of their interactions with users \cite{knijnenburg2016inferring, seeger2021chatbots}, i.e.
-supporting users in achieving users' goals.
+supporting users in achieving their goals.
 For instance, previous research suggests that there is a relationship between CAs' conversation architecture and how users perceive these agents %.
@@
 what elements of conversation architecture are impactful for users' perceptions and how.
-Specifically, while various studies investigated how some elements of conversation architecture affect some aspects of users' perceptions or discussed the speech specifics of agents as part of a broader analysis of the state of research \cite{clark2019state,feine2019taxonomy}, there is no comprehensive analysis of %research specifically for
+Specifically, while various studies investigated how some elements of conversation architecture affect aspects of users' perceptions or discussed the speech specifics of agents as part of a broader analysis of the state of research \cite{clark2019state,feine2019taxonomy}, there is no comprehensive analysis of %research specifically for
 conversation architecture elements that are relevant to user perceptions.
@@
 %These research gaps related to the paucity of knowledge on synthesizing the effect of speech specifics on perceptions of CAs as well as the lack of systematic understanding on the elements of conversation architecture and perceptions of agents
-To address this gap, in this paper, we
+To address this gap, %in this paper, we
 %we aim to understand how to design conversation architecture in order to orchestrate perceptions of conversational agents.
 %First, we 
-explore the following research questions: \textbf{(RQ1) what aspects of users' perceptions of agents have been explored in relation to the effects of conversation architecture elements}, \textbf{(RQ2) what elements of conversation architecture are relevant to users' perceptions of agents?}, and \textbf{(RQ3) what is known of the specifics of these relationships between conversation architecture elements and the perceptions of CAs?}
+we explore the following research questions in this paper: \textbf{(RQ1) what aspects of users' perceptions of agents have been explored in relation to the effects of conversation architecture elements?}, \textbf{(RQ2) what elements of conversation architecture are relevant to users' perceptions of agents?}, and \textbf{(RQ3) what is known about the specifics of these relationships between conversation architecture elements and the perceptions of CAs?}
 %While there are various elements of conversation architecture used in a CA's utterances, we don't have a systematic understanding of them.
@@
 To answer these questions, we performed a comprehensive review of the existing literature published from 2010 to 2022 and synthesized the effect of conversation architecture elements on the perceptions of CAs based on the final dataset of 57 relevant papers (\autoref{fig:heatmap_identified}).
-Based on this review, we grouped the perceptions of agents that were shown to be affected by conversation architecture into four categories and eleven aspects (\autoref{tbl:perceptions}) and grouped the speech variations related to perceptions of agents into four categories and eleven elements (\autoref{tbl:conversation_architecture}).
+Based on this review, we grouped the perceptions of agents that were shown to be affected by conversation architecture into four categories (interaction, ability, sociability and humanness) and eleven aspects (\autoref{tbl:perceptions}), and grouped the speech variations related to perceptions of agents into four categories (dialog strategy, content affectiveness, content style and speech format) and eleven elements (\autoref{tbl:conversation_architecture}).
 We found that perceptions of interaction with CAs (usability, engagement, satisfaction) have been most explored in relation to speech variations, while the perceptions of CAs' ability (intelligence, competence, credibility) have been explored the least.
 %the least number of explored and identified relationships. 
-Our results also show that the conversation architecture elements of response delay and agent-initiated dialog-related perceptions of CAs are under-explored in literature. 
-Thus, this work contributes to the CUI community by presenting a framework that synthesizes the findings on the effect of conversation architecture on perceptions of conversational agents and identifies and clusters perception aspects and conversation architecture elements.
+Our results also show that the conversation architecture elements of response delay and agent-initiated dialog related to perceptions of CAs are under-explored in literature. 
+Thus, our work contributes to the CUI community by presenting a framework that synthesizes the findings on the effect of conversation architecture on perceptions of conversational agents while also identifying and clustering perception aspects and conversation architecture elements.
 %, providing clear and consistent terms that can be used in future research.

### 2023-02-27 sections/2-related_work.tex
submitted version to CUI 2023

@@
 %Communication with conversational agents 
-Similar to human-human communication, human communication with conversational agents relies on natural languages for interaction.
+Similar to human-human communication, users utilize natural languages when interacting with conversational agents.
+%human communication with conversational agents relies on natural languages for interaction.
 However, while it is tempting to leverage components from human-human conversation in designing interactions with conversational agents, studies have demonstrated that there are differences between human-human communications and human-agent communications \cite{clark2019makes, hill2015real}.
@@
 
-In recent years, several papers have synthesized the current state of research for conversational agents for specific agent types (e.g.
+In recent years, several papers have synthesized the current state of research for particular types of conversational agents (e.g.
 text-based, voice-based, polyadic) highlighting major trends, topics, methods and evaluating metrics \cite{clark2019state, rapp2021human, zheng2022ux}\cmt{[33][5]}.

### 2023-02-27 sections/3-method.tex
submitted version to CUI 2023

@@
   \item The paper contains the use of voice-based or text-based conversational agents.
-  \item The paper contains studies on the impact of conversation architecture elements on the perceptions of agents.
-  \item The paper contains impact of conversation architecture elements can be separated from other effects (e.g. embodiment).
+  \item The paper contains studies on the effect of conversation architecture elements on the perceptions of agents.
+  \item The paper contains effects of conversation architecture elements can be separated from other effects (e.g. embodiment).
 
@@
 The papers reviewed (n=57) were published between May 2011 and November 2022.
-The majority of the papers were published in or after 2019, with a slight trend upwards over the years (see \autoref{fig:paper}).
-The vast majority of the papers in our corpus were published in conference proceedings (n=50), with the remainder papers published in journals.
+Most of the papers were published in or after 2019, with a slight trend upwards over the years (see \autoref{fig:paper}).
+The vast majority of the papers in our corpus were published in conference proceedings (n=50), while the remaining papers were published in journals.
 Out of the papers published in conferences, the top conferences were The ACM Conference on Human Factors in Computing Systems\footnote{https://dl.acm.org/conference/chi} (n=16), Conversational User Interfaces\footnote{https://dl.acm.org/conference/cui} (n=7), Human-Agent Interaction\footnote{https://dl.acm.org/conference/hai} (n=4), and Intelligent Virtual Agents\footnote{https://dl.acm.org/conference/iva} (n=4).
@@
 
-On the modality characteristics of the conversational agents in the corpus, there is a roughly even split between the modalities, with slightly more papers exploring voice-based CAs (n=30) compared to text-based CAs (n=27).
+On the modality characteristics of the conversational agents in our corpus, there is a roughly even split between voice and text modalities, with slightly more papers exploring voice-based CAs (n=30) compared to text-based CAs (n=27).
 
@@
 We used inductive thematic analysis to group these assessments into codes based on their meanings.
-For example, the code likeability of the agent contains the questionnaire item "this voice agent was likeable" used by \cite{cuadra2021my}\cmt{[67]}, Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed}'s set of questions on likeability used by \cite{linnemann2018can}\cmt{[15]}, and Subjective Assessment of Speech System Interface (SASSI) questionnaire \cite{hone2000towards}\cmt{sassi}'s set of questions on likeability used by \cite{chan2021kinvoices, choi2020nobody}\cmt{[74][54]}.
+For example, likeability of the agent contains Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed}'s set of questions on likeability used by \cite{linnemann2018can}\cmt{[15]}, Subjective Assessment of Speech System Interface (SASSI) questionnaire \cite{hone2000towards}\cmt{sassi}'s set of questions on likeability used by \cite{chan2021kinvoices, choi2020nobody}\cmt{[74][54]} and questionnaire items like ``\textit{this voice agent was likeable}'' used by \cite{cuadra2021my}\cmt{[67]}.
 This step resulted in 83 unique codes.
-These codes are then organized based on similarity of the meanings, resulting in 11 aspects of perceptions.
-For example, the aspect of personality traits of the agent contains measurements such as likeability, funniness, and kindness.
+These codes are then organized based on similarity of their meanings, resulting in 11 aspects of perceptions.
+For instance, the aspect of personality traits of the agent contains codes such as likeability, funniness, and kindness.
 Lastly, the 11 aspects are grouped into 4 categories: perception of interaction with agent, perception of agent's ability, perception of sociability with agent, and perception of agent's humanness (\autoref{tbl:perceptions}).
@@
 \subsubsection*{Conversation Architecture Elements}
-As to the elements of conversation architecture that are relevant to the perception of agents (RQ2), we extracted the specifics of conversation architecture used in each paper.
-Some of the papers used multiple features in their CA design, such as the the anthropomorphic agent used in Seeger et al's study \cite{seeger2021chatbots}\cmt{[35]}.
-In these composite situations, we broke them down into their individual features.
-For example, the anthropomorphic agent \cite{seeger2021chatbots}\cmt{[35]} was separated into emotional expressions, is-typing indicator, emoticons, and response delay and captured as codes.
+As for the elements of conversation architecture that are relevant to the perception of agents (RQ2), we extracted the speech variation features used in each paper.
+Some of the papers used multiple features in their CA design, such as the anthropomorphic agent used in Seeger et al's study \cite{seeger2021chatbots}\cmt{[35]}.
+In these composite situations, we broke the CA design down into its individual features.
+For example, the design of the anthropomorphic agent \cite{seeger2021chatbots}\cmt{[35]} was divided into features of emotional expressions, is-typing indicator, emoticons, and response delay and captured as separate codes.
 58 unique codes were created as part of this process, capturing features like sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}, lexical alignment \cite{spillner2021talk}\cmt{[18]}, and typos \cite{westerman2019believe}\cmt{[9]}.
-We then organized these codes into elements based on similarity, resulting in 12 elements of conversation architecture.
+We then organized these codes into elements based on similarity, resulting in 11 elements of conversation architecture.
 For example, the element of disfluency contains fillers \cite{jeong2019exploring, wester2015artificial}\cmt{[10][14]}, interjections \cite{ceha2022expressive, hu2021enhancing}\cmt{[77][56]}, repetitions \cite{yang2021effect}\cmt{[72]} and typos \cite{westerman2019believe}\cmt{[9]}.
-These elements are grouped into 4 categories: dialog strategy, content affectiveness, content style, and speech format (\autoref{tbl:conversation_architecture}).
+These elements are then grouped into 4 categories: dialog strategy, content affectiveness, content style, and speech format (\autoref{tbl:conversation_architecture}).
 
@@
 \cite{hoegen2019end}\cmt{[31]} did not find a significant difference between the style matching agent and the non-style matching agent for overall interaction satisfaction.
-Out of the 193 relationships, 10 were relationships based on agents modifying multiple architecture elements (e.g.
+Out of the 193 relationships, 10 were based on comparisons between CAs with multiple speech element variations (e.g.
 \cite{seeger2021chatbots, volkel2021manipulating}\cmt{[35][68]}).
-They were not included in the final framework as we could not attribute the perceptions of agents to the underlying core elements.
-Overall, 183 relationships between individual architecture elements and perceptions of agents are incorporated into our synthesized framework, visualized as a heatmap to demonstrate their relationships with each other (\autoref{fig:heatmap_identified}).
+They were not included in the final framework as we could not attribute the perceptions of agents to the individual elements.
+Overall, 183 relationships between individual conversation architecture elements and perceptions of agents are incorporated into our synthesized framework, visualized as a heatmap to demonstrate their relationships with each other (\autoref{fig:heatmap_identified}).
+
+\subsection{Limitations}
+
+Our systematic literature review was limited to papers published in the ACM Digital Library between 2010 and 2022.
+We may have missed literature published outside this time period, as well as in other libraries.
+Also, most of the studies in our corpus are based on lab experiments using short interactions with users.
+The generalizability of these findings needs to be verified through longer-term engagements with conversational agents deployed in real-world situations.
+Lastly, research without empirical studies on the perception of agents is excluded based on our selection criteria.
+We may have missed some influential findings in these papers.
+%To better understand the relationships between conversation architecture elements and the perceptions of agents, we plan to conduct future reviews in literature and user studies to understand their real-world impacts.

### 2023-02-27 sections/4-findings.tex
submitted version to CUI 2023

@@
 
-\textbf{Perception of interaction with agent} assesses the overall interaction quality users had with the conversational agent.
-The three aspects for this perceptions are usability, engagement and satisfaction.
+\textbf{Perception of interaction with agent} assesses the overall interaction quality between users and conversational agents.
+The three aspects in this perception category  are: usability, engagement and satisfaction.
 \textit{Usability} captures the utilitarian component of the interaction, whether it was accurate, easy to use, efficient or helpful.
@@
 Questions such as ``\textit{the system is easy to use}'' or ``\textit{it is easy to understand the agent}'' are also used to evaluate usability.
-\textit{Engagement} on the other hand captures users' emotional reactions to the CA, whether they have enjoyed the conversation, or annoyed or frustrated with the interaction.
+\textit{Engagement} on the other hand captures users' emotional reactions to the CA, including whether they have enjoyed the conversation, or felt annoyed or frustrated with the interaction.
 Some commonly used methods to evaluate engagement include the annoyance portion of the SASSI questionnaire \cite{hone2000towards}\cmt{sassi}, and the Use Engagement Scale (UES) \cite{o2018practical}\cmt{ues}.
@@
 Lastly, \textit{Satisfaction} captures users' overall satisfaction interacting with the agent.
-Questions such as ``\textit{the overall assessment of conversing with the CA was satisfactory}'' are used to evaluate this perception.
+Questions such as ``\textit{the overall assessment of conversing with the CA was satisfactory}'' are used to evaluate this aspect of perception.
+
+\input{tables/tbl-perceptions}
 
 \textbf{Perception of agent's ability} assesses the perceived capabilities of the agent.
-Unlike system capabilities that affect agent's performance, the perceived ability category captures perceptions of agents with equivalent system capabilities but varied conversation architecture elements.
-Specifically, \textit{intelligence} captures the agent's expertise and knowledge, and it is commonly administered through the Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed} using the set of questions related to perceived intelligence.
+Unlike system capabilities that affect agent's performance, this perceived ability category captures perceptions of agents with equivalent system capabilities but varied conversation architecture elements.
+Specifically, \textit{intelligence} captures the agent's perceived expertise and knowledge, and it is commonly administered through the Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed} using the set of questions related to perceived intelligence.
 Also survey questions such as asking users about the agent's intelligence and domain knowledge are used to evaluate perceived intelligence.
-\textit{Competence} takes intelligence one step further by examining the agent's ability to put its intelligence into practice.
+\textit{Competence} takes intelligence one step further by examining the agent's perceived ability to put its intelligence into practice.
 Surveys or qualitative feedback are usually used to assess if the agent is capable and competent, and whether users have confidence in the agent's ability to get the job done.
-Lastly, \textit{credibility} captures agent's truthfulness, benevolence, and user's confidence in CAs.
+Lastly, \textit{credibility} captures agent's perceived truthfulness, benevolence, and user's confidence in CAs.
 Some commonly used methods to evaluate trust include the Trust Propensity Scale \cite{mayer1999effect} and the Individualized Trust Scale (ITS) \cite{wheeless1977measurement}.
@@
 
-\textbf{Perception of the sociability with agent} assesses the emotional connections that users have with agents.
-This category includes perception aspects of conversation tone, social presence and intimacy.
+\textbf{Perception of sociability with agent} assesses the emotional connections that users have with conversational agents.
+This category includes the perception aspects of conversation tone, social presence and intimacy.
 \textit{Conversation tone} captures the affective impression of the agent's tone, such as empathy and expressiveness.
@@
 \textit{Social presence} captures the sense of connectedness and psychological distance users have with an agent.
-Some aspects in this category include the sense of familiarity or similarity with the agent, and whether users feel the agent behaves like them or has similar attitudes to them.
-The category of \textit{Intimacy} extends social presence into the realm of the quality of relationships with an agent.
+This perception aspect also includes the sense of familiarity or similarity with the agent, and whether users feel the agent behaves like them or has similar attitudes to them.
+The aspect of \textit{intimacy} extends social presence into the realm of the quality of relationships with an agent.
 Some commonly used methods to assess intimacy include the set of social attraction questions from the interpersonal attraction questionnaire \cite{mccroskey1975development} and the quality of relationship inventory (QRI) \cite{pierce1997assessing}.
@@
 The Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed} set of questions related to anthropomorphism and the Ascent of Man scale \cite{kteily2015ascent} are commonly used methods to evaluate human-likeness.
-Survey questions with semantic scales such as ``\textit{human-like / machine-like}'' and ``\textit{artificial / natural}'' are also commonly used for this aspect of perception.
-\textit{Personality traits} captures the human characteristics that are attributes to the agent.
-This is commonly collected as qualitative feedback from users, commenting on whether the agent is extroverted or introverted, or the perceived personality such as likeable, funny or witty.
+Survey questions with semantic scales such as ``\textit{human-like / machine-like}'' and ``\textit{artificial / natural}'' are also used frequently to assess this aspect of perception.
+\textit{Personality traits} captures the human characteristics that are attributed to the agent.
+This is commonly collected as qualitative feedback from users, commenting on whether the agent is extroverted or introverted, or its perceived personality such as likeable, funny or witty.
 Sometimes the Big-5 personality traits questionnaire \cite{gosling2003very} is used to map an agent's disposition on various personality dimensions.
 
-Overall there is a good coverage of different aspects of perception based on the list of papers reviewed in our corpus.
-The perception of interaction with agent is the most commonly explored category, followed by the perception of agent's humanness.
-There are two aspects that are the least explored compared to the others relationships: competence within the perception of agent's ability, and intimacy within the perception of social connection with agent.
-This may be due to the controlled lab settings for the experiments, where participants are given the scenarios for interaction.
+There is good coverage across the four perception categories based on our reviewed corpus.
+The perception category of interaction with agent is most commonly explored in literature, followed by the perception category of sociability with agent.
+Some aspects of perception are under explored in literature, such as the perceived intimacy with a CA or the perceived competence of an agent.
+This may be due to the controlled lab settings for experiments, where participants are given defined scenarios for interaction.
 This type of environment is not conducive to forming relationships with a conversational partner, as noted by Linnerman et al.
 in their discussions \cite{linnemann2018can}\cmt{[15]}.
-The same factor could impact the assessment of agent's competence, as the users may not feel like they have the expertise to assess their perceptions.
+The same factor could impact the assessment of an agent's perceived competence, as users may not feel comfortable assessing the expertise of their conversational partner.
 
-\input{tables/tbl-perceptions}
 \input{tables/tbl-conversation_architecture}
@@
 
-As shown in \autoref{tbl:conversation_architecture}, we defined four categories for conversation architecture across 12 different elements.
+As shown in \autoref{tbl:conversation_architecture}, we defined four categories for conversation architecture across 11 different elements.
 The details of each category and element are discussed below.
@@
 The category of \textbf{dialog strategy} refers to the approach used by a conversational agent to engage in a dialogue with a user, which includes the use of social dialogs, agent-initiated content, and adding delays to responses.
-Specifically, the element of \textit{social dialogue} captures non-task related conversations with the user to build social connection, such as self-disclosure \cite{lee2020hear}\cmt{[23]} and small talk like chitchats \cite{lubold2016effects, volkel2021manipulating}\cmt{[86][68]}.
-The element of \textit{initiative} captures utterances that are initiated by the agent without direct prompts from the user.
-For example, the agent is taking the initiative to proactively repair the conversation with a user \cite{ashktorab2019resilient, cuadra2021my}\cmt{[88][67]}, or actively elicit feedback from users \cite{xiao2021let}\cmt{[73]}.
+Specifically, the element of \textit{social dialogue} captures the use of non-task related conversations with users to build social connections, such as using self-disclosure \cite{lee2020hear}\cmt{[23]} and small talk \cite{lubold2016effects, volkel2021manipulating}\cmt{[86][68]}.
+The element of \textit{initiative} captures utterances that are initiated by an agent without direct prompts from users.
+For example, this element includes CAs designed to proactively initiate conversation repair \cite{ashktorab2019resilient, cuadra2021my}\cmt{[88][67]}, or actively elicit feedback from users \cite{xiao2021let}\cmt{[73]}.
 Lastly, \textit{response delay} refers to the tactic of deliberately delaying for a certain period of time before an agent responds to users \cite{gnewuch2018faster, gnewuch2022opposing}\cmt{[19][20]}.
@@
 
-\textbf{Content affectiveness} refers to the conversational agent's use of language to convey emotions or to elicit emotions from users.
-The architecture element of \textit{affective language} captures the injection of emotional words or phrases into the agent's utterance, such as affective expressions \cite{seeger2021chatbots, yang2017perceived, zhu2022effects}\cmt{[35][44][26]}, sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}, and encouraging words \cite{healey2013relating}\cmt{[39]}.
+\textbf{Content affectiveness} category refers to the conversational agent's use of language to convey emotions or to elicit emotions from users.
+The  element of \textit{affective language} captures injections of emotional words or phrases into an agent's utterances, such as the use of affective expressions \cite{seeger2021chatbots, yang2017perceived, zhu2022effects}\cmt{[35][44][26]}, sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}, and encouraging words \cite{healey2013relating}\cmt{[39]}.
 The other element in this category, \textit{humour}, captures an agent's attempt to include jokes in its dialog.
@@
 how something is said).
-The element of \textit{formality} describes the linguistic style used by the conversational agent, whether it is formal vs.
-casual, such as using honorific expressions to address users \cite{ouchi2019should}\cmt{[59]}.
-\textit{Alignment} captures the degree that the agent aligns its utterances to the users, such as lexical alignment on the content and structural of the sentences \cite{huiyang2022improving, linnemann2018can}\cmt{[17][15]}, as well as referring and agreeing with users' utterances \cite{volkel2021examining}\cmt{[69]}.
+The element of \textit{formality} describes the linguistic style used by a conversational agent, such as using formal language like honorific expressions to address users \cite{ouchi2019should}\cmt{[59]}.
+\textit{Alignment} captures the degree that an agent matches its utterances to users, such as being lexical aligned with the content and structure of users' sentences \cite{huiyang2022improving, linnemann2018can}\cmt{[17][15]}, as well as agreement with users \cite{volkel2021examining}\cmt{[69]}.
 Lastly, the element of \textit{elaborateness} captures the sentence complexity and length of agents' utterances.
-For example, Roy et al.
-explored the differences in perception for variations in elaborateness such as ``\textit{Cloudly, possibility of snow, high: 4, low: -10}'' vs ``\textit{Today will be cloudy, with a high of 4 and a low of -10.
-Snow is predicted}'' \cite{roy2021users}\cmt{[71]}.
+For example, \citet{roy2021users}\cmt{[71]} explored the differences in perceptions for elaborateness variations such as ``\textit{Cloudy, possibility of snow, high: 4, low: -10}'' vs.
+``\textit{Today will be cloudy, with a high of 4 and a low of -10.
+Snow is predicted}''.
 
-Lastly, the category of \textbf{speech format} captures the non-verbal component of a conversational agent's utterances for both text and voice modalities. \textit{Disfluency} captures 
-the use of non-lexical utterances like filler words (``\textit{um, uh}'') \cite{hu2021enhancing, jeong2019exploring}\cmt{[56][10]}, or repetition of words within a sentence \cite{yang2021effect}\cmt{[72]}.
-It also includes the format of using typos \cite{westerman2019believe}\cmt{[9]} for text-based agents.
+Lastly, the category of \textbf{speech format} refers to the non-verbal component of a conversational agent's utterances for both text and voice modalities. \textit{Disfluency} captures 
+the use of non-lexical utterances like filler words (``\textit{um, uh}'') \cite{hu2021enhancing, jeong2019exploring}\cmt{[56][10]} or repetition of words within a sentence \cite{yang2021effect}\cmt{[72]}.
+It also includes the use of typos \cite{westerman2019believe}\cmt{[9]} for text-based agents.
 For voice-based agents specifically, the element of \textit{prosody} encompasses vocal qualities like pitch \cite{habler2019effects, jestin2022effects}\cmt{[63][81]}, speech rate \cite{choi2020nobody}\cmt{[54]}, and spoken accent \cite{feijoo2021effects}\cmt{[70]}.
@@
 Overall there are similar number of conversation architecture elements explored across the four categories of dialog strategy, content affectiveness, content style, and speech format.
-As for explorations related to different modalities of agents, there is a noticeable difference in the category of speech format, where architecture elements related to voice-based agents (n=15) are explored more than text-based agents (n=7).
-Looking across the 12 different elements, there is good coverage of studies on the impact of affective language and prosody cues on the perceptions of agents.
+Looking across the 11 different elements of conversation architecture, there is a good coverage of studies on the effect of affective language and prosody cues on the perceptions of agents.
 However, there are less studies exploring the effect of agent initiated content and response delay on the perception of agents.
-Specifically for the element of initiative under dialog strategy category, there is literature on conversation repairs \cite{komatani2010online, reinkemeier2022repair} and agent proactively sharing content with users \cite{dubiel2019inquisitive, zargham2022understanding}, but many of them did not not include assessments of perceptions of the CA.
+Specifically for the element of agent initiated content, we found various research on conversation repairs \cite{komatani2010online, reinkemeier2022repair} and agents proactively sharing content with users \cite{dubiel2019inquisitive, zargham2022understanding}, but many of them did not not include assessments of users' perceptions of CAs.
 This may be due to the fact that the usage of agent-initiated content is relatively new, as CA interactions have historically been driven by users.
 As such, current research is focused on the functional aspects of agents initiating contents instead of exploring the perceptions of agents.
-As for response delay, there are indications that this element is under-explored in literature.
-Only 4 studies in our reviewed corpus used an agent with response delay, and the majority of these publications were written by the same authors.
+As for response delay, our research suggests this element is under-explored in literature, as only 4 studies in our reviewed corpus examined agents using response delay, with majority of these publications published by the same authors.
 
@@
 
-There are 183 identified relationships between perceptions of agents and conversation architecture out of the 265 explored connections that are included in our synthesized framework (\autoref{fig:heatmap_identified}).
-To compare the number of identified relationships vs.
+Our synthesized framework (\autoref{fig:heatmap_identified}) includes 183 identified relationships out of the 265 explored connections between perceptions of agents and conversation architecture elements.
+The differences between explored connections and identified relationships are shown as a side-by-side comparison in \autoref{fig:heatmap_coverage}, with detailed discussions in the subsections below.
+%To compare the number of identified relationships vs.
 the explored connections in literature, \autoref{fig:heatmap_coverage} shows a side-by-side comparison between the two.
@@
 
-While the number of papers studying CAs with voice (n=27) vs.
-text (n=30) modalities is not significantly different, there are some interesting patterns we found with regards to the modalities of the identified relationships between perceptions of agents and conversation architecture.
-Overall, we confirmed the pattern found earlier that there are more conversation architecture elements explored related to voice vs.
-text in the speech format category.
-Because there are smaller number of text-based CAs using speech format elements, we also observed significantly less number of relationships between text-based CA across all perceptions of agents.
-other interesting findings related to modality are discussed later in this paper.
+%While the number of papers studying CAs with voice (n=27) vs.
+text (n=30) modalities is not significantly different, there are some interesting patterns with regards to the modalities of the identified relationships between perceptions of agents and conversation architecture.
+Overall, there are more explored conversation architecture elements related to voice-based CAs as compared to text-based CAs in the speech format category.
+Because there are smaller number of text-based CAs using speech format elements in our corpus, we also observed significantly smaller number of relationships between text-based CA across all perceptions of agents.
+Other interesting findings related to modality are discussed later in this paper.
 
@@
 The effects of conversation architecture elements on the perception of interaction with agent is the most explored connections in the corpus (n=97).
-Out of these explored connections, the majority of them (n=66) discovered a relationship between aspects of perception related to the perception of interaction with agent related to the studied architecture element.
+Out of these explored connections, the majority of them (n=66) discovered relationships between the perceptions of interaction with agent related to the studied architecture element.
 Looking at the difference between modalities, we noticed more voice-based agents (n=25) resulted in null relationships compared to text-based agents (n=6).
-The conversation architecture element of \textit{alignment} contributed the most to the null results for voice-based agents, with 9 out of 11 explored connections did not find any relationships related the perception of interaction with agents.
+The conversation architecture element of \textit{alignment} contributed the most to the null results for voice-based agents, with 9 out of 11 explored connections not finding any relationships related the perception of interaction with agents.
 
-Across the aspects for the perception of interaction, both usability and engagement were assessed frequently in the reviewed literature, with conversation architecture having effects on these perception aspects across all architecture element categories.
-The aspect of satisfaction was used in some studies to evaluate perception but it is not used as often as engagement or usability.
-Several papers that assessed user satisfactions were conversation agents within the transaction context, especially within the customer service domain (e.g.
+Across the aspects for the perception of interaction, both usability and engagement were assessed frequently in our reviewed corpus, with speech variations having effects on both perception aspects across all conversation architecture element categories.
+The perception aspect of user satisfaction is commonly used to evaluate conversational agents within the customer service domain answering transactional inquiries (e.g.
 \cite{diederich2019emulating, elsholz2019exploring, gnewuch2018faster}\cmt{[25][61][19]}).
 
-The category of conversation architecture elements with the most identified relationships to perceptions of interaction is content style.
+The category of conversation architecture with the most identified relationships to perceptions of interaction is content style.
 Specifically for the element of \textit{elaborateness}, users found the use of full sentences more useful than keyword only \cite{haas2022keep, roy2021users}\cmt{[78][71]}.
 Otherwise, the effect of an agent's elaborateness on user's perception of interaction depends on the user's preference \cite{miehle2018exploring}\cmt{[51]}, as well as the topic of discussion \cite{haas2022keep}\cmt{[78]}.
-As for \textit{formality}, various studies reported significant differences in perceptions of interaction between using casual vs.
+As for \textit{formality}, various studies reported significant differences in the perceptions of interaction between CAs using casual vs.
 formal styles.
-Some users experienced higher engagement with agent interacting with the casual style of the conversation \cite{cox2022does}\cmt{[27]}, while in another study users reported the formal language style as less engaging as it is boring \cite{kim2019comparing}\cmt{[89]}.
+However, there are mixed results on the effects on formality, as some users experienced higher engagement interacting with agent using casual style of conversation \cite{cox2022does}\cmt{[27]}, while in another study users found the CA using formal language style as less engaging as it is boring \cite{kim2019comparing}\cmt{[89]}.
 
-The speech format of an agent also resulted in a high number of identified relationships with the perception of interaction with CAs, with majority of the explored connections resulted in effects between the perception aspects and architecture elements.
+There are also a number of papers in our reviewed corpus exploring the effect of speech format elements on the perception of interaction with CAs, with many of them finding significant relationships between them.
 The element with the most identified relationships is \textit{prosody}.
-For example, studies found that a CA's expressiveness in vocal cues increased participants' engagement ratings \cite{zhu2022effects}\cmt{[26]}, and different pitches of voice affect users' perception of engagement and usability \cite{chan2021kinvoices, habler2019effects}\cmt{[74][63]}.
+For instance, studies found that a CA's expressiveness in vocal cues increased participants' engagement ratings \cite{zhu2022effects}\cmt{[26]}, and different pitches of voice affect users' perception of engagement and usability \cite{chan2021kinvoices, habler2019effects}\cmt{[74][63]}.
 
 Dialog strategy and content affectiveness categories of conversation architecture did not have as many identified relationships with perceptions of interaction.
-It is worth noting the effect of using the \textit{initiative} element, as CAs that use self-initiated content are perceived as more efficient and higher quality of interaction (e.g.
-\cite{cuadra2021my}\cmt{[67]}).
-Also, some studies have discovered conflicting effects between different perception aspects of interaction for CAs using \textit{social dialog}, as users enjoyed the conversation using social talk \cite{lee2020hear, roy2021users}\cmt{[23][71]}, but perceived the CA as less efficient \cite{roy2021users}\cmt{[71]}.
+It is worth noting the effect of using the \textit{initiative} element, as CAs that use self-initiated content are perceived as more efficient and higher quality of interaction \cite{cuadra2021my}\cmt{[67]}.
+Also, some studies have discovered conflicting effects between different perception aspects of interaction for CAs using \textit{social dialog}.
+One such example is users enjoying of the conversation with CAs using social talk \cite{lee2020hear, roy2021users}\cmt{[23][71]}, but perceiving the agent as less efficient \cite{roy2021users}\cmt{[71]}.
 
@@
 The effects of conversation architecture elements on the perception of agent's ability is the least explored connection in the corpus (n=39).
-Out of these explored connections, the majority of them (n=30) found relationships between the studied architecture element and the perceptions of agent's ability.
+Out of these explored connections, the majority of them (n=30) found relationships between the studied speech element and the perceptions of agent's ability.
 There are no notable differences between the text and voice modalities of CAs for either explored connections or the identified relationships.
 
-Aspects within the perception of agent's ability had similar number of identified relationships across intelligence, competence and credibility.
+Perception aspects of agent's ability had similar number of identified relationships with speech elements across intelligence, competence and credibility.
 Our review revealed that the perceived ability of a CA is also dependent on other influencing factors in addition to conversation architecture elements.
-Volkel et al.
-\cite{kraus2020effects}\cmt{[64]} found that the perception of competence of a proactive CA is dependent on task difficulty \cite{kraus2020effects}\cmt{[64]}.
+For instance, \citet{kraus2020effects}\cmt{[64]} found that the perception of competence of a proactive CA is dependent on task difficulty.
 Also, the perception of intelligence for an agent using fillers depended on the context of the conversation, as the filler-speaking agent was perceived as less intelligent in task-oriented conditions, but was seen as slightly more intelligent in social-oriented conditions \cite{jeong2019exploring}\cmt{[10]}.
 
-Out of the explored conversation architecture elements, \textit{prosody} had relationships identified with aspects across the perception category of agent's ability.
+The conversation architecture element of \textit{prosody} has relationships identified with each perception aspect of an agent's ability.
 For example, Chan et al.
@@
 Also, the style of speech used by an agent affects the perception of appropriateness of tone, which is an aspect of the perceived competence of an agent \cite{misu2011toward}\cmt{[83]}.
-Different content styles of \textit{formality} also impacts the perceived competence of an agent \cite{cox2022does, jestin2022effects}\cmt{[27][81]}.
-Specifically related to perceived credibility of an agent, being \textit{lexically aligned} with the user resulted improved the rating of trustworthiness of an agent \cite{hoegen2019end, linnemann2018can}\cmt{[31][15]}.
-There were mixed results on the use of emoticons within the \textit{text formatting} element.
-One study found the chatbot using emoticons as less trustworthy \cite{wilhelm2022keep}\cmt{[28]}, while another study found that users assigned higher scores for confidence to the agent using emojis \cite{fadhil2018effect}\cmt{[52]}.
+Different content styles of \textit{formality} used by a CA also impacts its perceived competence \cite{cox2022does, jestin2022effects}\cmt{[27][81]}.
+Related to the perception aspect of credibility, being \textit{lexically aligned} with the user improved the rating of trustworthiness of an agent \cite{hoegen2019end, linnemann2018can}\cmt{[31][15]}.
+There are some mixed results on the use of emoticons within the \textit{text formatting} element.
+One study found that chatbots using emoticons as less trustworthy \cite{wilhelm2022keep}\cmt{[28]}, while another study found that users assigned higher scores of confidence to the agent using emojis \cite{fadhil2018effect}\cmt{[52]}.
 
-There are several conversation architecture elements with little to no explorations to the perception of agent's ability.
+There are several conversation architecture elements with little to no explorations related to the perception of agent's ability.
 Specifically, both categories of dialog strategy and content affectiveness are minimally explored in our reviewed corpus, with no explored connections with \textit{response delay} and only one or two connections explored for \textit{social dialog} and \textit{humour}.
-While the content style category had coverage in some aspects of perceived abilities, it is worth noting that \textit{elaborateness} did not have any explored connections with perceived ability of agents.
-Further research in these areas is needed to fill these gaps in understanding.
+While some speech elements within the content style category have been evaluated for agents' perceived abilities, it is worth noting that the element of \textit{elaborateness} did not have any explored connections with perceived ability of agents.
+Further research in these areas is needed to close these knowledge gaps.
 
@@
 
-The perception of agent's humanness is the second most explored category within our reviewed corpus (n=64), with majority of the connections identified relationship between the studied conversation architecture elements and the anthropomorphized perceptions of agent (n=49).
+The perception of agent's sociability is the second most explored category within our reviewed corpus (n=64), with majority of the connections found relationships between the studied conversation architecture elements and perceptions of agent (n=49).
 Interestingly, studies explored more perceptions of sociability with agent related to voice-based CAs (n=40) compared to text-based CAs (n=24), potentially due to the assumption that interactions with text-based agents are perceived as less personal and more formal \cite{kocielnik2018designing}.
-There are some mixed results for voice-based CAs, as 12 out of the 28 connections did not find any significant results.
+There are some mixed results for voice-based CAs, as 12 out of the 28 explored connections did not find any significant results.
 Drilling down to the specific elements, we noticed that the use of \textit{alignment} in voice-based agents did not effect the perception of sociability with agent \cite{healey2013relating, linnemann2018can}\cmt{[39][15]}.
-We didn't have data on text-based agents' perceived social connections with users to compare with voice-based agents, as the studies using alignment and text modality in our corpus did not assess this aspect category of perception.
+As there are no papers in our reviewed corpus studying the effect of text-based agents using alignment on the perceptions of sociability, we were not able to compare the effect of alignment between modalities.
 
-Across the aspects in this perception category, conversation tone had the most number of identified relationship (n=27) with the perceived social connection with CAs, followed by the aspect of social presence (n=17).
-There are only 5 relationships found that are linked to the perception aspect of intimacy.
-One reason for this is half of the explored connections did not have any effect on the perception of sociability with agent, such as the use of capitalization \cite{westerman2019believe}\cmt{[9]}, lexical alignment \cite{linnemann2018can}\cmt{[15]}, or social talk \cite{lubold2016effects}\cmt{[86]}.
-For the perception aspect of social presence, we noticed a gap in the exploration of conversation architecture elements of formality, alignment, and elaborateness in the content style category, as there are no papers explored at this intersection.
+Across the aspects in this perception category, perceived conversation tone has the most number of identified relationship (n=27), followed by perceived social presence (n=17).
+There are only 5 relationships found between speech elements and perceived intimacy.
+One reason for this is half of the explored connections with speech elements did not have any effect on the perception of sociability with agent, such as the use of capitalization \cite{westerman2019believe}\cmt{[9]}, lexical alignment \cite{linnemann2018can}\cmt{[15]}, and social talk \cite{lubold2016effects}\cmt{[86]}.
+For the perception aspect of social presence, we noticed a gap exploring elements in the content style category (formality, alignment, elaborateness), as there are no connections explored at this intersection.
 
-Looking at the different categories of conversation architecture elements, the heatmap (\autoref{fig:heatmap_identified}) shows that there are not many relationships in content style category that are related to the perceived sociability with CAs in general, with most of the discovered effects concentrated at the intersection of \textit{formality} and conversation tone.
+Looking at the different categories of conversation architecture elements, the heatmap (\autoref{fig:heatmap_identified}) shows that there are not many relationships in content style category of conversation architecture that are related to the aspects of perceived sociability with CAs.
+Most of the identified effects are concentrated at the intersection of \textit{formality} and perceived conversation tone.
 Studies have found that CAs using casual style of conversation are perceived as warm, empathetic and friendly \cite{jestin2022effects, kim2019comparing}\cmt{[81][89]}, while CAs using formal style of conversation are perceived as polite but lacks empathy \cite{cox2022does}\cmt{[27]}.
-The rest of the architecture elements and perception aspects of sociability are minimally explored in literature, which indicates the need for more research in this area.
+The rest of the speech elements related to the perceptions of sociability are minimally explored in literature, indicating the need for more research in this area.
 
-There are a few specific conversation architecture elements that had more identified relationships with perceptions of sociability with agent.
-Specifically, CAs using of \textit{affective language} were perceived to be more empathetic \cite{daher2020empathic, diederich2019emulating, yang2017perceived}\cmt{[58][25][44]} and emotionally expressive \cite{zhu2022effects}\cmt{[26]}, as well as being more emotional connected with their users \cite{lee2019s, lubis2019positive}\cmt{[55][43]}.
+There are a few specific conversation architecture elements that has more identified relationships with perceptions of sociability with agent.
+Specifically, CAs using \textit{affective language} are perceived to be more empathetic \cite{daher2020empathic, diederich2019emulating, yang2017perceived}\cmt{[58][25][44]} and emotionally expressive \cite{zhu2022effects}\cmt{[26]}, as well as being more emotional connected with their users \cite{lee2019s, lubis2019positive}\cmt{[55][43]}.
 Also, different variations of a voice-based CA's \textit{prosody} have effects on the perceived sociability with agent, such as an agent using expressive prosody is assessed as more intimate and more similar with the user \cite{kim2020can}\cmt{[24]}.
-Lastly, the conversation architecture element of \textit{humour} has identified relationships across the social connection category of perception.
-Clark et al.
-\cite{clark2019makes} found that humour is an important conversational characteristic for human-human interactions, but viewed as a novelty feature for human-agent conversations.
-However, in our review we found that humor has effects on human-agent relationships, as humorous agents are rated as more friendly, intimate, and similar by users compared to non-humorous agents \cite{go2021conversational, khooshabeh2011does}\cmt{[80][37]}.
+Lastly, the conversation architecture element of \textit{humour} has identified relationships across aspects of perceived sociability with CAs.
+Our review found that humor has effects on human-agent relationships, as humorous agents are rated as more friendly, intimate, and similar by users compared to non-humorous agents \cite{go2021conversational, khooshabeh2011does}\cmt{[80][37]}.
+This is contrary to \citet{clark2019makes}'s findings that while humour is an important conversational characteristic for human-human interactions, it is viewed as a novelty feature for human-agent conversations.
 
@@
 
-There are 55 explored connections between conversation architecture elements and the perception of sociability with agents, with majority of them (n=38) finding identified relationships in literature.
+There are 55 explored connections between conversation architecture elements and the perception of sociability with agents, with majority of them (n=38) discovering relationships in literature.
 There are significantly more explorations for voice-based agents (n=39) as compared to text-based agents (n=16).
@@
 Out of the 39 explored connections for voice-based agents, 14 of them did not result in any relationships.
-This is especially evident in the architecture element of \textit{affective language} for voice-based agents, as most of the connections resulted in null relationships.
+This is especially evident in the speech element of \textit{affective language} for voice-based agents, as most of the connections resulted in null relationships.
 For example, when comparing the ratings of human-likeness or likeability for a speech agent employing expressive words to the one not using any, Zhu et al \cite{zhu2022effects}\cmt{[26]} were unable to detect any statistically significant differences in both of the observation study and interaction study.
@@
 Across the aspects in this perception category, both human-likeness and personality traits have relationships with almost all the conversation architecture elements.
-Specifically for the use of \textit{prosody} elements, our review found some opposing effects on the perception of the agent's humanness.
-In the case of Chan et al's study \cite{chan2021kinvoices}\cmt{[74]}, participated rated the agent using kin voices as significantly more likeable compared to the generic voices, but it was perceived as eerie.
-This may be a warning indicator to watch out for the uncanny valley effect \cite{mori2012uncanny} and advise CA designers to carefully select conversation architecture elements to elicit anthropomorphized perceptions.
+Specifically for the use of \textit{prosody} in CAs, our review found some opposing effects on the perception of the agent's humanness.
+In the case of Chan et al's study \cite{chan2021kinvoices}\cmt{[74]}, participants rated the agent using kin voices as significantly more likeable compared to the generic voices, but it was perceived as eerie.
+This may be a warning indicator to beware of the uncanny valley effect \cite{mori2012uncanny} when designing conversation architecture elements to elicit anthropomorphized perceptions from users.
 
 There are a few notable conversation architecture elements related to the perceived humanness of conversational agents.
-The use of \textit{prosody} such as varying pitch, intonation and speech rate has more identified relationships with the perceived personality traits of an agent as compared to the perceived human-likeness, especially on the aspect of likeability \cite{choi2020nobody, jestin2022effects, misu2011toward}\cmt{[54][81][83]}.
-For the architecture elements of \textit{disfluency}, the type of impact on the perception of humanness depended on the context of the conversation.
+The element of \textit{prosody} such as varying pitch, intonation and speech rate has more identified relationships with perceived personality traits of an agent as compared to perceived human-likeness, especially on the perception of likeability for an agent \cite{choi2020nobody, jestin2022effects, misu2011toward}\cmt{[54][81][83]}.
+For the element of \textit{disfluency}, the effect on perceived humanness depended on the context of the conversation.
 Studies have found that participants perceived the filler-condition agent as more likeable in the social-oriented situation, but did not find the same effect in task-oriented situations \cite{jeong2019exploring, wester2015artificial}\cmt{[10][14]}.
-The use of \textit{alignment} in an agent had a number of identified relationships with the perception of personality traits, with some studies finding CAs that are lexically aligned with a user are more likeable \cite{huiyang2022improving, linnemann2018can}\cmt{[17][15]}.
+The use of \textit{alignment} in an agent has a number of identified relationships with the perception of personality traits of an agent, with some studies finding CAs that are lexically aligned with a user are more likeable \cite{huiyang2022improving, linnemann2018can}\cmt{[17][15]}.

### 2023-02-27 sections/5-discussion.tex
submitted version to CUI 2023

@@
 We found a diversity of approaches used to assess perceptions of agents in our reviewed corpus.
-While we made our best efforts to group perceptions used in literature based on similarity with each other, the inconsistent and composite nature of these perception assessments makes it challenging to synthesize them into a framework that contains homogeneous components in each perception aspect that can be compared with each other.
+While we made our best efforts to group perceptions used in literature based on similarity with each other, the inconsistent and composite nature of these perception assessments makes it challenging to synthesize them into a framework that contains homogeneous components in each perception aspect that are comparable with each other.
 
@@
 In Diedrech et al.'s study \cite{diederich2019emulating}\cmt{[25]}, empathy is assessed by asking users whether the CA is giving users individual or personal attention.
-In another study that also studies the perception of empathy \cite{daher2020empathic}\cmt{[58]}, the RoPE Scale \cite{charrier2019rope} is used with questions like "the robot cares about my feelings" or "the robot comforts me when I am upset." These two different evaluations of empathy seem to have different underlying meanings, one assessing the personalization aspect of CAs, while the other is assessing the emotional aspect of CAs.
+In another study that also assesses the perception of empathy \cite{daher2020empathic}\cmt{[58]}, the RoPE Scale \cite{charrier2019rope} is used with questions like ``\textit{the robot cares about my feelings}'' or ``\textit{the robot comforts me when I am upset.}'' These evaluations of empathy seem to have different underlying meanings, one assessing the personalization aspect of CAs, while the other is assessing the emotional aspect of CAs.
 
@@
 These composite measures collapse multiple aspects of perception into one measurement, making it impossible to break down perceptions into more granular aspects for analysis.
-One such example is Ma et al's study \cite{ma2022ask}\cmt{[29]} on the different approaches for CAs to reply to users' uncertain queries.
-A single UX score is used to evaluate the users' perceptions, which composes of questions on whether the user thinks the CA's response is pleasing / trustworthy / natural / acceptable / shorten the distance between CA and the user.
-The UX score encompasses multiple aspects across several perception categories.
-While this study has found significant effect for the use of formal language on the user-rated UX score, it is not possible to understand how the details of formality is related to the perception categories of interaction (pleasing, acceptable), sociability (shorten the distance between CA and user), and humanness (natural, trustworthy).
-The humanness questionnaire from Holtgraves et al \cite{holtgraves2007perceiving} has a similar problem, evaluating across perception categories of interaction (responsiveness, engagement), ability (skillfulness), sociability (politeness), and humanness (human-likeness, thoughtfulness).
+One such example is Ma et al's study \cite{ma2022ask}\cmt{[29]} to evaluate different approaches used by CAs to reply to users' uncertain queries.
+A single UX score is used to evaluate users' perceptions, which composes of questions on whether the user thinks the CA's response is pleasing / trustworthy / natural / acceptable / shorten the distance between CA and the user.
+This UX score encompasses multiple aspects across several perception categories.
+While the study has found significant effect for the use of formal language on the user-rated UX score, it is not possible to understand how the details of formality is related to the perception categories of interaction (pleasing, acceptable), sociability (shorten the distance between CA and user), and humanness (natural, trustworthy).
+The humanness questionnaire from \citet{holtgraves2007perceiving} has a similar problem, evaluating across perception categories of interaction (responsiveness, engagement), ability (skillfulness), sociability (politeness), and humanness (human-likeness, thoughtfulness).
 
@@
 Lastly, the authors found that perceived humanness have a positive impact on perceived enjoyment, which lead to higher intention to adopt the CA.
-This study outlines that the perception aspects identified in this paper are not independent of each other.
+This study indicates that the perception aspects identified in this paper are not independent of each other.
 
 Correlations between perception aspects are discussed in a few of the papers we reviewed.
-One of the studies showed that the CA's perceived personality trait of agreeableness has an influence on the users' perception of credibility \cite{andrews2012system}\cmt{[38]}.
-Seeger et al's study found a similar correlation, where higher perceived anthropomorphism led to lower loss of trust \cite{seeger2021chatbots}\cmt{[35]}.
-There are also correlations between aspects found within the same perception category, such as a speech agent that is rated higher in perceived human-likeness was associated with higher likability ratings \cite{zhu2022effects}\cmt{[26]}.
-Also, within the perception category of social connection, one study found that social distance is positively related to perceived social attraction \cite{westerman2019believe}\cmt{[9]}.
+One of the studies showed that the CA's perceived anthropomorphized personality trait of agreeableness has an influence on the users' perception of credibility \cite{andrews2012system}\cmt{[38]}.
+\citet{seeger2021chatbots}\cmt{[35]}'s study found a similar correlation, where higher perceived anthropomorphism led to lower loss of perceived trust.
+There are also correlations between aspects within the same perception category, such as a speech agent that is rated higher in perceived human-likeness is associated with higher likability ratings \cite{zhu2022effects}\cmt{[26]}.
+Also, within the perception category of social connection, one study found that perceived social distance is positively related to perceived social attraction \cite{westerman2019believe}\cmt{[9]}.
 
@@
 There are a few \textit{under-explored areas} in our synthesized framework.
-The perception category of agent's ability has the least number of explored connections with conversation architecture compared to other perception categories.
+The perception category of agent's ability has the least number of explored connections with conversation architecture compared to the other perception categories.
 Specifically, more studies are needed to understand the effects of social dialog, response delay, humour and elaborateness on users' perceptions of agents' ability.
-For the perception category of sociability with agents, there is a general lack of explored connections with the conversation architecture category of content style, especially for alignment and elaborateness elements.
-Lastly, more studies on the effect of dialog strategy for conversation architecture elements of initiative and response delay on the perceptions of agents are needed.
+For the perception category of sociability with agents, there is a general lack of explored connections with conversation architecture elements in the content style category, especially for alignment and elaborateness.
+Lastly, more studies on the effect of using agent-initiated content and response delay on the perceptions of agents are needed.
 
 Some studies have discussed how differences in \textit{contextual factors} resulted in variations in the perceptions of agents while using similar conversation architecture elements.
-One of the factors is users' experience with CAs, as Gnewuch et al.
-\cite{gnewuch2018faster}\cmt{[19]} found that experienced users perceived the agent with a response delay as lower in social presence because it is seen as inefficient to wait for the CA to respond, but novice users perceived higher social presence conversing with the CAs using response delays because it is more similar to conversations with human partners \cite{gnewuch2018faster}\cmt{[19]}.
-User characteristics is another factor, as the perceived trustworthiness of a style-matching agent depended on users' own conversational style \cite{hoegen2019end}\cmt{[31]}.
+One of the factors is users' prior experiences with CAs, as \citet{gnewuch2018faster}\cmt{[19]} found that experienced users perceived the agent using response delay as lower in social presence because it is seen as inefficient to wait for the CA to respond, but novice users perceived higher social presence conversing with the CAs using response delays because it is more similar to conversations with human partners \cite{gnewuch2018faster}\cmt{[19]}.
+Another factor is users' characteristics, as the perceived trustworthiness of a style-matching agent depended on users' own conversational style \cite{hoegen2019end}\cmt{[31]}.
 Some other contextual factors that resulted in differences in perceptions of an agent include the purpose of conversation (e.g.
@@
 Several papers in our reviewed corpus incorporated composite elements in an agent, such as the design of an anthropomorphized chatbot using elements such as affective language, emoticons, and response delays to assess users' perceptions compared to a non-anthropomorphized chatbot \cite{seeger2021chatbots}\cmt{[35]}.
-In addition to exploring the combined effects of conversation architecture elements on users' perceptions, it would also be interesting to understand the relative importance of each element on perceptions.
-Some studies analyzed the effect of modifying conversation architecture elements individually, as well as their combined effect on user's perceptions (e.g.
+In addition to exploring the combined effects of conversation architecture elements on users' perceptions, it would also be interesting to understand the relative importance of each element on users' perceptions.
+This can be studied by analyzing the effect of modifying conversation architecture elements individually, as well as their combined effect on user's perceptions (e.g.
 \cite{habler2019effects, lubold2016effects, zhu2022effects}\cmt{[63][86][26]}).
-Specifically, Habler et al.
-\cite{habler2019effects}\cmt{[63]} found that the effect of social dialog is higher than the effect of prosody on the perception of agents.
+For instance, \citet{habler2019effects}\cmt{[63]} found that the effect of social dialog is larger than the effect of prosody on the perception of agents.
 
@@
 
-For the element of prosody, various studies in our corpus explored the effect of different pitches on the perceptions of agents.
+For the element of prosody, various studies explored the effect of different pitches on the perceptions of agents.
 Even in studies that are not explicitly analyzing the effect of different gendered voices in an agent, possible stereotypes may still exist in the study.
 Based on our reviewed corpus, studies found that lower pitches commonly associated with men are considered to be more desirable and authoritative but less friendly \cite{jestin2022effects, tolmeijer2021female}\cmt{[81][62]}.
-For Dubiel et al's study \cite{dubiel2020persuasive}\cmt{[60]}, the agent with a lower mean pitch was selected as the more persuasive voice.
-These results may be demonstrating users' unconscious bias to select a male-sounding voice as more persuasive and authoritative over female-sounding voices that are commonly associated with higher pitches.
+For \citet{dubiel2020persuasive}\cmt{[60]}'s study, the agent with a lower mean pitch was selected as the more persuasive voice.
+This result may be demonstrating users' unconscious bias to select a male-sounding voice as more persuasive and authoritative over female-sounding voices that are commonly associated with higher pitches.
 While some guidelines recommend designing agents to be androgynous to avoid gender stereotypes \cite{ruane2019conversational}, there are limitations in creating gender-ambiguous voices.
@@
 
-Studies have demonstrated that conversation architecture elements can be used to design perceptions of agents to make CAs more persuasive.
+Studies have demonstrated that conversation architecture elements can be used to design perceptions of agents to make CAs more persuasive \cite{dubiel2020persuasive}\cmt{[60]}.
 This opens up the ethical issue of influencing users' attitudes and behaviours through these persuasion techniques.
@@
 These perceptions contribute to the agent being more engaging and persuasive, therefore people are more likely to comply with its requests.
-Andrew et al \cite{andrews2012system}\cmt{[38]} found that tailoring the personality of the CA to users will positively impact an agent's persuasiveness.
-These persuasion techniques can be beneficial to help users achieve their goals, but can also be used for harmful actions, such as trying to get users to believe in false information.
+In another study, \citet{andrews2012system}\cmt{[38]} found that tailoring the personality of the CA to users will positively impact an agent's persuasiveness.
+These persuasion techniques can be beneficial to help users achieve their goals, but they can also be used for harmful actions, such as trying to get users to believe in false information.
 
@@
 Designing for perceptions of agents requires careful consideration of privacy issues including the sensitivity of the data, who has access to it, and how to protect against nefarious users.
-
-\subsection{Limitations}
-
-Our systematic literature review was limited to papers published in the ACM Digital Library between 2010 and 2022.
-We may have missed literature published outside this time period, as well as in other libraries.
-Also, most of the studies in our corpus are based on lab experiments using short interactions with users.
-The generalizability of these findings needs to be verified through longer-term engagements with conversational agents deployed in real-world situations.
-Lastly, research without empirical studies on the perception of agents is excluded based on our selection criteria.
-We may have missed some influential findings in these papers.
-%To better understand the relationships between conversation architecture elements and the perceptions of agents, we plan to conduct future reviews in literature and user studies to understand their real-world impacts.

### 2023-02-27 sections/6-conclusion.tex
submitted version to CUI 2023

@@
 In this paper, we discussed the results of a systematic review of existing literature published in the ACM Digital Library on the effect of conversation architecture elements on the perceptions of CAs.
-Through our synthesis of 57 papers in our corpus, we present a framework outlining the relationships between elements of agents’ conversation architecture (dialog strategy, content affectiveness, content style and speech format) and aspects of users’ perception (interaction, ability, sociability and humanness).
+Through the synthesis of 57 papers in our corpus, we present a framework outlining the relationships between elements of agents’ conversation architecture (dialog strategy, content affectiveness, content style and speech format) and aspects of users’ perception (interaction, ability, sociability and humanness).
 During our analysis, we found the need for consistent protocols in evaluating perceptions of agents, as measurements are inconsistent across studies.
 Further research is needed to investigate the under-explored areas in the framework, the relationship across perception aspects, the influence of contextual factors, and the effect of composite conversation architecture elements on users' perceptions.
-While our research contribute to the design conversation architecture to orchestrate specific perceptions of agent, we urge designers to incorporate ethical perspectives into their design considerations.
+While our research contribute to the design of conversation architecture to orchestrate specific perceptions of agent, we urge designers to incorporate ethical perspectives into their design considerations.

### 2023-02-27 tables/tbl-conversation_architecture.tex
submitted version to CUI 2023

@@
 
-\begin{table*}[h]
+\begin{table*}[t]
+
+\caption{Categories of the conversation architecture elements with examples and related papers identified from our review.}
+\Description{This table categorizes conversation architecture elements into four categories, provides some examples for the element, and shows the number of papers as well as references to the papers in our reviewed corpus.
+The first category is dialog strategy, which contains the elements of social dialog, initiative and response delay.
+The second category is content affectiveness, which contains the elements of affective language and humour.
+The third category is content style, which contains the elements of formality, alignment and elaborateness.
+The fourth category is speech format, which contains the elements of prosody, disfluency, and text formatting.}
 \resizebox{\textwidth}{!}{
@@
 }
-\caption{Conversation architecture elements}
-\Description{This table categorizes conversation architecture elements into four categories,  provide some examples for the element, and show the number of papers as well as references to the papers in our reviewed corpus.
-The first category is dialog strategy, which contains the elements of social dialog, initiative and response delay.
-The second category is content affectiveness, which contains the elements of affective language and humour.
-The third category is content style, which contains the elements of formality, alignment and elaborateness.
-The fourth category is speech format, which contains the elements of prosody, disfluency, and text formatting.}
 \label{tbl:conversation_architecture}

### 2023-06-06 paper.tex
submitted version to CUI 2023
finalized copy uploaded to TAPS

@@
 %% The first command in your LaTeX source must be the \documentclass command.
-\documentclass[sigconf,screen,review, anonymous]{config/acmart}
+\documentclass[sigconf,screen]{config/acmart}
 
-\usepackage[linewidth=1pt]{mdframed}
+%\usepackage[linewidth=1pt]{mdframed}
 \usepackage{lipsum}
@@
 \usepackage{makecell} 
+\usepackage{stfloats}
+\usepackage{longtable}
 
 \newcommand{\cmt}[1]{}%{\ignorespaces}
+
+\usepackage{soul}
+\usepackage{color}
+\newcommand{\hlrev}[1]{{\sethlcolor{yellow}\hl{#1}}}
 
@@
 
+\copyrightyear{2023} 
+\acmYear{2023} 
+\setcopyright{acmlicensed}\acmConference[CUI '23]{ACM conference on Conversational User Interfaces}{July 19--21, 2023}{Eindhoven, Netherlands}
+\acmBooktitle{ACM conference on Conversational User Interfaces (CUI '23), July 19--21, 2023, Eindhoven, Netherlands}
+\acmPrice{15.00}
+\acmDOI{10.1145/3571884.3597139}
+\acmISBN{979-8-4007-0014-9/23/07}
+
 %% Rights management information.  This information is sent to you
@@
 %% complete the rights form.
-\setcopyright{acmcopyright}
-\copyrightyear{2023}
-\acmYear{2023}
-\acmDOI{XXXXXXX.XXXXXXX}
+%\setcopyright{acmcopyright}
+%\copyrightyear{2023}
+%\acmYear{2023}
+%\acmDOI{3571884.3597139}
 
 %% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[Conference acronym 'XX]{Make sure to enter the correct
-  conference title from your rights confirmation email}{June 03--05,
-  2018}{Woodstock, NY}
+%\acmConference[Conference acronym 'XX]{Make sure to enter the correct
+%  conference title from your rights confirmation email}{June 03--05,
+%  2018}{Woodstock, NY}
 %
@@
 %  June 03--05, 2018, Woodstock, NY} 
-\acmPrice{15.00}
-\acmISBN{978-1-4503-XXXX-X/18/06}
+%\acmPrice{15.00}
+%\acmISBN{978-1-4503-XXXX-X/18/06}
 
@@
 %% article.
+
 \begin{abstract}
@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{conversational agents, user perception, conversation architecture, anthropomorphized perceptions}
+\keywords{conversational agents, natural language interface, chatbots, virtual assistants, user perceptions, anthropomorphized perceptions, conversation architecture, speech variations}
 
@@
 \begin{acks}
-TBD
+This work was supported by NAVER Corp.
 \end{acks}
@@
 
+\input{sections/7-appendix}
+
 \end{document}

### 2023-06-06 sections/1-introduction.tex
finalized copy uploaded to TAPS

@@
 Conversational agents (CAs), such as Amazon Alexa or Google Assistant, are designed to interact with humans using natural language through voice or text modalities.
-Since these agents communicate in natural language, \textit{conversation architecture}---what and how a CA says---affects users' perceptions of agents and, in turn, the effectiveness of their interactions with users \cite{knijnenburg2016inferring, seeger2021chatbots}, i.e.
+Since these agents communicate in natural language, the effectiveness of interactions between users and conversational agents in achieving users' goals depend heavily on the \textit{conversation architecture}, which refers to the content and manner of communication utilized by the agents \mbox{\cite{knijnenburg2016inferring, seeger2021chatbots}}.
+%\textit{conversation architecture}---what and how a CA says---affects users' perceptions of agents and, in turn, the effectiveness of their interactions with users \cite{knijnenburg2016inferring, seeger2021chatbots}, i.e.
 supporting users in achieving their goals.
-For instance, previous research suggests that there is a relationship between CAs' conversation architecture and how users perceive these agents %.
+%For instance, p
+Previous research suggests that there is a relationship between CAs' conversation architecture and how users perceive these agents %.
 %While various studies investigated how some elements of conversation architecture affect users' perceptions of agents~
 (e.g.,~\cite{clark2019state, feine2019taxonomy, finch2020towards}).  
-However, there is currently a lack of systematic understanding of these relationships, i.e.
-what elements of conversation architecture are impactful for users' perceptions and how.
-Specifically, while various studies investigated how some elements of conversation architecture affect aspects of users' perceptions or discussed the speech specifics of agents as part of a broader analysis of the state of research \cite{clark2019state,feine2019taxonomy}, there is no comprehensive analysis of %research specifically for
+%\hlrev{However, there is currently a lack of overall comprehension of the relationship between users' perceptions and conversation architecture elements, specifically which elements are significant and how they impact these perceptions.}
+%However, there is currently a lack of systematic understanding of these relationships, i.e.
+what elements of conversation architecture are impactful for users' perceptions and how they impact these perceptions.
+While various studies investigated how some elements of conversation architecture affect aspects of users' perceptions or discussed the speech specifics of agents as part of a broader analysis of the state of research \cite{clark2019state,feine2019taxonomy}, there is no comprehensive analysis of %research specifically for
 conversation architecture elements that are relevant to user perceptions. 
-Yet, this systematic understanding is essential for guiding the design of conversation architecture, which would allow us to both predict and develop users' appropriate perceptions of agents.
+As such, this paper aims to provide a systematic understanding of the effect of conversation architecture elements on users' perceptions of conversational agents.
+Such an understanding is essential for guiding the design of conversation architecture, which would allow us to both predict and develop users' appropriate perceptions of agents.
 
@@
 %These research gaps related to the paucity of knowledge on synthesizing the effect of speech specifics on perceptions of CAs as well as the lack of systematic understanding on the elements of conversation architecture and perceptions of agents
-To address this gap, %in this paper, we
+
+%To address this gap, %in this paper, we
 %we aim to understand how to design conversation architecture in order to orchestrate perceptions of conversational agents.
 %First, we 
-we explore the following research questions in this paper: \textbf{(RQ1) what aspects of users' perceptions of agents have been explored in relation to the effects of conversation architecture elements?}, \textbf{(RQ2) what elements of conversation architecture are relevant to users' perceptions of agents?}, and \textbf{(RQ3) what is known about the specifics of these relationships between conversation architecture elements and the perceptions of CAs?}
+To gain this systematic understanding, we explored the following research questions in this paper: \textbf{(RQ1) what aspects of users' perceptions of agents have been explored in relation to the effects of conversation architecture elements?}, \textbf{(RQ2) what elements of conversation architecture are relevant to users' perceptions of agents?}, and \textbf{(RQ3) what is known about the specifics of these relationships between conversation architecture elements and the perceptions of CAs?}
 %While there are various elements of conversation architecture used in a CA's utterances, we don't have a systematic understanding of them.
 This leads to our second research question: \textbf{(RQ2) what elements of conversation architecture are relevant to users' perceptions of agents?} Lastly, we want to understand the effect of conversation architecture on perceptions of agent, specifically: \textbf{(RQ3) what are the relationships between conversation architecture elements and the perceptions of CAs?}
-To answer these questions, we performed a comprehensive review of the existing literature published from 2010 to 2022 and synthesized the effect of conversation architecture elements on the perceptions of CAs based on the final dataset of 57 relevant papers (\autoref{fig:heatmap_identified}).
+In order to answer these questions, we performed a comprehensive review of the existing literature published from 2010 to 2022 and synthesized the effect of conversation architecture elements on the perceptions of CAs based on the final dataset of 57 relevant papers (\autoref{fig:heatmap_identified}).
 Based on this review, we grouped the perceptions of agents that were shown to be affected by conversation architecture into four categories (interaction, ability, sociability and humanness) and eleven aspects (\autoref{tbl:perceptions}), and grouped the speech variations related to perceptions of agents into four categories (dialog strategy, content affectiveness, content style and speech format) and eleven elements (\autoref{tbl:conversation_architecture}).

### 2023-06-06 sections/3-method.tex
finalized copy uploaded to TAPS

@@
 %, we reviewed and selected literature exploring the relationship between the specifics of conversation architecture elements and perceptions of CAs.
-Searches were carried out in the ACM Digital Library between January 1 and January 15, 2023.
+In accordance with accepted practices, we defined the scope of our literature review by considering two factors: (1) time---specifically publications from 2010 to 2022---and (2) source---using the ACM Digital Library \mbox{\cite{zheng2022ux, stigall2019older, mcconvey2023human}.}
+%Searches were carried out between January 1 and January 15, 2023. 
 Through our analysis, we didn't find any common terms used to refer to either conversation architecture elements or aspects of perceptions.
@@
 
+We analyzed the data by conducting reflexive thematic analysis approach with open and axial coding procedures \mbox{\cite{braun2019reflecting}}.
+First, we performed open coding on each article to extract labels related to perceptions of agents and conversation architecture.
+These labels were then grouped into conceptual categories through axial coding.
+The first author was responsible for performing the data analysis, with the second and third authors cross-checking the codes.
+We resolved disagreements through regular discussions and multiple rounds of revisions.
+
 \subsubsection*{Perceptions of Agents} To understand the perceptions of agents related to conversation architecture (RQ1), assessments for the perceptions of agents were extracted from each paper. 
-We used inductive thematic analysis to group these assessments into codes based on their meanings.
+%We used inductive thematic analysis to group these assessments into codes based on their meanings. 
 For example, likeability of the agent contains Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed}'s set of questions on likeability used by \cite{linnemann2018can}\cmt{[15]}, Subjective Assessment of Speech System Interface (SASSI) questionnaire \cite{hone2000towards}\cmt{sassi}'s set of questions on likeability used by \cite{chan2021kinvoices, choi2020nobody}\cmt{[74][54]} and questionnaire items like ``\textit{this voice agent was likeable}'' used by \cite{cuadra2021my}\cmt{[67]}.
@@
 Overall, 183 relationships between individual conversation architecture elements and perceptions of agents are incorporated into our synthesized framework, visualized as a heatmap to demonstrate their relationships with each other (\autoref{fig:heatmap_identified}).
-
-\subsection{Limitations}
-
-Our systematic literature review was limited to papers published in the ACM Digital Library between 2010 and 2022.
-We may have missed literature published outside this time period, as well as in other libraries.
-Also, most of the studies in our corpus are based on lab experiments using short interactions with users.
-The generalizability of these findings needs to be verified through longer-term engagements with conversational agents deployed in real-world situations.
-Lastly, research without empirical studies on the perception of agents is excluded based on our selection criteria.
-We may have missed some influential findings in these papers.
-%To better understand the relationships between conversation architecture elements and the perceptions of agents, we plan to conduct future reviews in literature and user studies to understand their real-world impacts.

### 2023-06-06 sections/5-discussion.tex
finalized copy uploaded to TAPS

@@
 More research is needed in this area to standardize the assessment of perceptions to make them consistent, granular, and comparable across literature.
+In the interim, we urge researchers to maintain the granularity of measurements to ensure that the subtleties among different perceptions of agents are preserved in their analysis.
 
@@
 
-\subsection{Ethical Considerations}
+\subsection{Design Implications and Ethical Considerations}
 
-The designers of conversational agents need to consider ethical implications and potential negative impacts for users.
-This section discusses three main areas of concern related to the effect of conversation architecture on the perceptions of agents: gender stereotypes, influencing users' actions, and privacy concerns.
+Although there are existing research on the relationship between conversation architecture used by CAs and how users perceive them, there is currently a lack of a comprehensive understanding of these connections.
+Our work proposes a framework that establishes a foundational understanding of the current state of research and highlights under-explored areas that require further investigation.
+This framework also serves as a guide for designers by summarizing the various conversation architecture elements that can be utilized in design, along with their corresponding influences on user perception of agents.
+Designers can use this framework to understand how their choice of conversation architecture affects user perception of agents, or to design for specific perceptions of agents using conversation architecture elements.
+For instance, designers seeking to enhance the perception of competence in an agent may investigate the effects of initiative strategies, affective language, formal language, and different prosody settings.
+However, designers of conversational agents need to be aware of and consider ethical implications and potential negative impacts for users.
+There are three main areas of concern related to the effect of conversation architecture on the perceptions of agents: gender stereotypes, influencing users' actions, and privacy concerns.
 
@@
 There is also a lack of voice generators available to generate voices that are perceived as androgynous \cite{tolmeijer2021female}\cmt{[62]}.
+To address the issue of gender stereotype, CA designers should give users easy access to choose from a variety of voices.
 
@@
 These persuasion techniques can be beneficial to help users achieve their goals, but they can also be used for harmful actions, such as trying to get users to believe in false information.
+Designers who use persuasive techniques in CAs should be transparent about their goal of influencing human perceptions and behaviors, and ensure that their actions are in the best interest of the users.
 
@@
 This can expose users to attacks, such as CAs using voice impersonation to ask for personal information for malicious intents \cite{chan2021kinvoices}\cmt{[74]}.
-Designing for perceptions of agents requires careful consideration of privacy issues including the sensitivity of the data, who has access to it, and how to protect against nefarious users.
+As such, CAs ought to be constructed in a manner that ensures complete clarity regarding the storage and usage of user data.
+Moreover, designers need to protect the privacy of users by taking into account the sensitivity of the data, determining who can access it, and devising measures to prevent malicious users from exploiting it.
+
+\subsection{Limitations and Future Directions}
+
+Our systematic literature review was limited to papers published in the ACM Digital Library between 2010 and 2022.
+We may have missed literature published outside this time period, as well as in other libraries.
+Also, most of the studies in our corpus are based on lab experiments using short interactions with users.
+The generalizability of these findings needs to be verified through longer-term engagements with conversational agents deployed in real-world situations.
+Lastly, we needed to rely on our own interpretations to categorize some of the perception measures into the framework due to inconsistent protocols used in the evaluation of perceptions of agents.
+%Lastly, research without empirical studies on the perception of agents is excluded based on our selection criteria.
+We may have missed some influential findings in these papers.
+%To better understand the relationships between conversation architecture elements and the perceptions of agents, we plan to conduct future reviews in literature and user studies to understand their real-world impacts.
+
+There are several future research directions that could enhance the proposed framework outlined in this paper.
+Firstly, establishing consistent measures for evaluating users' perceptions of agents is crucial to increase validity and consistency.
+Additionally, exploring under-examined aspects of the framework, such as how an agent's elaborateness affects its perceived ability (intelligence, competence, credibility), is necessary to further contribute to the body of knowledge.
+Moreover, delving deeper into the nuances that affect the relationship between conversation architecture and users' perceptions of agents is essential.
+This includes exploring contextual factors, such as users' prior experiences with conversational agents, as well as understanding how the combination of multiple conversation architecture elements can influence users' perceptions.

### 2023-06-06 sections/6-conclusion.tex
finalized copy uploaded to TAPS

--- 2023-02-21 sections/6-conclusion.tex
@@
 
-In this paper, we discussed the results of a systematic review of existing literature published in the ACM Digital Library on the effect of conversation architecture elements on the perceptions of CAs.
-Through our synthesis of 57 papers in our corpus, we present a framework outlining the relationships between elements of agents’ conversation architecture (dialog strategy, content affectiveness, content style and speech format) and aspects of users’ perception (interaction, ability, sociability and humanness).
-During our analysis, we found the need for consistent protocols in evaluating perceptions of agents, as measurements are inconsistent across studies.
-Further research is needed to investigate the under-explored areas in the framework, the relationship across perception aspects, the influence of contextual factors, and the effect of composite conversation architecture elements on users' perceptions.
-While our research contribute to the design conversation architecture to orchestrate specific perceptions of agent, we urge designers to incorporate ethical perspectives into their design considerations.
+In this paper, we share our findings of a systematic review of existing literature published in the ACM Digital Library on the effect of conversation architecture elements on the perceptions of CAs.
+Through the synthesis of 57 papers in our corpus, we found that current literature has explored users' perceptions of agents related to interaction, ability, sociability and humanness in relation to the effects of conversation architecture (RQ1).
+Also, we observed that conversation architecture elements related to dialog strategy, content affectiveness, content style, and speech format are relevant to users' perceptions of agents (RQ2).
+Based on our in-depth analysis, we present a framework outlining the identified relationships between elements of agents' conversation architecture and aspects of users' perception (RQ3).
+Our investigation also revealed the need for consistent protocols in evaluating perceptions of agents, as measurements are inconsistent across studies.
+Also, more research is needed to investigate the under-explored areas in the framework, the relationship across perception aspects, the influence of contextual factors, and the effect of composite conversation architecture elements on users' perceptions.
+While our research contribute to the design of conversation architecture to orchestrate specific perceptions of agents, we urge designers to incorporate ethical perspectives into their design considerations, including potential gender stereotypes, the use of persuasive techniques to influence users, and privacy issues related to users disclosing sensitive information to agents.

### 2023-06-06 sections/7-appendix.tex
finalized copy uploaded to TAPS

%TC:ignore
\onecolumn
\section{Appendix}

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}

\begingroup
\renewcommand{\arraystretch}{1.3}

\begin{longtable}{@{} | p{0.14\textwidth} | p{0.48\textwidth} | p{0.035\textwidth} | p{0.27\textwidth} | @{}}
\caption{Articles included in literature review} \\
\hline \textbf{Authors} & \textbf{Title} & \textbf{Year} & \textbf{Venue} \\ \hline
\endfirsthead

\multicolumn{4}{c}{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\hline \textbf{Authors} & \textbf{Title} & \textbf{Year} & \textbf{Venue} \\ \hline
\endhead

\endlastfoot

%Data
\citet{andrews2012system}\cmt{[38]} & 
  System personality and persuasion in human-computer dialogue & 
  2012 & ACM Transactions on Interactive Intelligent Systems (TiiS) \\ \hline 
\citet{ashktorab2019resilient}\cmt{[88]} &
  Resilient chatbots: Repair strategy preferences for conversational breakdowns &
  2019 & ACM Conference on Human Factors in Computing Systems (CHI) \\ \hline
\citet{ceha2022expressive}\cmt{[77]} &
  Expressive Auditory Gestures in a Voice-Based Pedagogical Agent &
  2022 & ACM Conference on Human Factors in Computing Systems (CHI) \\ \hline
\citet{ceha2021can}\cmt{[57]} &
  Can a Humorous Conversational Agent Enhance Learning Experience and Outcomes? &
  2021 & ACM Conference on Human Factors in Computing Systems (CHI) \\ \hline
\citet{chan2021kinvoices}\cmt{[74]} &
  KinVoices: Using Voices of Friends and Family in Voice Interfaces &
  2021 & ACM Conference on Computer Supported Cooperative Work (CSCW) \\ \hline
\citet{choi2020nobody}\cmt{[54]} &
  "Nobody speaks that fast!" An empirical study of speech rate in conversational agents for people with vision impairments &
  2020 & ACM Conference on Human Factors in Computing Systems (CHI) \\ \hline
\citet{cox2022does}\cmt{[27]} &
  Does Chatbot Language Formality Affect Users’ Self-Disclosure? &
  2022 & ACM Conference Conversational User Interfaces (CUI) \\ \hline
\citet{cuadra2021my}\cmt{[67]} &
  My bad! repairing intelligent voice assistant errors improves interaction &
  2021 & ACM Conference on Computer Supported Cooperative Work (CSCW) \\ \hline
\citet{daher2020empathic}\cmt{[58]} &
  Empathic chatbot response for medical assistance &
  2020 & ACM International Conference on Intelligent Virtual Agents (IVA) \\ \hline
\citet{diederich2019emulating}\cmt{[25]} &
  Emulating empathetic behavior in online service encounters with sentiment-adaptive responses: insights from an experiment with a conversational agent &
  2019 & International Conference on Computers and Information Systems (ICIS) \\ \hline
\citet{dubiel2020persuasive}\cmt{[60]} &
  Persuasive synthetic speech: Voice perception and user behaviour &
  2020 & ACM Conference Conversational User Interfaces (CUI) \\ \hline
\citet{elsholz2019exploring}\cmt{[61]} &
  Exploring Language Style in Chatbots to Increase Perceived Product Value and User Engagement &
  2019 & Conference on Human Information Interaction and Retrieval (CHIIR) \\ \hline
\citet{fadhil2018effect}\cmt{[52]} &
  The effect of emojis when interacting with conversational interface assisted health coaching system &
  2018 & EAI International Conference on Pervasive Computing Technologies for Healthcare (PervasiveHealth) \\ \hline
\citet{feijoo2021effects}\cmt{[70]} &
  Effects of Virtual Humans' Gender and Spoken Accent on Users' Perceptions of Expertise in Mental Wellness Conversations &
  2021 & ACM International Conference on Intelligent Virtual Agents (IVA) \\ \hline
\citet{gnewuch2018faster}\cmt{[19]} &
  Faster is not always better: understanding the effect of dynamic response delays in human-chatbot interaction &
  2018 & European Conference on Information Systems (ECIS) \\ \hline
\citet{gnewuch2018chatbot}\cmt{[21]} &
  The Chatbot is typing…'–The Role of Typing Indicators in Human-Chatbot Interaction &
  2018 & International Conference on Computers and Information Systems (ICIS) \\ \hline
\citet{gnewuch2022opposing}\cmt{[20]} &
  Opposing Effects of Response Time in Human-Chatbot Interaction &
  2022 & Business \& Information Systems Engineering (BISE) \\ \hline
\citet{go2021conversational}\cmt{[80]} &
  Conversational Agents Replying with a Manzai-style Joke &
  2021 & Australian Conference on Human-Computer Interaction (OzCHI) \\ \hline
\citet{haas2022keep}\cmt{[78]} &
  Keep it Short: A Comparison of Voice Assistants' Response Behavior &
  2022 & ACM Conference on Human Factors in Computing Systems (CHI) \\ \hline
\citet{habler2019effects}\cmt{[63]} &
  Effects of Smart Virtual Assistants' Gender and Language &
  2019 & Conference on Message understanding (MuC) \\ \hline
\citet{healey2013relating}\cmt{[39]} &
  Relating to speech evoked car personalities &
  2013 & ACM Conference on Human Factors in Computing Systems (CHI) \\ \hline
\citet{hoegen2019end}\cmt{[31]} &
  An End-to-End Conversational Style Matching Agent &
  2019 & ACM International Conference on Intelligent Virtual Agents (IVA) \\ \hline
\citet{hu2021enhancing}\cmt{[56]} &
  Enhancing the Perceived Emotional Intelligence of Conversational Agents through Acoustic Cues &
  2021 & ACM Conference on Human Factors in Computing Systems (CHI) \\ \hline
\citet{hu2022polite}\cmt{[76]} &
  Polite or Direct? Conversation Design of a Smart Display for Older Adults Based on Politeness Theory &
  2022 & ACM Conference on Human Factors in Computing Systems (CHI) \\ \hline
\citet{huiyang2022improving}\cmt{[17]} &
  Improving Interaction Experience through Lexical Convergence: The Prosocial Effect of Lexical Alignment in Human-Human and Human-Computer Interactions &
  2022 & International Journal of Human-Computer Interaction (IJHCI) \\ \hline
\citet{jeong2019exploring}\cmt{[10]} &
  Exploring effects of conversational fillers on user perception of conversational agents &
  2019 & ACM Conference on Human Factors in Computing Systems (CHI) \\ \hline
\citet{jestin2022effects}\cmt{[81]} &
  Effects of Wording and Gendered Voices on Acceptability of Voice Assistants in Future Autonomous Vehicles &
  2022 & ACM Conference Conversational User Interfaces (CUI) \\ \hline
\citet{khooshabeh2011does}\cmt{[37]} &
  Does it matter if a computer jokes &
  2011 & ACM Conference on Human Factors in Computing Systems (CHI) \\ \hline
\citet{kim2020can}\cmt{[24]} &
  "I Can Feel Your Empathic Voice": Effects of Nonverbal Vocal Cues in Voice User Interface &
  2020 & ACM Conference on Human Factors in Computing Systems (CHI) \\ \hline
\citet{kim2019comparing}\cmt{[89]} &
  Comparing Data from Chatbot and Web Surveys: Effects of Platform and Conversational Style on Survey Response Quality &
  2019 & ACM Conference on Human Factors in Computing Systems (CHI) \\ \hline
\citet{kraus2020effects}\cmt{[64]} &
  Effects of proactive dialogue strategies on human-computer trust &
  2020 & ACM Conference on User Modeling, Adaptation and Personalization (UMAP) \\ \hline
\citet{lee2019s}\cmt{[55]} &
  What’s on Your Virtual Mind? Mind Perception in Human-Agent Negotiations &
  2019 & ACM International Conference on Intelligent Virtual Agents (IVA) \\ \hline
\citet{lee2020hear}\cmt{[23]} &
  "I Hear You, I Feel You": encouraging deep self-disclosure through a chatbot &
  2020 & ACM Conference on Human Factors in Computing Systems (CHI) \\ \hline
\citet{linnemann2018can}\cmt{[15]} &
  ‘Can I Trust the Spoken Dialogue System Because It Uses the Same Words as I Do?’—Influence of Lexically Aligned Spoken Dialogue Systems on Trustworthiness and User Satisfaction &
  2018 & Interacting with Computers (IWC) \\ \hline
\citet{lubis2019positive}\cmt{[43]} &
  Positive emotion elicitation in chat-based dialogue systems &
  2019 & IEEE/ACM Transactions on Audio, Speech and Language Processing (TASLP) \\ \hline
\citet{lubold2016effects}\cmt{[86]} &
  Effects of voice-adaptation and social dialogue on perceptions of a robotic learning companion &
  2016 & ACM/IEEE International Conference on Human-Robot Interaction (HRI) \\ \hline
\citet{ma2022ask}\cmt{[29]} &
  Ask a Further Question or Give a List? How Should Conversational Agents Reply to Users' Uncertain Queries &
  2022 & International Journal of Human-Computer Interaction (IJHCI) \\ \hline
\citet{miehle2018exploring}\cmt{[51]} &
  Exploring the impact of elaborateness and indirectness on user satisfaction in a spoken dialogue system &
  2018 & ACM Conference on User Modeling, Adaptation and Personalization (UMAP) \\ \hline
\citet{misu2011toward}\cmt{[83]} &
  Toward construction of spoken dialogue system that evokes users' spontaneous backchannels &
  2011 & SIGdial Workshop on Discourse and Dialogue (SIGDIAL) \\ \hline
\citet{miyamoto2017improving}\cmt{[46]} &
  Improving Relationships Based on Positive Politeness Between Humans and Life-Like Agents &
  2017 & International Conference on Human-Agent Interaction (HAI) \\ \hline
\citet{moilanen2022measuring}\cmt{[82]} &
  Measuring the Effect of Mental Health Chatbot Personality on User Engagement &
  2022 & International Conference on Mobile and Ubiquitous Multimedia (MUM) \\ \hline
\citet{niewiadomski2013laugh}\cmt{[85]} &
  Laugh-aware virtual agent and its impact on user amusement &
  2013 & International Conference on Autonomous Agents and Multiagent Systems (AAMAS) \\ \hline
\citet{ouchi2019should}\cmt{[59]} &
  Should speech dialogue system use honorific expression? &
  2019 & International Conference on Human-Agent Interaction (HAI) \\ \hline
\citet{roy2021users}\cmt{[71]} &
  Users, Tasks, and Conversational Agents: A Personality Study &
  2021 & International Conference on Human-Agent Interaction (HAI) \\ \hline
\citet{seeger2021chatbots}\cmt{[35]} &
  Chatbots often Fail! Can Anthropomorphic Design Mitigate Trust Loss in Conversational Agents for Customer Service? &
  2021 & European Conference on Information Systems (ECIS) \\ \hline
\citet{spillner2021talk}\cmt{[18]} &
  Talk to Me on My Level-Linguistic Alignment for Chatbots &
  2021 & International Conference on Human-Computer Interaction with Mobile Devices and Services (MobileHCI) \\ \hline
\citet{tolmeijer2021female}\cmt{[62]} &
  Female by default?--exploring the effect of voice assistant gender and pitch on trait and trust attribution &
  2021 & ACM Conference on Human Factors in Computing Systems (CHI) \\ \hline
\citet{volkel2021examining}\cmt{[69]} &
  Examining User Preference for Agreeableness in Chatbots &
  2021 & ACM Conference Conversational User Interfaces (CUI) \\ \hline
\citet{volkel2021manipulating}\cmt{[68]} &
  Manipulating and Evaluating Levels of Personality Perceptions of Voice Assistants through Enactment-Based Dialogue Design &
  2021 & ACM Conference Conversational User Interfaces (CUI) \\ \hline
\citet{volkel2022user}\cmt{[75]} &
  User perceptions of extraversion in chatbots after repeated use &
  2022 & ACM Conference on Human Factors in Computing Systems (CHI) \\ \hline
\citet{wester2015artificial}\cmt{[14]} &
  Artificial personality and disfluency &
  2015 & INTERSPEECH \\ \hline
\citet{westerman2019believe}\cmt{[9]} &
  I Believe in a Thing Called Bot: Perceptions of the Humanness of “Chatbots” &
  2019 & Communication Studies \\ \hline
\citet{wilhelm2022keep}\cmt{[28]} &
  Keep on Smiling: An Investigation of the Influence of the Use of Emoticons by Chatbots on User Satisfaction &
  2022 & ACM Conference Conversational User Interfaces (CUI) \\ \hline
\citet{xiao2021let}\cmt{[73]} &
  Let Me Ask You This: How Can a Voice Assistant Elicit Explicit User Feedback? &
  2021 & ACM Conference on Computer Supported Cooperative Work (CSCW) \\ \hline
\citet{yang2021effect}\cmt{[72]} &
  The Effect of the Repetitive Utterances Complexity on User’s Perceived Empathy and Desire to Continue Dialogue by a Chat-oriented Dialogue System &
  2021 & International Conference on Human-Agent Interaction (HAI) \\ \hline
\citet{yang2017perceived}\cmt{[44]} &
  Perceived Emotional Intelligence in Virtual Agents &
  2017 & ACM Conference on Human Factors in Computing Systems (CHI) \\ \hline
\citet{zhu2022effects}\cmt{[26]} &
  Effects of Emotional Expressiveness on Voice Chatbot Interactions &
  2022 & ACM Conference Conversational User Interfaces (CUI) \\ \bottomrule
%\end{tabular}
\end{longtable}
\label{tab:appendix}
\endgroup
%TC:endignore
